### 2021-05-19 main.tex
Initial Overleaf Import

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[
backend=biber,
style=authoryear,
citestyle=authoryear
]{biblatex}
\renewcommand*{\bibfont}{\small}
\usepackage[normalem]{ulem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}

\pagestyle{fancy}
\fancyhf{}
\rhead{The Causal Effect of Media Frames on Migration Attitudes}
\lhead{Nicolai Berk}
\cfoot{\thepage}

\useunder{\uline}{\ul}{}

\addbibresource{PhD-Proposal.bib}

\usepackage{xcolor}

\title{The Causal Effect of Media Frames on Migration Attitudes}
\author{Nicolai Berk\footnote{Doctoral Candidate, Dynamics Doctoral Program, Humboldt-Universität zu Berlin}}
\date{May 2021}

\begin{document}

\maketitle

\section{Motivation}

% \textbf{[DISCUSS IMPLICATIONS OF CHANGING FRAMING, MEANING CHANGING ISSUE ASSOCIATION: ATTITUDE CHANGE (DRUCKMAN, FRAMING LIT), CHANGING COGNITIVE ISSUE REPRESENTATION (HEBB, ???),

% \textbf{generally framing would let us expect strong effects from media changes, BUT findings here are mixed, lit alternates between weak and strong effects}

% \textbf{[AV: DISCUSS SPIRIG PAPER]}

% The first empirical study will lay the foundations for the remainder of the dissertation by establishing whether changes in the media framing of given issues result in changes in citizen's issue definitions and attitudes. Exploiting a rare shift in migration framing by the major German tabloid \textit{Bild} during the summer of 2015, I will assess the causal effect of a changing definition of migration in the media on opinions and issue definitions among citizens. The findings will speak to both the literature on the generalisability of framing effects and research about media effects on mass opinion formation.

While the validity of framing effects and their conditions has been extensively researched in the experimental setting, the applicability of these findings in real-world environments is still under debate (\cite{Barabas2010, Busby2019, Leeper2020}). The few observational studies that were conducted produced conflicting results and have usually not tried to estimate causal effects (\cite{Jerit2008, Jerit2009a, Mclaren2018}). This lack of clarity also relates to a broader debate about the influence of the media on citizens' political attitudes: the literature seems to alternate between conceptualising very strong and very weak effects (\cite{Bennett2008, Spirig2020, Zaller1996}).

As discussed in the first part of this proposal, experimental evidence suggests that changing issue definitions in the media should affect the mental pictures that citizens form about issues. This should first and foremost result in a changed weighting of considerations about the issue. If we present someone with a frame containing association A, they should be more likely to include consideration A in their reasoning about the issue than someone who has not received the frame or received a frame with a different consideration. I expect this logic to translate to news frames as well.

The association of an issue with different considerations should subsequently inform respondents' evaluation of the issue in line with the value-expectancy model. Thus, when the prevalence of positive considerations in the presented news content increases, the respondents should form a more positive opinion about the issue, and vice versa.

However, this effect of associated considerations on issue attitudes should not be unconditional. As previous research indicates, individuals' attitude stability is dependent on their political knowledge (\cite{Converse1962}). If citizens have higher knowledge about political issues, they should rely less on the immediately available considerations presented in the news and more on memorised information about an issue instead (\cite{Zaller1992}). Hence, they should show a weaker inclination to respond to changing issue associations in the media.

Similarly, the strength of pre-existing opinions about an issue has been shown to condition framing effects (\cite{Bechtel2015, Chong2013}). This means that only respondents with no clear opinion on an issue will show susceptibility to framing. This might be attributed to higher knowledge about an issue or cue-taking from political parties. If the former is the case, the effect of pre-existing opinions should diminish when controlling for political knowledge, if the latter, controlling for partisanship should explain the relationship.

Lastly, some commentators have argued that framing effects are unlikely in modern communication environments, where news consumption is divided among partisan lines and readers show higher selectivity in their media choices (\cite[720]{Bennett2008}). This would mean that, when a news outlet changes its reporting on an issue in such a way that it conflicts with readers' assessment of the topic, readers will seek out other information sources (instead of changing their opinion about the issue).

% discuss Slothuus 2010: When can political parties lead public opinion?

% gap: generalisability of framing effects, media effect size
% [discuss size of found media effects in the real world, Zaller, Ladd and Lenz, Murphy and Devine, Van Aelst and Walgrave 2011, Foos and Bischof, Boomgarden and Vliegenthart, Guess2021, Spirig2020; might also think about conditions under which this happens]

% Take in more from Spirig 2020 (5): "Be it radio stations (Yanagizawa-Drott, 2014; Adena et al., 2015), TV channels (DellaVigna and Kaplan, 2007; Enikolopov, Petrova and Zhuravskaya, 2011; Hopkins and Ladd, 2014; Barone, D’Acunto and Narciso, 2015; Martin and Yurukoglu, 2017) or newspapers (Ladd and Lenz, 2009; Gerber, Karlan and Bergan, 2009; Reeves, McKee and Stuckler, 2016), many recent studies drawing on causal inference research designs ﬁnd that exposure to a medium increases support for the candidates pushed by the medium. That is not the case in all studied contexts, however. For example, Martin and Yurukoglu (2017) do not ﬁnd that people who quasi-randomly watch MSNBC more are more likely to support democratic candidates and Gerber, Karlan and Bergan (2009) show that both randomly receiving the more liberal or the more conservative newspaper increased support for the Democrat candidate in the 2005 Virginia gubernatorial election. In particular, recent work on the eﬀect of newspapers on political preferences, both historic and contemporary, raises doubts about the power of newspapers. Gentzkow,"

\subsubsection{Hypotheses}

\begin{enumerate}
    \item[H 1.1]{When news coverage of an issue becomes more associated with specific considerations, these considerations will be more common in media consumers' descriptions of the issue.}
    \item[H 1.2]{When news coverage of an issue becomes more associated with positive (negative) considerations, consumers will develop a more positive (negative) opinion towards the issue.}
    \item[H 1.3]{When news coverage of an issue becomes more associated with  positive (negative) considerations, consumers will develop a more positive (negative) opinion towards the issue \textit{only if they have low political knowledge}.}
    \item[H 1.4a]{When news coverage of an issue becomes more associated with positive (negative) considerations, consumers will develop a more positive (negative) opinion towards the issue \textit{if they had no clear opinion about the issue before}.}
    \item[H 1.4b]{The moderating effect of pre-existing opinions can be explained by \textit{political knowledge}.}
    \item[H 1.4c]{The moderating effect of pre-existing opinions can be explained by \textit{partisanship}.}
    \item[H 1.5]{When news coverage of an issue becomes more associated with positive (negative) considerations, those readers with conflicting attitudes towards the issue will stop reading the paper.}
\end{enumerate}

\subsubsection{Empirical strategy}

% \textbf{[HK: DROP EXOGENOUS LANGUAGE, DISTINGUISH FROM FOOS \& BISCHOF, THINK ABOUT DV REG CONTRIBUTION, SPILLOVER FROM BILD TO OTHER OUTLETS?]}

% This study seeks to assess the causal effect of changing media frames on citizens' issue definitions and attitudes.

Exploiting a rare shift in migration framing by the major German tabloid \textit{Bild}, I will assess the causal effect of a changing definition of migration in the media on opinions and issue definitions among citizens.

During the summer of 2015, the German tabloid \textit{Bild} dramatically changed it's framing of migration and refugees, calling for support for the newly arriving immigrants and attacking those promoting hate against refugees online (\cite{Bild2015Pranger, TagesspiegelBildPranger}), before starting the campaign 'We help - \#refugeeswelcome' (\cite{BildRefugeesWelcome}). With this move, the paper heavily diverged from its right-wing tradition. The major change in tone was largely ascribed to editor-in-chief Kai Diekmann, who had also invited a refugee family to live in his house (\cite{BR2015Diekmann}). In late 2015, Diekmann left for another position in the company, and was replaced by Tanit Koch, who promoted a more anti-immigrant tone of the paper. She was replaced two years later by \textit{Bild online}-editor Julian Reichelt (\cite{Spiegel2018Koch}), who amplified the tone further, which resulted in major criticism of the paper (\cite{Niggemeyer2018Bild, DLF2018Reichelt}).

% \textbf{[treatment isnt endogenous and doesnt need to be]}

I hope to exploit these communicative shifts in the paper's migration framing to assess the effects of media framing on readers' issue definitions, attitudes, and voting behaviour. If the migration framing changed in \textit{Bild} while other outlets maintained their framing, this presents an ideal case to estimate the causal effect of changes in media framing.

%  (the migration issue came up unexpectedly, Diekmann was promoted\footnote{\url{https://www.sueddeutsche.de/medien/boulevard-zeitung-tanit-koch-wird-chefredakteurin-der-bild-1.2723462}} and Tanit Koch apparently lost an internal power struggle with Julian Reichelt\footnote{\url{https://www.faz.net/aktuell/feuilleton/medien/chefredakteurin-tanit-koch-verlaesst-die-bild-15429101.html}})

I will rely on several datasets to estimate the effect of this shift in migration framing:
\begin{itemize}
    \item \textit{Bild} articles (print) for the respective period (2015-2018) to measure the changes in migration framing.
    \item \textit{Bild online} articles would provide a comparison and credibility check to compare the framing under Reichelt and Koch, as he was in charge of the online news, while she was in charge of the print paper.
    \item Variables from the long-term online tracking survey of the German Longitudinal Election Study:
    \begin{itemize}
        \item \textbf{Respondents' media consumption.} This conditioning variable allows me to compare \textit{Bild}-readers to consumers of other media and to assess whether they were responsive to the paper's communicative shifts.
        \item \textbf{Open-ended 'most-important-problem' question (MIP).} This enables me to test whether respondents' associations with the migration issue changed.
        \item \textbf{Migration attitudes.} This variable indicates whether changes in migration framing in the media affect readers' assessment of political issues - the core claim of both the media effects and the framing literature.
        % \item \textbf{Vote decision.} This dependent allows to test whether changes in media frames affected voting behaviour.
        \item \textbf{Political Knowledge.} This independent variable allows to test whether susceptibility to framing is dependent on political knowledge.
    \end{itemize}
\end{itemize}

While I will collect the \textit{Bild} articles myself using webscraping, the survey data is provided by the German Longitudinal Election Study (GLES). The long-term online tracking consists of quarterly surveys of a random sample of about 1,000 respondents beginning in 2009 and ending in 2017 (\cite{GLES2019LongTermTracking}). Importantly, it contains questions on media usage, specifically if respondents read \textit{Bild}, as well as open-ended questions about the most important problem, attitudes towards migration (later on also specific batteries on attitudes towards refugees), and political knowledge in most waves.

This provides great data to estimate whether the issue definitions and attitudes of \textit{Bild} readers changed in response to changing coverage in 2015 and 2016, but the data has limitations. Most importantly, the survey does not interview the same respondents again. This means that I won't be able to assess hypotheses 1.4 a-c and 1.5. To test these hypotheses, the GLES Panel survey might be used. This data only covers 2016-2020, which includes the last but likely weakest treatment (Reichelt replaced Koch; see figure \ref{fig:gles}). Additionally, the number of respondents in the longterm online tracking is rather small given that my group of interest is \textit{Bild} readers. These should constitute 150-200 respondents per wave. Again, the panel would provide a solution, with 2,000-4,000 \textit{Bild} readers per wave (15-20\% of respondents).

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{gles_treatments.png}
    \caption{Relative timing of possible shifts in migration framing and survey field times.}
    \label{fig:gles}
\end{figure}

Which treatment is viable will have to be decided based on an empirical comparison of the migration frames in \textit{Bild} to those in other newspapers. If the framing in \textit{Bild} diverges from a parallel trend with the framing of other newspapers, the treatment is viable. This will be measured by pre-selecting migration articles with supervised machine-learning classifiers, before using sentiment analysis to track the tone of migration coverage.

After the selection of the viable treatment, a differences-in-differences design (DiD) will be estimated:

$$ y = \beta_1 * T + \beta_2 * B + \beta_3 * T * B $$

Where $y$ is the dependent (migration association or attitude), $T$ indicates the survey took place after the treatment/shift in migration framing, and $B$ indicates whether the respondent is a \textit{Bild}-reader. This means that the average of the dependent variable among \textit{Bild}-readers following the treatment is compared to non-\textit{Bild}-readers, both before and after the treatment, and \textit{Bild}-readers before treatment. $\beta_3$ - the quantity of interest - is then equal to the difference-in-differences, meaning the change in the dependent variable from before to after treatment, adjusted for the change among the control group (non-\textit{Bild} readers).

While the implementation is relatively straightforward for the migration attitude-variable using a five-point Likert scale, it is more complicated for the association of concepts with migration. Whether this can be measured is highly dependent on the number of responses discussing migration in the open answers to the most-important problem question. If possible, several surveys preceding and during the treatment (i.e. while the migration framing in \textit{Bild} differs from other newspapers) should be pooled to increase the number of respondents.

To estimate the changing meaning of concepts in text, word embeddings have emerged as a state-of-the-art method. This method allows the numerical representation of semantic meaning in a high-dimensional vector-space. Those words with more similar meanings will occur closer together in the vector space, which allows the identification of changing meaning across corpora. However, these models require extensive training data (\cite{Rodman2019}). Recent work has tackled this problem by mapping embeddings into pre-trained, high-quality embedding spaces (\cite{Khodak2018}). This opens the possibility to quantitatively assess changing meaning in applications with few observations, such as open survey responses. Building on this work, \citeauthor{Rodriguez2020} have developed \textit{embedding regression}, which allows to express changing meanings as a function of covariates (\citeyear{Rodriguez2020}). Using the DiD to estimate these changes in meaning, it will be possible to understand how \textit{Bild}-readers understanding of migration changed following the treatment, compared to changes in the control group.

This will be compared to the outputs of the embedding regression for DiD with newspaper data, comparing migration framing in the \textit{Bild} before and after treatment to other newspapers before and after treatment. If the changes in the definition of migration indicated by the DiD are similar in the newspaper data and the survey responses, this constitutes strong evidence for a direct transmission of news frames into the issue definitions of consumers of these news.

% \textbf{[AV:  You should add info on who the part of people who actually write a lot are. Are they representative of BILD readers? Reichelt: Move from online editor to main editor? Does she have no influence on frames already? Do you have data on how ppl consume media?]}

\end{document}

### 2021-05-31 main.tex
Updates from Overleaf

@@
 \fancyhf{}
-\rhead{The Causal Effect of Media Frames on Migration Attitudes}
+\rhead{Hypodermic needle after all?}
 \lhead{Nicolai Berk}
@@
 
-\title{The Causal Effect of Media Frames on Migration Attitudes}
-\author{Nicolai Berk\footnote{Doctoral Candidate, Dynamics Doctoral Program, Humboldt-Universität zu Berlin}}
+\title{Hypodermic needle after all? Individual-level Moderators of Media Framing Effects}
+\author{Nicolai Berk\footnote{Doctoral Candidate, Dynamics Doctoral Program, Humboldt-Universität zu Berlin, \href{mailto:nicolai.berk@hu-berlin.de}{nicolai.berk@hu-berlin.de}}}
 \date{May 2021}
@@
 
+\begin{abstract}
+    Scholars of political behaviour continue to debate the importance of the news media for citizens' opinion formation process.
+It has been argued that in today's media environment, persuasive effects of media coverage are unlikely, as viewers self-select into outlets whose coverage is in line with their preferences.
+At the same time, a growing body of evidence shows that endorsements and changing media content sometimes affect citizens' preferences, but not always.
+Current scholarship explains this with environmental conditions, such as the ability of consumers to discount for a newspaper's bias, which favour or inhibit the effectiveness of media coverage.
+This paper contributes to this debate by assessing how consumers' individual-level characteristics condition news framing effects.
+It does so by leveraging a sudden shift in the migration framing of the major German tabloid, \textit{Bild}.
+This case allows to assess the causal effect of changing news frames on survey respondents' migration attitudes and - using state-of-the-art text analysis tools - issue definitions, as well as conditioning characteristics.
+\end{abstract}
+
 \section{Motivation}
 
-% \textbf{[DISCUSS IMPLICATIONS OF CHANGING FRAMING, MEANING CHANGING ISSUE ASSOCIATION: ATTITUDE CHANGE (DRUCKMAN, FRAMING LIT), CHANGING COGNITIVE ISSUE REPRESENTATION (HEBB, ???),
+% This needs to be tailored more closely to the interest of media framing - currently, there is a lot more in here
 
-% \textbf{generally framing would let us expect strong effects from media changes, BUT findings here are mixed, lit alternates between weak and strong effects}
+How does the news media affect citizens' issue attitudes?
+Research on political behaviour has discussed this question for nearly a century.
+Classic theories of agenda setting hold that the attention devoted to issues in the news media will guide citizens to consider these issues important (\cite{McCombs1972}).
+Similarly, the literature on framing expects that the presentation of issues in the news media will affect recipients' opinions about these issues (\cite{Nelson1997}).
+Both theories suggest that media coverage strongly affects citizens' understanding of and opinions about politics.
 
-% \textbf{[AV: DISCUSS SPIRIG PAPER]}
+A vast amount of evidence supports this notion of the importance of newspaper coverage for political behaviour.
+Observational evidence shows that newspaper exposure (\cite{Foos2020, Spirig2020}), endorsements of specific candidates (\cite{Ladd2009a, Chiang2011a}), coverage of specific topics (\cite{King2017}), reports on political parties (\cite{Boomgaarden2009, Devine2020}), internet access (\cite{Schaub2020}), and changes in television news content (\cite{Durante2012}) have affected which issues citizens care about, their opinion about these issues, and their voting behaviour.
+An even larger body of experimental work reports strong effects of issue framing on participants' issue attitudes (see \cite{Busby2019} for a recent overview).
 
-% The first empirical study will lay the foundations for the remainder of the dissertation by establishing whether changes in the media framing of given issues result in changes in citizen's issue definitions and attitudes.
-Exploiting a rare shift in migration framing by the major German tabloid \textit{Bild} during the summer of 2015, I will assess the causal effect of a changing definition of migration in the media on opinions and issue definitions among citizens.
-The findings will speak to both the literature on the generalisability of framing effects and research about media effects on mass opinion formation.
+Yet, a popular critique of these theories maintains that strong news effects are unlikely in the modern media environment, where consumers self-select into news sources of their liking.
+As a result, "most media users will rarely find themselves in the path of attitude-discrepant information".
+Even if consumers had to face such discrepant information, this should reinforce their existing views rather than persuade as they are used to a partisan media diet (\cite[724f]{Bennett2008}).
+Similarly, agenda setting effects are unlikely as a result of selective exposure (\cite{Lau2021}).
 
-While the validity of framing effects and their conditions has been extensively researched in the experimental setting, the applicability of these findings in real-world environments is still under debate (\cite{Barabas2010, Busby2019, Leeper2020}).
-The few observational studies that were conducted produced conflicting results and have usually not tried to estimate causal effects (\cite{Jerit2008, Jerit2009a, Mclaren2018}).
-This lack of clarity also relates to a broader debate about the influence of the media on citizens' political attitudes: the literature seems to alternate between conceptualising very strong and very weak effects (\cite{Bennett2008, Spirig2020, Zaller1996}).
+This "minimal effects" view is supported by a body of evidence as well.
+\citeauthor{Gentzkow2011} show that even historically, the entry and exit of newspapers in the US does affect turnout, but that the newspapers' slant does not affect either party's vote share.
+They conclude that "the persuasive effect of partisan newspapers is limited" (\citeyear[3011]{Gentzkow2011}).
+Recently, \citeauthor{Guess2021} incentivised participants of an online-panel to visit left- or right-leaning news websites, with no effect on opinions (\citeyear{Guess2021}).
+An experiment by \citeauthor{Lau2021} indicates that increasing the likelihood of encountering information about a fictitious candidate's stance on a given issue does not increase the importance of that issue in reaching a voting decision, directly contradicting theories of agenda setting.
+This lack of evidence echos a general critique of the external validity of framing experiments and other experimental evidence about opinion formation (\cite{Barabas2010, Busby2019, Leeper2020}).
 
-As discussed in the first part of this proposal, experimental evidence suggests that changing issue definitions in the media should affect the mental pictures that citizens form about issues.
-This should first and foremost result in a changed weighting of considerations about the issue.
-If we present someone with a frame containing association A, they should be more likely to include consideration A in their reasoning about the issue than someone who has not received the frame or received a frame with a different consideration.
-I expect this logic to translate to news frames as well.
+This conflicting evidence begs the question: when can we expect media framing effects?
+\citeauthor{Chiang2011a} argue that endorsements from newspapers with ideological leanings neutral or opposite to the endorsed party/candidate should have stronger effects on voting behaviour, as voters discount the general bias of a newspaper (\citeyear{Chiang2011a}).
+\citeauthor{Spirig2020} shows that the takeover of a Swiss regional newspaper through a leading politician of the far-right and the subsequent change in its political slant had no effect on citizens' voting behaviour and suggests that this is a result of voters discounting the new owner's political slant and stopping to read the newspaper.
 
-The association of an issue with different considerations should subsequently inform respondents' evaluation of the issue in line with the value-expectancy model.
-Thus, when the prevalence of positive considerations in the presented news content increases, the respondents should form a more positive opinion about the issue, and vice versa.
+Prior experimental research also suggests that individual characteristics condition opinion stability (\cite{Converse1962, Zaller1992}).
+As a result, news framing should affect individuals differently.
+The goal of the present study is to assess whether changing news frames affect individual issue definitions and attitudes in a case where voters are unlikely to discount, and whether the strength of this effect is dependent on individual characteristics.
+This manuscript proceeds in three steps: the next section explains how I will operationalise framing, before I discuss possible individual-level moderators and formulate hypotheses.The last section describes the case of interest and briefly outlines my empirical strategy.
 
-However, this effect of associated considerations on issue attitudes should not be unconditional.
+\section{Emphasis framing and the value-expectancy model of opinion formation}
+
+While news slant is a very general concept, and sometimes operationalised as closeness to specific parties (\cite{Gentzkow2010}) or issue positions/tonality (\cite{Spirig2020}), framing theory provides a specific expectation about which treatment should affect which issue attitudes how.
+"Framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy" (\cite[567]{Nelson1997}).
+A "frame" is then the operating unit of this process, defining the issue at hand in a specific way.
+Different forms of frames have been conceptualised.
+When I talk about 'frames', I refer to \textit{emphasis frames}.
+These frames emphasise certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame (\cite[153f]{Leeper2020}).
+For example, issues of increasing welfare contributions might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes.
+Individuals' support of a statement will differ dependent on the frame presented (\cite{sniderman2004structure}).
+
+While this broad definition gives a first idea of what framing is about, the concept of emphasis framing has been criticised for being too broad and imprecise to contribute anything meaningful to the field (\cite{Scheufele2012}).
+To address this shortcoming, I follow the framing literature building on the \textit{value-expectancy model} (\cite{Ajzen2000, Nelson1997}).
+This model suggests that an attitude on a given issue is a function of two things: considerations and their respective weights.
+The evaluation of the issue is subdivided into a number of considerations (to which political scientists might refer as "valence issues") that will be easier to evaluate.
+For example, to evaluate whether a lockdown is necessary to battle the spread of Covid-19 in one's country, a person might consider the detrimental short-term effect on businesses and individuals' mental health (negative considerations), as well as the cost of overburdened hospitals and additional deaths (positive considerations, at least with respect to the evaluation of a lockdown).
+Individuals weigh each of these considerations to form an overall opinion on the subject.
+
+Figure \ref{fig:cogStor} visualises this logic.
+A given issue is associated with an attitude or evaluation $y$.
+The issue is related to a number of different considerations, each of which carries an associated evaluation $x_i$, e.g.
+that the prevention of overcrowded hospitals is a good thing.
+Each of these considerations is more or less associated with the issue.
+Based on the strength of this association $w_i$, a given consideration's evaluation is more or less reflected in the issue evaluation $y$, which is equal to the weighted sum of considerations.
+Emphasis framing affects the issue attitude $y$ by changing the weights of different considerations\footnote{Note that this concept of framing is identical to second-level or attribute agenda setting (\cite{Lopezescobar2017, McCombs2000}; see \cite[174]{Mclaren2018} for a discussion of the overlap of these literatures).
+I will stick to the framing perspective here as the literature is focused on issues rather than candidates' attributes, and the conceptualisation as frame allows to form expectations about citizens' reactions to changing news frames.}.
+
+This operationalisation allows us to generate specific expectations about how frames in the news media affect respondents' issue opinions.
+When presented with an emphasis frame on a given issue, the respondents' cognitive association of the issue with the emphasised consideration should increase, thus changing the evaluation of the issue by increasing the importance of the consideration.
+If the consideration is positive (towards the issue), the attitude towards the issue should improve, and the opposite when it is negative.
+This also means that the definition of the issue (the cognitive image evoked when thinking of the issue) is changed by strengthening the association with the consideration.
+
+% JB: I’m wondering if negative reference might help you with the definition.
+In our last colloquium you still got the criticism that framing was not well defined enough.
+I think you might be able to avoid a lot of the criticism (what makes framing different from issue ownership etc.) by addressing the contrast from framing from some of the more used concepts such as issue attention.
+Just an idea
+
+% \footnote{I will stop here to outline the other chapters.
+However, a future version of this draft will discuss the cognitive basis of this model (considerations: affective storage as discussed by Taber and Lodge, Kunda; weights: physical cognitive association through Hebbian learning) and  whether this is a rational model (\cite{Ajzen2000, Druckman2001}).}.
+
+\begin{center}
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{CognitiveStorage.png}
+    \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}
+    \label{fig:cogStor}
+\end{figure}
+\end{center}
+
+\section{Susceptibility to framing effects}
+
+As discussed before, my interest revolves not only around whether media frames affect respondents' issue definitions and attitudes, but also whether this effect is dependent on individual characteristics.
 As previous research indicates, individuals' attitude stability is dependent on their political knowledge (\cite{Converse1962}).
@@
 Hence, they should show a weaker inclination to respond to changing issue associations in the media.
-
 Similarly, the strength of pre-existing opinions about an issue has been shown to condition framing effects (\cite{Bechtel2015, Chong2013}).
 This means that only respondents with no clear opinion on an issue will show susceptibility to framing.
-This might be attributed to higher knowledge about an issue or cue-taking from political parties.
+% This might be attributed to higher knowledge about an issue or cue-taking from political parties.
 If the former is the case, the effect of pre-existing opinions should diminish when controlling for political knowledge, if the latter, controlling for partisanship should explain the relationship.
 
-Lastly, some commentators have argued that framing effects are unlikely in modern communication environments, where news consumption is divided among partisan lines and readers show higher selectivity in their media choices (\cite[720]{Bennett2008}).
-This would mean that, when a news outlet changes its reporting on an issue in such a way that it conflicts with readers' assessment of the topic, readers will seek out other information sources (instead of changing their opinion about the issue).
+If the media environment conditions framing effects across time (\cite{Bennett2008}), it might also well be that individuals with different news consumption habits are differently affected by framing.
+While consumers with only a single source of news might - similar to citizens in the golden age of broadcast television - be more inclined to follow their news source's framing, those with a more balanced media diet from different sources might resist the changing framing.
 
-% discuss Slothuus 2010: When can political parties lead public opinion?
+% add motivated reasoners taking partisan cues
 
-% gap: generalisability of framing effects, media effect size
-% [discuss size of found media effects in the real world, Zaller, Ladd and Lenz, Murphy and Devine, Van Aelst and Walgrave 2011, Foos and Bischof, Boomgarden and Vliegenthart, Guess2021, Spirig2020; might also think about conditions under which this happens]
+The next section lists the main hypotheses.
+Hypotheses 1 and 2 are based on the value-expectancy model of framing: if a reader is exposed to a given consideration through an emphasis frame, this consideration will feature more prominently in their definition of the issue.
+As a result of this, the consideration will also affect their issue attitude.
+3 and 4a build on the viewer's choice framework.
+An extreme version of this framework could predict that, in response to the changing media framing, opinionated readers will seek out other news sources in line with their attitudes (see also \cite{Spirig2020}).
+If readers are solely dependent on the source of the frame (consuming no other newspaper), they will be more susceptible to framing.
+The two other conditioning variables - political knowledge and clear opinion - relate to the availability of frames in memory (4b \& 4c).
+Without a clear information about the issue or a position to identify with, receivers should be more likely to follow the frame.
+% add that motivated reasoning suggests that partisans are cue-takers ad will ignore frames
 
-% Take in more from Spirig 2020 (5): "Be it radio stations (Yanagizawa-Drott, 2014; Adena et al., 2015), TV channels (DellaVigna and Kaplan, 2007; Enikolopov, Petrova and Zhuravskaya, 2011; Hopkins and Ladd, 2014; Barone, D’Acunto and Narciso, 2015; Martin and Yurukoglu, 2017) or newspapers (Ladd and Lenz, 2009; Gerber, Karlan and Bergan, 2009; Reeves, McKee and Stuckler, 2016), many recent studies drawing on causal inference research designs ﬁnd that exposure to a medium increases support for the candidates pushed by the medium.
-That is not the case in all studied contexts, however.
-For example, Martin and Yurukoglu (2017) do not ﬁnd that people who quasi-randomly watch MSNBC more are more likely to support democratic candidates and Gerber, Karlan and Bergan (2009) show that both randomly receiving the more liberal or the more conservative newspaper increased support for the Democrat candidate in the 2005 Virginia gubernatorial election.
-In particular, recent work on the eﬀect of newspapers on political preferences, both historic and contemporary, raises doubts about the power of newspapers.
-Gentzkow,"
-
-\subsubsection{Hypotheses}
+\section{Hypotheses}
 
 \begin{enumerate}
-    \item[H 1.1]{When news coverage of an issue becomes more associated with specific considerations, these considerations will be more common in media consumers' descriptions of the issue.}
-    \item[H 1.2]{When news coverage of an issue becomes more associated with positive (negative) considerations, consumers will develop a more positive (negative) opinion towards the issue.}
-    \item[H 1.3]{When news coverage of an issue becomes more associated with  positive (negative) considerations, consumers will develop a more positive (negative) opinion towards the issue \textit{only if they have low political knowledge}.}
-    \item[H 1.4a]{When news coverage of an issue becomes more associated with positive (negative) considerations, consumers will develop a more positive (negative) opinion towards the issue \textit{if they had no clear opinion about the issue before}.}
-    \item[H 1.4b]{The moderating effect of pre-existing opinions can be explained by \textit{political knowledge}.}
-    \item[H 1.4c]{The moderating effect of pre-existing opinions can be explained by \textit{partisanship}.}
-    \item[H 1.5]{When news coverage of an issue becomes more associated with positive (negative) considerations, those readers with conflicting attitudes towards the issue will stop reading the paper.}
+    \item{When news coverage of an issue becomes more associated with specific considerations, these considerations will be more common in media consumers' definition of the issue.}
+    \item{When news coverage of an issue becomes more associated with positive (negative) considerations, consumers will develop a more positive (negative) opinion towards the issue.}
+    \item{When news coverage of an issue becomes more associated with positive (negative) considerations, those readers with conflicting attitudes towards the issue will stop reading the paper.}
+    \item{The framing effect on attitudes (2) is only observable among respondents who...}
+    \begin{enumerate}
+        \item{\textit{have a limited media diet}.}
+        \item{\textit{have low political knowledge}.}
+        \item{\textit{had no clear opinion about the issue before}.}
+    \end{enumerate}
+    % \item{The moderating effect of pre-existing opinions can be explained by...}
+    % \begin{enumerate}
+    %     \item{\textit{political knowledge}}
+    %     \item{\textit{partisanship}}
+    % \end{enumerate}
 \end{enumerate}
 
-\subsubsection{Empirical strategy}
+\section{Case and empirical strategy}
 
 % \textbf{[HK: DROP EXOGENOUS LANGUAGE, DISTINGUISH FROM FOOS \& BISCHOF, THINK ABOUT DV REG CONTRIBUTION, SPILLOVER FROM BILD TO OTHER OUTLETS?]}
-
-% This study seeks to assess the causal effect of changing media frames on citizens' issue definitions and attitudes.
-
-Exploiting a rare shift in migration framing by the major German tabloid \textit{Bild}, I will assess the causal effect of a changing definition of migration in the media on opinions and issue definitions among citizens.
 
@@
 
-% \textbf{[treatment isnt endogenous and doesnt need to be]}
-
 I hope to exploit these communicative shifts in the paper's migration framing to assess the effects of media framing on readers' issue definitions, attitudes, and voting behaviour.
@@
 
-I will rely on several datasets to estimate the effect of this shift in migration framing:
+I will rely on two major datasets to estimate the effect of this shift in migration framing:
 \begin{itemize}
-    \item \textit{Bild} articles (print) for the respective period (2015-2018) to measure the changes in migration framing.
-    \item \textit{Bild online} articles would provide a comparison and credibility check to compare the framing under Reichelt and Koch, as he was in charge of the online news, while she was in charge of the print paper.
+    \item \textit{Bild online} articles for the respective period (2013-2018) to measure the changes in migration framing.
+    \item \textit{Bild} articles (print) would possibly provide a comparison and credibility check to compare the framing under Reichelt and Koch, as he was in charge of the online news, while she was in charge of the print paper\footnote{Not sure if this is entirely necessary, I haven't figured out where to get these yet - I thought maybe Lexis Nexis or the Bild Zeitung has an archive, I am grateful for suggestions though.
+The survey is asking for print and online news consumed, but i haven't looked into the data yet.}.
     \item Variables from the long-term online tracking survey of the German Longitudinal Election Study:
@@
         \item \textbf{Political Knowledge.} This independent variable allows to test whether susceptibility to framing is dependent on political knowledge.
+        \item \textbf{Media diet.} This independent variable indicates whether the respondent consumes additional news sources.
+Allows to test whether susceptibility to framing is dependent on having alternate news sources.
     \end{itemize}
@@
 
-While I will collect the \textit{Bild} articles myself using webscraping, the survey data is provided by the German Longitudinal Election Study (GLES).
+While I collected the \textit{Bild} articles myself using webscraping, the survey data is provided by the German Longitudinal Election Study (GLES).
 The long-term online tracking consists of quarterly surveys of a random sample of about 1,000 respondents beginning in 2009 and ending in 2017 (\cite{GLES2019LongTermTracking}).
@@
 Most importantly, the survey does not interview the same respondents again.
-This means that I won't be able to assess hypotheses 1.4 a-c and 1.5.
+This means that I won't be able to assess hypotheses 3 and 4c.
 To test these hypotheses, the GLES Panel survey might be used.
 This data only covers 2016-2020, which includes the last but likely weakest treatment (Reichelt replaced Koch; see figure \ref{fig:gles}).
-Additionally, the number of respondents in the longterm online tracking is rather small given that my group of interest is \textit{Bild} readers.
+Additionally, the number of respondents in the longterm online tracking is rather small given that my group of interest is \textit{Bild} readers and the hypothesised interaction effects.
 These should constitute 150-200 respondents per wave.
@@
 If the framing in \textit{Bild} diverges from a parallel trend with the framing of other newspapers, the treatment is viable.
-This will be measured by pre-selecting migration articles with supervised machine-learning classifiers, before using sentiment analysis to track the tone of migration coverage.
+I have not yet decided on how to measure framing here.
+The most straightforward approach would in my opinion be to pre-select migration content (in all newspapers) with a supervised machine-learning classifier.
+Then either identify pre-defined frames (e.g.
+humanitarian frame, crime, ...) using a dictionary approach, possibly with dictionary extension using word embeddings; or use factor analysis/structural topic modelling to identify frames inductively (\cite{Nicholls2020}).
+Either way, I would have to select relevant positive and negative frames to track across time, either a priori or as a selection from the topic model.
+If e.g.
+the change from Diekmann to Koch corresponded with a major shift in framing (e.g.
+lower emphasis of the humanitarian frame, more discussion of crime in relation to immigration/integration), relative to other newspapers, this would indicate a viable treatment.
 
@@
 
-Where $y$ is the dependent (migration association or attitude), $T$ indicates the survey took place after the treatment/shift in migration framing, and $B$ indicates whether the respondent is a \textit{Bild}-reader.
+Where $y$ is the dependent (migration association or attitude), $T$ indicates whether the interview took place after the treatment/shift in migration framing, and $B$ indicates whether the respondent is a \textit{Bild}-reader.
 This means that the average of the dependent variable among \textit{Bild}-readers following the treatment is compared to non-\textit{Bild}-readers, both before and after the treatment, and \textit{Bild}-readers before treatment.
@@
 Whether this can be measured is highly dependent on the number of responses discussing migration in the open answers to the most-important problem question.
-If possible, several surveys preceding and during the treatment (i.e.
-while the migration framing in \textit{Bild} differs from other newspapers) should be pooled to increase the number of respondents.
+If possible, several surveys preceding and following the treatment should be pooled to increase the number of respondents.
 
@@
 Building on this work, \citeauthor{Rodriguez2020} have developed \textit{embedding regression}, which allows to express changing meanings as a function of covariates (\citeyear{Rodriguez2020}).
-Using the DiD to estimate these changes in meaning, it will be possible to understand how \textit{Bild}-readers understanding of migration changed following the treatment, compared to changes in the control group.
+Using the DiD to estimate these changes in meaning, it will be possible to understand how \textit{Bild}-readers' understanding of migration changed following the treatment, compared to changes in the control group.
 
@@
 If the changes in the definition of migration indicated by the DiD are similar in the newspaper data and the survey responses, this constitutes strong evidence for a direct transmission of news frames into the issue definitions of consumers of these news.
+
+Lastly, another model with political knowledge and the diversity of the media diet as moderators and migration attitude as the dependent will be estimated to test hypotheses 4a and 4b.
 
@@
 
+\newpage
+
+\printbibliography
+
 \end{document}

### 2021-06-09 pres/Presentation_20210503.Rmd
Cleanup folder structure

---
title: "Hypodermic needle after all? Individual-level Moderators of Media Framing Effects"
subtitle: "Presentation at EPSIP Colloquium, HU Berlin"
author: "Nicolai Berk$^*$"
institute: "$^*$RTG Dynamics/Humboldt Universität zu Berlin"
date: "May 3rd, 2021"
output: 
  beamer_presentation:
    theme: "Frankfurt"
    # colortheme: "lily"
    # fonttheme: "professionalfonts"
    slide_level: 2
    toc: False
header-includes:
# - \usepackage{fontawesome}
# - \AtBeginSection{}
bibliography: PhD-Proposal.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Motivation

## Media effects - maximal or minimal? {.allowframebreaks}

\center

![](vis/volksempfanger.jpg){width=40%} ![](vis/ufo_scares.jpg){width=40%}

\flushleft

\framebreak

Maximal paradigm also follows from classic work

- attitude instability [@Converse1962; @Zaller1992]
- framing [@Nelson1997]
- agenda-setting [@McCombs1972]

\framebreak

\center

![](vis/mineff.png){width=30%}

\flushleft

Minimal effects assumption with increasing media diversity [@Bennett2008]:

- media environment more polarised and more diverse,
- viewers more likely to reject news conflicting with their views,
- viewers can opt for other sources.

$\rightarrow$ strong effects unlikely

\framebreak

Evidence seems to support both views:

### strong media effects on:
- voting behaviour [@Boomgaarden2009; @Devine2020; @Ladd2009a],
- issue agenda [@King2017],
- attitudes [@Nelson1997; @Foos2020]

### weak or no effects on:
- voting behaviour [@Gentzkow2011],
- issue agenda [@Lau2021],
- attitudes [@Guess2021].

# Moderators

## Towards a theory of conditioning factors

Recently more discussion of moderators

- Mostly based on expectations regarding source:
  + Discounting of biased news [@Chiang2011a]
  + Rejection of partisan takeovers [@Spirig2020]
- facing biased new media outlets doesn't seem to affect citizens [@Guess2021]

## Open questions:

- What about outlets currently consumed changing their commentary?
- What about individual-level factors?
  + political knowledge, opinion strength [@Zaller1992]?
  + media diet [@Bennett2008]?
  + partisan identification [@Taber2006]?
- Is attitude change a result of changing issue definitions [@Ajzen2000; @Nelson1997]?

# The case

- In fall of 2015, major German tabloid Bild started calling for support for incoming refugees.
- This was a major deviation from the papers' agitative history.

![](vis/BildFlüchtlingskinder.png)

![](vis/BildNot.png)

## 2016 onwards the framing changed

\center
![](vis/UebermedienBild2.png){height=50%}

## Logic of the paper

- I argue this represents a natural experiment to study migration framing,
- allowing to identify the *causal* impact of news framing on:
  + migration opinions, 
  + and issue definitions.
- especially interesting case:
  + instead of treatment with a new source [@Guess2021], cue-taking (from the newspaper) can be expected.
  + expectation of change in bias among readers unlikely [@Chiang2011a; @Spirig2020]

*$\rightarrow$ strong expectations for framing effect!*

# Data and research design

## The GLES offers a number of possible data sources:
- Longterm-tracking, 
  - N $\approx$ 1000, 
  - four times/year, 
  - 2009-17
- Panel, 
  - N $>$ 10,000, 
  - clustered around election

Both regularly contain questions on

- news consumption,
- migration/integration attitudes,
- open-ended MIP.

## Treatments and Field Dates {.allowframebreaks}

Journalists ascribe change to changing editors. This leaves us with a total of 4 possible treatments:

1. Summer of 2015
2. Diekmann replaced as editor-in-chief by Tanit Koch in 2016, 
3. Diekmann finally left Bild in February 2017,
4. Koch replaced by Julian Reichelt in January 2018.

Not entirely clear which treatment is relevant -> assess changing framing in the newspaper!

\framebreak

![](vis/gles_treatments.png)

## Treatment selection

1. Pre-select migration content with supervised classifier.

2. Several possible approaches for treatment identification:

  - inductive frame identification (FA/STM)
  - dictionary for frames (humanitarian/crime/...)
  - sentiment towards migration

3. Treatment identified where parallel paths diverge

## Modelling

Diff-in-Diff:

\center

$$ y = \beta_1 * T + \beta_2 * B + \beta_3 * T * B $$

- DVs: migration attitudes & issue definitions
- Additional interactions for individual-level moderators.

## Measuring issue definitions

### Embedding regression [@Rodriguez2020]

- applicable in low-N environments.
- pre-existing word embeddings to understand how different groups communicate about migration.
- assess associations with migration in the MIP answers.

## Fin

\center \Large Thank you for your attention!

# Appendix

## A preliminary effort at sentiment identification {.allowframebreaks}

- identify sentences mentioning terms from migration dictionary.
- estimate sentiment of these sentences with German BERT sentiment classifier [@Guhr2020].
- Trained to classify a variety of German text (wiki, reviews, tweets, ...) into positive, neutral, and negative content

![](vis/comparative_sentiment_migration.png)

\framebreak

However, unclear what this really measures:

![](vis/BERTProbs2.png){width=45%} ![](vis/BERTProbs3.png){width=45%}

![](vis/BERTProbs4.png){width=45%} ![](vis/BERTProbs5.png){width=45%}

\framebreak

Takeaways:

- wait for supervised coding.
- focus on specific frames.
- measure association.

# Resources

## Resources {.allowframebreaks}

### 2021-06-09 code/gles_explore.R

@@ -1,0 +1,356 @@
+# ______________________________________________
+# Effects of changing media frames - case of Bild
+# Goal: Data overview GLES
+# Procedure: load, explore
+# ______________________________________________
+# Date:  Wed Apr 07 16:32:03 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(here)
+library(data.table)
+library(haven)
+library(gridExtra)
+library(magrittr)
+
+#  Rolling cross section ####
+gles_rc <- read_dta(here('data/gles/RCS/ZA6834_v1-0-0.dta'))
+
+## BILD
+### Lesen Sie gelegentlich oder regelmäßig die BILD-Zeitung? (Falls ja, an wie vielen Tagen pro Woche lesen Sie politische Berichte?)
+gles_nna <- gles_rc[gles_rc$pre2401 > 0, ]
+table(gles_nna$pre2401)
+
+gles_nna$bild <- gles_nna$pre2401 < 7
+sum(gles_nna$bild == 1) # 2049 Bild readers total
+sum(gles_nna$bild == 1)/nrow(gles_nna) # ~10%
+
+### unique readers per wave: 627 - 715
+t1 <- table(gles_nna$bild, gles_nna$year)
+t1
+round(prop.table(t1, margin = 2), 2)
+t1 %>% tableGrob() %>% grid.arrange()
+
+
+## MIP open question: pre1001_org (not available, check .sav)
+
+## MIP open question: pre1001_org (.sav; not available - mail went out to GLES)
+# gles_rc <- read_sav('data/gles/ZA6834_v1-0-0.sav')
+
+## Integration attitude: 
+  # pre1401f (2013 pre: Einwanderer an dt. Kultur anpassen) 
+  # pos1001a_2 (2013 post: Einwanderer an dt. Kultur anpassen) 
+  # pos1001a_1 (2017: Einwanderer an dt. Kultur anpassen) 
+
+## Immigration attitude:
+  # Zuwanderung: ego position pre1302 (2017)
+  # Zuwanderung: ego position pos0901 (2017)
+
+## Wahlentscheidung: pos0303a, pos0303b, pos0304a, pos0304b
+
+
+rm(list = ls())
+
+
+
+
+
+# Panel ####
[…]

### 2021-09-03 paper/main.tex
Structure new draft

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[
backend=biber,
style=authoryear,
citestyle=authoryear
]{biblatex}
\renewcommand*{\bibfont}{\small}
\usepackage[normalem]{ulem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}

\pagestyle{fancy}
\fancyhf{}
\rhead{Can Meaning Travel?}
\lhead{Nicolai Berk}
\cfoot{\thepage}

\useunder{\uline}{\ul}{}

\addbibresource{PhD-Proposal.bib}

\usepackage{xcolor}

\title{Can Meaning Travel? The Causal Effect of Media Frames on Issue Definitions and Attitudes}
\author{Nicolai Berk\footnote{Doctoral Candidate, Dynamics Doctoral Program, Humboldt-Universität zu Berlin, \href{mailto:nicolai.berk@hu-berlin.de}{nicolai.berk@hu-berlin.de}}}
\date{May 2021}

\begin{document}

\maketitle

\begin{abstract}
    A large body of literature debates the existence and extent of effects of media framing on consumers' issue attitudes. At the same time, mechanisms of opinion formation have mainly been studied experimentally. Combining panel data from the German Longitudinal Election Study with fine-grained analyses of media framing, I address both debates with observational data. I provide strong evidence from 1,338 fixed-effect, difference-in-differences models suggesting the existence of sizeable media effects. Second, I show that such changes in consumers' issue attitudes correspond to changes in the issue framing of their preferred media outlet. Lastly, the study explores whether such changes in media framing affect consumers' issue definitions using state-of-the-art text analysis methods. The findings contribute to our understanding of opinion formation processes and the relevance of the news media in the 21st century.
\end{abstract}

\section{Introduction}

% starting point: historical discussion on minimal vs maximal media effects and the discussion on external validity
% agenda setting yes (cite), but what about framing? Debate goes on
% second: unclear mechanisms - look for lab evidence to cite on this

\section{Framing in the wild}

\subsection{General evidence of framing effects}

% argument 1: key issue is not the external validity of framing experiments, but the more likely to observe framing effects when consuming the SAME newspaper, which one trusts already - basically cue taking (Foos, Spirig, Ladd vs Gentzkow, Guess, resolved by Slothuus and Leeper)

\subsection{Mechanisms of framing}

% argument 2: opinion shifts come about through changing associations (framing/) -> value expectancy framework, but with a neurological basis

\subsection{Implications for the study of framing effects}

% Lesson: more observational data necessary, but we need to study cases where the slant of a newspaper that people already read changes, without obvious changes eg in ownership that made readers discount the slant
% people could a) not care, b) stop reading their newspaper, c) change their opinion

% changes in issue association should affect first people's issue definitions, which changes their opinion on the issue.

\section{Study design}

\subsection{Data and case description}

\subsection{Study design}

\subsubsection{Can framing effects among newspaper readers be observed?}

% 1.5k DiDs for all issue-paper-wave combinations

\subsubsection{Can these opinion shifts be explained by changing media frames?}

% look at migration, maybe a second issue: how strongly do DiD's correlate with changing topic prevalence?
% add right/wing slant as second dependent using AfD-classifier

\subsubsection{Have readers' issue definitions changed as a result of the changing media frames?}

% embedding regression: do shifts in migration definitions among the readers correspond to changes in the media definition?

\section{Results}

\subsection{DiD-assumption: Parallel trends}

% show graphs from issue with longest-running issues, add table with all graphs in appendix, show correlation of positions of different newspapers

% also think about excludability: how can you ensure that these shifts are a result of media framing (this might be answered in number two)

\subsection{Distribution of DiD-effect significance}

% show distribution of p-values vs theoretical distribution -> looks like there is systematic deviation

\subsection{Correlation of DiD with frame prevalence}

% show correlation of DiD with prevalence of media frames (STM)

\subsection{Shifts in issue definitions}

% show for one specific case that shift in media frame corresponded to

\section{Discussion}

\end{document}

### 2021-09-10 paper/main.tex

@@
 Combining panel data from the German Longitudinal Election Study with fine-grained analyses of media framing, I address both debates with observational data.
-I provide strong evidence from 1,338 fixed-effect, difference-in-differences models suggesting the existence of sizeable media effects.
-Second, I show that such changes in consumers' issue attitudes correspond to changes in the issue framing of their preferred media outlet.
+I provide strong evidence from 1,338 fixed-effect, difference-in-differences models suggesting the existence of media effects.
+Second, I show that such changes in consumers' issue attitudes do \textit{not} correspond to changes in the issue framing of their preferred media outlet.
+Instead, these changes could be explained by an ideological readership reacting differently to changes in the news agenda.
 Lastly, the study explores whether such changes in media framing affect consumers' issue definitions using state-of-the-art text analysis methods.
@@
 
-% starting point: historical discussion on minimal vs maximal media effects and the discussion on external validity
-% agenda setting yes (cite), but what about framing? Debate goes on
-% second: unclear mechanisms - look for lab evidence to cite on this
+\begin{itemize}
+  \item starting point: historical discussion on minimal vs maximal media effects and the discussion on external validity
+  \item agenda setting yes (cite), but what about framing? Debate goes on
+  \item second: unclear mechanisms - look for lab evidence to cite on this
+\end{itemize}
 
@@
 
-% argument 1: key issue is not the external validity of framing experiments, but the more likely to observe framing effects when consuming the SAME newspaper, which one trusts already - basically cue taking (Foos, Spirig, Ladd vs Gentzkow, Guess, resolved by Slothuus and Leeper)
+argument 1: key issue is not the external validity of framing experiments, but the more likely to observe framing effects when consuming the SAME newspaper, which one trusts already - basically cue taking (Foos, Spirig, Ladd vs Gentzkow, Guess, resolved by Slothuus and Leeper)
 
@@
 
-% argument 2: opinion shifts come about through changing associations (framing/) -> value expectancy framework, but with a neurological basis
+argument 2: opinion shifts come about through changing associations (framing/issue definition) $\rightarrow$ value expectancy framework, but with a neurological basis
 
 \subsection{Implications for the study of framing effects}
-
-% Lesson: more observational data necessary, but we need to study cases where the slant of a newspaper that people already read changes, without obvious changes eg in ownership that made readers discount the slant
-% people could a) not care, b) stop reading their newspaper, c) change their opinion
-
-% changes in issue association should affect first people's issue definitions, which changes their opinion on the issue.
+\begin{itemize}
+\item Lesson: more observational data necessary, but we need to study cases where the slant of a newspaper that people already read changes, without obvious changes eg in ownership that made readers discount the slant
+\item people could a) not care, b) stop reading their newspaper, c) change their opinion
+\item changes in issue association should affect first people's issue definitions, which changes their opinion on the issue.
+\end{itemize}
 
@@
 
+% plot with opinion development per paper for four / six issues
+
+% plot with descriptives and survey dates
+
 \subsection{Study design}
@@
 
-% 1.5k DiDs for all issue-paper-wave combinations
+1,336 DiDs for all issue-paper-wave combinations
 
@@
 
-% look at migration, maybe a second issue: how strongly do DiD's correlate with changing topic prevalence?
-% add right/wing slant as second dependent using AfD-classifier
+\begin{itemize}
+    \item look at migration, maybe a second issue: how strongly do DiD's correlate with changing topic prevalence?
+    \item look at how FE model DiD's change when controlling for newspaper attention/DiD
+    \item add right/wing slant as second dependent using AfD-classifier
+\end{itemize}
 
@@
 
-% embedding regression: do shifts in migration definitions among the readers correspond to changes in the media definition?
+embedding regression: do shifts in migration definitions among the readers correspond to changes in the media definition?
 
@@
 
+\newpage
+
+\section{Comments for Thomas}
+
+Das hier war grob die geplante Vorgehensweise.
+Ich denke gegeben der Findings nicht so sinnvoll mehr, aber man könnte meines Erachtens in zwei Richtungen gehen: a) Evidenz zeigen, dass opinion shifts als Reaktionen ideologischer Leserschaft gelesen werden können (Modell mit Interaktion Migration attention und newspaper), b) Leserschaft als dependent, um zu zeigen, ob Framing shifts Leserschaft abstossen.
+Hier könnte man auch überlegen, ob das mit dem Slant der Zeitung zusammenhängt.
+Ausserdem könnte es auch re validity noch sinnvoll sein, wenigstens agenda-setting effects zu zeigen.
+Fraglich ist, ob es noch sinnvoll ist, die (methodisch eigentlich am spannendsten \& theoretisch an innovativsten) issue definitions zu analysieren.
+
 \end{document}

### 2021-09-10 code/vis.R
update dv vis

@@ -98,7 +98,8 @@ for (issue in c('Immigration', 'Integration')){
   }
   
   
-  gles_p_long_paper %>% 
+  temp <- 
+    gles_p_long_paper %>% 
     filter(reader == T) %>% 
     group_by(wave, paper) %>% 
     filter(!is.na(dv)) %>% 
@@ -110,11 +111,15 @@ for (issue in c('Immigration', 'Integration')){
     mutate(
       dv_up = (dv + qt(1 - (0.05/2), respondents - 1)*dv_sd/respondents),
       dv_low = (dv - qt(1 - (0.05/2), respondents - 1)*dv_sd/respondents),
-    ) %>% 
-    ggplot(aes(x = date_clean)) +
+    )
+  
+  unique_waves <- paste(sort(unique(temp$wave)))
+  
+  ggplot(temp, aes(x = date_clean)) +
     geom_line(aes(y = dv, col = paper)) +
     geom_ribbon(aes(ymax = dv_up, ymin = dv_low, fill = paper), alpha = 0.5) +
-    ggtitle(glue("{issue} attitude among newspaper-readers"), "Data: GLES Panel, waves 1-13, a1 & a2")
+    ggtitle(glue("{issue} attitude among newspaper-readers"), 
+            glue("Data: GLES Panel, waves {unique_waves}"))
   
   ggsave(filename = here(glue('paper/vis/{issue}_papers.png')),
          width = 8, height = 6)

### 2021-09-10 paper/main.tex
Updates from Overleaf

@@
 % show graphs from issue with longest-running issues, add table with all graphs in appendix, show correlation of positions of different newspapers
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/Immigration_papers.png}
+    \caption{Opinions on migration across time (higher values indicate more restrictive attitudes).}
+    \label{fig:issues}
+\end{figure}
 
@@
 Das hier war grob die geplante Vorgehensweise.
-Ich denke gegeben der Findings nicht so sinnvoll mehr, aber man könnte meines Erachtens in zwei Richtungen gehen: a) Evidenz zeigen, dass opinion shifts als Reaktionen ideologischer Leserschaft gelesen werden können (Modell mit Interaktion Migration attention und newspaper), b) Leserschaft als dependent, um zu zeigen, ob Framing shifts Leserschaft abstossen.
+Ich denke gegeben der Findings nicht so sinnvoll mehr, aber man könnte meines Erachtens in zwei Richtungen gehen: a) Evidenz zeigen, dass opinion shifts als Reaktionen ideologischer Leserschaft gelesen werden können (Modell mit Interaktion Migration attention und newspaper), b) Leserschaft als dependent, um zu zeigen, dass Framing shifts Leserschaft abstossen.
 Hier könnte man auch überlegen, ob das mit dem Slant der Zeitung zusammenhängt.
@@
 Fraglich ist, ob es noch sinnvoll ist, die (methodisch eigentlich am spannendsten \& theoretisch an innovativsten) issue definitions zu analysieren.
+Eine recht einfache Erklärung für fehlende Effekte könnte auch fehlende Varianz, vor allem in den unabhängigen Variablen (Frames, Salienz) sein - dann  müsste ich mir komplett neue Daten suchen.
 

### 2021-09-25 paper/AppendixSTM.Rmd
Add STM appendix

---
title: "Explore topics in German migration coverage"
author: "Nicolai Berk"
date: "16 9 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(data.table)
library(here)
library(stm)
library(lubridate)
library(tidytext)
library(ggthemes)
library(scales)
library(knitr)
library(dplyr)
```

This document describes the topics in a 60-topic structural topic model (cite) of German news coverage of the migration issue in 2015-2019. It contains a plot showing the relative frequencies of topics, a table with most important words according to different statistics and a list of the ten most representative documents for each topic.

## Figure

```{r plot, fig.height=15}

# explore following Julia Silge's blogpost: https://juliasilge.com/blog/evaluating-stm/
load(here('data/topic_model_K60.Rdata'))
load(here('data/out_docs.Rdata'))

td_beta <- tidy(topic_model)
td_gamma <- tidy(topic_model, matrix = "gamma",
                 document_names = rownames(out$documents))

top_terms <- td_beta %>%
  arrange(beta) %>%
  group_by(topic) %>%
  top_n(7, beta) %>%
  arrange(-beta) %>%
  select(topic, term) %>%
  summarise(terms = list(term)) %>%
  mutate(terms = map(terms, paste, collapse = ", ")) %>%
  unnest(cols = c(terms))

gamma_terms <- td_gamma %>%
  group_by(topic) %>%
  summarise(gamma = mean(gamma)) %>%
  arrange(desc(gamma)) %>%
  left_join(top_terms, by = "topic") %>%
  mutate(topic = paste0("Topic ", topic),
         topic = reorder(topic, gamma))

gamma_terms %>%
  top_n(60, gamma) %>%
  ggplot(aes(topic, gamma, label = terms, fill = topic)) +
  geom_col(show.legend = FALSE) +
  geom_text(hjust = 0, nudge_y = 0.0005, size = 3) +
  coord_flip() +
  scale_y_continuous(expand = c(0,0),
                     limits = c(0, 0.09),
                     labels = percent_format()) +
  theme_tufte(ticks = FALSE) +
  theme(plot.title = element_text(size = 16),
        plot.subtitle = element_text(size = 13)) +
  labs(x = NULL, y = expression(gamma),
       title = "Migration topics by prevalence",
       subtitle = "With the top words that contribute to each topic")
```

## most representative words per topic

```{r wordlist}

sageLabels(topic_model)

```

## most representative articles per topic

```{r}
## associated documents of selected topics
for (i in 1:60){
  cat(paste(
    '\n\n------------------------------------------------------------\n\n',
    '5 most representative documents for topic ', i,
    '\n\n------------------------------------------------------------\n\n'))
  print(findThoughts(topic_model, texts = out$meta$text, n = 5, topics = i, )$docs[[1]])
  cat(paste('\n\n------------------------------------------------------------\n\n'))
}

```

<!-- ## look into selected topic prevalence across time & newspapers -->

<!-- ### crime 1: police & refugees -->
<!-- crime <- topic_model$theta[,25] -->
<!-- ggplot(mapping = aes(x=out$meta$date_new, y = crime))+ -->
<!--   geom_smooth() -->
<!-- ggplot(mapping = aes(x=out$meta$paper, y = log(crime)))+ -->
<!--   geom_boxplot() -->

<!-- ### mediterranean route & drowning of refugees -->
<!-- medit <- topic_model$theta[,49]  -->
<!-- ggplot(mapping = aes(x=out$meta$date_new, y = medit))+ -->
<!--   geom_smooth() -->

<!-- ### number of asylum seekers arriving -->
<!-- refnums <- topic_model$theta[,32]  -->
<!-- ggplot(mapping = aes(x=out$meta$date_new, y = refnums))+ -->
<!--   geom_smooth() -->

<!-- ### deportation (Afghanistan) -->
<!-- deport <- topic_model$theta[,44]  -->
<!-- ggplot(mapping = aes(x=out$meta$date_new, y = deport))+ -->
<!--   geom_smooth() -->

<!-- ### local refugee accommodation -->
<!-- accomm <- topic_model$theta[,58]  -->
<!-- ggplot(mapping = aes(x=out$meta$date_new, y = accomm))+ -->
<!--   geom_smooth() -->

<!-- ### greek internment camps -->
<!-- camps <- topic_model$theta[,27]  -->
<!-- ggplot(mapping = aes(x=out$meta$date_new, y = camps))+ -->
<!--   geom_smooth() -->

<!-- ### labour market integration -->
<!-- labmar <- topic_model$theta[,11]  -->
<!-- ggplot(mapping = aes(x=out$meta$date_new, y = labmar))+ -->
<!--   geom_smooth() -->

<!-- ### crime 2: capital crimes (rape, murder, cologne) -->
<!-- capcrime <- topic_model$theta[,48]  -->
<!-- ggplot(mapping = aes(x=out$meta$date_new, y = capcrime))+ -->
<!--   geom_smooth() -->
<!-- ggplot(mapping = aes(x=out$meta$paper, fill = out$meta$paper, y = log(capcrime)))+ -->
<!--   geom_violin() -->

<!-- ggplot(mapping = aes(x=out$meta$date_new, y = capcrime+crime))+ -->
<!--   geom_smooth() -->
<!-- ggplot(mapping = aes(x=out$meta$paper, fill = out$meta$paper, y = log(capcrime+crime)))+ -->
<!--   geom_violin() -->

<!-- ### generate output file with daily prevalence -->
<!-- prevalence <-  -->
<!--   data.frame( -->
<!--     crime, medit, deport, refnums, camps, labmar, capcrime -->
<!--   ) %>%  -->
<!--   cbind(paper = out$meta$paper) %>%  -->
<!--   cbind(date_new = out$meta$date_new) %>%  -->
<!--   group_by(paper, date_new) %>%  -->
<!--   summarise( -->
<!--     crime_m    = mean(crime), -->
<!--     medit_m    = mean(medit), -->
<!--     deport_m   = mean(deport), -->
<!--     refnums_m  = mean(refnums), -->
<!--     camps_m    = mean(camps), -->
<!--     labmar_m   = mean(labmar), -->
<!--     capcrime_m = mean(capcrime), -->
<!--     crime_s    = sum(crime), -->
<!--     medit_s    = sum(medit), -->
<!--     deport_s   = sum(deport), -->
<!--     refnums_s  = sum(refnums), -->
<!--     camps_s    = sum(camps), -->
<!--     labmar_s   = sum(labmar), -->
<!--     capcrime_s = sum(capcrime), -->
<!--     crime_sd   = sd(crime), -->
<!--     medit_sd   = sd(medit), -->
<!--     deport_sd  = sd(deport), -->
<!--     refnums_sd = sd(refnums), -->
<!--     camps_sd   = sd(camps), -->
<!--     labmar_sd  = sd(labmar), -->
<!--     capcrime_sd = sd(capcrime) -->
<!--     ) -->

<!-- save(prevalence, file = here('data/daily_mig_topics.Rdata')) -->

<!-- # save meta with topic attention -->
<!-- topic_attention <-  -->
<!--   data.frame( -->
<!--     crime, medit, deport, refnums, camps, labmar, capcrime -->
<!--     ) -->

<!-- output <- cbind(out$meta, topic_attention) -->
<!-- save(output, file = here('data/mig_articles_topics.Rdata')) -->

### 2021-09-25 paper/main.tex

@@
 % show distribution of p-values vs theoretical distribution -> looks like there is systematic deviation
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps.png}
+    \caption{Empirical and theoretical p-values of 1,363 DiD-models.}
+    \label{fig:p_values}
+\end{figure}
 
@@
 
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/frames_papers_wtd.png}
+    \caption{Prevalence of different migration frames across newspapers. Gray vertical lines indicate survey field dates.}
+    \label{fig:frames}
+\end{figure}
+
 % show correlation of DiD with prevalence of media frames (STM)
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/effectplot_noimp.png}
+    \caption{Correlation of opinion shifts (DiDs) with media attention or shifts in attention (DiD's) for different specifications.
+Note that immigration and integration are inversely coded.
+Higher values indicate more restrictive attitudes on immigration, but more liberal attitudes on integration.
+Signs indicate the hypothesized effect of the frame on integration.}
+    \label{fig:did_corr}
+\end{figure}
 

### 2021-09-25 paper/main.tex
Updates from Overleaf

@@
 \author{Nicolai Berk\footnote{Doctoral Candidate, Dynamics Doctoral Program, Humboldt-Universität zu Berlin, \href{mailto:nicolai.berk@hu-berlin.de}{nicolai.berk@hu-berlin.de}}}
-\date{May 2021}
+\date{September 2021}
 
@@
 Combining panel data from the German Longitudinal Election Study with fine-grained analyses of media framing, I address both debates with observational data.
-I provide strong evidence from 1,338 fixed-effect, difference-in-differences models suggesting the existence of media effects.
-Second, I show that such changes in consumers' issue attitudes do \textit{not} correspond to changes in the issue framing of their preferred media outlet.
+I provide evidence from 1,056 fixed-effect, difference-in-differences models suggesting systematic differences in newspaper readers' opinion shifts.
+Second, I show that such changes in consumers' attitudes do \textit{not} correspond to changes in the issue framing of the consumed media outlet.
 Instead, these changes could be explained by an ideological readership reacting differently to changes in the news agenda.
@@
 
-argument 1: key issue is not the external validity of framing experiments, but the more likely to observe framing effects when consuming the SAME newspaper, which one trusts already - basically cue taking (Foos, Spirig, Ladd vs Gentzkow, Guess, resolved by Slothuus and Leeper)
+argument 1: key issue is not the external validity of framing experiments, but more likely to observe framing effects when consuming the SAME newspaper, which one trusts already - basically cue taking (Foos, Spirig, Ladd vs Gentzkow, Guess, resolved by Slothuus and Leeper)
 
@@
 \subsection{Implications for the study of framing effects}
+
 \begin{itemize}
 \item Lesson: more observational data necessary, but we need to study cases where the slant of a newspaper that people already read changes, without obvious changes eg in ownership that made readers discount the slant
-\item people could a) not care, b) stop reading their newspaper, c) change their opinion
-\item changes in issue association should affect first people's issue definitions, which changes their opinion on the issue.
+\item people could a) not react, b) stop reading their newspaper, c) change their opinion
+\item changes in issue association (in the news) should affect people's issue definitions, which changes their opinion on the issue.
 \end{itemize}
@@
 
+\subsubsection{Public opinion data}
+
 % plot with opinion development per paper for four / six issues
 
-% plot with descriptives and survey dates
-
-\subsection{Study design}
-
-\subsubsection{Can framing effects among newspaper readers be observed?}
-
-1,336 DiDs for all issue-paper-wave combinations
-
-\subsubsection{Can these opinion shifts be explained by changing media frames?}
-
 \begin{itemize}
-    \item look at migration, maybe a second issue: how strongly do DiD's correlate with changing topic prevalence?
-    \item look at how FE model DiD's change when controlling for newspaper attention/DiD
-    \item add right/wing slant as second dependent using AfD-classifier
+    \item GLES Panel 2016-2020
+    \item about 10,000 - 15,000 respondents per wave
+    \item data on issue attitudes, importance, and news consumption
 \end{itemize}
 
-\subsubsection{Have readers' issue definitions changed as a result of the changing media frames?}
-
-embedding regression: do shifts in migration definitions among the readers correspond to changes in the media definition?
-
-\section{Results}
-
-\subsection{DiD-assumption: Parallel trends}
-
-% show graphs from issue with longest-running issues, add table with all graphs in appendix, show correlation of positions of different newspapers
-\begin{figure}[!h]
+\begin{figure}[!ht]
     \centering
@@
 
+\subsubsection{Data on news framing}
+% plot with frames and survey dates
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/frames_papers_wtd_focus.png}
+    \caption{Prevalence of different migration frames across newspapers. Gray vertical lines indicate survey field dates.}
+    \label{fig:frames}
+\end{figure}
+
+\begin{itemize}
+    \item Collected around 2.5 million newspaper articles from six major newspapers
+    \item Extracted and annotated a stratified sample of articles using a migration dictionary
+    \item Trained a migration classifier (BERT transformer) based on these annotations
+    \item estimated migration frames using STM on migration articles only (N = 90,000): 
+    \item retained most common and relevant frames that allow to form clear hypotheses about attitude formation:
+    \begin{itemize}
+        \item Internment camps, 
+        \item capital crime (sexual assault/rape/murder) committed by refugees, 
+        \item general petty crime by refugees and issues in refugee living quarters in Germany,
+        \item deportations,
+        \item labour market needs for and integration of refugees
+        \item drownings in the mediterranean
+        \item refugee numbers
+    \end{itemize}
+\end{itemize}
+
+\subsection{Study design}
+
+\subsubsection{Can framing effects among newspaper readers be observed?}
+
+To get a glimpse of whether opinion shifts might be influenced by news consumption, I estimate difference-in-differences models (DiDs) for all available combinations of news outlets (incl.
+TV news), issues, and survey waves.
+The main term of interest is the interaction of a binary indicator of readership of a certain outlet with a binary indicator which equals 1 for the current wave and 0 for the preceding wave.
+That means I measure the shift in opinions of the readership of a certain outlet, controlling for the changes taking place among consumers of other news.
+
+\subsubsection{Can these opinion shifts be explained by changing media frames?}
+
+\begin{itemize}
+    \item look at migration, maybe a second issue: how strongly do DiD's correlate with changing frame prevalence/DiD of frame attention?
+    \item look at how FE model DiD's change when controlling for newspaper attention/DiD
+    \item add right-wing slant as second dependent using AfD-classifier
+\end{itemize}
+
+\subsubsection{Have readers' issue definitions changed as a result of the changing media frames?}
+
+The final analysis in this paper aims to show that changes in readers' migration definitions correspond to changes in news coverage.
+This can be achieved by applying embedding regression to open survey responses, which shows differing word associations for subgroups of documents.
+This would show if respondents reading a certain newspaper define migration more in line with e.g.
+the humanitarian situation in refugee camps, compared to a preceding wave and controlling for shifts in other newspapers.
+
+\section{Results}
+
+\subsection{DiD-assumption: Parallel trends}
+
+% refer to graph on mig issue
+The parallel trends assumption is met, as can be seen in figure \ref{fig:issues}. A plot of all other issues showing similar co-variation will be added to the appendix at a later point in time.
+
 % also think about excludability: how can you ensure that these shifts are a result of media framing (this might be answered in number two)
@@
 \subsection{Distribution of DiD-effect significance}
+
+The upper panel of figure \ref{fig:p_values} shows the distribution of p-values for the DiD-term from 1,056 fixed-effect models with GLES Panel data.
+The distribution shows a considerable deviation from the expected uniform distribution (visible in the lower panel) were there no explaining variation in the DiD-term beyond the uniform effects of wave and paper readership.
+This means, more often than random, the opinions of consumers of certain news deviate from the opinions of other citizens.
 
@@
 \subsection{Correlation of DiD with frame prevalence}
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=\textwidth]{paper/vis/frames_papers_wtd.png}
-    \caption{Prevalence of different migration frames across newspapers. Gray vertical lines indicate survey field dates.}
-    \label{fig:frames}
-\end{figure}
-
 % show correlation of DiD with prevalence of media frames (STM)
@@
     \includegraphics[width=\textwidth]{paper/vis/effectplot_noimp.png}
-    \caption{Correlation of opinion shifts (DiDs) with media attention or shifts in attention (DiD's) for different specifications.
+    \caption{Correlation of opinion shifts (DiDs) with media attention or shifts in attention (DiD's) for different specifications.}
+    \label{fig:did_corr}
+\end{figure}
+
+Figure \ref{fig:did_corr} shows the core analysis to estimate the effect of media attention on reader opinion.
+Each dot in this graph represents the t-value of a model explaining aggregate opinion shifts (DiDs, blue dots) with aggregate media attention or shifts in attention (DiDs) for a specific frame and a specific model specification.
+These aggregate parameters come from models explaining immigration opinion/media attention with news outlet-wave interactions, as in the models providing the p-values for figure \ref{fig:p_values}.
+If opinion shifts among newpapers' readers - relative to other readers - can be explained by shifts in newspapers' issue framing, these two variables should be highly correlated.
+The displayed estimates are hence obtained by regressing the resulting DiD-estimates for issue attitudes on the DiD-estimates for media attention.
+
+For example, the left graph in the top panel row shows the effect of media attention on immigration attitudes for two different independent variables (DiD \textit{coef}ficients estimating the increase in news coverage in the consumed outlet relative to all others, and the general \textit{attention} in the preceding period) and four different time lags (see horizontal lines in descending order: 1 week, 1 month, 6 months, and the full period until last survey wave [g]).
 Note that immigration and integration are inversely coded.
 Higher values indicate more restrictive attitudes on immigration, but more liberal attitudes on integration.
-Signs indicate the hypothesized effect of the frame on integration.}
-    \label{fig:did_corr}
-\end{figure}
++/- signs corresponding to the frames (visible on the right-hand side) indicate the hypothesized effect of the frame on integration.
+
+The analysis shows that, generally, no clear pattern can be observed in the correlation of these effects.
+Independent of the choice of the dependent variable, specification of the independent variable (DiD/attention and differing periods of news coverage), and across all migration frames, t-values scatter around 0 (see also \ref{fig:t_values} in the appendix).
+This constitutes strong evidence against an effect of news framing on opinion formation.
+Even changes in issue salience in a given newspaper do not correspond to changes in readers' issue attitudes (see bottom two panels).
+
+A second analysis will estimate the decrease in explanatory value of the wave-news consumption interaction/DiD when media attention is added as a control.
 
@@
 
-\newpage
+\section{Appendix}
 
-\section{Comments for Thomas}
-
-Das hier war grob die geplante Vorgehensweise.
-Ich denke gegeben der Findings nicht so sinnvoll mehr, aber man könnte meines Erachtens in zwei Richtungen gehen: a) Evidenz zeigen, dass opinion shifts als Reaktionen ideologischer Leserschaft gelesen werden können (Modell mit Interaktion Migration attention und newspaper), b) Leserschaft als dependent, um zu zeigen, dass Framing shifts Leserschaft abstossen.
-Hier könnte man auch überlegen, ob das mit dem Slant der Zeitung zusammenhängt.
-Ausserdem könnte es auch re validity noch sinnvoll sein, wenigstens agenda-setting effects zu zeigen.
-Fraglich ist, ob es noch sinnvoll ist, die (methodisch eigentlich am spannendsten \& theoretisch an innovativsten) issue definitions zu analysieren.
-Eine recht einfache Erklärung für fehlende Effekte könnte auch fehlende Varianz, vor allem in den unabhängigen Variablen (Frames, Salienz) sein - dann  müsste ich mir komplett neue Daten suchen.
+\begin{figure}
+    \centering
+    \includegraphics[width = \textwidth]{paper/vis/t_values_noimp.png}
+    \caption{Caption}
+    \label{fig:t_values}
+\end{figure}
 

### 2021-09-25 code/05_estimation.R
Add table ind. level regression

@@ -18,6 +18,7 @@ library(here)
 library(lubridate)
 library(glue)
 library(gridExtra)
+library(stargazer)
   
 # 1. load data ####
 load(here("data/coefs_media.Rdata"))
@@ -393,10 +394,13 @@ imm_mod_unw_all_nosal <-
        labmar_tot_7d_unw + 
        deport_tot_7d_unw )
 
-summary(imm_mod_unw_all_nosal) # all but crime significant, refnums and deport negative
+mod_tbl <- summary(imm_mod_unw_all_nosal) # all but crime significant, refnums and deport negative
+
 
 longnames <- c('(Intercept)', 'Lagged DV', 'Petty Crime', 'Capital Crime', 'Refugee Numbers', 'Camps', 'Mediterranean Rescue', 'Labour Market', 'Deportations')
-arm::coefplot(imm_mod_unw_all_nosal, longnames)
+arm::coefplot(imm_mod_unw_all_nosal, longnames) %>% 
+  ggsave(filename = here('paper/vis/individual_effects_immigration.png'),
+                         width = 8, height = 6)
 
 
 
@@ -415,6 +419,11 @@ int_mod_unw_all_nosal <-
        deport_tot_7d_unw )
 
 summary(int_mod_unw_all_nosal) # capcrime negative (expected), deport positive (also expected), but surprisingly labmar no effect
+
+stargazer(imm_mod_unw_all_nosal, 
+          int_mod_unw_all_nosal,
+          title = 'Individual-level Model', 
+          out = here('paper/imm_unw.tex'))
 
 arm::coefplot(int_mod_unw_all_nosal)
 

### 2021-09-28 code/05_estimation.R
Add party preference and ideology as moderators, cleanup estimation

@@ -19,6 +19,8 @@ library(lubridate)
 library(glue)
 library(gridExtra)
 library(stargazer)
+library(interplot)
+library(sjPlot)
   
 # 1. load data ####
 load(here("data/coefs_media.Rdata"))
@@ -167,13 +169,14 @@ gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv'))
 ## generate lagged dependent
 gles_p_long <- 
   gles_p_long %>% 
-  select(lfdn, wave, date_clean, `1130_clean`, `1210_clean`, contains("1661")) %>% 
   filter(!is.na(date_clean)) %>% 
   group_by(lfdn) %>% 
   dplyr::arrange(date_clean, .by_group = T) %>% 
   mutate(
     `1130_lag` = dplyr::lag(`1130_clean`),
     `1210_lag` = dplyr::lag(`1210_clean`),
+    `1140_lag` = dplyr::lag(`1140_clean`),
+    `1220_lag` = dplyr::lag(`1220_clean`),
     date_str = as.character(date_clean)
   )
 
@@ -403,7 +406,7 @@ arm::coefplot(imm_mod_unw_all_nosal, longnames) %>%
                          width = 8, height = 6)
 
 
-
+# integration
 int_mod_unw_all_nosal <- 
   merged_data %>% 
   lm(data = .,
@@ -425,7 +428,9 @@ stargazer(imm_mod_unw_all_nosal,
           title = 'Individual-level Model', 
           out = here('paper/imm_unw.tex'))
 
-arm::coefplot(int_mod_unw_all_nosal)
+arm::coefplot(int_mod_unw_all_nosal) %>% 
+  ggsave(filename = here('paper/vis/individual_effects_immigration.png'),
+         width = 8, height = 6)
 
 
 ## holds controlling for salience:
@@ -464,6 +469,7 @@ int_mod_unw_all_sal <-
        deport_tot_7d_unw )
 
 summary(int_mod_unw_all_sal) # capcrime negative (expected), labmar positive (unclear)
+arm::coefplot(int_mod_unw_all_sal)
 
 
 ## interact salience with share
@@ -535,3 +541,276 @@ int_mod_wtd_all <-
      data = merged_data)
 
 summary(int_mod_wtd_all) # no effects
+
+
+
+
+## 3.5 explore individual-level moderators ####
+
+
[…]

### 2021-09-28 code/05a_main_models.R

@@ -1,0 +1,382 @@
+# ______________________________________________
+# Effect of framing on issue attitudes
+# Goal: Estimate effects
+# Procedure: load, estimate
+# ______________________________________________
+# Date:  Thu Sep 09 17:24:28 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# 0. setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(here)
+library(lubridate)
+library(glue)
+library(gridExtra)
+library(stargazer)
+library(sjPlot)
+
+# 1. load data ####
+load(here("data/coefs_media.Rdata"))
+framing_dids <- 
+  framing_dids %>% 
+  filter(!is.na(p))
+
+attitude_dids <- read.csv(here('data/coeftable_gles_noimp.csv'))
+
+attitude_dids$paper_name <- ''
+attitude_dids$paper_name[attitude_dids$paper == 'a'] <- 'bild'
+attitude_dids$paper_name[attitude_dids$paper == 'b'] <- 'falg'
+attitude_dids$paper_name[attitude_dids$paper == 'c'] <- 'faz'
+attitude_dids$paper_name[attitude_dids$paper == 'd'] <- 'sz'
+attitude_dids$paper_name[attitude_dids$paper == 'e'] <- 'taz'
+attitude_dids$paper_name[attitude_dids$paper == 'f'] <- 'welt'
+
+
+
+# 2. estimation and vis ####
+
+
+## 2.1 framing ####
+
+## select relevant issues (immigration & integration)
+imm_dids <- 
+  attitude_dids %>% 
+  filter(issue == "1130")
+
+int_dids <- 
+  attitude_dids %>% 
+  filter(issue == "1210")
+
+## pivot frametable wide to get 1 var/frame
+framing_dids <- 
+  framing_dids %>% 
+  select(-change) %>% 
+  pivot_wider(id_cols = c(paper, pre_wave, dv_lag), names_from = 'frame', values_from = 'coef')
+
+
+## correlate with frames
+efftable <- data.frame()
+for (issue in c("immigration", "integration")){
+  for (lag in c("g", "1d", "1w", "1m", "6m")){
+    for (respons in unique(attitude_dids$respondents)){
+      
+      if (issue == "immigration"){
+        dv_set <- 
[…]

### 2021-09-28 code/06_vis.R
Improve vis

@@ -119,6 +119,7 @@ for (issue in c('Immigration', 'Integration')){
     ggplot(temp, aes(x = date_clean)) +
     geom_line(aes(y = dv, col = paper)) +
     geom_ribbon(aes(ymax = dv_up, ymin = dv_low, fill = paper), alpha = 0.5) +
+    xlab('') + ylab('')+
     ggtitle(glue("{issue} attitude among newspaper-readers"), 
             glue("Data: GLES Panel; waves {unique_waves}"))
   
@@ -127,7 +128,7 @@ for (issue in c('Immigration', 'Integration')){
 
 grid.arrange(plots[['Immigration']], plots[['Integration']]) %>% 
   ggsave(filename = here(glue('paper/vis/issues_readers.png')),
-         width = 10, height = 10)
+         width = 8, height = 8)
 
 ## 2.2 vis independents ####
 load(here('data/efftable_noimp.Rdata'))
@@ -167,7 +168,7 @@ salience_sum %>%
   geom_line() +
   geom_vline(xintercept = survey_dates$date, col = 'darkgray') +
   ggtitle('Migration salience in different newspapers', 'Gray lines indicate survey waves')
-ggsave(here('paper/vis/salience_papers.png'), width = 10, height = 6)
+ggsave(here('paper/vis/salience_papers.png'), width = 8, height = 5)
 
 sal_2017 <- 
   salience_sum %>% 
@@ -177,7 +178,8 @@ sal_2017 <-
   geom_line() +
   geom_vline(xintercept = survey_dates$date, col = 'darkgray') +
   ggtitle('Migration salience in different newspapers', 'Gray lines indicate survey waves')
-ggsave(sal_2017, filename = here('paper/vis/salience_papers_focus.png'), width = 10, height = 6)
+ggsave(sal_2017, filename = here('paper/vis/salience_papers_focus.png'), 
+       width = 8, height = 5)
 
 
 ## frames over time
@@ -220,10 +222,10 @@ framing_sum %>%
   ggplot(aes(x = date, y = attention, col = frame)) +
   geom_line() +
   geom_rug(data = survey_dates, aes(x = date),sides = 't', inherit.aes = F) +
-  facet_grid(frame~paper, scales = 'free') +
+  facet_grid(frame~paper, scales = 'free', ) +
   ggtitle('Migration frames in different newspapers 2017', 'Black ticks indicate survey waves') +
[…]

### 2021-09-28 paper/main.tex

@@
 \fancyhf{}
-\rhead{Can Meaning Travel?}
+\rhead{The Causal Effect of Media Frames}
 \lhead{Nicolai Berk}
@@
 
-\title{Can Meaning Travel? The Causal Effect of Media Frames on Issue Definitions and Attitudes}
+\title{The Causal Effect of Media Frames on Issue Attitudes}
 \author{Nicolai Berk\footnote{Doctoral Candidate, Dynamics Doctoral Program, Humboldt-Universität zu Berlin, \href{mailto:nicolai.berk@hu-berlin.de}{nicolai.berk@hu-berlin.de}}}
@@
     A large body of literature debates the existence and extent of effects of media framing on consumers' issue attitudes.
-At the same time, mechanisms of opinion formation have mainly been studied experimentally.
-Combining panel data from the German Longitudinal Election Study with fine-grained analyses of media framing, I address both debates with observational data.
-I provide evidence from 1,056 fixed-effect, difference-in-differences models suggesting systematic differences in newspaper readers' opinion shifts.
-Second, I show that such changes in consumers' attitudes do \textit{not} correspond to changes in the issue framing of the consumed media outlet.
-Instead, these changes could be explained by an ideological readership reacting differently to changes in the news agenda.
-Lastly, the study explores whether such changes in media framing affect consumers' issue definitions using state-of-the-art text analysis methods.
+Combining panel data from the German Longitudinal Election Study with a fine-grained analyses of media framing, I address this debate with observational data, providing evidence from 1,752 fixed-effect, difference-in-differences models suggesting systematic differences in newspaper readers' opinion shifts.
+Second, I show that such changes in consumers' attitudes towards immigration surrounding the German national election 2017 did \textit{not} correspond to changes in the migration framing of consumed media outlets.
 The findings contribute to our understanding of opinion formation processes and the relevance of the news media in the 21st century.
@@
 
-\begin{itemize}
-  \item starting point: historical discussion on minimal vs maximal media effects and the discussion on external validity
-  \item agenda setting yes (cite), but what about framing? Debate goes on
-  \item second: unclear mechanisms - look for lab evidence to cite on this
-\end{itemize}
+How does news media content affect citizens' issue attitudes?
+Research on political behaviour has discussed this question for nearly a century.
+Classic theories of agenda setting hold that the attention devoted to issues in the news media will guide citizens to consider these issues important (\cite{McCombs1972}).
+Similarly, the literature on framing expects that the presentation of issues in the news media will affect recipients' opinions about these issues (\cite{Nelson1997}).
+Both theories suggest that media coverage strongly affects citizens' understanding of and opinions about politics.
+
+Yet, a popular critique of these theories maintains that strong news effects are unlikely in the modern media environment, where consumers self-select into news sources of their liking.
+As a result, "most media users will rarely find themselves in the path of attitude-discrepant information".
+Even if consumers had to face such discrepant information, this should reinforce their existing views rather than persuade as they are used to a partisan media diet (\cite[724f]{Bennett2008}).
+Similarly, agenda setting effects are unlikely as a result of selective exposure (\cite{Lau2021}).
+
+This conflicting evidence begs the question: when can we expect media framing effects?
+Some authors have argued that a lack of media effects can be explained by readers who discount a publications' bias.
+For example, when a left-wing newspaper endorses a left-wing candidate, this should have no effect on citizens' assessment of the candidate, as the endorsement was to be expected (\cite{Chiang2011a}, see also \cite{Spirig2020}).
+Additionally, citizens might take cues from their preferred publication because they developed trust in its coverage over time.
+
+The present study contributes to this debate in two ways.
+First, instead of taking media slant as a given (\cite{Foos2020, Guess2021}), I measure the prevalence of different frames directly and assess whether their presence in the media across time affected readers' issue attitudes.
+Second, I use the variation in framing \textit{within} a given newspaper across time as the main independent variable.
+Many other studies explored effects of changes in newspaper consumption (\cite{Foos2020, Gentzkow2011}) or randomly assigned participants to consume certain news media rather than others (\cite{Guess2021}).
+However, readers usually do not change readership, nor are all newspapers equally credible to them.
+If trust in a given news source matters, or if readers' discount publications' bias, such designs are unlikely to measure how news consumption affects consumers' opinions.
+This paper hence assesses how the changing framing of a salient issue within an already consumed paper changes citizens' attitudes.
 
@@
 
-argument 1: key issue is not the external validity of framing experiments, but more likely to observe framing effects when consuming the SAME newspaper, which one trusts already - basically cue taking (Foos, Spirig, Ladd vs Gentzkow, Guess, resolved by Slothuus and Leeper)
+A large amount of evidence underlines the importance of newspaper coverage for political opinion formation.
+Observational evidence shows that newspaper exposure (\cite{Foos2020, Spirig2020}), endorsements of specific candidates (\cite{Ladd2009a, Chiang2011a}), coverage of specific topics (\cite{King2017}), reports on political parties (\cite{Boomgaarden2009, Devine2020}), internet access (\cite{Schaub2020}), and changes in television news content (\cite{Durante2012}) have affected which issues citizens care about, their opinion about these issues, and their voting behaviour.
+An even larger body of experimental work reports strong effects of issue framing on participants' issue attitudes (see \cite{Busby2019} for a recent overview).
 
-\subsection{Mechanisms of framing}
+This "maximal effects" view is contrasted by a body of evidence indicating weak to absent media effects as well.
+\citeauthor{Gentzkow2011} show that even historically, the entry and exit of newspapers in the US does affect turnout, but that the newspapers' slant does not affect either party's vote share.
+They conclude that "the persuasive effect of partisan newspapers is limited" (\citeyear[3011]{Gentzkow2011}).
+Recently, \citeauthor{Guess2021} incentivised participants of an online-panel to visit left- or right-leaning news websites, with no effect on opinions (\citeyear{Guess2021}).
+An experiment by \citeauthor{Lau2021} indicates that increasing the likelihood of encountering information about a fictitious candidate's stance on a given issue does not increase the importance of that issue in reaching a voting decision, directly contradicting theories of agenda setting.
+This lack of evidence echos a general critique of the external validity of framing experiments and other experimental evidence about opinion formation (\cite{Barabas2010, Busby2019, Leeper2020}).
 
-argument 2: opinion shifts come about through changing associations (framing/issue definition) $\rightarrow$ value expectancy framework, but with a neurological basis
+What might explain these different findings?
+Scope conditions for media effects seem to be surprisingly understudied given the contradicting body of evidence.
+\citeauthor{Chiang2011a} argue that endorsements from newspapers with ideological leanings neutral or opposite to the endorsed party/candidate should have stronger effects on voting behaviour, as voters discount the general bias of a newspaper (\citeyear{Chiang2011a}).
+\citeauthor{Spirig2020} shows that the takeover of a Swiss regional newspaper through a leading politician of the far-right and the subsequent change in its political slant had no effect on citizens' voting behaviour and suggests that this is a result of voters discounting the new owner's political slant and stopping to read the newspaper.
 
-\subsection{Implications for the study of framing effects}
+If citizens discount the content of newspapers, they should not react to news content which is randomly assigned to them.
+Instead, a most likely case for effects of news exposure would have to assess changing content \textit{within} the same newspapers and its effect on consumers' issue attitudes.
+This is precisely what this study aims to do.
 
-\begin{itemize}
-\item Lesson: more observational data necessary, but we need to study cases where the slant of a newspaper that people already read changes, without obvious changes eg in ownership that made readers discount the slant
-\item people could a) not react, b) stop reading their newspaper, c) change their opinion
-\item changes in issue association (in the news) should affect people's issue definitions, which changes their opinion on the issue.
-\end{itemize}
+\subsection{Agenda Setting}
+
+\textbf{[Now that there seem to be no framing effects, I am considering to make this a broader study of media effects and include agenda setting.
+But I guess this might be hard to finish until the weekend, so I should probably drop it for now.
+Might still be relevant for future direction of the paper]}\medskip
+
+[Insert discussion of McCombs \& Shaw, as well as recent studies on agenda setting through the media, might also contrast 'latent salience model' (similar to Gamson \& Modigliani) and 'direct agenda setting']
+
+\medskip
+
+\textbf{H1a (direct agenda setting):} The more an issue is emphasised in a given newspaper, the more important this issue is considered by readers of this newspaper, relative to other newspapers.
+
+\textbf{H1b (latent salience model):} Increased issue attention in the news across time corresponds to increased importance among all readers, but higher attention in one newspaper compared to others does not increase the perceived importance among its readers relative to those of other newspapers (all move at the same time).
+
+\subsection{Mechanisms of Framing}
+
+While news slant is a very general concept, and sometimes operationalised as similarity to specific parties' communication (\cite{Gentzkow2010}) or issue positions/tonality (\cite{Spirig2020}), framing theory provides a specific expectation about which treatment should affect which issue attitudes how.
+As \citeauthor{Nelson1997} write: "framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy" (\citeyear[567]{Nelson1997}).
+A "frame" is then the operating unit of this process, defining the issue at hand in a specific way.
+Different forms of frames have been conceptualised.
+When I talk about 'frames' here, I refer to \textit{emphasis frames}.
+These frames emphasise certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame (\cite[153f]{Leeper2020}).
+For example, issues of increasing welfare contributions might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes.
+Individuals' support of a statement will differ dependent on the frame presented (\cite{sniderman2004structure}).
+
+While this broad definition gives a first idea of what framing is about, the concept of emphasis framing has been criticised for being too broad and imprecise to contribute anything meaningful to the field (\cite{Scheufele2012}).
+To address this shortcoming, I follow the framing literature building on the \textit{value-expectancy model} (\cite{Ajzen2000, Nelson1997}).
+This model suggests that an attitude on a given issue is a function of two things: considerations and their respective weights.
+The evaluation of the issue is subdivided into a number of considerations (to which political scientists might refer as "valence issues"), that will be easier to evaluate.
+For example, to decide whether a lockdown is necessary to battle the spread of Covid-19 in one's country, a person might consider the detrimental short-term effect on businesses and individuals' mental health (negative considerations), as well as the cost of overburdened hospitals and additional deaths (positive considerations, at least with respect to the evaluation of a lockdown).
+Individuals weigh each of these considerations to form an overall opinion on the subject.
+
+Figure \ref{fig:cogStor} visualises this logic.
+A given issue is associated with an attitude or evaluation $y$.
+The issue is related to a number of different considerations, each of which carries an associated evaluation $x_i$, e.g.
+that the prevention of overcrowded hospitals is a good thing.
+Each of these considerations is more or less associated with the issue.
+Based on the strength of this association $w_i$, a given consideration's evaluation is more or less reflected in the issue evaluation $y$, which is equal to the weighted sum of considerations.
+Emphasis framing affects the issue attitude $y$ by changing the weights of different considerations\footnote{Note that this concept of framing is identical to second-level or attribute agenda setting (\cite{Lopezescobar2017, McCombs2000}; see \cite[174]{Mclaren2018} for a discussion of the overlap of these literatures).
+I will stick to the framing perspective here as the literature is focused on issues rather than candidates' attributes, and the conceptualisation as frame allows to form expectations about citizens' reactions to changing news frames.}.
+
+This operationalisation allows us to generate specific expectations about how frames in the news media affect respondents' issue opinions.
+When presented with an emphasis frame on a given issue, the respondents' cognitive association of the issue with the emphasised consideration should increase, thus changing the evaluation of the issue by increasing the importance of the consideration.
+If the consideration is positive (towards the issue), the attitude towards the issue should improve, and the opposite when it is negative.
+\medskip
+
+\textbf{H2 (emphasis framing):} If a newspaper emphasises more positive/negative frames of an issue, the readers' attitude about the issue should become more positive/negative.
+
+% JB: I’m wondering if negative reference might help you with the definition.
+In our last colloquium you still got the criticism that framing was not well defined enough.
+I think you might be able to avoid a lot of the criticism (what makes framing different from issue ownership etc.) by addressing the contrast from framing from some of the more used concepts such as issue attention.
+Just an idea
+% \footnote{I will stop here to outline the other chapters.
+However, a future version of this draft will discuss the cognitive basis of this model (considerations: affective storage as discussed by Taber and Lodge, Kunda; weights: physical cognitive association through Hebbian learning) and  whether this is a rational model (\cite{Ajzen2000, Druckman2001}).}.
+
+\begin{center}
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{pres/vis/CognitiveStorage.png}
+    \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}
+    \label{fig:cogStor}
+\end{figure}
+\end{center}
 
@@
 
-\subsection{Data and case description}
+\subsection{Case description}
 
-\subsubsection{Public opinion data}
+[describe context of German election 2017 and dominance of migration topic]
 
-% plot with opinion development per paper for four / six issues
+\subsection{Public opinion data}
 
-\begin{itemize}
-    \item GLES Panel 2016-2020
-    \item about 10,000 - 15,000 respondents per wave
-    \item data on issue attitudes, importance, and news consumption
-\end{itemize}
+To measure the dependent variable (issue attitudes) and differentiate the treatment groups (newspaper readers), I employ panel data from the German Longitudinal Election Study (GLES, \cite{GLES2019LongTermTracking}).
+The panel consists of 15 waves, of which 6 (4) contain variables on newspaper consumption and immigration (integration) attitudes.
+In each wave 9,000-15,000 respondents were interviewed, which allows the precise estimation of effects of media consumption.
+
+Figure \ref{fig:issues} shows the two main dependent variables for each group of readers.
+Note that higher values on the immigration variable indicate more restrictive attitudes, while higher values on the integration variable are most liberal.
+As can be seen, readers of the tabloid 'Bild' differ strongly from consumers of other outlets, with far more restrictive attitudes.
+Both variables seem inversely correlated (as expected), with values moving towards the more liberal pole until autumn, where the trend is reversed.
+The development of issue importance across time can be found in Appendix \ref{app:importance}.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{paper/vis/Immigration_papers.png}
-    \caption{Opinions on migration across time (higher values indicate more restrictive attitudes).}
+    \includegraphics[width=\textwidth]{paper/vis/issues_readers.png}
+    \caption{Opinions on migration and integration across time (higher values on immigration indicate more restrictive attitudes, vice versa for integration).}
     \label{fig:issues}
@@
 
-\subsubsection{Data on news framing}
-% plot with frames and survey dates
+\subsection{Measuring news framing}
+
+\subsubsection{Measuring news attention to migration}
+
 \begin{figure}[!ht]
     \centering
-    \includegraphics[width=\textwidth]{paper/vis/frames_papers_wtd_focus.png}
+    \includegraphics[width=\textwidth]{paper/vis/salience_papers_focus.png}
+    \caption{Share of migration articles out of all articles across time for different newspapers.}
+    \label{fig:salience}
+\end{figure}
+
+\subsubsection{Measuring news frames}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/frames_papers_focus.png}
     \caption{Prevalence of different migration frames across newspapers. Gray vertical lines indicate survey field dates.}
@@
 
-\subsubsection{Have readers' issue definitions changed as a result of the changing media frames?}
-
-The final analysis in this paper aims to show that changes in readers' migration definitions correspond to changes in news coverage.
-This can be achieved by applying embedding regression to open survey responses, which shows differing word associations for subgroups of documents.
-This would show if respondents reading a certain newspaper define migration more in line with e.g.
-the humanitarian situation in refugee camps, compared to a preceding wave and controlling for shifts in other newspapers.
-
 \section{Results}
@@
     \centering
-    \includegraphics[width=\textwidth]{paper/vis/effectplot_noimp.png}
+    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames.png}
     \caption{Correlation of opinion shifts (DiDs) with media attention or shifts in attention (DiD's) for different specifications.}
@@
 
-The analysis shows that, generally, no clear pattern can be observed in the correlation of these effects.
-Independent of the choice of the dependent variable, specification of the independent variable (DiD/attention and differing periods of news coverage), and across all migration frames, t-values scatter around 0 (see also \ref{fig:t_values} in the appendix).
-This constitutes strong evidence against an effect of news framing on opinion formation.
-Even changes in issue salience in a given newspaper do not correspond to changes in readers' issue attitudes (see bottom two panels).
-
-A second analysis will estimate the decrease in explanatory value of the wave-news consumption interaction/DiD when media attention is added as a control.
-
-\subsection{Shifts in issue definitions}
-
 % show for one specific case that shift in media frame corresponded to 
+\begin{table}[!htbp] \centering 
+  \caption{Individual-level Model} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-3} 
+\\[-1.8ex] & Immigration attitude & Integration attitude \\ 
+\\[-1.8ex] & (1) & (2)\\ 
+\hline \\[-1.8ex] 
+ Lagged DV & 0.793$^{***}$ & 0.664$^{***}$ \\ 
+  &  & (0.004) \\ 
+  & & \\ 
+ Petty Crime & 0.0001 & 0.002 \\ 
+  & (0.002) & (0.004) \\ 
+  & & \\ 
+ Capital Crime & 0.033$^{***}$ & $-$0.027$^{**}$ \\ 
+  & (0.006) & (0.012) \\ 
+  & & \\ 
+ Refugee Numbers & $-$0.016$^{***}$ & $-$0.001 \\ 
+  & (0.002) & (0.004) \\ 
+  & & \\ 
+ Refugee Camps & 0.025$^{***}$ & $-$0.004 \\ 
+  & (0.004) & (0.012) \\ 
+  & & \\ 
+ Mediterranean S\&R & 0.035$^{***}$ & $-$0.005 \\ 
+  & (0.002) & (0.005) \\ 
+  & & \\ 
+ Labour Market & 0.015$^{***}$ & 0.009 \\ 
+  & (0.003) & (0.006) \\ 
+  & & \\ 
+ Deportation & $-$0.002$^{***}$ & 0.002$^{**}$ \\ 
+  & (0.001) & (0.001) \\ 
+  & & \\ 
+ Constant & 0.045$^{***}$ & $-$0.288$^{***}$ \\ 
+  & (0.015) & (0.036) \\ 
+  & & \\ 
+\hline \\[-1.8ex] 
+Observations & 88,026 & 36,180 \\ 
+R$^{2}$ & 0.617 & 0.421 \\ 
+Adjusted R$^{2}$ & 0.617 & 0.421 \\ 
+Residual Std. Error & 1.095 (df = 88017) & 1.095 (df = 36171) \\ 
+F Statistic & 17,740.240$^{***}$ (df = 8; 88017) & 3,286.942$^{***}$ (df = 8; 36171) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 
 \section{Discussion}
+\begin{itemize}
+    \item 
+    \item people could a) not react, b) stop reading their newspaper, c) change their opinion
+\end{itemize}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width = \textwidth]{paper/vis/t_values_noimp.png}
-    \caption{Caption}
-    \label{fig:t_values}
-\end{figure}
+\subsection{Descriptives on issue importance across time and newspaper consumption}\label{app:importance}
+
+[add description and plot issue importance]
 

### 2021-09-28 paper/main.tex

@@
 
+To measure media attention to immigration, I collected 2.5 million newspaper articles from the most important German broadsheets \textit{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt} and the major German tabloid \textit{Bild} for the period 2016-2019.
+To identify whether an article is about migration, I train a BERT deep-learning classifier.
+
+As migration content is rare, and my training data needs to be somewhat balanced, I first construct a dictionary of terms related to migration.
+I use dictionary extension based on German Glove\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles.
+Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from the third with fewest migration terms, 100 from the third with most migration terms and 100 from the third in between) for each paper for a total of 1,800 papers.
+Then, a student assistant\footnote{Thank you Robin.} hand-coded these articles, assessing whether their main topic is related to migration.
+
+Using this sample, a BERT deep-learning classifier\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a subset of 1,400 annotated articles.
+After fine-tuning, the model correctly classifies 95.5\% of the test set (F1: 0.94, recall: 0.93, precision: 0.95).
+This classifier is then used to annotate all 2.5 million newspaper articles.
+For the time frame of relevance for this study (the entire year of 2017), out of the total of 388,617 articles, 13,589 (3.5\%) are identified to treat the issue of migration.
+
 \begin{figure}[!ht]
@@
 
+Figure \ref{fig:salience} shows the share of migration articles in each newspaper.
+While the first few months of 2017 show rather high salience of the issue, attention decreases until May, before the share of articles covering this issue increases again in all newspapers except Bild, which shows a stark decrease in July and maintains this level afterward.
+Most newspapers show similar levels of attention to the issue between 2.5\% and 6\%, with the exception of SZ, which moves between 5\% and 12.5\%.
+
 \subsubsection{Measuring news frames}
+
+To measure news frames, I estimate a structural topic model with 60 topics for the nearly 90,000 migration articles in the full period (2016-2019)\footnote{The }.
+Topic prevalence is estimated as a function of the release date of the article, as well as the paper it has been published in.
+The 60 topics' most predictive words and ten most representative articles were assessed to assess the content of each topic, and the most frequent and relevant topics that allow to form clear hypotheses regarding their effect on immigration attitudes are selected.
+
+With this procedure, the following seven 'large' migration frames were selected:
+
+\begin{enumerate}
+    \item Capital crime (sexual assault/rape/murder) committed by refugees, 
+    \item general petty crime by refugees and issues in refugee living quarters in Germany,
+    \item refugee numbers,
+    \item labour market needs for and integration of refugees,
+    \item deportations,
+    \item internment camps (e.g. Moria),
+    \item drownings in the Mediterranean.
+\end{enumerate}
+
+I expect both crime frames and the refugee numbers to have negative effects on attitudes towards migrants (as connected to negative considerations regarding immigration), while labour market considerations, deportations, internment camps, and drownings in the Mediterranean sea should have positive effects as positive considerations, framing immigration either as a labour market need or a humanitarian necessity.
+Figure \ref{fig:frames} shows the prevalence of all frames across time for each newspaper.
+It can be seen that substantial variation exists in the relative emphasis of migration frames both within and across newspapers.
 
@@
 
-\begin{itemize}
-    \item Collected around 2.5 million newspaper articles from six major newspapers
-    \item Extracted and annotated a stratified sample of articles using a migration dictionary
-    \item Trained a migration classifier (BERT transformer) based on these annotations
-    \item estimated migration frames using STM on migration articles only (N = 90,000): 
-    \item retained most common and relevant frames that allow to form clear hypotheses about attitude formation:
-    \begin{itemize}
-        \item Internment camps, 
-        \item capital crime (sexual assault/rape/murder) committed by refugees, 
-        \item general petty crime by refugees and issues in refugee living quarters in Germany,
-        \item deportations,
-        \item labour market needs for and integration of refugees
-        \item drownings in the mediterranean
-        \item refugee numbers
-    \end{itemize}
-\end{itemize}
-
 \subsection{Study design}
@@
 
-To get a glimpse of whether opinion shifts might be influenced by news consumption, I estimate difference-in-differences models (DiDs) for all available combinations of news outlets (incl.
-TV news), issues, and survey waves.
+To get a glimpse of whether opinion shifts might be influenced by news consumption, I estimate difference-in-differences models (DiDs) for all available combinations of news outlets, issues, and survey waves.
 The main term of interest is the interaction of a binary indicator of readership of a certain outlet with a binary indicator which equals 1 for the current wave and 0 for the preceding wave.
@@
 
+\subsection{Structural Topic Model}\label{app:stm}
+
 \end{document}

### 2021-09-29 code/06_vis.R
Update model, improve visualisation

@@ -224,8 +224,10 @@ framing_sum %>%
   geom_rug(data = survey_dates, aes(x = date),sides = 't', inherit.aes = F) +
   facet_grid(frame~paper, scales = 'free', ) +
   ggtitle('Migration frames in different newspapers 2017', 'Black ticks indicate survey waves') +
-  scale_x_date(date_labels = '%b')
-ggsave(here('paper/vis/frames_papers_focus.png'), width = 8, height = 7)
+  scale_x_date(date_labels = '%b') +
+  xlab('Share of all migration articles') +
+  ylab('') + theme(legend.position = "none")
+ggsave(here('paper/vis/frames_papers_focus.png'), width = 8, height = 10)
 
 framing_sum %>% 
   filter(date < as.Date('2018-01-01')) %>% 
@@ -345,6 +347,8 @@ for (frame in c('crime', 'capcrime', 'refnums', 'medit', 'camps', 'labmar', 'dep
     coord_cartesian(xlim = c(-2, 2))
 }
 
-grid.arrange(grobs = plots, nrow = 7) %>% 
+library(ggpubr)
+ggarrange(plotlist = plots, ncol = 2, nrow = 4, 
+          common.legend = T, legend = "bottom") %>% 
   ggsave(filename = here("paper/vis/effectplot_frames.png"),
-       width = 7, height = 12)
+         width = 10, height = 7)

### 2021-09-29 paper/main.tex

@@
 
-\subsubsection{Can framing effects among newspaper readers be observed?}
+\subsubsection{Differences in opinion formation across readers}
 
-To get a glimpse of whether opinion shifts might be influenced by news consumption, I estimate difference-in-differences models (DiDs) for all available combinations of news outlets, issues, and survey waves.
+To assess whether opinion shifts might be influenced by news consumption, I estimate difference-in-differences (DiDs) for all available combinations of issues, news outlets, and survey waves.
 The main term of interest is the interaction of a binary indicator of readership of a certain outlet with a binary indicator which equals 1 for the current wave and 0 for the preceding wave.
-That means I measure the shift in opinions of the readership of a certain outlet, controlling for the changes taking place among consumers of other news.
+Hence I measure the shift in opinions of the readership of a certain outlet, controlling for the changes taking place among consumers of other news.
+The distribution of p-values of these DiDs allows me to assess whether meaningful variation exists in readers' attitude formation that can be explained by shifts in media consumption.
+The formula is given below:
 
-\subsubsection{Can these opinion shifts be explained by changing media frames?}
+$$ y = \beta_1 * W + \beta_2 * R + \beta_3 * W * R, $$
 
-\begin{itemize}
-    \item look at migration, maybe a second issue: how strongly do DiD's correlate with changing frame prevalence/DiD of frame attention?
-    \item look at how FE model DiD's change when controlling for newspaper attention/DiD
-    \item add right-wing slant as second dependent using AfD-classifier
-\end{itemize}
+where $y$ is the dependent (attention to migration frame or migration opinion), $W$ indicates whether the interview took place ($W = 1$) in a given survey wave or in the preceding one ($W = 0$), and $R$ indicates whether the respondent is a reader of the newspaper of interest.
+
+\subsubsection{Estimation of framing effect}\label{sec:models}
+
+I estimate the same DiDs to measure shifts in migration framing in a certain newspaper, controlling for shifts in all other newspapers.
+To do that, I first sum the attention given to a certain frame in a given newspaper in the past day, week, month, or half year, up to the last survey.
+This allows me to assess whether choosing different lags affects my estimates.
+Then, I estimate the DiD, indicating how much a newspaper changed its attention to a given migration frame.
+These estimates are then matched and correlated with the DiDs estimating the opinion shifts.
+If increasing attention to a certain frame causes a shift in migration attitudes, these two measures should be highly correlated.
+
+Second, I estimate an individual-level model predicting immigration opinion with a lagged dependent variable and the exposure to each frame.
+Controlling for the lagged dependent variable means that I restrict the variance to the shift in opinions since the last wave.
+I measure exposure to each frame by summing up the frame attention of the past week in each newspaper the respondent claimed to have read in the past week and dividing it by the total number of newspapers read.
+This way, I estimate frame exposure for each individual respondent's interview date and news diet.
 
@@
 
-% refer to graph on mig issue
-The parallel trends assumption is met, as can be seen in figure \ref{fig:issues}. A plot of all other issues showing similar co-variation will be added to the appendix at a later point in time.
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps.png}
+    \caption{Empirical and theoretical p-values of 1,752 DiD-models.}
+    \label{fig:p_values}
+\end{figure}
 
-% also think about excludability: how can you ensure that these shifts are a result of media framing (this might be answered in number two)
+DiD-designs rest on the assumption that treated and untreated units would follow the same trend, were it not for the treatment.
+This means that, generally, treated and untreated units should show similar trends.
+Returning to figure \ref{fig:issues}, we can safely state that the parallel trends assumption is met in this case.
+All reader groups move in a highly similar fashion on both variables, albeit at different levels, which reflect the ideological leaning of their newspaper.
 
@@
 
-The upper panel of figure \ref{fig:p_values} shows the distribution of p-values for the DiD-term from 1,056 fixed-effect models with GLES Panel data.
+As a first step, the DiDs for all wave-issue-paper combinations are estimated.
+This means I use all political issues included in the surveys (economic, issues, climate, ...) are used as dependent variable, and assess whether news consumption matters for opinion formation more generally.
+The upper panel of figure \ref{fig:p_values} shows the distribution of p-values for the DiD-term from 1,752 fixed-effect models with GLES Panel data.
 The distribution shows a considerable deviation from the expected uniform distribution (visible in the lower panel) were there no explaining variation in the DiD-term beyond the uniform effects of wave and paper readership.
 This means, more often than random, the opinions of consumers of certain news deviate from the opinions of other citizens.
-
-% show distribution of p-values vs theoretical distribution -> looks like there is systematic deviation
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps.png}
-    \caption{Empirical and theoretical p-values of 1,363 DiD-models.}
-    \label{fig:p_values}
-\end{figure}
+This strongly indicates that news consumption matters for opinion formation.
 
@@
 
+There seems to be interesting variation in the dependent variable.
+Can these opinion shifts be explained by shifts in news content?
 Figure \ref{fig:did_corr} shows the core analysis to estimate the effect of media attention on reader opinion.
-Each dot in this graph represents the t-value of a model explaining aggregate opinion shifts (DiDs, blue dots) with aggregate media attention or shifts in attention (DiDs) for a specific frame and a specific model specification.
-These aggregate parameters come from models explaining immigration opinion/media attention with news outlet-wave interactions, as in the models providing the p-values for figure \ref{fig:p_values}.
-If opinion shifts among newpapers' readers - relative to other readers - can be explained by shifts in newspapers' issue framing, these two variables should be highly correlated.
-The displayed estimates are hence obtained by regressing the resulting DiD-estimates for issue attitudes on the DiD-estimates for media attention.
+The displayed estimates are obtained by regressing the resulting DiD-estimates for issue attitudes on the DiD-estimates for media attention.
+Each dot in this graph represents the coefficient of a model explaining standardised aggregate opinion shifts with standardised shifts in media attention to specific frames for a specific frame and a specific model specification, as outlined in section \ref{sec:models}.
+If opinion shifts among newspapers' readers - relative to other readers - can be explained by shifts in newspapers' issue framing, these two variables should be highly correlated.
 
-For example, the left graph in the top panel row shows the effect of media attention on immigration attitudes for two different independent variables (DiD \textit{coef}ficients estimating the increase in news coverage in the consumed outlet relative to all others, and the general \textit{attention} in the preceding period) and four different time lags (see horizontal lines in descending order: 1 week, 1 month, 6 months, and the full period until last survey wave [g]).
-Note that immigration and integration are inversely coded.
-Higher values indicate more restrictive attitudes on immigration, but more liberal attitudes on integration.
-+/- signs corresponding to the frames (visible on the right-hand side) indicate the hypothesized effect of the frame on integration.
+This is however not the case.
 
@@
 \begin{itemize}
-    \item 
     \item people could a) not react, b) stop reading their newspaper, c) change their opinion
+    \item add right-wing slant as second dependent using AfD-classifier
 \end{itemize}

### 2021-09-29 code/05a_main_models.R
Standardise individual level model inputs

@@ -325,13 +325,13 @@ imm_mod_unw_all_nosal <-
      formula = 
        `1130_clean` ~ 
        `1130_lag` + 
-       crime_tot_7d_unw + 
-       capcrime_tot_7d_unw + 
-       refnums_tot_7d_unw + 
-       camps_tot_7d_unw + 
-       medit_tot_7d_unw + 
-       labmar_tot_7d_unw + 
-       deport_tot_7d_unw )
+       scale(crime_tot_7d_unw,    center = T, scale = T) + 
+       scale(capcrime_tot_7d_unw, center = T, scale = T) + 
+       scale(refnums_tot_7d_unw,  center = T, scale = T) + 
+       scale(camps_tot_7d_unw,    center = T, scale = T) + 
+       scale(medit_tot_7d_unw,    center = T, scale = T) + 
+       scale(labmar_tot_7d_unw,   center = T, scale = T) + 
+       scale(deport_tot_7d_unw,   center = T, scale = T))
 
 summary(imm_mod_unw_all_nosal) # only camps very restrictive effect - weird, generally large effects
 

### 2021-09-29 code/05a_main_models.R
Update model: add scaled ivs for integration

@@ -355,13 +355,13 @@ int_mod_unw_all_nosal <-
      formula = 
        `1210_clean` ~ 
        `1210_lag` + 
-       crime_tot_7d_unw + 
-       capcrime_tot_7d_unw + 
-       refnums_tot_7d_unw + 
-       camps_tot_7d_unw + 
-       medit_tot_7d_unw + 
-       labmar_tot_7d_unw + 
-       deport_tot_7d_unw )
+       scale(crime_tot_7d_unw , center = T, scale = T)+ 
+       scale(capcrime_tot_7d_unw, center = T, scale = T) + 
+       scale(refnums_tot_7d_unw, center = T, scale = T) + 
+       scale(camps_tot_7d_unw, center = T, scale = T) + 
+       scale(medit_tot_7d_unw, center = T, scale = T) + 
+       scale(labmar_tot_7d_unw, center = T, scale = T) + 
+       scale(deport_tot_7d_unw ))
 
 summary(int_mod_unw_all_nosal)
 

### 2021-09-29 paper/main.tex

@@
 This is however not the case.
+As figure \ref{fig:did_corr} shows, even with different specifications, \textit{no} estimate has predictive power for our analysis.
+For example, in the upper left panel 'crime', we can see 5 different lags 'g', '6m', '1m', '1w', '1d' distinguished vertically, and the effects for two different issues in the two different panes.
+Additionally, the color of the points indicates whether the model was estimated only for readers of a single newspaper (lower N, but no treatment diffusion) or all readers of a newspaper (who might read another newspaper, say SZ readers who also read FAZ).
+All estimates are clearly clustering around the null, indicating no effect.
+While the 'exclusive reader' estimates show more variation, they also indicate far broader confidence intervals.
+There is no considerable difference across lags, and the variables only differ by the broader confidence intervals of the integration variable, owing to the fewer waves including this question.
+Generally, this analysis indicates no effect of media framing of migration on migration attitudes.
 
-% show for one specific case that shift in media frame corresponded to 
-\begin{table}[!htbp] \centering 
-  \caption{Individual-level Model} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lcc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-3} 
-\\[-1.8ex] & Immigration attitude & Integration attitude \\ 
-\\[-1.8ex] & (1) & (2)\\ 
-\hline \\[-1.8ex] 
- Lagged DV & 0.793$^{***}$ & 0.664$^{***}$ \\ 
-  &  & (0.004) \\ 
-  & & \\ 
- Petty Crime & 0.0001 & 0.002 \\ 
-  & (0.002) & (0.004) \\ 
-  & & \\ 
- Capital Crime & 0.033$^{***}$ & $-$0.027$^{**}$ \\ 
-  & (0.006) & (0.012) \\ 
-  & & \\ 
- Refugee Numbers & $-$0.016$^{***}$ & $-$0.001 \\ 
-  & (0.002) & (0.004) \\ 
-  & & \\ 
- Refugee Camps & 0.025$^{***}$ & $-$0.004 \\ 
-  & (0.004) & (0.012) \\ 
-  & & \\ 
- Mediterranean S\&R & 0.035$^{***}$ & $-$0.005 \\ 
-  & (0.002) & (0.005) \\ 
-  & & \\ 
- Labour Market & 0.015$^{***}$ & 0.009 \\ 
-  & (0.003) & (0.006) \\ 
-  & & \\ 
- Deportation & $-$0.002$^{***}$ & 0.002$^{**}$ \\ 
-  & (0.001) & (0.001) \\ 
-  & & \\ 
- Constant & 0.045$^{***}$ & $-$0.288$^{***}$ \\ 
-  & (0.015) & (0.036) \\ 
-  & & \\ 
-\hline \\[-1.8ex] 
-Observations & 88,026 & 36,180 \\ 
-R$^{2}$ & 0.617 & 0.421 \\ 
-Adjusted R$^{2}$ & 0.617 & 0.421 \\ 
-Residual Std. Error & 1.095 (df = 88017) & 1.095 (df = 36171) \\ 
-F Statistic & 17,740.240$^{***}$ (df = 8; 88017) & 3,286.942$^{***}$ (df = 8; 36171) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
+To corroborate these results, I estimate another model directly predicting individual migration opinions with a lagged dependent and individual estimates of consumed migration frames (see section \ref{sec:models}).
+The results for migration and integration attitudes can be seen in table \ref{tab:ind_model}.
+While the
 

### 2021-09-29 code/05a_main_models.R
Fix model scaling iv

@@ -361,7 +361,7 @@ int_mod_unw_all_nosal <-
        scale(camps_tot_7d_unw, center = T, scale = T) + 
        scale(medit_tot_7d_unw, center = T, scale = T) + 
        scale(labmar_tot_7d_unw, center = T, scale = T) + 
-       scale(deport_tot_7d_unw ))
+       scale(deport_tot_7d_unw, center = T, scale = T))
 
 summary(int_mod_unw_all_nosal)
 

### 2021-09-29 code/05a_main_models.R
Fix issue of few observations in individual model

@@ -257,8 +257,8 @@ merged_data <-
         (`1661c_clean` > 0),
         (`1661d_clean` > 0),
         (`1661e_clean` > 0),
-        (`1661f_clean` > 0)
-      )
+        (`1661f_clean` > 0),
+        na.rm = T)
   )
 
 merged_data <- 

### 2021-09-29 code/05a_main_models.R
Fix issue grouping n_read variable

@@ -249,17 +249,14 @@ merged_data <-
     labmar_7d_taz  = ifelse(is.na(labmar_7d_taz),  0, labmar_7d_taz),
     labmar_7d_welt = ifelse(is.na(labmar_7d_welt), 0, labmar_7d_welt)
     
-  ) %>% 
-  mutate(
-    n_read = 
-      sum(
-        (`1661a_clean` > 0),
-        (`1661c_clean` > 0),
-        (`1661d_clean` > 0),
-        (`1661e_clean` > 0),
-        (`1661f_clean` > 0),
-        na.rm = T)
   )
+
+merged_data$n_read  <-  
+  merged_data %>% 
+  ungroup() %>% 
+  select(contains("1661")) %>% 
+  select(contains("bin"), -`1661g_bin`, -`1661b_bin`) %>% 
+  rowSums()
 
 merged_data <- 
   merged_data %>% 

### 2021-09-29 code/05a_main_models.R
Get rid of scaling again

@@ -322,13 +322,13 @@ imm_mod_unw_all_nosal <-
      formula = 
        `1130_clean` ~ 
        `1130_lag` + 
-       scale(crime_tot_7d_unw,    center = T, scale = T) + 
-       scale(capcrime_tot_7d_unw, center = T, scale = T) + 
-       scale(refnums_tot_7d_unw,  center = T, scale = T) + 
-       scale(camps_tot_7d_unw,    center = T, scale = T) + 
-       scale(medit_tot_7d_unw,    center = T, scale = T) + 
-       scale(labmar_tot_7d_unw,   center = T, scale = T) + 
-       scale(deport_tot_7d_unw,   center = T, scale = T))
+       crime_tot_7d_unw     + 
+       capcrime_tot_7d_unw  + 
+       refnums_tot_7d_unw   + 
+       camps_tot_7d_unw     + 
+       medit_tot_7d_unw     + 
+       labmar_tot_7d_unw    + 
+       deport_tot_7d_unw   )
 
 summary(imm_mod_unw_all_nosal) # only camps very restrictive effect - weird, generally large effects
 
@@ -352,13 +352,13 @@ int_mod_unw_all_nosal <-
      formula = 
        `1210_clean` ~ 
        `1210_lag` + 
-       scale(crime_tot_7d_unw , center = T, scale = T)+ 
-       scale(capcrime_tot_7d_unw, center = T, scale = T) + 
-       scale(refnums_tot_7d_unw, center = T, scale = T) + 
-       scale(camps_tot_7d_unw, center = T, scale = T) + 
-       scale(medit_tot_7d_unw, center = T, scale = T) + 
-       scale(labmar_tot_7d_unw, center = T, scale = T) + 
-       scale(deport_tot_7d_unw, center = T, scale = T))
+       crime_tot_7d_unw + 
+       capcrime_tot_7d_unw + 
+       refnums_tot_7d_unw + 
+       camps_tot_7d_unw + 
+       medit_tot_7d_unw + 
+       labmar_tot_7d_unw  + 
+       deport_tot_7d_unw)
 
 summary(int_mod_unw_all_nosal)
 

### 2021-09-29 paper/main.tex
Updates from Overleaf

@@
 
-I expect both crime frames and the refugee numbers to have negative effects on attitudes towards migrants (as connected to negative considerations regarding immigration), while labour market considerations, deportations, internment camps, and drownings in the Mediterranean sea should have positive effects as positive considerations, framing immigration either as a labour market need or a humanitarian necessity.
+I expect both crime frames and the refugee numbers to have negative effects on attitudes towards migrants (as connected to negative considerations regarding immigration), while deportations, internment camps, and drownings in the Mediterranean sea should have positive effects, framing immigration either as a labour market need or a humanitarian necessity.
+The labour market frame should show mixed results, given that labour market integration might be perceived as threatening or addressing needs in the German economy.
 Figure \ref{fig:frames} shows the prevalence of all frames across time for each newspaper.
@@
 The results for migration and integration attitudes can be seen in table \ref{tab:ind_model}.
-While the
 

### 2021-10-04 paper/main.tex
Updates from Overleaf

@@
 The results for migration and integration attitudes can be seen in table \ref{tab:ind_model}.
+Maybe even more interesting, these frames differ for the two dependent variables.
+The effects for the frame variables can be read as "one standard deviation increase in frame attention increases the dependent variable by X points on a -3 to 3 scale".
+Note that higher values on the immigration variable indicate more restrictive attitudes, and vice versa for the integration variable.
+
+Surprisingly, several frames show highly significant results in this model.
+Additionally, these effects can be considered fairly large.
+For example, a one-standard deviation increase in the attention to refugee numbers in the preceding week (compared to a week preceding the last interview) moves respondents 0.328 points towards the \textit{liberal} end of the 7-point immigration attitude scale.
+Similarly, respondents move 1.12 points towards the restrictive pole when discussion of the humanitarian crisis in the Mediterranean Sea increases by one standard deviation, and 2.43 points when the labour market frame is increasingly discussed.
+Most interestingly, the labour market frame has the \textit{opposite} effect on integration attitudes, making people .34 points towards the liberal pole.
+Lastly, deportations have a slightly liberalising effect.
+None of these frames have the expected impact on opinions.
+Perhaps the clearest expectation can be formulated regarding the capital crime frame, which has pretty much no effect.
+
+\begin{table}[!htbp] \centering 
+  \caption{Individual-level Model} 
+  \label{tab:ind_model} 
+\begin{tabular}{@{\extracolsep{5pt}}lcc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-3} 
+\\[-1.8ex] & Immigration & Integration \\ 
+\hline \\[-1.8ex] 
+ Immigration (lag) & 0.816$^{***}$ &  \\ 
+  & (0.005) &  \\ 
+  & & \\ 
+ Integration (lag) &  & 0.745$^{***}$ \\ 
+  &  & (0.012) \\ 
+  & & \\ 
+ Petty Crime & 0.022 & $-$0.071 \\ 
+  & (0.019) & (0.069) \\ 
+  & & \\ 
+ Capital Crime& 0.011 & 0.016 \\ 
+  & (0.015) & (0.041) \\ 
+  & & \\ 
+ Refugee numbers & $-$0.328$^{***}$ & $-$0.163 \\ 
+  & (0.046) & (0.165) \\ 
+  & & \\ 
+ Internment Camps & 0.011 & 0.183 \\ 
+  & (0.012) & (0.134) \\ 
+  & & \\ 
+ Mediterranean & 0.112$^{***}$ & 0.035 \\ 
+  & (0.018) & (0.052) \\ 
+  & & \\ 
+ Labour Market & 0.243$^{***}$ & 0.340$^{**}$ \\ 
+  & (0.029) & (0.148) \\ 
+  & & \\ 
+ Deportations & $-$0.048$^{***}$ & $-$0.008 \\ 
+  & (0.012) & (0.065) \\ 
+  & & \\ 
+ Constant & 0.168$^{***}$ & $-$0.092 \\ 
+  & (0.018) & (0.090) \\ 
+  & & \\ 
+\hline \\[-1.8ex] 
+Observations & 13,346 & 3,818 \\ 
+R$^{2}$ & 0.646 & 0.509 \\ 
+Adjusted R$^{2}$ & 0.646 & 0.508 \\ 
+Residual Std. Error & 1.083 (df = 13337) & 1.035 (df = 3809) \\ 
+F Statistic & 3,045.212$^{***}$ (df = 8; 13337) & 493.950$^{***}$ (df = 8; 3809) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 
 \section{Discussion}
-\begin{itemize}
-    \item people could a) not react, b) stop reading their newspaper, c) change their opinion
-    \item add right-wing slant as second dependent using AfD-classifier
-\end{itemize}
+
+It is unclear so far what to make of these results.
+While I am fairly certain that I need to re-assess the code, it seems that null effects dominate the (more identified) DiD-model, while the individual-level model shows odd, significant effects, highly dependent on model specifications.
+It might be that these effects are conditional, perhaps dependent on pre-existing immigration attitudes, issue importance, or partisanship.
+While these interactions do seem to have an effect, no clear narrative seems to emerge.
+For example, Petty Crime news are de-polarising, while news on capital crime by refugees affect opinions in a polarising way.
+If I settle on the first model and argue for null-effects, it is unclear how to present more evidence.
+Look for alternative explanation of opinion shifts?
+Assess effect on issue definitions, as initially planned?
+Show that strong shifts in frame attention drive people to stop reading the newspaper?
+Run an alternative model with 'right-wingness' of the migration discourse as main independent variable?
+
+It seems I have crashed.
 
@@
 
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=2\textwidth]{paper/vis/mig_topics_plot.png}
+    \label{fig:did_corr}
+\end{figure}
+
 \end{document}

### 2021-10-04 paper/main.tex

@@
 \fancyhf{}
-\rhead{The Causal Effect of Media Frames}
+\rhead{Media Framing and Issue Attitudes}
 \lhead{Nicolai Berk}
@@
 
-\title{The Causal Effect of Media Frames on Issue Attitudes}
+\title{The Effect of Media Frames on Issue Attitudes}
 \author{Nicolai Berk\footnote{Doctoral Candidate, Dynamics Doctoral Program, Humboldt-Universität zu Berlin, \href{mailto:nicolai.berk@hu-berlin.de}{nicolai.berk@hu-berlin.de}}}
@@
 Combining panel data from the German Longitudinal Election Study with a fine-grained analyses of media framing, I address this debate with observational data, providing evidence from 1,752 fixed-effect, difference-in-differences models suggesting systematic differences in newspaper readers' opinion shifts.
-Second, I show that such changes in consumers' attitudes towards immigration surrounding the German national election 2017 did \textit{not} correspond to changes in the migration framing of consumed media outlets.
+Second, I present evidence that such changes in consumers' attitudes towards immigration surrounding the German national election 2017 did \textit{not} correspond to changes in the migration framing of consumed media outlets.
 The findings contribute to our understanding of opinion formation processes and the relevance of the news media in the 21st century.
@@
 
-Yet, a popular critique of these theories maintains that strong news effects are unlikely in the modern media environment, where consumers self-select into news sources of their liking.
+Yet, a critique of these theories maintains that strong news effects are unlikely in the modern media environment, where consumers self-select into news sources of their liking.
 As a result, "most media users will rarely find themselves in the path of attitude-discrepant information".
@@
 
-This conflicting evidence begs the question: when can we expect media framing effects?
+This discussion begs the question: when can we expect media framing effects?
 Some authors have argued that a lack of media effects can be explained by readers who discount a publications' bias.
@@
 The present study contributes to this debate in two ways.
-First, instead of taking media slant as a given (\cite{Foos2020, Guess2021}), I measure the prevalence of different frames directly and assess whether their presence in the media across time affected readers' issue attitudes.
+First, instead of taking media framing as a given (\cite{Foos2020, Guess2021}), I measure the prevalence of different frames directly and assess whether their presence in the media across time affected readers' issue attitudes.
 Second, I use the variation in framing \textit{within} a given newspaper across time as the main independent variable.
@@
 Recently, \citeauthor{Guess2021} incentivised participants of an online-panel to visit left- or right-leaning news websites, with no effect on opinions (\citeyear{Guess2021}).
-An experiment by \citeauthor{Lau2021} indicates that increasing the likelihood of encountering information about a fictitious candidate's stance on a given issue does not increase the importance of that issue in reaching a voting decision, directly contradicting theories of agenda setting.
+An experiment by \citeauthor{Lau2021} indicates that increasing the likelihood of encountering information about a fictitious candidate's stance on a given issue does not increase the importance of that issue in reaching a voting decision, directly contradicting theories of agenda setting (\citeyear{Lau2021}).
 This lack of evidence echos a general critique of the external validity of framing experiments and other experimental evidence about opinion formation (\cite{Barabas2010, Busby2019, Leeper2020}).
 
-What might explain these different findings?
+What might explain these contradicting findings?
 Scope conditions for media effects seem to be surprisingly understudied given the contradicting body of evidence.
@@
 
-If citizens discount the content of newspapers, they should not react to news content which is randomly assigned to them.
+If citizens discount the content of media outlets, they should not react to the presentation of news from outlets they do not usually consume.
 Instead, a most likely case for effects of news exposure would have to assess changing content \textit{within} the same newspapers and its effect on consumers' issue attitudes.
@@
 
-\subsection{Agenda Setting}
+% \subsection{Agenda Setting}
 
-\textbf{[Now that there seem to be no framing effects, I am considering to make this a broader study of media effects and include agenda setting.
+% \textbf{[Now that there seem to be no framing effects, I am considering to make this a broader study of media effects and include agenda setting.
 But I guess this might be hard to finish until the weekend, so I should probably drop it for now.
@@
 
-[Insert discussion of McCombs \& Shaw, as well as recent studies on agenda setting through the media, might also contrast 'latent salience model' (similar to Gamson \& Modigliani) and 'direct agenda setting']
+% [Insert discussion of McCombs \& Shaw, as well as recent studies on agenda setting through the media, might also contrast 'latent salience model' (similar to Gamson \& Modigliani) and 'direct agenda setting']
 
-\medskip
+% \medskip
 
-\textbf{H1a (direct agenda setting):} The more an issue is emphasised in a given newspaper, the more important this issue is considered by readers of this newspaper, relative to other newspapers.
+% \textbf{H1a (direct agenda setting):} The more an issue is emphasised in a given newspaper, the more important this issue is considered by readers of this newspaper, relative to other newspapers.
 
-\textbf{H1b (latent salience model):} Increased issue attention in the news across time corresponds to increased importance among all readers, but higher attention in one newspaper compared to others does not increase the perceived importance among its readers relative to those of other newspapers (all move at the same time).
+% \textbf{H1b (latent salience model):} Increased issue attention in the news across time corresponds to increased importance among all readers, but higher attention in one newspaper compared to others does not increase the perceived importance among its readers relative to those of other newspapers (all move at the same time).
 
@@
 
-% JB: I’m wondering if negative reference might help you with the definition.
-In our last colloquium you still got the criticism that framing was not well defined enough.
-I think you might be able to avoid a lot of the criticism (what makes framing different from issue ownership etc.) by addressing the contrast from framing from some of the more used concepts such as issue attention.
-Just an idea
-% \footnote{I will stop here to outline the other chapters.
-However, a future version of this draft will discuss the cognitive basis of this model (considerations: affective storage as discussed by Taber and Lodge, Kunda; weights: physical cognitive association through Hebbian learning) and  whether this is a rational model (\cite{Ajzen2000, Druckman2001}).}.
-
 \begin{center}
@@
     \centering
-    \includegraphics[width=\textwidth]{pres/vis/CognitiveStorage.png}
+    \includegraphics[width=\textwidth]{paper/vis/CognitiveStorage.png}
     \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}

### 2021-10-04 code/04_vis.R
Fix plot labels salience & framing

@@ -178,7 +178,8 @@ salience_sum %>%
   ggplot(aes(x = date_m, y = share_mig, col = paper)) +
   geom_line() +
   geom_vline(xintercept = survey_dates$date, col = 'darkgray') +
-  ggtitle('Migration salience in different newspapers', 'Gray lines indicate survey waves')
+  ggtitle('Migration salience in different newspapers', 'Gray lines indicate survey waves') +
+  xlab('') + ylab('Share of migration articles')
 ggsave(here('paper/vis/salience_papers.png'), width = 8, height = 5)
 
 sal_2017 <- 
@@ -188,7 +189,8 @@ sal_2017 <-
   ggplot(aes(x = date_m, y = share_mig, col = paper)) +
   geom_line() +
   geom_vline(xintercept = survey_dates$date, col = 'darkgray') +
-  ggtitle('Migration salience in different newspapers', 'Gray lines indicate survey waves')
+  ggtitle('Migration salience in different newspapers', 'Gray lines indicate survey waves') +
+  xlab('') + ylab('Share of migration articles')
 ggsave(sal_2017, filename = here('paper/vis/salience_papers_focus.png'), 
        width = 8, height = 5)
 

### 2021-10-04 paper/main.tex
Updates from Overleaf

@@
 These frames emphasise certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame (\cite[153f]{Leeper2020}).
-For example, issues of increasing welfare contributions might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes.
+For example, issues of increasing welfare benefits might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes.
 Individuals' support of a statement will differ dependent on the frame presented (\cite{sniderman2004structure}).
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/CognitiveStorage.png}
+    \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}
+    \label{fig:cogStor}
+\end{figure}
 
@@
 Figure \ref{fig:cogStor} visualises this logic.
-A given issue is associated with an attitude or evaluation $y$.
+A given issue is associated with an attitude $y$.
 The issue is related to a number of different considerations, each of which carries an associated evaluation $x_i$, e.g.
@@
 
-This operationalisation allows us to generate specific expectations about how frames in the news media affect respondents' issue opinions.
+This operationalisation allows me to generate specific expectations about how frames in the news media affect respondents' issue opinions.
 When presented with an emphasis frame on a given issue, the respondents' cognitive association of the issue with the emphasised consideration should increase, thus changing the evaluation of the issue by increasing the importance of the consideration.
@@
 
-\textbf{H2 (emphasis framing):} If a newspaper emphasises more positive/negative frames of an issue, the readers' attitude about the issue should become more positive/negative.
-
-\begin{center}
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{paper/vis/CognitiveStorage.png}
-    \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}
-    \label{fig:cogStor}
-\end{figure}
-\end{center}
+\textbf{Emphasis framing hypothesis:} If a newspaper emphasises more positive/negative frames of an issue, the readers' attitude about the issue becomes more positive/negative.
 
@@
 
-[describe context of German election 2017 and dominance of migration topic]
+To test this hypothesis, I analyse media and opinion data on the migration issue from the German national election in 2017.
+Following a period of increased refugee arrivals in Europe in the summer of 2015, the election was dominated by the migration topic and the related upcoming of the radical-right populist challenger party \textit{AfD}.
+The major two parties dominating German post-war politics, \textit{SPD} and \textit{CDU/CSU}, had to face severe losses following their 'grand coalition' (\cite{Bieber2021, Wessels2021}).
+
+This strong (although still variant, see figure \ref{fig:salience}) salience of the migration issue both in the media as well as in citizens subjective evaluations presents an ideal case to study the effects of shifting media framing on issue attitudes, as continuous coverage on and public debate of the issue are a given.
 
@@
 
-To measure the dependent variable (issue attitudes) and differentiate the treatment groups (newspaper readers), I employ panel data from the German Longitudinal Election Study (GLES, \cite{GLES2019LongTermTracking}).
+To measure the dependent variable (issue attitudes) and differentiate the treatment groups (newspaper readers), I employ panel data from the German Longitudinal Election Study (\cite{GLES2019LongTermTracking}).
 The panel consists of 15 waves, of which 6 (4) contain variables on newspaper consumption and immigration (integration) attitudes.
@@
 Figure \ref{fig:issues} shows the two main dependent variables for each group of readers.
-Note that higher values on the immigration variable indicate more restrictive attitudes, while higher values on the integration variable are most liberal.
+Note that higher values indicate more restrictive attitudes towards immigration/integration (see plot subtitles for more information).
 As can be seen, readers of the tabloid 'Bild' differ strongly from consumers of other outlets, with far more restrictive attitudes.
-Both variables seem inversely correlated (as expected), with values moving towards the more liberal pole until autumn, where the trend is reversed.
-The development of issue importance across time can be found in Appendix \ref{app:importance}.
+Both variables seem correlated (as expected), with values moving towards the more liberal pole until autumn, where the trend is reversed.
 
@@
 
-To measure media attention to immigration, I collected 2.5 million newspaper articles from the most important German broadsheets \textit{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt} and the major German tabloid \textit{Bild} for the period 2016-2019.
-To identify whether an article is about migration, I train a BERT deep-learning classifier.
-
-As migration content is rare, and my training data needs to be somewhat balanced, I first construct a dictionary of terms related to migration.
-I use dictionary extension based on German Glove\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles.
-Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from the third with fewest migration terms, 100 from the third with most migration terms and 100 from the third in between) for each paper for a total of 1,800 papers.
-Then, a student assistant\footnote{Thank you Robin.} hand-coded these articles, assessing whether their main topic is related to migration.
-
-Using this sample, a BERT deep-learning classifier\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a subset of 1,400 annotated articles.
-After fine-tuning, the model correctly classifies 95.5\% of the test set (F1: 0.94, recall: 0.93, precision: 0.95).
-This classifier is then used to annotate all 2.5 million newspaper articles.
-For the time frame of relevance for this study (the entire year of 2017), out of the total of 388,617 articles, 13,589 (3.5\%) are identified to treat the issue of migration.
-
 \begin{figure}[!ht]
@@
 
+To measure media attention to immigration, I collected 2.5 million newspaper articles from the most important German broadsheets \textit{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt} and the major German tabloid \textit{Bild} for the period 2013-2019.
+To identify whether an article is about migration, I train a BERT deep-learning classifier.
+
+As migration content is rare, and my training data needs to be somewhat balanced, I first construct a dictionary of terms related to migration.
+I use dictionary extension based on German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles.
+Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from the third with fewest migration terms, 100 from the third with most migration terms and 100 from the third in between) for each newspaper for a total of 1,800 papers.
+Then, a student assistant\footnote{Thank you Robin.} hand-coded these articles, assessing whether their main topic is related to migration.
+
+Using this sample, a BERT deep-learning classifier\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a subset of 1,400 annotated articles.
+After fine-tuning, the model correctly classifies 95.5\% of the test set (F1: 0.94, recall: 0.93, precision: 0.95).
+This classifier is then used to annotate all 2.5 million newspaper articles.
+For the time frame of relevance for this study (the entire year of 2017), out of the total of 388,617 articles, 13,589 (3.5\%) are identified to treat the issue of migration\footnote{Note that the classifier, as well as the following topic model, was trained on a corpus of documents spanning 2013-2019.
+This was largely a decision to maximise possible applications for the resulting dataset, but also enables to compare issue attention and frames across time for validity checks.}.
+
 Figure \ref{fig:salience} shows the share of migration articles in each newspaper.
-While the first few months of 2017 show rather high salience of the issue, attention decreases until May, before the share of articles covering this issue increases again in all newspapers except Bild, which shows a stark decrease in July and maintains this level afterward.
-Most newspapers show similar levels of attention to the issue between 2.5\% and 6\%, with the exception of SZ, which moves between 5\% and 12.5\%.
+While the first few months of 2017 show rather high salience of the issue, attention decreases until May, before the share of articles covering this issue increases again in all newspapers except \textit{Bild}, which shows a stark decrease in July and maintains this level afterward.
+Most newspapers show similar levels of attention to the issue between 2.5\% and 6\%, with the exception of \textit{SZ}, which moves between 5\% and 12.5\%.
 
@@
 
-To measure news frames, I estimate a structural topic model with 60 topics for the nearly 90,000 migration articles in the full period (2016-2019)\footnote{The }.
-Topic prevalence is estimated as a function of the release date of the article, as well as the paper it has been published in.
-The 60 topics' most predictive words and ten most representative articles were assessed to assess the content of each topic, and the most frequent and relevant topics that allow to form clear hypotheses regarding their effect on immigration attitudes are selected.
+To measure news frames, I estimate a structural topic model with 60 topics for the nearly 90,000 migration articles in the full period (2016-2019)\footnote{The topics' prevalence along with the most important words can be assessed in appendix \ref{app:stm}.}.
+The number of topics was chosen to strike a balance between the computational and human resources necessary to estimate and annotate the topics and finding appropriate topics for the large corpus of nearly 90,000 migration articles.
+Topic prevalence is estimated as a function of the release date of the article, as well as the newspaper it has been published in.
+The 60 topics' most predictive words and ten most representative articles were assessed to identify and label the content of each topic, and the most frequent and relevant topics that allow to form clear hypotheses regarding their effect on immigration attitudes are selected.
 
-With this procedure, the following seven 'large' migration frames were selected:
+With this procedure, the following seven 'large' migration frames were selected (number of topic added corresponds to the graph in appendix \ref{app:stm}):
 
 \begin{enumerate}
-    \item Capital crime (sexual assault/rape/murder) committed by refugees, 
-    \item general petty crime by refugees and issues in refugee living quarters in Germany,
-    \item refugee numbers,
-    \item labour market needs for and integration of refugees,
-    \item deportations,
-    \item internment camps (e.g. Moria),
-    \item drownings in the Mediterranean.
+    \item Capital crime (sexual assault/rape/murder) committed by refugees (topic 48), 
+    \item illegal entry and petty crime (topic 25),
+    \item refugee numbers (topic 32),
+    \item labour market needs for and integration of refugees (topic 11),
+    \item deportations (topic 44),
+    \item internment camps (e.g. Moria; topic 27),
+    \item drownings in the Mediterranean (topic 49).
 \end{enumerate}
 
-I expect both crime frames and the refugee numbers to have negative effects on attitudes towards migrants (as connected to negative considerations regarding immigration), while deportations, internment camps, and drownings in the Mediterranean sea should have positive effects, framing immigration either as a labour market need or a humanitarian necessity.
+I expect the capital crime, illegal entry/petty crime, and the refugee numbers frames to have negative effects on attitudes towards migrants (as connected to negative considerations regarding immigration), while deportations, internment camps, and drownings in the Mediterranean sea should have positive effects, framing immigration as a humanitarian issue.
 The labour market frame should show mixed results, given that labour market integration might be perceived as threatening or addressing needs in the German economy.
@@
     \centering
-    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames.png}
+    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames_did.png}
     \caption{Correlation of opinion shifts (DiDs) with media attention or shifts in attention (DiD's) for different specifications.}
@@
 
-\subsection{Descriptives on issue importance across time and newspaper consumption}\label{app:importance}
+\subsection{Extended migration dictionary}\label{app:dictionary}
 
-[add description and plot issue importance]
+The extended migration dictionary for the pre-sampling of articles on migration consists of 35 terms (matching both lower and upper case): \textit{asyl, asylant, asylanten, asylbewerber, asylbewerberin, auslander, einwanderer, einwandernde, einwanderung, migration, immigration, schutzsuchende, visa, visum, zuwanderung, zuwanderer, zuwandernde, ausländer, ausländerinnen, flüchtling, flüchtende, flüchtlinge, flüchtlingen, migranten, vertriebene, asylantinnen, asylbewerberinnen, auslanderinnen, einwandererin, einwandererinnen, fluchtling, fluchtende, fluchtlinge, schutzbedurftige, schutzbedürftige.}
 

### 2021-10-04 code/02b_did_iv.R
Fix lag: max up to last survey wave, rerun models

@@ -85,10 +85,10 @@ for (wave_id in 1:nrow(survey_dates)){
   
   upper <- survey_dates$date[wave_id]
   
-  lower_1d <- upper - days(1)
-  lower_1w <- upper - weeks(1)
-  lower_1m <- upper - months(1)
-  lower_6m <- upper - months(6)
+  lower_1d <- max((upper - days(1)),   lower)
+  lower_1w <- max((upper - weeks(1)),  lower)
+  lower_1m <- max((upper - months(1)), lower)
+  lower_6m <- max((upper - months(6)), lower)
   
   wave <- survey_dates$wave[wave_id]
     

### 2021-10-04 code/03_estimation.R

@@ -64,7 +64,7 @@ framing_dids <-
 ## correlate with frames
 efftable <- data.frame()
 for (issue in c("immigration", "integration")){
-  for (lag in c("g", "1d", "1w", "1m", "6m")){
+  for (lag in c("all", "1d", "1w", "1m", "6m")){
     for (respons in unique(attitude_dids$respondents)){
     
       if (issue == "immigration"){

### 2021-10-04 paper/main.tex

@@
 It can be seen that substantial variation exists in the relative emphasis of migration frames both within and across newspapers.
+Interestingly, some issues seem to vary according to newspaper slant.
+For example, more right-leaning outlets \textit{Bild, FAZ}, and \textit{Welt} seem to largely ignore the humanitarian crisis in the Mediterranean sea, while they emphasise petty crime more.
+This lends some first credibility to the expected effects for these frames, although the differences are not clearly visible for the other frames.
 
@@
 
-\subsubsection{Differences in opinion formation across readers}
+\subsubsection{Differences in opinion formation across readers}\label{sec:did_readers}
 
-To assess whether opinion shifts might be influenced by news consumption, I estimate difference-in-differences (DiDs) for all available combinations of issues, news outlets, and survey waves.
-The main term of interest is the interaction of a binary indicator of readership of a certain outlet with a binary indicator which equals 1 for the current wave and 0 for the preceding wave.
+To assess whether opinion shifts might be influenced by news consumption, I isolate the opinion shift by readers of one newspaper relative to all other newspaper readers.
+To do this, I estimate difference-in-differences (DiDs) for all available combinations of issues, news outlets, and survey waves.
+The binary variable indicating readership controls for differences in levels between different news consumers, while the binary variable indicating the survey wave controls for general attitudinal shifts across time.
+The main term of interest is then the interaction of the binary indicator of readership of a certain outlet with the binary indicator for the current wave.
+This captures the change of the specified group (e.g.
+\textit{Bild}-readers), beyond time-constant differences between the newspapers and general trends from one survey wave to another.
 Hence I measure the shift in opinions of the readership of a certain outlet, controlling for the changes taking place among consumers of other news.
-The distribution of p-values of these DiDs allows me to assess whether meaningful variation exists in readers' attitude formation that can be explained by shifts in media consumption.
 The formula is given below:
@@
 This allows me to assess whether choosing different lags affects my estimates.
-Then, I estimate the DiD, indicating how much a newspaper changed its attention to a given migration frame.
-These estimates are then matched and correlated with the DiDs estimating the opinion shifts.
+Then, I estimate the DiD, indicating how much a newspaper changed its attention to a given migration frame, relative to all others.
+The DiDs estimating the opinion shifts described in \ref{sec:did_readers} are then matched and regressed on the shifts in migration framing.
 If increasing attention to a certain frame causes a shift in migration attitudes, these two measures should be highly correlated.
 
-Second, I estimate an individual-level model predicting immigration opinion with a lagged dependent variable and the exposure to each frame.
-Controlling for the lagged dependent variable means that I restrict the variance to the shift in opinions since the last wave.
-I measure exposure to each frame by summing up the frame attention of the past week in each newspaper the respondent claimed to have read in the past week and dividing it by the total number of newspapers read.
-This way, I estimate frame exposure for each individual respondent's interview date and news diet.
+Second, I fit individual-level fixed-effect models with individual news framing estimates for each survey interview.
+I measure exposure to each frame by summing up the frame attention of the past week (relative to the interview) in each newspaper the respondent claimed to have read in the past week and dividing it by the total number of newspapers read.
+This way, I estimate frame exposure for each individual respondent's interview date and news diet, which allows to estimate the correlation of changes in immigration opinion with the migration framing in recently consumed outlets.
+
+While the DiD's are causally better identified, controlling for shifts in other newspapers and reader groups, they suffer from the fact that surveys are conducted for several days, often up to two weeks, which makes the precise matching of newspaper content impossible.
+The fixed-effect models control for wave effects and (time-constant) individual characteristics, therefor restricting the explainable variance to everything beyond general trends and individual characteristics, but might include more noise.
+Another difference is that the DiD-models correlate relative shifts, while the fixed-effect models regress opinion levels on frame attention levels.
 
@@
 
-As a first step, the DiDs for all wave-issue-paper combinations are estimated.
-This means I use all political issues included in the surveys (economic, issues, climate, ...) are used as dependent variable, and assess whether news consumption matters for opinion formation more generally.
+These highly parallel trends might raise another problem, however.
+Possibly, no significant variation of reader groups' migration opinion from the general trend can be observed.
+To address this concern, I estimate DiDs for all wave-issue-paper combinations.
+This means I use attitudinal questions on all political issues included in the GLES Panel (economic, issues, climate, ...), and assess whether news consumption matters for opinion formation more generally.
 The upper panel of figure \ref{fig:p_values} shows the distribution of p-values for the DiD-term from 1,752 fixed-effect models with GLES Panel data.
 The distribution shows a considerable deviation from the expected uniform distribution (visible in the lower panel) were there no explaining variation in the DiD-term beyond the uniform effects of wave and paper readership.
-This means, more often than random, the opinions of consumers of certain news deviate from the opinions of other citizens.
-This strongly indicates that news consumption matters for opinion formation.
+This means, more often than random (12\% vs 5\%), the opinions of consumers of certain news deviate from the opinions of other citizens.
+This is even more severe for the 192 wave-paper combinations concerning the immigration or integration item used in the remainder of this study, where 18\% of all estimated DiDs fall under the 5\%-threshold\footnote{See plot in appendix \ref{}}.
+This strongly indicates that news consumption matters for opinion formation and that the data shows variation which can be explained, despite highly parallel trends.
 
@@
 
-\begin{table}[!htbp] \centering 
-  \caption{Individual-level Model} 
-  \label{tab:ind_model} 
-\begin{tabular}{@{\extracolsep{5pt}}lcc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-3} 
-\\[-1.8ex] & Immigration & Integration \\ 
-\hline \\[-1.8ex] 
- Immigration (lag) & 0.816$^{***}$ &  \\ 
-  & (0.005) &  \\ 
-  & & \\ 
- Integration (lag) &  & 0.745$^{***}$ \\ 
-  &  & (0.012) \\ 
-  & & \\ 
- Petty Crime & 0.022 & $-$0.071 \\ 
-  & (0.019) & (0.069) \\ 
-  & & \\ 
- Capital Crime& 0.011 & 0.016 \\ 
-  & (0.015) & (0.041) \\ 
-  & & \\ 
- Refugee numbers & $-$0.328$^{***}$ & $-$0.163 \\ 
-  & (0.046) & (0.165) \\ 
-  & & \\ 
- Internment Camps & 0.011 & 0.183 \\ 
-  & (0.012) & (0.134) \\ 
-  & & \\ 
- Mediterranean & 0.112$^{***}$ & 0.035 \\ 
-  & (0.018) & (0.052) \\ 
-  & & \\ 
- Labour Market & 0.243$^{***}$ & 0.340$^{**}$ \\ 
-  & (0.029) & (0.148) \\ 
-  & & \\ 
- Deportations & $-$0.048$^{***}$ & $-$0.008 \\ 
-  & (0.012) & (0.065) \\ 
-  & & \\ 
- Constant & 0.168$^{***}$ & $-$0.092 \\ 
-  & (0.018) & (0.090) \\ 
-  & & \\ 
-\hline \\[-1.8ex] 
-Observations & 13,346 & 3,818 \\ 
-R$^{2}$ & 0.646 & 0.509 \\ 
-Adjusted R$^{2}$ & 0.646 & 0.508 \\ 
-Residual Std. Error & 1.083 (df = 13337) & 1.035 (df = 3809) \\ 
-F Statistic & 3,045.212$^{***}$ (df = 8; 13337) & 493.950$^{***}$ (df = 8; 3809) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames_fe_abs.png}
+    \caption{Caption}
+    \label{fig:mode_fe}
+\end{figure}
 
@@
 
+\subsection{P-values immigration and integration issue}\label{app:p-val_imm}
+
 \end{document}

### 2021-10-04 paper/main.tex

@@
 This means, more often than random (12\% vs 5\%), the opinions of consumers of certain news deviate from the opinions of other citizens.
-This is even more severe for the 192 wave-paper combinations concerning the immigration or integration item used in the remainder of this study, where 18\% of all estimated DiDs fall under the 5\%-threshold\footnote{See plot in appendix \ref{}}.
+This is even more severe for the 192 wave-paper combinations concerning the immigration or integration item used in the remainder of this study, where 18\% of all estimated DiDs fall under the 5\%-threshold\footnote{See plot in appendix \ref{app:p-val_imm}}.
 This strongly indicates that news consumption matters for opinion formation and that the data shows variation which can be explained, despite highly parallel trends.
@@
 \subsection{Correlation of DiD with frame prevalence}
-% show correlation of DiD with prevalence of media frames (STM)
+
 \begin{figure}[!ht]
@@
 As figure \ref{fig:did_corr} shows, even with different specifications, \textit{no} estimate has predictive power for our analysis.
-For example, in the upper left panel 'crime', we can see 5 different lags 'g', '6m', '1m', '1w', '1d' distinguished vertically, and the effects for two different issues in the two different panes.
+For example, in the upper left panel 'crime', we can see four different lags indicating the frame prevalence of the past day, week, month, or half year (up to the last survey date) distinguished vertically, and the effects for two different issues in the two different panes.
 Additionally, the color of the points indicates whether the model was estimated only for readers of a single newspaper (lower N, but no treatment diffusion) or all readers of a newspaper (who might read another newspaper, say SZ readers who also read FAZ).
@@
 
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps_immint.png}
+    \caption{Empirical and theoretical p-values of 192 DiD-models corresponding to the immigration and integration questions of the GLES.}
+    \label{fig:my_label}
+\end{figure}
+
 \end{document}

### 2021-10-04 code/03_estimation.R
No rounding.

@@ -605,31 +605,31 @@ for (spec in c('absolute', 'share')){
                 respondents = respons,
                 specification = spec,
                 
-                beta_crime  = mod$coefficients['crime'] %>% round(3),
+                beta_crime  = mod$coefficients['crime'],
                 lower_beta_crime = confint(rawmod)['crime',1],
                 upper_beta_crime = confint(rawmod)['crime',2],
                 
-                beta_capcrime = mod$coefficients['capcrime'] %>% round(3),
+                beta_capcrime = mod$coefficients['capcrime'],
                 lower_beta_capcrime = confint(rawmod)['capcrime',1],
                 upper_beta_capcrime = confint(rawmod)['capcrime',2],
                 
-                beta_medit = mod$coefficients['medit'] %>% round(3),
+                beta_medit = mod$coefficients['medit'],
                 lower_beta_medit = confint(rawmod)['medit',1],
                 upper_beta_medit = confint(rawmod)['medit',2],
                 
-                beta_deport = mod$coefficients['deport'] %>% round(3),
+                beta_deport = mod$coefficients['deport'],
                 lower_beta_deport = confint(rawmod)['deport',1],
                 upper_beta_deport = confint(rawmod)['deport',2],
                 
-                beta_refnums = mod$coefficients['refnums'] %>% round(3),
+                beta_refnums = mod$coefficients['refnums'],
                 lower_beta_refnums = confint(rawmod)['refnums',1],
                 upper_beta_refnums = confint(rawmod)['refnums',2],
                 
-                beta_camps = mod$coefficients['camps'] %>% round(3),
+                beta_camps = mod$coefficients['camps'],
                 lower_beta_camps = confint(rawmod)['camps',1],
                 upper_beta_camps = confint(rawmod)['camps',2],
                 
-                beta_labmar = mod$coefficients['labmar'] %>% round(3),
+                beta_labmar = mod$coefficients['labmar'],
                 lower_beta_labmar = confint(rawmod)['labmar',1],
                 upper_beta_labmar = confint(rawmod)['labmar',2]
                 

### 2021-10-04 paper/main.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames_did.png}
-    \caption{Correlation of opinion shifts (DiDs) with media attention or shifts in attention (DiD's) for different specifications.}
+    \includegraphics[width=1.2\textwidth]{paper/vis/effectplot_frames_did.png}
+    \caption{Regression coefficients from DiD-models with different specifications.}
     \label{fig:did_corr}
@@
 This is however not the case.
-As figure \ref{fig:did_corr} shows, even with different specifications, \textit{no} estimate has predictive power for our analysis.
-For example, in the upper left panel 'crime', we can see four different lags indicating the frame prevalence of the past day, week, month, or half year (up to the last survey date) distinguished vertically, and the effects for two different issues in the two different panes.
+Figure \ref{fig:did_corr} shows standardised\footnote{Meaning that independent and dependent variables were mean-corrected and standardised before regression.
+A coefficient of one means that a one-standard-deviation shift in the independent variable corresponds to a one-standard deviation shift in the dependent variable.} regression coefficients for different specifications of the DiD-model.
+Each panel shows the effect of one frame on an attitude variable (controlling for all other frames), across different lags and different treatment definitions.
+For example, in the upper left panel 'crime', we can see two different panes ('immigration' and 'integration') for each dependent variable.
+The vertical rows distinguish four different lags indicating the frame prevalence of the past day, week, month, half year, or´the entire period up to the last survey date.
 Additionally, the color of the points indicates whether the model was estimated only for readers of a single newspaper (lower N, but no treatment diffusion) or all readers of a newspaper (who might read another newspaper, say SZ readers who also read FAZ).
-All estimates are clearly clustering around the null, indicating no effect.
+
+Only very few estimates are significant, but no trends emerge across specifications for any variable.
+All estimates are clearly clustering around zero, indicating no effect.
+Estimates of all relationship indicate both positive and negative relationships across specifications.
 While the 'exclusive reader' estimates show more variation, they also indicate far broader confidence intervals.
@@
 
-To corroborate these results, I estimate another model directly predicting individual migration opinions with a lagged dependent and individual estimates of consumed migration frames (see section \ref{sec:models}).
-The results for migration and integration attitudes can be seen in table \ref{tab:ind_model}.
-Maybe even more interesting, these frames differ for the two dependent variables.
-The effects for the frame variables can be read as "one standard deviation increase in frame attention increases the dependent variable by X points on a -3 to 3 scale".
-Note that higher values on the immigration variable indicate more restrictive attitudes, and vice versa for the integration variable.
-
-Surprisingly, several frames show highly significant results in this model.
-Additionally, these effects can be considered fairly large.
-For example, a one-standard deviation increase in the attention to refugee numbers in the preceding week (compared to a week preceding the last interview) moves respondents 0.328 points towards the \textit{liberal} end of the 7-point immigration attitude scale.
-Similarly, respondents move 1.12 points towards the restrictive pole when discussion of the humanitarian crisis in the Mediterranean Sea increases by one standard deviation, and 2.43 points when the labour market frame is increasingly discussed.
-Most interestingly, the labour market frame has the \textit{opposite} effect on integration attitudes, making people .34 points towards the liberal pole.
-Lastly, deportations have a slightly liberalising effect.
-None of these frames have the expected impact on opinions.
-Perhaps the clearest expectation can be formulated regarding the capital crime frame, which has pretty much no effect.
-
 \begin{figure}
@@
     \includegraphics[width=\textwidth]{paper/vis/effectplot_frames_fe_abs.png}
-    \caption{Caption}
-    \label{fig:mode_fe}
+    \caption{Regression coefficients from fixed-effects models with different specifications.}
+    \label{fig:model_fe}
 \end{figure}
+
+To corroborate these results, I estimate another model directly regressing individual migration opinions on individual estimates of consumed migration frames with fixed effects for survey wave and respondent.
+The results for migration and integration attitudes can be seen in figure \ref{fig:mode_fe}.
+
+Again, most estimates are not significant, differ in direction across specifications, and cluster around 0.
+While some estimates are unidirectional (crime and labour market in the immigration issue), they show tiny effects (a standard deviation increase in attention to the labour market ) and
 
@@
 
-It is unclear so far what to make of these results.
-While I am fairly certain that I need to re-assess the code, it seems that null effects dominate the (more identified) DiD-model, while the individual-level model shows odd, significant effects, highly dependent on model specifications.
-It might be that these effects are conditional, perhaps dependent on pre-existing immigration attitudes, issue importance, or partisanship.
-While these interactions do seem to have an effect, no clear narrative seems to emerge.
-For example, Petty Crime news are de-polarising, while news on capital crime by refugees affect opinions in a polarising way.
-If I settle on the first model and argue for null-effects, it is unclear how to present more evidence.
-Look for alternative explanation of opinion shifts?
-Assess effect on issue definitions, as initially planned?
-Show that strong shifts in frame attention drive people to stop reading the newspaper?
-Run an alternative model with 'right-wingness' of the migration discourse as main independent variable?
-
-It seems I have crashed.
+\newpage
 
@@
     \caption{Empirical and theoretical p-values of 192 DiD-models corresponding to the immigration and integration questions of the GLES.}
-    \label{fig:my_label}
+    \label{fig:p-val_imm}
 \end{figure}

### 2021-10-04 code/04_vis.R
Improve plot layout models

@@ -341,10 +341,10 @@ for (frame in c('crime', 'capcrime', 'refnums', 'medit', 'camps', 'labmar', 'dep
 }
 
 library(ggpubr)
-ggarrange(plotlist = plots, ncol = 2, nrow = 4, 
+ggarrange(plotlist = plots, ncol = 1, nrow = 7,
           common.legend = T, legend = "bottom") %>% 
   ggsave(filename = here("paper/vis/effectplot_frames_did.png"),
-         width = 10, height = 7)
+         width = 6, height = 12)
 
 
 
@@ -379,10 +379,10 @@ for (frame in c('crime', 'capcrime', 'refnums', 'medit', 'camps', 'labmar', 'dep
     theme_minimal()
 }
 
-ggarrange(plotlist = plots, 
+ggarrange(plotlist = plots, ncol = 2, nrow = 4,
           common.legend = T, legend = "bottom") %>% 
   ggsave(filename = here("paper/vis/effectplot_frames_fe_abs.png"),
-         width = 10, height = 7)
+         width = 7, height = 10)
 
 
 ## relative frame attention model
@@ -409,7 +409,7 @@ for (frame in c('salience', 'crime', 'capcrime', 'refnums', 'medit', 'camps', 'l
     theme_minimal()
 }
 
-ggarrange(plotlist = plots, 
+ggarrange(plotlist = plots,  nrow = 4, ncol = 2,
           common.legend = T, legend = "bottom") %>% 
   ggsave(filename = here("paper/vis/effectplot_frames_fe_rel.png"),
-         width = 10, height = 7)
+         width = 7, height = 10)

### 2021-10-04 paper/main.tex

@@
 Again, most estimates are not significant, differ in direction across specifications, and cluster around 0.
-While some estimates are unidirectional (crime and labour market in the immigration issue), they show tiny effects (a standard deviation increase in attention to the labour market ) and
+While some estimates are unidirectional (crime and labour market in the immigration issue), they show tiny effects (a standard deviation increase in attention to the labour market makes issue attitudes 0.015 standard deviations more conservative) and are usually not significant.
+Most importantly, both models do not correspond to expectations.
+This is probably most visible for the capital and sex crime frame ('capcrime'), which should show strongly positive effects (leading to more restrictive attitudes), but also for the illegal immigration and petty crime frame ('crime'), which shows consistently negative (i.e.
+liberalising) effects.
 

### 2021-11-01 paper/main.tex
Update abstract & title

--- 2021-10-04 paper/main.tex
@@
 \fancyhf{}
-\rhead{Media Framing and Issue Attitudes}
-\lhead{Nicolai Berk}
+\rhead{The Effect of News Framing}
+\lhead{Berk}
 \cfoot{\thepage}
@@
 
-\title{The Effect of Media Frames on Issue Attitudes}
+\title{The Effect of News Framing on Issue Attitudes and Voting Behaviour}
 \author{Nicolai Berk\footnote{Doctoral Candidate, Dynamics Doctoral Program, Humboldt-Universität zu Berlin, \href{mailto:nicolai.berk@hu-berlin.de}{nicolai.berk@hu-berlin.de}}}
-\date{September 2021}
+\date{October 2021}
 
@@
 
+% \begin{center}
+%     \textit{Manuscript prepared for the Empirical Political Science in Progress Colloquium at Humboldt University Berlin}
+% \end{center}
+
+\medskip
+
 \begin{abstract}
-    A large body of literature debates the existence and extent of effects of media framing on consumers' issue attitudes.
-Combining panel data from the German Longitudinal Election Study with a fine-grained analyses of media framing, I address this debate with observational data, providing evidence from 1,752 fixed-effect, difference-in-differences models suggesting systematic differences in newspaper readers' opinion shifts.
-Second, I present evidence that such changes in consumers' attitudes towards immigration surrounding the German national election 2017 did \textit{not} correspond to changes in the migration framing of consumed media outlets.
-The findings contribute to our understanding of opinion formation processes and the relevance of the news media in the 21st century.
+    A large body of literature debates the extent to which media consumption affects consumers' issue attitudes and voting behaviour in contemporary media environments.
+Studies supporting the minimal effects hypothesis have often used designs estimating the effects of novel, previously unconsumed content on participants' attitudes.
+However, experimental evidence suggests that media consumers discount the bias of different outlets.
+Additionally, most studies assume rather than measure the extent of newspaper bias.
+Combining panel data with state-of-the-art methods of text analysis and exploiting an editorial change, I address both shortcomings with observational data.
+Results across different specifications indicate that even when assessing within-newspaper changes in issue framing, no effect on attitudes or voting behaviour can be found.
+These findings add further evidence that media effects in the post-broadcast era are limited.
 \end{abstract}
@@
 What might explain these contradicting findings?
-Scope conditions for media effects seem to be surprisingly understudied given the contradicting body of evidence.
+Scope conditions of media effects seem to be surprisingly understudied given the contradicting body of evidence.
 \citeauthor{Chiang2011a} argue that endorsements from newspapers with ideological leanings neutral or opposite to the endorsed party/candidate should have stronger effects on voting behaviour, as voters discount the general bias of a newspaper (\citeyear{Chiang2011a}).
-\citeauthor{Spirig2020} shows that the takeover of a Swiss regional newspaper through a leading politician of the far-right and the subsequent change in its political slant had no effect on citizens' voting behaviour and suggests that this is a result of voters discounting the new owner's political slant and stopping to read the newspaper.
+\citeauthor{Durante2012} find that a rightwards shift in Italian public TV channels' slant after the takeover of the Berlusconi government led left-wing consumers to chose different outlets, rather than changing their political opinions  \citeyear{Durante2012}.
+\citeauthor{Spirig2020} shows that the takeover of a Swiss regional newspaper through a leading politician of the far-right and the subsequent change in its political slant had no effect on citizens' voting behaviour and suggests that this is a result of voters discounting the new owner's political slant and stopping to read the newspaper (\citeyear{Spirig2020}).
 
@@
 Different forms of frames have been conceptualised.
+Some readers might think of loss and gain frames, as used in the famous experiments by \citeauthor{Kahneman1979prospect} (\citeyear{Kahneman1979prospect}).
+Others will think of ’generic’ frames, which describe frames that can be applied in different contexts.
+For example, an election might be described as a ’horse race’, where parties strive to ’win’ by getting to ﬁrst place.
 When I talk about 'frames' here, I refer to \textit{emphasis frames}.
@@
 This model suggests that an attitude on a given issue is a function of two things: considerations and their respective weights.
-The evaluation of the issue is subdivided into a number of considerations (to which political scientists might refer as "valence issues"), that will be easier to evaluate.
+The evaluation of the issue is subdivided into a number of considerations (to which political scientists might refer as "valence issues"), which will be easier to evaluate.
 For example, to decide whether a lockdown is necessary to battle the spread of Covid-19 in one's country, a person might consider the detrimental short-term effect on businesses and individuals' mental health (negative considerations), as well as the cost of overburdened hospitals and additional deaths (positive considerations, at least with respect to the evaluation of a lockdown).
@@
 Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from the third with fewest migration terms, 100 from the third with most migration terms and 100 from the third in between) for each newspaper for a total of 1,800 papers.
-Then, a student assistant\footnote{Thank you Robin.} hand-coded these articles, assessing whether their main topic is related to migration.
+Then, a student assistant\footnote{Thank you, Robin.
+I know it was painful.} hand-coded these articles, assessing whether their main topic is related to migration.
 
@@
 While the first few months of 2017 show rather high salience of the issue, attention decreases until May, before the share of articles covering this issue increases again in all newspapers except \textit{Bild}, which shows a stark decrease in July and maintains this level afterward.
-Most newspapers show similar levels of attention to the issue between 2.5\% and 6\%, with the exception of \textit{SZ}, which moves between 5\% and 12.5\%.
+Most newspapers show similar levels of attention to the issue between 2.5\% and 6\% of all articles, with the exception of \textit{SZ}, which moves between 5\% and 12.5\%.
 
-\subsubsection{Measuring news frames}
+\subsubsection{Measuring news frames}\label{sec:frame_selection}
 
@@
     \item refugee numbers (topic 32),
-    \item labour market needs for and integration of refugees (topic 11),
+    \item labour market needs for and job market integration of refugees (topic 11),
     \item deportations (topic 44),
@@
 
-\subsection{Study design}
+\subsection{Estimation}
 
@@
 
-where $y$ is the dependent (attention to migration frame or migration opinion), $W$ indicates whether the interview took place ($W = 1$) in a given survey wave or in the preceding one ($W = 0$), and $R$ indicates whether the respondent is a reader of the newspaper of interest.
+where $y$ is the dependent (migration opinion), $W$ indicates whether the interview took place ($W = 1$) in a given survey wave or in the preceding one ($W = 0$), and $R$ indicates whether the respondent is a reader of the newspaper of interest.
 
@@
 I estimate the same DiDs to measure shifts in migration framing in a certain newspaper, controlling for shifts in all other newspapers.
-To do that, I first sum the attention given to a certain frame in a given newspaper in the past day, week, month, or half year, up to the last survey.
+To do that, I first sum the attention given to a certain frame in a given newspaper in the past day, week, month, or half year, up to the last survey wave.
 This allows me to assess whether choosing different lags affects my estimates.
@@
 
-Second, I fit individual-level fixed-effect models with individual news framing estimates for each survey interview.
+Second, I fit two-way fixed-effect models with individual news framing estimates for each survey interview.
 I measure exposure to each frame by summing up the frame attention of the past week (relative to the interview) in each newspaper the respondent claimed to have read in the past week and dividing it by the total number of newspapers read.
@@
 The fixed-effect models control for wave effects and (time-constant) individual characteristics, therefor restricting the explainable variance to everything beyond general trends and individual characteristics, but might include more noise.
-Another difference is that the DiD-models correlate relative shifts, while the fixed-effect models regress opinion levels on frame attention levels.
+Another difference is that the DiD-models correlate changes, while the fixed-effect models regress opinion levels on frame attention levels.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps.png}
-    \caption{Empirical and theoretical p-values of 1,752 DiD-models.}
+    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps_notheory.png}
+    \caption{P-values of 1,752 DiD-models estimating attitudinal shifts of media consumers, relative to consumers of other outlets.}
     \label{fig:p_values}
@@
 This means I use attitudinal questions on all political issues included in the GLES Panel (economic, issues, climate, ...), and assess whether news consumption matters for opinion formation more generally.
-The upper panel of figure \ref{fig:p_values} shows the distribution of p-values for the DiD-term from 1,752 fixed-effect models with GLES Panel data.
-The distribution shows a considerable deviation from the expected uniform distribution (visible in the lower panel) were there no explaining variation in the DiD-term beyond the uniform effects of wave and paper readership.
+Figure \ref{fig:p_values} shows the distribution of p-values for the DiD-term from 1,752 fixed-effect models with GLES Panel data.
+The distribution shows a considerable deviation from the expected uniform distribution (red line) were there no explaining variation in the DiD-term beyond the uniform effects of wave and paper readership.
 This means, more often than random (12\% vs 5\%), the opinions of consumers of certain news deviate from the opinions of other citizens.
@@
 
-\begin{figure}[!ht]
+There seems to be interesting variation in the dependent variable.
+Can these opinion shifts be explained by shifts in news content?
+Figure \ref{fig:did_corr} shows the core analysis to estimate the effect of migration framing on reader opinion.
+The displayed estimates are obtained by regressing the DiD-estimates for issue attitudes on the DiD-estimates for media attention, as described in section \ref{sec:models}.
+If opinion shifts among newspapers' readers - relative to other readers - can be explained by shifts in newspapers' issue framing, these two variables should be highly correlated.
+
+\begin{figure}
     \centering
-    \includegraphics[width=1.2\textwidth]{paper/vis/effectplot_frames_did.png}
+    \includegraphics[width=0.7\textwidth]{paper/vis/effectplot_frames_did.png}
     \caption{Regression coefficients from DiD-models with different specifications.}
@@
 
-There seems to be interesting variation in the dependent variable.
-Can these opinion shifts be explained by shifts in news content?
-Figure \ref{fig:did_corr} shows the core analysis to estimate the effect of media attention on reader opinion.
-The displayed estimates are obtained by regressing the resulting DiD-estimates for issue attitudes on the DiD-estimates for media attention.
-Each dot in this graph represents the coefficient of a model explaining standardised aggregate opinion shifts with standardised shifts in media attention to specific frames for a specific frame and a specific model specification, as outlined in section \ref{sec:models}.
-If opinion shifts among newspapers' readers - relative to other readers - can be explained by shifts in newspapers' issue framing, these two variables should be highly correlated.
-
 This is however not the case.
-Figure \ref{fig:did_corr} shows standardised\footnote{Meaning that independent and dependent variables were mean-corrected and standardised before regression.
-A coefficient of one means that a one-standard-deviation shift in the independent variable corresponds to a one-standard deviation shift in the dependent variable.} regression coefficients for different specifications of the DiD-model.
-Each panel shows the effect of one frame on an attitude variable (controlling for all other frames), across different lags and different treatment definitions.
+Each panel in figure \ref{fig:did_corr} shows the effect of one frame on an attitude variable (controlling for all other frames mentioned in section \ref{sec:frame_selection}), across different lags and treatment definitions.
+Each dot in this graph represents the coefficient of a model explaining standardised\footnote{Meaning that independent and dependent variables were mean-corrected and re-scaled to standard deviations before regression.
+A coefficient of one means that a one-standard-deviation shift in the independent variable corresponds to a one-standard deviation shift in the dependent variable.} aggregate opinion shifts with standardised shifts in media attention to specific frames.
 For example, in the upper left panel 'crime', we can see two different panes ('immigration' and 'integration') for each dependent variable.
-The vertical rows distinguish four different lags indicating the frame prevalence of the past day, week, month, half year, or´the entire period up to the last survey date.
+The vertical rows distinguish four different lags indicating the frame prevalence of the past day, week, month, half year, or the entire period up to the last survey date.
 Additionally, the color of the points indicates whether the model was estimated only for readers of a single newspaper (lower N, but no treatment diffusion) or all readers of a newspaper (who might read another newspaper, say SZ readers who also read FAZ).
 
-Only very few estimates are significant, but no trends emerge across specifications for any variable.
+Only very few estimates are significant and no trends emerge across specifications for any variable.
 All estimates are clearly clustering around zero, indicating no effect.
-Estimates of all relationship indicate both positive and negative relationships across specifications.
+Estimates of all relationships indicate both positive and negative relationships across specifications.
 While the 'exclusive reader' estimates show more variation, they also indicate far broader confidence intervals.
@@
 Generally, this analysis indicates no effect of media framing of migration on migration attitudes.
+
+To corroborate these results, I estimate another model directly regressing individual migration opinions on individual estimates of consumed migration frames with fixed effects for survey wave and respondent (see section \ref{sec:models}).
+The results for migration and integration attitudes can be seen in figure \ref{fig:model_fe}.
+
+Again, most estimates are not significant, differ in direction across specifications, and cluster around 0.
+While some estimates are unidirectional (crime and labour market in the immigration issue), they show tiny effects (a standard deviation increase in attention to the labour market makes issue attitudes between 0.005 and 0.015 standard deviations more conservative) and are usually not significant.
+Most importantly, both models do not correspond to expectations.
+This is probably most visible for the capital and sex crime frame ('capcrime'), which should show strongly positive effects (leading to more restrictive attitudes), but also for the illegal immigration and petty crime frame ('crime'), which consistently shows insignificant negative (i.e.
+liberalising) effects.
 
@@
 
-To corroborate these results, I estimate another model directly regressing individual migration opinions on individual estimates of consumed migration frames with fixed effects for survey wave and respondent.
-The results for migration and integration attitudes can be seen in figure \ref{fig:mode_fe}.
+\section{Discussion}
 
-Again, most estimates are not significant, differ in direction across specifications, and cluster around 0.
-While some estimates are unidirectional (crime and labour market in the immigration issue), they show tiny effects (a standard deviation increase in attention to the labour market ) and
+This paper assessed the responsiveness of newspaper consumers' migration attitudes to the migration framing of their respective newspaper.
+Aggregate difference-in-differences models and individual estimates show that consumers' opinions on immigration and integration were not reacting to changes in the newspaper framing of the respective issue.
+However, several alternative explanations are possible.
 
-\section{Discussion}
+Some other studies found that, instead of reacting with opinion shifts, readers might change their political preferences or mobilise to vote (\cite{Stetka2020}).
+Similarly, several studies indicate that changes in a media outlet's slant will result in a change in the composition of the consumers (ie those with conflicting attitudes stop reading the newspaper) rather than a change in a fixed readership's attitudes (\cite{Arceneaux2013, Durante2012, Spirig2020}).
+Whether similar effects can be observed when explicitly measuring newspaper framing are likely next steps for analysis.
+
+Another theoretical alternative might be the idea of \textit{issue evolution} (\cite{Carmines1986}).
+If a process of 'issue-sorting' took place in 2015, when the migration issue became very salient for the first time in a long time, citizens might have chosen a side and stuck to their opinion afterward.
+Hence, a second further avenue for analysis might look into opinion stability across a longer time horizon or a different case.
+
+On the empirical side, I cannot ensure that respondents actually received treatment when they say they read the newspaper.
+Some might only read the sports section, some might only read specific sub-issues (e.g.
+only the crime news about immigration, but not the news on migrants drowning in the Mediterranean).
+It also might be that survey responses regarding newspaper consumption are generally more statements of which paper respondents like rather than consume.
+It is therefor in no way clear whether the treatment actually reaches respondents, although similar studies connecting survey- and media data (\cite{Eberl2015}) have found effects of media content on attitudes and even voting behaviour.
+
+More could be done to measure emphasis frames as well.
+Recent innovations exploiting word embeddings are particularly noteworthy here, either extracting topics from the embedding space (\cite{Angelov2020, Urman2021}) or measuring conceptual associations across time with diachronic word embeddings (\cite{Rodman2019}).
+
+Beyond the improvement of the analysis, I could try to add a different case and/or exploit a natural experiment.
+The Bild had an editorial shift in 2017 which seems to have coincided with more emphasis of crime topics - in line with anecdotal evidence of the results of this change among journalists.
+Returning to an earlier framing of the paper, this case could be presented as additional evidence of null effects.
+It might also be possible to exploit the increasing attention to the climate issue in 2019 and again in 2020 to assess an opinion formation process from the beginning, although this would necessitate to leave the paper alone for a while, until the survey data is available.
+
+Lastly, if there were in fact no effect of news framing on respondents' attitudes towards migration, there is still a major open question: what does explain the variation that can be observed?
 
@@
 
+\newpage
+
 \subsection{Structural Topic Model}\label{app:stm}
@@
     \includegraphics[width=2\textwidth]{paper/vis/mig_topics_plot.png}
-    \label{fig:did_corr}
+    \label{fig:topics}
 \end{figure}
+
+\newpage
 

### 2022-06-28 code/old/04_vis.spin.Rmd
Update from December
Pray

```{r }
# ______________________________________________
# Effect of framing on issue attitudes
# Goal: Visualisation
# Procedure: Step 1, Step 2, Step 3
# ______________________________________________
# Date:  Thu Sep 09 17:46:22 2021
# Author: Nicolai Berk
#  R version 4.0.3 (2020-10-10)
# ______________________________________________

# Setup ####
library(tidyverse)
library(dplyr)
library(here)
library(data.table)
library(ggExtra)
library(glue)
library(haven)
library(gridExtra)
library(lubridate)
library(ggpubr)

# Step 1 ####

## 2.1 vis dependents ####

## load data
gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv'))

# ## immigration attitude across time
# imm_mean <- 
#   gles_p_long %>%
#   group_by(wave) %>% 
#   filter(!is.na(`1130_clean`)) %>% 
#   summarise(immigration = mean(`1130_clean`),
#             immigration_sd = sd(`1130_clean`),
#             date_clean  = max(date_clean),
#             respondents = n()) %>% 
#   mutate(
#     imm_up = (immigration + qt(1 - (0.05/2), respondents - 1)*immigration_sd/respondents),
#     imm_low = (immigration - qt(1 - (0.05/2), respondents - 1)*immigration_sd/respondents),
#   ) %>% 
#   ggplot(aes(x = date_clean)) +
#   geom_line(aes(y = immigration), col = "red") +
#   geom_ribbon(aes(ymax = imm_up, ymin = imm_low), fill = "red") +
#   ggtitle("Immigration attitude in Germany across time", 
#           "Should immigration of foreigners be made easier (-3) or restricted (3) \nData: GLES Panel, waves 1-13, a1 & a2")
# 
# ### exclusive readers
# 
# ## integration attitude across time
# int_mean <- 
#   gles_p_long %>%
#   group_by(wave) %>% 
#   filter(!is.na(`1210_clean`)) %>% 
#   summarise(integration = mean(`1210_clean`)*(-1),
#             integration_sd = sd(`1210_clean`),
#             date_new  = max(as.Date(date_clean, unit = 'days')),
#             respondents = n()) %>% 
#   mutate(
#     imm_up = (integration + qt(1 - (0.05/2), respondents - 1)*integration_sd/respondents),
#     imm_low = (integration - qt(1 - (0.05/2), respondents - 1)*integration_sd/respondents),
#   ) %>% 
#   ggplot(aes(x = date_new)) +
#   geom_line(aes(y = integration), col = "blue") +
#   geom_ribbon(aes(ymax = imm_up, ymin = imm_low), fill = "blue") +
#   ggtitle("Integration attitude in Germany across time", 
#           "Should foreigners be allowed to live according to their own culture (-3) or fully adapt to German culture (3) \nData: GLES Panel, waves 1-13, a1 & a2")
# 
# grid.arrange(imm_mean, int_mean, nrow = 2) %>% 
#   ggsave(here('paper/vis/dv_plot.png'), plot = .)

## average per paper
plots <- list()
for (issue in c('Immigration', 'Integration', 'AfD-support')){
  if (issue == 'Immigration'){
    gles_p_long[,'dv'] <- gles_p_long[,'1130_clean']
  }else if (issue == 'Integration'){
    gles_p_long[,'dv'] <- gles_p_long[,'1210_clean']*(-1)
  }else{
    gles_p_long[,'dv'] <- gles_p_long[,'430i_clean']
  }

  if (issue == 'Integration'){
    scale_desc <- "Should foreigners be allowed to live according to their own culture (-3)\n or fully adapt to German culture (3) \n"
  }else if (issue == 'Immigration'){
    scale_desc <- "Should immigration of foreigners be made easier (-3) or restricted (3) \n"
  }else{
    scale_desc <- "What do you think about the AfD? Don't like the party at all (-5),\n like the party a lot (5) \n"
  }

  temp <- 
    gles_p_long %>% 
    filter(!is.na(dv)) %>% 
    filter(wave %in% c(1, 3:8)) %>%  
    filter(most_read != "None") %>% 
    group_by(wave, most_read) %>% 
    summarise(dv_mean = mean(dv, na.rm = T),
              resps = n(),
              dv_sd = sd(dv, na.rm = T),
              date = max(date_clean))

  unique_waves <- paste(sort(unique(temp$wave)), collapse = ', ')

  plots[[issue]] <- 
    temp %>% 
    ggplot(
      aes(x = date, 
          y = dv_mean, 
          ymin = dv_mean +     qt((0.05/2), resps - 1)*dv_sd/resps, 
          ymax = dv_mean + qt(1 - (0.05/2), resps - 1)*dv_sd/resps, 
          col = most_read, 
          fill = most_read, 
          lty = most_read)) +
    geom_vline(xintercept = as.Date("2017-01-31"), col = "red", lty = 2) +
    geom_line() +
    geom_ribbon(alpha = 0.5) +
    theme_minimal() +
    xlab('') + ylab('')+
    ggtitle(glue("{issue} attitude among newspaper-readers"), 
            paste0(scale_desc, glue("Data: GLES Panel; waves {unique_waves}")))
}

ggarrange(plots[["Immigration"]], 
             plots[["Integration"]], 
             plots[["AfD-support"]], 
          nrow = 1, 
          common.legend = T, 
          legend = "bottom") %>% 
  ggsave(filename = here(glue('paper/vis/issues_most_read.png')),
         width = 15, height = 10)

# ### pivot long paper (multiple entries for respondents reading several newspapers)
# gles_p_long_paper <- 
#   gles_p_long %>% 
#   select(lfdn, wave, contains('clean')) %>% 
#   select(lfdn, wave, date_clean, contains('1661'), contains('1130'), contains('1210'), contains('430i')) %>% 
#   pivot_longer(cols = starts_with('1661'), names_prefix = '1661',
#                names_to = 'paper', values_to = 'days_read') %>% 
#   mutate(
#     paper = str_extract(paper, pattern = '.{1}')
#   )
# 
# ## adjust paper names
# gles_p_long_paper$paper[gles_p_long_paper$paper == 'a'] <- 'Bild'
# gles_p_long_paper$paper[gles_p_long_paper$paper == 'c'] <- 'FAZ'
# gles_p_long_paper$paper[gles_p_long_paper$paper == 'd'] <- 'SZ'
# gles_p_long_paper$paper[gles_p_long_paper$paper == 'e'] <- 'TAZ'
# gles_p_long_paper$paper[gles_p_long_paper$paper == 'f'] <- 'Welt'
# 
# gles_p_long_paper$reader <- gles_p_long_paper$days_read > 0
# 
# plots <- list()
# for (issue in c('Immigration', 'Integration', 'AfD-support')){
#   if (issue == 'Immigration'){
#     gles_p_long_paper['dv'] <- gles_p_long_paper['1130_clean']
#   }else if (issue == 'Integration'){
#     gles_p_long_paper['dv'] <- gles_p_long_paper['1210_clean']*(-1)
#   }else{
#     gles_p_long_paper['dv'] <- gles_p_long_paper['430i_clean']
#   }
#   
#   
#   temp <- 
#     gles_p_long_paper %>% 
#     filter(reader == T) %>% 
#     group_by(wave, paper) %>% 
#     filter(!is.na(dv)) %>% 
#     filter(!paper %in% letters) %>% 
#     summarise(dv_sd = sd(dv),
#               dv = mean(dv),
#               date_clean  = max(date_clean, na.rm = T),
#               respondents = n()) %>% 
#     mutate(
#       dv_up = (dv + qt(1 - (0.05/2), respondents - 1)*dv_sd/respondents),
#       dv_low = (dv - qt(1 - (0.05/2), respondents - 1)*dv_sd/respondents),
#     )
#   
#   unique_waves <- paste(sort(unique(temp$wave)), collapse = ', ')
#   
#   if (issue == 'Integration'){
#     scale_desc <- "Should foreigners be allowed to live according to their own culture (-3) or fully adapt to German culture (3) \n"
#   }else if (issue == 'Immigration'){
#     scale_desc <- "Should immigration of foreigners be made easier (-3) or restricted (3) \n"
#   }else{
#     scale_desc <- "What do you think about the AfD? Don't like the party at all (-5), like the party a lot (5) \n"
#   }
#   
#   plots[[issue]] <- 
#     ggplot(temp, aes(x = date_clean)) +
#     geom_line(aes(y = dv, col = paper)) +
#     geom_ribbon(aes(ymax = dv_up, ymin = dv_low, fill = paper), alpha = 0.5) +
#     xlab('') + ylab('')+
#     ggtitle(glue("{issue} attitude among newspaper-readers"), 
#             paste0(scale_desc, glue("Data: GLES Panel; waves {unique_waves}")))
#   
# 
# }
# 
# grid.arrange(plots[['Immigration']], plots[['Integration']]) %>% 
#   ggsave(filename = here(glue('paper/vis/issues_readers.png')),
#          width = 8, height = 8)
# 
# 
# ggsave(plot = plots[['Immigration']], 
#        here('pres/vis/imm_readers_pres.png'), width = 6, height = 4)
# 
# ggsave(plot = plots[['AfD-support']], 
#        here('pres/vis/afd_readers_pres.png'), width = 6, height = 4)

## 2.2 vis readership size ####

readers_survey <- 
  gles_p_long %>% 
  filter(wave == "1") %>% 
  group_by(most_read) %>% 
  summarise(count = n()) %>% 
  mutate(share = prop.table(count)) %>% 
  ggplot(aes(x = reorder(most_read, -share), y = share)) + 
  geom_bar(stat = "identity") +
  theme_minimal() +
  theme(legend.position = "None") +
  ylab("") + xlab("") +
  ggtitle("Most commonly read daily newspaper", "Data: GLES Panel; wave 1")

load("data/papers_dist.RDta")

auflage %>% 
  filter(Quarter == 20174) %>% 
  group_by(paper) %>% 
  summarise(count = n()) %>% 
  mutate(share = prop.table(count)) %>% 
  ggplot(aes(x = reorder(most_read, -share), y = share)) + 
  geom_bar(stat = "identity") +
  theme_minimal() +
  theme(legend.position = "None") +
  ylab("") + xlab("") +
  ggtitle("Print sales per newspaper", "Data: IVW 2021; First Quarter 2017")

## 2.3 vis independents ####

load(here('data/efftable_noimp.Rdata'))
survey_dates <- 
  gles_p_long %>% 
  filter(!is.na(date_clean)) %>% 
  filter(!is.na('1130_clean') | !is.na('1210_clean')) %>% 
  filter(date_clean >= as.Date('2017-01-01')) %>% 
  filter(date_clean < as.Date('2018-01-01')) %>% 
  group_by(wave) %>% 
  summarise(date = max(date_clean)) %>% 
  ungroup() %>% 
  select(date)

## salience over time
load(here('data/salience_cleaned.csv'))

salience_sum <- 
  salience_raw %>% 
  mutate(date_m = floor_date(date_new, 'month')) %>% 
  group_by(date_m, paper) %>% 
  summarise(
    n_mig = sum(mig),
    n_all = n()
  )

salience_sum <- 
  salience_sum %>% 
  mutate(
    share_mig = n_mig/n_all
  )

salience_sum %>% 
  filter(date_m < as.Date('2020-01-01')) %>% 
  ggplot(aes(x = date_m, y = share_mig, col = paper)) +
  geom_line() +
  geom_vline(xintercept = survey_dates$date, col = 'darkgray') +
  ggtitle('Migration salience in different newspapers', 'Gray lines indicate survey waves') +
  xlab('') + ylab('Share of migration articles')
ggsave(here('paper/vis/salience_papers.png'), width = 8, height = 5)

sal_2017 <- 
  salience_sum %>% 
  filter(date_m < as.Date('2018-01-01')) %>% 
  filter(date_m >= as.Date('2017-01-01')) %>% 
  ggplot(aes(x = date_m, y = share_mig, col = paper)) +
  geom_line() +
  geom_vline(xintercept = survey_dates$date, col = 'darkgray') +
  ggtitle('Migration salience in different newspapers', 'Gray lines indicate survey waves') +
  xlab('') + ylab('Share of migration articles')
ggsave(sal_2017, filename = here('paper/vis/salience_papers_focus.png'), 
       width = 8, height = 5)

## frames over time
load(here("data/media_daily_2021-10-03.Rdata"))

framing_sum <- 
  merged_media %>% 
  mutate(
    date = floor_date(as.Date(date_new), 'month')
  ) %>% 
  select(-date_new) %>% 
  group_by(paper, date) %>% 
  summarise_all(mean, na.rm = T) %>% 
  pivot_longer(cols = !c(date, paper, crime, n_tot, 
                         n_mig_fra, n_mig_sal, share_mig,
                         medit, deport, refnums, camps, 
                         labmar, capcrime), 
               names_to = 'frame', values_to = 'attention') %>% 
  mutate(paper = recode(paper, 
                        'bild' = 'Bild', 'faz' = 'FAZ', 'spon' = 'Spiegel',
                        'sz' = 'SZ', 'taz' = 'TAZ', 'welt' = 'Welt'
                        )) %>% 
  mutate(frame = recode(frame,
                        'camps_share' = 'Camps', 'crime_share' = 'Petty Crime',
                        'capcrime_share' = 'Capital Crime', 'deport_share' = 'Deportations',
                        'labmar_share' = 'Labour Market', 'medit_share' = 'Mediterranean',
                        'refnums_share' = 'Refugee Numbers'
                        ))

framing_sum %>% 
  filter(date < as.Date('2020-01-01')) %>%
  group_by(paper, frame) %>% 
  ggplot(aes(x = date, y = attention, col = frame)) +
  geom_line() +
  facet_grid(paper~frame, scales = 'free') +
  ggtitle('Migration framing in different newspapers') +
  ylab('Share of all migration articles') +
  xlab('') + theme(legend.position = "none")
ggsave(here('paper/vis/frames_papers.png'), width = 10, height = 6)

## presi version
framing_sum %>% 
  filter(date < as.Date('2020-01-01')) %>%
  filter(paper %in% c("Bild", "SZ")) %>% 
  filter(frame %in% c("Camps", "Capital Crime", "Mediterranean", "Petty Crime")) %>% 
  group_by(paper, frame) %>% 
  ggplot(aes(x = date, y = attention, col = frame)) +
  geom_line() +
  facet_wrap(~paper, scales = 'free', nrow = 2) +
  ggtitle('Migration framing in different newspapers') +
  ylab('Share of all migration articles') +
  xlab('') +
  labs(col = "Frame")
ggsave(here('pres/vis/frames_papers_pres.png'), width = 8, height = 5)

framing_sum %>% 
  filter(date < as.Date('2018-01-01')) %>%
  filter(date > as.Date('2017-01-01')) %>% 
  filter(paper %in% c("Bild", "SZ")) %>% 
  filter(frame %in% c("Camps", "Capital Crime", "Mediterranean", "Petty Crime")) %>% 
  group_by(paper, frame) %>% 
  ggplot(aes(x = date, y = attention, col = frame)) +
  geom_line() +
  facet_wrap(~paper, scales = 'free', nrow = 2) +
  ggtitle('Migration framing in different newspapers') +
  ylab('Share of all migration articles') +
  xlab('') +
  labs(col = "Frame")
ggsave(here('pres/vis/frames_papers_focus_pres.png'), width = 8, height = 5)
ggsave(here('paper/vis/frames_papers_focus.png'), width = 10, height = 6)

# effect of Diekmann leaving
framing_sum %>% 
  filter(date < as.Date('2020-01-01')) %>%  
  filter(paper %in% c("Bild", "Welt")) %>% 
  filter(frame %in% c("Camps", "Capital Crime", "Mediterranean", "Petty Crime")) %>%
  group_by(paper, frame) %>% 
  ggplot(aes(x = date, y = attention, col = frame)) +
  geom_line() +
  geom_smooth() +
  geom_vline(xintercept = as.Date('2017-01-31'), lty = 2, col = 'red') +
  facet_grid(frame~paper, scales = "free_y") +
  xlab('') + theme(legend.position = "none")
ggsave(here('pres/vis/frames_bild_diekmann_pres.png'), width = 8, height = 5)
ggsave(here('paper/vis/frames_bild_diekmann.png'), width = 10, height = 6)

framing_sum %>% 
  filter(date < as.Date('2018-01-01')) %>% 
  filter(date >= as.Date('2017-01-01')) %>% 
  group_by(paper, frame) %>% 
  ggplot(aes(x = date, y = attention, col = frame)) +
  geom_line() +
  geom_rug(data = survey_dates, aes(x = date),sides = 't', inherit.aes = F) +
  facet_grid(paper~frame, scales = 'free') +
  ggtitle('Migration frames in different newspapers 2017', 'Black ticks indicate survey waves') +
  scale_x_date(date_labels = '%b') +
  ylab('Share of all migration articles') +
  xlab('') + theme(legend.position = "none")
ggsave(here('pres/vis/frames_papers_focus_pres.png'), width = 8, height = 5)
ggsave(here('paper/vis/frames_papers_focus.png'), width = 10, height = 6)

## 2.3 vis p-values attitude did ####
attitude_dids <- read.csv(here('data/coeftable_gles_noimp.csv'))

attitude_dids$sig_fe <- (attitude_dids$p_fe < 0.05)
attitude_dids$sig_lm <- (attitude_dids$p_lm < 0.05)

prop.table(table(attitude_dids$sig_fe)) %>% round(2) # 12% instead of 5% -> significant effects overrepresented

attitude_dids %>% 
  ggplot(aes(x = p_fe, y = ..count../nrow(attitude_dids))) +
  geom_histogram(bins = 20, col = 'gray', breaks = seq(from = 0, to = 0.95, 0.05)) +
  geom_hline(aes(yintercept = 0.05), col = 'red', lty = 2) +
  ylim(0, 0.25) +
  ylab('Density')+xlab('p')+
  ggtitle(glue("P-values from {nrow(attitude_dids)} fixed-effect DiD-models"), 
          "Treatment = wave, condition = media outlet consumption")
ggsave(filename = here("paper/vis/DiD_model_ps_notheory.png"),
       width = 8, height = 3)

# theoryplot <- data.frame(p = runif(1336, 0, 1)) %>% 
#   ggplot(aes(x = p, y = ..count../1336)) +
#   geom_histogram(bins = 20, col = 'gray', breaks = seq(from = 0, to = 0.95, 0.05)) +
#   geom_hline(aes(yintercept = 0.05), col = 'red', lty = 2) +
#   ylim(0, 0.25) +
#   ylab('Density')+xlab('p')+
#   ggtitle(glue("Theoretical distribution of p-values with no effect of media consumption"))
# 
# gridExtra::grid.arrange(fe_plot, theoryplot, nrow = 2) %>% 
#   ggsave(plot = ., 
#          filename = here("paper/vis/DiD_model_ps.png"),
#          width = 8, height = 6)

## migration and integration only
mig_dids <- 
  attitude_dids %>% 
  filter(issue == '1130' | issue == '1210')

prop.table(table(mig_dids$sig_fe)) %>% round(2) # 18% instead of 5% -> significant effects overrepresented

mig_dids %>% 
  ggplot(aes(x = p_fe, y = ..count../nrow(mig_dids))) +
  geom_histogram(bins = 20, col = 'gray', breaks = seq(from = 0, to = 0.95, 0.05)) +
  geom_hline(aes(yintercept = 0.05), col = 'red', lty = 2) +
  ylim(0, 0.25) +
  ylab('Density')+xlab('p')+
  ggtitle(glue("P-values from {nrow(mig_dids)} fixed-effect DiD-models of migration attitudes"), 
          "Treatment = wave, condition = media outlet consumption")
ggsave(filename = here("paper/vis/DiD_model_ps_immint_notheory.png"),
       width = 8, height = 3)

## look at attitude dids across treatment specifications
mig_dids$respondents[mig_dids$respondents == 'only readers'] <- 'all readers'

mig_dids %>% 
  ggplot(aes(x = p_fe, y = ..count../(nrow(mig_dids)/2))) +
  geom_histogram(bins = 20, col = 'gray', breaks = seq(from = 0, to = 0.95, 0.05)) +
  geom_hline(aes(yintercept = 0.05), col = 'red', lty = 2) +
  ylab('Density')+xlab('p')+
  facet_grid(~respondents)+
  ggtitle(glue("P-values from {nrow(mig_dids)} fixed-effect DiD-models of migration attitudes"), 
          "Treatment = wave, condition = media outlet consumption")
ggsave(filename = here("paper/vis/DiD_model_ps_immint_bytreat.png"),
       width = 8, height = 3)

## afd-support
afd_dids <- 
  attitude_dids %>% 
  filter(issue == '430i')

prop.table(table(afd_dids$sig_fe)) %>% round(2) # 8% instead of 5% -> significant effects overrepresented

afd_dids %>% 
  ggplot(aes(x = p_fe, y = ..count../nrow(afd_dids))) +
  geom_histogram(bins = 20, col = 'gray', breaks = seq(from = 0, to = 0.95, 0.05)) +
  geom_hline(aes(yintercept = 0.05), col = 'red', lty = 2) +
  ylim(0, 0.25) +
  ylab('Density')+xlab('p')+
  ggtitle(glue("P-values from {nrow(afd_dids)} fixed-effect DiD-models of migration attitudes"), 
          "Treatment = wave, condition = media outlet consumption")
ggsave(filename = here("paper/vis/DiD_model_ps_afd_notheory.png"),
       width = 8, height = 3)

## look at attitude dids across treatment specifications
afd_dids$respondents[afd_dids$respondents == 'only readers'] <- 'all readers'

afd_dids %>% 
  ggplot(aes(x = p_fe, y = ..count../(nrow(afd_dids)/2))) +
  geom_histogram(bins = 20, col = 'gray', breaks = seq(from = 0, to = 0.95, 0.05)) +
  geom_hline(aes(yintercept = 0.05), col = 'red', lty = 2) +
  ylab('Density')+xlab('p')+
  facet_grid(~respondents)+
  ggtitle(glue("P-values from {nrow(afd_dids)} fixed-effect DiD-models of migration attitudes"), 
          "Treatment = wave, condition = media outlet consumption")
ggsave(filename = here("paper/vis/DiD_model_ps_afd_bytreat.png"),
       width = 8, height = 3)

## vis effects across specifications ####
load(here('data/efftable_did_2021-10-25.Rdata'))
efftable$dv_lag_f <- factor(efftable$dv_lag, levels = c('all', '6m', '1m', '1w', '1d'))

plots <- list()
for (frame in c('crime', 'capcrime', 'refnums', 'medit', 'camps', 'labmar', 'deport')){

  plots[[frame]] <- 
    efftable %>% 
    ggplot(mapping = 
             aes_string(
              x = paste0('beta_', frame), 
              y = 'dv_lag_f', 
              xmin = paste0('lower_beta_', frame),
              xmax = paste0('upper_beta_', frame),
              col = 'respondents'
            )) +
    geom_vline(aes(xintercept = 0), col = "red", lty = 2) +
    geom_pointrange(size = 0.3, position = ggstance::position_dodgev(height = 0.75)) +
    facet_grid( ~ dv) +
    xlab("Beta") +
    ylab("") +
    ggtitle(frame) +
    theme_minimal() +
    coord_cartesian(xlim = c(-2, 2))
}

library(ggpubr)
ggarrange(plotlist = plots, ncol = 1, nrow = 7,
          common.legend = T, legend = "bottom") %>% 
  ggsave(filename = here("paper/vis/effectplot_frames_did.png"),
         width = 9, height = 12)

## individual fe model
load(here('data/efftable_fe_2021-10-25.Rdata'))
efftable$dv_lag_f <- factor(efftable$dv_lag, levels = c('30d', '7d'))

## absolute frame attention model
plots <- list()
for (frame in c('crime', 'capcrime', 'refnums', 'medit', 'camps', 'labmar', 'deport')){

  plots[[frame]] <- 
    efftable %>% 
    filter(specification == 'absolute') %>%
    ggplot(mapping = 
             aes_string(
               x = paste0('beta_', frame), 
               y = 'dv_lag_f', 
               xmin = paste0('lower_beta_', frame),
               xmax = paste0('upper_beta_', frame),
               col = 'respondents'
             )) +
    geom_vline(aes(xintercept = 0), col = "red", lty = 2) +
    geom_pointrange(size = 0.3, position = ggstance::position_dodgev(height = 0.75)) +
    facet_grid( ~ dv, scales = 'free') +
    xlab("Beta") +
    ylab("") +
    ggtitle(frame) +
    theme_minimal()
}

ggarrange(plotlist = plots, ncol = 2, nrow = 4,
          common.legend = T, legend = "bottom") %>% 
  ggsave(filename = here("paper/vis/effectplot_frames_fe_abs.png"),
         width = 10, height = 10)

## relative frame attention model
plots <- list()
for (frame in c('salience', 'crime', 'capcrime', 'refnums', 'medit', 'camps', 'labmar', 'deport')){

  plots[[frame]] <- 
    efftable %>% 
    filter(specification == 'share') %>% 
    ggplot(mapping = 
             aes_string(
               x = paste0('beta_', frame), 
               y = 'dv_lag_f', 
               xmin = paste0('lower_beta_', frame),
               xmax = paste0('upper_beta_', frame),
               col = 'respondents'
             )) +
    geom_vline(aes(xintercept = 0), col = "red", lty = 2) +
    geom_pointrange(size = 0.3, position = ggstance::position_dodgev(height = 0.75)) +
    facet_grid( ~ dv, scales = 'free') +
    xlab("Beta") +
    ylab("") +
    ggtitle(frame) +
    theme_minimal()
}

ggarrange(plotlist = plots,  nrow = 4, ncol = 2,
          common.legend = T, legend = "bottom") %>% 
  ggsave(filename = here("paper/vis/effectplot_frames_fe_rel.png"),
         width = 7, height = 10)

## for presi: visualise effect distribution

### did model
load(here('data/efftable_did_2021-10-25.Rdata'))
efftable %>% 
  select(!contains("lower")) %>% 
  select(!contains("upper")) %>% 
  pivot_longer(cols = contains("beta"), names_to = "frame", names_prefix = "beta_") %>%
  mutate(frame = recode(frame,
                        'camps_share' = 'Camps', 'crime_share' = 'Petty Crime',
                        'capcrime_share' = 'Capital Crime', 'deport_share' = 'Deportations',
                        'labmar_share' = 'Labour Market', 'medit_share' = 'Mediterranean',
                        'refnums_share' = 'Refugee Numbers'
  )) %>% 
  filter(frame != "salience") %>% 
  ggplot(aes(x = value, y = frame, col = frame)) +
  geom_violin() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  xlab("Standardised Effect") + ylab("Frame") +
  ggtitle("Framing effects in DiD-models across specifications") +
  theme(legend.position = "None") +
  facet_wrap(~dv, scales = "free")
ggsave(here("pres/vis/frame_effects_did.png"), width = 8, height = 5)

### fe model
load(here('data/efftable_fe_2021-10-25.Rdata'))
efftable %>% 
  select(!contains("lower")) %>% 
  select(!contains("upper")) %>% 
  pivot_longer(cols = contains("beta"), names_to = "frame", names_prefix = "beta_") %>%
  mutate(frame = recode(frame,
                        'camps_share' = 'Camps', 'crime_share' = 'Petty Crime',
                        'capcrime_share' = 'Capital Crime', 'deport_share' = 'Deportations',
                        'labmar_share' = 'Labour Market', 'medit_share' = 'Mediterranean',
                        'refnums_share' = 'Refugee Numbers'
  )) %>% 
  filter(frame != "salience") %>% 
  ggplot(aes(x = value, y = frame, col = frame)) +
  geom_violin() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  xlab("Standardised Effect") + ylab("Frame") +
  ggtitle("Framing effects in 2-way FE-models across specifications") +
  theme(legend.position = "None") +
  facet_wrap(~dv, scales = "free")
ggsave(here("pres/vis/frame_effects_fe.png"), width = 8, height = 5)
```

---
title: 04_vis.R
author: nicol
date: '2021-11-29'

---

### 2022-06-28 code/old/news_framing.Rmd
Update from December
Pray

---
title: "Factor analysis migration framing"
author: "Nicolai Berk"
date: "7 7 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = T)

# import libraries
library(dplyr)
library(tidyr)
library(stringr)
library(tidytext)
library(data.table)
library(here)
library(stm)

# library(psych)
# library(GPArotation)
# library(psy)
# library(corrplot)
# library(anacor)

# load data
mig_dta <- fread(here("data/_migration_btgrams.csv")) # migration articles with bi- and trigram dtm

# clean
mig_dta$paper[mig_dta$paper == "weltonline"] <- "welt"
mig_dta$date_new <- NA
mig_dta$date_new[mig_dta$paper == "bild"] <- mig_dta$date[mig_dta$paper == "bild"] %>% as.Date()
mig_dta$date_new[mig_dta$paper == "faz"] <- mig_dta$date[mig_dta$paper=="faz"] %>% as.integer() %>% lubridate::days() + as.Date("1970-01-01")
mig_dta$date_new[mig_dta$paper == "spon"] <- mig_dta$date[mig_dta$paper=="spon"] %>% as.Date(format = "%d.%m.%Y")
mig_dta$date_new[mig_dta$paper == "sz"] <- mig_dta$date[mig_dta$paper=="sz"] %>% as.integer() %>% lubridate::days() + as.Date("1970-01-01")
mig_dta$date_new[mig_dta$paper == "taz"] <- mig_dta$date[mig_dta$paper=="taz"] %>% as.integer() %>% lubridate::days() + as.Date("1970-01-01")
mig_dta$date_new[mig_dta$paper == "welt"] <- mig_dta$date[mig_dta$paper=="welt"] %>% as.integer() %>% lubridate::days() + as.Date("1970-01-01")
mig_dta$date_new <- as.Date(mig_dta$date_new, origin = '1970-01-01')
mig_dta <- mig_dta[mig_dta$date_new > as.Date('2010-01-01'),]

```

<!-- ## Factor analysis -->

<!-- ```{r preprocessing} -->
<!-- items <- mig_dta[complete.cases(mig_dta[, 9:(ncol(mig_dta)-1)]), 9:(ncol(mig_dta)-1)] -->

<!-- # smoothing -->
<!-- items <- items + .01 -->
<!-- items <- log(items/sum(items)) -->

<!-- cormtrx <- cor(items) -->

<!-- ``` -->

<!-- Calculate eigenvalues -->
<!-- ```{r eigen} -->
<!-- # eigen_d <- eigen(cormtrx) -->
<!-- # sum(eigen_d$values > 1.5) -->
<!-- # nfactors(items) -->
<!-- ``` -->

<!-- Scree plot -->
<!-- ```{r scree} -->
<!-- scree.plot(eigen_d$values, type = "E") -->
<!-- scree.plot(eigen_d$values[1:100], type="E") -->
<!-- scree.plot(eigen_d$values[1:50], type="E")  -->

<!-- ``` -->

<!-- No clear elbow, far too many factors with eigenvalue $>$ 1.5, trying with 8 factors for now based on scree plot. -->

<!-- ```{r fa_model} -->
<!-- # fa_model <- fa(cormtrx, n.obs = nrow(items), nfactors=8, use = "pairwise.complete.obs") -->
<!-- fa_model <- factanal(items, 8, rotation="varimax") -->

<!-- ``` -->

<!-- Are the factors meaningful? - assessment of 20 items with highest correlation for each factor -->

<!-- ```{r fa_asses} -->

<!-- ``` -->

<!-- ## Correspondence Analysis -->

<!-- Since factor analysis doesn't seem to work at the moment, we'll try to make do with correspondence analysis, as suggested by @Lowe2016. -->

<!-- [Try to figure out how to plot sigma (canonical correlation), see @Lowe2016, Fig. 3] -->

<!-- ```{r ca} -->
<!-- res <- anacor(cormtrx) -->
<!-- summary(res) -->

<!-- ``` -->

## STM

As I am interested in different topics within the discourse about immigration rather than the different positions on immigration, I opt for the commonly used STM (Stewart 2016).

```{r stm}

## assess token count
token_count <- mig_dta[,9:(ncol(mig_dta)-1)] %>% 
  colSums()
names(token_count) <- colnames(items)
token_count %>% sort(decreasing = T) %>% head(30)

## pre-processing
mig_dta <- mig_dta[complete.cases(mig_dta),]
mig_dta <- mig_dta[rowSums(mig_dta[, 9:(ncol(mig_dta)-1)]) > 0, ] # drop empty documents
meta <- mig_dta[, c('date_new', 'paper')]
mig_dtm <- quanteda::as.dfm(mig_dta[, 9:(ncol(mig_dta)-1)])

stm_model <- stm(documents = mig_dtm,
                 K = 0, # sets an ideal number of topics, however should be tested with searchK()
                 prevalence =~ paper * date_new, 
                 max.em.its = 75, 
                 data = meta, 
                 init.type = "Spectral")

labelTopics(stm_model)

```

## Migration Framing of Bild vs others

## AfD slant in migration coverage

### 2022-06-28 code/old/news_framing_from_scratch.Rmd
Update from December
Pray

---
title: "Migration Framing"
author: "Nicolai Berk"
date: "7 8 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(dplyr)
library(tidyverse)
library(data.table)
library(here)
library(stm)
library(lubridate)
library(tidytext)
library(stopwords)

```

Since factor analysis, correspondence analysis and the structural topic model failed to run on the bi- & trigram matrix, I will estimate a classic structural topic model (yes, I can hear you booing) in the hope to get a little fancier with word embeddings later. I follow Julia Silge's tutorial [here](https://juliasilge.com/blog/sherlock-holmes-stm/).

```{r load}

# load the preselected migration articles
mig_texts_raw <- fread(here('data/_migration_articles_new.csv'), encoding = 'UTF-8') %>% as_tibble()

# use subsample for now
# mig_texts_raw <- mig_texts_raw[sample(1:nrow(mig_texts_raw), 10000),]

# fix dates
mig_texts_raw$paper[mig_texts_raw$paper == "weltonline"] <- "welt"
mig_texts_raw$date_new <- NA_Date_
mig_texts_raw$date_new[mig_texts_raw$paper == "bild"] <- mig_texts_raw$date[mig_texts_raw$paper == "bild"] %>% as.Date()
mig_texts_raw$date_new[mig_texts_raw$paper == "faz"] <- mig_texts_raw$date[mig_texts_raw$paper=="faz"] %>% as.numeric() %>% as.Date(origin = "1970-01-01")
mig_texts_raw$date_new[mig_texts_raw$paper == "spon"] <- mig_texts_raw$date[mig_texts_raw$paper=="spon"] %>% as.Date(format = "%d.%m.%Y")
mig_texts_raw$date_new[mig_texts_raw$paper == "sz"] <- mig_texts_raw$date[mig_texts_raw$paper=="sz"] %>% as.integer() %>% as.Date(origin = "1970-01-01")
mig_texts_raw$date_new[mig_texts_raw$paper == "taz"] <- mig_texts_raw$date[mig_texts_raw$paper=="taz"] %>% as.integer() %>% as.Date(origin = "1970-01-01")
mig_texts_raw$date_new[mig_texts_raw$paper == "welt"] <- mig_texts_raw$date[mig_texts_raw$paper=="welt"] %>% as.integer() %>% as.Date(origin = "1970-01-01")
mig_texts_raw <- mig_texts_raw[mig_texts_raw$date_new > as.Date('2010-01-01'),]

## check uniqueness of articles
# length(unique(mig_texts_raw$url)) # some duplicates

## load german stopwords
german_stopwords <- data.frame(word = stopwords("de"), stringsAsFactors = F)

## preprocess: sort out non-unique cases, tokenize, remove stopwords
mig_texts_tidy <- mig_texts_raw %>%
  group_by(url) %>% 
  summarise(date_new = first(date_new),
            paper = first(paper),
            title = first(title),
            text = first(text)
            ) %>%
  mutate(article = row_number()) %>% 
  unnest_tokens(word, text) %>% 
  anti_join(german_stopwords) %>% 
  filter(!word %in% c('dass', 'sagte', 'sagt', 'sei')) # missing in stopwords

mig_dfm <- mig_texts_tidy %>% 
  count(article, word, sort = T) %>% 
  cast_dfm(article, word, n)

topic_model <- stm(mig_dfm, K = 100, init.type = 'Spectral') # k = 0 chooses optimal number of topics 
summary(topic_model)

```

### 2022-06-28 code/old/robust.Rmd
Update from December
Pray

---
title: "Robustness and additional estimates"
author: "Nicolai Berk"
date: "14 3 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, cache = T, fig.align='center', eval = T, dev = "svg")
# knitr::opts_knit$set(root.dir = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild')

library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)
library(lubridate)
library(patchwork)
```

## Why is the direct effect of the crime treatment negative? Shouldn't it be positive?

### Standard model

```{r}
gles_p_long <- fread('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/gles/Panel/long_cleaned.csv')

gles_p_long$dv <- gles_p_long$`1130_clean`
gles_p_long$treat <- gles_p_long$`1661a_clean` > 0
gles_p_long$treat[is.na(gles_p_long$`1661a_clean`)] <- NA

gles_p_long$post <- gles_p_long$date_clean>= as.Date("2017-02-01")
gles_p_long <- 
  gles_p_long %>% 
  select(lfdn, date_clean, `1130_clean`) %>% 
  filter(!is.na(`1130_clean`)) %>% 
  arrange(lfdn, date_clean) %>% 
  group_by(lfdn) %>% 
  slice(1) %>% 
  mutate(init_mig = `1130_clean`) %>% 
  select(lfdn, init_mig) %>% 
  right_join(gles_p_long, by = "lfdn")

gles_p_long <- 
  gles_p_long %>% 
  mutate(mip_mig_crime_lag = lag(mip_mig_crime)) %>% 
  filter(!is.na(mip_mig_crime)) %>% 
  arrange(lfdn, date_clean) %>% 
  group_by(lfdn) %>% 
  slice(1) %>% 
  mutate(mip_mig_crime_init = mip_mig_crime) %>% 
  select(lfdn, mip_mig_crime_init) %>% 
  right_join(gles_p_long, by = "lfdn")

gles_p_long_1617 <- 
  gles_p_long %>% 
        filter(date_clean >= as.Date("2016-01-01"),
               date_clean <  as.Date("2018-01-01"))
rm(gles_p_long)

# model 1: direct effect
ate <- 
  feglm(dv ~ post * treat | lfdn, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

inter <- 
  feglm(dv ~ post * treat * init_mig, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

points <- ate$coefficients
ests <- cbind(points, confint(ate))
plot_did_ate <- 
  ests %>% 
  # mutate(name = factor(row.names(.), levels = row.names(.))) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(row.names(ests)),
                   labels = rev(c("Post", "Treatment", "Post X Treatment")))

points <- inter$coefficients
ests <- cbind(points, confint(inter))

plot_did_inter <- 
  ests %>% 
  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig")) %>% 
  mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
  ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("DiD-estimate with interaction") +
  xlim(-0.1, 0.4) + 
  scale_y_discrete(labels = rev(c("Post X Treatment", "Post X Treatment X Initial Opinion")))

plot_did_ate/plot_did_inter

```

## Direct effect, controlling for initial attitude

```{r}

ctrl <- 
  feglm(dv ~ post * treat + init_mig, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

points <- ctrl$coefficients
ests <- cbind(points, confint(ctrl))
plot_did_ctrl <- 
  ests %>% 
  mutate(name = factor(row.names(.), levels = row.names(.))) %>%
  filter(!name %in% c("", "(Intercept)", "init_mig")) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(row.names(ests)[!row.names(ests) %in% c("", "(Intercept)", "init_mig")]),
                   labels = rev(c("Post", "Treatment", "Post X Treatment"))) +
  xlim(-0.1, 0.4) + 
  ggtitle("Controlling for initial attitude")

plot_did_ctrl

```

## Distribution of Bild readers on pre-treatment outcome

```{r}

bild_readers <- 
  gles_p_long_1617 %>% 
  arrange(lfdn, date_clean) %>% 
  group_by(lfdn) %>% 
  slice(1) %>% 
  filter(`1661a_bin`) %>% 
  ggplot(aes(x = `1130_clean`, after_stat(density))) +
  geom_histogram(binwidth = .5) + 
  ggtitle("Bild readers") + xlab("") +
  theme_minimal() +
  ylim(0, 0.75)

rest_readers <- 
  gles_p_long_1617 %>% 
  arrange(lfdn, date_clean) %>% 
  group_by(lfdn) %>% 
  slice(1) %>% 
  filter(!`1661a_bin`) %>% 
  ggplot(aes(x = `1130_clean`, after_stat(density))) +
  geom_histogram(binwidth = .5) + 
  ggtitle("Not bild readers") +xlab("") +
  theme_minimal() +
  ylim(0, 0.75)

bild_readers/rest_readers

```

## estimate effect based on pre-treatment groups

```{r}

gles_p_long_1617 <- 
  gles_p_long_1617 %>% 
  filter(wave == "1") %>% 
  mutate(bild_init = ifelse(is.na(`1661a_clean`), NA, `1661a_clean` > 0)) %>% 
  select(bild_init, lfdn) %>% 
  right_join(gles_p_long_1617, by = "lfdn")

treat_alt_ate <- 
  feglm(dv ~ post * bild_init, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

points <- treat_alt_ate$coefficients
ests <- cbind(points, confint(treat_alt_ate))
plot_did_alt_ate <- 
  ests %>% 
  mutate(name = factor(row.names(.), levels = row.names(.))) %>%
  filter(!name %in% c("", "(Intercept)", "init_mig")) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(row.names(ests)[!row.names(ests) %in% c("", "(Intercept)", "init_mig")]),
                   labels = rev(c("Post", "Treatment", "Post X Treatment"))) +
  xlim(-0.1, 0.4) + 
  ggtitle("Controlling for initial attitude")

plot_did_alt_ate

```

## interaction with alternative treatment definition

```{r}

treat_alt_inter <- 
  feglm(dv ~ post * bild_init * init_mig, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

points <- treat_alt_inter$coefficients
ests <- cbind(points, confint(treat_alt_inter))
plot_did_alt_inter <- 
  ests %>% 
  mutate(name = factor(row.names(.), levels = row.names(.))) %>%
  filter(name %in% c("postTRUE:bild_initTRUE", "postTRUE:bild_initTRUE:init_mig")) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(row.names(ests)[row.names(ests) %in% c("postTRUE:bild_initTRUE", "postTRUE:bild_initTRUE:init_mig")]),
                   labels = rev(c("Post X Treatment", "Post X Treatment X Initial Attitude"))) +
  xlim(-0.1, 0.4) + 
  ggtitle("Controlling for initial attitude")

plot_did_alt_inter

```

## Nicer visualisation of interaction effect

### new treatment definition

```{r}

## run bootstrap to estimate 1000 direct and conditional effects

library(rsample)
library(purrr)

set.seed(42)
B <- 1000

modeldata <- 
  gles_p_long_1617 %>% 
  filter(!is.na(bild_init) & !is.na(dv) & !is.na(init_mig)) %>% 
  select(lfdn, dv, init_mig, bild_init, post) %>% 
  nest(-lfdn)

bs <- bootstraps(modeldata, times = B)
bs_ests <- map(bs$splits, ~as.tibble(.) %>% 
                       unnest %>% 
                       summarize(DiD = 
                                   feglm(dv ~ post * bild_init * init_mig, 
                                    cluster = c("lfdn"), 
                                    data = .) %>% 
                                   coef() %>% 
                                   .["postTRUE:bild_initTRUE"],
                                 IA = 
                                   feglm(dv ~ post * bild_init * init_mig, 
                                    cluster = c("lfdn"), 
                                    data = .) %>% 
                                   coef() %>% 
                                   .["postTRUE:bild_initTRUE:init_mig"],
                                 )) %>% 
  bind_rows(.id = 'boots')

direct <- coef(treat_alt_inter)["postTRUE:bild_initTRUE"]
interact <- coef(treat_alt_inter)["postTRUE:bild_initTRUE:init_mig"]

ggplot() +
  geom_histogram(data = gles_p_long_1617 %>% filter(wave == "1"), mapping = aes(x = init_mig, after_stat(density)), alpha = 0.4, bins = 8) +
  geom_abline(data = bs_ests, aes(slope = IA, intercept = DiD, group = boots), alpha= 0.05) +
  geom_abline(slope = interact, intercept = direct, col = "red") +
  theme_minimal() +
  geom_hline(yintercept = 0, col = "black") +
  scale_x_continuous(limits=c(-3,3)) +
  scale_y_continuous(limits=c(0,.6)) +
  ggtitle(paste0(B, " bootstrap estimates of heterogenous treatment effect")) +
  ylab("Estimate") + xlab("Initial migration attitude")

ggsave('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/paper/vis/DiDXinit_imm.svg', device = "svg")

```

### old treatment definition (probably shouldn't be used anymore)

### 2022-06-28 code/00c_frame_extraction.R

@@ -1,175 +1,0 @@
-# ______________________________________________
-# Effect of framing on issue attitudes
-# Goal: Define relevant frames, export estimates
-# ______________________________________________
-# Date:  Thu Oct 04 17:06:22 2021
-# Author: Nicolai Berk
-#  R version 4.0.3 (2020-10-10)
-# ______________________________________________
-
-
-# Setup ####
-library(tidyverse)
-library(data.table)
-library(here)
-library(stm)
-library(lubridate)
-library(tidytext)
-library(ggthemes)
-library(scales)
-library(knitr)
-library(dplyr)
-
-
-
-# explore following Julia Silge's blogpost: https://juliasilge.com/blog/evaluating-stm/
-load(here('data/out_docs.Rdata'))
-load(here('data/topic_model_K60.Rdata'))
-
-td_beta <- tidy(topic_model)
-td_gamma <- tidy(topic_model, matrix = "gamma",
-                 document_names = rownames(out$documents))
-
-
-top_terms <- td_beta %>%
-  arrange(beta) %>%
-  group_by(topic) %>%
-  top_n(7, beta) %>%
-  arrange(-beta) %>%
-  select(topic, term) %>%
-  summarise(terms = list(term)) %>%
-  mutate(terms = map(terms, paste, collapse = ", ")) %>%
-  unnest(cols = c(terms))
-
-gamma_terms <- td_gamma %>%
-  group_by(topic) %>%
-  summarise(gamma = mean(gamma)) %>%
-  arrange(desc(gamma)) %>%
-  left_join(top_terms, by = "topic") %>%
-  mutate(topic = paste0("Topic ", topic),
-         topic = reorder(topic, gamma))
-
-gamma_terms %>%
-  top_n(20, gamma) %>%
-  ggplot(aes(topic, gamma, label = terms, fill = topic)) +
-  geom_col(show.legend = FALSE) +
-  geom_text(hjust = 0, nudge_y = 0.0005, size = 3,
-            family = "IBMPlexSans") +
-  coord_flip() +
-  scale_y_continuous(expand = c(0,0),
-                     limits = c(0, 0.09),
-                     labels = percent_format()) +
-  theme_tufte(base_family = "IBMPlexSans", ticks = FALSE) +
-  theme(plot.title = element_text(size = 16,
-                                  family="IBMPlexSans-Bold"),
[…]

### 2022-06-28 code/01a_preprocessing_dv.R

@@ -1,419 +1,0 @@
-
-# ______________________________________________
-# Media effects on issue definitions
-# Goal: Preprocess survey data
-# Procedure: load, pivot, clean
-# ______________________________________________
-# Date:  Mon Sep 13 08:17:34 2021
-# Author: Nicolai Berk
-#  R version 4.0.3 (2020-10-10)
-# ______________________________________________
-
-# 0. load ####
-
-library(here)
-library(tidyverse)
-library(data.table)
-library(haven)
-library(lubridate)
-library(glue)
-library(naniar)
-library(dplyr)
-
-gles_p <- read_dta(here('data/gles/Panel/GLESMerge/ZA6838_allwaves_sA_v4-0-0.dta'))
-
-## id var
-gles_p$lfdn <- as.factor(gles_p$lfdn)
-
-
-
-# 1. Pivot wide -> long ####
-
-
-## date
-date_vars <- colnames(gles_p)[grep(pattern = 'datetime', colnames(gles_p))]
-
-### date
-gles_p_long <- gles_p %>%
-  select(c(lfdn, contains("datetime"))) %>%
-  pivot_longer(
-    cols = c(contains("datetime"))) %>%
-  mutate(
-    wave = str_match(name, "kp(.*)_")[,2],
-    date_new = value
-  ) %>%
-  select(lfdn, wave, date_new)
-
-### vis missings
-vis_miss(gles_p_long[sample(1:nrow(gles_p_long), 10000),])
-
-
-## media vars
-
-mediumlist <- c('1681', '1661')
-
-for (medium in mediumlist){
-  
-  if (medium == '1661'){
-    papers_list <- letters[1:8]
-    # papers_label_list <- c()
-  }else{
-    papers_list <- letters[1:6]
-    # papers_label_list <- c('Tagesschau', 'Heute_Journal', 'RTL_Aktuell', 'Sat.1_Nachrichten', 'Andere_Sender', 'Keine_Fernsehnachrichten')
-  }
-  
-  for (paper in papers_list){
-      
-      tempdta <- gles_p
-      
-      ## papervar
-      papervar_vars <- colnames(tempdta)[grep(pattern = paste0(medium, paper), colnames(tempdta))]
-      papervar_waves <- str_match(papervar_vars, 'kp(.*)_')[,2]
-      
-      ## wide -> long
-      ### paper
[…]

### 2022-06-28 code/01b_did_dv.R

@@ -1,227 +1,0 @@
-# ______________________________________________
-# Media effects on issue definitions
-# Goal: estimate DiD opinion shifts
-# Procedure: load data, broad estimation, only paper estimates
-# ______________________________________________
-# Date:  Mon Sep 13 08:36:30 2021
-# Author: Nicolai Berk
-#  R version 4.0.3 (2020-10-10)
-# ______________________________________________
-
-
-# Setup ####
-library(here)
-library(dplyr)
-library(tidyverse)
-library(data.table)
-library(haven)
-library(lubridate)
-library(glue)
-library(fixest)
-
-# load data ####
-gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv')) %>% as.data.frame()
-
-
-# DiD with treatment X readership var
-
-coeftable <- data.frame()
-sample_set <- c("exclusive readers", "all readers", "all respondents")
-
-for (sample_restriction in sample_set){
-
-  if (sample_restriction == 'exclusive readers'){
-    
-    # filter only exclusive readers
-    tempdta_res <- 
-      gles_p_long %>% 
-      mutate(n_papers = rowSums(gles_p_long %>% 
-                                  select(contains("1661")) %>% 
-                                  select(!contains("1661h")) %>% 
-                                  select(contains('bin')))) %>% 
-      filter(n_papers == 1)
-    
-  }else if (sample_restriction == "all readers"){
-    
-    tempdta_res <- 
-      gles_p_long %>% 
-      filter(!is.na(readership) & (readership != "")) %>% 
-      filter(readership != "None")
-    
-  }else if (sample_restriction == "all respondents"){
-    
-    tempdta_res <- 
-      gles_p_long %>% 
-      filter(!is.na(readership) & (readership != ""))
-    
-  }else{
-    stop(paste0("Unknown sample restriction: ", sample_restriction))
-  }
-  
-  if (nrow(tempdta_res) == 0){next}
-  
-  post_wave_set <- 
-    tempdta_res %>% 
-    filter(wave != "1") %>% 
-    select(wave) %>% 
-    unique() %>% 
-    unlist() %>% 
-    as.character()
-  
-  
-
-  for (post_wave in post_wave_set){
-  
-    
-    min_date_post <- 
-      tempdta_res %>% 
-      filter(wave == post_wave) %>% 
-      filter(!is.na(date_clean)) %>% 
-      select(date_clean) %>% 
-      unlist() %>% 
[…]

### 2022-06-28 code/02a_iv_prep.R

@@ -1,110 +1,0 @@
-# ______________________________________________
-# Effect of framing on issue attitudes
-# Goal: Prepare independent variables
-# Procedure: load, transform, save
-# ______________________________________________
-# Date:  Wed Sep 08 14:20:28 2021
-# Author: Nicolai Berk
-#  R version 4.0.3 (2020-10-10)
-# ______________________________________________
-
-
-# 0. Setup ####
-library(tidyverse)
-library(dplyr)
-library(here)
-library(data.table)
-library(here)
-library(lubridate)
-library(glue)
-
-# 1. load ####
-
-## survey data for wave dates
-attitude_dids <- read.csv(here('data/coeftable_gles_noimp.csv'))
-
-attitude_dids$paper_name <- ''
-attitude_dids$paper_name[attitude_dids$paper == 'a'] <- 'bild'
-attitude_dids$paper_name[attitude_dids$paper == 'b'] <- 'falg'
-attitude_dids$paper_name[attitude_dids$paper == 'c'] <- 'faz'
-attitude_dids$paper_name[attitude_dids$paper == 'd'] <- 'sz'
-attitude_dids$paper_name[attitude_dids$paper == 'e'] <- 'taz'
-attitude_dids$paper_name[attitude_dids$paper == 'f'] <- 'welt'
-
-load(here('data/frames_cleaned.csv'))
-load(here('data/salience_cleaned.csv'))
-
-# 2. transform ####
-
-## 2.1 framing ####
-
-## estimate absolute frame attention
-framing_daily <- 
-  framing_raw %>% 
-  select(-date, -title, -url, -text) %>% 
-  group_by(date_new, paper) %>% 
-  summarise_all(sum) %>%
-  as_tibble()
-
-## estimate n of mig articles in frame set
-framing_daily$n_mig_fra <- 
-  framing_raw %>% 
-  group_by(date_new, paper) %>% 
-  summarise(n_mig_fra = n()) %>% 
-  ungroup %>% 
-  select(n_mig_fra) %>% 
-  unlist()
-
-rm(framing_raw)
-
-
-## 2.2 salience ####
-
-# estimate absolute and relative saleince
-salience_daily <- 
-  salience_raw %>% 
-  group_by(date_new, paper) %>% 
-  summarise(
-    n_mig_sal = sum(mig),
-    n_tot = n()
-  ) %>% 
-  mutate(
[…]

### 2022-06-28 code/02b_did_iv.R

@@ -1,215 +1,0 @@
-# ______________________________________________
-# Effect of framing on issue attitudes
-# Goal: Prepare independent variables
-# Procedure: load, transform, save
-# ______________________________________________
-# Date:  Wed Sep 08 14:20:28 2021
-# Author: Nicolai Berk
-#  R version 4.0.3 (2020-10-10)
-# ______________________________________________
-
-
-# 0. Setup ####
-library(tidyverse)
-library(dplyr)
-library(here)
-library(data.table)
-library(here)
-library(lubridate)
-library(glue)
-
-# 1. load ####
-
-## get relevant waves and dates
-gles_p_long <- 
-  fread(here('data/gles/Panel/long_cleaned.csv')) %>% 
-  as.data.frame()
-
-wavelist <- 
-  gles_p_long %>% 
-  select(wave) %>% 
-  filter(wave != 'a1', wave != 'a2') %>% 
-  unique() %>% 
-  unlist() %>% 
-  as.numeric() %>% 
-  sort()
-
-datelist <- c()
-for (wave_treat in wavelist){
-  
-  datelist <- 
-    c(datelist,
-      gles_p_long %>% 
-        filter(wave == wave_treat) %>% 
-        select(date_clean) %>% 
-        unlist() %>% 
-        max(na.rm = T)
-    )
-}
-
-datelist <- 
-  datelist %>% 
-  as.Date(origin = "1970-01-01")
-
-survey_dates <- 
-  data.frame(
-    wave = wavelist,
-    date = datelist
-  )
-
-rm(gles_p_long)
-
-## load media data
-load(here('data/media_daily_2021-10-03.Rdata'))
-
-
-# 2. transform ####
-
-## 2.1 framing ####
-
-## add relevant treatment waves for did
-merged_media$pre_wave <- NA # upcoming survey wave
-merged_media$pre_wave_1d <- NA # upcoming survey wave
-merged_media$pre_wave_1w <- NA # upcoming survey wave
-merged_media$pre_wave_1m <- NA # upcoming survey wave
-merged_media$pre_wave_6m <- NA # upcoming survey wave
-
-## calculate topic prevalence in between survey waves
-for (wave_id in 1:nrow(survey_dates)){
-  
-  if (wave_id == 1){
-    lower <- as.Date('2016-01-01')
-  }else{
-    lower <- survey_dates$date[wave_id-1]
-  }
-  
-  upper <- survey_dates$date[wave_id]
-  
-  lower_1d <- max((upper - days(1)),   lower)
[…]

### 2022-06-28 code/02c_iv_edit.R

@@ -1,139 +1,0 @@
-# ______________________________________________
-# Media framing effects
-# Goal: Bild editorial change frame attention 
-# Procedure: load data, estimate DiD, visualise
-# ______________________________________________
-# Date:  Tue Nov 16 14:36:30 2021
-# Author: Nicolai Berk
-#  R version 4.1.1 (2021-08-10)
-# ______________________________________________
-
-
-# Setup ####
-library(tidyverse)
-library(dplyr)
-library(here)
-library(lubridate)
-
-# load data ####
-load(here('data/media_daily_2021-10-03.Rdata'))
-framenames <- colnames(merged_media)[6:12]
-
-# estimate DiD ####
-
-## aggregate
-media_agg <- 
-  merged_media %>% 
-  filter(date_new < as.Date('2020-01-01')) %>% 
-  mutate(month = floor_date(date_new, 'months')) %>% 
-  group_by(paper, month) %>% 
-  summarise(across(c(framenames, paste0(framenames, '_share'), share_mig), mean, na.rm = T))
-
-## define treatment indicator
-media_agg$edit_change <- 0
-media_agg$edit_change[media_agg$month > as.Date('2017-01-31')] <- 1
-
-
-# estimate model per newspaper per frame
-
-if (exists('model_ests')){rm(model_ests)}
-
-for (period in c('1617', 'all')){
-  for (paper in unique(media_agg$paper)){
-    for (frame in framenames){
-      
-      if(period == '1617'){
-        temp <- 
-          media_agg %>% 
-          filter(year(month) >= 2016 & (year(month) <= 2017))
-      }else{
-        temp <- media_agg
-      }
-      
-      
-      temp$frame_share <- temp[[paste0(frame, '_share')]]
-      temp$paper_bin   <- temp$paper == paper
-      
-      
-      m_share <- lm(frame_share ~ edit_change * paper_bin, data = temp)
-      
-      if (!exists('model_ests')){
-        model_ests <- 
-          data.frame(
-            frame = frame, 
-            paper = paper, 
-            period = period,
-            est_share = m_share$coefficients[[4]],
-            est_lower = confint(m_share)[4,][[1]],
-            est_upper = confint(m_share)[4,][[2]]
-              )
-      }else{
-        
-        model_ests <- 
-          rbind(
-            data.frame(
-              frame = frame, 
-              paper = paper, 
-              period = period,
[…]

### 2022-06-28 code/03_estimation.R

@@ -1,752 +1,0 @@
-# ______________________________________________
-# Effect of framing on issue attitudes
-# Goal: Estimate effects
-# Procedure: load, estimate
-# ______________________________________________
-# Date:  Thu Sep 09 17:24:28 2021
-# Author: Nicolai Berk
-#  R version 4.0.3 (2020-10-10)
-# ______________________________________________
-
-
-# 0. setup ####
-library(tidyverse)
-library(dplyr)
-library(here)
-library(data.table)
-library(here)
-library(lubridate)
-library(glue)
-library(gridExtra)
-library(stargazer)
-library(interplot)
-library(sjPlot)
-library(RcppRoll)
-  
-# 1. load data ####
-load(here("data/coefs_media_2021-10-03.Rdata"))
-framing_dids <- 
-  framing_dids %>% 
-  filter(!is.na(p))
-
-attitude_dids <- read.csv(here('data/coeftable_gles_noimp.csv'))
-
-attitude_dids$paper_name <- ''
-attitude_dids$paper_name[attitude_dids$paper == 'a'] <- 'bild'
-attitude_dids$paper_name[attitude_dids$paper == 'b'] <- 'falg'
-attitude_dids$paper_name[attitude_dids$paper == 'c'] <- 'faz'
-attitude_dids$paper_name[attitude_dids$paper == 'd'] <- 'sz'
-attitude_dids$paper_name[attitude_dids$paper == 'e'] <- 'taz'
-attitude_dids$paper_name[attitude_dids$paper == 'f'] <- 'welt'
-
-
-
-# 2. estimation did ####
-
-
-## 2.1 framing ####
-
-## select relevant issues (immigration & integration)
-imm_dids <- 
-  attitude_dids %>% 
-  filter(issue == "1130")
-
-int_dids <- 
-  attitude_dids %>% 
-  filter(issue == "1210")
-
-afd_dids <- 
-  attitude_dids %>%
-  filter(issue == "430i")
-  
-
-## pivot frametable wide to get 1 var/frame
-framing_dids <- 
-  framing_dids %>% 
-  pivot_wider(id_cols = c(paper, pre_wave, dv_lag), names_from = 'frame', values_from = 'coef')
-
-
-## correlate with frames
-efftable <- data.frame()
-for (issue in c("immigration", "integration", "afd-support")){
[…]

### 2022-06-28 code/04_vis.R

@@ -1,579 +1,0 @@
-# ______________________________________________
-# Effect of framing on issue attitudes
-# Goal: Visualisation
-# Procedure: Step 1, Step 2, Step 3
-# ______________________________________________
-# Date:  Thu Sep 09 17:46:22 2021
-# Author: Nicolai Berk
-#  R version 4.0.3 (2020-10-10)
-# ______________________________________________
-
-
-# Setup ####
-library(tidyverse)
-library(dplyr)
-library(here)
-library(data.table)
-library(ggExtra)
-library(glue)
-library(haven)
-library(gridExtra)
-library(lubridate)
-
-# Step 1 ####
-
-## 2.1 vis dependents ####
-
-## load data
-gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv'))
-
-## immigration attitude across time
-imm_mean <- 
-  gles_p_long %>%
-  group_by(wave) %>% 
-  filter(!is.na(`1130_clean`)) %>% 
-  summarise(immigration = mean(`1130_clean`),
-            immigration_sd = sd(`1130_clean`),
-            date_clean  = max(date_clean),
-            respondents = n()) %>% 
-  mutate(
-    imm_up = (immigration + qt(1 - (0.05/2), respondents - 1)*immigration_sd/respondents),
-    imm_low = (immigration - qt(1 - (0.05/2), respondents - 1)*immigration_sd/respondents),
-  ) %>% 
-  ggplot(aes(x = date_clean)) +
-  geom_line(aes(y = immigration), col = "red") +
-  geom_ribbon(aes(ymax = imm_up, ymin = imm_low), fill = "red") +
-  ggtitle("Immigration attitude in Germany across time", 
-          "Should immigration of foreigners be made easier (-3) or restricted (3) \nData: GLES Panel, waves 1-13, a1 & a2")
-
-### exclusive readers
-
-## integration attitude across time
-int_mean <- 
-  gles_p_long %>%
-  group_by(wave) %>% 
-  filter(!is.na(`1210_clean`)) %>% 
-  summarise(integration = mean(`1210_clean`)*(-1),
-            integration_sd = sd(`1210_clean`),
-            date_new  = max(as.Date(date_clean, unit = 'days')),
-            respondents = n()) %>% 
-  mutate(
[…]

### 2022-06-28 code/add_auflage.R

@@ -14,37 +14,47 @@ library(tidyverse)
 library(dplyr)
 library(here)
 library(data.table)
+library(glue)
 
 # load and transform data ####
 
+rawlink <- "https://ivw.de/aw/print/qa/titel/{ivw_title}/export?quartal%5B20131%5D=20131&quartal%5B20132%5D=20132&quartal%5B20133%5D=20133&quartal%5B20134%5D=20134&quartal%5B20141%5D=20141&quartal%5B20142%5D=20142&quartal%5B20143%5D=20143&quartal%5B20144%5D=20144&quartal%5B20151%5D=20151&quartal%5B20152%5D=20152&quartal%5B20153%5D=20153&quartal%5B20154%5D=20154&quartal%5B20161%5D=20161&quartal%5B20162%5D=20162&quartal%5B20163%5D=20163&quartal%5B20164%5D=20164&quartal%5B20171%5D=20171&quartal%5B20172%5D=20172&quartal%5B20173%5D=20173&quartal%5B20174%5D=20174&quartal%5B20181%5D=20181&quartal%5B20182%5D=20182&quartal%5B20183%5D=20183&quartal%5B20184%5D=20184&quartal%5B20191%5D=20191&quartal%5B20192%5D=20192&quartal%5B20193%5D=20193&quartal%5B20194%5D=20194&quartal%5B20201%5D=20201&quartal%5B20202%5D=20202&quartal%5B20203%5D=20203&quartal%5B20204%5D=20204&quartal%5B20211%5D=20211&quartal%5B20212%5D=20212&quartal%5B20213%5D=20213"
+
 ## print
-for (file in list.files('data/auflage')){
-  if(grepl('print', file)){
-  temp <- fread(paste0('data/auflage/', file))
-    if (exists('auflage')){
-      auflage <- 
-        temp %>% 
-        rbind(auflage)
-    }else{
-      auflage <- temp
-    }
+for (ivw_title in c('7110', '6751', '122', '1056', '1221', '1335')){
+  temp <- fread(glue(rawlink))
+  if (exists('auflage')){
+    auflage <- 
+      temp %>% 
+      rbind(auflage, fill = T)
+  }else{
+    auflage <- temp
   }
 }
+
+
 
 auflage <- 
   auflage %>% 
   filter(Zusatz == '') %>% 
+  filter(Korrektur_KZ != 'VK' | is.na(Korrektur_KZ)) %>%
[…]

### 2022-06-28 code/app_simulation.R

@@ -1,0 +1,175 @@
+# ______________________________________________
+# Bild
+# Goal: Simulation of FE model
+# Procedure: generate data, estimate models, visualise
+# ______________________________________________
+# Date:  Fri Apr 29 14:55:00 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+set.seed(42)
+
+# generate data ####
+
+
+
+
+## parameters
+n_ids <- 10000
+n_waves <- 5
+
+# add effect size and treatment size in DiD to make FE and DiD comparable
+# -> effect should be the same, just treatment strength should differ
+
+
+## observations
+id <- 1:n_ids
+wave <- 1:n_waves
+
+## values
+id_fe <- rnorm(n_ids)
+wave_fe <- rnorm(n_waves)
+
+# generate empty dataframe
+df <- 
+  expand.grid(ID = id, 
+              wave = wave)
+
+df$id_fe <- id_fe
+
+df <- 
+  df %>% 
+  arrange(ID)
+
+df$wave_fe <- wave_fe
+
+df <- 
+  df %>% 
+  filter(wave == 1) %>% 
+  mutate(imm_init = round(rnorm(n_ids))) %>% 
+  select(imm_init, ID) %>% 
+  right_join(df)
+
+df <- 
+  df %>% 
+  mutate(post = as.integer(wave > 1)) %>% 
+  mutate(treat = as.integer(ID < (max(ID)/2))) %>% 
+  mutate(epsilon = rnorm(nrow(df))) %>% 
+  mutate(imm_att = round(imm_init + id_fe + wave_fe + post*treat*((imm_init-3)*-0.1) + epsilon))
+
+
+## plot
+
+df %>% 
+  group_by(wave, treat) %>% 
+  summarise(imm_att = mean(imm_att)) %>% 
+  ggplot(aes(x = wave, y = imm_att, col = as.factor(treat))) +
+  geom_line()
+
+df %>% 
+  mutate(group_treat = paste(treat, imm_init)) %>% 
+  group_by(wave, group_treat) %>% 
+  summarise(imm_att = mean(imm_att), treat = mean(treat)) %>% 
+  ggplot(aes(x = wave, y = imm_att, group = as.factor(group_treat), col = as.factor(treat))) +
+  geom_line()
+
+# estimate models ####
+
+## direct
[…]

### 2022-06-28 code/content_analysis/bert/crime/dict/_mig_dict.R

@@ -1,0 +1,167 @@
+# ______________________________________________
+# Media reactions to RR violence
+# Goal: Generate migration dictionary
+# Procedure: function, set params, generate & save
+# ______________________________________________
+# Date:  Fri Apr 23 18:13:56 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+
+
+# Setup ####
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(ggplot2)
+library(gridExtra)
+library(word2vec)
+library(here)
+library(lsa)
+library(pbapply)
+
+# function ####
+
+DictionaryExpander <- function(paper, union_size, seed_dict, top_n) {
+  ## load model
+  model <- read.word2vec(here(paste0("_dt/_emb_models/", paper, ".bin")))
+  
+  ## create matrix for embeddings
+  embedding <- as.matrix(model)
+  
+  temp_dict <- seed_dict[seed_dict %in% row.names(embedding)]
+  
+
+  
+  ## define migration dictionary 
+  
+  ### find close terms for several terms related to migration
+  extended <- predict(model, temp_dict, 
+                           type = "nearest", top_n = top_n)
+  
+  ### get most commonly associated terms
+  dump <- c()
+  for (i in extended){
+    dump <- c(i$term2, dump)
+  }
+  
+  ### keep only those associated with at least [union_size] terms
+  #     (it might be better to do this with a similarity cutoff, 
+  #     e.g. include everything with similarity >0.9).
+  refined <- table(dump)[table(dump) >= union_size] %>% names() 
+  refined <- unique(c(refined, seed_dict))
+  
+  ## write to .csv
+  write.csv(refined, here(paste0('_sc/_dict/_dicts/', paper, '.csv')))
+  
+  
+  ## alternative: take most similar word to each term:
+  
+  ### find closest term for several terms related to migration
+  extended <- predict(model, temp_dict, 
+                      type = "nearest", top_n = top_n)
+  dump <- c()
+  for (i in extended){
+    dump <- c(i$term2[1], dump)
+  }
+  
+  refined <- unique(c(seed_dict, dump))
+
+  ### write to .csv
+  write.csv(refined, here(paste0('_sc/_dict/_dicts/', paper, '_alt.csv')))
+  
+  
+}
+
+
+# params ####
[…]

### 2022-06-28 code/content_analysis/bert/crime/dict/crime_dict.R

@@ -1,0 +1,87 @@
+# ______________________________________________
+# Bild
+# Goal: crime dictionary extension
+# Procedure: define seed, extend, save
+# ______________________________________________
+# Date:  Wed Mar 23 09:32:40 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(ggplot2)
+library(gridExtra)
+library(word2vec)
+library(here)
+library(lsa)
+library(pbapply)
+# define seed ####
+
+seed_dict <- 
+  c(
+    "täter", "täterin", "polizei", "verbrechen", "überfall", "mord",
+    "attacke", "raub", "straftat", "ermittelt", "gericht", "prozess",
+    "staatsanwaltschaft", "staatsanwalt", "staatsanwältin", "gefährder", 
+    "haft", "festnahme", "betrug", "betrüger", "erstochen", "opfer", 
+    "anwalt", "drogen", "dealer", "getötet", "verletzung", "delikt",
+    "vergewaltigung"
+    )
+
+## set up embedidng input
+
+if (!file.exists(here('code/dict/_emb_models/glove.german.txt'))) {
+  download.file('https://int-emb-glove-de-wiki.s3.eu-central-1.amazonaws.com/vectors.txt', 
+                destfile = here('code/dict/_emb_models/glove.german.txt'))
+}
+
+vectors = data.table::fread(here('code/dict/_emb_models/glove.german.txt'), data.table = F,  encoding = 'UTF-8')
+colnames(vectors) = c('word', paste('dim', 1:(dim(vectors)[2] - 1), sep = '_'))
+embeddings <- as.matrix(vectors[2:301])
+row.names(embeddings) <- vectors$word; rm(vectors)
+
+# extend ####
+temp_dict <- seed_dict[seed_dict %in% row.names(embeddings)]
+
+## generate cosin similarity matrix for the relevant terms to all others (lunchtime!)
+cosin_matrix <- matrix(nrow = nrow(embeddings), ncol = length(temp_dict))
+colnames(cosin_matrix) <- temp_dict
+row.names(cosin_matrix) <- row.names(embeddings)
+
+if (!file.exists(here('code/dict/_emb_models/glove_cosine.Rda'))) {
+  for (term in temp_dict){
+    print(paste("Calculating cosine similarity of", term, "to all other terms..."))
[…]

### 2022-06-28 code/content_analysis/bert/crime/dict/crime_sample_generator.R

@@ -1,0 +1,101 @@
+# ______________________________________________
+# Bild media effects
+# Goal: Generate stratified sample for crime coding
+# Procedure: load data, estimate, save sample
+# ______________________________________________
+# Date:  Wed Mar 23 15:06:24 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(pbapply)
+
+# load data ####
+
+## load dict
+dict <- sort(read.csv(here("code/dict/_dicts/crime_glove.csv"))$x)
+papers <- c("bild", "faz", "spon", "sz", "taz", "weltonline")
+n_sample <- 100
+
+for (p in papers){
+  
+  cat(paste("\n\nSampling", p, "..."))
+  
+  ## load newspaper articles
+  cat("\n\tLoading data...")
+  raw <- fread(here(paste0("data/newspapers/_", p, "_articles.csv")), encoding = "UTF-8")[,c("title", "url", "text")]
+  raw <- raw[text != "",]
+  ncols_raw <- ncol(raw)
+  
+  # assign scores & sample ####
+  
+  ## count occurences/article length
+  cat("\n\tAssigning dictionary scores...")
+  for (d in dict){
+    cat(paste0('\n\t\tCounting occurrences of "', d, '"...'))
+    raw[,eval(d)] <- str_count(raw$text, d)
+  }
+  
+  raw$sum <- rowSums(raw[,(ncols_raw+1):ncol(raw)])
+  raw$ntokens <- str_length(raw$text)
+  raw$mig_share <- (raw$sum/raw$ntokens)
+  
+  ## pull stratified sample
+  cat("\n\tPulling stratified sample...")
+  
+  ### sample 100 cases from articles low, mid, and high on migration mentions
+  quantiles_nozero <- quantile(raw$mig_share[raw$mig_share != 0], na.rm = T)
+  low_sample <- sample_n(raw[raw$mig_share == 0], n_sample)
+  mid_sample <- sample_n(raw[raw$mig_share > 0 &
+                               raw$mig_share <= quantile(raw$mig_share, 0.95)], n_sample)
+  high_sample <- sample_n(raw[raw$mig_share > quantile(raw$mig_share, 0.95)], n_sample)
+  
+  ## check language, keep german
+  low_sample <-  low_sample[cld2::detect_language(low_sample$text) == "de",]
[…]

### 2022-06-28 code/content_analysis/bert/crime/handcoding/crime/gui.R

@@ -1,0 +1,402 @@
+# ______________________________________________
+# Media rections to RR violence
+# Goal: Write GUI for sample coding
+# Procedure: draw sample, annotate, save
+# ______________________________________________
+# Date:  Wed Apr 28 17:26:26 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(here)
+library(data.table)
+library(shiny)
+
+
+# setup ui
+
+ui <- fluidPage(
+  tags$head(
+    # Note the wrapping of the string in HTML()
+    tags$style(HTML("
+      
+      
+    body {
+      background-color:white;
+      font-family: 'Lato', sans-serif;
+    }
+    
+    body{
+    color: black; 
+    text-align:justify;
+    font-size:16px;
+    }
+    
+    img {
+      vertical-align: bottom;
+    }
+    
+    ul {
+      list-style-type: none;
+      margin: 0;
+      padding: 0;
+    }
+    
+    h1, .h1 {
+      display: none;
+    }
+    
+    
+    h2, .h2 {
+      color: #0e5484;
+      text-decoration: underline;
+    }
+    
+    h3, .h3  {
+        margin-top: 18px;
+        color: #0e5484;
+    }
+    
+    h4, .h4  {
+        margin-top: 12px;
+          color: #0e5484;
+    }
+    
+    /* link */
+    a, .navbar-default .navbar-nav > .active > a {
+      color: #0e5484;
+    }
+    
+    a:active, a:hover{
+      color: #0e5484;
+      text-decoration: underline;
+    }
+    
+    a p {
+      display:none;
+    }
+    
+    a:hover p {
+      display:block;
+    }
+    
+    span {
+      color: #0e5484;
+      font-weight: bold;
+    }
+    
+    .btn {
+        border-width: 0 0 0 0;
+        font-weight: bold;
+    }
+    
+    /* brand name in menu */
+    .navbar-default .navbar-brand {
+      color: #0e5484;
+    }
+    
+    .btn-default, .nav-pills:active>a {
+        color: white;
+        background-color: #6892D3;
+        border-color: white;
+    }
+    
+    .navbar-default{
+      background-color: #6892D3;
+    }
+    
+    .nav-pills:hover>a, .nav-pills>li>a, .navbar-default .navbar-nav>li>a:hover  {
+        color: white;
[…]

### 2022-06-28 code/content_analysis/bert/mig/_handcoding/_gui.R

@@ -1,0 +1,529 @@
+# ______________________________________________
+# Media rections to RR violence
+# Goal: Write GUI for sample coding
+# Procedure: draw sample, annotate, save
+# ______________________________________________
+# Date:  Wed Apr 28 17:26:26 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(here)
+library(data.table)
+library(shiny)
+
+
+# setup ui
+
+ui <- fluidPage(
+  tags$head(
+    # Note the wrapping of the string in HTML()
+    tags$style(HTML("
+      
+      
+    body {
+      background-color:white;
+      font-family: 'Lato', sans-serif;
+    }
+    
+    body{
+    color: black; 
+    text-align:justify;
+    font-size:16px;
+    }
+    
+    img {
+      vertical-align: bottom;
+    }
+    
+    ul {
+      list-style-type: none;
+      margin: 0;
+      padding: 0;
+    }
+    
+    h1, .h1 {
+      display: none;
+    }
+    
+    
+    h2, .h2 {
+      color: #0e5484;
+      text-decoration: underline;
+    }
+    
+    h3, .h3  {
+        margin-top: 18px;
+        color: #0e5484;
+    }
+    
+    h4, .h4  {
+        margin-top: 12px;
+          color: #0e5484;
+    }
+    
+    /* link */
+    a, .navbar-default .navbar-nav > .active > a {
+      color: #0e5484;
+    }
+    
+    a:active, a:hover{
+      color: #0e5484;
+      text-decoration: underline;
+    }
+    
+    a p {
+      display:none;
+    }
+    
+    a:hover p {
+      display:block;
+    }
+    
+    span {
+      color: #0e5484;
+      font-weight: bold;
+    }
+    
+    .btn {
+        border-width: 0 0 0 0;
+        font-weight: bold;
+    }
+    
+    /* brand name in menu */
+    .navbar-default .navbar-brand {
+      color: #0e5484;
+    }
+    
+    .btn-default, .nav-pills:active>a {
+        color: white;
+        background-color: #6892D3;
+        border-color: white;
+    }
+    
+    .navbar-default{
+      background-color: #6892D3;
+    }
+    
+    .nav-pills:hover>a, .nav-pills>li>a, .navbar-default .navbar-nav>li>a:hover  {
+        color: white;
[…]

### 2022-06-28 code/content_analysis/bert/mig/_mig_clsfr/_classifier.py

@@ -1,0 +1,203 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jun 21 20:22
+@author: Nicolai Berk
+"""
+
+# install language model
+# python -m spacy download de_core_news_sm
+
+# import
+# import csv
+import os
+import datetime
+import pandas as pd
+from _functions import TextCleaner
+from sklearn.feature_extraction.text import CountVectorizer
+from sklearn.feature_extraction.text import TfidfVectorizer
+from imblearn.over_sampling import SMOTE
+from sklearn import metrics
+from sklearn.model_selection import train_test_split
+from sklearn.linear_model import LogisticRegression
+from sklearn.naive_bayes import MultinomialNB
+from sklearn import svm
+# from sklearn.model_selection import cross_val_score
+import joblib
+import random
+import numpy as np
+import copy
+import pickle
+import nltk
+# nltk.download('stopwords')
+# from nltk.corpus import stopwords
+# sws_german = stopwords.words("german")
+import random
+
+os.chdir('../..') # moves from _sc/_mig_clsfr to main project folder
+datadir = os.path.expanduser('_dt/_handcoding/')
+# datadir = 'drive/MyDrive/rrviol/' # colab
+
+dt = str(datetime.datetime.now().strftime("%Y%m%d-%H%M%S"))
+
+# load data
+print('Loading data...')
+dta = pd.read_csv(datadir+'handcoding_finished.csv', header=0)
+print('\tDone!')
+
+
+# preprocess
+print('Preprocessing articles...')
+dta['tokens'], dta['stems'] = TextCleaner(dta.text)
+dta['labels'] = dta.mig == 'Ja'
+print('\tDone!')
+
+
+# create dict for different datasets
+dta_dict = {form: {vec: {ds: {v: [] for v in ['X', 'y']} for ds in ['train', 'test']} for vec in ['tfidf', 'count']} for form in ['stems', 'tokens']}
+
+vec_dict = {form: {vec: [] for vec in ['tfidf', 'count']} for form in ['stems', 'tokens']}
+
+# vectorize and train-test-split
+print('Vectorizing and train-test-split...')
+
+for form in dta_dict:
+    for vec in dta_dict[form]:
+        
+        if vec == 'tfidf':
+            vec_dict[form][vec] = TfidfVectorizer(max_df=.5, min_df=5, 
+#                                                   stop_words = sws_german
+                                                 )
+        else:
[…]

### 2022-06-28 code/content_analysis/bert/mig/_mig_clsfr/_estimation.py

@@ -1,0 +1,61 @@
+import joblib
+import pickle
+import os
+import pandas as pd
+import csv
+import sys
+import numpy as np
+
+os.chdir('../..')
+
+
+
+csv.field_size_limit(sys.maxsize)
+
+clf = joblib.load('_dt/classifier.pkl')
+vectorizer = pickle.load(open('_dt/vectorizer.pkl', mode='rb'))
+textrow = 5
+fieldnames = ['date', 'paper', 'title', 'link', 'topic', 'mig_pred', 'mig_proba']
+
+
+
+for paper in os.listdir('_dt/2019_data/'):
+    with open('_dt/2019_data/'+paper, mode="r", encoding="utf-8") as fi:
+        reader = csv.reader(fi)
+
+        for row in reader:
+            # define relative position in row based on title
+            titlerow = np.argmax([r == 'title' for r in row])
+            linkrow  = np.argmax([r == 'url'   for r in row])
+            daterow  = np.argmax([r == 'date'  for r in row])
+            textrow  = np.argmax([r == 'text'  for r in row])
+            topicrow = np.argmax([r == 'topic' for r in row])
+            break
+        if os.path.isfile('_dt/_mig_estimates/_2019_estimates_'+paper):
+            i = pd.read_csv('_dt/_mig_estimates/_2019_estimates'+paper).shape[0] # set starting point
+        else:
+            i = 0
+        
+        for skip in range(i):
+            next(reader)
+
+
+        with open('_dt/_mig_estimates/_2019_estimates'+paper, mode="a", encoding="utf-8") as fo:
+
+            writer = csv.DictWriter(fo, lineterminator = '\n', fieldnames = fieldnames)
+            writer.writeheader()
+
+            for row in reader:
+                i += 1
+                mtrx = vectorizer.transform(pd.array([row[textrow]]))
+                pred = clf.predict(mtrx)[0]
+                proba = clf.predict_proba(mtrx)[0][1]
+                writer.writerow({'date':         row[daterow], 
+                                 'paper':        paper, 
+                                 'title':        row[titlerow], 
+                                 'link':         row[linkrow], 
+                                 'topic':        row[topicrow],
+                                 'mig_pred':     pred,
+                                 'mig_proba':    proba})
+                print(f'Classified {i} speeches. Current file: {paper}', end="\r")
+            print(f'Finished estimating {i} speeches ({paper})\n')

### 2022-06-28 code/content_analysis/bert/mig/_mig_clsfr/_estimation_BERT.py

@@ -1,0 +1,54 @@
+import os
+import pandas as pd
+import csv
+import sys
+import numpy as np
+from transformers import TFAutoModelForSequenceClassification
+
+os.chdir('../..')
+
+
+
+csv.field_size_limit(sys.maxsize)
+
+model = TFAutoModelForSequenceClassification.from_pretrained('_dt/mig_clsfr_BERT')
+fieldnames = ['date', 'paper', 'title', 'link', 'topic', 'mig_pred', 'mig_proba']
+
+
+
+for paper in os.listdir('_dt/Archive/'):
+    with open('_dt/Archive/'+paper, mode="r", encoding="utf-8") as fi:
+        reader = csv.reader(fi)
+
+        for row in reader:
+            # define relative position in row based on title
+            titlerow = np.argmax([r == 'title' for r in row])
+            linkrow  = np.argmax([r == 'url'   for r in row])
+            daterow  = np.argmax([r == 'date'  for r in row])
+            textrow  = np.argmax([r == 'text'  for r in row])
+            topicrow = np.argmax([r == 'topic' for r in row])
+            break
+        
+        for skip in range(i):
+            next(reader)
+
+
+        with open('_dt/_mig_estimates/_BERT_estimates'+paper, mode="a", encoding="utf-8") as fo:
+
+            writer = csv.DictWriter(fo, lineterminator = '\n', fieldnames = fieldnames)
+            writer.writeheader()
+
+            for row in reader:
+                i += 1
+                mtrx = vectorizer.transform(pd.array([row[textrow]]))
+                pred = clf.predict(mtrx)[0]
+                proba = clf.predict_proba(mtrx)[0][1]
+                writer.writerow({'date':         row[daterow], 
+                                 'paper':        paper, 
+                                 'title':        row[titlerow], 
+                                 'link':         row[linkrow], 
+                                 'topic':        row[topicrow],
+                                 'mig_pred':     pred,
+                                 'mig_proba':    proba})
+                print(f'Classified {i} speeches. Current file: {paper}', end="\r")
+            print(f'Finished estimating {i} speeches ({paper})\n')

### 2022-06-28 code/content_analysis/bert/mig/_mig_clsfr/_functions.py

@@ -1,0 +1,47 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jun 22 11:22
+@author: Nicolai Berk
+@title: Cleaner
+"""
+
+# Import
+import nltk
+from nltk.tokenize import RegexpTokenizer
+from nltk.stem.snowball import SnowballStemmer
+stemmer = SnowballStemmer('german')
+# from sklearn.feature_extraction.text import CountVectorizer
+# from sklearn.feature_extraction.text import TfidfVectorizer
+
+# Clean Text
+def TextCleaner(docs):
+    
+    # remove punctuation and tokenize
+    DocTokenizer = RegexpTokenizer(r'\w+')
+    Tokenizer = lambda x : DocTokenizer.tokenize(x)
+    tokens = docs.apply(Tokenizer)
+    
+    # stem
+    def WordStemmer(toks):
+      stems = ''
+      for word in toks:
+        stems = stems + stemmer.stem(word) + ' '
+
+      return stems
+
+
+    stems = tokens.apply(WordStemmer)    
+    
+    tokens = [' '.join(t) for t in tokens] # joins into single string
+    
+    return tokens, stems
+
+
+# def Vectorizer(tokens, vec_type = 'tfidf'):
+#     if vec_type == 'tfidf':
+#         vectorizer = TfidfVectorizer(max_df=.5, min_df=5)
+#     else:
+#         vectorizer = CountVectorizer(max_df=.5, min_df=5)
+        
+#     mtrx = vectorizer.fit_transform(tokens)
+#     return mtrx

### 2022-06-28 code/content_analysis/bert/mig/dict/_mig_scores_dict.R

@@ -1,0 +1,100 @@
+# ______________________________________________
+# Media reactions to RR violence
+# Goal: Estimate migration content with dictionary
+# Procedure: load data, assign scores, save sample
+# ______________________________________________
+# Date:  Fri Apr 30 17:04:58 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(here)
+library(data.table)
+library(pbapply)
+
+# load data ####
+
+## load dict
+dict <- sort(read.csv("_dicts/german_glove.csv")$x)
+papers <- c("bild", "faz", "spon", "sz", "taz", "weltonline")
+n_sample <- 100
+
+for (p in papers){
+  
+  cat(paste("\n\nSampling", p, "..."))
+  
+  ## load newspaper articles
+  cat("\n\tLoading data...")
+  raw <- fread(here(paste0("_dt/_out/_", p, "_articles.csv")), encoding = "UTF-8")[,c("title", "url", "text")]
+  raw <- raw[text != "",]
+  ncols_raw <- ncol(raw)
+  
+  # assign scores & sample ####
+  
+  ## count occurences/article length
+  cat("\n\tAssigning dictionary scores...")
+  for (d in dict){
+    cat(paste0('\n\t\tCounting occurrences of "', d, '"...'))
+    raw[,eval(d)] <- str_count(raw$text, d)
+  }
+  
+  raw$sum <- rowSums(raw[,(ncols_raw+1):ncol(raw)])
+  raw$ntokens <- str_length(raw$text)
+  raw$mig_share <- (raw$sum/raw$ntokens)
+  
+  ## pull stratified sample
+  cat("\n\tPulling stratified sample...")
+  
+  ### sample 100 cases from articles low, mid, and high on migration mentions
+  quantiles_nozero <- quantile(raw$sum[raw$sum != 0], na.rm = T)
+  low_sample <- sample_n(raw[raw$sum == 0], n_sample)
+  mid_sample <- sample_n(raw[raw$sum >= quantiles_nozero[2] &
+                               raw$sum <= quantiles_nozero[4]], n_sample)
+  high_sample <- sample_n(raw[raw$sum > quantiles_nozero[4]], n_sample)
+  
+  ## check language, keep german
+  low_sample <-  low_sample[cld2::detect_language(low_sample$text) == "de",]
+  mid_sample <-  mid_sample[cld2::detect_language(mid_sample$text) == "de",]
[…]

### 2022-06-28 code/content_analysis/bert/mig/dict/_text2vec_embeddings.R

@@ -1,0 +1,114 @@
+# ______________________________________________
+# Media reactions to RR violence
+# Goal: Embeddings for each paper with text2vec
+# Procedure: function, set params, generate & save
+# ______________________________________________
+# Date:  Fri Apr 23 18:13:56 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+# ______________________________________________
+# This is not necessary for dictionary expansion, 
+#  but could be useful later on to estimate the
+#  shift in framing before and after an attack
+#  (Rodriguez et al. 2020).
+# 
+# To do this, the model needed to run on the texts,
+#  and we might want to compare the submodels to a 
+#  model trained on the merged set of articles.
+# 
+# It might be very useful to use this to generate
+#  migration dictionaries for each party.
+# 
+# Note that when running with full texts, docs
+#  need to be split into sentences.
+# 
+# ______________________________________________
+
+
+
+
+# Setup ####
+library(dplyr)
+library(tidyr)
+library(quanteda)
+library(stringr)
+library(ggplot2)
+library(gridExtra)
+library(word2vec)
+library(here)
+
+# function ####
+
+EmbeddingGenerator <- function(paper, textcol, is_csv) {
+  
+  ## load data
+  if(is_csv){
+    
+    path <- here(paste0('_dt/_', paper, '_raw.csv'))
+    dta <- read.csv(path)
+    rm(list = setdiff(ls(), c('dta', 'paper', 'textcol')))
+    
+  }else{
+    
+    path <- here(paste0('_dt/_', paper, '_raw.Rdata'))
+    dta <- get(load(path))
+    rm(list = setdiff(ls(), c('dta', 'paper', 'textcol'))) # this is necessary bc load() loads to original namespace
+    
+  }
+  
+  ## clean
+  cleaner <- function(x){
+    y <- gsub(x, pattern = "\\n|\\t|\\r|  ", replacement = "")
+    return(y)
+  }
+  
+  dta <- lapply(dta[textcol], cleaner) %>% 
+    as.data.frame()
+  
+  ## prepare tokens
+  toks <- dta$title %>% 
+    corpus() %>% 
+    tokens(remove_punct = T, remove_numbers = T) %>% # remove punctuation and numbers
+    tokens_tolower()
[…]

### 2022-06-28 code/content_analysis/stm/02a_stm.R

@@ -1,0 +1,55 @@
+library(tidyverse)
+library(data.table)
+library(here)
+library(stm)
+library(lubridate)
+library(tidytext)
+library(ggthemes)
+library(scales)
+library(knitr)
+library(dplyr)
+
+# load the preselected migration articles
+# mig_texts_raw <- fread(here('data/_migration_articles_new.csv'), encoding = 'UTF-8') %>% as_tibble()
+mig_texts_raw <- fread(here('data/_migration_articles_BERT.csv'), encoding = 'UTF-8') %>% as_tibble()
+
+
+# use subsample for now
+# mig_texts_raw <- mig_texts_raw[sample(1:nrow(mig_texts_raw), 1000),]
+
+# fix dates
+mig_texts_raw$paper[mig_texts_raw$paper == "weltonline"] <- "welt"
+mig_texts_raw$date_new <- NA_Date_
+mig_texts_raw$date_new[mig_texts_raw$paper == "bild"] <- mig_texts_raw$date[mig_texts_raw$paper == "bild"] %>% as.Date()
+mig_texts_raw$date_new[mig_texts_raw$paper == "faz"] <- mig_texts_raw$date[mig_texts_raw$paper=="faz"] %>% as.numeric() %>% as.Date(origin = "1970-01-01")
+mig_texts_raw$date_new[mig_texts_raw$paper == "spon"] <- mig_texts_raw$date[mig_texts_raw$paper=="spon"] %>% as.Date(format = "%d.%m.%Y")
+mig_texts_raw$date_new[mig_texts_raw$paper == "sz"] <- mig_texts_raw$date[mig_texts_raw$paper=="sz"] %>% as.integer() %>% as.Date(origin = "1970-01-01")
+mig_texts_raw$date_new[mig_texts_raw$paper == "taz"] <- mig_texts_raw$date[mig_texts_raw$paper=="taz"] %>% as.integer() %>% as.Date(origin = "1970-01-01")
+mig_texts_raw$date_new[mig_texts_raw$paper == "welt"] <- mig_texts_raw$date[mig_texts_raw$paper=="welt"] %>% as.integer() %>% as.Date(origin = "1970-01-01")
+mig_texts_raw <- mig_texts_raw[mig_texts_raw$date_new > as.Date('2010-01-01'),]
+
+## load german stopwords
+german_stopwords <- data.frame(word = c(stopwords::stopwords("de"), 'dass', 'sagte', 'sagt', 'sei'), stringsAsFactors = F)
+
+
+## preprocess
[…]

### 2022-06-28 code/crime_june_2016.R

@@ -1,0 +1,46 @@
+# ______________________________________________
+# Bild
+# Goal: Explain peak in June
+# ______________________________________________
+# Date:  Fri May 13 18:09:21 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+bert <- fread(here("data/processed/bert_crime_clean.csv"), encoding = "UTF-8")
+
+bert %>%
+  mutate(nberg = grepl(text, pattern = ".*nürnberg.*", ignore.case = T),
+         tumult = grepl(text, pattern = ".*tumult.*", ignore.case = T),
+         afghane = grepl(text, pattern = ".*afghane.*", ignore.case = T),
+         arnschwang = grepl(text, pattern = ".*arnschwang.*", ignore.case = T)) -> bert
+
+bert %>%
+  mutate(date_clean = lubridate::floor_date(date_clean, "month")) %>%
+  mutate(paper = paper == "Bild") %>% 
+  group_by(paper, date_clean) %>%
+  summarise(
+    crime_share = mean(crime_label),
+    afghane = mean(afghane),
+    tumult = mean(tumult),
+    nberg = mean(nberg),
+    arnschwang = mean(arnschwang)
+  ) -> bert_month
+
+bert_month %>%
+  filter(date_clean >= as.Date("2017-01-01"), date_clean < as.Date("2018-01-10")) %>%
+  ggplot(aes(x = date_clean)) +
+  geom_line(aes(y = arnschwang), col = "violet", lty = 5) +
+  geom_line(aes(y = nberg), col = "black", lty = 4) +
+  geom_line(aes(y = tumult), col = "green", lty = 3) +
+  geom_line(aes(y = afghane), col = "red", lty = 2) +
+  geom_line(aes(y = crime_share), col = "blue", lty = 1) +
+  facet_wrap(~paper)
+

### 2022-06-28 code/estimation/03_bootstrap.R

@@ -1,0 +1,266 @@
+# ______________________________________________
+# Bild media effects
+# Goal: bootstrap did and individual model
+# Procedure: load data, run bootstrap, save
+# ______________________________________________
+# Date:  Mon Mar 21 13:40:05 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(here)
+library(data.table)
+library(fixest)
+library(lubridate)
+library(rsample)
+library(purrr)
+library(dplyr)
+
+set.seed(42)
+B <- 1000
+run_inop <- F
+run_mip_did <- F
+run_mip_fe <- F
+run_exp_fe <- F
+run_cor_mip_crime <- T
+
+# load data ####
+
+## DiD ####
+
+gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
+
+gles_p_long$dv <- gles_p_long$`1130_clean`
+gles_p_long$post <- gles_p_long$date_clean >= as.Date("2017-02-01")
+
+## Indiv. Exp. ####
+
+merged_data <- fread(file = here("data/processed/merged_bert.csv"))
+
+merged_data <- 
+  merged_data %>% 
+  mutate(crime_share = crime_label_share,
+         crime_share_lag = crime_label_share_lag,
+         dv = `1130_clean`) %>% 
+  filter(lag == 7)
+
+
+
+# bootstrap ####
+
+## DiD ####
+
+if(run_inop){
+  
+
+### initial opinion ####
+  
+  modeldata <- 
+    gles_p_long %>% 
+    filter(!is.na(treat) & !is.na(dv) & !is.na(init_mig)) %>% 
+    select(lfdn, dv, init_mig, treat, post) %>% 
+    nest(-lfdn)
+  
+  bs <- bootstraps(modeldata, times = B)
+  bs_did_ests <- map(bs$splits, ~as.tibble(.) %>% 
+                       unnest %>% 
+                       summarize(DiD = 
+                                   feglm(dv ~ post * treat * init_mig, 
+                                         cluster = c("lfdn"), 
+                                         data = .) %>% 
+                                   coef() %>% 
+                                   .["postTRUE:treatTRUE"],
+                                 IA = 
+                                   feglm(dv ~ post * treat * init_mig, 
+                                         cluster = c("lfdn"), 
+                                         data = .) %>% 
[…]

### 2022-06-28 code/functions.R

@@ -1,0 +1,145 @@
+# ______________________________________________
+# Bild
+# Goal: Functions for paper
+# ______________________________________________
+# Date:  Thu Apr 21 08:37:00 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+
+
+DiD_direct <- function(dta, size = 1, col = "black") {
+  
+  
+  
+  # model 1: direct effect
+  ate <- 
+    feglm(dv ~ post * treat, 
+          cluster = c("lfdn"), 
+          data = dta)
+  
+  points <- ate$coefficients
+  ests <- cbind(points, confint(ate))
+  
+  plot_did_ate <- 
+    ests %>%
+    filter(row.names(.) == "postTRUE:treatTRUE") %>% 
+    ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
+    geom_pointrange(size = size, col = col) +
+    geom_vline(xintercept = 0, col = "red", lty = 2, size = size) +
+    ylab("") + xlab("Estimate") +
+    xlim(-0.1, 0.3) + 
+    scale_y_discrete(labels = rev(c("DiD"))) +
+    ggtitle("Average treatment effect") 
+  
+  
+  return(plot_did_ate)
+  
+  
+
+  
+}
+
+
+DiD_inter <- function(dta, size = 1, col = "black") {
+  
+  
+  inter <- 
+    feglm(dv ~ post * treat * init_mig, 
+          cluster = c("lfdn"), 
+          data = dta)
+  
+  points <- inter$coefficients
+  ests <- cbind(points, confint(inter))
+  
+  plot_did_inter <- 
+    ests %>% 
+    filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig")) %>% 
+    mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
+    ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
+    geom_pointrange(col = col, size = size) +
+    geom_vline(xintercept = 0, col = "red", lty = 2, size = size) +
+    ylab("") + xlab("Estimate") +
+    ggtitle("DiD-estimate with interaction") +
[…]

### 2022-06-28 code/functions/estimation.R

@@ -1,0 +1,373 @@
+# ______________________________________________
+# Bild
+# Goal: Functions for Estimation
+# ______________________________________________
+# Date:  Sun May 15 13:50:05 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(fixest)
+library(modelsummary)
+
+# Difference-in-Difference model
+DiDModels <- function(dv_name, 
+                      cond_var = "init_mig", 
+                      cond_name = "\nImmigration Attitude W1",
+                      ctrl_var = F, 
+                      restrict_period = F,
+                      restrict_sample = F,
+                      estimate = "{estimate}{stars}",
+                      ctrl_name,
+                      gof_omit = "^(?!R2.Pseudo|Num|Std|FE)") {
+  
+  gles_p_long <- data.table::fread(here('data/raw/gles/Panel/long_cleaned.csv'))
+  
+  # restrict to relevant time frame
+  if(restrict_period){
+    
+    gles_p_long <-
+      gles_p_long %>%
+      filter(date_clean >= as.Date("2016-01-01"),
+             date_clean <  as.Date("2018-01-01"))
+  
+  }
+  
+  if (restrict_sample == "conservative_outlets"){
+    gles_p_long <-
+      gles_p_long %>%
+      filter(bild_init | faz_init | welt_init)
+  }
+  
+  # define dv and conditioning variable
+  gles_p_long[["dv"]] <- gles_p_long[[dv_name]]
+  gles_p_long[["cond"]] <- gles_p_long[[cond_var]]
+  
+  gles_p_long$ID <- as.factor(gles_p_long$lfdn)
+  
+  # model 1: direct effect
+  ate <- 
+    feglm(dv ~ post * treat, 
+          cluster = c("ID"), 
+          data = 
+            gles_p_long %>% 
+            filter(!is.na(dv), !is.na(treat), !is.na(post)))
+  
+  if (!isFALSE(ctrl_var)){
+    
+    if (ctrl_var == "cond"){
+      ate_ctrl <- 
+        feglm(dv ~ post * treat + cond, 
+              cluster = c("ID"), 
+              data = 
+                gles_p_long %>% 
[…]

### 2022-06-28 code/functions/visualisation (LAPTOP-4OK12DRH's conflicted copy 2022-06-27).R

@@ -1,0 +1,587 @@
+# ______________________________________________
+# Bild
+# Goal: Generate visualisations for Paper and appendix
+# ______________________________________________
+# Date:  Fri May 13 11:32:01 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+
+# Migration Salience ####
+
+MigSaliencePlot <- function(aggregation = "months"){
+  
+  mig_salience_plot <- fread(here("data/processed/bert_crime_daily.csv")) %>% 
+    select(date_clean, paper, mig_share) %>% 
+    mutate(date_new = floor_date(date_clean, aggregation)) %>% 
+    group_by(date_new, paper) %>% 
+    summarise_all(mean) %>% 
+    filter(date_new < as.Date('2019-01-01')) %>%
+    ggplot(aes(x = date_new, y = mig_share, col = paper, lty = paper, shape = paper)) +
+    geom_line() + geom_point() +
+    ggtitle('Migration salience in different newspapers') +
+    xlab('') + ylab('Share of migration articles') +
+    theme_minimal() +
+    labs(color = "Outlet", lty = "Outlet", shape = "Outlet")
+  
+  return(mig_salience_plot)
+}
+
+
+# Treatment: shift in attention to crime
+
+TreatmentTrendPlot <- function(size = 1, 
+                               cntrl_col = "black",
+                               treat_col = "red",
+                               maxdate = as.Date("2020-01-01")) {
+  
+  ## load BERT data
+  bert_ests_raw <- 
+    fread(here('data/processed/bert_crime_clean.csv'))
+    
+    bert_ests <- 
+      bert_ests_raw %>% 
+      mutate(month = lubridate::floor_date(date_clean, "month")) %>% 
+      group_by(paper, month) %>% 
+      summarise(
+        crime_share = mean(crime_label)
+      ) %>% 
+      mutate(paper = ifelse(paper %in% c("bild", "Bild"), "Bild", "Other")) %>%
+      group_by(month, paper) %>%
+      select(crime_share) %>% 
+      summarise(
+        crime_share = mean(crime_share)
+      )
+    
+    survey_dates <- 
+      fread(here("data/processed/SurveyDates.csv")) %>% 
[…]

### 2022-06-28 code/functions/visualisation.R

@@ -1,0 +1,584 @@
+# ______________________________________________
+# Bild
+# Goal: Generate visualisations for Paper and appendix
+# ______________________________________________
+# Date:  Fri May 13 11:32:01 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+
+# Migration Salience ####
+
+MigSaliencePlot <- function(){
+  
+  mig_salience_plot <- fread(here("data/processed/bert_crime_daily.csv")) %>% 
+    select(date_clean, paper, mig_share) %>% 
+    mutate(date_new = floor_date(date_clean, "month")) %>% 
+    group_by(date_new, paper) %>% 
+    summarise_all(mean) %>% 
+    filter(date_new < as.Date('2019-01-01')) %>%
+    ggplot(aes(x = date_new, y = mig_share, col = paper, lty = paper, shape = paper)) +
+    geom_line() + geom_point() +
+    ggtitle('Migration salience in different newspapers') +
+    xlab('') + ylab('Share of migration articles') +
+    theme_minimal() +
+    labs(color = "Outlet", lty = "Outlet", shape = "Outlet")
+  
+  return(mig_salience_plot)
+}
+
+
+# Treatment: shift in attention to crime
+
+TreatmentTrendPlot <- function(size = 1, 
+                               cntrl_col = "black",
+                               treat_col = "red",
+                               maxdate = as.Date("2020-01-01")) {
+  
+  ## load BERT data
+  bert_ests_raw <- 
+    fread('../data/processed/bert_crime_clean.csv')
+    
+    bert_ests <- 
+      bert_ests_raw %>% 
+      mutate(month = lubridate::floor_date(date_clean, "quarter")) %>% 
+      group_by(paper, month) %>% 
+      summarise(
+        crime_share = mean(crime_label)
+      ) %>% 
+      mutate(paper = ifelse(paper %in% c("bild", "Bild"), "Bild", "Other")) %>%
+      group_by(month, paper) %>%
+      select(crime_share) %>% 
+      summarise(
+        crime_share = mean(crime_share)
+      )
+    
+    survey_dates <- 
+      fread(here("data/processed/SurveyDates.csv")) %>% 
+      filter(as.Date(date) < as.Date(maxdate))
[…]

### 2022-06-28 code/independent/01_surveydates.R

@@ -1,0 +1,26 @@
+# ______________________________________________
+# Function preparing survey dates for treatment plot
+# ______________________________________________
+# Date:  Mon May 09 20:45:26 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+## define survey dates
+gles_p_long <- 
+  fread(here('data/raw/gles/Panel/long_cleaned.csv')); envlist <- c("gles_p_long")
+
+survey_dates <- 
+  gles_p_long %>% 
+  filter(!is.na(date_clean)) %>% 
+  filter(!is.na('1130_clean') & !is.na('1661a_clean')) %>%  
+  filter(date_clean < as.Date("2018-01-01")) %>% 
+  group_by(wave) %>% 
+  summarise(date = max(date_clean)) %>% 
+  ungroup() %>% 
+  select(date); envlist <- c(envlist, "survey_dates")
+
+fwrite(survey_dates, file = "data/processed/SurveyDates.csv")
+
+rm(envlist)

### 2022-06-28 code/independent/02c_stm_clean.R

@@ -1,0 +1,104 @@
+# ______________________________________________
+# Effect of framing on issue attitudes
+# Goal: Prepare independent variables
+# Procedure: load, transform, save
+# ______________________________________________
+# Date:  Wed Sep 08 14:20:28 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# 0. Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(here)
+library(lubridate)
+library(glue)
+
+# 1. load ####
+
+## survey data for wave dates
+attitude_dids <- read.csv(here('data/coeftable_gles_noimp.csv'))
+
+attitude_dids$paper_name <- ''
+attitude_dids$paper_name[attitude_dids$paper == 'a'] <- 'bild'
+attitude_dids$paper_name[attitude_dids$paper == 'b'] <- 'falg'
+attitude_dids$paper_name[attitude_dids$paper == 'c'] <- 'faz'
+attitude_dids$paper_name[attitude_dids$paper == 'd'] <- 'sz'
+attitude_dids$paper_name[attitude_dids$paper == 'e'] <- 'taz'
+attitude_dids$paper_name[attitude_dids$paper == 'f'] <- 'welt'
+
+load(here('data/mig_articles_topics2022-02-02.Rdata'))
+load(here('data/salience_cleaned.csv'))
+
+# 2. transform ####
+
+## 2.1 framing ####
+
+## estimate absolute frame attention
+framing_daily <- 
+  output %>% 
+  select(-date, -title, -url, -text) %>% 
+  group_by(date_new, paper) %>% 
+  summarise_all(sum) %>%
+  as_tibble()
+
+
+## estimate n of mig articles in frame set
+framing_daily$n_mig_fra <- 
+  output %>% 
+  group_by(date_new, paper) %>% 
+  summarise(n_mig_fra = n()) %>% 
+  ungroup %>% 
+  select(n_mig_fra) %>% 
+  unlist()
+
+rm(output)
+
+
+## 2.2 salience ####
+
+# estimate absolute and relative saleince
+salience_daily <- 
+  salience_raw %>% 
+  group_by(date_new, paper) %>% 
+  summarise(
+    n_mig_sal = sum(mig),
+    n_tot = n()
+  ) %>% 
+  mutate(
+    share_mig = n_mig_sal/n_tot
+  ) %>% 
+  as_tibble()
+
[…]

### 2022-06-28 code/independent/03a_bert_crime_clean.R

@@ -1,0 +1,77 @@
+# ______________________________________________
+# Quick assessment of BERT Crime Estimates
+# ______________________________________________
+# Date:  Mon May 09 11:49:57 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+envlist <- c()
+
+# load data, describe ####
+articles <- fread('data/crime_annotations.csv'); envlist <- c("articles")
+
+articles$crime_label %>% 
+  table() %>% 
+  prop.table() %>% 
+  round(2)
+
+summary(articles)
+
+# clean ####
+
+# fix probs var: IS label prob, SHOULD crime prob
+
+articles <- 
+  articles %>% 
+  mutate(
+    label_prob = crime_prob,
+    crime_prob = 
+      ifelse(
+        crime_label == 1,
+        crime_prob,
+        1 - crime_prob)
+  )
+
+
+# date
+
+articles %>% 
+  group_by(paper) %>% 
+  slice(1) %>% 
+  select(paper, date)
+
+## fix
+articles <- 
+  articles %>% 
+    mutate(
+      date_clean = 
+        case_when(
+          grepl("\\.", date) ~ as.Date(date, format = "%d.%m.%Y"),
+          grepl("-", date) ~ as.Date(date, format = "%Y-%m-%d"),
+          stringr::str_count(date) == 5 ~ as.Date(as.integer(date), origin = "1970-01-01")
+        )
+      ) %>% 
+  mutate(paper = 
+           case_when(paper %in% c("weltonline", "welt") ~ "Welt",
+                     paper == "taz"  ~ "TAZ",
+                     paper == "spon" ~ "Spiegel",
+                     paper == "faz"  ~ "FAZ",
+                     paper == "sz"   ~ "SZ",
+                     paper == "bild" ~ "Bild")); envlist <- c(envlist, "bert_ests")
+
+# check missings produced (fine, scraping wasn't fully perfect but small n of missings)
+# articles %>% filter(is.na(date_clean)) %>% select(date) %>% unique()
+# articles %>% filter(is.na(date_clean)) %>% select(paper, date) %>% table()
+
+
+fwrite(articles, 'data/processed/bert_crime_clean.csv')
+
+rm(envlist)

### 2022-06-28 code/independent/03b_bert_crime_aggregate.R

@@ -1,0 +1,12 @@
+# aggregate BERT estimates to daily measure
+prevalence <- fread(here("data/processed/bert_crime_clean.csv"))
+
+
+prevalence <- 
+  prevalence %>% 
+  select(date_clean, paper, crime_label, crime_prob) %>% 
+  group_by(date_clean, paper) %>% 
+  mutate(n_articles = 1) %>% 
+  summarise_all(sum)
+
+fwrite(prevalence, here("data/processed/bert_crime_daily.csv"))

### 2022-06-28 code/independent/04a_merge_bert.R

@@ -1,0 +1,149 @@
+# ______________________________________________
+# Media effects Bild
+# Goal: merge survey and stm data
+# ______________________________________________
+# Date:  Tue Feb 15 08:40:42 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(RcppRoll)
+
+
+gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
+
+## generate lagged dependent
+gles_p_long <- 
+  gles_p_long %>% 
+  filter(!is.na(date_clean)) %>% 
+  select(-contains("2880")) %>% 
+  group_by(lfdn) %>% 
+  dplyr::arrange(date_clean, .by_group = T) %>% 
+  mutate(
+    `1130_lag` = dplyr::lag(`1130_clean`),
+    `1210_lag` = dplyr::lag(`1210_clean`),
+    `1140_lag` = dplyr::lag(`1140_clean`),
+    `1220_lag` = dplyr::lag(`1220_clean`),
+    `430i_lag` = dplyr::lag(`430i_clean`),
+    date_str = as.character(date_clean)
+  )
+
+## prepare media estimates
+prevalence_daily <- fread(here("data/processed/bert_crime_daily.csv"))
+
+# calculate salience in relevant lag
+prevalence_daily <- 
+  prevalence_daily %>% 
+  group_by(paper) %>% 
+  mutate(
+    across(crime_label:n_articles, ~roll_sum(.x,    7, fill=NA, align = 'right', na.rm = T), .names = "{.col}_7d")
+    # across(english:n_articles, ~roll_sum(.x,    30, fill=NA, align = 'right', na.rm = T), .names = "{.col}_30d")
+    
+  )
+
+prevalence_daily <- 
+  prevalence_daily %>% 
+  pivot_wider(names_from = paper, values_from = 3:ncol(prevalence_daily)) %>% 
+  mutate(date_str = as.character(date_clean))
+
+## merge
+merged_data <- 
+  gles_p_long %>% 
+  left_join(prevalence_daily %>% 
+              select(-date_clean), by = c("date_str"))
+
+rm(gles_p_long, prevalence_daily)
+
+## replace missings, add number of newspapers read
+merged_data <- 
[…]

### 2022-06-28 code/independent/04a_merge_stm.R

@@ -1,0 +1,149 @@
+# ______________________________________________
+# Media effects bild
+# Goal: merge survey and stm data
+# ______________________________________________
+# Date:  Tue Feb 15 08:40:42 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(RcppRoll)
+
+
+gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
+
+## generate lagged dependent
+gles_p_long <- 
+  gles_p_long %>% 
+  filter(!is.na(date_clean)) %>% 
+  select(-contains("2880")) %>% 
+  group_by(lfdn) %>% 
+  dplyr::arrange(date_clean, .by_group = T) %>% 
+  mutate(
+    `1130_lag` = dplyr::lag(`1130_clean`),
+    `1210_lag` = dplyr::lag(`1210_clean`),
+    `1140_lag` = dplyr::lag(`1140_clean`),
+    `1220_lag` = dplyr::lag(`1220_clean`),
+    `430i_lag` = dplyr::lag(`430i_clean`),
+    date_str = as.character(date_clean)
+  )
+
+## prepare media estimates
+load(here("data/processed/stm_daily.Rdata"))
+
+# calculate salience in relevant lag
+merged_media <- 
+  merged_media %>% 
+  group_by(paper) %>% 
+  mutate(
+    across(n_mig_sal:n_mig_fra, ~roll_sum(.x,    7, fill=NA, align = 'right', na.rm = T), .names = "{.col}_7d")
+    # across(english:n_articles, ~roll_sum(.x,    30, fill=NA, align = 'right', na.rm = T), .names = "{.col}_30d")
+    
+  )
+
+merged_media <- 
+  merged_media %>% 
+  pivot_wider(names_from = paper, values_from = 3:ncol(merged_media)) %>% 
+  mutate(date_str = as.character(date_new))
+
+## merge
+merged_data <- 
+  gles_p_long %>% 
+  left_join(merged_media %>% 
+              select(-date_new), by = c("date_str"))
+
+rm(gles_p_long, merged_media)
+
+## replace missings, add number of newspapers read
+merged_data <- 
+  merged_data %>% 
[…]

### 2022-06-28 code/independent/old/discontinued_02_stm_treatment_bild.R

@@ -1,0 +1,28 @@
+# function preparing data for independent variable (STM)
+
+## load & transform data frame attention
+load(here("data/processed/stm_daily_2022-02-02.Rdata")); envlist <- c("merged_media")
+
+merged_media <- 
+  merged_media %>% 
+  mutate(post = date_new >= as.Date("2017-02-01"),
+         date_month = floor_date(as.Date(date_new), 'month')) %>% 
+  mutate(
+    date_month = floor_date(as.Date(date_new), 'month')
+  ) %>%
+  group_by(paper, date_month) %>%
+  summarise(across(share_mig:hungary_referendum_share, mean, na.rm = T),
+            across(n_mig_sal:n_tot, sum, na.rm = T)) %>%
+  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
+         post = date_month >= as.Date("2017-02-01")) %>% 
+  mutate(paper = ifelse(paper %in% c("bild", "Bild"), "Bild", "Other"),
+         month = date_month) %>%
+  group_by(month, paper) %>%
+  select(crime_share) %>% 
+  summarise(
+    crime_share = mean(crime_share)
+  ) %>% 
+  mutate(estimate = "STM")
+
+save(list = c("merged_media"), file = here("data/processed/stm_for_treatment.Rdata"))
+rm(envlist)

### 2022-06-28 code/independent/source.R

@@ -1,0 +1,41 @@
+# ______________________________________________
+# source file for treatment plot preparation
+# Goal: Project Goal
+# Procedure: Step 1, Step 2, Step 3
+# ______________________________________________
+# Date:  Mon May 09 20:48:08 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(data.table)
+library(here)
+library(lubridate)
+
+# generate survey dates - technically dependent variable
+source(here("code/preprocessing/independent/01_surveydates.R"))
+
+# run stm
+source(here("code/preprocessing/independent/02a_stm.R"))
+
+# label topics
+source(here("code/preprocessing/independent/02b_stm_label.R"))
+
+# generate daily estimates
+source(here("code/preprocessing/independent/02c_stm_clean.R"))
+
+# clean BERT
+source(here("code/preprocessing/independent/03a_bert_crime_clean.R"))
+
+# aggregate BERT crime estimates daily
+source(here("code/preprocessing/independent/03b_bert_crime_aggregate.R"))
+
+
+# merge estimates for individual exposure variable
+source(here("code/preprocessing/independent/04_merge.R"))
+
+

### 2022-06-28 code/old/01b_did_dv.R

@@ -1,0 +1,662 @@
+# ______________________________________________
+# Media effects on issue definitions
+# Goal: estimate DiD opinion shifts
+# Procedure: load data, broad estimation, only paper estimates
+# ______________________________________________
+# Date:  Mon Sep 13 08:36:30 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(here)
+library(dplyr)
+library(tidyverse)
+library(data.table)
+library(haven)
+library(lubridate)
+library(glue)
+library(fixest)
+
+# load data ####
+gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv')) %>% as.data.frame()
+
+## vis relevant waves
+gles_p_long %>% 
+  filter(readership != "", !is.na(`1130_clean`)) %>% 
+  ggplot(aes(date_clean, wave)) + 
+  geom_bin2d()
+
+# simple DiD for Reichelt takeover
+gles_p_long$post <- 
+  gles_p_long$date_clean > as.Date("2017-01-01")
+
+gles_p_long_nona$post <- 
+  gles_p_long_nona$date_clean > as.Date("2017-01-01")
+
+gles_p_long$treat <- 
+  gles_p_long$readership == "Bild"
+
+gles_p_long_nona$treat <- 
+  gles_p_long_nona$readership == "Bild"
+
+gles_p_long <- 
+  gles_p_long %>% 
+  filter(wave == 1) %>% 
+  mutate(imm_att = cut(`1130_clean`, breaks = c(-Inf, -1.5, 1.5, Inf), labels = c("liberal", "moderate", "conservative"))) %>% 
+  select(imm_att, lfdn) %>% 
+  right_join(gles_p_long, by = "lfdn")
+
+gles_p_long_nona <- 
+  gles_p_long_nona %>% 
+  filter(wave == 1) %>% 
+  mutate(imm_att = cut(`1130_clean`, breaks = c(-Inf, -1.5, 1.5, Inf), labels = c("liberal", "moderate", "conservative"))) %>% 
+  select(imm_att, lfdn) %>% 
+  right_join(gles_p_long_nona, by = "lfdn")
+
+
+## vis
+gles_p_long %>% 
+  filter(readership != "") %>% 
+  filter(!is.na(date_clean), wave != 5) %>% 
+  select(wave, treat, `1130_clean`, date_clean) %>% 
[…]

### 2022-06-28 code/old/02_preprocessing_iv.R

@@ -1,0 +1,161 @@
+# ______________________________________________
+# Medoia effects on opinion formation
+# Goal: Preprocess media data
+# Procedure: load, generate daily attention table
+# ______________________________________________
+# Date:  Mon Sep 20 11:58:18 2021
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# 0. Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(here)
+library(lubridate)
+library(glue)
+library(RcppRoll)
+
+# 1. load and clean ####
+
+## 1.1 framing ####
+load(here('data/mig_articles_topics.Rdata'))
+framing_raw <- output; rm(output)
+
+frames <- 
+  framing_raw %>% 
+  ungroup() %>% 
+  select(7:13) %>% 
+  colnames()
+
+# fix dates
+framing_raw$date_new <- NA_Date_
+framing_raw$date_new[framing_raw$paper == "bild"] <- framing_raw$date[framing_raw$paper == "bild"] %>% as.Date()
+framing_raw$date_new[framing_raw$paper == "faz"] <- framing_raw$date[framing_raw$paper=="faz"] %>% as.numeric() %>% as.Date(origin = "1970-01-01")
+framing_raw$date_new[framing_raw$paper == "spon"] <- framing_raw$date[framing_raw$paper=="spon"] %>% as.Date(format = "%d.%m.%Y")
+framing_raw$date_new[framing_raw$paper == "sz"] <- framing_raw$date[framing_raw$paper=="sz"] %>% as.integer() %>% as.Date(origin = "1970-01-01")
+framing_raw$date_new[framing_raw$paper == "taz"] <- framing_raw$date[framing_raw$paper=="taz"] %>% as.integer() %>% as.Date(origin = "1970-01-01")
+framing_raw$date_new[framing_raw$paper == "welt"] <- framing_raw$date[framing_raw$paper=="welt"] %>% as.integer() %>% as.Date(origin = "1970-01-01")
+framing_raw <- framing_raw[framing_raw$date_new >= as.Date('2013-01-01'),]
+framing_raw <- framing_raw %>% filter(!is.na(date_new))
+
+## 1.2 salience ####
+salience <- fread(here('data/BERT_estimates_cleaned.csv'), header = T)
[…]

### 2022-06-28 code/old/02b_did_kink_iv.R

@@ -1,0 +1,377 @@
+# foreach test
+
+
+# 0. Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(here)
+library(lubridate)
+library(glue)
+library(doParallel)
+library(tcltk)
+
+# 1. load ####
+
+## get relevant waves and dates
+gles_p_long <- 
+  fread(here('data/gles/Panel/long_cleaned.csv')) %>% 
+  as.data.frame()
+
+wavelist <- 
+  gles_p_long %>% 
+  select(wave) %>% 
+  filter(wave != 'a1', wave != 'a2') %>% 
+  unique() %>% 
+  unlist() %>% 
+  as.numeric() %>% 
+  sort()
+
+datelist_max <- c()
+datelist_min <- c()
+for (wave_treat in wavelist){
+  
+  datelist_max <- 
+    c(datelist_max,
+      gles_p_long %>% 
+        filter(wave == wave_treat) %>% 
+        select(date_clean) %>% 
+        unlist() %>% 
+        max(na.rm = T)
+    )
+  datelist_min <- 
+    c(datelist_min,
+      gles_p_long %>% 
+        filter(wave == wave_treat) %>% 
+        select(date_clean) %>% 
+        unlist() %>% 
+        min(na.rm = T)
+    )
+}
+
+datelist_max <- 
+  datelist_max %>% 
+  as.Date(origin = "1970-01-01")
+
+datelist_min <- 
+  datelist_min %>% 
+  as.Date(origin = "1970-01-01")
+
+survey_dates <- 
+  data.frame(
+    wave = wavelist,
+    date_max = datelist_max,
+    date_min = datelist_min
+  )
+
+rm(gles_p_long)
+
+## load media data
+load(here('data/media_daily_2021-11-19.Rdata'))
+
+merged_media %>% 
+  ggplot(aes(x = date_new, fill = paper)) + 
+  geom_histogram()
+
+## issue with post 2020 articles -> drop
+merged_media <- 
+  merged_media %>% 
+  filter(date_new < as.Date('2020-01-01'))
+
+
+# 2. transform ####
+
+## add relevant treatment waves for did
+merged_media$pre_wave_all <- NA # upcoming survey wave
+merged_media$pre_wave_field <- NA # upcoming survey wave
+merged_media$pre_wave_2w <- NA # upcoming survey wave
+merged_media$pre_wave_1m <- NA # upcoming survey wave
[…]

### 2022-06-28 code/old/02c_iv_edit_old.R

@@ -1,0 +1,337 @@
+# ______________________________________________
+# Media framing effects
+# Goal: Bild editorial change frame attention 
+# Procedure: load data, estimate DiD, visualise
+# ______________________________________________
+# Date:  Tue Nov 16 14:36:30 2021
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(lubridate)
+
+# load data ####
+load(here('data/media_daily_2021-11-19.Rdata'))
+framenames <- colnames(merged_media)[6:12]
+
+# estimate DiD ####
+
+## aggregate
+media_agg <- 
+  merged_media %>% 
+  filter(date_new < as.Date('2020-01-01')) %>% 
+  mutate(month = floor_date(date_new, 'months')) %>% 
+  group_by(paper, month) %>% 
+  summarise(across(share_mig:`60_share`, mean, na.rm = T))
+
+## define treatment indicator
+media_agg$edit_change <- 0
+media_agg$edit_change[media_agg$month > as.Date('2017-01-31')] <- 1
+
+
+# estimate model per newspaper per frame
+
+if (exists('model_ests')){rm(model_ests)}
+
+for (period in c('1617', 'all')){
+  for (paper in unique(media_agg$paper)){
+    for (frame in c(framenames, "share_mig")){
+      for (dv in c("Share of migration content", "Share of all articles")){
+        if(period == '1617'){
+          temp <- 
+            media_agg %>% 
+            filter(year(month) >= 2016 & (year(month) <= 2017))
+        }else{
+          temp <- media_agg
+        }
+        
+        if (dv == "Share of migration content" & (frame != "share_mig")){
+          temp$frame_share <- temp[[paste0(frame, '_share')]]
+        }else if (dv == "Share of all articles" & (frame != "share_mig")){
+          temp$frame_share <- temp[[paste0(frame, '_share')]]*temp[["share_mig"]]
+        }else if (dv == "Share of all articles" & (frame == "share_mig")){
+          next
+        }else if (frame == "share_mig"){
+          temp$frame_share <- temp$share_mig
+        }
+        
+        temp$paper_bin   <- temp$paper == paper
+        
+        
+        m_share <- lm(frame_share ~ edit_change * paper_bin, data = temp)
+        
+        if (!exists('model_ests')){
+          model_ests <- 
+            data.frame(
[…]

### 2022-06-28 code/old/02c_placebos.R

@@ -1,0 +1,288 @@
+# ______________________________________________
+# Media framing effects
+# Goal: Visualise treatment strength & placebos
+# Procedure: load data, visualise
+# ______________________________________________
+# Date:  Mon Jan 03 10:36:01 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(lubridate)
+library(rdrobust)
+
+# descriptive change ####
+
+
+## load & transform data frame attention
+load(here("data/media_daily_2022-02-02.Rdata"))
+
+merged_media <- 
+  merged_media %>% 
+  mutate(paper = recode(paper, 
+                        'bild' = 'Bild', 'faz' = 'FAZ', 'spon' = 'Spiegel',
+                        'sz' = 'SZ', 'taz' = 'TAZ', 'welt' = 'Welt'),
+         post = date_new > as.Date("2017-02-01"),
+         date_month = floor_date(as.Date(date_new), 'month'))
+
+## visualise
+
+### relative change
+merged_media %>% 
+  select(date_month, paper:share_mig, english_share:hungary_referendum_share) %>%
+  group_by(paper, date_month) %>%
+  summarise(across(share_mig:hungary_referendum_share,mean, na.rm = T)) %>%
+  pivot_longer(
+    cols = !c(paper, date_month),
+    names_to = "frame",
+    values_to = "attention"
+  ) %>%
+  mutate(post = date_month >= as.Date("2017-02-01")) %>% 
+  filter(date_month < as.Date("2020-01-01")) %>% 
+  filter(paper %in% c("Bild", "Welt", "FAZ")) %>% 
+  ggplot(aes(x = date_month, y = attention, col = paper, lty = paper)) +
+  geom_line() +
+  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") +
+  facet_wrap(~frame) +
+  ylim(c(0, 0.2)) +
+  ggtitle("Relative attention to selected migration frames in Bild and Welt, 2013-2018")
+
+
+# crime only
+merged_media %>% 
+  mutate(
+    date_month = floor_date(as.Date(date_new), 'quarter')
+  ) %>%
+  group_by(paper, date_month) %>%
[…]

### 2022-06-28 code/old/03_estimation.R

@@ -1,0 +1,192 @@
+# ______________________________________________
+# Effect of framing on issue attitudes
+# Goal: Estimate effects
+# Procedure: load, estimate
+# ______________________________________________
+# Date:  Thu Sep 09 17:24:28 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# 0. setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(here)
+library(lubridate)
+library(glue)
+library(gridExtra)
+library(stargazer)
+library(interplot)
+library(sjPlot)
+library(RcppRoll)
+  
+# 1. load data ####
+load(here("data/did_media_2021-12-15.Rdata"))
+load(here("data/kink_media_2021-12-15.Rdata"))
+
+framing_dids <- 
+  did_estimates %>% 
+  filter(!is.na(est)) %>% 
+  mutate(
+    frame = topic,
+    paper = paper_treat,
+    coef = est
+  )
+
+framing_kinks <- 
+  kink_estimates %>% 
+  filter(!is.na(est)) %>% 
+  mutate(
+    frame = topic,
+    coef = est
+  )
+
+
+rm(kink_estimates, did_estimates)
+
+
+
+attitude_dids <- read.csv(here('data/coeftable_gles_noimp.csv'))
+
+attitude_dids$paper_name <- ''
+attitude_dids$paper_name[attitude_dids$paper == 'a'] <- 'bild'
+attitude_dids$paper_name[attitude_dids$paper == 'b'] <- 'falg'
+attitude_dids$paper_name[attitude_dids$paper == 'c'] <- 'faz'
+attitude_dids$paper_name[attitude_dids$paper == 'd'] <- 'sz'
+attitude_dids$paper_name[attitude_dids$paper == 'e'] <- 'taz'
+attitude_dids$paper_name[attitude_dids$paper == 'f'] <- 'welt'
+
+
+
+# 2. estimation did ####
+
+
+## 2.1 framing ####
+
+## select relevant issues (immigration & integration)
+imm_dids <- 
+  attitude_dids %>% 
+  filter(dv == "imm")
+
+int_dids <- 
+  attitude_dids %>% 
+  filter(dv == "int")
+
+afd_dids <- 
+  attitude_dids %>%
+  filter(dv == "afd")
+  
+
+## pivot frametable wide to get 1 var/frame
[…]

### 2022-06-28 code/old/03_newFEmodel_immatt.R

@@ -1,0 +1,218 @@
+# ______________________________________________
+# media effects bild
+# Goal: estimate FE models for all frames for different ideological sbgroups
+# Procedure: load data, run models, vis 
+# ______________________________________________
+# Date:  Mon Feb 14 15:10:08 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+# load data ####
+merged_data <- fread(here('data/merged_2022-03-01.csv'))
+
+# define treatment
+merged_data <- 
+  merged_data %>% 
+  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
+         imm_att = factor(imm_att, levels = c("conservative", "moderate", "liberal", "")))
+
+
+# run models ####
+library(fixest)
+
+## 7-day lag
+merged_data_7d <- 
+  merged_data %>% 
+  filter(lag == "7")
+
+# naïve model
+merged_data_7d <- 
+  merged_data_7d %>% 
+  mutate(dv = `1130_clean`) %>% 
+  arrange(lfdn, date_clean.x) %>% 
+  group_by(lfdn) %>% 
+  mutate(dv_lag = lag(`1130_clean`))
+
+summary(lm(dv ~ crime_schlepp_share, data = merged_data_7d)) # increasingly conservatiive
+# summary(lm(dv ~ crime_schlepp_share + dv_lag, data = merged_data_7d)) # negative effect
+feglm(dv ~ crime_schlepp_share + dv_lag | wave, data = merged_data_7d) # positive
+feglm(dv ~ crime_schlepp_share + dv_lag | wave, data = merged_data_7d, cluster = c("lfdn", "wave")) # positive, sig
+# feglm(dv ~ crime_schlepp_share + dv_lag | wave, data = merged_data_7d, cluster = c("wave", "lfdn")) # positive
+
+# remove missing conditioning variables
+merged_data_7d <- 
+  merged_data_7d %>% 
+  filter(imm_att != "")
+
+# interaction model
+feglm(dv ~ crime_schlepp_share*imm_att | wave, data = merged_data_7d, cluster = c("lfdn", "wave")) # becomes stronger for libs
[…]

### 2022-06-28 code/old/03b_FEModel.R

@@ -1,0 +1,293 @@
+# ______________________________________________
+# Bild
+# Goal: Fixed effect estimates
+# ______________________________________________
+# Date:  Wed Dec 15 14:12:14 2021
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+
+#################################
+#### CODE LIKELY BROKEN HERE #### 
+#################################
+
+# (working with old dataset)
+
+# 1. individual-level model ####
+
+fread("data/merged_2022-02-15.csv")
+
+## visualise simple correlations frame exposure X opinion
+
+## immigration attitude
+
+merged_data %>%
+  filter(!is.na(`1130_clean`), wave %in% c(1, 3:8)) %>%
+  ggplot(aes(as.factor(`1130_clean`), crime_share_7d_wtd)) +
+  stat_summary(geom = "bar", fun = mean) +
+  stat_summary(geom = "errorbar", fun.data = mean_se) +
+  facet_wrap(~wave) +
+  theme_minimal() +
+  xlab('less restrictive <- migration opinion -> more restrictive') +
+  ylab('Share of crime frame in migration coverage in consumed newspapers') +
+  ggtitle('Exposure to crime frames on immigration and migration opinions across waves')
+ggsave(here('paper/vis/crime_imm_att.png'))
+
+merged_data %>%
+  filter(!is.na(`1130_clean`), wave %in% c(1, 3:8)) %>%
+  ggplot(aes(as.factor(`1130_clean`), n_mig_tot_7d_unw/n_tot_tot_7d_unw)) +
+  stat_summary(geom = "bar", fun = mean) +
+  stat_summary(geom = "errorbar", fun.data = mean_se) +
+  facet_wrap(~wave) +
+  theme_minimal() +
+  xlab('less restrictive <- migration opinion -> more restrictive') +
+  ylab('Migration content exposure') +
+  ggtitle('Exposure to migration content and migration opinions across waves')
+ggsave(here('paper/vis/salience_imm_att.png'))
+
+
+### integration attitude
+merged_data %>%
+  filter(!is.na(`1210_clean`), wave %in% c(1, 4:8)) %>%
+  ggplot(aes(as.factor(`1210_clean`), crime_share_7d_wtd)) +
[…]

### 2022-06-28 code/old/03new_bootstrapped_case_did.R

@@ -1,0 +1,409 @@
+# ______________________________________________
+# Media effects
+# Goal: Estimate case DiDs with bootstraps
+# Procedure: load data, define vars, estimation
+# ______________________________________________
+# Date:  Thu Feb 03 14:54:48 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(fixest)
+library(boot)
+
+# load data ####
+
+## load cleaned survey data
+gles_p_long <- 
+  fread(here('data/gles/Panel/long_cleaned.csv'))
+
+## get rid of missings in relevant waves to avoid sample attrition
+gles_p_wide_nona <- 
+  gles_p_long %>% 
+  filter(wave %in% c(1, 3, 4, 6:8)) %>% 
+  select(lfdn, wave, date_clean,
+         # voteint_w1, # party vote
+         # `1661a_bin`, # Bild readership
+         # `1661a_clean`, # Bild days/week
+         contains("1661"), # newspaper use
+         `1600_clean`, # political internet use
+         # `1610_bin`, # political social media use
+         print_sources_n, # n of newspapers consumed
+         news_sources_n, # print and tv sources consumed
+         `1130_clean`, # immigration attitude
+         imm_att # immigration attitude first wave
+  ) %>% 
+  pivot_wider(id_cols = lfdn, names_from = wave, 
+              values_from = date_clean:imm_att) %>% 
+  na.omit()
+
+
+
+# define vars ####
+gles_p_long_nona <- 
+  gles_p_wide_nona %>% 
+  pivot_longer(cols = `date_clean_1`:`imm_att_8`, 
+               names_to = c(".value", "wave"),
+               names_pattern = "(.*)_(.)"
+  )
+rm(gles_p_wide_nona)
+
+fwrite(gles_p_long_nona, file = here('data/gles/Panel/long_cleaned_nona.csv'))
+
+## define post-period
+gles_p_long_nona$post <- 
+  gles_p_long_nona$date_clean >= as.Date("2017-02-01")
+
[…]

### 2022-06-28 code/old/04_vis.R

@@ -1,0 +1,719 @@
+# ______________________________________________
+# Effect of framing on issue attitudes
+# Goal: Visualisation
+# Procedure: Step 1, Step 2, Step 3
+# ______________________________________________
+# Date:  Thu Sep 09 17:46:22 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(ggExtra)
+library(glue)
+library(haven)
+library(gridExtra)
+library(lubridate)
+library(ggpubr)
+
+# Step 1 ####
+
+## 2.1 vis dependents ####
+
+## load data
+gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv'))
+
+# ## immigration attitude across time
+# imm_mean <- 
+#   gles_p_long %>%
+#   group_by(wave) %>% 
+#   filter(!is.na(`1130_clean`)) %>% 
+#   summarise(immigration = mean(`1130_clean`),
+#             immigration_sd = sd(`1130_clean`),
+#             date_clean  = max(date_clean),
+#             respondents = n()) %>% 
+#   mutate(
+#     imm_up = (immigration + qt(1 - (0.05/2), respondents - 1)*immigration_sd/respondents),
+#     imm_low = (immigration - qt(1 - (0.05/2), respondents - 1)*immigration_sd/respondents),
+#   ) %>% 
+#   ggplot(aes(x = date_clean)) +
+#   geom_line(aes(y = immigration), col = "red") +
+#   geom_ribbon(aes(ymax = imm_up, ymin = imm_low), fill = "red") +
+#   ggtitle("Immigration attitude in Germany across time", 
+#           "Should immigration of foreigners be made easier (-3) or restricted (3) \nData: GLES Panel, waves 1-13, a1 & a2")
+# 
+# ### exclusive readers
+# 
+# ## integration attitude across time
+# int_mean <- 
+#   gles_p_long %>%
+#   group_by(wave) %>% 
+#   filter(!is.na(`1210_clean`)) %>% 
+#   summarise(integration = mean(`1210_clean`)*(-1),
+#             integration_sd = sd(`1210_clean`),
+#             date_new  = max(as.Date(date_clean, unit = 'days')),
[…]

### 2022-06-28 code/old/04_vis.spin.R

@@ -1,0 +1,662 @@
+# ______________________________________________
+# Effect of framing on issue attitudes
+# Goal: Visualisation
+# Procedure: Step 1, Step 2, Step 3
+# ______________________________________________
+# Date:  Thu Sep 09 17:46:22 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(ggExtra)
+library(glue)
+library(haven)
+library(gridExtra)
+library(lubridate)
+library(ggpubr)
+
+# Step 1 ####
+
+## 2.1 vis dependents ####
+
+## load data
+gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv'))
+
+# ## immigration attitude across time
+# imm_mean <- 
+#   gles_p_long %>%
+#   group_by(wave) %>% 
+#   filter(!is.na(`1130_clean`)) %>% 
+#   summarise(immigration = mean(`1130_clean`),
+#             immigration_sd = sd(`1130_clean`),
+#             date_clean  = max(date_clean),
+#             respondents = n()) %>% 
+#   mutate(
+#     imm_up = (immigration + qt(1 - (0.05/2), respondents - 1)*immigration_sd/respondents),
+#     imm_low = (immigration - qt(1 - (0.05/2), respondents - 1)*immigration_sd/respondents),
+#   ) %>% 
+#   ggplot(aes(x = date_clean)) +
+#   geom_line(aes(y = immigration), col = "red") +
+#   geom_ribbon(aes(ymax = imm_up, ymin = imm_low), fill = "red") +
+#   ggtitle("Immigration attitude in Germany across time", 
+#           "Should immigration of foreigners be made easier (-3) or restricted (3) \nData: GLES Panel, waves 1-13, a1 & a2")
+# 
+# ### exclusive readers
+# 
+# ## integration attitude across time
+# int_mean <- 
+#   gles_p_long %>%
+#   group_by(wave) %>% 
+#   filter(!is.na(`1210_clean`)) %>% 
+#   summarise(integration = mean(`1210_clean`)*(-1),
+#             integration_sd = sd(`1210_clean`),
+#             date_new  = max(as.Date(date_clean, unit = 'days')),
[…]

### 2022-06-28 code/old/05_RISK.R

@@ -1,0 +1,137 @@
+# ______________________________________________
+# Effect of framing on issue attitudes
+# Goal: Estimate risk-models of stopping to consume newspaper
+# Procedure: load data, prepare, estimate
+# ______________________________________________
+# Date:  Wed Jan 12 11:12:28 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(ggpubr)
+library(survival)
+library(survminer)
+library(fixest)
+
+# load data ####
+gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv'))
+
+
+# prepare ####
+
+## select bild readers from first wave
+bild_readers_w1 <- 
+  gles_p_long %>% 
+  filter(wave == 1 & `1661a_clean` > 0) %>% 
+  select(lfdn) %>% 
+  unlist()
+
+risk_set <- 
+  gles_p_long %>% 
+  filter(lfdn %in% bild_readers_w1) 
+
+## define immigration attitude and afd support based on first wave
+risk_set <- 
+  risk_set %>% 
+  filter(wave == 1) %>% 
+  mutate(imm_att = cut(`1130_clean`, breaks = c(-Inf, -1.5, 1.5, Inf), labels = c("liberal", "moderate", "conservative")),
+         afd_att = cut(`430i_clean`, breaks = c(-Inf, -1.5, 1.5, Inf), labels = c("negative", "ambiguous", "positive"))) %>% 
+  select(imm_att, afd_att, lfdn) %>% 
+  right_join(risk_set, by = "lfdn")
+  
+
+# estimate ####
+
+## vis declines in readership
+readers_imm <- 
+  risk_set %>% 
+  group_by(imm_att, wave) %>% 
+  filter(!is.na(imm_att), !is.na(`1661a_clean`)) %>% 
+  summarise(bild_reader = mean(`1661a_clean` > 0, na.rm = T),
+            date_clean = mean(date_clean)) %>% 
+  ggplot(aes(x = date_clean, y = bild_reader, col = imm_att, lty = imm_att)) +
+  geom_line() + geom_point() +
+  ylim(c(0,1)) + ylab("Reader share") + xlab("Wave") +
[…]

### 2022-06-28 code/old/05_main_models.R

@@ -1,0 +1,552 @@
+# ______________________________________________
+# Effect of framing on issue attitudes
+# Goal: Estimate effects
+# Procedure: load, estimate
+# ______________________________________________
+# Date:  Thu Sep 09 17:24:28 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# 0. setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(here)
+library(lubridate)
+library(glue)
+library(gridExtra)
+library(stargazer)
+library(sjPlot)
+
+# 1. load data ####
+load(here("data/media_daily_wlags.Rdata"))
+gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv'))
+
+
+# 2. estimation and vis ####
+
+## 2.1 prepare individual estimates dependent variable ####
+
+
+## 2.2 prepare daily media estimates ####
+
+media_attention <- 
+  media_attention %>% 
+  pivot_wider(names_from = paper, values_from = 3:ncol(media_attention)) %>% 
+  mutate(date_str = as.character(date_new)) %>% 
+  select(contains('7d'), contains('30d'), date_str)
+
+gles_p_long <- 
+  gles_p_long %>% 
+  select(contains('1661'), lfdn, wave, date_clean, 
+         `1130_clean`, `1210_clean`, `1140_clean`, `1220_clean`) %>% 
+  filter(wave > 2, wave < 9)
+
+
+## merge
+merged_data <- 
+  gles_p_long %>% 
+  mutate(date_str = as.character(date_clean)) %>% 
+  inner_join(media_attention, by = c("date_str"))
+
+
+
+## estimate frame exposure
+# merged_data <- 
+#   merged_data %>% 
+#   mutate(
+#     n_tot_7d_bild = ifelse(is.na(n_tot_7d_bild), 0, n_tot_7d_bild),
[…]

### 2022-06-28 code/old/NEW_final_ests.R

@@ -1,0 +1,275 @@
+# ______________________________________________
+# Bild
+# Goal: Estimate FE model w values and attentiveness
+# Procedure: load, estimation, save
+# ______________________________________________
+# Date:  Tue Mar 01 23:22:33 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(fixest)
+
+# run other scripts (only once)
+
+# source(here("code/01a_preprocessing_dv.R")) # clean survey data
+# rm(list = ls())
+# source(here("code/03a_merge.R")) # merge to text estimates
+# rm(list = ls())
+
+
+# load ####
+merged_data <- fread(file = paste0("data/merged_2022-03-05.csv"))
+
+merged_data <- 
+  merged_data %>% 
+  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
+         # imm_att = factor(imm_att, levels = c("conservative", "moderate", "liberal", "miss")),
+         dv = `1130_clean`) %>% 
+  filter(lag == 7)
+
+merged_data <- 
+  merged_data %>% 
+  filter(!is.na(`1130_clean`)) %>% 
+  group_by(lfdn) %>% 
+  arrange(lfdn, date_clean.x) %>% 
+  select(`1130_clean`, lfdn) %>% 
+  slice(1) %>% 
+  mutate(init_mig = `1130_clean`) %>%
+  select(init_mig, lfdn) %>% 
+  right_join(merged_data, by = "lfdn")
+
+# add lagged crime_share and dv
+merged_data <- 
+  merged_data %>%
+  ungroup() %>% 
+  arrange(lfdn, date_clean.x) %>% 
+  group_by(lfdn) %>% 
+  filter(!is.na(crime_share)) %>% 
+  mutate(crime_share_lag = lag(crime_share),
+         dv_lag = lag(dv))
+
+# estimation ####
+
+# individual exposure ####
+
+# direct crime
+feglm(dv ~ crime_share | wave + lfdn,  # positive, p < 0.1
+      cluster = c("lfdn"), data = merged_data)
+
+feglm(dv ~ crime_share + dv_lag | wave,  # positive, highly significant
+      cluster = c("lfdn"), data = merged_data)
+
+# crime X initial imm_att
[…]

### 2022-06-28 code/old/_mig_dict.R

@@ -1,0 +1,98 @@
+# ______________________________________________
+# causal effect of media frames
+# Goal: extend migration dictionary
+# Procedure: set params, generate & save
+# ______________________________________________
+# Date:  Fri Apr 23 18:13:56 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+
+
+# Setup ####
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(ggplot2)
+library(gridExtra)
+library(word2vec)
+library(here)
+library(lsa)
+library(pbapply)
+
+# generate one overall dict, based on german wiki model ####
+
+
+# define dicts
+seed_dict <- c("asyl", "asylant", "asylanten", "asylantinnen", 
+               "asylbewerber", "asylbewerberin", "asylbewerberinnen", 
+               "auslander","auslanderinnen", 
+               "einwanderer", "einwandererin", "einwandererinnen", "einwandernde", "einwanderung",  
+               "fluchtling", "fluchtende", "fluchtlinge",
+               "migration", "immigration", 
+               "schutzsuchende", "schutzbedurftige",
+               "visa", "visum", 
+               "zuwanderung", "zuwanderer",  "zuwandernde",
+               "ausländer", "ausländerinnen", 
+                 "flüchtling", "flüchtende", "flüchtlinge", 
+                 "schutzbedürftige")
+
+## see https://deepset.ai/german-word-embeddings (GloVe)
+
+## load pre-trained embeddings, if not already (get a coffee, this runs a bit)
+if (!file.exists('_emb_models/glove.german.txt')) {
+  download.file('https://int-emb-glove-de-wiki.s3.eu-central-1.amazonaws.com/vectors.txt', 
+                destfile = '_emb_models/glove.german.txt')
+}
+
+vectors = data.table::fread('_emb_models/glove.german.txt', data.table = F,  encoding = 'UTF-8')
+colnames(vectors) = c('word', paste('dim', 1:(dim(vectors)[2] - 1), sep = '_'))
+embeddings <- as.matrix(vectors[2:301])
+row.names(embeddings) <- vectors$word; rm(vectors)
+
+## extend dict
+temp_dict <- seed_dict[seed_dict %in% row.names(embeddings)]
+
+## generate cosin similarity matrix for the relevant terms to all others (lunchtime!)
[…]

### 2022-06-28 code/old/add_embreg_bild_crime.R

@@ -1,0 +1,156 @@
+# ______________________________________________
+# Media effects Bild
+# Goal: Assess crime association of migration in Bild
+# Procedure: load data, run regression, vis
+# ______________________________________________
+# Date:  Tue Feb 22 18:39:54 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(text2vec)
+library(quanteda)
+library(conText)
+library(glue)
+
+# load data ####
+papers <- 
+  list.files(here("data/newspapers")) %>% 
+  stringr::str_match("_(.*)_.*") %>% 
+  as_tibble() %>% 
+  select(V2) %>% 
+  filter(!grepl(pattern = "2019", V2) & !grepl(pattern = "article", V2)) %>% 
+  unlist()
+
+# embeddings
+load(here("data/local_glove.Rdata"))
+
+# transformation matrix
+load(here("data/trns_mtrx.Rdata"))
+
+
+# define terms
+mig_term <- "*migrant*"
+crime_terms <- c("täter", "verbrechen", "kriminell", "illegal", "festgenommen")
+
+# define empty tibble
+immig_cs <- tibble()
+
+
+for (paper in papers){
+  
+  
+  if (!file.exists(here(glue("data/toks_{paper}.Rdata")))){
+    
+    print(glue("Tokenizing {paper} articles..."))
+  
+    # articles
+    articles <- 
+      fread(here(glue("data/newspapers/_{paper}_articles.csv"))) %>%  # add other NPs to run DiD at later stage
+      mutate(ext = tolower(text)) %>% 
+      select(date, text) %>% 
+      mutate(paper = paper) %>% 
+      filter(!is.na(date))
+      
+    # create covariate
+    articles <- 
+      articles %>% 
+      mutate(
+        date = as.Date(date, 
+                       origin = "1970-01-01", 
+                       format = ifelse(paper == "spon", "%d.%m.%Y", "%Y-%m-%d"))
+          )
+    
+    
+    articles$year <- lubridate::year(articles$date)
+    articles$month <- lubridate::month(articles$date)
+    articles$ym <- paste(articles$year, articles$month, sep = "-")
+  
+  
+  
+    # transform ####
+    
+    # create corpus
[…]

### 2022-06-28 code/old/add_local_np_dist.R

@@ -1,0 +1,48 @@
+# ______________________________________________
+# Emphasis framing in the wild
+# Goal: Explore data newspaper distribution
+# Procedure: load data, merge, vis
+# ______________________________________________
+# Date:  Thu Dec 02 10:37:28 2021
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+# load data ####
+path_2016 <- "data/auflage/local/Div VA/VA2016_1_1/Verbreitungsanalyse Tageszeitungen 2016/IVW VA 2016 Daten Vollversion/WIN/"
+
+## distribution
+local_dist <- read.fwf(here(paste0(path_2016, "IVWAUF.TXT")),
+                       width = c(11, 8, 7, 7),
+                       col.names = c("VA", "AGS", "sold_tot", "sold_epaper"))
+
+
+## local id lookup
+local_id   <- read.fwf(here(paste0(path_2016, "IVWORT.TXT")), 
+                       width = c(8, (35-8), (43-35), (46-43), (47-46), (48-47), (53-48), (61-53), (69-61), (77-69), (85-77), (93-85), (101-93), (109-101), (117-109), (125-117), (133-125), (141-133)),
+                       col.names = c("AGS", "Gebietsname", "leer", "NUTS21312", "SGTyp", "Webb", "PLZ", "Einwohner deutsch", "Einwohner ab 14 Jahre deutsch", "Einwohner 14-29 Jahre deutsch", "Einwohner 30-49 Jahre deutsch", "Einwohner ab 50 Jahre deutsch", "Haushalte deutsch", "Haushalte 14-29 deutsch", "Haushalte 30-49 deutsch", "Haushalte ab 50 deutsch", "Einwohner gesamt", "Haushalte gesamt"))
+
+## paper id lookup
+paper_id   <- read.fwf(here(paste0(path_2016, "IVWTIT.TXT")), 
+                       width = c(11, (59-11), (107-59), (155-107), (185-155), (215-185), (245-215), (255-245), (261-255), (266-261), (274-261), (282-274), (290-282), (298-290), (306-298), (314-306), (315-314), (318-315)),
[…]

### 2022-06-28 code/old/add_media_diversification.R

@@ -1,0 +1,29 @@
+# ______________________________________________
+# Media framing effects
+# Goal: Visualise media diversification
+# Procedure: load data, visualise data
+# ______________________________________________
+# Date:  Wed Feb 02 16:52:43 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(haven)
+
+# load data ####
+
+## URL: https://data.gesis.org/sharing/vaadinServlet/APP/connector/3/678/dl/MA_Zeitschriften_gesamt_54_09_MLFZ.sav.rar
+MA_Zeit <- 
+  subset(read_sav("data/media_markets/MA_Pressemedien_gesamt_54_09_MLFZ.sav"))
+
+
+## URL: https://data.gesis.org/sharing/vaadinServlet/APP/connector/3/718/dl/MA_Pressemedien_gesamt_54_09_MLFZ.7z
+
+
+# visualise data ####

### 2022-06-28 code/old/add_risk.R

@@ -1,0 +1,85 @@
+# ______________________________________________
+# Bild
+# Goal: Estimate risk of stopping to read
+# Procedure: load, prepare, risk model
+# ______________________________________________
+# Date:  Wed Dec 15 14:14:26 2021
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+# load ####
+gles_p_long <- fread(here('data/gles/Panel/long_cleaned.csv'))
+
+# migration trend of bild readers vs non-readers ####
+bild_readers_w1 <- 
+  gles_p_long %>% 
+  filter(`1661a_clean` > 0 & wave == "1") %>% 
+  select(lfdn) %>% 
+  unlist() %>% 
+  unique()
+
+bild_nonreaders_w1 <- 
+  gles_p_long %>% 
+  filter(`1661a_clean` == 0 & wave == "1") %>% 
+  select(lfdn) %>% 
+  unlist() %>% 
+  unique()
+
+gles_p_long <- 
+  gles_p_long %>% 
+  mutate(bild_w1 = case_when(lfdn %in% bild_readers_w1 ~ T,
+                             lfdn %in% bild_nonreaders_w1 ~ F))
+
+gles_p_long %>% 
+  filter(!is.na(bild_w1)) %>% 
+  filter(!is.na(`1130_clean`)) %>% 
+  filter(!is.na(date_clean)) %>% 
+  group_by(wave, bild_w1) %>% 
+  summarise(imm_op = mean(`1130_clean`),
+            date_clean = max(date_clean)) %>% 
+  ggplot(aes(x = date_clean, y = imm_op, col = bild_w1)) +
+  geom_line()
+
+# prepare ####
+
+## select only Bild readers ####
+bild_dta <- 
+  gles_p_long %>% 
+  filter(lfdn %in% bild_readers_w1)
+
+# construct dataset
+bild_dta <- 
+  bild_dta %>%
+  mutate(
+    stop_read = `1661a_clean` == 0
+  )
+
+table(bild_dta$wave, bild_dta$stop_read)
+
+# visualisation
+
+
+# log reg per wave ####
+gles_p_long %>% 
+  filter(!is.na(`1661a_bin`) & !is.na(`1130_clean`)) %>% 
+  group_by(wave) %>% 
[…]

### 2022-06-28 code/old/bootstrap_test.R

@@ -1,0 +1,160 @@
+# test bootstrap
+gles_p_long <- 
+  fread(here('data/gles/Panel/long_cleaned.csv')) %>% as.data.frame()
+
+gles_p_long$post <- 
+  gles_p_long$date_clean > as.Date("2017-01-01")
+
+gles_p_long$treat <- 
+  gles_p_long$readership == "Bild"
+
+gles_p_long <- 
+  gles_p_long %>% 
+  filter(wave == 1) %>% 
+  mutate(imm_att = cut(`1130_clean`, breaks = c(-Inf, -1.5, 1.5, Inf), labels = c("liberal", "moderate", "conservative"))) %>% 
+  select(imm_att, lfdn) %>% 
+  right_join(gles_p_long, by = "lfdn")
+
+
+boot_sample <- 
+  gles_p_long %>% 
+  mutate(
+    dv = `1130_clean`,
+    iv = treat
+  ) %>% 
+  select(lfdn, wave, iv, dv, post, imm_att) %>% 
+  pivot_wider(id_cols = c(lfdn), values_from = c(iv, dv, imm_att, post), names_from = c(wave)) %>% 
+  sample_n(1000)
+
+  
+library(boot)
+set.seed(42)
+B <- 100
+
+effs1 <- function(dat, inds){
+  
+  # sample observations, then wide to long
+  dta_model <- 
+    dat[inds,] %>% 
+    pivot_longer(cols = contains("iv"), names_to = "wave", values_to = "iv", names_prefix = "(.*)_") %>% 
+    select(lfdn, wave, iv)
+  
+  dta_model <- 
+    dat[inds,] %>% 
+    pivot_longer(cols = contains("dv"), names_to = "wave", values_to = "dv", names_prefix = "(.*)_") %>% 
+    select(c(contains("dv"), wave, lfdn)) %>% 
+    left_join(., dta_model, by = c("wave", "lfdn"))
+  
+  dta_model <- 
+    dat[inds,] %>% 
+    pivot_longer(cols = contains("imm_att"), names_to = "wave", values_to = "imm_att", names_prefix = "(.*)_") %>% 
+    select(c(contains("imm_att"), wave, lfdn)) %>% 
+    left_join(., dta_model, by = c("wave", "lfdn"))
+  
+  
+  dta_model <- 
+    dat[inds,] %>% 
[…]

### 2022-06-28 code/old/dv_transform_est.R

@@ -1,0 +1,470 @@
+
+# estimate DiD for each issue-paper-wave-combination
+
+library(here)
+library(dplyr)
+library(tidyverse)
+library(data.table)
+library(haven)
+library(lubridate)
+library(glue)
+library(fixest)
+
+gles_p <- read_dta(here('data/gles/Panel/GLESMerge/ZA6838_allwaves_sA_v4-0-0.dta'))
+
+## id var
+gles_p$lfdn <- as.factor(gles_p$lfdn)
+
+
+## date
+date_vars <- colnames(gles_p)[grep(pattern = 'datetime', colnames(gles_p))]
+date_waves <- str_match(date_vars, 'kp(.*)_')[,2]
+
+### generate cleaned variables
+for (i in 1:length(date_vars)){
+  
+  new_var <- paste0('date_w', date_waves[i])
+  
+  gles_p[[new_var]] <- NA
+  
+  gles_p <- gles_p
+  
+  subset <- gles_p[[date_vars[i]]] > 0 & (!is.na(gles_p[[date_vars[i]]]))
+  
+  gles_p[[new_var]][subset] <- gles_p[[date_vars[i]]][subset]
+  
+}
+
+
+date_vars <- colnames(gles_p)[grep(pattern = 'date_w', colnames(gles_p))]
+
+## extract ego-issues
+ego_issues <- 
+  str_match(
+    string = colnames(gles_p), 
+    pattern = "kp.*\\d+_2880(.*)"
+  )[,2] %>% 
+  unique()
+ego_issues <- paste0("2880", ego_issues[!is.na(ego_issues)])
+
+coeflist_medium <- c()
+coeflist_paper <- c()
+coeflist_issue <- c()
+coeflist_wave  <- c()
+coeflist_date <- c()
+coeflist_coef_lm <- c()
+coeflist_p_lm <- c()
+coeflist_coef_fe <- c()
+coeflist_p_fe <- c()
+
+
+
+
+
+mediumlist <- c('1681', '1661')
+
+for (medium in mediumlist){
+  
+  if (medium == '1661'){
+    papers_list <- letters[1:7]
+    non_reader_var <- letters[8]
+  }else{
+    papers_list <- letters[1:5]
+    non_reader_var <- letters[6]
+  }
+  
+  for (paper in papers_list){
+    for (issue in c(ego_issues, "1500", "1090", "1130", 
+                    "1290", "1210", "1140", "1220", "1300", 
[…]

### 2022-06-28 code/old/explore_handcoding.R

@@ -1,0 +1,101 @@
+# ______________________________________________
+# Explore handcodings RA's
+# ______________________________________________
+# Date:  Tue Apr 19 16:32:17 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+# load
+
+# crime_coding_nico <- 
+#   fread(here("data/handcoding/crime/handcoding_nico.csv"))
+
+crime_coding_nat <- 
+  fread(here("data/handcoding/crime/nathalie/handcoding_nathalie.csv"), encoding = "UTF-8")
+
+crime_coding_rob <- 
+  fread(here("data/handcoding/crime/robin/handcoding_robin.csv"), encoding = "UTF-8")
+
+## descriptives
+table(crime_coding_nat$crime) # 25.5% Crime
+table(crime_coding_rob$crime) # 25.4% Crime
+
+## correlation of codings
+common_nat <- 
+  crime_coding_nat %>% 
+  filter(url %in% crime_coding_rob$url) %>% 
+  arrange(url)
+
+common_rob <- 
+  crime_coding_rob %>% 
+  filter(url %in% crime_coding_nat$url) %>% 
+  arrange(url)
+
+# correlation table - not so great
+table(common_nat$crime, common_rob$crime)
+
+# cor: 0.79
+cor(common_nat$crime == "Ja", common_rob$crime == "Ja")
+
+
+# merge
+
+coding_merge <- 
+  crime_coding_nat %>% 
+  full_join(crime_coding_rob, by = c("url", "title", "text")) %>% 
+  mutate(crime.nat = crime.x, crime.rob = crime.y) %>% 
+  select(-crime.x, -crime.y)
+
+# assess differences
+
+## Nathalie yes, Robin no - mostly not crime but foreign news
+coding_merge %>% 
+  filter(crime.nat == "Ja", crime.rob == "Nein") %>% 
+  select(title)
+
+
+## Nathalie no, Robin yes - mostly crime
+coding_merge %>% 
+  filter(crime.nat == "Nein", crime.rob == "Ja") %>% 
+  select(title)
+
+# generate merge file with robin overriding Nathalie
+training_data <- 
+  crime_coding_nat %>%
+  filter(!url %in% crime_coding_rob$url) %>% 
[…]

### 2022-06-28 code/old/gles_explore.R

@@ -1,0 +1,358 @@
+# ______________________________________________
+# Effects of changing media frames - case of Bild
+# Goal: Data overview GLES
+# Procedure: load, explore
+# ______________________________________________
+# Date:  Wed Apr 07 16:32:03 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(here)
+library(data.table)
+library(haven)
+library(gridExtra)
+library(magrittr)
+
+#  Rolling cross section ####
+gles_rc <- read_dta(here('data/gles/RCS/ZA6834_v1-0-0.dta'))
+
+## BILD
+### Lesen Sie gelegentlich oder regelmäßig die BILD-Zeitung? (Falls ja, an wie vielen Tagen pro Woche lesen Sie politische Berichte?)
+gles_nna <- gles_rc[gles_rc$pre2401 > 0, ]
+table(gles_nna$pre2401)
+
+gles_nna$bild <- gles_nna$pre2401 < 7
+sum(gles_nna$bild == 1) # 2049 Bild readers total
+sum(gles_nna$bild == 1)/nrow(gles_nna) # ~10%
+
+### unique readers per wave: 627 - 715
+t1 <- table(gles_nna$bild, gles_nna$year)
+t1
+round(prop.table(t1, margin = 2), 2)
+t1 %>% tableGrob() %>% grid.arrange()
+
+
+## MIP open question: pre1001_org (not available, check .sav)
+
+## MIP open question: pre1001_org (.sav; not available - mail went out to GLES)
+# gles_rc <- read_sav('data/gles/ZA6834_v1-0-0.sav')
+
+## Integration attitude: 
+  # pre1401f (2013 pre: Einwanderer an dt. Kultur anpassen) 
+  # pos1001a_2 (2013 post: Einwanderer an dt. Kultur anpassen) 
+  # pos1001a_1 (2017: Einwanderer an dt. Kultur anpassen) 
+
+## Immigration attitude:
+  # Zuwanderung: ego position pre1302 (2017)
+  # Zuwanderung: ego position pos0901 (2017)
+
+## Wahlentscheidung: pos0303a, pos0303b, pos0304a, pos0304b
+
+
+rm(list = ls())
+
+
+
+
+
+# Panel ####
[…]

### 2022-06-28 code/old/no_sentiment_vis.R

@@ -1,0 +1,162 @@
+# ______________________________________________
+# Bild
+# Goal: Estimate migration sentiment in nps
+# ______________________________________________
+# Date:  Fri May 21 08:30:00 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(here)
+library(data.table)
+library(lubridate)
+library(Hmisc)
+
+# parameters ####
+paper_list <- c("bild", "faz", "spon", 'sz')
+aggregation <- "quarter"
+
+for (paper in paper_list){
+  print(paper)
+    # load data ####
+    dta <- fread(here(paste0("data/np_sentiment_bert/", paper, "_estimates.csv")))
+    
+    if (paper == "faz" | paper == "sz"){
+      dta$date <- as.Date(dta$date, origin = "1970-01-01")
+    }else if (paper == "spon"){
+      dta$date <- as.Date(dta$date, format = "%d.%m.%Y")
+    }
+    
+    dta$time_agg <- floor_date(dta$date, aggregation)
+    
+    
+    ## aggregate to new dataframe
+    temp <- dta %>%
+      select(time_agg, mig_sent, mig_sent_n) %>%
+      group_by(time_agg) %>%
+      summarise(mean_mig_sent = mean(mig_sent, na.rm = T),
+                wtd_mean_mig_sent = wtd.mean(mig_sent, weights = mig_sent_n, na.rm = T, normwt = T),
+                sd_mig_sent = sd(mig_sent, na.rm = T),
+                n_mig = n() - sum(is.na(mig_sent))
+                )
+    temp$se_mig_sent <- temp$sd_mig_sent/sqrt(temp$n_mig)
+    
+    x <- paste0("dta_sum_", paper)
+    eval(call("<-", as.name(x), temp))
+    
+    ## add CIs
+    
+    ## single np graph [add CI]
+    temp <- get(paste0("dta_sum_", paper)) %>% 
+      ggplot(aes(x = time_agg)) +
+      geom_line(aes(y = mean_mig_sent, col = "raw")) +
+      geom_line(aes(y = wtd_mean_mig_sent, col = "weighted")) +
+      ggtitle("Sentiment in migration-related sentences", paper)
+    
+    ggsave(filename = here(paste0("github/bild/paper/", paper, "_sentiment_migration.png")),
[…]

### 2022-06-28 code/old/np_slant.R

@@ -1,0 +1,46 @@
+# ______________________________________________
+# causal effect of media frames
+# Goal: estimate migration slant in papers
+# Procedure: identify mentions, extract windows, measure slant
+# ______________________________________________
+# Date:  Wed May 19 12:22:30 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(here)
+library(data.table)
+library(word2vec)
+library(stringr)
+
+## load dict
+mig_dict <- sort(read.csv(here("data/embeddings/german_glove.csv"))$x)
+pos_dict <- c()
+neg_dict <- c()
+
+papers <- c("bild", "faz", "spon", "sz", "taz", "weltonline")
+window_size <- 5
+
+for (p in papers){
+  
+  cat(paste("\n\nEstimating migration slant in", p, "..."))
+  
+  ## load newspaper articles
+  cat("\n\tLoading data...")
+  dta <- fread(here(paste0("data/newspapers/_", p, "_articles.csv")), encoding = "UTF-8")[,c("title", "url", "text")]
+  dta <- dta[text != "",]
+  
+  # identify mentions ####
+  
+  ## get kwic windows based on mig_dict
+  cat("\n\tExtract windows...")
+  kwicVec <- kwic(dta$text, pattern = mig_dict, window = window_size, case_insensitive = T)
+  
+  # extract windows ####
+  
+  # measure slant ####
+
+  }

### 2022-06-28 code/old/old_ind_models.R

@@ -1,0 +1,460 @@
+
+# old individual models
+
+# #############################################################################
+# ###################### OLD BELOW HERE #######################################
+# #############################################################################
+# 
+# ## unweighted independent
+# imm_mod_unw_all_nosal <- 
+#   merged_data %>% 
+#   lm(data = .,
+#      formula = 
+#        `1130_clean` ~ 
+#        `1130_lag` + 
+#        crime_tot_7d_unw + 
+#        capcrime_tot_7d_unw + 
+#        refnums_tot_7d_unw + 
+#        camps_tot_7d_unw + 
+#        medit_tot_7d_unw + 
+#        labmar_tot_7d_unw + 
+#        deport_tot_7d_unw )
+# 
+# mod_tbl <- summary(imm_mod_unw_all_nosal) 
+# 
+# 
+# longnames <- c('(Intercept)', 'Lagged DV', 'Petty Crime', 'Capital Crime', 'Refugee Numbers', 'Camps', 'Mediterranean Rescue', 'Labour Market', 'Deportations')
+# arm::coefplot(imm_mod_unw_all_nosal, longnames) %>% 
+#   ggsave(filename = here('paper/vis/individual_effects_immigration.png'),
+#                          width = 8, height = 6)
+# 
+# 
+# # integration
+# int_mod_unw_all_nosal <- 
+#   merged_data %>% 
+#   lm(data = .,
+#      formula = 
+#        `1210_clean` ~ 
+#        `1210_lag` + 
+#        crime_tot_7d_unw + 
+#        capcrime_tot_7d_unw + 
+#        refnums_tot_7d_unw + 
+#        camps_tot_7d_unw + 
+#        medit_tot_7d_unw + 
+#        labmar_tot_7d_unw + 
+#        deport_tot_7d_unw )
+# 
+# summary(int_mod_unw_all_nosal) # capcrime negative (expected), deport positive (also expected), but surprisingly labmar no effect
+# 
+# stargazer(imm_mod_unw_all_nosal, 
+#           int_mod_unw_all_nosal,
+#           title = 'Individual-level Model', 
+#           out = here('paper/imm_unw.tex'))
+# 
[…]

### 2022-06-28 code/old/pivot_wider_stack_example.R

@@ -1,0 +1,47 @@
+# pivot_longer test script
+library(tidyverse)
+
+df_wide <- 
+  data.frame(id = 1:3, A_1 = 1:3, A_2 = 4:6, B_1 = 7:9, B_2 = 10:12)
+
+# what I try
+df_long <- 
+  df_wide %>% 
+  pivot_longer(
+    cols = A_1:B_2,
+    names_to = c(".value", "wave"),
+    names_pattern = "(.*)_(.)",
+    values_to = c("A", "B")
+  )
+
+# Error in standardise_join_by(by, x_names = x_names, y_names = y_names) : 
+#   object 'wave' not found
+
+
+# what I want to do, in multiple commands
+
+## generate variable "A"
+df_long <- 
+  df_wide %>% 
+  select(id, A_1, A_2) %>% 
+  pivot_longer(
+    cols = A_1:A_2,
+    names_to = c("wave"),
+    names_pattern = ".*_(.)",
+    values_to = "A"
+  )
+
+## add variable "B"
+df_long <- 
+  df_wide %>% 
+  select(id, B_1, B_2) %>% 
+  pivot_longer(
+    cols = B_1:B_2,
+    names_to = c("wave"),
+    names_pattern = ".*_(.)",
+    values_to = "B"
+  ) %>% 
+  full_join(df_long, by = c("id", "wave")) %>% 
+  select(id, wave, A, B)
+
+df_long

### 2022-06-28 code/preprocessing/dependent/01_WideToLong.R

@@ -1,0 +1,67 @@
+# ______________________________________________
+# Bild
+# Goal: transform df wide to long
+# Procedure: load, transform, save
+# ______________________________________________
+# Date:  Sun May 15 11:03:55 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+
+# 0. load ####
+
+library(here)
+library(tidyverse)
+library(data.table)
+library(haven)
+library(lubridate)
+library(glue)
+library(naniar)
+library(dplyr)
+
+gles_p <- read_dta(here('data/raw/gles/Panel/GLESMerge/ZA6838_allwaves_sA_v4-0-0.dta'))
+
+## id var
+gles_p$lfdn <- as.factor(gles_p$lfdn)
+
+
+
+# 1. Pivot wide -> long ####
+
+## using single command
+gles_p_long <- 
+  gles_p  %>% 
+  select(lfdn, # id
+         contains("datetime"), contains("participation"),
+         contains("_010"), contains("_020"), # political interest & satisfaction w. democracy
+         contains("_2280"), contains("_2290"), # gender, age
+         contains("190"), contains("430"), # vote intention, party scalometer
+         contains("840"), contains("860"), # MIP
+         contains("1555"), # Political Motivation
+         # issue attitudes
+         contains("1500"), contains("1090"), contains("1300"), contains("1210"),
+         contains("2880"), contains("1130"), contains("1290"), contains("1411"), 
+         contains("1210"), contains("1140"), contains("1220"), contains("1250"),
+         contains("1260"), 
+         contains("3320"), # schwartz values
+         contains('_090_v1'), contains('_110'), contains('_130'), contains('3430'), # political knowledge
+         # media use
+         contains("1621"), contains("1600"), contains("1610"), contains("1681"),
+         contains("1661"), contains("1701"), contains("1702"), contains("2180")) %>%
+  select(!contains("flag")) %>%  
+  pivot_longer(cols = kp1_datetime:kp8_1702, 
+               names_to = c("wave", ".value"),
+               names_pattern = "kp(..?)_(.*)"
+  )
+
+### check
+# vis_miss(gles_p_long[sample(1:nrow(gles_p_long), 1000),])
+# table(gles_p_long$wave)
+# plot(as.Date(gles_p_long$datetime), gles_p_long$wave)
+
+## save
+fwrite(gles_p_long, file = here(paste0('data/raw/gles/Panel/long.csv')))
+

### 2022-06-28 code/preprocessing/dependent/02_cleaning.R

@@ -1,0 +1,620 @@
+
+# ______________________________________________
+# Media effects on issue definitions
+# Goal: Preprocess survey data
+# Procedure: load, pivot, clean
+# ______________________________________________
+# Date:  Mon Sep 13 08:17:34 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+# 0. load ####
+
+library(here)
+library(tidyverse)
+library(data.table)
+library(haven)
+library(lubridate)
+library(glue)
+library(naniar)
+library(dplyr)
+
+
+# load raw data ####
+rm(list = ls())
+gles_p_long <- fread(file = here(paste0('data/raw/gles/Panel/long.csv'))) %>% as.data.frame()
+
+# define parameters ####
+media_vars <- 
+  gles_p_long %>% 
+  select(contains('1661'), contains('1681'), contains("1600"), contains("1610")) %>% 
+  select(!contains('1661h')) %>% 
+  select(!contains('1681f')) %>%  
+  colnames()
+
+
+
+newsm_vars <- gles_p_long %>% select(contains('1701')) %>% colnames()
+non_vars   <- gles_p_long %>% select(contains('1661h'), contains('1681f')) %>%  colnames()
+# issue_vars <- gles_p_long %>% select(contains('2880'), "1500", "1090", "1130", 
+#                                      "1290", "1210", "1140", "1220", "1300", 
+#                                      "1411", "1250", "1260") %>% colnames()
+
+main_news_vars <- gles_p_long %>% select(contains('1621')) %>% colnames()
+web_politics_vars <- gles_p_long %>% select(contains('1600')) %>% colnames()
+sm_politics_vars <- gles_p_long %>% select(contains('1610')) %>% colnames()
+big5_vars <- gles_p_long %>% select(contains('2180')) %>% colnames()
+schwartz_vars <- gles_p_long %>% select(contains('3320')) %>% colnames()
+
+
+
+
+# clean variables ####
+
+## date  ####
+gles_p_long$date_clean <- gles_p_long$datetime
[…]

### 2022-06-28 code/preprocessing/independent/01_surveydates.R

@@ -1,0 +1,30 @@
+# ______________________________________________
+# Function preparing survey dates for treatment plot
+# ______________________________________________
+# Date:  Mon May 09 20:45:26 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+library(tidyverse)
+library(dplyr)
+library(data.table)
+
+
+## define survey dates
+gles_p_long <- 
+  fread(here('data/raw/gles/Panel/long_cleaned.csv')); envlist <- c("gles_p_long")
+
+survey_dates <- 
+  gles_p_long %>% 
+  filter(!is.na(date_clean)) %>% 
+  filter(!is.na(`1130_clean`)) %>%  
+  # filter(date_clean < as.Date("2018-01-01")) %>% 
+  group_by(wave) %>% 
+  summarise(date = max(date_clean)) %>% 
+  ungroup() %>% 
+  select(date); envlist <- c(envlist, "survey_dates")
+
+fwrite(survey_dates, file = "data/processed/SurveyDates.csv")
+
+rm(envlist)

### 2022-06-28 code/preprocessing/independent/02b_stm_label.R

@@ -1,0 +1,227 @@
+# ______________________________________________
+# Effect of framing on issue attitudes
+# Goal: Define relevant frames, export estimates
+# ______________________________________________
+# Date:  Thu Oct 04 17:06:22 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(data.table)
+library(here)
+library(stm)
+library(lubridate)
+library(tidytext)
+library(ggthemes)
+library(scales)
+library(knitr)
+library(dplyr)
+
+
+
+# explore following Julia Silge's blogpost: https://juliasilge.com/blog/evaluating-stm/
+load(here('data/out_docs.Rdata'))
+load(here('data/topic_model_K60.Rdata'))
+
+
+## look into selected topic prevalence across time & newspapers
+prevalence <- data.frame(row.names = 1:length(out$documents))
+
+### topic 1: english
+prevalence$english <- topic_model$theta[,1]
+
+### topic 2: stock market NY/FRA
+prevalence$finance_bonds <- topic_model$theta[,2]
+
+### topic 3: international distribution of refugees
+prevalence$international_dist <- topic_model$theta[,3]
+
+### topic 4: Stock markets eastern europe
+prevalence$stocks_cee <- topic_model$theta[,4]
+
+### topic 5: foreign government reaction to migration pact
+prevalence$un_mig_pact <- topic_model$theta[,5]
+
+### topic 6: unionsstreit asyl
+prevalence$asylstreit <- topic_model$theta[,6]
+
+### topic 7: discussion of right-wing intellectuals
+prevalence$rw_intellectuals <- topic_model$theta[,7]
+
+### topic 8: asian stock markets
+prevalence$stocks_asia <- topic_model$theta[,8]
+
+### topic 9: german länder politics
+prevalence$laender <- topic_model$theta[,9]
+
+### topic 10: legal aspects integration (doppelpass, einwanderungsgesetz)
+prevalence$legal_integration <- topic_model$theta[,10]
+
+### topic 11: job market integration of refugees
+prevalence$jobmarket_integration <- topic_model$theta[,11]
+
+### topic 12: european borders
+prevalence$eu_borders <- topic_model$theta[,12]
+
+### topic 13: war in syria
[…]

### 2022-06-28 code/preprocessing/independent/02c_stm_clean.R

@@ -1,0 +1,104 @@
+# ______________________________________________
+# Effect of framing on issue attitudes
+# Goal: Prepare independent variables
+# Procedure: load, transform, save
+# ______________________________________________
+# Date:  Wed Sep 08 14:20:28 2021
+# Author: Nicolai Berk
+#  R version 4.0.3 (2020-10-10)
+# ______________________________________________
+
+
+# 0. Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(here)
+library(lubridate)
+library(glue)
+
+# 1. load ####
+
+## survey data for wave dates
+attitude_dids <- read.csv(here('data/coeftable_gles_noimp.csv'))
+
+attitude_dids$paper_name <- ''
+attitude_dids$paper_name[attitude_dids$paper == 'a'] <- 'bild'
+attitude_dids$paper_name[attitude_dids$paper == 'b'] <- 'falg'
+attitude_dids$paper_name[attitude_dids$paper == 'c'] <- 'faz'
+attitude_dids$paper_name[attitude_dids$paper == 'd'] <- 'sz'
+attitude_dids$paper_name[attitude_dids$paper == 'e'] <- 'taz'
+attitude_dids$paper_name[attitude_dids$paper == 'f'] <- 'welt'
+
+load(here('data/mig_articles_topics2022-02-02.Rdata'))
+load(here('data/salience_cleaned.csv'))
+
+# 2. transform ####
+
+## 2.1 framing ####
+
+## estimate absolute frame attention
+framing_daily <- 
+  output %>% 
+  select(-date, -title, -url, -text) %>% 
+  group_by(date_new, paper) %>% 
+  summarise_all(sum) %>%
+  as_tibble()
+
+
+## estimate n of mig articles in frame set
+framing_daily$n_mig_fra <- 
+  output %>% 
+  group_by(date_new, paper) %>% 
+  summarise(n_mig_fra = n()) %>% 
+  ungroup %>% 
+  select(n_mig_fra) %>% 
+  unlist()
+
+rm(output)
+
+
+## 2.2 salience ####
+
+# estimate absolute and relative saleince
+salience_daily <- 
+  salience_raw %>% 
+  group_by(date_new, paper) %>% 
+  summarise(
+    n_mig_sal = sum(mig),
+    n_tot = n()
+  ) %>% 
+  mutate(
+    share_mig = n_mig_sal/n_tot
+  ) %>% 
+  as_tibble()
+
[…]

### 2022-06-28 code/preprocessing/independent/03a_bert_crime_clean.R

@@ -1,0 +1,81 @@
+# ______________________________________________
+# Quick assessment of BERT Crime Estimates
+# ______________________________________________
+# Date:  Mon May 09 11:49:57 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+envlist <- c()
+
+# load data, describe ####
+articles <- fread(here('data/processed/bert_crime_raw.csv')); envlist <- c("articles")
+
+articles$crime_label %>% 
+  table() %>% 
+  prop.table() %>% 
+  round(2)
+
+# summary(articles)
+
+# clean ####
+
+# fix probs var: IS label prob, SHOULD crime prob
+
+articles <- 
+  articles %>% 
+  mutate(
+    label_prob = crime_prob,
+    crime_prob = 
+      ifelse(
+        crime_label == 1,
+        crime_prob,
+        1 - crime_prob)
+  )
+
+
+# date
+
+articles %>% 
+  group_by(paper) %>% 
+  slice(1) %>% 
+  select(paper, date)
+
+## fix
+articles <- 
+  articles %>% 
+    mutate(
+      date_clean = 
+        case_when(
+          grepl("\\.", date) ~ as.Date(date, format = "%d.%m.%Y"),
+          grepl("-", date) ~ as.Date(date, format = "%Y-%m-%d"),
+          stringr::str_count(date) == 5 ~ as.Date(as.integer(date), origin = "1970-01-01")
+        )
+      ) %>% 
+  mutate(paper = 
+           case_when(paper %in% c("weltonline", "welt") ~ "Welt",
+                     paper == "taz"  ~ "TAZ",
+                     paper == "spon" ~ "Spiegel",
+                     paper == "faz"  ~ "FAZ",
+                     paper == "sz"   ~ "SZ",
+                     paper == "bild" ~ "Bild")) %>% 
+  filter(paper != "Spiegel") %>%  # as Spiegel not part of the analysis
+  filter(date_clean < as.Date("2020-01-01")) # data only collected until end of 2019, some dates are off
+
+envlist <- c(envlist, "bert_ests")
+
+# check missings produced (fine, scraping wasn't fully perfect but small n of missings)
+# articles %>% filter(is.na(date_clean)) %>% select(date) %>% unique()
[…]

### 2022-06-28 code/preprocessing/independent/03b_bert_crime_aggregate.R

@@ -1,0 +1,42 @@
+
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+
+# aggregate BERT estimates to daily measure
+prevalence <- fread(here("data/processed/bert_crime_clean.csv"))
+
+
+prevalence <- 
+  prevalence %>% 
+  select(date_clean, paper, crime_label, crime_prob) %>% 
+  group_by(date_clean, paper) %>% 
+  mutate(n_mig = 1) %>% 
+  summarise_all(sum)
+
+# get number of news articles total from original data
+load(here("data/salience_cleaned.csv"))
+
+salience <- 
+  salience_raw %>% 
+  mutate(date_clean = as.IDate(date_new),
+         paper = 
+           case_when(
+             paper == "bild" ~ "Bild",
+             paper == "faz"  ~ "FAZ",
+             paper == "spon" ~ "Spiegel",
+             paper == "sz"   ~ "SZ",
+             paper == "taz"  ~ "TAZ",
+             paper == "welt" ~ "Welt",
+           )) %>% 
+  group_by(paper, date_clean) %>% 
+  summarise(n_tot = n()) #; rm(salience_raw)
+
+prevalence <- 
+  prevalence %>% 
+  left_join(salience, by = c("paper", "date_clean")) %>% 
+  mutate(mig_share = n_mig/n_tot)
+
+
+fwrite(prevalence, here("data/processed/bert_crime_daily.csv"))

### 2022-06-28 code/preprocessing/independent/04a_merge_bert.R

@@ -1,0 +1,158 @@
+# ______________________________________________
+# Media effects Bild
+# Goal: merge survey and stm data
+# ______________________________________________
+# Date:  Tue Feb 15 08:40:42 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(RcppRoll)
+
+
+gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
+
+## generate lagged dependent
+gles_p_long <- 
+  gles_p_long %>% 
+  filter(!is.na(date_clean)) %>% 
+  select(-contains("2880")) %>% 
+  group_by(lfdn) %>% 
+  dplyr::arrange(date_clean, .by_group = T) %>% 
+  mutate(
+    `1130_lag` = dplyr::lag(`1130_clean`),
+    `1210_lag` = dplyr::lag(`1210_clean`),
+    `1140_lag` = dplyr::lag(`1140_clean`),
+    `1220_lag` = dplyr::lag(`1220_clean`),
+    `430i_lag` = dplyr::lag(`430i_clean`),
+    date_str = as.character(date_clean)
+  )
+
+## prepare media estimates
+prevalence_daily <- fread(here("data/processed/bert_crime_daily.csv"))
+
+# calculate salience in relevant lag
+prevalence_daily <- 
+  prevalence_daily %>% 
+  group_by(paper) %>% 
+  mutate(
+    across(crime_label:n_tot, ~roll_sum(.x,    7, fill=NA, align = 'right', na.rm = T), .names = "{.col}_7d")
+    # across(english:n_tot, ~roll_sum(.x,    30, fill=NA, align = 'right', na.rm = T), .names = "{.col}_30d")
+    
+  )
+
+prevalence_daily <- 
+  prevalence_daily %>% 
+  pivot_wider(names_from = paper, values_from = 3:ncol(prevalence_daily)) %>% 
+  mutate(date_str = as.character(date_clean))
+
+## merge
+merged_data <- 
+  gles_p_long %>% 
+  left_join(prevalence_daily %>% 
+              select(-date_clean), by = c("date_str"))
+
+rm(gles_p_long, prevalence_daily)
+
[…]

### 2022-06-28 code/preprocessing/independent/04b_merge_stm.R

@@ -1,0 +1,169 @@
+# ______________________________________________
+# Media effects Bild
+# Goal: merge survey and stm data
+# ______________________________________________
+# Date:  Tue Feb 15 08:40:42 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(RcppRoll)
+
+
+gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
+
+## generate lagged dependent
+gles_p_long <- 
+  gles_p_long %>% 
+  filter(!is.na(date_clean)) %>% 
+  select(-contains("2880")) %>% 
+  group_by(lfdn) %>% 
+  dplyr::arrange(date_clean, .by_group = T) %>% 
+  mutate(
+    `1130_lag` = dplyr::lag(`1130_clean`),
+    `1210_lag` = dplyr::lag(`1210_clean`),
+    `1140_lag` = dplyr::lag(`1140_clean`),
+    `1220_lag` = dplyr::lag(`1220_clean`),
+    `430i_lag` = dplyr::lag(`430i_clean`),
+    date_str = as.character(date_clean)
+  )
+
+## prepare media estimates
+load(here("data/processed/stm_daily.Rdata"))
+
+# calculate salience in relevant lag
+merged_media <- 
+  merged_media %>% 
+  select(date_new:share_mig, 
+         sexual_assault, crime_schlepp,
+         sexual_assault_share, crime_schlepp_share, n_mig_fra) %>% 
+  group_by(paper) %>% 
+  mutate(
+    across(n_mig_sal:n_mig_fra, ~roll_sum(.x,    7, fill=NA, align = 'right', na.rm = T), .names = "{.col}_7d")
+    # across(english:n_articles, ~roll_sum(.x,    30, fill=NA, align = 'right', na.rm = T), .names = "{.col}_30d")
+    
+  )
+
+merged_media <- 
+  merged_media %>% 
+  pivot_wider(names_from = paper, values_from = 3:ncol(merged_media)) %>% 
+  mutate(date_str = as.character(date_new))
+
+## merge
+merged_data <- 
+  gles_p_long %>% 
+  select(lfdn, wave, contains("1661"), date_str, date_clean) %>% 
[…]

### 2022-06-28 code/preprocessing/tobit_prep.R

@@ -1,0 +1,36 @@
+# ______________________________________________
+# Bild
+# Goal: Prepare dataset for stata estimation
+# Procedure: load, prepare, save
+# ______________________________________________
+# Date:  Mon May 23 12:24:36 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+# Setup ####
+library(tidyverse)
+library(dplyr)
+library(here)
+library(data.table)
+library(haven)
+
+# load ####
+gles_p_long <- fread(here("data/raw/gles/Panel/long_cleaned.csv"))
+
+# prepare ####
+gles_p_long <- 
+  gles_p_long %>% 
+  mutate(Individual = lfdn,
+         dv = `1130_clean`) %>% 
+  select(Individual, post, treat, dv) %>% 
+  filter(!is.na(post), !is.na(treat), !is.na(dv))
+
+# test regression
+lm(dv ~ post*treat, data = gles_p_long)
+fixest::feglm(dv ~ post*treat | Individual, data = gles_p_long)
+
+
+# save ####
+write_dta(gles_p_long, here("data/processed/GLES_tobit.dta"))

### 2022-06-28 paper/appendix.Rmd
Update pres as well
pray

---
title: "Appendix for 'Framing Effects in the Wild'"
author: "Nicolai Berk"
date: "15 5 2022"
output: 
  pdf_document:
    number_sections: TRUE
toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center')

library(tidyverse)
library(dplyr)
library(data.table)
library(here)
library(patchwork)

# load self-made functions
for (filename in list.files(here("code/functions"))){
  source(here(paste0('code/functions/', filename)))
}
```

# Independent Variable

## Market Coverage of Different Newspapers

```{=tex}
\begin{table}[!htbp] \centering
    \begin{tabular}{@{\extracolsep{5pt}} lcc}
    \\[-1.8ex]\hline
    \hline \\[-1.8ex]
    Paper & Print Sales & Web Impressions \\
     & (thousands) & (millions) \\
    \hline \\[-1.8ex]
    Bild & 1756 & 555 \\
    Spiegel & 758 & 388 \\
    FAZ & 242 & 123 \\
    SZ & 358 & 13 \\
    taz & 51 & 7 \\
    Welt & 521 & 135 \\
    \hline \\[-1.8ex]
    \end{tabular}
  \caption{Average daily sales and monthly online impressions of different newspapers in 2017. Source: Informationsgemeinschaft zur Feststellung der Verbreitung von Werbeträgern e. V. (2021). Quartalsauflagen. https://ivw.de/aw/print/qa. Table generated with stargazer.}
  \label{tab:paper_sales}
\end{table}
```

## BERT Classifiers

### Migration

### Crime

# Structural Topic Model

To identify different considerations about migration in news coverage, I estimate a structural topic model with 60 topics for the nearly 90,000 migration articles in the full period (2013-2019)\footnote{The topics' prevalence along with the most important words can be assessed in the appendix.}. The number of topics was chosen to strike a balance between the computational and human resources necessary to estimate and annotate the topics and finding appropriate topics for the large corpus of nearly 90,000 migration articles\footnote{Currently, I work to identify crime content using supervised models (similar to the identification of migration content) to provide a specific estimate of the attention to the consideration of interest. I will also analyse the data with embedding regression, assessing how the meaning of migration related terms like 'migrant', 'asylum' or 'syrian' changed in Bild compared to other newspapers}. Topic prevalence is estimated as a function of the release date of the article, as well as the newspaper it has been published in. The 60 topics' most predictive words and ten most representative articles were assessed to identify and label the content of each topic, and all topics related to crime (two in total) are selected and their prevalence added together for a daily measure of attention to crime in each newspaper.

## Treatment

## Modeling Exposure with STM in TWFE Model

# Difference-in-Differences Estimates

Treated Group: Bild Readers in first (and only pre-treatment) wave.
Control Group: Never-Readers of Bild.
Post Date: $>=$ 01.02.2017

## Descriptives

Show Demographics for Treatment and Control Groups.

```{r, bild_descriptives}

gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))

desc <- 
  gles_p_long %>% 
  filter(wave == "1", !is.na(treat)) %>% 
  group_by(treat) %>% 
  select(gender_clean, ybirth_clean, `010_clean`, 
         `1130_clean`, `1500_clean`, `afd_vote`, `430i_clean`) %>%
  mutate(gender_clean = gender_clean-1) %>% 
  mutate(across(.fns = as.integer)) %>% 
  summarise(across(.fns = mean, na.rm = T)) %>% 
  select(-treat) %>% 
  t() %>% round(2)

colnames(desc) <- c("Control", "Treatment")
row.names(desc) <- c("Gender (0 = m, 1 = f)", "Birthyear", 
                     "Political interest (1, 5)", "Immigration Attitude (-3, 3)",
                     "General left-right (0-10)", "Share of AfD supporters", "AfD attitude (-5, 5)")

knitr::kable(desc, align = c("c", "c"))

rm(gles_p_long, desc)

```

Note that the variable "Birthyear" is left-censored in the data. All respondents born before 1955 were assigned 1955 as birth year.

## Variable: Immigration Attitudes

### Outcome: Reduce Immigration (1130)

#### Question Text

Jetzt geht es um Zuzugsmöglichkeiten für Ausländer. Sollten die Zuzugsmöglichkeiten für Ausländer erleichtert oder eingeschränkt werden?

(1) 1 Zuzug von Ausländern erleichtern 
(2) 2  
(3) 3  
(4) 4  
(5) 5  
(6) 6  
(7) 7 Zuzug von Ausländern einschränken

*Transformed to [-3, 3].*

#### Treatment groups across time

(add counterfactual if time)

```{r did_imm_att_plot}

fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(init_mig_groups != "", !is.na(`1130_clean`), !is.na(treat)) %>% 
  group_by(treat, wave) %>% 
  summarise(
    date_clean = min(date_clean, na.rm = T),
    `1130_clean` = mean(`1130_clean`, na.rm = T)
  ) %>% 
  ggplot(aes(x = date_clean, y = `1130_clean`, lty = !treat, col = !treat)) +
  geom_line() +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
  # facet_wrap(~init_mig_groups, ncol = 1) + 
  theme_minimal()

```
#### Treatment groups across time, by prior attitude

```{r did_imm_att_plot_groups}

fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(init_mig_groups != "", !is.na(`1130_clean`), !is.na(treat)) %>% 
  group_by(init_mig_groups, treat, wave) %>% 
  summarise(
    date_clean = min(date_clean, na.rm = T),
    `1130_clean` = mean(`1130_clean`, na.rm = T)
  ) %>% 
  ggplot(aes(x = date_clean, y = `1130_clean`, lty = !treat, col = init_mig_groups)) +
  geom_line() +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
  # facet_wrap(~init_mig_groups, ncol = 1) + 
  theme_minimal()

```

#### Effect by prior opinion

```{r linearEffect}

InterLinear() + 
  InterLinear(placebo = T)

```
#### Regression to the mean among Bild readers

- Placebo-treatment post Bundestagswahl (3-6 months after treatment)
- Exclusing Bild readers actually treated

```{r}
DiDPlot(placebo = T, exclude_pretreated = T, legend_position = "None") + InterLinear(placebo = T, exclude_pretreated = T)
```

#### Effect of Reichelt takeover

```{r did_imm_att}

DiDModels(dv_name = "1130_clean", 
          ctrl_var  = "cond",
          ctrl_name = "Initial Migration Att.")

```

#### Number of respondents in each group

```{r treat_initmig_n, fig.cap="Number of respondents in treatment and control group by pre-existing attitude."}

gles_p_long <- 
  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(wave == "1")

table(gles_p_long$init_mig, gles_p_long$treat) %>% 
  knitr::kable()

rm(gles_p_long)

```

#### Number of observations

```{r treat_initmig_obs, fig.cap="Number of observations in treatment and control group by pre-existing attitude."}

gles_p_long <- 
  fread(here('data/raw/gles/Panel/long_cleaned.csv'))

table(gles_p_long$init_mig, gles_p_long$treat) %>% 
  knitr::kable()

rm(gles_p_long)

```

#### Conservative Outlets only

```{r did_imm_att_cons}

DiDModels("1130_clean", restrict_sample = "conservative_outlets")

```

```{r did_imm_att_cons_vis}

fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(init_mig_groups != "", !is.na(`1130_clean`), !is.na(treat)) %>% 
  filter(bild_init | faz_init | welt_init) %>% 
  group_by(init_mig_groups, treat, wave) %>% 
  summarise(
    date_clean = min(date_clean, na.rm = T),
    `1130_clean` = mean(`1130_clean`, na.rm = T)
  ) %>% 
  ggplot(aes(x = date_clean, y = `1130_clean`, lty = !treat, col = init_mig_groups)) +
  geom_line() +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
  ggtitle("Immigration attitudes among Bild readers across time", "Compared to FAZ & Welt readers") + 
  theme_minimal()

```

### Outcome: Immigration Attitude Nonresponse (1130 = -99)

```{r did_imm_dodge}

DiDModels("1130_dodge")

```

### Outcome: Integration Attitude (1210)

#### Question Text

Es gibt unterschiedliche Auffassungen darüber, wie sehr sich Ausländer in Deutschland anpassen sollten. Manche denken, dass sich Ausländer vollständig an die deutsche Kultur anpassen sollten. Andere denken, Ausländer sollten auch hier möglichst nach der eigenen Kultur leben können.

(1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen 
(2)  
(3)  
(4)  
(5)  
(6)  
(7) Ausländer sollten möglichst nach eigener Kultur leben können

*Recoded to [-3, 3].*

#### Effect of Reichelt takover

```{r did_int_att}

DiDModels("1210_clean")

```

### Outcome: Integration Attitude Nonresponse (1210 = -99)

## General Nonresponse/Attrition (1130 = -95)

```{r did_part}

DiDModels("participation")

```

## Variable: Voting Behaviour

### Outcome: Voting AfD (190b)

Bei der Bundestagswahl können Sie ja zwei Stimmen vergeben. Die Erststimme für einen Kandidaten aus Ihrem Wahlkreis und die Zweitstimme für eine Partei. Was werden Sie auf Ihrem Stimmzettel ankreuzen?

```{r afd_vote}

DiDModels("afd_vote")

```

### Outcome: Voting Nonresponse (190b = -99 | -98)

```{r vote_mis}

DiDModels("vote_miss")

```

**Sizable effect, most likely among liberals.**

### Outcome: Scalometer AfD (430i)

```{r afd_scale}

DiDModels("430i_clean")

```

**Decrease, if anything. Most sizable among liberals, but disappers when controlling for individual FEs.**

## Variable: Issue Considerations

### Outcome: MIP Migrant Crime (840s)

```{r did_mip_mig_crime}

DiDModels("mip_mig_crime")

```
No effect, but also very low N.

### Outcome: MIP Migration (840s)

```{r did_mip_mig}

DiDModels("mip_mig")

```

**NO effect on general problem perception of migration.**.

### Outcome: Crime Attitude (2880h)

```{r did_crime_att}

DiDModels("2880h_clean")

```

*Nothing.*

### Outcome: Correlation of Crime Attitude (2880h) & Immigration Attitude (1130)

#### Question

Die staatlichen Befugnisse in der Kriminalitätsbekämpfung sollten ausgeweitet werden, auch wenn das zu einer stärkeren Überwachung der Bürger führt.

(1) stimme überhaupt nicht zu 
(2) stimme eher nicht zu 
(3) teils/teils 
(4) stimme eher zu 
(5) stimme voll und ganz zu

#### Bootstrap of correlations

```{r crime_mig_cor}

cors <- 
  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(!is.na(`1130_clean`), !is.na(`2880h_clean`), !is.na(treat)) %>% 
  group_by(treat, post) %>% 
  summarise(mig_crime_cor = cor(`1130_clean`, `2880h_clean`, use = "complete.obs")) %>% 
  mutate(universe = "factual")

cors <- 
  cors %>% 
  rbind(
    data.frame(
      treat = c(TRUE, TRUE),
      post = c(FALSE, TRUE),
      mig_crime_cor = c(cors[cors$treat & !cors$post, "mig_crime_cor"][[1]], 
                        cors[cors$treat & !cors$post, "mig_crime_cor"][[1]] +  
                          sqrt((cors[cors$treat & cors$post, "mig_crime_cor"][[1]] -
                          cors[!cors$treat & cors$post, "mig_crime_cor"][[1]])^2)),
      universe = "counterfactual"
    ), 
  ) %>% 
  mutate(universe = factor(universe, levels = c("factual", "counterfactual")))

cors %>% 
  mutate(treat_universe = paste(treat, universe, sep = "_")) %>% 
  ggplot(aes(x = post, y = mig_crime_cor, col = treat, lty = universe, group = treat_universe)) +
  geom_point() +
  geom_line() +
  theme_minimal()

```

(cannot show this by subgroup bc would condition on pre-treatment opinion, which restricts variation on migration attitudes to 0, hence no correlation)

#### Interaction of DiD with Crime Attitude (following Nelson & Kinder 1996)

(Association of Crime with migration attitude should be sigificantly higher in post-treatment-group)

```{r did_cond_crime}

gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))

# define dv and conditioning variable
gles_p_long[["dv"]] <- gles_p_long[["1130_clean"]]
gles_p_long[["crime_att"]] <- gles_p_long[["2880h_clean"]]
gles_p_long$Individual <- gles_p_long$lfdn

inter <- 
  feglm(dv ~ post * treat * crime_att, 
        cluster = c("Individual"), 
        data = gles_p_long %>% 
          filter(!is.na(dv), !is.na(treat), !is.na(post), !is.na(crime_att)))

inter_cond <- 
  feglm(dv ~ post * treat * init_mig * crime_att , 
        cluster = c("Individual"), 
        data = gles_p_long %>% 
          filter(!is.na(dv), !is.na(treat), !is.na(post), 
                 !is.na(crime_att), !is.na(init_mig)))

inter_fe_cond <- 
  feglm(dv ~ post * treat * init_mig * crime_att | Individual, 
        cluster = c("Individual"), 
        data = gles_p_long %>% 
          filter(!is.na(dv), !is.na(treat), !is.na(post), 
                 !is.na(crime_att), !is.na(init_mig)))

inter_fe <- 
  feglm(dv ~ post * treat * crime_att | Individual, 
        cluster = c("Individual"), 
        data = gles_p_long %>% 
          filter(!is.na(dv), !is.na(treat), !is.na(post), !is.na(crime_att)))

modelsummary(
  list(
    inter, inter_fe, inter_cond, inter_fe_cond
  ),
  stars = T,
  # coef_map =
  #   c("postTRUE:treatTRUE" = "ATE",
  #     "postTRUE:treatTRUE:crime_att" = "ATE X Crime Attitude",
  #     "postTRUE:treatTRUE:init_mig:crime_att" = "ATE X Crime Attitude X \nInitial Migration Attitude"),
  gof_omit = "^(?!R2.Pseudo|Num|Std|FE)", 
  output = "markdown"
)

rm(gles_p_long, inter, inter_fe, inter_cond, inter_fe_cond)

```

## Variable: Accuracy Motivation

**This variable is only measured post-treatment**

### Mean accuracy motivation by initial immigration attitude

```{r acc_mot_means}

gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))

gles_p_long %>% 
  filter(!is.na(init_mig)) %>% 
  group_by(init_mig) %>% 
  summarise(acc_mot = mean(`1555d_clean`, na.rm = T)) %>% 
  ggplot(aes( x = init_mig, y = acc_mot)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  xlab("Initial Immigration Opinion") +
  ylab("Accuracy motivation") +
  theme_minimal()

```

### DiD by post-treatment accuracy motivation

```{r did_acc_mot}

DiDModels("1130_clean",
          cond_var = "acc_goal",
          cond_name = "Accuracy Motivation")

```

# TWFE: BERT Estimates

## Distribution of Independent Variable

```{r bert_dist}

fread(here("data/processed/merged_bert.csv")) %>% 
  ggplot(aes(crime_label_share)) + 
  geom_histogram(bins = 50, col = "white") +
  theme_minimal()

```

## Variable: Immigration Attitudes

### Outcome: Reduce Immigration (1130)

Jetzt geht es um Zuzugsmöglichkeiten für Ausländer. Sollten die Zuzugsmöglichkeiten für Ausländer erleichtert oder eingeschränkt werden?

(1) 1 Zuzug von Ausländern erleichtern 
(2) 2  
(3) 3  
(4) 4  
(5) 5  
(6) 6  
(7) 7 Zuzug von Ausländern einschränken

```{r ind_imm_att}

TWFEModels("1130_clean")

```

### Outcome: Immigration Attitude Nonresponse (1130 = -99)

```{r ind_imm_dodge}

TWFEModels("1130_dodge")

```

### Outcome: Integration Attitude (1210)

Es gibt unterschiedliche Auffassungen darüber, wie sehr sich Ausländer in Deutschland anpassen sollten. Manche denken, dass sich Ausländer vollständig an die deutsche Kultur anpassen sollten. Andere denken, Ausländer sollten auch hier möglichst nach der eigenen Kultur leben können.

(1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen 
(2)  
(3)  
(4)  
(5)  
(6)  
(7) Ausländer sollten möglichst nach eigener Kultur leben können

```{r ind_int_att}

TWFEModels("1210_clean")

```

### Outcome: Integration Attitude Nonresponse (1210 = -99)

```{r ind_int_dodge}

TWFEModels("1210_dodge")

```

## Conditioning on Prior Exposure

### DV: Immigration Attitude

```{r ind_cond_exp_lag}

TWFEModels("1130_clean", 
           cond = "crime_label_share_lag", 
           cond_name = "\nLagged Exposure")

```

Exposure has no conditioning effect - maybe conditional effect IS ceiling effect? (but still holds compared to conservative news consumers?)

## Variable: Voting Behaviour

### Outcome: Voting AfD (190b)

Bei der Bundestagswahl können Sie ja zwei Stimmen vergeben. Die Erststimme für einen Kandidaten aus Ihrem Wahlkreis und die Zweitstimme für eine Partei. Was werden Sie auf Ihrem Stimmzettel ankreuzen?

### Outcome: Voting Nonresponse (190b = -99 | -98)

```{r ind_afd_dodge}

TWFEModels("vote_miss")

```

### Outcome: Scalometer AfD (430i)

```{r ind_afd_vote}

TWFEModels("430i_clean")

```

## Variable: Issue Considerations

### Outcome: MIP Migrant Crime (840s)

```{r ind_mip_mig_crime}

TWFEModels("mip_mig_crime")

```

### Outcome: MIP Migration (840s)

```{r ind_mip_mig}

TWFEModels("mip_mig")

```

## TWFE Conditional on Paper Consumed (driven by Bild-readers?)

```{r}

TWFEModels("1130_clean", cond_var = "bild_init", cond_name = "Paper: Bild")

```

Effect **lower** among Bild readers!

<!-- # TWFE: STM Estimates -->

<!-- **STM estimates currently NOT reliable - fix 04a_merge_stm.R** -->

<!-- ## Distribution of Independent Variable -->

<!-- ```{r stm_dist} -->

<!-- fread(here("data/processed/merged_stm.csv")) %>%  -->
<!--   ggplot(aes(crime_label_share)) +  -->
<!--   geom_histogram(bins = 50, col = "white") + -->
<!--   theme_minimal() -->

<!-- ``` -->

<!-- ## Variable: Immigration Attitudes -->

<!-- ### Outcome: Reduce Immigration (1130) -->

<!-- Jetzt geht es um Zuzugsmöglichkeiten für Ausländer. Sollten die Zuzugsmöglichkeiten für Ausländer erleichtert oder eingeschränkt werden? -->

<!-- (1) 1 Zuzug von Ausländern erleichtern  -->
<!-- (2) 2   -->
<!-- (3) 3   -->
<!-- (4) 4   -->
<!-- (5) 5   -->
<!-- (6) 6   -->
<!-- (7) 7 Zuzug von Ausländern einschränken -->

<!-- ```{r ind_imm_att_stm} -->

<!-- TWFEModels("1130_clean", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: Immigration Attitude Nonresponse (1130 = -99) -->

<!-- ```{r ind_imm_dodge_stm} -->

<!-- TWFEModels("1130_dodge", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: Integration Attitude (1210) -->

<!-- Es gibt unterschiedliche Auffassungen darüber, wie sehr sich Ausländer in Deutschland anpassen sollten. Manche denken, dass sich Ausländer vollständig an die deutsche Kultur anpassen sollten. Andere denken, Ausländer sollten auch hier möglichst nach der eigenen Kultur leben können.  -->

<!-- (1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen  -->
<!-- (2)   -->
<!-- (3)   -->
<!-- (4)   -->
<!-- (5)   -->
<!-- (6)   -->
<!-- (7) Ausländer sollten möglichst nach eigener Kultur leben können  -->

<!-- ```{r ind_int_att_stm} -->

<!-- TWFEModels("1210_clean", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: Integration Attitude Nonresponse (1210 = -99) -->

<!-- ```{r ind_int_dodge_stm} -->

<!-- TWFEModels("1210_dodge", dataset = "stm") -->

<!-- ``` -->

<!-- ## Conditioning on Prior Exposure -->

<!-- ### DV: Immigration Attitude -->

<!-- ```{r ind_cpond_explag_stm} -->

<!-- TWFEModels("1130_clean",  -->
<!--            cond = "crime_label_share_lag",  -->
<!--            cond_name = "\nLagged Exposure", -->
<!--            dataset = "stm") -->

<!-- ``` -->

<!-- Exposure has no conditioning effect - maybe conditional effect IS ceiling effect? (but still holds compared to conservative news consumers?) -->

<!-- ## Variable: Voting Behaviour -->

<!-- ### Outcome: Voting AfD (190b) -->

<!-- Bei der Bundestagswahl können Sie ja zwei Stimmen vergeben. Die Erststimme für einen Kandidaten aus Ihrem Wahlkreis und die Zweitstimme für eine Partei. Was werden Sie auf Ihrem Stimmzettel ankreuzen?  -->

<!-- ### Outcome: Voting Nonresponse (190b = -99 | -98) -->

<!-- ```{r ind_afd_dodge_stm} -->

<!-- TWFEModels("vote_miss", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: Scalometer AfD (430i) -->

<!-- ```{r ind_afd_scale} -->

<!-- TWFEModels("430i_clean", dataset = "stm") -->

<!-- ``` -->

<!-- ## Variable: Issue Considerations -->

<!-- ### Outcome: MIP Migrant Crime (840s) -->

<!-- ```{r ind_mip_mig_crime_stm} -->

<!-- TWFEModels("mip_mig_crime", dataset = "stm") -->

<!-- ``` -->

<!-- ### Outcome: MIP Migration (840s) -->

<!-- ```{r ind_mip_mig_stm} -->

<!-- TWFEModels("mip_mig", dataset = "stm") -->

<!-- ``` -->

<!-- # TWFE Conditional on Paper Consumed (driven by Bild-readers?) -->

<!-- ```{r ind_cond_paper_stm} -->

<!-- TWFEModels("1130_clean", cond_var = "bild_init", cond_name = "Paper: Bild", dataset = "stm") -->

<!-- ``` -->

### 2022-06-28 pres/20210503/Presentation_20210503.tex
Update pres as well
pray

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usetheme[]{Frankfurt}
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Hypodermic needle after all? Individual-level Moderators of Media Framing Effects},
  pdfauthor={Nicolai Berk\^{}*},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Hypodermic needle after all? Individual-level Moderators of Media
Framing Effects}
\subtitle{Presentation at EPSIP Colloquium, HU Berlin}
\author{Nicolai Berk\(^*\)}
\date{May 3rd, 2021}
\institute{\(^*\)RTG Dynamics/Humboldt Universität zu Berlin}

\begin{document}
\frame{\titlepage}

\hypertarget{motivation}{%
\section{Motivation}\label{motivation}}

\hypertarget{media-effects---maximal-or-minimal}{%
\subsection{Media effects - maximal or
minimal?}\label{media-effects---maximal-or-minimal}}

\begin{frame}[allowframebreaks]{Media effects - maximal or minimal?}
\center

\includegraphics[width=0.4\textwidth,height=\textheight]{vis/volksempfanger.jpg}
\includegraphics[width=0.4\textwidth,height=\textheight]{vis/ufo_scares.jpg}

\flushleft

\framebreak

Maximal paradigm also follows from classic work

\begin{itemize}
\tightlist
\item
  attitude instability (Converse 1962; Zaller 1992)
\item
  framing (Nelson, Clawson, and Oxley 1997)
\item
  agenda-setting (McCombs and Shaw 1972)
\end{itemize}

\framebreak

\center

\includegraphics[width=0.3\textwidth,height=\textheight]{vis/mineff.png}

\flushleft

Minimal effects assumption with increasing media diversity (Bennett and
Iyengar 2008):

\begin{itemize}
\tightlist
\item
  media environment more polarised and more diverse,
\item
  viewers more likely to reject news conflicting with their views,
\item
  viewers can opt for other sources.
\end{itemize}

\(\rightarrow\) strong effects unlikely

\framebreak

Evidence seems to support both views:
\end{frame}

\begin{frame}{strong media effects on:}
\protect\hypertarget{strong-media-effects-on}{}
\begin{itemize}
\tightlist
\item
  voting behaviour (Boomgaarden and Vliegenthart 2009; Devine and Murphy
  2020; Ladd and Lenz 2009),
\item
  issue agenda (King, Schneer, and White 2017),
\item
  attitudes (Nelson, Clawson, and Oxley 1997; Foos and Bischof 2020)
\end{itemize}
\end{frame}

\begin{frame}{weak or no effects on:}
\protect\hypertarget{weak-or-no-effects-on}{}
\begin{itemize}
\tightlist
\item
  voting behaviour (Gentzkow, Shapiro, and Sinkinson 2011),
\item
  issue agenda (Lau, Rogers, and Love 2021),
\item
  attitudes (Guess et al. 2021).
\end{itemize}
\end{frame}

\hypertarget{moderators}{%
\section{Moderators}\label{moderators}}

\hypertarget{towards-a-theory-of-conditioning-factors}{%
\subsection{Towards a theory of conditioning
factors}\label{towards-a-theory-of-conditioning-factors}}

\begin{frame}{Towards a theory of conditioning factors}
Recently more discussion of moderators

\begin{itemize}
\tightlist
\item
  Mostly based on expectations regarding source:

  \begin{itemize}
  \tightlist
  \item
    Discounting of biased news (Chiang and Knight 2011)
  \item
    Rejection of partisan takeovers (Spirig 2020)
  \end{itemize}
\item
  facing biased new media outlets doesn't seem to affect citizens (Guess
  et al. 2021)
\end{itemize}
\end{frame}

\hypertarget{open-questions}{%
\subsection{Open questions:}\label{open-questions}}

\begin{frame}{Open questions:}
\begin{itemize}
\tightlist
\item
  What about outlets currently consumed changing their commentary?
\item
  What about individual-level factors?

  \begin{itemize}
  \tightlist
  \item
    political knowledge, opinion strength (Zaller 1992)?
  \item
    media diet (Bennett and Iyengar 2008)?
  \item
    partisan identification (Taber and Lodge 2006)?
  \end{itemize}
\item
  Is attitude change a result of changing issue definitions (Ajzen and
  Fishbein 2000; Nelson, Clawson, and Oxley 1997)?
\end{itemize}
\end{frame}

\hypertarget{the-case}{%
\section{The case}\label{the-case}}

\begin{frame}{The case}
\begin{itemize}
\tightlist
\item
  In fall of 2015, major German tabloid Bild started calling for support
  for incoming refugees.
\item
  This was a major deviation from the papers' agitative history.
\end{itemize}

\includegraphics{vis/BildFlüchtlingskinder.png}

\includegraphics{vis/BildNot.png}
\end{frame}

\hypertarget{onwards-the-framing-changed}{%
\subsection{2016 onwards the framing
changed}\label{onwards-the-framing-changed}}

\begin{frame}{2016 onwards the framing changed}
\center

\includegraphics[width=\textwidth,height=0.5\textheight]{vis/UebermedienBild2.png}
\end{frame}

\hypertarget{logic-of-the-paper}{%
\subsection{Logic of the paper}\label{logic-of-the-paper}}

\begin{frame}{Logic of the paper}
\begin{itemize}
\tightlist
\item
  I argue this represents a natural experiment to study migration
  framing,
\item
  allowing to identify the \emph{causal} impact of news framing on:

  \begin{itemize}
  \tightlist
  \item
    migration opinions,
  \item
    and issue definitions.
  \end{itemize}
\item
  especially interesting case:

  \begin{itemize}
  \tightlist
  \item
    instead of treatment with a new source (Guess et al. 2021),
    cue-taking (from the newspaper) can be expected.
  \item
    expectation of change in bias among readers unlikely (Chiang and
    Knight 2011; Spirig 2020)
  \end{itemize}
\end{itemize}

\emph{\(\rightarrow\) strong expectations for framing effect!}
\end{frame}

\hypertarget{data-and-research-design}{%
\section{Data and research design}\label{data-and-research-design}}

\hypertarget{the-gles-offers-a-number-of-possible-data-sources}{%
\subsection{The GLES offers a number of possible data
sources:}\label{the-gles-offers-a-number-of-possible-data-sources}}

\begin{frame}{The GLES offers a number of possible data sources:}
\begin{itemize}
\tightlist
\item
  Longterm-tracking,

  \begin{itemize}
  \tightlist
  \item
    N \(\approx\) 1000,
  \item
    four times/year,
  \item
    2009-17
  \end{itemize}
\item
  Panel,

  \begin{itemize}
  \tightlist
  \item
    N \(>\) 10,000,
  \item
    clustered around election
  \end{itemize}
\end{itemize}

Both regularly contain questions on

\begin{itemize}
\tightlist
\item
  news consumption,
\item
  migration/integration attitudes,
\item
  open-ended MIP.
\end{itemize}
\end{frame}

\hypertarget{treatments-and-field-dates}{%
\subsection{Treatments and Field
Dates}\label{treatments-and-field-dates}}

\begin{frame}[allowframebreaks]{Treatments and Field Dates}
Journalists ascribe change to changing editors. This leaves us with a
total of 4 possible treatments:

\begin{enumerate}
\tightlist
\item
  Summer of 2015
\item
  Diekmann replaced as editor-in-chief by Tanit Koch in 2016,
\item
  Diekmann finally left Bild in February 2017,
\item
  Koch replaced by Julian Reichelt in January 2018.
\end{enumerate}

Not entirely clear which treatment is relevant -\textgreater{} assess
changing framing in the newspaper!

\framebreak

\includegraphics{vis/gles_treatments.png}
\end{frame}

\hypertarget{treatment-selection}{%
\subsection{Treatment selection}\label{treatment-selection}}

\begin{frame}{Treatment selection}
\begin{enumerate}
\item
  Pre-select migration content with supervised classifier.
\item
  Several possible approaches for treatment identification:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  inductive frame identification (FA/STM)
\item
  dictionary for frames (humanitarian/crime/\ldots)
\item
  sentiment towards migration
\end{itemize}

\begin{enumerate}
\setcounter{enumi}{2}
\tightlist
\item
  Treatment identified where parallel paths diverge
\end{enumerate}
\end{frame}

\hypertarget{modelling}{%
\subsection{Modelling}\label{modelling}}

\begin{frame}{Modelling}
Diff-in-Diff:

\center

\[ y = \beta_1 * T + \beta_2 * B + \beta_3 * T * B \]

\begin{itemize}
\tightlist
\item
  DVs: migration attitudes \& issue definitions
\item
  Additional interactions for individual-level moderators.
\end{itemize}
\end{frame}

\hypertarget{measuring-issue-definitions}{%
\subsection{Measuring issue
definitions}\label{measuring-issue-definitions}}

\begin{frame}{Embedding regression (Rodriguez, Spirling, and Stewart
2020)}
\protect\hypertarget{embedding-regression-rodriguez2020}{}
\begin{itemize}
\tightlist
\item
  applicable in low-N environments.
\item
  pre-existing word embeddings to understand how different groups
  communicate about migration.
\item
  assess associations with migration in the MIP answers.
\end{itemize}
\end{frame}

\hypertarget{fin}{%
\subsection{Fin}\label{fin}}

\begin{frame}{Fin}
\center \Large Thank you for your attention!
\end{frame}

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\hypertarget{a-preliminary-effort-at-sentiment-identification}{%
\subsection{A preliminary effort at sentiment
identification}\label{a-preliminary-effort-at-sentiment-identification}}

\begin{frame}[allowframebreaks]{A preliminary effort at sentiment
identification}
\begin{itemize}
\tightlist
\item
  identify sentences mentioning terms from migration dictionary.
\item
  estimate sentiment of these sentences with German BERT sentiment
  classifier (Guhr et al. 2020).
\item
  Trained to classify a variety of German text (wiki, reviews, tweets,
  \ldots) into positive, neutral, and negative content
\end{itemize}

\includegraphics{vis/comparative_sentiment_migration.png}

\framebreak

However, unclear what this really measures:

\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs2.png}
\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs3.png}

\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs4.png}
\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs5.png}

\framebreak

Takeaways:

\begin{itemize}
\tightlist
\item
  wait for supervised coding.
\item
  focus on specific frames.
\item
  measure association.
\end{itemize}
\end{frame}

\hypertarget{resources}{%
\section{Resources}\label{resources}}

\hypertarget{resources-1}{%
\subsection*{Resources}\label{resources-1}}
\addcontentsline{toc}{subsection}{Resources}

\begin{frame}[allowframebreaks]{Resources}
\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Ajzen2000}{}%
Ajzen, Icek, and Martin Fishbein. 2000. {``{Attitudes and the
Attitude-Behavior Relation: Reasoned and Automatic Processes}.''}
\emph{European Review of Social Psychology} 11 (1): 1--33.
\url{https://doi.org/10.1080/14792779943000116}.

\leavevmode\hypertarget{ref-Bennett2008}{}%
Bennett, W. Lance, and Shanto Iyengar. 2008. {``{A new era of minimal
effects? The changing foundations of political communication}.''}
\emph{Journal of Communication} 58 (4): 707--31.
\url{https://doi.org/10.1111/j.1460-2466.2008.00410.x}.

\leavevmode\hypertarget{ref-Boomgaarden2009}{}%
Boomgaarden, Hajo G., and Rens Vliegenthart. 2009. {``{How news content
influences anti-immigration attitudes: Germany, 1993-2005}.''}
\emph{European Journal of Political Research} 48 (4): 516--42.
\url{https://doi.org/10.1111/j.1475-6765.2009.01831.x}.

\leavevmode\hypertarget{ref-Chiang2011a}{}%
Chiang, Chun Fang, and Brian Knight. 2011. {``{Media bias and influence:
Evidence from newspaper endorsements}.''} \emph{Review of Economic
Studies} 78 (3): 795--820. \url{https://doi.org/10.1093/restud/rdq037}.

\leavevmode\hypertarget{ref-Converse1962}{}%
Converse, Philip E. 1962. {``{Information flow and the stability of
partisan attitudes}.''} \emph{Public Opinion Quarterly} 26 (4): 578--99.
\url{https://doi.org/10.1086/267129}.

\leavevmode\hypertarget{ref-Devine2020}{}%
Devine, Daniel, and Justin Murphy. 2020. {``{Does Media Coverage Drive
Public Support for UKIP or Does Public Support for UKIP Drive Media
Coverage?}''} \emph{British Journal of Political Science} 50 (3):
893--910. \url{https://doi.org/10.1017/S0007123418000145}.

\leavevmode\hypertarget{ref-Foos2020}{}%
Foos, Florian, and Daniel Bischof. 2020. {``{Can the tabloid media
create Eurosceptic attitudes? A quasi-experiment on media innuence in
England},''} no. page 26.

\leavevmode\hypertarget{ref-Gentzkow2011}{}%
Gentzkow, Matthew, Jesse M. Shapiro, and Michael Sinkinson. 2011.
{``{The effect of newspaper entry and exit on electoral politics}.''}
\emph{American Economic Review} 101 (7): 2980--3018.
\url{https://doi.org/10.1257/aer.101.7.2980}.

\leavevmode\hypertarget{ref-Guess2021}{}%
Guess, Andrew M, Pablo Barberá, Simon Munzert, and Junghwan Yang. 2021.
{``{The consequences of online partisan media},''} 1--8.
\url{https://doi.org/10.1073/pnas.2013464118/-/DCSupplemental.y}.

\leavevmode\hypertarget{ref-Guhr2020}{}%
Guhr, Oliver, Anne Kathrin Schumann, Frank Bahrmann, and Hans Joachim
Böhme. 2020. {``{Training a broad-coverage German sentiment
classification model for dialog systems}.''} \emph{LREC 2020 - 12th
International Conference on Language Resources and Evaluation,
Conference Proceedings}, no. May: 1627--32.

\leavevmode\hypertarget{ref-King2017}{}%
King, Gary, Benjamin Schneer, and Ariel White. 2017. {``{How the news
media activate public expression and influence national agendas}.''}
\emph{Science} 358 (November): 776--80.
\url{https://doi.org/10.1007/978-1-349-11336-1_13}.

\leavevmode\hypertarget{ref-Ladd2009a}{}%
Ladd, Jonathan Mc Donald, and Gabriel S. Lenz. 2009. {``{Exploiting a
rare communication shift to document the persuasive power of the news
media}.''} \emph{American Journal of Political Science} 53 (2):
394--410. \url{https://doi.org/10.1111/j.1540-5907.2009.00377.x}.

\leavevmode\hypertarget{ref-Lau2021}{}%
Lau, Richard R., Kathleen Rogers, and Jamel Love. 2021. {``{Media
Effects in the Viewer's Choice Era: Testing Revised Agenda-Setting and
Priming Hypotheses}.''} \emph{Political Communication} 38 (3): 199--221.
\url{https://doi.org/10.1080/10584609.2020.1763526}.

\leavevmode\hypertarget{ref-McCombs1972}{}%
McCombs, Maxwell E., and Donald L Shaw. 1972. {``{The agenda-setting
function of mass media}.''} \emph{Public Opinion Quarterly} 36 (2):
176--87.

\leavevmode\hypertarget{ref-Nelson1997}{}%
Nelson, Thomas E, Rosalee A Clawson, and Zoe Oxley. 1997. {``{Media
Framing of a Civil Liberties Conflict and Its Effect on Tolerance}.''}
\emph{American Political Science Review} 91 (3): 567--83.

\leavevmode\hypertarget{ref-Rodriguez2020}{}%
Rodriguez, Pedro L., Arthur Spirling, and Brandon M. Stewart. 2020.
{``{Embedding Regression: Models for Context-Specific Description and
Inference in Political Science}.''}

\leavevmode\hypertarget{ref-Spirig2020}{}%
Spirig, Judith. 2020. {``{Media Take-Over and Voting Behavior : Can
Politician-Owned Newspapers Sway Voters ?}''}

\leavevmode\hypertarget{ref-Taber2006}{}%
Taber, Charles S, and Milton Lodge. 2006. {``{Motivated Skepticism in
the Evaluation of Political Beliefs}.''} \emph{American Journal of
Political Science} 50 (3): 755--69.

\leavevmode\hypertarget{ref-Zaller1992}{}%
Zaller, John. 1992. \emph{{The nature and origins of mass opinion}}.
Cambridge University Press.

\end{CSLReferences}
\end{frame}

\end{document}

### 2022-06-28 pres/20211007/PSAI_20211009.Rmd
Update pres as well
pray

---
title: "The effect of changing news frames"
subtitle: "Presentation at the 2021 Annual Conference of the Political Studies Association of Ireland"
author: "Nicolai Berk$^*$"
institute: "$^*$RTG Dynamics/Humboldt Universität zu Berlin"
date: "Oct 9th, 2021"
output: 
  beamer_presentation:
    theme: "Frankfurt"
    # colortheme: "lily"
    # fonttheme: "professionalfonts"
    slide_level: 2
    toc: False
header-includes:
# - \usepackage{fontawesome}
- \AtBeginSection{}
bibliography: PhD-Proposal.bib
---

# Motivation

\center

![](vis/volksempfanger.jpg){width=40%}

# Literature and Theory

## Media effects - maximal or minimal? {.allowframebreaks}

Maximal paradigm also follows from classic work:

- attitude instability [@Converse1962; @Zaller1992]
- agenda-setting [@McCombs1972]
- framing [@Nelson1997]

\framebreak

Minimal effects assumption with increasing media diversity [@Bennett2008]:

- media environment more polarised and more diverse,
- viewers more likely to reject news conflicting with their views,
- viewers can opt for other sources.

$\rightarrow$ strong effects unlikely

## Empirical evidence {.allowframebreaks}

### Evidence for large effects

- Framing effects found in experimental data [@Busby2019; @Leeper2020].
- Newspaper slant affects attitudes [@Foos2020].
- Salience and tonality of migration news affects attitudes [@Boomgaarden2009].

### Evidence for no/weak effects

- Newspaper slant has no effect on attitudes [@Gentzkow2011; @Guess2021; @Stetka2020].
- Newspaper takeovers have no effect on attitudes [@Durante2012; @Spirig2020].

## Synthesis

**When** can we expect strong media effects?

- Many current approaches test media effects of different outlets [@Gentzkow2011; @Guess2021].
- However, **news consumers discount bias and take cues from outlets**.
  + @Baum2008 show that consumers take heuristics about content bias from outlet brands.
  + @Chiang2011a show that outlet bias moderates the effect of candidate endorsements.

$\rightarrow$ **within-outlet changes** in content most likely cases to observe media effects.

## Emphasis framing {.allowframebreaks}

**What kind of changes should matter?**

- I draw on literature on 
  + the **value-expectancy** framework [@Ajzen2000].
  + and **emphasis framing** [@Leeper2020; @Nelson1997].
- Argues that issue attitudes are a product of **associated considerations**.

<!-- \framebreak -->

<!-- - For example, migration could be associated with  -->
<!--   + humanitarian crises in the mediterranean (positive frame);  -->
<!--   + crime (negative frame); -->
<!--   + cost for the welfare state (negative frame); -->
<!--   + labour market demand (positive frame). -->
<!-- - These considerations will be weighted to form an overall evaluation of the issue at hand. -->

\framebreak

![](vis/CognitiveStorage.png)

# Empirical strategy

## The case: Germany 2017

- First election after 2015 refugee movements.
- Radical-right challenger party enters parliament, center loses.
- Migration top of the agenda.

$\rightarrow$ constantly strong attention to migration,

$\rightarrow$ good case to study effects of framing.

## Design

- Collect 2.5M articles from major German newspapers.
- Classify according to migration content.
- Identify emphasis frames.
- Correlate changes in framing with changes in attitudes.

## Issue attitudes and news consumption {.allowframebreaks}

- Panel data from the German Longitudinal Election Study [@GLES2019LongTermTracking].
- Contains questions on news consumption and immigration and integration attitudes.
- 6 waves in 2017, containing both items.
- Immigration attitude measured on a 7-point Likert scale:
  + "*Immigration should be made easier (-3) or restricted (3)*".

## Migration content {.allowframebreaks}

- Pre-assign likelihoods for migration content using extended migration dictionary.
- Draw stratified sample of 1,800 articles, hand-code.
- Fine-tune German BERT deep-learning classifier.
- Performs very well: F1: 0.94, recall: 0.93, precision: 0.95.
- 13.5k out of 400k articles in 2017 about migration (3.5\%)

\framebreak

![](vis/salience_papers.png)

## Migration framing {.allowframebreaks}

- Estimate 60-topic structural topic model [@Roberts2014], using date and paper as covariates.
- Annotate.
- Select relevant frames with clear expectations regarding attitudinal effects.

\framebreak

**Topics**:

- Capital crime (sexual assault/rape/murder) committed by refugees,
- illegal entry and petty crime,
- refugee numbers,
- labour market needs for and job market integration of refugees,
- deportations,
- internment camps (e.g. Moria),
- drownings in the Mediterranean.

\framebreak

![](vis/frames_papers_pres.png)

## Estimation

*Two models*:

- OLS of aggregate Difference-in-Differences (DiDs).
- Individual-level model with 2-way fixed effects.

## DiD-model {.allowframebreaks}

$$y = \beta_1*W + \beta_2*R + \beta_3*W*R$$

\centering

![](vis/Illustration_of_Difference_in_Differences.png){width=50%}

\framebreak

- Estimate change in newspaper framing and attitudes among readers from one wave to another, controlling for shifts in other newspapers/reader groups.
- Regress opinion shift among readership on shift in newspaper attention to different frames.
- Better identified (exact change *beyond* general trend), 
- but framing not individually matched.

## 2-way FE model {.allowframebreaks}

- Individual estimate of frame attention for each respondent, according to newspaper read.
- Regress opinion on exposure to each frame, 
- controlling for wave and individual fixed-effects.

\framebreak

- Individual estimates,
- but explains *all* variation beyond 
  + time-independent individual factors and 
  + general trends across time,
  + including random individual deviations.

# Preliminary results

Different specifications:

- all readers/exclusive readers of one newspaper,
- different lags to measure exposure (1 day, 1 week, 1 month, half a year),
- immigration and integration attitude as dependent variable.

## Difference-in-Difference model {.allowframebreaks}

![](vis/frame_effects_did.png)

## Fixed-effect model

![](vis/frame_effects_fe.png)

## Preliminary conclusion

- No effects of media framing even in most-likely case.
- *However*, many possible explanations:
  + Measurement issues,
  + Issue-sorting in 2015, subsequent "digging in",
  + too little variation in dependent.

$\rightarrow$ further work necessary...

## Further hypotheses

- Motivated reasoning and polarisation [@Taber2006].
- Readers respond by changing outlet [@Arceneaux2013].
- Mobilisation, not attitudinal change [@Gentzkow2011; @Stetka2020].

## To-do's up next

- Clump frames together for holistic picture.
- Estimate effect on readership, attitude polarisation, and AfD-support.
- Natural experiment (again)?

## Fin

\centering

*Thank you!*

# Appendix

## Variation dependent variable {.allowframebreaks}

\centering

![](vis/imm_readers_pres.png)

\framebreak

\centering

![](vis/DiD_model_ps_immint.png)

## Salience {.allowframebreaks}

![](vis/salience_papers_focus.png)

## Framing attention {.allowframebreaks}

![](vis/frames_papers_focus_pres.png)

## Specifications DiD

\centering

![](vis/effectplot_frames_did.png){width=70%}

## Specifications 2-way FE

\centering

![](vis/effectplot_frames_fe_abs.png){width=70%}

# Resources

## Resources {.allowframebreaks}

### 2022-06-28 pres/20211007/PSAI_20211009.tex
Update pres as well
pray

--- 2022-06-28 pres/20210503/Presentation_20210503.tex
@@
 \hypersetup{
-  pdftitle={Hypodermic needle after all? Individual-level Moderators of Media Framing Effects},
+  pdftitle={The effect of changing news frames},
   pdfauthor={Nicolai Berk\^{}*},
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-
+\AtBeginSection{}
 \ifluatex
@@
 
-\title{Hypodermic needle after all? Individual-level Moderators of Media
-Framing Effects}
-\subtitle{Presentation at EPSIP Colloquium, HU Berlin}
+\title{The effect of changing news frames}
+\subtitle{Presentation at the 2021 Annual Conference of the Political
+Studies Association of Ireland}
 \author{Nicolai Berk\(^*\)}
-\date{May 3rd, 2021}
+\date{Oct 9th, 2021}
 \institute{\(^*\)RTG Dynamics/Humboldt Universität zu Berlin}
@@
 
-\hypertarget{media-effects---maximal-or-minimal}{%
-\subsection{Media effects - maximal or
-minimal?}\label{media-effects---maximal-or-minimal}}
-
-\begin{frame}[allowframebreaks]{Media effects - maximal or minimal?}
+\begin{frame}{Motivation}
 \center
@@
 \includegraphics[width=0.4\textwidth,height=\textheight]{vis/volksempfanger.jpg}
-\includegraphics[width=0.4\textwidth,height=\textheight]{vis/ufo_scares.jpg}
+\end{frame}
 
-\flushleft
+\hypertarget{literature-and-theory}{%
+\section{Literature and Theory}\label{literature-and-theory}}
 
-\framebreak
-
-Maximal paradigm also follows from classic work
+\begin{frame}[allowframebreaks]{Media effects - maximal or minimal?}
+\protect\hypertarget{media-effects---maximal-or-minimal}{}
+Maximal paradigm also follows from classic work:
 
@@
 \item
+  agenda-setting (McCombs and Shaw 1972)
+\item
   framing (Nelson, Clawson, and Oxley 1997)
-\item
-  agenda-setting (McCombs and Shaw 1972)
 \end{itemize}
@@
 \framebreak
-
-\center
-
-\includegraphics[width=0.3\textwidth,height=\textheight]{vis/mineff.png}
-
-\flushleft
 
@@
 \(\rightarrow\) strong effects unlikely
-
-\framebreak
-
-Evidence seems to support both views:
 \end{frame}
 
-\begin{frame}{strong media effects on:}
-\protect\hypertarget{strong-media-effects-on}{}
+\begin{frame}[allowframebreaks]{Empirical evidence}
+\protect\hypertarget{empirical-evidence}{}
+\begin{block}{Evidence for large effects}
+\protect\hypertarget{evidence-for-large-effects}{}
 \begin{itemize}
@@
 \item
-  voting behaviour (Boomgaarden and Vliegenthart 2009; Devine and Murphy
-  2020; Ladd and Lenz 2009),
+  Framing effects found in experimental data (Busby, Flynn, and Druckman
+  2019; Leeper and Slothuus 2020).
 \item
-  issue agenda (King, Schneer, and White 2017),
+  Newspaper slant affects attitudes (Foos and Bischof 2020).
 \item
-  attitudes (Nelson, Clawson, and Oxley 1997; Foos and Bischof 2020)
+  Salience and tonality of migration news affects attitudes (Boomgaarden
+  and Vliegenthart 2009).
 \end{itemize}
-\end{frame}
+\end{block}
 
-\begin{frame}{weak or no effects on:}
-\protect\hypertarget{weak-or-no-effects-on}{}
+\begin{block}{Evidence for no/weak effects}
+\protect\hypertarget{evidence-for-noweak-effects}{}
 \begin{itemize}
@@
 \item
-  voting behaviour (Gentzkow, Shapiro, and Sinkinson 2011),
+  Newspaper slant has no effect on attitudes (Gentzkow, Shapiro, and
+  Sinkinson 2011; Guess et al. 2021; Štětka, Mihelj, and Tóth 2020).
 \item
-  issue agenda (Lau, Rogers, and Love 2021),
-\item
-  attitudes (Guess et al. 2021).
+  Newspaper takeovers have no effect on attitudes (Durante and Knight
+  2012; Spirig 2020).
 \end{itemize}
+\end{block}
 \end{frame}
 
-\hypertarget{moderators}{%
-\section{Moderators}\label{moderators}}
-
-\hypertarget{towards-a-theory-of-conditioning-factors}{%
-\subsection{Towards a theory of conditioning
-factors}\label{towards-a-theory-of-conditioning-factors}}
-
-\begin{frame}{Towards a theory of conditioning factors}
-Recently more discussion of moderators
+\begin{frame}{Synthesis}
+\protect\hypertarget{synthesis}{}
+\textbf{When} can we expect strong media effects?
 
@@
 \item
-  Mostly based on expectations regarding source:
+  Many current approaches test media effects of different outlets
+  (Gentzkow, Shapiro, and Sinkinson 2011; Guess et al. 2021).
+\item
+  However, \textbf{news consumers discount bias and take cues from
+  outlets}.
 
@@
   \item
-    Discounting of biased news (Chiang and Knight 2011)
+    Baum and Gussin (2008) show that consumers take heuristics about
+    content bias from outlet brands.
   \item
-    Rejection of partisan takeovers (Spirig 2020)
+    Chiang and Knight (2011) show that outlet bias moderates the effect
+    of candidate endorsements.
   \end{itemize}
-\item
-  facing biased new media outlets doesn't seem to affect citizens (Guess
-  et al. 2021)
 \end{itemize}
+
+\(\rightarrow\) \textbf{within-outlet changes} in content most likely
+cases to observe media effects.
 \end{frame}
 
-\hypertarget{open-questions}{%
-\subsection{Open questions:}\label{open-questions}}
-
-\begin{frame}{Open questions:}
-\begin{itemize}
-\tightlist
-\item
-  What about outlets currently consumed changing their commentary?
-\item
-  What about individual-level factors?
+\begin{frame}[allowframebreaks]{Emphasis framing}
+\protect\hypertarget{emphasis-framing}{}
+\textbf{What kind of changes should matter?}
 
@@
 \item
-    political knowledge, opinion strength (Zaller 1992)?
-  \item
-    media diet (Bennett and Iyengar 2008)?
-  \item
-    partisan identification (Taber and Lodge 2006)?
-  \end{itemize}
-\item
-  Is attitude change a result of changing issue definitions (Ajzen and
-  Fishbein 2000; Nelson, Clawson, and Oxley 1997)?
-\end{itemize}
-\end{frame}
-
-\hypertarget{the-case}{%
-\section{The case}\label{the-case}}
-
-\begin{frame}{The case}
-\begin{itemize}
-\tightlist
-\item
-  In fall of 2015, major German tabloid Bild started calling for support
-  for incoming refugees.
-\item
-  This was a major deviation from the papers' agitative history.
-\end{itemize}
-
-\includegraphics{vis/BildFlüchtlingskinder.png}
-
-\includegraphics{vis/BildNot.png}
-\end{frame}
-
-\hypertarget{onwards-the-framing-changed}{%
-\subsection{2016 onwards the framing
-changed}\label{onwards-the-framing-changed}}
-
-\begin{frame}{2016 onwards the framing changed}
-\center
-
-\includegraphics[width=\textwidth,height=0.5\textheight]{vis/UebermedienBild2.png}
-\end{frame}
-
-\hypertarget{logic-of-the-paper}{%
-\subsection{Logic of the paper}\label{logic-of-the-paper}}
-
-\begin{frame}{Logic of the paper}
-\begin{itemize}
-\tightlist
-\item
-  I argue this represents a natural experiment to study migration
-  framing,
-\item
-  allowing to identify the \emph{causal} impact of news framing on:
+  I draw on literature on
 
@@
   \item
-    migration opinions,
+    the \textbf{value-expectancy} framework (Ajzen and Fishbein 2000).
   \item
-    and issue definitions.
+    and \textbf{emphasis framing} (Leeper and Slothuus 2020; Nelson,
+    Clawson, and Oxley 1997).
   \end{itemize}
 \item
-  especially interesting case:
+  Argues that issue attitudes are a product of \textbf{associated
+  considerations}.
+\end{itemize}
+
+\framebreak
+
+\includegraphics{vis/CognitiveStorage.png}
+\end{frame}
+
+\hypertarget{empirical-strategy}{%
+\section{Empirical strategy}\label{empirical-strategy}}
+
+\begin{frame}{The case: Germany 2017}
+\protect\hypertarget{the-case-germany-2017}{}
+\begin{itemize}
+\tightlist
+\item
+  First election after 2015 refugee movements.
+\item
+  Radical-right challenger party enters parliament, center loses.
+\item
+  Migration top of the agenda.
+\end{itemize}
+
+\(\rightarrow\) constantly strong attention to migration,
+
+\(\rightarrow\) good case to study effects of framing.
+\end{frame}
+
+\begin{frame}{Design}
+\protect\hypertarget{design}{}
+\begin{itemize}
+\tightlist
+\item
+  Collect 2.5M articles from major German newspapers.
+\item
+  Classify according to migration content.
+\item
+  Identify emphasis frames.
+\item
+  Correlate changes in framing with changes in attitudes.
+\end{itemize}
+\end{frame}
+
+\begin{frame}[allowframebreaks]{Issue attitudes and news consumption}
+\protect\hypertarget{issue-attitudes-and-news-consumption}{}
+\begin{itemize}
+\tightlist
+\item
+  Panel data from the German Longitudinal Election Study (GLES 2019).
+\item
+  Contains questions on news consumption and immigration and integration
+  attitudes.
+\item
+  6 waves in 2017, containing both items.
+\item
+  Immigration attitude measured on a 7-point Likert scale:
 
@@
   \item
-    instead of treatment with a new source (Guess et al. 2021),
-    cue-taking (from the newspaper) can be expected.
-  \item
-    expectation of change in bias among readers unlikely (Chiang and
-    Knight 2011; Spirig 2020)
+    ``\emph{Immigration should be made easier (-3) or restricted (3)}.''
   \end{itemize}
 \end{itemize}
-
-\emph{\(\rightarrow\) strong expectations for framing effect!}
 \end{frame}
 
-\hypertarget{data-and-research-design}{%
-\section{Data and research design}\label{data-and-research-design}}
-
-\hypertarget{the-gles-offers-a-number-of-possible-data-sources}{%
-\subsection{The GLES offers a number of possible data
-sources:}\label{the-gles-offers-a-number-of-possible-data-sources}}
-
-\begin{frame}{The GLES offers a number of possible data sources:}
+\begin{frame}[allowframebreaks]{Migration content}
+\protect\hypertarget{migration-content}{}
 \begin{itemize}
@@
 \item
-  Longterm-tracking,
+  Pre-assign likelihoods for migration content using extended migration
+  dictionary.
+\item
+  Draw stratified sample of 1,800 articles, hand-code.
+\item
+  Fine-tune German BERT deep-learning classifier.
+\item
+  Performs very well: F1: 0.94, recall: 0.93, precision: 0.95.
+\item
+  13.5k out of 400k articles in 2017 about migration (3.5\%)
+\end{itemize}
+
+\framebreak
+
+\includegraphics{vis/salience_papers.png}
+\end{frame}
+
+\begin{frame}[allowframebreaks]{Migration framing}
+\protect\hypertarget{migration-framing}{}
+\begin{itemize}
+\tightlist
+\item
+  Estimate 60-topic structural topic model (Roberts et al. 2014), using
+  date and paper as covariates.
+\item
+  Annotate.
+\item
+  Select relevant frames with clear expectations regarding attitudinal
+  effects.
+\end{itemize}
+
+\framebreak
+
+\textbf{Topics}:
 
@@
 \item
-    N \(\approx\) 1000,
+  Capital crime (sexual assault/rape/murder) committed by refugees,
 \item
-    four times/year,
+  illegal entry and petty crime,
 \item
-    2009-17
+  refugee numbers,
+\item
+  labour market needs for and job market integration of refugees,
+\item
+  deportations,
+\item
+  internment camps (e.g.~Moria),
+\item
+  drownings in the Mediterranean.
 \end{itemize}
-\item
-  Panel,
+
+\framebreak
+
+\includegraphics{vis/frames_papers_pres.png}
+\end{frame}
+
+\begin{frame}{Estimation}
+\protect\hypertarget{estimation}{}
+\emph{Two models}:
 
@@
 \item
-    N \(>\) 10,000,
+  OLS of aggregate Difference-in-Differences (DiDs).
 \item
-    clustered around election
+  Individual-level model with 2-way fixed effects.
 \end{itemize}
-\end{itemize}
+\end{frame}
 
-Both regularly contain questions on
+\begin{frame}[allowframebreaks]{DiD-model}
+\protect\hypertarget{did-model}{}
+\[y = \beta_1*W + \beta_2*R + \beta_3*W*R\]
+
+\centering
+
+\includegraphics[width=0.5\textwidth,height=\textheight]{vis/Illustration_of_Difference_in_Differences.png}
+
+\framebreak
 
@@
 \item
-  news consumption,
+  Estimate change in newspaper framing and attitudes among readers from
+  one wave to another, controlling for shifts in other newspapers/reader
+  groups.
 \item
-  migration/integration attitudes,
+  Regress opinion shift among readership on shift in newspaper attention
+  to different frames.
 \item
-  open-ended MIP.
+  Better identified (exact change \emph{beyond} general trend),
+\item
+  but framing not individually matched.
 \end{itemize}
@@
 
-\hypertarget{treatments-and-field-dates}{%
-\subsection{Treatments and Field
-Dates}\label{treatments-and-field-dates}}
-
-\begin{frame}[allowframebreaks]{Treatments and Field Dates}
-Journalists ascribe change to changing editors. This leaves us with a
-total of 4 possible treatments:
-
-\begin{enumerate}
+\begin{frame}[allowframebreaks]{2-way FE model}
+\protect\hypertarget{way-fe-model}{}
+\begin{itemize}
 \tightlist
 \item
-  Summer of 2015
+  Individual estimate of frame attention for each respondent, according
+  to newspaper read.
 \item
-  Diekmann replaced as editor-in-chief by Tanit Koch in 2016,
+  Regress opinion on exposure to each frame,
 \item
-  Diekmann finally left Bild in February 2017,
-\item
-  Koch replaced by Julian Reichelt in January 2018.
-\end{enumerate}
-
-Not entirely clear which treatment is relevant -\textgreater{} assess
-changing framing in the newspaper!
+  controlling for wave and individual fixed-effects.
+\end{itemize}
 
 \framebreak
-
-\includegraphics{vis/gles_treatments.png}
-\end{frame}
-
-\hypertarget{treatment-selection}{%
-\subsection{Treatment selection}\label{treatment-selection}}
-
-\begin{frame}{Treatment selection}
-\begin{enumerate}
-\item
-  Pre-select migration content with supervised classifier.
-\item
-  Several possible approaches for treatment identification:
-\end{enumerate}
 
@@
 \item
-  inductive frame identification (FA/STM)
+  Individual estimates,
 \item
-  dictionary for frames (humanitarian/crime/\ldots)
-\item
-  sentiment towards migration
-\end{itemize}
-
-\begin{enumerate}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Treatment identified where parallel paths diverge
-\end{enumerate}
-\end{frame}
-
-\hypertarget{modelling}{%
-\subsection{Modelling}\label{modelling}}
-
-\begin{frame}{Modelling}
-Diff-in-Diff:
-
-\center
-
-\[ y = \beta_1 * T + \beta_2 * B + \beta_3 * T * B \]
+  but explains \emph{all} variation beyond
 
@@
   \item
-  DVs: migration attitudes \& issue definitions
+    time-independent individual factors and
   \item
-  Additional interactions for individual-level moderators.
+    general trends across time,
+  \item
+    including random individual deviations.
+  \end{itemize}
 \end{itemize}
@@
 
-\hypertarget{measuring-issue-definitions}{%
-\subsection{Measuring issue
-definitions}\label{measuring-issue-definitions}}
+\hypertarget{preliminary-results}{%
+\section{Preliminary results}\label{preliminary-results}}
 
-\begin{frame}{Embedding regression (Rodriguez, Spirling, and Stewart
-2020)}
-\protect\hypertarget{embedding-regression-rodriguez2020}{}
+\begin{frame}{Preliminary results}
+Different specifications:
+
 \begin{itemize}
@@
 \item
-  applicable in low-N environments.
+  all readers/exclusive readers of one newspaper,
 \item
-  pre-existing word embeddings to understand how different groups
-  communicate about migration.
+  different lags to measure exposure (1 day, 1 week, 1 month, half a
+  year),
 \item
-  assess associations with migration in the MIP answers.
+  immigration and integration attitude as dependent variable.
 \end{itemize}
@@
 
-\hypertarget{fin}{%
-\subsection{Fin}\label{fin}}
+\begin{frame}[allowframebreaks]{Difference-in-Difference model}
+\protect\hypertarget{difference-in-difference-model}{}
+\includegraphics{vis/frame_effects_did.png}
+\end{frame}
+
+\begin{frame}{Fixed-effect model}
+\protect\hypertarget{fixed-effect-model}{}
+\includegraphics{vis/frame_effects_fe.png}
+\end{frame}
+
+\begin{frame}{Preliminary conclusion}
+\protect\hypertarget{preliminary-conclusion}{}
+\begin{itemize}
+\tightlist
+\item
+  No effects of media framing even in most-likely case.
+\item
+  \emph{However}, many possible explanations:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Measurement issues,
+  \item
+    Issue-sorting in 2015, subsequent ``digging in,''
+  \item
+    too little variation in dependent.
+  \end{itemize}
+\end{itemize}
+
+\(\rightarrow\) further work necessary\ldots{}
+\end{frame}
+
+\begin{frame}{Further hypotheses}
+\protect\hypertarget{further-hypotheses}{}
+\begin{itemize}
+\tightlist
+\item
+  Motivated reasoning and polarisation (Taber and Lodge 2006).
+\item
+  Readers respond by changing outlet (Arceneaux and Johnson 2013).
+\item
+  Mobilisation, not attitudinal change (Gentzkow, Shapiro, and Sinkinson
+  2011; Štětka, Mihelj, and Tóth 2020).
+\end{itemize}
+\end{frame}
+
+\begin{frame}{To-do's up next}
+\protect\hypertarget{to-dos-up-next}{}
+\begin{itemize}
+\tightlist
+\item
+  Clump frames together for holistic picture.
+\item
+  Estimate effect on readership, attitude polarisation, and AfD-support.
+\item
+  Natural experiment (again)?
+\end{itemize}
+\end{frame}
 
 \begin{frame}{Fin}
-\center \Large Thank you for your attention!
+\protect\hypertarget{fin}{}
+\centering
+
+\emph{Thank you!}
 \end{frame}
@@
 
-\hypertarget{a-preliminary-effort-at-sentiment-identification}{%
-\subsection{A preliminary effort at sentiment
-identification}\label{a-preliminary-effort-at-sentiment-identification}}
+\begin{frame}[allowframebreaks]{Variation dependent variable}
+\protect\hypertarget{variation-dependent-variable}{}
+\centering
 
-\begin{frame}[allowframebreaks]{A preliminary effort at sentiment
-identification}
-\begin{itemize}
-\tightlist
-\item
-  identify sentences mentioning terms from migration dictionary.
-\item
-  estimate sentiment of these sentences with German BERT sentiment
-  classifier (Guhr et al. 2020).
-\item
-  Trained to classify a variety of German text (wiki, reviews, tweets,
-  \ldots) into positive, neutral, and negative content
-\end{itemize}
-
-\includegraphics{vis/comparative_sentiment_migration.png}
+\includegraphics{vis/imm_readers_pres.png}
 
@@
 
-However, unclear what this really measures:
+\centering
 
-\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs2.png}
-\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs3.png}
+\includegraphics{vis/DiD_model_ps_immint.png}
+\end{frame}
 
-\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs4.png}
-\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs5.png}
+\begin{frame}[allowframebreaks]{Salience}
+\protect\hypertarget{salience}{}
+\includegraphics{vis/salience_papers_focus.png}
+\end{frame}
 
-\framebreak
+\begin{frame}[allowframebreaks]{Framing attention}
+\protect\hypertarget{framing-attention}{}
+\includegraphics{vis/frames_papers_focus_pres.png}
+\end{frame}
 
-Takeaways:
+\begin{frame}{Specifications DiD}
+\protect\hypertarget{specifications-did}{}
+\centering
 
-\begin{itemize}
-\tightlist
-\item
-  wait for supervised coding.
-\item
-  focus on specific frames.
-\item
-  measure association.
-\end{itemize}
+\includegraphics[width=0.7\textwidth,height=\textheight]{vis/effectplot_frames_did.png}
+\end{frame}
+
+\begin{frame}{Specifications 2-way FE}
+\protect\hypertarget{specifications-2-way-fe}{}
+\centering
+
+\includegraphics[width=0.7\textwidth,height=\textheight]{vis/effectplot_frames_fe_abs.png}
 \end{frame}
@@
 
-\hypertarget{resources-1}{%
-\subsection*{Resources}\label{resources-1}}
-\addcontentsline{toc}{subsection}{Resources}
-
 \begin{frame}[allowframebreaks]{Resources}
+\protect\hypertarget{resources-1}{}
 \hypertarget{refs}{}
@@
 \url{https://doi.org/10.1080/14792779943000116}.
+
+\leavevmode\hypertarget{ref-Arceneaux2013}{}%
+Arceneaux, Kevin, and Martin Johnson. 2013. \emph{{Changing Mind or
+Changing Channels? Partisan News in an Age of Choice}}. University of
+Chicago Press.
+
+\leavevmode\hypertarget{ref-Baum2008}{}%
+Baum, Matthew A., and Phil Gussin. 2008. {``{In the Eye of the Beholder:
+How Information Shortcuts Shape Individual Perceptions of Bias in the
+Media}.''} \emph{Quarterly Journal of Political Science} 3 (1): 1--31.
+https://doi.org/\url{http://dx.doi.org/10.1561/100.00007010}.
 
@@
 
+\leavevmode\hypertarget{ref-Busby2019}{}%
+Busby, Ethan, D. J. Flynn, and James N. Druckman. 2019. {``{Studying
+Framing Effects on Political Preferences}.''} \emph{Doing News Framing
+Analysis II}, 27--50. \url{https://doi.org/10.4324/9781315642239-2}.
+
 \leavevmode\hypertarget{ref-Chiang2011a}{}%
@@
 
-\leavevmode\hypertarget{ref-Devine2020}{}%
-Devine, Daniel, and Justin Murphy. 2020. {``{Does Media Coverage Drive
-Public Support for UKIP or Does Public Support for UKIP Drive Media
-Coverage?}''} \emph{British Journal of Political Science} 50 (3):
-893--910. \url{https://doi.org/10.1017/S0007123418000145}.
+\leavevmode\hypertarget{ref-Durante2012}{}%
+Durante, Ruben, and Brian Knight. 2012. {``{Partisan control, media
+bias, and viewer responses: Evidence from berlusconi's italy}.''}
+\emph{Journal of the European Economic Association} 10 (3): 451--81.
+\url{https://doi.org/10.1111/j.1542-4774.2011.01060.x}.
 
@@
 
+\leavevmode\hypertarget{ref-GLES2019LongTermTracking}{}%
+GLES. 2019. {``{Longterm-Online-Tracking 2009-2017 (GLES)}.''} Cologne:
+GESIS Data Archive.
+https://doi.org/\url{https://doi.org/10.4232/1.13416}.
+
 \leavevmode\hypertarget{ref-Guess2021}{}%
@@
 
-\leavevmode\hypertarget{ref-Guhr2020}{}%
-Guhr, Oliver, Anne Kathrin Schumann, Frank Bahrmann, and Hans Joachim
-Böhme. 2020. {``{Training a broad-coverage German sentiment
-classification model for dialog systems}.''} \emph{LREC 2020 - 12th
-International Conference on Language Resources and Evaluation,
-Conference Proceedings}, no. May: 1627--32.
-
-\leavevmode\hypertarget{ref-King2017}{}%
-King, Gary, Benjamin Schneer, and Ariel White. 2017. {``{How the news
-media activate public expression and influence national agendas}.''}
-\emph{Science} 358 (November): 776--80.
-\url{https://doi.org/10.1007/978-1-349-11336-1_13}.
-
-\leavevmode\hypertarget{ref-Ladd2009a}{}%
-Ladd, Jonathan Mc Donald, and Gabriel S. Lenz. 2009. {``{Exploiting a
-rare communication shift to document the persuasive power of the news
-media}.''} \emph{American Journal of Political Science} 53 (2):
-394--410. \url{https://doi.org/10.1111/j.1540-5907.2009.00377.x}.
-
-\leavevmode\hypertarget{ref-Lau2021}{}%
-Lau, Richard R., Kathleen Rogers, and Jamel Love. 2021. {``{Media
-Effects in the Viewer's Choice Era: Testing Revised Agenda-Setting and
-Priming Hypotheses}.''} \emph{Political Communication} 38 (3): 199--221.
-\url{https://doi.org/10.1080/10584609.2020.1763526}.
+\leavevmode\hypertarget{ref-Leeper2020}{}%
+Leeper, Thomas J., and Rune Slothuus. 2020. {``{How the News Media
+Persuades}.''} \emph{The Oxford Handbook of Electoral Persuasion},
+150--68. \url{https://doi.org/10.1093/oxfordhb/9780190860806.013.4}.
 
@@
 
-\leavevmode\hypertarget{ref-Rodriguez2020}{}%
-Rodriguez, Pedro L., Arthur Spirling, and Brandon M. Stewart. 2020.
-{``{Embedding Regression: Models for Context-Specific Description and
-Inference in Political Science}.''}
+\leavevmode\hypertarget{ref-Roberts2014}{}%
+Roberts, Margaret E., Brandon M. Stewart, Dustin Tingley, Christopher
+Lucas, Jetson Leder-Luis, Shana Kushner Gadarian, Bethany Albertson, and
+David G. Rand. 2014. {``{Structural topic models for open-ended survey
+responses}.''} \emph{American Journal of Political Science} 58 (4):
+1064--82. \url{https://doi.org/10.1111/ajps.12103}.
 
@@
 Politician-Owned Newspapers Sway Voters ?}''}
+
+\leavevmode\hypertarget{ref-Stetka2020}{}%
+Štětka, Václav, Sabina Mihelj, and Fanni Tóth. 2020. {``{The Impact of
+News Consumption on Anti-immigration Attitudes and Populist Party
+Support in a Changing Media Ecology}.''} \emph{Political Communication}
+38 (5): 539--60. \url{https://doi.org/10.1080/10584609.2020.1820647}.
 

### 2022-06-28 pres/20211014/TADA_20211014.Rmd
Update pres as well
pray

--- 2022-06-28 pres/20211007/PSAI_20211009.Rmd
@@
 title: "The effect of changing news frames"
-subtitle: "Presentation at the 2021 Annual Conference of the Political Studies Association of Ireland"
 author: "Nicolai Berk$^*$"
 institute: "$^*$RTG Dynamics/Humboldt Universität zu Berlin"
-date: "Oct 9th, 2021"
+date: "Oct 14th, 2021"
 output: 
@@
 - Many current approaches test media effects of different outlets [@Gentzkow2011; @Guess2021].
-- However, **news consumers discount bias and take cues from outlets**.
+- However, \alert{news consumers discount bias and take cues from outlets}.
   + @Baum2008 show that consumers take heuristics about content bias from outlet brands.
@@
 
-$\rightarrow$ **within-outlet changes** in content most likely cases to observe media effects.
+$\rightarrow$ \alert{within-outlet changes} in content most likely cases to observe media effects.
 
@@
 - I draw on literature on 
-  + the **value-expectancy** framework [@Ajzen2000].
-  + and **emphasis framing** [@Leeper2020; @Nelson1997].
-- Argues that issue attitudes are a product of **associated considerations**.
+  + the \alert{value-expectancy} framework [@Ajzen2000].
+  + and \alert{emphasis framing} [@Leeper2020; @Nelson1997].
+- Argues that issue attitudes are a product of \alert{associated considerations}.
 
@@
 
-**Topics**:
+\alert{Topics}:
 

### 2022-06-28 pres/20211028/EPSIP_20211028.Rmd
Update pres as well
pray

--- 2022-06-28 pres/20211014/TADA_20211014.Rmd
@@
 
-![](vis/volksempfanger.jpg){width=40%}
+![](vis/volksempfanger.jpg){width=30%} 
+![](vis/bild_umgebracht_asyl.jpeg){width=60%}
 
@@
 - Panel data from the German Longitudinal Election Study [@GLES2019LongTermTracking].
-- Contains questions on news consumption and immigration and integration attitudes.
-- 6 waves in 2017, containing both items.
-- Immigration attitude measured on a 7-point Likert scale:
-  + "*Immigration should be made easier (-3) or restricted (3)*".
+- Contains questions on news consumption, immigration and integration attitudes, as well as party preference.
+- Dependent variables:
+  + Immigration attitude (7-point scale).
+  + Integration attitude (7-point scale).
+  + Attitude toward AfD (11-point scale).
 
@@
 
-- Capital crime (sexual assault/rape/murder) committed by refugees,
-- illegal entry and petty crime,
+- Capital/sexual crime committed by refugees,
+- general crime,
 - refugee numbers,
@@
 
-## Preliminary conclusion
+## Preliminary conclusion {.allowframebreaks}
 
-- No effects of media framing even in most-likely case.
-- *However*, many possible explanations:
-  + Measurement issues,
-  + Issue-sorting in 2015, subsequent "digging in",
-  + too little variation in dependent.
+\begin{center}
+
+\textbf{No effects of media framing even when considering within-outlet changes.}
+
+\end{center}
+
+\framebreak
+
+However, other possible explanations:
+
+- Issue-sorting in 2015, subsequent "digging in",
+- Measurement issues (esp. news exposure).
 
@@
 
-## Further hypotheses
+## Next steps (possibly paper #2)
 
-- Motivated reasoning and polarisation [@Taber2006].
-- Readers respond by changing outlet [@Arceneaux2013].
-- Mobilisation, not attitudinal change [@Gentzkow2011; @Stetka2020].
+### Theoretical additions:
 
-## To-do's up next
+- Test if readers respond by **stopping to read newspaper** [@Arceneaux2013; @Chiang2011a].
+- Assess **issue sorting** [@Carmines1986] across time.
 
-- Clump frames together for holistic picture.
-- Estimate effect on readership, attitude polarisation, and AfD-support.
-- Natural experiment (again)?
+### Empirical additions:
+
+- (Alternative measure of association: diachronic embeddings? embedding topic model?)
+- (Back to natural experiment?)
+- (More cases?)
 
@@
 ![](vis/DiD_model_ps_immint.png)
+
+## Potential natural experiment
+
+\centering
+
+![](vis/frames_bild_diekmann_pres.png)
 

### 2022-06-28 pres/20211126/PolBB_261121.Rmd
Update pres as well
pray

---
title: "Assessing media influence in contemporary news environments"
subtitle: "Right-wing media, crime, and anti-immigration attitudes"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
    includes:
      after_body: insert-logo.html
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#03396d", background_color = "#bfbfbf",
  base_font_size = "25px",
  header_h1_font_size = "2rem",
  header_h2_font_size = "1.75rem",
  header_h3_font_size = "1.25rem",
  header_font_google = google_font("Montserrat", 'Thin 100'),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  footnote_font_size = "0.75rem"
)
```

class: inverse, center, middle

# Media Influence in Contemporary News Environments
### Right-wing Media, Crime, and Anti-Immigration Attitudes

<br></br>

### Nicolai Berk<sup>*</sup>

Presentation at the Political Behavior Workshop Berlin-Brandenburg, WZB

`r Sys.Date()`

.left[.footnote[<sup>*</sup> Dynamics RTG & Humboldt Universität Berlin]]

---
class: middle, center, inverse

# Can the news media affect voters' political attitudes and behaviour?

---

# Can the news media shape opinions?

### Maximal effects literature builds on 
  + idea that __media is the main source of information__ for citizens,
  + experimental findings,
  + attitude instability (Converse; Zaller).

### Minimal effects scholars argue that 
  + __selective exposure__ 
  + in diverse and polarised contemporary news markets
  + make opinion changes unlikely.
  + Consumers will instead __change outlet__.

---

# Empirical literature

### Focus on

- __changing supply__ in media markets (Foos & Bischof 2020; Gentzkow, Shapiro & Silkinson 2011; Grossman, Margalit & Mitts 2021),
- __highly visible__ media takeovers (Durante & Knight 2012; Spirig 2020).

--

### Findings:

- __Consumers change outlet, but not opinion__ when takeovers are salient (Durante & Knight 2012; Spirig 2020).
- __Consumers persuaded__ when they change outlet (Grossman, Margalit & Mitts 2021).
- __Consumers socialised__ in new media environment will change opinion (Foos & Bischof 2020).

---

# Blind spots I

Highly visible takeovers & media changes such as boycotts result in __co-treatment__.

### Example: Sun Boycott in Merseyside (Foos & Bischof 2021)

> "_You’re in Liverpool mate, not sure if you’re a football fan, but no Scouser would dare read it. You might get the odd one or two in the city, maybe the odd tourist, but that’s about it. Ever since Hillsborough, nobody in this city touches it._"  (p. 5).

---
# Blind spots II

### Unclear whether

- __less visible changes__ in the framing of a media outlet might __persuade__.
- short-term effects ( __persuasion__ ) can be observed __or socialisation__ is main mechanism.
- changes in __framing or co-treatment__ (esp. identity changes) are main driver.

<!-- __First evidence on less visible changes in media framing suggests persuasive effects (Djourelova 2021).__ -->

---

class: center, inverse, middle

# Are changes in framing more persuasive when they are less visible?

---

# The Case

.left-column[

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/3/3c/Kai_Diekmann_MediaMakers.jpg/435px-Kai_Diekmann_MediaMakers.jpg)

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/5/5a/2018-11-07-Julian_Reichelt-Maischberger-1141.jpg/800px-2018-11-07-Julian_Reichelt-Maischberger-1141.jpg)

]

.right-column[

- Bild editor-in-chief Kai Diekmann drove an unexpectedly positive slant towards refugees in 2015.
- Diekmann left in February 2017, with Reichelt taking over.
- Reichelt increasingly **framed migrants as criminals** (Niggemeier 2018).

Interesting because:

- __Low-salience__ change in editorial slant.
- clearly identifiable short-term-change in framing.
$\rightarrow$ __No co-treatment__!

]

---
# Emphasis framing

**Why should changing definitions matter?**

- I draw on literature on 
  + the __value-expectancy framework__ (Ajzen & Fishbein 2000).
  + and __emphasis framing__ (Leeper and Slothuus 2020; Nelson et al. 1997).
- Argues that issue attitudes are a product of __associated considerations__.

---
class: center, middle

.left[
# Emphasis framing II 
]

```{r emph_framing, eval=TRUE, echo = F, out.width="70%", fig.pos="center"}

knitr::include_graphics(path = "vis/CognitiveStorage.png")

```

---
class: inverse, center, middle

# Empirical Strategy

---
# Measuring Framing

### Identify migration content

- Annotate 1800 articles to identify their migration content.
- Fine-tune German BERT deep-learning classifier.
- accuracy: 95.5% (F1: 0.94, recall: 0.93, precision: 0.95)
- 13.5k out of 400k articles in 2017 about migration (3.5\%)

### Measure migration frames

- Estimate 60-topic structural topic model (Roberts, Stewart and Tingley 2019), using date and paper as covariates.
- Annotate.
- Select relevant frames with clear expectations regarding attitudinal effects.

---
class: inverse, center, middle

```{r salience_des, eval=TRUE, echo = F, out.width="70%", fig.pos="center"}

knitr::include_graphics(path = "vis/salience_papers.png")

```

---
class: inverse, center, middle

```{r frames_des, eval=TRUE, echo = F, out.width="70%", fig.pos="center"}

knitr::include_graphics(path = "vis/frames_papers_pres.png")

```

---
# The treatment I

```{r treatment, eval=TRUE, echo = F, out.width="70%", fig.pos="center"}

knitr::include_graphics(path = "vis/frames_bild_diekmann_pres.png")

```

---
# The treatment II

```{r treatment2, eval=TRUE, echo = F, out.width="70%", fig.pos="center"}

knitr::include_graphics(path = "vis/did_papers_frames_1617_scatter.png")

```

---
# The treatment III

```{r treatment3, eval=TRUE, echo = F, out.width="70%", fig.pos="center"}

knitr::include_graphics(path = "vis/did_papers_allframes_all_hist.png")

```

---
# Estimation

Two studies:

- Study correlating changes in migration framing with readers' migration opinion in *survey data*.
  + Main advantage: direct measurement of dependent, individual level data.
  + Disadvantage: Self-reported newspaper exposure.
- DiD assessing impact of changing framing on *local-level proxies* like voting behaviour, protests and violence.
  + Main advantage: Proper causal identification (no limitation of survey data).
  + Disadvantage: Only aggregate-level measures.

---
class: inverse, center, middle

# First Results

---

# Individual-level study

Different specifications:

- DiD only for Bild shift, changing frame attention per newspaper.
- all readers/exclusive readers of one newspaper,
- different lags to measure exposure (1 day, 1 week, 1 month, half a year),
- immigration and integration attitude as dependent variable.

---
# 2-way fixed-effects model

$$y = \beta_1*ID + \beta_2*Wave + \beta_{f1}*ExposureFrame_1 + ... + \beta_{fi}*ExposureFrame_i$$

```{r effects_fe, eval=TRUE, echo = F, out.width="70%", fig.pos="center"}

knitr::include_graphics(path = "vis/frame_effects_fe.png")

```

---
# Difference-in-Difference correlation

$$y = \beta_1*W + \beta_2*R + \beta_3*W*R$$
```{r effects_did, eval=TRUE, echo = F, out.width="70%", fig.pos="center"}

knitr::include_graphics(path = "vis/frame_effects_did.png")

```

---
# simple DiD Bild shift

.left-column[

- Fun friday morning surprise!
- Effects in wrong direction.
- __Think about control group__

]

.right-column[

```{r simple_DiD, echo = F, message=F, fig.pos = 'center'}

library(dplyr)
library(ggplot2)
library(here)

did_ests <- read.csv(here('data/simple_did.csv'))

did_ests %>% 
  ggplot(aes(x = est,
             xmin = lower,
             xmax = upper,
             y = control)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = 'red', lty = 2) +
  facet_grid(period~dv) +
  xlab('Estimated change on 7-point scale')+
  ylab('Control group')+
  ggtitle('Estimated opinion change following Reichelt takeover', 'For different specifications')

```

]

---
class: inverse, center, middle

# Next steps

---
# Estimation on the local level

$$y_{dt} = \beta_1 * Bild_{d} + \beta_2 * Post_{t} + \beta_3 * Bild_{d} * Post_{t}$$

Potential anti-immigation attitude proxies:

- Voting behaviour
- Anti-immigrant/-refugee violence
- Protests
- Google Searches

---
# Open questions

- Framing
  + Get rid of emphasis framing? 
  + More focus on crime as right-wing issue?
  + More electoral behaviour focus?
- Appropriate control group?
- Matching? Instruments?
- Add 2015 framing shift as second case?

---
class: center, middle, inverse

# Thank you!

---

<!-- # News media framing -->

<!-- .left-column[ -->
<!-- ![via http://tabloid-watch.blogspot.com/2013/01/corrections-must-be-given-more.html](vis/130103mail.jpg) -->

<!-- ![via ](vis/bild_umgebracht_asyl.jpeg) -->

<!-- .right-column[ -->

<!-- ```{r bild_main_2, eval=TRUE, echo = F, out.width="70%", fig.pos="center"} -->

<!-- knitr::include_graphics(path = "vis/bild_auslaender.jpeg") -->

<!-- ``` -->

<!-- .footnote[via https://uebermedien.de/1184/die-bruellspirale/] -->

### 2022-06-28 pres/20220128/UNDA_20220128.Rmd
Update pres as well
pray

---
title: "Assessing media influence in contemporary news environments"
subtitle: "Right-wing media, crime, and anti-immigration attitudes"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
    includes:
      after_body: insert-logo.html
bibliography: PhD-Proposal.bib
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#03396d", background_color = "#bfbfbf",
  base_font_size = "25px",
  header_h1_font_size = "2rem",
  header_h2_font_size = "1.75rem",
  header_h3_font_size = "1.25rem",
  header_font_google = google_font("Montserrat", 'Thin 100'),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  footnote_font_size = "0.75rem"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, dev.args = list(bg = 'transparent') )
```

```{r bib, include=F, warning = F}
library(RefManageR)
BibOptions(check.entries = FALSE, bib.style = "authoryear", style = "text")
# file <- system.file("Bib", "PhD-Proposal.bib", package = "RefManageR")
bib <- ReadBib("PhD-Proposal.bib", check = F)

```

class: inverse, center, middle

# Puppet Masters, Ice Vendors or Entertainers?
### Assessing Media Influence in Contemporary News Environments

<br></br>

### Nicolai Berk<sup>*</sup>

Presentation at the Unanonymous Negroni Drinkers Association

`r Sys.Date()`

.left[.footnote[<sup>*</sup> Dynamics RTG & Humboldt Universität Berlin]]

---

class: middle, center, inverse

# Can a single media outlet still shape opinions in contemporary news environments?

---

# Conflicting theoretical views I

### Emphasis Framing

- Issue attitudes dependent on considerations in mind `r Cite(bib, "Druckman2001")`.
- These considerations can be altered by the the empasis of different frames in the news media `r Cite(bib, "Nelson1997")`.
- As a result, issue attitudes can be manipulated.

___

__Emphasis framing hypothesis__:

.center[*If a newspaper emphasises more positive/negative considerations of an issue, the readers’ attitude about the issue becomes more positive/negative*.]

---

# Conflicting theoretical views II

### Selective Exposure

- Modern news environments offer plenty of choice to consumers `r Cite(bib, c("Arceneaux2013", "Bennett2008"))`.
- Viewers seek out attitude-congruent news content `r Cite(bib, c("Iyengar2009", "Taber2006"))`.
- Hence they will change the news outlet if their preferred news outlet changes its slant.

___

__Opt-out hypothesis__: If a newspaper emphasises more positive/negative considerations of an issue, attitude-incongruent readers will stop consuming the newspaper.

---

# Conflicting theoretical views III

### Selective Exposure II

- However, unclear whether consumers seek out different articles or outlets `r Cite(bib, c("Lau2021", "Marquart2016", "Zillich2021"))`.

___

__Selective avoidance hypothesis__: If a newspaper emphasises more positive/negative considerations of an issue, attitude-incongruent readers will continue consuming the newspaper.

---

class: middle, center, inverse

# The Case

---

# Bild Chief Editor Julian Reichelt

- Germany 2015
- declining readership`
- insert quote on lost readership

<!-- [insert graph of declining readership] -->

<!-- [insert Reichelt picture, maybe Diekmann on the other side of the graph] -->

---

class: middle, center, inverse

# Data

---

# Measurement of News Framing

- BERT for selection of news content about migration
- STM for relative considerations - focus on crime content

---

# Migration Attitude and Readership

- GLES Panel Data preceding the German election 2017

[insert MIP graph]

---

class: middle, center, inverse

# Study Design

---

# Study I

Does a change in migration framing lead to changing migration attitudes?

1. Aggregate-level DiD design exploiting change in Bild migration framing.
2. Assessing all changes in migration framing in the major German dailys.
  1. Aggregate DiD-correlations of frame change and opinion change 
  2. Individual-level estimation of news diet and correlation with over-time opinion changes.

---

# Study 2

Does a change in migration framing lead to changes in readership composition?

Assessment of association of initial and current migration attitude with reported readership.

---

class: middle, center, inverse

# Results

---

# Treatment: Change in Bild Migration Framing

```{r treatment, fig.align='center', dev = 'svg', fig.height = 4, fig.width = 12}

library(here)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(lubridate)

## frames over time
load(here("data/media_daily_2021-11-19.Rdata"))

framing_sum <- 
  merged_media %>% 
  mutate(
    date = floor_date(as.Date(date_new), 'month')
  ) %>% 
  select(-date_new) %>% 
  group_by(paper, date) %>% 
  summarise_all(mean, na.rm = T) %>% 
  pivot_longer(cols = !c(date, paper, crime, n_tot, 
                         n_mig_fra, n_mig_sal, share_mig,
                         medit, deport, refnums, camps, 
                         labmar, capcrime), 
               names_to = 'frame', values_to = 'attention') %>% 
  mutate(paper = recode(paper, 
                        'bild' = 'Bild', 'faz' = 'FAZ', 'spon' = 'Spiegel',
                        'sz' = 'SZ', 'taz' = 'TAZ', 'welt' = 'Welt'
                        )) %>% 
  mutate(frame = recode(frame,
                        'camps_share' = 'Camps', 'crime_share' = 'Petty Crime',
                        'capcrime_share' = 'Capital Crime', 'deport_share' = 'Deportations',
                        'labmar_share' = 'Labour Market', 'medit_share' = 'Mediterranean',
                        'refnums_share' = 'Refugee Numbers'
                        ))
framing_sum$post <- framing_sum$date > as.Date("2017-02-01")

# effect of Diekmann leaving
framing_sum %>%
  filter(date < as.Date('2020-01-01')) %>%
  filter(paper %in% c("Bild", "Welt", "FAZ")) %>% 
  filter(frame %in% c("Camps", "Capital Crime", "Labour Market", "Petty Crime")) %>%
  group_by(paper, frame) %>% 
  ggplot(aes(x = date, y = attention, col = paper)) +
  geom_point(alpha = 0.3) +
  geom_smooth(aes(col = paper, lty = post)) +
  geom_vline(xintercept = as.Date('2017-01-31'), lty = 2, col = 'red') +
  facet_wrap(~frame, scales = "free_y") +
  xlab('')+
  theme_minimal()

```

---

# Study 1: Effects on Migration Attitudes - Case findings

![](vis/case_multiple_dvs.png)

---

# Study 1: Effects on Migration Attitudes - Overall findings

![](vis/frame_effects_did.png){height=50%}

---

class: inverse

### Finding:

- No association of migration framing and change in migration attitude!
- Instead change in media consumption in response to changes in issue framing?

---

# Study 2: Effects on readership

![](vis/reader_share_immatt.png){height=50%}

---

![](vis/imm_bildread_waves.png){height=50%}

---

class: inverse

### Finding:

- No association of migration framing and readership either.

---

class: middle, center, inverse

# Conclusion

---

# Conclusion

- No effects of substantial change in migration framing on issue attitudes.
- No association of changes in migration framing generally with changing issue attitudes.
- No association of sustantial change in migration framing with changing readership behaviour.

__$\rightarrow$ Limited influence of single outlets in diverse media markets!__

---

# Limitations

- Unclear how this translates from tabloids to broadsheets.
- Unclear if salience of migration issue contributed to fixed issue positions.

---

class: middle, center, inverse

# Negroni time!

![](Negroni.png)

---

# Resources

```{r biblio, echo=F, results='asis'}

PrintBibliography(bib)

```

### 2022-06-28 pres/20220217/Thomas_20220128.Rmd
Update pres as well
pray

---
title: "Assessing media influence in contemporary news environments"
subtitle: "Down the rabbit hole of conditioning on prior attitude"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
    includes:
      after_body: insert-logo.html
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#03396d", background_color = "#bfbfbf",
  base_font_size = "25px",
  header_h1_font_size = "2rem",
  header_h2_font_size = "1.75rem",
  header_h3_font_size = "1.25rem",
  header_font_google = google_font("Montserrat", 'Thin 100'),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  footnote_font_size = "0.75rem"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, dev.args = list(bg = 'transparent'), cache = T, out.width="100%", fig.height=6, fig.width=15)

library(tidyverse)
library(dplyr)
library(here)
library(data.table)
library(fixest)
library(lubridate)
library(patchwork)

# load data ####
merged_data <- fread(here('data/merged_2022-02-22.csv'))

# define modeling function

modeltable <- function(data, iv_name, dv_name = "1130_clean") {

  # if(!exists(iv)){stop("Independent not specified.")}

  modeldata <- 
    data %>% 
    mutate(dv = get(dv_name), iv = get(iv_name)) %>% 
    arrange(lfdn, date_clean.x) %>% 
    group_by(lfdn) %>% 
    mutate(dv_lag = lag(dv))

  m_naive <- lm(dv ~ iv, data = modeldata)
  m_dvlag <- lm(dv ~ iv + lfdn, data = modeldata)
  m_wavef <- feglm(dv ~ iv + lfdn | wave, data = modeldata, cluster = c("lfdn", "wave"))
  m_inter <- feglm(dv ~ iv * imm_att | wave, data = modeldata, cluster = c("lfdn", "wave"))

  estimate_table <- 
    data.frame(
      estimate = c("Frame exposure", "CI", "individual FEs", "wave FEs", "Frame X moderate", "CI", "Frame X liberal", "CI"),
      naive    = c(round(m_naive$coefficients[["iv"]], 3), 
                   paste0("[", round(confint(m_naive)["iv",][[1]], 3), ";", 
                          round(confint(m_naive)["iv",][[2]], 3), "]"),
                   "No", "No", "-", "-", "-", "-"),
      lagged   = c(round(m_dvlag$coefficients[["iv"]], 3),
                   paste0("[", round(confint(m_dvlag)["iv",][[1]], 3), ";", 
                          round(confint(m_dvlag)["iv",][[2]], 3), "]"), 
                   "Yes", "No", "-", "-", "-", "-"),
      wavefe   = c(round(m_wavef$coefficients[["iv"]], 3), 
                   paste0("[", round(confint(m_wavef)["iv",][[1]], 3), ";", 
                          round(confint(m_wavef)["iv",][[2]], 3), "]"), 
                   "Yes", "Yes", "-", "-", "-", "-"),
      inter    = c(round(m_inter$coefficients[["iv"]], 3), 
                   paste0("[", round(confint(m_inter)["iv",][[1]], 3), ";", 
                          round(confint(m_inter)["iv",][[2]], 3), "]"),  
                   "No", "Yes", 
                   round(m_inter$coefficients[["iv:imm_attmoderate"]], 3),
                   paste0("[", round(confint(m_inter)["iv:imm_attmoderate",][[1]], 3), ";", 
                          round(confint(m_inter)["iv:imm_attmoderate",][[2]], 3), "]"), 
                   round(m_inter$coefficients[["iv:imm_attliberal"]], 3), 
                   paste0("[", round(confint(m_inter)["iv:imm_attliberal",][[1]], 3), ";", 
                          round(confint(m_inter)["iv:imm_attliberal",][[2]], 3), "]"))
    )

  return(estimate_table)

}

```

```{r bib, include=F, warning = F}
# library(RefManageR)
# BibOptions(check.entries = FALSE, bib.style = "authoryear", style = "text")
# file <- system.file("Bib", "PhD-Proposal.bib", package = "RefManageR")
# bib <- ReadBib("PhD-Proposal.bib", check = F)

```

class: inverse, center, middle

## Does framing matter for news consumption?

---

## Reichelt takeover

More Crime framing of migration in Bild

```{r case_crime}

## define survey dates
gles_p_long <- 
  fread(here('data/gles/Panel/long_cleaned.csv'))

survey_dates <- 
  gles_p_long %>% 
  filter(!is.na(date_clean)) %>% 
  filter(!is.na('1130_clean') & !is.na('1661a_clean')) %>%  
  filter(date_clean < as.Date("2018-01-01")) %>% 
  group_by(wave) %>% 
  summarise(date = max(date_clean)) %>% 
  ungroup() %>% 
  select(date)

## load & transform data frame attention
load(here("data/media_daily_2022-02-02.Rdata"))

merged_media <- 
  merged_media %>% 
  mutate(paper = recode(paper, 
                        'bild' = 'Bild', 'faz' = 'FAZ', 'spon' = 'Spiegel',
                        'sz' = 'SZ', 'taz' = 'TAZ', 'welt' = 'Welt'),
         post = date_new > as.Date("2017-02-01"),
         date_month = floor_date(as.Date(date_new), 'month'))

## visualise
trendplot <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"), date_new >= as.Date("2016-01-01")) %>% 
  mutate(
    date_month = floor_date(as.Date(date_new), 'month')
  ) %>%
  group_by(paper != "Bild", date_month) %>%
  summarise(across(share_mig:hungary_referendum_share, mean, na.rm = T),
            across(n_mig_sal:n_tot, sum, na.rm = T)) %>%
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         post = date_month >= as.Date("2017-02-01")) %>% 
  filter(date_month < as.Date("2020-01-01")) %>% 
  ggplot(aes(x = date_month, y = crime_share, col = `paper != "Bild"`)) +
  geom_line() +
  geom_rug(data = survey_dates, aes(x = date),sides = 't', inherit.aes = F) +
  # geom_point() +
  # geom_smooth(alpha = 0.1) +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") +
  ggtitle("Monthly Share of Migration Content Devoted to Crime Frames", "Bild vs. other major daily newspapers, 2016-2017") + 
  xlab("Date") + ylab("Share of Migration Content") +
  # facet_wrap(~paper)
  theme_minimal() +
  theme(legend.position = "none")

# DiD with placebo papers, 2016-17
merged_media <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"),
         date_new >= "2016-01-01")

treatment_ests <- 
  data.frame()

merged_media$dv    <-  merged_media[["crime_schlepp_share"]] + merged_media[["sexual_assault_share"]] + merged_media[["bild_footer_share"]]
merged_media$post  <-  merged_media$date_new >= as.Date("2017-02-01")

for (p in unique(merged_media$paper)){

  merged_media$treatment <-  merged_media$paper == p

  did_model <- lm(dv ~ post*treatment, data = merged_media)

  est <- did_model$coefficients["postTRUE:treatmentTRUE"][[1]]
  lower <- confint(did_model)["postTRUE:treatmentTRUE", 1]
  upper <- confint(did_model)["postTRUE:treatmentTRUE", 2]

  treatment_ests <- 
    rbind(treatment_ests,
          data.frame(
            model = "DiD",
            paper = p,
            est   = est,
            lower = lower,
            upper = upper
          ))
}

## vis
treatment_ests$paper <- 
  factor(treatment_ests$paper,
          levels = treatment_ests %>%
                    filter(model == "DiD") %>% 
                    arrange(est) %>% 
                    select(paper) %>%
                    unlist()
    )

placebo_papers <- 
  treatment_ests %>% 
  ggplot(aes(x = est, xmin = lower, xmax = upper, 
             y = paper, col = paper != "Bild")) +
  geom_pointrange() +
  geom_vline(xintercept = 0,
             col = "red", lty = 2) +
  theme_minimal() +
  xlab("Estimated DiD") + ylab("") +
  # ggtitle("Papers' Change in Crime Framing (DiD), 2016-2017") +
  theme(legend.position = "None") +
  coord_flip()

trendplot + placebo_papers

```

---

## Case estimate

```{r did_case}

## load estimates
gles_p_long_nona <- fread(file = here('data/gles/Panel/long_cleaned_nona.csv'))

## define post-period
gles_p_long_nona$post <- 
  gles_p_long_nona$date_clean >= as.Date("2017-02-01")

## define treatment: read Bild or not
gles_p_long_nona$treat <- 
  gles_p_long_nona$`1661a_bin` == T

# estimation function ####

did_table <- function(data, dv_name = "1130_clean") {

  ## define dv
  data$dv <- data[[dv_name]]

  data <- 
    data %>% 
    filter(!is.na(dv), !is.na(treat), !is.na(post), !is.na(imm_att))

  m_naive <- feglm(dv ~ treat*post | lfdn, cluster = c("lfdn", "wave"), data = data)
  m_cntrl <- feglm(dv ~ treat*post + imm_att, cluster = c("lfdn", "wave"), data = data)
  m_inter <- feglm(dv ~ treat*post*imm_att, cluster = c("lfdn", "wave"), data = data) # slightly significant difference of liberals
  # m_inter_fe <- feglm(dv ~ treat*post*imm_att, cluster = c("lfdn", "wave"), data = data) # slightly
  #

  estimate_table <- 
      data.frame(
        estimate = c("DiD", "CI", "initial opinion", "individual FEs", "clustered SEs", "DiD X moderate", "CI", "DiD X liberal", "CI"),
        fe    = c(round(m_naive$coefficients[["treatTRUE:postTRUE"]], 3), 
                     paste0("[", round(confint(m_naive)["treatTRUE:postTRUE",][[1]], 3), ";", 
                            round(confint(m_naive)["treatTRUE:postTRUE",][[2]], 3), "]"),
                     "No", "Yes", "Yes", "-", "-", "-", "-"),
        cntrl    = c(round(m_cntrl$coefficients[["treatTRUE:postTRUE"]], 3), 
                     paste0("[", round(confint(m_cntrl)["treatTRUE:postTRUE",][[1]], 3), ";", 
                            round(confint(m_cntrl)["treatTRUE:postTRUE",][[2]], 3), "]"),
                     "Yes", "No", "Yes", "-", "-", "-", "-"),
        inter    = c(round(m_inter$coefficients[["treatTRUE:postTRUE"]], 3), 
                     paste0("[", round(confint(m_inter)["treatTRUE:postTRUE",][[1]], 3), ";", 
                            round(confint(m_inter)["treatTRUE:postTRUE",][[2]], 3), "]"),  
                     "Yes", "No", "Yes", 
                     round(m_inter$coefficients[["treatTRUE:postTRUE:imm_attmoderate"]], 3),
                     paste0("[", round(confint(m_inter)["treatTRUE:postTRUE:imm_attmoderate",][[1]], 3), ";", 
                            round(confint(m_inter)["treatTRUE:postTRUE:imm_attmoderate",][[2]], 3), "]"), 
                     round(m_inter$coefficients[["treatTRUE:postTRUE:imm_attliberal"]], 3), 
                     paste0("[", round(confint(m_inter)["treatTRUE:postTRUE:imm_attliberal",][[1]], 3), ";", 
                            round(confint(m_inter)["treatTRUE:postTRUE:imm_attliberal",][[2]], 3), "]"))
        # inter_fe    = c(round(m_inter$coefficients[["treatTRUE:postTRUE"]], 3), 
        #              paste0("[", round(confint(m_inter)["treatTRUE:postTRUE",][[1]], 3), ";", 
        #                     round(confint(m_inter)["treatTRUE:postTRUE",][[2]], 3), "]"),  
        #              "No", "Yes", 
        #              round(m_inter_fe$coefficients[["treatTRUE:postTRUE:imm_attmoderate"]], 3),
        #              paste0("[", round(confint(m_inter_fe)["treatTRUE:postTRUE:imm_attmoderate",][[1]], 3), ";", 
        #                     round(confint(m_inter_fe)["treatTRUE:postTRUE:imm_attmoderate",][[2]], 3), "]"), 
        #              round(m_inter_fe$coefficients[["treatTRUE:postTRUE:imm_attliberal"]], 3), 
        #              paste0("[", round(confint(m_inter_fe)["treatTRUE:postTRUE:imm_attliberal",][[1]], 3), ";", 
        #                     round(confint(m_inter_fe)["treatTRUE:postTRUE:imm_attliberal",][[2]], 3), "]"))
      )

  return(estimate_table)
}

did_all <- did_table(gles_p_long_nona)

knitr::kable(did_all)

```

### No direct effect, but liberals become more conservative
But could this just be regression to the mean? (And why is the direct effect negative?)

---

## Compared to readers of other conservative outlets

```{r did_case_cons}

# restrict to conservative NP readers
gles_cons <- 
  gles_p_long_nona %>% 
  filter(`1661a_bin` | `1661c_bin` | `1661f_bin`)

did_cons <- did_table(gles_cons)

knitr::kable(did_cons)

rm(gles_p_long_nona, gles_cons)

```

### Liberal effect persists on top of positive effect for conservative bild readers.

---

## What about AfD support?

```{r}

gles_p_long$afd_vote <- gles_p_long$`190b_clean` == "AfD"
## define post-period
gles_p_long$post <- 
  gles_p_long$date_clean >= as.Date("2017-02-01")

## define treatment: read Bild or not
gles_p_long$treat <- 
  gles_p_long$`1661a_bin` == T

knitr::kable(did_table(gles_p_long, dv = "afd_vote"))

```

### Unaffected, if anything, negative.

---

## AfD scalometer

```{r}
knitr::kable(did_table(gles_p_long, dv = "430i_clean"))

```
Seems to *decrease*, at least among liberal and moderate bild readers! But unclear if liberal decrease significantly different from zero.

---

## Takeaways

- Predisposition matters (Zaller, Lazarsfeld)
- But does this generalise beyond this case?

---

class: center, inverse, middle

# Individual estimation of news diet

---

## Individual models

- Estimate individual frame exposure based on news diet
- allows to correlate opinions and migration framing in read newspapers directly

---

## Individual models: Crime

```{r crime_effs}

# IMPORTANT: all non-readers kicked out here! #

# define treatment
merged_data <- 
  merged_data %>% 
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         imm_att = factor(imm_att, levels = c("conservative", "moderate", "liberal", "")))

merged_data$n_articles[is.na(merged_data$n_articles)] <- 0

# select 7d lag
merged_data_7d <- 
  merged_data %>% 
  filter(lag == "7") %>% 
  filter(imm_att != "")

rm(merged_data)

crime_effects <- modeltable(merged_data_7d, "crime_share")

knitr::kable(crime_effects)

```

---

## Individual models: Crime II

```{r crime_vis}

merged_data_7d %>% 
  ggplot(aes(crime_share, `1130_clean`)) +
  geom_density_2d_filled() +
  geom_smooth(method = "lm") +
  facet_grid(~imm_att) +
  theme_minimal()

```

## Can this be explained by differences in values?

### The country must be safe

```{r}

merged_data_7d$dv <- merged_data_7d$`1130_clean`
merged_data_7d$iv <- merged_data_7d$crime_schlepp_share
merged_data_7d$security <- as.factor(merged_data_7d$`3320m_clean`)
modeldata <- 
  merged_data_7d %>% 
  filter(!is.na(dv), !is.na(iv), !is.na(security)) %>% 
  select(dv, iv , wave, security, lfdn)

feglm(dv ~ iv * security | wave, data = modeldata, cluster = c("lfdn", "wave"))

```

---

## Individual Model: Crime on AfD support

```{r}
crime_effects_afd <- modeltable(merged_data_7d, "crime_share", dv_name = "430i_clean")

knitr::kable(crime_effects_afd)
```

Positive direct effect, gets weird with interaction (might als not make that much sense to interact)

---

```{r}
merged_data_7d %>% 
  ggplot(aes(crime_share, `430i_clean`)) +
  geom_density_2d_filled() +
  geom_smooth(method = "lm") +
  facet_grid(~imm_att) +
  theme_minimal()
```

## Crime effect on AfD-vote

```{r}
merged_data_7d$afd_vote <- merged_data_7d$`190b_clean` == "AfD"

crime_effects_afd <- modeltable(merged_data_7d, "crime_share", dv_name = "afd_vote")

knitr::kable(crime_effects_afd)
```

No significant effects on AfD support

---

## Does crime effect on attitude persist when controlling for changing issue definitions?

```{r issdef}

merged_data_7d$dv <- merged_data_7d$`1130_clean`
merged_data_7d$crime_def <- 
  (merged_data_7d$`840_c1` == "3411") |
  (merged_data_7d$`840_c2` == "3411") |
  (merged_data_7d$`840_c3` == "3411") |
  (merged_data_7d$`840_c4` == "3411") |
  (merged_data_7d$`840_c5` == "3411")

feglm(dv ~ crime_share*imm_att | wave, cluster = c("lfdn", "wave"), data = merged_data_7d)
feglm(dv ~ crime_share*imm_att + crime_def | wave, cluster = c("lfdn", "wave"), data = merged_data_7d)

```

### Yes.

---

## Individual models: Camps

```{r camp_effs}

# IMPORTANT: all non-readers kicked out here! #

merged_data_7d <- 
  merged_data_7d %>% 
  mutate(camps_share = camps_greece_share + ME_camps_share)

camps_effects <- modeltable(merged_data_7d, "camps_share")

knitr::kable(camps_effects)

```

---

## Individual Models: Camps II

```{r camp_vis}

merged_data_7d %>% 
  ggplot(aes(camps_share, `1130_clean`)) +
  geom_density_2d_filled() +
  geom_smooth(method = "lm") +
  facet_grid(~imm_att)

```

---

## Individual Models: Mediterranean

```{r med_effs}

# IMPORTANT: all non-readers kicked out here! #

merged_data_7d <- 
  merged_data_7d %>% 
  mutate(medit_share = mediterranean_share+ sr_medit_share)

medit_effects <- modeltable(merged_data_7d, "medit_share")

knitr::kable(medit_effects)

```

---

## Individual Models: Refugee numbers

```{r nums_effs}

# IMPORTANT: all non-readers kicked out here! #
nums_effects <- modeltable(merged_data_7d, "refugee_nums_share")

knitr::kable(nums_effects)

```

---

## Salience

Effect of salience not uniform $\rightarrow$ polarising!

```{r salience}

sal_effects <- modeltable(merged_data_7d, "n_articles")

knitr::kable(sal_effects)

```

---

## Crime frame $\rightarrow$ issue definitions

### Tiny positive effect on mentioning migrant crime as most important topic

```{r mip_migrant_crime}

merged_data_7d <- 
  merged_data_7d %>% 
  mutate(dv = `840_c1` == "3411",
         dv_lag = lag(dv),
         ctrl = `840_c1` %in% c(3412:3413, 3750:3759),
         ctrl_lag = lag(ctrl))

model <- feglm(dv ~ crime_schlepp_share + dv_lag | wave, data = merged_data_7d)

knitr::kable(model$coeftable)

```

### ...but stronger effect on other migration topics

```{r mig_oth}

model <- feglm(ctrl ~ crime_schlepp_share + ctrl_lag | wave, data = merged_data_7d %>% filter(imm_att != "")) # stronger positive effect

knitr::kable(model$coeftable)

cor_sal_att <- cor(merged_data_7d$`1140_clean`, merged_data_7d$`1130_clean`, use = "pairwise.complete.obs")

```

---

## Take-Away

- Each frame uniquely shapes public opinion.
- Effect is dependent on existing attitude.
- __Content__ is crucial, salience alone does not explain shifts!
- Public opinion is still a "product of information and predisposition" (Zaller 1992)

## Next steps

- add hypothesis 1b) (interaction with predispositions)
- add analysis of reaction to contrasting frames $\rightarrow$ higher likelihood to stop reading? (sufficient with only crime frame?)
- Frame exposure might affect issue definitions - another paper?

## Addendum: Interaction model with salience

- Correlation of saleince and position on migration: `r cor_sal_att`.
- Quadratic relationship: those with extreme attitudes care about the issue!

```{r sal_att_plot}

merged_data_7d %>% 
  filter(!is.na(`1130_clean`) & !is.na(`1140_clean`)) %>% 
  ggplot(aes(x = `1140_clean`, y = `1130_clean`)) +
  geom_violin(aes(x = as.factor(`1140_clean`))) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2))

```

```{r sal_inter_1}

merged_data_7d <- 
  merged_data_7d %>% 
  mutate(dv = `1130_clean`,
         dv_lag = lag(dv))

# interaction with issue salience
feglm(dv ~ crime_schlepp_share*`1140_clean` | wave, data = merged_data_7d, cluster = c("lfdn", "wave")) # no interaction effect of salience

```

```{r sal_inter_2}

# interaction with issue salience
feglm(dv ~ crime_schlepp_share*`1140_clean` + dv_lag | wave, data = merged_data_7d, cluster = c("lfdn", "wave")) # no interaction effect of salience

```

---

```{r sal_inter_3}

# interaction with issue salience
feglm(dv ~ crime_schlepp_share*as.factor(`1140_clean`) + dv_lag | wave, data = merged_data_7d, cluster = c("lfdn", "wave")) # no interaction effect of salience

cor_lr_att <- cor(merged_data_7d$`1500_clean`, merged_data_7d$`1130_clean`, use = "pairwise.complete.obs")

```

### $\rightarrow$ Interaction of past attitude change not explained by issue attitudes!

---

## Are those with liberal migration attitudes more responsive?

Correlation of general left-right self-placement with migration attitude `r cor_lr_att`.

```{r lr}

feglm(dv ~ crime_schlepp_share*`1500_clean` + dv_lag | wave, data = merged_data_7d, cluster = c("lfdn", "wave")) # no interaction effect of general l-r

```
## Nope.

---

## Are those with liberal migration attitudes more reactive to all frames?

```{r frame_effects, fig.height = 10}

est_ov <- data.frame()

for (treat in merged_data_7d %>% select(n_articles:hungary_referendum_share, -essener_tafel_share) %>% colnames()){
  merged_data_7d$treatment <- merged_data_7d[, get(treat)]
  ests <- feglm(dv ~ treatment*imm_att | wave, data = merged_data_7d, cluster = c("lfdn", "wave"))

  data.frame(
    treatment   = treat,
    treat_est   = ests$coefficients[["treatment"]],
    treat_lower = confint(ests)["treatment",][[1]],
    treat_upper = confint(ests)["treatment",][[2]],
    iamod_est   = ests$coefficients[["treatment:imm_attmoderate"]],
    iamod_lower = confint(ests)["treatment:imm_attmoderate",][[1]],
    iamod_upper = confint(ests)["treatment:imm_attmoderate",][[2]],
    ialib_est   = ests$coefficients[["treatment:imm_attliberal"]],
    ialib_lower = confint(ests)["treatment:imm_attliberal",][[1]],
    ialib_upper = confint(ests)["treatment:imm_attliberal",][[2]]
  ) %>% 
  rbind(est_ov, .) -> est_ov

}

est_ov %>% 
  pivot_longer(cols = treat_est:ialib_upper, names_to = c("estimate", ".value"), names_pattern = "(.*)_(.*)") %>% 
  ggplot(aes(x = est, xmin = lower, xmax = upper, y = estimate, col = estimate == "treat")) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  facet_wrap(~treatment, scales = "free_x")

```

### No. Frame content matters.

---

## Table of frame effects

```{r}

ov_table <- 
  data.frame(
    c("Asylstreit           ", "None"),
    c("Asylum Law           ", "- All"),
    c("Asylum Reform        ", "- All"),
    c("Australia            ", "- All"),
    c("Balcan               ", "None"),
    c("BAMF                 ", "None"),
    c("Bild Footer          ", "+ Libs"),
    c("Boat full            ", "- All"),
    c("Calais               ", "- Libs"),
    c("Camps Greece         ", "(- Libs)"),
    c("Carneval             ", "None"),
    c("Children             ", "None"),
    c("Church               ", "- All"),
    c("Crime Schlepp        ", "+ Liberals"),
    c("CSU Poverty          ", "POLARISATION"),
    c("Cultural Integration ", "None"),
    c("Deportations         ", "None"),
    c("Economy              ", "(+ Liberals)"),
    c("English              ", "None"),
    c("Episodic             ", "None"),
    c("EU Asylum            ", "- All"),
    c("EU Borders           ", "(- Libs)"),
    c("Families Episodic    ", "(+ Liberals)"),
    c("Finance Bonds        ", "+ All"),
    c("Great Coalition      ", "None"),
    c("Hamburg              ", "- Libs"),
    c("History              ", "- Libs"),
    c("Hungary Referendum   ", "- Libs"),
    c("International Distr. ", "- All"),
    c("Islamic State        ", "Polarisation"),
    c("Interviews Morals    ", "None"),
    c("Jobmarket Integration", "Polarisation"),
    c("Länder               ", "- All"),
    c("Lageso               ", "- Libs"),
    c("Legal Integration    ", "- All"),
    c("Local Distribution   ", "Polarisation/+Cons"),
    c("MENA Camps           ", "None"),
    c("Mexico               ", "None"),
    c("Salience             ", "Polarisation/+Cons"),
    c("NY Stocks            ", "+ All"),
    c("Party Politics       ", "- All"),
    c("Politicians EU       ", "None"),
    c("Polls                ", "None"),
    c("Pop. Statistics      ", "None"),
    c("Refugee cost         ", "None"),
    c("Refugee numbers      ", "None"),
    c("Refugees Berlin      ", "(- Libs)"),
    c("RR protests          ", "None"),
    c("RW Intellectuals     ", "- All"),
    c("Sexual Assault       ", "None"),
    c("Spiegel              ", "- All"),
    c("SR Mediterranean     ", "- All"),
    c("Stocks Asia          ", "+ All"),
    c("Stocks CEE           ", "+ All"),
    c("Stock DAX            ", "+ All"),
    c("Swiss Initiative     ", "None"),
    c("Trump                ", "- All"),
    c("UN Migration Pact    ", "None"),
    c("War Syria            ", "- All/(- Cons)")
  ) %>% t() %>% 
  as.tibble() %>% 
  filter(V2 != "None") %>% 
  arrange(V2)

knitr::kable(ov_table)

```

---

### 2022-06-28 pres/20220225-MethodIssues/HowDoIEstimateThat.Rmd
Update pres as well
pray

---
title: "How do I estimate that?"
subtitle: "The perils of panel data"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
    includes:
      after_body: insert-logo.html
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#03396d", background_color = "#bfbfbf",
  base_font_size = "35px",
  header_h1_font_size = "1.5rem",
  header_h2_font_size = "1.25rem",
  header_h3_font_size = "1.1rem",
  header_font_google = google_font("Montserrat", 'Thin 100'),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  footnote_font_size = "0.75rem"
)

```

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, cache = T, out.width="75%", fig.height=4, fig.width=10, fig.align='center', eval = T)
knitr::opts_knit$set(root.dir = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild')

library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)
library(lubridate)

```

class: inverse, center, middle

# Interactions in panel data and other shenanigans

### Nicolai Berk<sup>*</sup>

Presentation prepared for Will Lowe's Research Design course at Hertie School

`r Sys.Date()`

.left[.footnote[<sup>*</sup> Dynamics RTG & Humboldt Universität Berlin]]

---

class: inverse, middle, center

## The research question

### How do issue definitions in the media affect individual attitudes?

---

## The model

```{r fig.height=5, fig.width=8}
library(dagitty)
dag <- dagitty("dag {
  Information -> Consideration -> Attitude
               }", layout = T)
plot( graphLayout( dag ) )

```

---

## Starting point: Fixed-effect model

$$y_{it} = I_{it} + c_i + c_w + \epsilon_{it}$$

- $y_{it}$ $:=$ attitude of individual $i$ at time $t$
- $I_{it}$ $:=$ Information consumed by individual $i$ at time $t$
- $c_{i}$ $:=$ individual fixed effect (i.e. average individual opinion across time)
- $c_{w}$ $:=$ wave fixed effect (i.e. average opinion across individuals)

---

## However.... (Problem I)

### Zaller: effects of information dependent on

- **individual core values**
  + Depend which considerations are formed in response to information
  + e.g. perceiving a homeless person: bum or unlucky?
- **individual attentiveness to politics**
  + increases receptiveness
  + but also ability to relate information to own values

---

## Modeling

- for direct effect: could just use 2-way FEs (or could I?)
- However, values and attentiveness are (considered to be) **stable across time**
- Hence, including them in the model seems to make FEs rather superfluous

... right?

---

## Candidate I

.left-column[

```{r out.width="100%", fig.height=5, fig.width= 3, fig.align='right'}
library(dagitty)
dag <- dagitty("dag {
  Information -> Attitude
  Information <-  Confounder -> Attitude

               }", layout = T)
plot( graphLayout( dag ) )

```

]

.right-column[

### No individual FEs<sup>1</sup>:

$$y_{it} = I_{it} * V_{i} * A_{i} + c_w + \epsilon_{it}$$

>- Issue: not controlling for time-constant individual differences

.footnote[<sup>1</sup>: Imagine constitutive terms.]

]

---

## Candidate II

### Lagged DV:

$$y_{it} = I_{it} * V_{i} * A_{i} + y_{i, t-1} + c_w + \epsilon_{it}$$

>- Issue: post-treatment bias when it comes to values? (values correlate with dv)

---

## Can PTB be an issue here?

.center[There should be a figure here.]

---

## Candidate III

### With FEs:

$$y_{it} = I_{it} * V_{i} * A_{i} + c_{i} + \epsilon_{it}$$

>- Issue: Collinearity

___

$\rightarrow$ Currently leaning towards first version (no FEs).

---

class: center, middle, inverse

## Suggestions? Hot takes? Emotions?

---

## Problem II: No real control in individual model

### DiD: no problem

```{r case_crimev}

## define survey dates

gles_p_long <- 
  fread('data/gles/Panel/long_cleaned.csv')

survey_dates <- 
  gles_p_long %>% 
  filter(!is.na(date_clean)) %>% 
  filter(!is.na('1130_clean') & !is.na('1661a_clean')) %>%  
  filter(date_clean < as.Date("2018-01-01")) %>% 
  group_by(wave) %>% 
  summarise(date = max(date_clean)) %>% 
  ungroup() %>% 
  select(date)

rm(gles_p_long)

## load & transform data frame attention
load("data/media_daily_2022-02-02.Rdata")

merged_media <- 
  merged_media %>% 
  mutate(paper = recode(paper, 
                        'bild' = 'Bild', 'faz' = 'FAZ', 'spon' = 'Spiegel',
                        'sz' = 'SZ', 'taz' = 'TAZ', 'welt' = 'Welt'),
         post = date_new > as.Date("2017-02-01"),
         date_month = floor_date(as.Date(date_new), 'month'))

## visualise
trendplot <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"), date_new >= as.Date("2016-01-01")) %>% 
  mutate(
    date_month = floor_date(as.Date(date_new), 'month')
  ) %>%
  group_by(paper != "Bild", date_month) %>%
  summarise(across(share_mig:hungary_referendum_share, mean, na.rm = T),
            across(n_mig_sal:n_tot, sum, na.rm = T)) %>%
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         post = date_month >= as.Date("2017-02-01")) %>% 
  filter(date_month < as.Date("2020-01-01")) %>% 
  ggplot(aes(x = date_month, y = crime_share, col = `paper != "Bild"`)) +
  geom_line() +
  geom_rug(data = survey_dates, aes(x = date),sides = 't', inherit.aes = F) +
  # geom_point() +
  # geom_smooth(alpha = 0.1) +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") +
  ggtitle("Monthly Share of Migration Content Devoted to Crime Frames", "Bild vs. other major daily newspapers, 2016-2017") + 
  xlab("Date") + ylab("Share of Migration Content") +
  # facet_wrap(~paper)
  theme_minimal() +
  theme(legend.position = "none")

# DiD with placebo papers, 2016-17
merged_media <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"),
         date_new >= "2016-01-01")

treatment_ests <- 
  data.frame()

merged_media$dv    <-  merged_media[["crime_schlepp_share"]] + merged_media[["sexual_assault_share"]] + merged_media[["bild_footer_share"]]
merged_media$post  <-  merged_media$date_new >= as.Date("2017-02-01")

for (p in unique(merged_media$paper)){

  merged_media$treatment <-  merged_media$paper == p

  did_model <- lm(dv ~ post*treatment, data = merged_media)

  est <- did_model$coefficients["postTRUE:treatmentTRUE"][[1]]
  lower <- confint(did_model)["postTRUE:treatmentTRUE", 1]
  upper <- confint(did_model)["postTRUE:treatmentTRUE", 2]

  treatment_ests <- 
    rbind(treatment_ests,
          data.frame(
            model = "DiD",
            paper = p,
            est   = est,
            lower = lower,
            upper = upper
          ))
}

## vis
treatment_ests$paper <- 
  factor(treatment_ests$paper,
          levels = treatment_ests %>%
                    filter(model == "DiD") %>% 
                    arrange(est) %>% 
                    select(paper) %>%
                    unlist()
    )

placebo_papers <- 
  treatment_ests %>% 
  ggplot(aes(x = est, xmin = lower, xmax = upper, 
             y = paper, col = paper != "Bild")) +
  geom_pointrange() +
  geom_vline(xintercept = 0,
             col = "red", lty = 2) +
  theme_minimal() +
  xlab("Estimated DiD") + ylab("") +
  # ggtitle("Papers' Change in Crime Framing (DiD), 2016-2017") +
  theme(legend.position = "None") +
  coord_flip()

gridExtra::grid.arrange(trendplot, placebo_papers, nrow = 1)

rm(merged_media)

```

---

### Individual estimates: problem?

```{r}

# load data ####
merged_data <- 
  fread('data/merged_2022-02-22.csv') %>% 
  mutate(crime_share = crime_schlepp_share + sexual_assault_share)

merged_data %>% 
  filter(!is.na(crime_share)) %>% 
  ggplot(aes(x = crime_share)) +
  geom_histogram(fill = "lightblue", alpha = 0.7) +
  ggtitle("Individual exposure to crime frame") +
  xlab("Share of crime news out of all news on migration") + ylab("Count")+
  theme_minimal() 
  # facet_wrap(~wave)

```

---

## Potential solutions?

- Create bins for different levels of exposure?
- Actually not a problem to estimate 2-way FE model? (but *reverse causality*?)
- something else?

---

class: center, middle, inverse

## Suggestions? Hot takes? Emotions?

---

## Mo' problems

- DiD standard errors: all solved with bootstrap?
- do 2-way FEs account for switching in DiD groups?
- standard error clustering
- test for endogeneity

---

class: center, middle, inverse

## Like and subscribe for more research riddled with problems

### 2022-06-28 pres/20220225-MethodIssues/MemoWill.Rmd
Update pres as well
pray

---
title: "Questions Concerning Model Choice when Facing Collinearity"
author: "Nicolai Berk"
date: "4 3 2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r data, include=FALSE}

# Setup ####
library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)

# run other scripts (only once)

# source(here("code/01a_preprocessing_dv.R")) # clean survey data
# rm(list = ls())
# source(here("code/03a_merge.R")) # merge to text estimates
# rm(list = ls())

# load ####
merged_data <- fread(file = "C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/merged_2022-03-03.csv")

merged_data <- 
  merged_data %>% 
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         # imm_att = factor(imm_att, levels = c("conservative", "moderate", "liberal", "miss")),
         dv = `1130_clean`) %>% 
  filter(lag == 7)

merged_data <- 
  merged_data %>% 
  filter(!is.na(`1130_clean`)) %>% 
  group_by(lfdn) %>% 
  arrange(lfdn, date_clean.x) %>% 
  select(`1130_clean`, lfdn) %>% 
  slice(1) %>% 
  mutate(init_mig = `1130_clean`) %>%
  select(init_mig, lfdn) %>% 
  right_join(merged_data, by = "lfdn")

# add lagged crime_share and dv
merged_data <- 
  merged_data %>%
  ungroup() %>% 
  arrange(lfdn, date_clean.x) %>% 
  group_by(lfdn) %>% 
  filter(!is.na(crime_share)) %>% 
  mutate(crime_share_lag = lag(crime_share),
         dv_lag = lag(dv))

```

Dear Will,

apologies for annoying you with this, but I am increasingly confused by the estimates of models I tried to present in last week's course.

The basic problem I am interested in is whether news exposure affects issue attitudes. More specifically, I am interested in whether increased emphasis of crime in immigration news changes migration attitudes, and whether this effect is conditioned by past attitude on the issue (I described this as values in class, but I believe the prior issue stance is a more appropriate measure of the concept I am trying to capture). I believe the model for the direct effect would look something like this:

$$ y_{it} = \alpha + \beta_1*CrimeExposure_{it} + \rho_i + \phi_t + \epsilon_{it}  $$

With $y_{it}$ being the immigration attitude of individual $i$ at time $t$, $CrimeExposure_{it}$ symbolising the estimated exposure of individual $i$ to crime news in immigration coverage in the week preceding the interview at time $t$, and $\rho_i$ & $\phi_t$ describing individual fixed effects.

The above mentioned model returns a weak positive correlation of crime exposure and migration attitude that might well arise by chance:

```{r rawmodel_2fe}

summary(feglm(dv ~ crime_share | wave + lfdn,
      cluster = c("lfdn"), data = merged_data))

```

Now what about the conditioning effect of past migration opinions? First, I tried the model discussed in class:

$$ y_{it} = \alpha + \beta_1*CrimeExposure_{it} + \beta_2*PastOpinion + \beta_3*CrimeExposure*PastOpinion + \rho_i + \phi_t + \epsilon_{it}  $$
Using the initial migration attitude of a respondent as conditioning variable creates collinearity issues:

```{r int_1}

summary(feglm(dv ~ crime_share*init_mig | wave + lfdn,
      cluster = c("lfdn"), data = merged_data))

```

We find a significant decrease with more restrictive (higher) migration attitudes, but the direct effect of initial migration attitudes isn't taken into account. I wouldn't consider this a huge problem, as the individual fixed effects should take care of this, but I am cautious so I try different models.

```{r int_1b}

summary(feglm(dv ~ crime_share*init_mig | wave,
      cluster = c("lfdn"), data = merged_data))

```

Dropping the fixed effects and controlling for initial migration opinion (init_mig) returns an even larger estimate. So far, so good - but this entire thing could also be modelled with a lagged dependent variable instead of the initial migration opinion. This also solves the multicollinearity issue.

```{r int_2}

summary(feglm(dv ~ crime_share*dv_lag | wave + lfdn,
      cluster = c("lfdn"), data = merged_data))

```

In this model, the interaction effect disappears. The lagged dependent has a negative effect, which i interpret as regression to the mean around some underlying migration opinion captured by the fixed effects. However, given this I am also worried that controlling for the lagged dependent is overdoing it (since the individual fixed effects should take care of this). I go against the holy wisdom of Brambor et al and drop a constitutive term:

```{r int_2b}

summary(feglm(dv ~ crime_share:dv_lag + crime_share | wave + lfdn,
      cluster = c("lfdn"), data = merged_data))

```

Which returns a significant direct and interaction effect again. I am however still unsure about the preceding model, which seems to control for too much but might also be showing some cross-temporal variation I should take into account - the news content of last week should not be predictable from some opinion four months ago. I also added estimated the same model with the initial opinion as a moderator, which again returned significant effects:

```{r add}
feglm(dv ~ crime_share:init_mig + crime_share | wave + lfdn,  
      cluster = c("lfdn"), data = merged_data)

```

I hoped for some guidance here. My main idea for now is to present the four significant models and add an analysis where I regress the news content of the week *following* the interview on the migration opinion given in the interview to show that this is not a result of respondents actively seeking out news content on crime. However, if the model including the lagged dependent variable shows some serious flaw, I might dig deeper to see what is going on -  I am just not sure where yet. Additionally, I see the reviewer comment "but Brambor et al tell us to include constitutive terms" coming (could be me) and would love to have a convincing answer.

Thank you so much for taking a look, all the best,
Nico

### 2022-06-28 pres/20220311/Aarhus.Rmd
Update pres as well
pray

---
title: "Emphasis Framing in the Real World"
subtitle: "Migration, Crime and the Heterogenous Impact of Media Content"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
    includes:
      after_body: insert-logo.html
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#03396d", background_color = "#bfbfbf",
  base_font_size = "32px",
  header_h1_font_size = "1.5rem",
  header_h2_font_size = "1.25rem",
  header_h3_font_size = "1.1rem",
  header_font_google = google_font("Montserrat", 'Thin 100'),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  footnote_font_size = "0.75rem"
)

```

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, cache = T, out.width="80%", fig.height=4, fig.width=10, fig.align='center', eval = T, dev = "svg")
# knitr::opts_knit$set(root.dir = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild')

library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)
library(lubridate)
library(patchwork)

```

class: inverse, center, middle

<!-- # Issue Definitions and Public Opinion -->

## Migration, Crime and the Heterogenous Impact of Emphasis Framing

#### Nicolai Berk<sup>*</sup>

Presentation prepared for the Political Behaviour and Institutions section at the University of Aarhus

`r Sys.Date()`

.left[.footnote[<sup>*</sup> Dynamics RTG & Humboldt Universität Berlin]]

<!-- --- -->

<!-- class: center, middle -->

<!-- #### *"The only feeling that anyone can have about an event he does not experience is the feeling aroused by his __mental image__ of that event." - W. Lippmann (1922, 3)* -->

---

## Migration coverage can look like this

![](collage_ukraine.png)

---

## ...or like this

![](collage.png)

---

## Does News Content Affect Political Attitudes?

.center[

<br></br>

### "media campaigns on emerging issues can have large, lasting, and ultimately consequential effects" (Foos and Bischof 2021)

### "it is difficult for people to be persuaded by competing media accounts" (Guess et al 2021)

]

<!-- #### Yes, says Foos and Bischof, BUT: -->
<!-- - very __long-term__ study -->
<!--   - __pre-internet__ (Bennett & Iyengar) -->
<!--   - likely __socialisation__ effect -->
<!-- - __unclear treatment__ (anti-Sun identity?) -->
<!-- - does not speak to content changes __within__ newspapers -->

---

## Does News Content Affect Political Attitudes?

### What can explain this discrepancy?

- existing observational studies often use **structural, long-term changes** in media markets (Durante & Knight, Foos & Bischof, Grossman et al).
- Unclear what the **everyday, short-term** impact of changing news content is.
- Recent studies assessing short-term changes usually present **null-effects** (Spirig, Guess et al).

---

# Argument

1. By __changing the emphasis__ of different considerations about political issues, news outlets can **reshape** their consumers' **attitudes**.
  + in the short term
  + in contemporary news environments
2. The minimal effects literature has been ignoring the **importance of predispositions**.
  + __Selective exposure__ takes place, but doesn't mitigate framing effects.

---

# Theoretical Model

.left-column[

![](minDAG.png)

]

.right-column[

- building on **emphasis framing** literature (Leeper & Slothuus, Nelson et al)
- cognitive association with a consideration is a function of emphasis of this aspect in media content
- conditioned by 
  + **pre-disposition** (Zaller)
  + **pre-treatment** (Slothuus 2016)

]

---

# Emphasis Framing

```{r out.width="70%"}

knitr::include_graphics("CognitiveStorage.png")

```

---

class: center, middle, inverse

# The Case

---

# Bild's migration coverage following 2015

.left-column[

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/3/3c/Kai_Diekmann_MediaMakers.jpg/435px-Kai_Diekmann_MediaMakers.jpg)

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/5/5a/2018-11-07-Julian_Reichelt-Maischberger-1141.jpg/800px-2018-11-07-Julian_Reichelt-Maischberger-1141.jpg)

]

.right-column[

- Migration is __the__ big topic preceding the 2017 _Bundestag_ election in Germany.
- Bild editor-in-chief Kai Diekmann left in February 2017, with Reichelt taking over.
- Reichelt increasingly **framed migrants as criminals** (Niggemeier 2018).
- **Least likely case**: 
  + pre-treatment, 
  + issue sorting, 
  + salient party cues, 
  + emotional issue.

]

---

# Bild's migration coverage following 2015 II

.left-column[

![](bild_umgebracht_asyl.jpeg)
![](bild_auslaender.jpeg)

]

.right-column[

Interesting because:

- **clearly identifiable short-term-change** in migration coverage.
- clear expectations regarding impact.
- Changing editor was not debated in the media $\rightarrow$ __No co-treatment__! (see Spirig)

]

---

class: center, middle, inverse

# Study Design

---

# Study Design

#### Combine panel data with media content analysis in Germany surrounding the 2017 election

- Study 1: Exploit change in migration framing due to **editorial change**
  + DiD design pre-post editorial change
  + newspaper consumption conditions treatment
- Study 2: correlate opinion change with **individual exposure**
  + generate estimates of individual frame exposure
  + based on reported newspaper consumption and interview date
  + robustness, but also extension beyond tabloid readers

---

## Measurement: Emphasis Framing in Print Media

#### Independent Variable (following Nicholson & Culpepper)
- Collected 2.5M news articles from major German dailies
- Two-step identification of issue definitions:
  1. Supervised deep-learning model (BERT) to **identify migration content**
  2. Structural Topic Model to **measure attention to issue considerations**

---

## Identify migration content

- Annotate 1800 articles to identify their migration content.
- Fine-tune German BERT deep-learning classifier.
- accuracy: 95.5% (F1: 0.94, recall: 0.93, precision: 0.95)
- 13.5k out of 400k articles in 2017 about migration (3.5\%)

---

## Measure migration frames

- Estimate 60-topic structural topic model on identified migration articles (Roberts, Stewart and Tingley 2019).
- using date and paper as covariates (Nicholls & Culpepper).
- Annotate.
- Select crime-related frames.

---

# Change in Crime News post-Reichelt (treatment validity)

```{r case_crime, out.width = "90%"}

## define survey dates
gles_p_long <- 
  fread('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/gles/Panel/long_cleaned.csv')

survey_dates <- 
  gles_p_long %>% 
  filter(!is.na(date_clean)) %>% 
  filter(!is.na('1130_clean') & !is.na('1661a_clean')) %>%  
  filter(date_clean < as.Date("2018-01-01")) %>% 
  group_by(wave) %>% 
  summarise(date = max(date_clean)) %>% 
  ungroup() %>% 
  select(date)

rm(gles_p_long)

## load & transform data frame attention
load("C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/media_daily_2022-02-02.Rdata")

merged_media <- 
  merged_media %>% 
  mutate(paper = recode(paper, 
                        'bild' = 'Bild', 'faz' = 'FAZ', 'spon' = 'Spiegel',
                        'sz' = 'SZ', 'taz' = 'TAZ', 'welt' = 'Welt'),
         post = date_new > as.Date("2017-02-01"),
         date_month = floor_date(as.Date(date_new), 'month'))

## visualise
trendplot <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"), date_new >= as.Date("2016-01-01")) %>% 
  mutate(
    date_month = floor_date(as.Date(date_new), 'month')
  ) %>%
  group_by(paper != "Bild", date_month) %>%
  summarise(across(share_mig:hungary_referendum_share, mean, na.rm = T),
            across(n_mig_sal:n_tot, sum, na.rm = T)) %>%
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         post = date_month >= as.Date("2017-02-01")) %>% 
  filter(date_month < as.Date("2020-01-01")) %>% 
  ggplot(aes(x = date_month, y = crime_share, col = `paper != "Bild"`)) +
  geom_line() +
  geom_rug(data = survey_dates, aes(x = date),sides = 't', inherit.aes = F) +
  # geom_point() +
  # geom_smooth(alpha = 0.1) +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") +
  ggtitle("Monthly Share of Migration Content Devoted to Crime Frames", "Bild vs. other major daily newspapers, 2016-2017") + 
  xlab("Date") + ylab("Share of Migration Content") +
  # facet_wrap(~paper)
  theme_minimal() +
  theme(legend.position = "none")

# DiD with placebo papers, 2016-17
merged_media <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"),
         date_new >= "2016-01-01")

treatment_ests <- 
  data.frame()

merged_media$dv    <-  merged_media[["crime_schlepp_share"]] + merged_media[["sexual_assault_share"]] + merged_media[["bild_footer_share"]]
merged_media$post  <-  merged_media$date_new >= as.Date("2017-02-01")

for (p in unique(merged_media$paper)){

  merged_media$treatment <-  merged_media$paper == p

  did_model <- lm(dv ~ post*treatment, data = merged_media)

  est <- did_model$coefficients["postTRUE:treatmentTRUE"][[1]]
  lower <- confint(did_model)["postTRUE:treatmentTRUE", 1]
  upper <- confint(did_model)["postTRUE:treatmentTRUE", 2]

  treatment_ests <- 
    rbind(treatment_ests,
          data.frame(
            model = "DiD",
            paper = p,
            est   = est,
            lower = lower,
            upper = upper
          ))
}

## vis
treatment_ests$paper <- 
  factor(treatment_ests$paper,
          levels = treatment_ests %>%
                    filter(model == "DiD") %>% 
                    arrange(est) %>% 
                    select(paper) %>%
                    unlist()
    )

placebo_papers <- 
  treatment_ests %>% 
  ggplot(aes(x = est, xmin = lower, xmax = upper, 
             y = paper, col = paper != "Bild")) +
  geom_pointrange() +
  geom_vline(xintercept = 0,
             col = "red", lty = 2) +
  theme_minimal() +
  xlab("Estimated DiD") + ylab("") +
  # ggtitle("Papers' Change in Crime Framing (DiD), 2016-2017") +
  theme(legend.position = "None") +
  coord_flip()

trendplot + placebo_papers

# rm(merged_media)

```

---

## Measurement: Immigration Attitude

#### Dependent Variable
- German Longitudinal Election Study (GLES) Panel
- 7-point Likert-scale asking whether immigration to Germany should be 
  + made easier (-3) or
  + restricted (3).

---

## Measurement: News Consumption

#### Conditioning Variable
- Question on print media consumed last week
- Match estimates for media content with interview date
- Calculate share of migration content devoted to crime
- Weighted by days read past week

---

class: center, middle, inverse

# Results

---

# DiD

$y_{it} = \alpha + \beta_1*Post_t + \beta_2 * Treatment_i + \beta_3 * Post_t * Treatment_i + \epsilon_{gt}$

```{r did-ests}
gles_p_long <- fread('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/gles/Panel/long_cleaned.csv')

gles_p_long$dv <- gles_p_long$`1130_clean`
gles_p_long$treat <- gles_p_long$`1661a_bin`
gles_p_long$post <- gles_p_long$date_clean>= as.Date("2017-02-01")
gles_p_long <- 
  gles_p_long %>% 
  select(lfdn, date_clean, `1130_clean`) %>% 
  filter(!is.na(`1130_clean`)) %>% 
  arrange(lfdn, date_clean) %>% 
  group_by(lfdn) %>% 
  slice(1) %>% 
  mutate(init_mig = `1130_clean`) %>% 
  select(lfdn, init_mig) %>% 
  right_join(gles_p_long, by = "lfdn")

gles_p_long <- 
  gles_p_long %>% 
  mutate(mip_mig_crime_lag = lag(mip_mig_crime)) %>% 
  filter(!is.na(mip_mig_crime)) %>% 
  arrange(lfdn, date_clean) %>% 
  group_by(lfdn) %>% 
  slice(1) %>% 
  mutate(mip_mig_crime_init = mip_mig_crime) %>% 
  select(lfdn, mip_mig_crime_init) %>% 
  right_join(gles_p_long, by = "lfdn")

gles_p_long_1617 <- 
  gles_p_long %>% 
        filter(date_clean >= as.Date("2016-01-01"),
               date_clean <  as.Date("2018-01-01"))
rm(gles_p_long)

# model 1: direct effect
ate <- 
  feglm(dv ~ post * treat | lfdn, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

inter <- 
  feglm(dv ~ post * treat * init_mig, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

inter_ctrl <- 
  feglm(dv ~ post * treat * init_mig + mip_mig_crime, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

points <- ate$coefficients
ests <- cbind(points, confint(ate))
ests %>% 
  # mutate(name = factor(row.names(.), levels = row.names(.))) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(row.names(ests)),
                   labels = rev(c("Post", "Treatment", "Post X Treatment")))

```

---

# Conditioning on initial migration opinion

$y_{it} = \beta_1 * Post_t *  Treatment_i * y_{i,t=1} + \epsilon_{gt}$

```{r did_inter}

points <- inter$coefficients
ests <- cbind(points, confint(inter))

plot_did_inter <- 
  ests %>% 
  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig")) %>% 
  mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
  ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("DiD-estimate with interaction") +
  xlim(-0.1, 0.4) + 
  scale_y_discrete(labels = rev(c("Post X Treatment", "Post X Treatment X Initial Opinion")))

plot_did_inter

```

(Constitutive terms omitted for brevity.)

---

# Or, descriptively:

```{r}

gles_p_long_1617 %>% 
  filter(!is.na(treat), !is.na(init_mig)) %>%
  group_by(treat, post, init_mig) %>% 
  summarise(
    dv_point = mean(dv, na.rm = T)
    ) %>% 
  filter(post) %>% 
  pivot_wider(
    names_from = treat,
    values_from = dv_point
  ) %>% 
  mutate(difference = `TRUE`-`FALSE`) %>% 
  ggplot(aes(x = init_mig, y = difference)) +
  geom_col(fill = 'lightblue') + 
  theme_minimal() + xlab("") + ylab("") +
  ggtitle("Pre-post differences of treated and untreated across initial migration attitude")

```

---

# Individual-level exposure model

$y_{it} = \alpha + \beta_1*CrimeExposure_{it} + \rho_i + \phi_t + \epsilon_{it}$

```{r ind_exp}

merged_data <- fread(file = "C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/merged_2022-03-05.csv")

merged_data <- 
  merged_data %>% 
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         # imm_att = factor(imm_att, levels = c("conservative", "moderate", "liberal", "miss")),
         dv = `1130_clean`) %>% 
  filter(lag == 7)

merged_data <- 
  merged_data %>% 
  filter(!is.na(`1130_clean`)) %>% 
  group_by(lfdn) %>% 
  arrange(lfdn, date_clean.x) %>% 
  select(`1130_clean`, lfdn) %>% 
  slice(1) %>% 
  mutate(init_mig = `1130_clean`) %>%
  select(init_mig, lfdn) %>% 
  right_join(merged_data, by = "lfdn")

# add lagged crime_share and dv
merged_data <- 
  merged_data %>%
  ungroup() %>% 
  arrange(lfdn, date_clean.x) %>% 
  group_by(lfdn) %>% 
  filter(!is.na(crime_share)) %>% 
  mutate(crime_share_lag = lag(crime_share),
         dv_lag = lag(dv))

# estimation ####

# individual exposure ####

# direct crime
ind_ate <- 
  feglm(dv ~ crime_share | wave + lfdn,  # positive, p < 0.1
      cluster = c("lfdn"), data = merged_data)

# crime X initial imm_att
ind_inter <- 
  feglm(dv ~ crime_share:init_mig + crime_share | wave + lfdn,  
      cluster = c("lfdn"), data = merged_data)

ind_inter_ctrl <- 
  feglm(dv ~ crime_share:init_mig + crime_share + mip_mig_crime | wave + lfdn,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_ate$coefficients
ests <- cbind(points, confint(ind_ate))
plot_ind_ate <- 
  ests %>% 
  # mutate(name = factor(row.names(.), levels = row.names(.))) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("") +
  scale_y_discrete(limits=rev(row.names(ests)),
                   labels = rev(c("Crime Exposure"))) +
  xlim(-0.75, 2)

points <- ind_inter$coefficients
ests <- cbind(points, confint(ind_inter))
plot_ind_inter <- 
  ests %>% 
  # mutate(name = factor(row.names(.), levels = row.names(.))) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("") +
  scale_y_discrete(limits=rev(row.names(ests)),
                   labels = rev(c("Crime Exposure", "Crime Exposure X Initial Opinion"))) +
  xlim(-0.75, 2)

plot_ind_ate/plot_ind_inter

```

---

# Summary

- ATE is null, even slightly negative, when not controlling for prior attitude
- Conservatives do not react to increased crime framing
- Is this a ceiling effect? No, because
  - results hold when comparing among conservative outlets
  - Conservatives react to other frames (ISIS, cues by party elites)

### Is lack of conservative response a result of pre-treatment?

---

## Can this be explained by pre-treatment effects?

$y_{it} = \alpha + \beta_1*CrimeExposure_{it} + \beta_2*CrimeExposure_{it}*y_{i,t=1} + \rho_i + \phi_t + \epsilon_{it}$

```{r ind_ctrl_pret}
ind_inter_pret <- 
  feglm(dv ~ crime_share:init_mig + crime_share + crime_share_lag | wave + lfdn,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_inter_pret$coefficients
ests <- cbind(points, confint(ind_inter_pret))
plot_ind_int_pret <- 
  ests %>% 
  filter(row.names(.) %in% c("crime_share", "crime_share:init_mig", "crime_share_lag")) %>%
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") + xlim(-0.75, 2) +
  scale_y_discrete(limits=rev(c("crime_share_lag", "crime_share", "crime_share:init_mig")),
                   labels = rev(c("Lagged Crime Exposure", "Crime Exposure", "Crime Exposure X Initial Opinion"))) +
  ggtitle("added control for past exposure")

plot_ind_inter/plot_ind_int_pret
```

## Yes!

---

# Conclusion
- Citizens seem to **learn from new information** - if a consideration is already available, no opinion updating takes place
- **ATE not informative** when interested in effects of media content
- important to take into account decreased susceptibility through **prior treatment**

---

# Open Questions

- Strongest point: Focus on prior opinion effect? More on selective exposure/pre-treatment? 
- **Framing**: ComSci, Framing, Media Effects, ...?
- **additional analyses**
- Can I use **variation/cutoff in pre-treatment** to make stronger argument about moderation?

---

## Pre-treatment DiD?

```{r}

dv_diff_plot <- 
  gles_p_long_1617 %>%
  filter(!is.na(treat), !is.na(dv)) %>% 
  filter(init_mig < 0) %>% 
  group_by(treat, wave) %>% 
  select(dv, date_clean) %>% 
  summarise_all(mean, na.rm = T) %>%  
  pivot_wider(names_from = treat, values_from = dv) %>%
  mutate(difference = `TRUE` - `FALSE`) %>% 
  ggplot(aes(x = date_clean, y = difference)) + 
  geom_line() +
  theme_minimal() + xlab("") + ylab("") +
  ggtitle("Difference between treated and untreated liberals")

iv_plot <- 
  merged_media %>% 
  filter(paper == "Bild", date_new >= as.Date("2016-10-01"), date_new <= as.Date("2017-10-01")) %>% 
  mutate(date_new = floor_date(date_new, "month")) %>%
  group_by(date_new) %>%
  summarise_all(mean, na.rm = T) %>%
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         crime_share_lag = lag(crime_share)) %>% 
  ggplot(aes(date_new)) +
  geom_col(aes(y = crime_share), width = 10) +
  theme_minimal() + xlab("") + ylab("") +
  ggtitle("Attention to Crime in Bild Migration Content")

dv_diff_plot/iv_plot

```

---

class: center, middle, inverse

# Thank you!

---

class: center, middle, inverse

# Appendix

---

class: inverse, center, middle

## Variables

---

## Individual Crime Exposure

```{r}

merged_data %>% 
  ggplot(aes(crime_share)) +
  geom_histogram() +
  xlab("Share of migration content consumed concerning crime")

```

---

# Dependent Variable

```{r}

gles_p_long_1617 %>% 
  filter(!is.na(`1130_clean`), !
           readership %in% c("", "Other", "None", "FR")) %>% 
  group_by(wave, readership) %>% 
  summarise(dv = mean(`1130_clean`, na.rm = T),
            date_min = min(date_clean)) %>% 
  ggplot(aes(x = date_min, y = dv, col = readership)) +
  geom_line()

```

---

## Correlation of past and present exposure to crime content is `r cor(merged_data$crime_share_lag, merged_data$crime_share, use = "complete.obs")`

```{r}

plot(merged_data$crime_share_lag, merged_data$crime_share)

```

---

class: inverse, center, middle

# Placebo Issues

---

## Effects on climate and socio-economic self-placement

```{r}

ests <- data.frame()

for(placebo_name in c("1090_clean", "1290_clean")){

  merged_data$placebo <- merged_data[[placebo_name]]

  ind_placebo <- 
    feglm(placebo ~ crime_share * crime_share_lag | wave,  
        cluster = c("lfdn"), data = merged_data)

  points <- ind_placebo$coefficients

  ests <- rbind(cbind(estimate = names(points), 
                      points, 
                      confint(ind_placebo), 
                      placebo = rep(placebo_name, 3)), 
                ests)

}

plot_ind_pretint <- 
  ests %>% 
  ggplot(aes(y = estimate, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Interaction with past exposure") +
  facet_grid(placebo~1) +
  scale_y_discrete(limits=rev(c("crime_share_lag", "crime_share", "crime_share:crime_share_lag")))

plot_ind_pretint

```

---

class: inverse, center, middle

# Mediated by pre-existing issue definitions?

---

## Control for mention of migrant crime as MIP in DiD:

```{r inter_ctrl}

points <- inter_ctrl$coefficients
ests <- cbind(points, confint(inter_ctrl))
plot_did_int_mip <- 
  ests %>% 
  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig", "mip_mig_crimeTRUE")) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(row.names(ests)[row.names(ests) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig", "mip_mig_crimeTRUE")])) +
  ggtitle("added control for mention of migrant crime")+
  xlim(-0.1, 0.4)

plot_did_inter/plot_did_int_mip

```

---

# Control for MIP: Migrant Crime

```{r ind_inter_ctrl}
points <- ind_inter_ctrl$coefficients
ests <- cbind(points, confint(ind_inter_ctrl))
plot_ind_int_mip <- 
  ests %>% 
  filter(row.names(.) %in% c("crime_share", "crime_share:init_mig", "mip_mig_crimeTRUE")) %>%
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(c("mip_mig_crimeTRUE", "crime_share", "crime_share:init_mig"))) +
  ggtitle("added control for mention of migrant crime")

plot_ind_inter/plot_ind_int_mip
```

### No: effect seems to be independent.

---

class: inverse, middle, center

## Effect on Issue Definitions

---

## Does increased exposure to crime affect likelihood to report criminal migrants as the main problem?

```{r ind_inter_dv}

ind_dv_mip <- 
  feglm(mip_mig_crime ~ crime_share | wave + lfdn,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_dv_mip$coefficients
ests <- cbind(points, confint(ind_dv_mip))
plot_ind_dv_mip <- 
  ests %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Effect of exposure on reporting migrant crime as MIP")

ind_inter_dv <- 
  feglm(mip_mig_crime ~ crime_share:init_mig + crime_share + init_mig | wave,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_inter_dv$coefficients
ests <- cbind(points, confint(ind_inter_dv))
plot_ind_int_mip <- 
  ests %>% 
  filter(row.names(.) %in% c("crime_share", "crime_share:init_mig")) %>%
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(c("crime_share", "crime_share:init_mig"))) +
  ggtitle("and interaction with prior attitudes")

plot_ind_dv_mip/plot_ind_int_mip
```

### Effect larger among liberals and moderates (also huge effect).

---

### What if controlling for attitude?

```{r mip_ctrl_dv}

ind_inter_dv_ctrl <- 
  feglm(mip_mig_crime ~ crime_share:init_mig + crime_share + dv | wave,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_inter_dv_ctrl$coefficients
ests <- cbind(points, confint(ind_inter_dv_ctrl))
plot_ind_int_mip_ctrl <- 
  ests %>% 
  # filter(row.names(.) %in% c("crime_share", "crime_share:init_mig")) %>%
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  # scale_y_discrete(limits=rev(c("crime_share", "crime_share:init_mig"))) +
  ggtitle("additional control: dependent variable")

plot_ind_int_mip/plot_ind_int_mip_ctrl

```

### Interaction disappears. Model highly sensitive to inclusion of past and current attitude as well as individual FEs.

---

class: inverse, middle, center

# Other frames

---

## All frames conditioned on initial attitude

```{r}

est_ov <- data.frame()

for (treat in 
     merged_data %>% 
     ungroup() %>%  
     select(n_articles:hungary_referendum_share, -essener_tafel_share) %>% 
     .[,apply(., FUN = mean, na.rm = T, MARGIN = 2) > 0.02] %>% # restrict to topics making up 2% or more of imm coverage on average
     colnames()){
  merged_data$treatment <- merged_data[[eval(treat)]]
  ests <- feglm(dv ~ treatment*init_mig | wave, data = merged_data, cluster = c("lfdn"))

  data.frame(
    treatment   = treat,
    treat_est   = ests$coefficients[["treatment"]],
    treat_lower = confint(ests)["treatment",][[1]],
    treat_upper = confint(ests)["treatment",][[2]],
    ia_est   = ests$coefficients[["treatment:init_mig"]],
    ia_lower = confint(ests)["treatment:init_mig",][[1]],
    ia_upper = confint(ests)["treatment:init_mig",][[2]]
  ) %>% 
  rbind(est_ov, .) -> est_ov

}

est_ov %>% 
  pivot_longer(cols = treat_est:ia_upper, names_to = c("estimate", ".value"), names_pattern = "(.*)_(.*)") %>% 
  filter(estimate == "ia") %>% 
  ggplot(aes(x = est, xmin = lower, xmax = upper, y = treatment)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2)

```

---

## All frames conditioned on pre-treatment

```{r}

est_ov_pret <- data.frame()

for (treat in 
     merged_data %>% 
     ungroup() %>%  
     select(n_articles:hungary_referendum_share, -essener_tafel_share) %>% 
     .[,apply(., FUN = mean, na.rm = T, MARGIN = 2) > 0.02] %>% # restrict to topics making up 2% or more of imm coverage on average
     colnames()){
  merged_data$treatment <- merged_data[[eval(treat)]]
  merged_data <- 
    merged_data %>% 
    arrange(lfdn, date_clean.x) %>% 
    group_by(lfdn) %>% 
    mutate(treatment_lag = lag(treatment))

  ests <- feglm(dv ~ treatment*treatment_lag | wave, data = merged_data, cluster = c("lfdn"))

  data.frame(
    treatment   = treat,
    treat_est   = ests$coefficients[["treatment"]],
    treat_lower = confint(ests)["treatment",][[1]],
    treat_upper = confint(ests)["treatment",][[2]],
    treat_lag_est   = ests$coefficients[["treatment_lag"]],
    treat_lag_lower = confint(ests)["treatment_lag",][[1]],
    treat_lag_upper = confint(ests)["treatment_lag",][[2]],
    ia_est   = ests$coefficients[["treatment:treatment_lag"]],
    ia_lower = confint(ests)["treatment:treatment_lag",][[1]],
    ia_upper = confint(ests)["treatment:treatment_lag",][[2]]
  ) %>% 
  rbind(est_ov_pret, .) -> est_ov_pret

}

est_ov_pret %>% 
  pivot_longer(cols = treat_est:ia_upper, names_to = c("estimate", ".value"), names_pattern = "(.*)_(.*)") %>% 
  filter(estimate == "ia") %>% 
  ggplot(aes(x = est, xmin = lower, xmax = upper, y = treatment)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2)

```

---

## Camps Frame

```{r}

merged_data <- 
  merged_data %>% 
  mutate(camps_share = camps_greece_share + ME_camps_share) %>% 
  mutate(camps_share_lag = lag(camps_share))

ind_pretind <- 
  feglm(dv ~ camps_share * camps_share_lag | wave,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_pretind$coefficients
ests <- cbind(points, confint(ind_pretind))
plot_ind_pretint <- 
  ests %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Interaction with past exposure") +
  scale_y_discrete(limits=rev(c("camps_share_lag", "camps_share", "camps_share:camps_share_lag")))

plot_ind_pretint
```

---

## ISIS Frame

```{r}

merged_data <- 
  merged_data %>% 
  mutate(islamic_state_share_lag = lag(islamic_state_share))

ind_pretind <- 
  feglm(dv ~ islamic_state_share * islamic_state_share_lag | wave,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_pretind$coefficients
ests <- cbind(points, confint(ind_pretind))
plot_ind_pretint <- 
  ests %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Interaction with past exposure") +
  scale_y_discrete(limits=rev(c("islamic_state_share_lag", "islamic_state_share", "islamic_state_share:islamic_state_share_lag")))

plot_ind_pretint
```

---

## Party Cue

```{r}

merged_data <- 
  merged_data %>% 
  mutate(csu_poverty_share_lag = lag(csu_poverty_share))

ind_pretind <- 
  feglm(dv ~ csu_poverty_share * csu_poverty_share_lag | wave,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_pretind$coefficients
ests <- cbind(points, confint(ind_pretind))
plot_ind_pretint <- 
  ests %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Interaction with past exposure") +
  scale_y_discrete(limits=rev(c("csu_poverty_share_lag", "csu_poverty_share", "csu_poverty_share:csu_poverty_share_lag")))

plot_ind_pretint
```

---

class: center, inverse, middle

## Other

---

## Is effect of exposure dependent on past exposure?

```{r pret_ind}

ind_pretind <- 
  feglm(dv ~ crime_share * crime_share_lag | wave,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_pretind$coefficients
ests <- cbind(points, confint(ind_pretind))
plot_ind_pretint <- 
  ests %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Interaction with past exposure") +
  scale_y_discrete(limits=rev(c("crime_share_lag", "crime_share", "crime_share:crime_share_lag")),
                   labels = rev(c("Lagged Crime Exposure", "Crime Exposure", "Crime Exposure X Lagged Crime Exposure")))

plot_ind_pretint

```

### Yes.

(Finding is sensitive to individual fixed effects.)

---

## Agenda setting vs framing

```{r}

inter <- 
  feglm(dv ~ crime_share * n_articles | lfdn + wave, 
      cluster = c("lfdn"), 
      data = merged_data)

points <- inter$coefficients
ests <- cbind(points, confint(inter))

plot_did_inter_ag <- 
  ests %>% 
  mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
  ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Agenda setting vs framing effects")

inter

```
(not significant)

---

## Model Bild readers vs. other conservatives

```{r}

inter <- 
  feglm(dv ~ post * treat * init_mig, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617 %>% 
        filter(`1661a_bin` | `1661c_bin` | `1661f_bin`))

points <- inter$coefficients
ests <- cbind(points, confint(inter))

plot_did_inter_cons <- 
  ests %>% 
  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig")) %>% 
  mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
  ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Control: conservative readers")

plot_did_inter_cons

```

---

# Relationship of Issue Importance and Attitude

```{r}

merged_data %>% 
  filter(!is.na(`1130_clean`) & !is.na(`1140_clean`)) %>% 
  ggplot(aes(x = `1140_clean`+3, y = `1130_clean`)) +
  geom_violin(aes(x = as.factor(`1140_clean`)), fill = 'lightblue') +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2))

```

### 2022-06-28 pres/20220401/UNDA.Rmd
Update pres as well
pray

--- 2022-06-28 pres/20220311/Aarhus.Rmd
@@
 ---
-title: "Emphasis Framing in the Real World"
-subtitle: "Migration, Crime and the Heterogenous Impact of Media Content"
+title: "Learning what's at Stake"
+subtitle: "How the News Media Shapes Public Opinion by Defining Political Issues"
 author: "Nicolai Berk"
@@
 
+# 1000 Bootstraps
+
+```{r, out.width= "90%"}
+
+gles_p_long_1617$dv <- gles_p_long_1617$`1130_clean`
+gles_p_long_1617$treat <- gles_p_long_1617$bild_init
+gles_p_long_1617$post <- gles_p_long_1617$date_clean>= as.Date("2017-02-01")
+
+inter <- 
+  feglm(dv ~ post * treat * init_mig, 
+      cluster = c("lfdn"), 
+      data = gles_p_long_1617)
+
+points <- ate$coefficients
+ests <- cbind(points, confint(ate))
+
+load('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/did_bootstraps.RData')
+
+direct <- coef(inter)["postTRUE:treatTRUE"]
+interact <- coef(inter)["postTRUE:treatTRUE:init_mig"]
+
+did_bootstrap <- 
+  ggplot() +
+  geom_histogram(data = gles_p_long_1617 %>% filter(wave == "1"), mapping = aes(x = init_mig, after_stat(density)), alpha = 0.4, bins = 8) +
+  geom_abline(data = bs_did_ests, aes(slope = IA, intercept = DiD, group = boots), alpha= 0.05) +
+  geom_abline(slope = interact, intercept = direct, col = "red") +
+  theme_minimal() +
+  geom_hline(yintercept = 0, col = "black") +
+  scale_x_continuous(limits=c(-3,3)) +
+  scale_y_continuous(limits=c(0,.6)) +
+  ggtitle(paste0(B, " bootstrap estimates of heterogenous treatment effect")) +
+  ylab("Estimate") + xlab("Initial migration attitude")
+
+```
+
+---
+
 # Or, descriptively:

### 2022-06-28 pres/20220422/Firenze.Rmd
Update pres as well
pray

---
title: "How the News Media Shapes Public Opinion"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
    includes:
      after_body: insert-logo.html
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#004A95", background_color = "#bfbfbf",
  base_font_size = "36px",
  header_h1_font_size = "1.3rem",
  header_h2_font_size = "1.2rem",
  header_h3_font_size = "1.05rem",
  header_font_google = google_font("Lato", '700'),
  text_font_google   = google_font("Lato", "400"),
  code_font_google   = google_font("Fira Mono"),
  footnote_font_size = "0.75rem"
)

```

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear",
           cite.style = "authoryear",
           style = "markdown",
           hyperlink = FALSE,
           dashed = FALSE)
myBib <- ReadBib("C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib", check = FALSE)
```

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE, 
  message = F, 
  warning = F, 
  cache = T, 
  out.width="80%", 
  fig.height=9, 
  fig.width=16, 
  fig.align='center', 
  eval = T, 
  dev = "svg"
  )
# knitr::opts_knit$set(root.dir = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild')

library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)
library(lubridate)
library(patchwork)

```

class: inverse, center, middle

## How the News Media Shapes Public Opinion by Defining Political Issues

#### Nicolai Berk<sup>*</sup>

Presentation prepared for the 13th European Graduate Network Conference at the European University Institute, Florence

`r Sys.Date()`

.left[.footnote[<sup>*</sup> Dynamics RTG & Humboldt Universität Berlin]]

---

## Migration coverage can look like this

```{r out.width="70%"}

knitr::include_graphics("firenze_intro_ukraine.png")

```

---

## ...or like this

```{r out.width="70%"}

knitr::include_graphics("firenze_crime.png")

```

---

## Does News Content Affect Political Attitudes?

<br>

A bullet-point review:

- Experimental research shows large framing effects `r Citep(myBib[c("kahneman2011thinking", "Leeper2020")])`.
- Unclear if externally valid `r Citep(myBib[c("Barabas2010")])`.
- Increasing reliance on **observational studies** and **field experiments**.

---

## Research Gap

<br>

Current focus on:

- **Structural, long-term changes** in media markets `r Citep(myBib[c("Foos2022", "Grossman2022")])`.
- Effects of **changing news outlets** `r Citep(myBib[c("Broockman2022", "Guess2021")])`.
- **Average** treatment effects.

---

## Research Gap II

<br>

Unclear:

- **everyday, medium-term** impact?
- Which news **content** is effective?
- Effect dependent on individual **predispositions**?

---

## Argument

<br>

1. News media influences public opinion by __emphasising certain considerations__ over others.
3. **Predispositions** structure individual susceptibility.

---

class: center, middle, inverse

# Theoretical Framework

---

## Expectancy-Value Model `r Citep(myBib["Ajzen2000"])`

```{r out.width="70%"}

knitr::include_graphics("CognitiveStorage.png")

```

---

## Theoretical Model

.left-column[

![](minDAG.png)

]

.right-column[

Cognitive **association** with a consideration is a **function of emphasis** of this aspect in media content `r Citep(myBib[c("Leeper2020",  "Nelson1997")])`.

<br>

### H1: Increased **exposure to negative considerations** results in more **negative attitudes** about an issue.

]

---

## Accessibility

<br>

- Experimental research suggests **exposure to consideration mutes effect** of subsequent exposure `r Citep(myBib[c("Druckman2012")])`.
- Hence media content only affects opinions when exposed individual **learns something new**.

### H2: Individuals are less susceptible when exposed to considerations that are **already accessible** to them.

---

class: center, middle, inverse

# The Case

---

## Bild's migration coverage following 2015

.left-column[

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/3/3c/Kai_Diekmann_MediaMakers.jpg/435px-Kai_Diekmann_MediaMakers.jpg)

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/5/5a/2018-11-07-Julian_Reichelt-Maischberger-1141.jpg/800px-2018-11-07-Julian_Reichelt-Maischberger-1141.jpg)

]

.right-column[

- Migration is __the__ big topic preceding the 2017 _Bundestag_ election in Germany.
- Bild editor-in-chief Kai Diekmann left in February 2017, with Reichelt taking over.
- Reichelt increasingly **framed migrants as criminals** `r Citep(myBib[c("Niggemeier2018Bild")])`.

]

---

## Bild's migration coverage following 2015 II

.left-column[

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/3/3c/Kai_Diekmann_MediaMakers.jpg/435px-Kai_Diekmann_MediaMakers.jpg)

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/5/5a/2018-11-07-Julian_Reichelt-Maischberger-1141.jpg/800px-2018-11-07-Julian_Reichelt-Maischberger-1141.jpg)

]

.right-column[

**Least likely case**: 
- Issue sorting, 
- pre-treatment, 
- salient party cues, 
- emotional issue.

]

---
## Bild's migration coverage following 2015 III

.left-column[

![](bild_umgebracht_asyl.jpeg)
![](bild_auslaender.jpeg)

]

.right-column[

Interesting because:

- **Clearly identifiable short-term-change** in migration coverage.
- Clear expectations regarding impact.
- Changing editor was not debated in the media $\rightarrow$ __No co-treatment__! `r Citep(myBib["Spirig2020"])`.

]

---

class: center, middle, inverse

# Study Design

---

## Measurement: Emphasis Framing in Print Media

<br>

#### Independent Variable `r Citep(myBib["Nicholson2020"], before = "partly following ")`

- Collected 2.5M news articles from major German daily newspapers.
- Two-step identification of issue definitions:
  1. Supervised deep-learning model (BERT) to **select migration content**
  2. Structural Topic Model to **identify considerations**

---

## Change in Crime News post-Reichelt

```{r case_crime}

## define survey dates
gles_p_long <- 
  fread('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/gles/Panel/long_cleaned.csv')

survey_dates <- 
  gles_p_long %>% 
  filter(!is.na(date_clean)) %>% 
  filter(!is.na('1130_clean') & !is.na('1661a_clean')) %>%  
  filter(date_clean < as.Date("2018-01-01")) %>% 
  group_by(wave) %>% 
  summarise(date = max(date_clean)) %>% 
  ungroup() %>% 
  select(date)

rm(gles_p_long)

## load & transform data frame attention
load("C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/media_daily_2022-02-02.Rdata")

merged_media <- 
  merged_media %>% 
  mutate(paper = recode(paper, 
                        'bild' = 'Bild', 'faz' = 'FAZ', 'spon' = 'Spiegel',
                        'sz' = 'SZ', 'taz' = 'TAZ', 'welt' = 'Welt'),
         post = date_new > as.Date("2017-02-01"),
         date_month = floor_date(as.Date(date_new), 'month'))

## visualise
trendplot <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"), date_new >= as.Date("2016-01-01")) %>% 
  mutate(
    date_month = floor_date(as.Date(date_new), 'month')
  ) %>%
  group_by(paper != "Bild", date_month) %>%
  summarise(across(share_mig:hungary_referendum_share, mean, na.rm = T),
            across(n_mig_sal:n_tot, sum, na.rm = T)) %>%
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         post = date_month >= as.Date("2017-02-01")) %>% 
  filter(date_month < as.Date("2020-01-01")) %>% 
  ggplot(aes(x = date_month, y = crime_share, col = `paper != "Bild"`)) +
  geom_line(size = 2) +
  geom_rug(data = survey_dates, aes(x = date),sides = 't', inherit.aes = F, size = 2) +
  # geom_point() +
  # geom_smooth(alpha = 0.1) +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red", size = 2) +
  # ggtitle("Monthly Share of Migration Content Devoted to Crime Frames", "Bild vs. other major daily newspapers, 2016-2017") + 
  xlab("") + ylab("Share of Migration Content") +
  # facet_wrap(~paper)
  # theme(legend.position = "none") +
  theme_xaringan() + 
  scale_color_discrete(name = "Bild reader", labels = c("Yes", "No"))

# DiD with placebo papers, 2016-17
merged_media <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"),
         date_new >= "2016-01-01")

treatment_ests <- 
  data.frame()

merged_media$dv    <-  merged_media[["crime_schlepp_share"]] + merged_media[["sexual_assault_share"]] + merged_media[["bild_footer_share"]]
merged_media$post  <-  merged_media$date_new >= as.Date("2017-02-01")

for (p in unique(merged_media$paper)){

  merged_media$treatment <-  merged_media$paper == p

  did_model <- lm(dv ~ post*treatment, data = merged_media)

  est <- did_model$coefficients["postTRUE:treatmentTRUE"][[1]]
  lower <- confint(did_model)["postTRUE:treatmentTRUE", 1]
  upper <- confint(did_model)["postTRUE:treatmentTRUE", 2]

  treatment_ests <- 
    rbind(treatment_ests,
          data.frame(
            model = "DiD",
            paper = p,
            est   = est,
            lower = lower,
            upper = upper
          ))
}

## vis
treatment_ests$paper <- 
  factor(treatment_ests$paper,
          levels = treatment_ests %>%
                    filter(model == "DiD") %>% 
                    arrange(est) %>% 
                    select(paper) %>%
                    unlist()
    )

placebo_papers <- 
  treatment_ests %>% 
  ggplot(aes(x = est, xmin = lower, xmax = upper, 
             y = paper, col = paper != "Bild")) +
  geom_pointrange(size = 2) +
  geom_vline(xintercept = 0,
             col = "red", lty = 2, size = 2) +
  xlab("Estimated DiD") + ylab("") +
  # ggtitle("Papers' Change in Crime Framing (DiD), 2016-2017") +
  theme(legend.position = "None") +
  coord_flip() + theme_xaringan()

trendplot

# rm(merged_media)

```

---

## Placebo papers

```{r}

placebo_papers

```

---

## Measurement: Immigration Attitude

<br>

#### Dependent Variable

- German Longitudinal Election Study (GLES) Panel
- 7-point Likert-scale asking whether immigration to Germany should be 
  + made easier (-3) or
  + restricted (3).

---

## Measurement: News Consumption

<br>

#### Conditioning Variable

- Question on newspapers consumed last week.
- Simple binary variable for DiD-model.
- Calculate share of migration content devoted to crime for FE model.

---

## Measurement: Accessibility

<br>

#### Moderator

- **Initial migration opinion** reflects product of weighted considerations.
- Those with **liberal migration attitudes** are **less likely to hold crime considerations**.

---

# Estimation

**Difference-in-Differences (DiD)**

- Comparing Bild readers and non-readers,
- before and after Reichelt takeover.
- Interaction with initial report of migrant crime as most important problem.

$$y_{it} = \alpha + \beta * Post_t *  Treatment_i * y_{i,t=1} + \epsilon_{gt}$$

.footnote[(Constitutive terms omitted for brevity.)]

---

# Estimation II

<br>

**Fixed-effects-model**
- Generate estimates of **individual exposure** to consideration.
- Control for **individual** and **wave fixed effects**.
- Interaction with prior report of migrant crime.

$$y_{it} = \beta * CrimeExposure_{it} * y_{i,t=1} + \rho_i + \phi_t + \epsilon_{it}$$
.footnote[(Constitutive terms omitted for brevity.)]

---

class: center, middle, inverse

# Results

---

# DiD Model

```{r did-data}

source("C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/code/functions.R")

gles_p_long_1617 <- 
  DiD_data_prep()

```

```{r did-ests}

plot_did_ate <- bs_inter_vis(gles_p_long_1617, size = 2, col = "#004A95")  + theme_xaringan()
plot_did_inter <- bs_inter_vis(gles_p_long_1617, size = 2, col = "#004A95") + theme_xaringan()

plot_did_ate/plot_did_inter

```

---

## Conditioning on Accessibility

```{r did_bs}

DiD_bs(gles_p_long_1617) +
  theme_xaringan()

```

---

## Or, descriptively:

```{r}

DiD_groups(gles_p_long_1617) +
  theme_xaringan()

```

---

# Individual-level exposure model

```{r ind_exp}

merged_data <- fread(file = "C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/merged_2022-03-05.csv")

merged_data <- 
  merged_data %>% 
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         dv = `1130_clean`) %>% 
  filter(lag == 7)

merged_data <- 
  merged_data %>% 
  filter(!is.na(`1130_clean`)) %>% 
  group_by(lfdn) %>% 
  arrange(lfdn, date_clean.x) %>% 
  select(`1130_clean`, lfdn) %>% 
  slice(1) %>% 
  mutate(init_mig = `1130_clean`) %>%
  select(init_mig, lfdn) %>% 
  right_join(merged_data, by = "lfdn")

# add lagged crime_share and dv
merged_data <- 
  merged_data %>%
  ungroup() %>% 
  arrange(lfdn, date_clean.x) %>% 
  group_by(lfdn) %>% 
  filter(!is.na(crime_share)) %>% 
  mutate(crime_share_lag = lag(crime_share),
         dv_lag = lag(dv))

# estimation ####

# individual exposure ####

# direct crime
ind_ate <- 
  feglm(dv ~ crime_share | wave + lfdn,  # positive, p < 0.1
      cluster = c("lfdn"), data = merged_data)

# crime X initial imm_att
ind_inter <- 
  feglm(dv ~ crime_share:init_mig + crime_share | wave + lfdn,  
      cluster = c("lfdn"), data = merged_data)

ind_inter_ctrl <- 
  feglm(dv ~ crime_share:init_mig + crime_share + mip_mig_crime | wave + lfdn,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_ate$coefficients
ests <- cbind(points, confint(ind_ate))
plot_ind_ate <- 
  ests %>% 
  # mutate(name = factor(row.names(.), levels = row.names(.))) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2, col = "#004A95") +
  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
  ylab("") + xlab("") +
  scale_y_discrete(limits=rev(row.names(ests)),
                   labels = rev(c("Crime Exposure"))) +
  xlim(-0.75, 2) + 
  theme_xaringan()

points <- ind_inter$coefficients
ests <- cbind(points, confint(ind_inter))
plot_ind_inter <- 
  ests %>% 
  # mutate(name = factor(row.names(.), levels = row.names(.))) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2, col = "#004A95") +
  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
  ylab("") + xlab("") +
  scale_y_discrete(limits=rev(row.names(ests)),
                   labels = rev(c("Crime Exposure", "Crime Exposure\n X Initial Opinion"))) +
  xlim(-0.75, 2) +
  theme_xaringan()

plot_ind_ate/plot_ind_inter

```

---

# Summary

<br>

- **ATE is null** when not moderating with prior attitude.
- **Conservatives do not react** to increased crime framing.
- Is this a ceiling effect? No, because:
  - results hold when comparing among conservative outlets
  - Conservatives react to other frames (ISIS, cues by party elites)

---

# Conclusion

<br>

- Media **content affects attitude** formation.
- **Effect is conditional** on pre-existing attitude.

## $\rightarrow$ Attitude is a **product of information and predisposition** `r Citep(myBib["Zaller1992"])`.

---

# Limitations

<br>

#### Unclear:

- how important these effects are in **more fragmented media landscapes**,
- which content affects **which groups**,
- which **other actors** can affect framing in the media.

---

class: center, middle, inverse

# Thank you!

---

class: center, middle, inverse

## This research is generously funded by:

```{r out.width="50%"}

knitr::include_graphics("banner_new.png")

```

```{r out.width="50%"}

knitr::include_graphics("dfg_logo_englisch_blau_en.jpg")

```

---

# References

.footnote[

```{r refs, echo=FALSE, results="asis", cache=FALSE}

PrintBibliography(myBib, end = 4)

```

]
---

# References II

.footnote[

```{r refs2, echo=FALSE, results="asis", cache=FALSE}

PrintBibliography(myBib, start = 5, end = 8)

```

]
---

# References II

.footnote[

```{r refs3, echo=FALSE, results="asis", cache=FALSE}

PrintBibliography(myBib, start = 9)

```

]
---

class: center, middle, inverse

# Appendix

---

class: inverse, center, middle

## Variables

---

## Individual Crime Exposure

```{r}

merged_data %>% 
  ggplot(aes(crime_share)) +
  geom_histogram() +
  xlab("Share of migration content consumed concerning crime") +
  theme_xaringan()

```

---

# Dependent Variable

```{r}

gles_p_long_1617 %>% 
  filter(!is.na(`1130_clean`), !
           readership %in% c("", "Other", "None", "FR")) %>% 
  group_by(wave, readership) %>% 
  summarise(dv = mean(`1130_clean`, na.rm = T),
            date_min = min(date_clean)) %>% 
  ggplot(aes(x = date_min, y = dv, col = readership)) +
  geom_line(size = 2) +
  theme_xaringan()

```

---

## Identify Migration Content

<br>

- Annotate 1800 articles to identify their migration content.
- Fine-tune German BERT deep-learning classifier.
- accuracy: 95.5% (F1: 0.94, recall: 0.93, precision: 0.95)
- 13.5k out of 400k articles in 2017 about migration (3.5\%)

---

## Measure Considerations about Migration

<br>

- Estimate 60-topic structural topic model on identified migration articles `r Citep(myBib["Roberts2014"])`.
- using date and paper as covariates `r Citep(myBib["Nicolls2020"])`.
- Annotate.
- Select crime-related considerations.

---

class: inverse, center, middle

# Mediated by pre-existing issue definitions?

---

## Control for mention of migrant crime as MIP in DiD:

```{r inter_ctrl}

inter_ctrl <- 
  feglm(dv ~ post * treat * init_mig + mip_mig_crime, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)
points <- inter_ctrl$coefficients
ests <- cbind(points, confint(inter_ctrl))
plot_did_int_mip <- 
  ests %>% 
  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig", "mip_mig_crimeTRUE")) %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2) +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(row.names(ests)[row.names(ests) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig", "mip_mig_crimeTRUE")])) +
  ggtitle("added control for mention of migrant crime")+
  xlim(-0.1, 0.4) +
  theme_xaringan()

plot_did_inter/plot_did_int_mip

```

---

# Control for MIP: Migrant Crime

```{r ind_inter_ctrl, height = 6}
points <- ind_inter_ctrl$coefficients
ests <- cbind(points, confint(ind_inter_ctrl))
plot_ind_int_mip <- 
  ests %>% 
  filter(row.names(.) %in% c("crime_share", "crime_share:init_mig", "mip_mig_crimeTRUE")) %>%
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2) +
  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(c("mip_mig_crimeTRUE", "crime_share", "crime_share:init_mig"))) +
  ggtitle("added control for mention of migrant crime") +
  theme_xaringan()

plot_ind_inter/plot_ind_int_mip
```

### No: effect seems to be independent.

---

class: inverse, middle, center

## Effect on Issue Definitions

---

## Does increased exposure to crime affect likelihood to report criminal migrants as the main problem?

```{r ind_inter_dv, fig.height=6}

ind_dv_mip <- 
  feglm(mip_mig_crime ~ crime_share | wave + lfdn,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_dv_mip$coefficients
ests <- cbind(points, confint(ind_dv_mip))
plot_ind_dv_mip <- 
  ests %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2) +
  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Effect of exposure on reporting migrant crime as MIP") +
  theme_xaringan()

ind_inter_dv <- 
  feglm(mip_mig_crime ~ crime_share:init_mig + crime_share + init_mig | wave,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_inter_dv$coefficients
ests <- cbind(points, confint(ind_inter_dv))
plot_ind_int_mip <- 
  ests %>% 
  filter(row.names(.) %in% c("crime_share", "crime_share:init_mig")) %>%
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(limits=rev(c("crime_share", "crime_share:init_mig"))) +
  ggtitle("and interaction with prior attitudes") +
  theme_xaringan()

plot_ind_dv_mip/plot_ind_int_mip
```

### Effect larger among liberals and moderates (also huge effect).

---

class: inverse, middle, center

# Other frames

---

## All frames conditioned on initial attitude

```{r}

est_ov <- data.frame()

for (treat in 
     merged_data %>% 
     ungroup() %>%  
     select(n_articles:hungary_referendum_share, -essener_tafel_share) %>% 
     .[,apply(., FUN = mean, na.rm = T, MARGIN = 2) > 0.02] %>% # restrict to topics making up 2% or more of imm coverage on average
     colnames()){
  merged_data$treatment <- merged_data[[eval(treat)]]
  ests <- feglm(dv ~ treatment*init_mig | wave, data = merged_data, cluster = c("lfdn"))

  data.frame(
    treatment   = treat,
    treat_est   = ests$coefficients[["treatment"]],
    treat_lower = confint(ests)["treatment",][[1]],
    treat_upper = confint(ests)["treatment",][[2]],
    ia_est   = ests$coefficients[["treatment:init_mig"]],
    ia_lower = confint(ests)["treatment:init_mig",][[1]],
    ia_upper = confint(ests)["treatment:init_mig",][[2]]
  ) %>% 
  rbind(est_ov, .) -> est_ov

}

est_ov %>% 
  pivot_longer(cols = treat_est:ia_upper, names_to = c("estimate", ".value"), names_pattern = "(.*)_(.*)") %>% 
  filter(estimate == "ia") %>% 
  ggplot(aes(x = est, xmin = lower, xmax = upper, y = treatment)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  theme_xaringan() +
  ggtitle("Interaction Effect")

```

---

class: center, inverse, middle

## Other

---

## Is effect of exposure dependent on past exposure?

```{r pret_ind, fig.height=6}

ind_pretind <- 
  feglm(dv ~ crime_share * crime_share_lag | wave,  
      cluster = c("lfdn"), data = merged_data)

points <- ind_pretind$coefficients
ests <- cbind(points, confint(ind_pretind))
plot_ind_pretint <- 
  ests %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2) +
  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Interaction with past exposure") +
  scale_y_discrete(limits=rev(c("crime_share_lag", "crime_share", "crime_share:crime_share_lag")),
                   labels = rev(c("Lagged Crime Exposure", "Crime Exposure", "Crime Exposure X Lagged Crime Exposure"))) +
  theme_xaringan()

plot_ind_pretint

```

### Yes.

(Finding is sensitive to individual fixed effects.)

---

## Model Bild readers vs. other conservatives

```{r}

inter <- 
  feglm(dv ~ post * treat * init_mig, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617 %>% 
        filter(`1661a_bin` | `1661c_bin` | `1661f_bin`))

points <- inter$coefficients
ests <- cbind(points, confint(inter))

plot_did_inter_cons <- 
  ests %>% 
  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig")) %>% 
  mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
  ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, col = "red", lty = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("Control: conservative readers") +
  theme_xaringan()

plot_did_inter_cons

```

---

# Relationship of Issue Importance and Attitude

```{r}

merged_data %>% 
  filter(!is.na(`1130_clean`) & !is.na(`1140_clean`)) %>% 
  ggplot(aes(x = `1140_clean`+3, y = `1130_clean`)) +
  geom_violin(aes(x = as.factor(`1140_clean`))) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2)) +
  theme_xaringan()

```

### 2022-06-28 pres/20220506/Dublin.Rmd
Update pres as well
pray

--- 2022-06-28 pres/20220422/Firenze.Rmd
@@
 
+# Framing Effects in the Wild
+
 ## How the News Media Shapes Public Opinion by Defining Political Issues
@@
 
-Presentation prepared for the 13th European Graduate Network Conference at the European University Institute, Florence
+Presentation prepared for the 4th Annual CompText Conference, Dublin
 
@@
 
-```{r out.width="70%"}
-
-knitr::include_graphics("firenze_intro_ukraine.png")
+```{r out.width="80%"}
+
+knitr::include_graphics("collage_ukraine.png")
 
@@
 
-```{r out.width="70%"}
-
-knitr::include_graphics("firenze_crime.png")
+```{r, out.width='100%'}
+
+knitr::include_graphics("collage.png")
 
@@
 
-- **everyday, medium-term** impact?
 - Which news **content** is effective?
+- **Everyday, medium-term** impact?
 - Effect dependent on individual **predispositions**?
@@
 1. News media influences public opinion by __emphasising certain considerations__ over others.
-3. **Predispositions** structure individual susceptibility.
+2. **Predispositions** structure individual susceptibility.
 
@@
 
-## Accessibility
+## Availability
 
@@
 
-- Experimental research suggests **exposure to consideration mutes effect** of subsequent exposure `r Citep(myBib[c("Druckman2012")])`.
+- Experimental research suggests that **holding a consideration in mind decreases susceptibility to framing** `r Citep(myBib[c("Druckman2012")])`.
 - Hence media content only affects opinions when exposed individual **learns something new**.
@@
 ![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/5/5a/2018-11-07-Julian_Reichelt-Maischberger-1141.jpg/800px-2018-11-07-Julian_Reichelt-Maischberger-1141.jpg)
+
+]
+
+.right-column[
+
+Interesting because:
+
+- **Clearly identifiable short-term-change** in migration coverage.
+- Clear expectations regarding impact.
+- Changing editor was not debated in the media $\rightarrow$ __No co-treatment__! `r Citep(myBib["Spirig2020"])`.
+
+]
+
+---
+## Bild's migration coverage following 2015 III
+
+.left-column[
+
+![](bild_umgebracht_asyl.jpeg)
+![](bild_auslaender.jpeg)
 
@@
 ---
-## Bild's migration coverage following 2015 III
-
-.left-column[
-
-![](bild_umgebracht_asyl.jpeg)
-![](bild_auslaender.jpeg)
-
-]
-
-.right-column[
-
-Interesting because:
-
-- **Clearly identifiable short-term-change** in migration coverage.
-- Clear expectations regarding impact.
-- Changing editor was not debated in the media $\rightarrow$ __No co-treatment__! `r Citep(myBib["Spirig2020"])`.
-
-]
-
----
 
@@
 
-#### Independent Variable `r Citep(myBib["Nicholson2020"], before = "partly following ")`
+#### Independent Variable
 
@@
 - Two-step identification of issue definitions:
-  1. Supervised deep-learning model (BERT) to **select migration content**
-  2. Structural Topic Model to **identify considerations**
+  1. Supervised deep-learning model (BERT) to **select migration content**.
+  2. Structural Topic Model to **identify considerations**.
+
+---
+
+# Identifying migration content
+
+#### Problem: migration content is rare
+
+### Solution: oversample migration content
+
+1. Define **seed dictionary** of migration terms.
+2. Extend dictionary using word embeddings.
+3. Oversample from articles mentioning immigration terms.
+
+---
+
+# Identifying migration content II
+
+<br>
+
+- RA annotates 1800 articles.
+- Fine-tune **German BERT** to identify migration content (accuracy 0.96, F1: 0.94, recall: 0.93, precision: 0.95).
+- Predict label for 2.5M news articles: 90,000 about migration.
+
+---
+
+# Identifying Considerations about Immigration `r Citep(myBib["Nicholson2020"], before = "following ")`
+
+<br>
+
+- Apply **STM** with 60 topics `r Citep(myBib["Roberts2014"])` to identify migration frames.
+- **Annotate** all topics, **select** the ones about crime.
+- Estimate daily prevalence for each newspaper.
 
@@
   theme_xaringan() + 
-  scale_color_discrete(name = "Bild reader", labels = c("Yes", "No"))
+  scale_color_discrete(name = "Outlet", labels = c("Bild", "Other"))
 
@@
 
-## Measurement: News Consumption
-
-<br>
-
-#### Conditioning Variable
+## Measurement: News Consumption and Availability
+
+#### Exposure to Treatment
 
 - Question on newspapers consumed last week.
-- Simple binary variable for DiD-model.
-- Calculate share of migration content devoted to crime for FE model.
-
----
-
-## Measurement: Accessibility
-
-<br>
-
-#### Moderator
-
-- **Initial migration opinion** reflects product of weighted considerations.
-- Those with **liberal migration attitudes** are **less likely to hold crime considerations**.
+- Simple binary variable indicating *Bild* consumption.
+- Alternative: Calculate individual exposure to crime framing.
+
+--
+
+#### Availability
+
+- **Initial migration opinion**.
+- Reporting **migrant crime as MIP**.
 
@@
 # Estimation II
-
-<br>
 
@@
 
-plot_did_ate <- bs_inter_vis(gles_p_long_1617, size = 2, col = "#004A95")  + theme_xaringan()
-plot_did_inter <- bs_inter_vis(gles_p_long_1617, size = 2, col = "#004A95") + theme_xaringan()
-
-plot_did_ate/plot_did_inter
-
-```
-
----
-
-## Conditioning on Accessibility
+gles_p_long <- fread('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/gles/Panel/long_cleaned.csv')
+
+set.seed(42)
+B <- 1000
+
+## no resampling
+gles_p_long <- 
+  gles_p_long %>% 
+  select(lfdn, date_clean, `1130_clean`, wave) %>% 
+  filter(!is.na(`1130_clean`), wave == "1") %>% 
+  mutate(init_mig = `1130_clean`) %>% 
+  select(lfdn, init_mig) %>% 
+  right_join(gles_p_long, by = "lfdn")
+
+## with resampling
+## still need to think about implications of this
+gles_p_long <-
+  gles_p_long %>%
+  select(lfdn, date_clean, `1130_clean`) %>%
+  filter(!is.na(`1130_clean`)) %>%
+  arrange(lfdn, date_clean) %>%
+  group_by(lfdn) %>%
+  slice(1) %>%
+  mutate(init_mig_res = `1130_clean`) %>%
+  select(lfdn, init_mig_res) %>%
+  right_join(gles_p_long, by = "lfdn")
+
+gles_p_long <- 
+  gles_p_long %>% 
+  mutate(mip_mig_crime_lag = lag(mip_mig_crime)) %>% 
+  filter(!is.na(mip_mig_crime)) %>% 
+  arrange(lfdn, date_clean) %>% 
+  group_by(lfdn) %>% 
+  filter(wave == "1") %>% 
+  mutate(mip_mig_crime_init = mip_mig_crime) %>% 
+  select(lfdn, mip_mig_crime_init) %>% 
+  right_join(gles_p_long, by = "lfdn")
+
+gles_p_long <- 
+  gles_p_long %>% 
+  filter(wave == "1") %>% 
+  mutate(bild_init = ifelse(is.na(`1661a_clean`), NA, `1661a_clean` > 0)) %>% 
+  select(bild_init, lfdn) %>% 
+  right_join(gles_p_long, by = "lfdn")
+
+gles_p_long <- 
+  gles_p_long %>% 
+  arrange(lfdn, date_clean) %>% 
+  group_by(lfdn) %>% 
+  slice(1) %>% 
+  mutate(treat_alt = ifelse(is.na(`1661a_clean`), NA, `1661a_clean` > 0)) %>% 
+  select(treat_alt, lfdn) %>% 
+  right_join(gles_p_long, by = "lfdn")
+
+## vis dv by treatment group and conditioning var
+
+did_desc_plot <- 
+  gles_p_long %>%
+  filter(date_clean < as.Date("2018-01-01")) %>% 
+  filter(!is.na(`1130_clean`) & !is.na(bild_init)) %>% 
+  mutate(init_mig_cat = 
+           case_when(
+             init_mig > 0 ~ "01 - Conservative",
+             init_mig == 0 ~ "02 - Neutral",
+             init_mig < 0 ~ "03 - Liberal"
+           )) %>% 
+  group_by(bild_init, wave, init_mig) %>% 
+  select(`1130_clean`, date_clean) %>% 
+  summarise(dv = mean(`1130_clean`, na.rm = T),
+            dv_sd = sd(`1130_clean`, na.rm = T),
+            date_min = min(date_clean, na.rm = T),
+            n_resps = n()) %>%
+  mutate(
+    lower = dv + qt(0.025, n_resps - 1) * (dv_sd/sqrt(n_resps)),
+    upper = dv + qt(0.975, n_resps - 1) * (dv_sd/sqrt(n_resps))
+  ) %>% 
+  ggplot(aes(date_min, dv, ymin = lower, ymax = upper, col = !bild_init, fill = !bild_init)) +
+  geom_line() +
+  geom_ribbon(alpha = 0.5) +
+  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") +
+  facet_grid(~init_mig) +
+  ggtitle("Average migration opinion dependent on initial migration opinion", 
+          "Bild vs. other major daily newspapers, 2016-2017") + 
+  xlab("Date") + ylab("Migration Opinion") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+ggsave("C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/paper/vis/did_descriptive.svg",
+       did_desc_plot,
+       device = "svg", width = 10, height = 6)
+
+gles_p_long_1617 <- 
+  gles_p_long %>% 
+        filter(date_clean >= as.Date("2016-01-01"),
+               date_clean <  as.Date("2018-01-01"))
+
+rm(gles_p_long)
+
+gles_p_long_1617$dv <- gles_p_long_1617$`1130_clean`
+gles_p_long_1617$treat <- gles_p_long_1617$bild_init
+gles_p_long_1617$post <- gles_p_long_1617$date_clean>= as.Date("2017-02-01")
+
+# model 1: direct effect
+ate <- 
+  feglm(dv ~ post * treat, 
+      cluster = c("lfdn"), 
+      data = gles_p_long_1617)
+
+inter <- 
+  feglm(dv ~ post * treat * init_mig, 
+      cluster = c("lfdn"), 
+      data = gles_p_long_1617)
+
+points <- ate$coefficients
+ests <- cbind(points, confint(ate))
+
+plot_did_ate <- 
+  ests %>%
+  filter(row.names(.) == "postTRUE:treatTRUE") %>% 
+  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
+  geom_pointrange(size = 2) +
+  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
+  ylab("") + xlab("Estimate") +
+  xlim(-0.1, 0.3) + 
+  scale_y_discrete(labels = rev(c("DiD"))) +
+  ggtitle("Average treatment effect") + 
+  theme_xaringan()
+
+points <- inter$coefficients
+ests <- cbind(points, confint(inter))
+
+plot_did_inter <- 
+  ests %>% 
+  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig")) %>% 
+  mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
+  ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
+  geom_pointrange(size = 2) +
+  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
+  ylab("") + xlab("Estimate") +
+  ggtitle("DiD-estimate with interaction") +
+  xlim(-0.1, 0.3) + 
+  scale_y_discrete(labels = rev(c("DiD", "DiD X Initial Opinion"))) +
+  ggtitle("Heterogenous treatment effects") + 
+  theme_xaringan()
+
+did_groups <- 
+  gles_p_long_1617 %>% 
+  filter(!is.na(treat), !is.na(init_mig)) %>%
+  group_by(treat, post, init_mig) %>% 
+  summarise(
+    dv_point = mean(dv, na.rm = T)
+    ) %>% 
+  filter(post) %>% 
+  pivot_wider(
+    names_from = treat,
+    values_from = dv_point
+  ) %>% 
+  mutate(difference = `TRUE` - `FALSE`) %>% 
+  ggplot(aes(x = init_mig, y = difference)) +
+  geom_col() + 
+  theme_xaringan() + xlab("") + ylab("") +
+  ggtitle("Effect across initial migration attitude")
+
+load('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/did_bootstraps.RData')
+
+direct <- coef(inter)["postTRUE:treatTRUE"]
+interact <- coef(inter)["postTRUE:treatTRUE:init_mig"]
+
+did_bootstrap <- 
+  ggplot() +
+  geom_histogram(data = gles_p_long_1617 %>% filter(wave == "1"), mapping = aes(x = init_mig, after_stat(density)), alpha = 0.4, bins = 8) +
+  geom_abline(data = bs_did_ests, aes(slope = IA, intercept = DiD, group = boots), alpha= 0.05) +
+  geom_abline(slope = interact, intercept = direct, col = "red") +
+  geom_hline(yintercept = 0, col = "black") +
+  scale_x_continuous(limits=c(-3,3)) +
+  scale_y_continuous(limits=c(0,.6)) +
+  ggtitle(paste0(B, " bootstrap estimates of heterogenous treatment effect")) +
+  ylab("Estimate") + xlab("Initial migration attitude") +
+  theme_xaringan()
+
+ggsave(plot = did_bootstrap,
+       filename = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/paper/vis/DiDXinit_imm.svg', device = "svg")
+
+plot_did_ate / plot_did_inter
+
+```
+
+---
+
+## Conditioning on Availability
 
@@
 
-DiD_bs(gles_p_long_1617) +
-  theme_xaringan()
+did_bootstrap
 
@@
 
-DiD_groups(gles_p_long_1617) +
-  theme_xaringan()
+did_groups
 
@@
 
+# Moderator: MIP
+
+```{r}
+
+# DiD
+# model 1: direct effect
+ate <- 
+  feglm(dv ~ post * treat, 
+      cluster = c("lfdn"), 
+      data = gles_p_long_1617)
+
+inter <- 
+  feglm(dv ~ post * treat * mip_mig_crime_init, 
+      cluster = c("lfdn"), 
+      data = gles_p_long_1617)
+
+points <- ate$coefficients
+ests <- cbind(points, confint(ate))
+
+plot_did_ate <- 
+  ests %>%
+  filter(row.names(.) == "postTRUE:treatTRUE") %>% 
+  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
+  geom_pointrange(size = 2) +
+  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
+  ylab("") + xlab("Estimate") +
+  scale_y_discrete(labels = rev(c("DiD"))) +
+  ggtitle("Average treatment effect") + 
+  theme_xaringan()
+
+points <- inter$coefficients
+ests <- cbind(points, confint(inter))
+
+plot_did_inter <- 
+  ests %>% 
+  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:mip_mig_crime_initTRUE")) %>% 
+  mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
+  ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
+  geom_pointrange(size = 2) +
+  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
+  ylab("") + xlab("Estimate") +
+  ggtitle("DiD-estimate with interaction") +
+  scale_y_discrete(labels = rev(c("DiD", "DiD X Initial Opinion"))) +
+  ggtitle("Heterogenous treatment effects") + 
+  theme_xaringan()
+
+plot_did_ate/plot_did_inter
+
+```
+
+---
+
 # Summary
@@
 
+- Media **content affects attitude** formation.
 - **ATE is null** when not moderating with prior attitude.
-- **Conservatives do not react** to increased crime framing.
-- Is this a ceiling effect? No, because:
-  - results hold when comparing among conservative outlets
-  - Conservatives react to other frames (ISIS, cues by party elites)
-
----
-
-# Conclusion
+- Effect conditioned by **Prior availability** of consideration.
+
+### $\rightarrow$ Attitude is a **product of information and predisposition** `r Citep(myBib["Zaller1992"])`.
+
+---
+
+# Limitations
 
@@
 
-- Media **content affects attitude** formation.
-- **Effect is conditional** on pre-existing attitude.
-
-## $\rightarrow$ Attitude is a **product of information and predisposition** `r Citep(myBib["Zaller1992"])`.
-
----
-
-# Limitations
-
-<br>
-
 #### Unclear:
 
-- how important these effects are in **more fragmented media landscapes**,
-- which content affects **which groups**,
-- which **other actors** can affect framing in the media.
+- How important are these effects in **more fragmented media landscapes**?
+- Which content affects **which groups**?
+- Which **other actors** can affect framing in the media?
 
@@
 ```
-
----
-
-## Identify Migration Content
-
-<br>
-
-- Annotate 1800 articles to identify their migration content.
-- Fine-tune German BERT deep-learning classifier.
-- accuracy: 95.5% (F1: 0.94, recall: 0.93, precision: 0.95)
-- 13.5k out of 400k articles in 2017 about migration (3.5\%)
-
----
-
-## Measure Considerations about Migration
-
-<br>
-
-- Estimate 60-topic structural topic model on identified migration articles `r Citep(myBib["Roberts2014"])`.
-- using date and paper as covariates `r Citep(myBib["Nicolls2020"])`.
-- Annotate.
-- Select crime-related considerations.
 

### 2022-06-28 pres/Abstract.Rmd
Update pres as well
pray

---
title: "Assessing Media Influence in Contemporary News Environments"
author: "Nicolai Berk"
date: "`r Sys.Date()`"
output: pdf_document
abstract: "A large body of literature debates the extent to which media consumption affects consumers' issue attitudes and voting behaviour in contemporary news environments. Studies arguing that the media has minimal influence on opinion formation have often used designs estimating the effects of novel, previously unconsumed content on participants' attitudes. However, experimental evidence suggests that media consumers discount the bias of different outlets. Additionally, most studies assume rather than measure the extent of newspaper bias. I address both shortcomings with observational evidence exploiting a change in migration framing following an editorial shift in Germany's largest tabloid, *Bild*. The study combines panel data with state-of-the-art methods of text analysis and assesses the effect of changing migration frames in respondents' media diet on their attitudes towards migration. Results across different specifications indicate that even when assessing within-newspaper changes in issue framing, no effect on attitudes or voting behaviour can be found. These findings add further evidence that short-term media effects in the viewers choice era are limited."
subtitle: Right-wing Media, Crime, and Anti-Immigration Attitudes
bibliography: PhD-Proposal.bib
institute: Humboldt Universität Berlin
---

### 2022-06-28 pres/Presentation.Rmd
Update pres as well
pray

---
title: "Framing Effects in the Wild"
subtitle: "How the News Media Shapes Public Opinion by Defining Political Issues"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: true
      ratio: 16:9
    includes:
      after_body: insert-logo.html
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#004A95", background_color = "#bfbfbf",
  base_font_size = "32px",
  header_h1_font_size = "1.3rem",
  header_h2_font_size = "1.2rem",
  header_h3_font_size = "1.05rem",
  footnote_font_size = "0.75rem",
  header_font_google = google_font("Lato", '700'),
  text_font_google   = google_font("Lato", "400"),
  code_font_google   = google_font("Fira Mono")
)

```

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear",
           cite.style = "authoryear",
           style = "markdown",
           hyperlink = FALSE,
           max.names = 2, 
           longnamesfirst = F,
           dashed = FALSE)
myBib <- ReadBib("C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib", check = FALSE)
```

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE, 
  message = F, 
  warning = F, 
  cache = F, 
  out.width="90%", 
  fig.height=8, 
  fig.width=15, 
  fig.align='center', 
  eval = T, 
  dev = "svg"
  )
# knitr::opts_knit$set(root.dir = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild')

library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)
library(lubridate)
library(patchwork)
library(here)

# load self-made functions
for (filename in list.files(here("code/functions"))){
  source(here(paste0('code/functions/', filename)))
}

```

class: inverse, center, middle

# Framing Effects in the Wild

### Does News Framing Affect Public Opinion?

#### Nicolai Berk<sup>*</sup>

Presentation prepared for the $12^{th}$ Annual Conference of the European Political Science Association in Prague

25.06.2022

.left[.footnote[<sup>*</sup> Dynamics RTG & Humboldt Universität Berlin]]

---

## A classic framing experiment

### Would you support increased welfare spending...

.pull-left[

### in order to support the poor?

```{r hista}

resps <- 
  rnorm(1000, 1.5, 2) %>% 
  round() %>% 
  ifelse(. < -3, -3, .) %>% 
  ifelse(. > 3, 3, .) %>% 
  as_tibble()

resps %>% 
  ggplot(aes(x = value)) +
  geom_histogram() +
  xlab("") +
  geom_vline(xintercept = mean(resps$value), lty = 2, col = "red", size = 2) +
  theme_xaringan()

```

]

.pull-right[

### even if it means higher taxes?

```{r histb}

resps <- 
  rnorm(1000, -1.5, 2) %>% 
  round() %>% 
  ifelse(. < -3, -3, .) %>% 
  ifelse(. > 3, 3, .) %>% 
  as_tibble()

resps %>% 
  ggplot(aes(x = value)) +
  geom_histogram() +
  xlab("") +
  geom_vline(xintercept = mean(resps$value), lty = 2, col = "red", size = 2) +
  theme_xaringan()

```

]

.footnote[(Very liberal after Sniderman and Theriault 2004)]

---

## Are framing experiments externally valid?

<br>

- Plenty of evidence from experiments <font size="5" color="#004A95"> `r Citep(myBib[c("Busby2019", "Leeper2020")])` </font>
- But limited capacity to emulate real world environments <font size="5" color="#004A95"> `r Citep(myBib[c("Barabas2010")])` </font>.
- Strongest theoretical critique: **selective exposure** <font size="5" color="#004A95"> `r Citep(myBib[c("Bennett2008", "Lau2021a")])` </font>.

--

### "A more balanced reading [...] requires methodological diversification, experiments and studies oriented to the world outside” <font size="5" color="#004A95"> `r Citep(myBib[c("Kinder2007")], after = ": 157")` </font>.

---

# Evidence from Observational Studies

<br>

- Few observational studies with mixed findings and endogeneity concerns <font size="5" color="#004A95"> `r Citep(myBib[c("Jerit2008", "Jerit2009")])` </font>.
- Causal inference work not concerned with framing <font size="5" color="#004A95"> `r Citep(myBib[c("Durante2012", "Foos2020", "Martin2017", "Spirig2020")])` </font>.

--

<br>

## No observational studies assessing causal effect of framing!

---

## What is necessary for the study of framing effects?

<br>

# 1. Precisely identifiable, sharp change of frames in communication.
# 2. Good measure of frames in mind.

---

class: inverse, center, middle

# Case

---

## Bild's migration coverage following 2015

.left-column[

```{r bildlogo, out.width = "50%"}

knitr::include_graphics("https://upload.wikimedia.org/wikipedia/commons/thumb/e/e3/Logo_BILD.svg/848px-Logo_BILD.svg.png")

```

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/5/5a/2018-11-07-Julian_Reichelt-Maischberger-1141.jpg/800px-2018-11-07-Julian_Reichelt-Maischberger-1141.jpg)

]

.right-column[

<br>

- Editorial change in the largest German tabloid newspaper, **Bild**.
- Increasingly **framed migrants as criminals** <font size="5" color="#004A95"> `r Citep(myBib[c("Niggemeier2018Bild")])`</font>.
- Potentially exogenous timing.

]

---

## Bild's migration coverage following 2015

.left-column[

```{r bildlogo2, out.width = "50%"}

knitr::include_graphics("https://upload.wikimedia.org/wikipedia/commons/thumb/e/e3/Logo_BILD.svg/848px-Logo_BILD.svg.png")

```

![Source: Wikipedia](https://upload.wikimedia.org/wikipedia/commons/thumb/5/5a/2018-11-07-Julian_Reichelt-Maischberger-1141.jpg/800px-2018-11-07-Julian_Reichelt-Maischberger-1141.jpg)

]

.right-column[

### Interesting because:

- **Clearly identifiable short-term-change** in migration coverage.
- Clear expectations regarding impact.
- Change not debated in the media $\rightarrow$__No co-treatment__! <font size="5" color="#004A95"> `r Citep(myBib["Spirig2020"])`</font>.

]

---

class: inverse, center, middle

# How does this affect migration attitudes?

---

## Theoretical Expectations

.pull-left[

![](vis/CognitiveStorage.png)

]

.pull-right[

### Increased exposure to crime frames will lead to...
- H1: **more conservative** attitudes towards migration.
- H2: **stronger association** of crime and migration attitudes.

]

---

class: inverse, center, middle

# Measurement & Estimation

---

## Frames in Communication

- Collected 2.5M news articles from major German daily newspapers' websites.
- Two-step identification of crime frames:
  1. **Select migration content**:
    + Generate dictionary, oversample migration content.
    + Annotate 1800 articles.
    + Supervised deep-learning model (BERT) to **identify migration content**.
  2. **Select crime frames**.
    + Same, but subset of articles about migration content.

---

## A sharp, identifiable change in frames in communication

```{r trendplot, cache = F}

TreatmentTrendPlot(size = 2, 
                   cntrl_col = "#004A95", 
                   treat_col = "#cc0000") +
  theme_xaringan()

```

---

## Frames in Mind

German Longitudinal Election Study (GLES) Panel <font size="5" color="#004A95"> `r Citep(myBib["GLES2017Panel"])`</font>.

.pull-left[

### Immigration Attitudes
- **Opportunities for immigration** of foreigners should be 
  + extended (-3) or
  + restricted (3).
- Asked in **13** waves (1 pre).

]

.pull-right[

### Integration Attitudes
- Foreigners should...
  + completely **adapt to German culture** (-3) or
  + be able to live according to their own culture (3).
- Asked in **4** waves (1 pre)

]

---

## Frames in Mind (continued)

.pull-left[

### Support for radical-right AfD
- Attitude towards **AfD**
  + strongly dislike (-5) to
  + strongly like (5).
- Asked in **14** waves (1 pre)

### MIP: Migration
- Binary indicator, 1 if most important problem is migration.

]

.pull-right[

### Attitude towards crime policy
- "state should get **more competences in fighting crime**, even if this means more surveillance"
  + strongly disagree (1) to
  + strongly agree (5).
- Asked in **4** waves (1 pre)

]

---

## Estimation

### Difference-in-Differences Design

$$y_{it} = \delta * Post_t *  Bild_i + \lambda * Post_t + \rho_i +  \epsilon_{it}$$

.pull-left[

```{r didtheory}

data.frame(
  X = factor(c("pre", "pre", "post", "post", "pre", "post"),
             levels = c("pre", "post")),
  Y = c(1.1, 1.3, 1.5, 1.9, 1.3, 1.7),
  universe = factor(c(rep("counterfactual", 4), rep("factual", 2)),
                    levels = c("counterfactual", "factual")),
  group = factor(c("untreated", "treated", "untreated", 
                   "treated", "untreated", "untreated"),
                 levels = c("treated", "untreated"))
) %>% 
  ggplot(aes(x = X, y = Y, 
             lty = universe, col = group,
             group = paste0(universe, group))) +
  geom_line(size = 2) + 
  geom_point(size = 6) +
  ylab("") + xlab("") +
  theme(axis.text.y = element_blank(), 
        legend.position = "None") +
  theme_xaringan()

```

]

.pull-right[

- Compare those reading *Bild* in W1 to *never*-readers.
- ATT = $\Delta$ attitude Bild readers - $\Delta$ control group.

]

---

class: inverse, center, middle

# Results

---

## Effect on Immigration Attitudes

<br>

```{r singledv, fig.height=3}

EffectPlot(multi = F, scaled = "raw", size = 2) +
  theme_xaringan()

```

.footnote[(Green lines indicate effect equivalent to 5% of scale. Effect size in `r Citep(myBib["Nelson1997Rally"])`: 0.65/11% of scale.)]

---

## Effect of Changing Framing on Alternative DVs

```{r multidv}

EffectPlot(multi = T, scaled = T, size = 2) +
  theme_xaringan()

```

---

## Effect on Migration Attitudes across Waves

```{r migwaves}

EffectByWavePlot(size = 2) +
  theme_xaringan()

```

---

## Effect on other Attitudes across Waves

.pull-left[

### Crime

```{r crimewaves}

EffectByWavePlot("2880h_clean", size = 2) +
  theme_xaringan()

```

]

.pull-left[

### Integration

```{r intwaves}

EffectByWavePlot(dv = "1210_clean", size = 2) +
  theme_xaringan()

```

]

---

## Effect on other DVs across time I

.pull-left[

### AfD Vote

```{r afdwaves}

EffectByWavePlot(dv = "430i_clean", size = 2) +
  theme_xaringan()

```

]

.pull-left[

### MIP: Migration

```{r mipwaves}

EffectByWavePlot(dv = "mip_mig", size = 2) +
  theme_xaringan()

```

]

---

## Association of Immigration and Crime Attitudes

```{r corplot}

MigCrimeCorPlot(size = 2) +
  theme_xaringan()

```

---

## Selecting out

<br>

- No change in association of migration attitudes and Bild readership.
- No differential out-selection across prior attitudes.

---

## Takeaways

<br>

## 1. News framing effects do not easily translate into real world.

- Questions external validity of decades of framing studies.
- Single media outlets have limited influence on public opinion.

## 2. Media effects literature should pay more attention to precise changes in *content*.

---

class: inverse, center, middle

## Fin

### This research is generously funded by

```{r out.width="50%"}

knitr::include_graphics("vis/banner_new.png")

```

```{r out.width="50%"}

knitr::include_graphics("vis/dfg_logo_englisch_blau_en.jpg")

```

---

# Resources I

.footnote[

```{r refs, echo=FALSE, results="asis", cache=FALSE}

PrintBibliography(myBib, end = 4)

```

]

---

# Resources II

.footnote[

```{r refstwo, echo=FALSE, results="asis", cache=FALSE}

PrintBibliography(myBib, start = 5, end = 8)

```

]

---

# Resources III

.footnote[

```{r refsthree, echo=FALSE, results="asis", cache=FALSE}

PrintBibliography(myBib, start = 9)

```

]

### 2022-06-28 pres/Quick Modeling Summary for WIll/Quick Modeling Summary for WIll.Rmd
Update pres as well
pray

---
title: "Modeling Report for Will"
author: Nicolai Berk
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE, 
  message = F, 
  warning = F, 
  cache = T, 
  # out.width="80%", 
  fig.height=4, 
  fig.width=6, 
  fig.align='center', 
  eval = T, 
  dev = "svg"
  )
# knitr::opts_knit$set(root.dir = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild')

library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)
library(lubridate)
library(patchwork)
library(here)

# load self-made functions
for (filename in list.files(here("code/functions"))){
  source(here(paste0('code/functions/', filename)))
}

```

# OLS

```{r did_imm_att}

DiDModels(dv_name = "1130_clean", 
          ctrl_var  = "cond",
          ctrl_name = "Initial Migration Att.")

```

---

# Tobit (no FEs, no Clustering)

```{r tobit_direct, results = 'markup'}

TobitDiD("1130_clean")

```

---

# Effect dependent on prior position

```{r}

InterLinear()

```

---

# Descriptive Plot

```{r}

DiDDist()

```

---

# Current Questions

- Interaction effect seems like an artifact?
- Main problem the inclusion of FEs similar to e.g. `fixest`.
- Seems like best estimation strategy is ordinal logit/probit.

### 2022-06-28 pres/20210503/vis/gles_treatment_plot.R

@@ -1,0 +1,63 @@
+library(tidyverse)
+
+header <-  c("survey", "unit", "start_date", "end_date")
+schedule <- t(data.frame(
+  a = c("LT tracking", "T27", "27.02.2015", "07.03.2015"),
+  b = c("LT tracking", "T28", "05.06.2015", "19.06.2015"),
+  c = c("LT tracking", "T29", "11.09.2015", "25.09.2015"),
+  d = c("LT tracking", "T30", "04.12.2015", "18.12.2015"),
+  e = c("LT tracking", "T31", "26.02.2016", "11.03.2016"),
+  f = c("LT tracking", "T32", "03.06.2016", "17.06.2016"),
+  g = c("LT tracking", "T33", "19.08.2016", "02.09.2016"),
+  h = c("LT tracking", "T34", "02.12.2016", "16.12.2016"),
+  i = c("LT tracking", "T35", "17.03.2017", "31.03.2017"),
+  j = c("LT tracking", "T36", "16.06.2017", "30.06.2017"),
+  k = c("LT tracking", "T37", "12.09.2017", "23.09.2017"),
+  l = c("LT tracking", "T38", "01.12.2017", "15.12.2017"),
+  m = c("Panel", "Wave 1", "06.10.2016", "11.10.2016"),
+  n = c("Panel", "Wave 2", "16.02.2017", "03.03.2017"),
+  o = c("Panel", "Wave 3", "11.05.2017", "23.05.2017"),
+  p = c("Panel", "Wave 4", "06.07.2017", "09.08.2017"),
+  r = c("Panel", "Wave 5", "17.08.2017", "28.08.2017"),
+  s = c("Panel", "Wave 6", "04.09.2017", "13.09.2017"),
+  t = c("Panel", "Wave 7", "18.09.2017", "23.09.2017"),
+  u = c("Panel", "Wave 8", "27.09.2017", "09.10.2017"),
+  v = c("Panel", "Wave 9", "15.03.2018", "26.03.2018"),
+  w = c("Panel", "Wave 10", "06.11.2018", "31.01.2019"),
+  x = c("Panel", "Wave 11", "28.05.2019", "08.07.2019"),
+  y = c("Panel", "Wave 12", "05.11.2019", "17.12.2019"),
+  z = c("Panel", "Wave 13", "21.04.2020", "01.06.2020")
+)) %>% 
+  as.data.frame()
+
+colnames(schedule) <- header
+
[…]

### 2022-06-28 paper/Manuscript_Framing.Rmd
Revert "Delete paper directory"
This reverts commit b3ea5c81fc5d1df3344229a23a919c1f6b27542d.

---
title: "Framing Effects in the Wild: How the News Media Shapes Public Opinion by Defining Political Issues"
author: "Nicolai Berk"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: false
    fig_caption: yes
    includes:
      in_header: preamble.tex
subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
fontsize: 12pt
geometry: margin=1.5in
abstract: "A vast body of research is devoted to the persuasive effects of news framing. However, the study of the effects of framing has almost exclusively taken an experimental approach, with limited external validity. Existing observational work has so far mostly studied correlational data or assessed 'media effects' broadly. I contribute to these bodies of research by exploiting a unique case from Germany, where an editorial change in Germany's largest tabloid - *Bild* - led to a substantial shift in the paper's migration framing. Combining panel data from over 15,000 individuals with content analysis of 2.5 million newspaper articles using transformer models and a difference-in-differences design, I show that a substantial increase in the emphasis of crime in migration coverage did not affect immigration attitudes, nor did it increase the association of migration attitudes with attitudes about crime. These findings question the generalizability of framing effects research and add to a recent body of empirical studies questioning the role of the news media for opinion formation in the twentyfirst century."
bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
---

```{r setup, include = F}

knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = F, fig.height=6, fig.width=10, fig.align='center', eval = T)

library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)
library(lubridate)
library(patchwork)
library(here)
library(censReg)

# load self-made functions
for (filename in list.files(here("code/functions"))){
  source(here(paste0('code/functions/', filename)))
}

```

*I am thankful for extensive feedback on earlier stages of this draft from Christian Arnold, Daniel Bischof, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Felix Hagemann, Julian Heid, Christina Gahn, Matthew Levendusky, Heike Klüver, Thomas M. Meyer, Rune Slothuus, Antonio Valentim as well as participants in the EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI, CompText Conference 2022, and the Political Behaviour Section at Aarhus University.*

# Introduction: Does Framing Matter?

The persuasiveness of the news media has been a fixation of research on political communication and public opinion for at least the past 100 years. One of the largest fields within this literature is concerned with framing effects. A huge body of experimental evidence suggests that citizens substantially alter their issue attitudes when presented with different frames [@Busby2019; @Chong2007b; @Leeper2020; @Nelson1997Rally; @sniderman2004structure; @Slothuus2008a]. However, there is little research investigating whether these findings translate into a messy reality [@Barabas2010], where frames are communicated by specific actors, and citizens self-select into media outlets, potentially shielding them from some frames and exposing them to others.

In fact, many researchers argue that the effects of media content on attitudes are minimal. Observational research on media effects is abundant [@Broockman2022; @Durante2012; @Foos2022; @Grossman2022; @Guess2021; @Levendusky2022; @Martin2017; @Spirig2020], but has rarely paid attention to the precise content affecting issue attitudes [see @Djourelova2020 for an exception]. To the authors knowledge, no existing observational study assesses the causal effect of changing news framing on issue attitudes.

I address this gap in the literature by presenting evidence from an editorial change in the largest German tabloid *Bild*, resulting in an increasing emphasis of crime in the paper's migration coverage. The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet changed it's framing while other papers maintained theirs. By employing BERT models for the measurement of crime frames in a corpus of 2.5 million newspaper articles, I am able to clearly identify the treatment - something that is usually left to experimental studies. Coupling this data with a large-scale panel survey of over 15,000 individuals allows the precise estimation of this framing effect with a difference-in-differences design.

The results show that emphasis framing does not affect citizens' political attitudes in the real world. The influence of the news media on opinion formation in contemporary news environments with high levels of consumer choice and diverse exposure seems to be rather limited. Similarly, the study contributes to the media effects literature by investigating the effects of changing news *content* on public opinion, independent of the effects of the changing availability of news *outlets*. More generally, this research has important implications for our understanding of contemporary democracies, questioning the role of the media in public opinion formation.

The paper will proceed as follows: in the next section I will briefly discuss the existing literature on framing and media effects, before describing the theoretical framework and research design, including case, measurement, and estimation strategy. The results section will then showcase findings from difference-in-differences and fixed-effect models assessing the impact of increased emphasis of crime in news coverage about migration, both on the association of attitudes about crime with attitudes about migration, as well as migration attitudes themselves. Lastly, I discuss the wider implications of the findings for the study of framing effects and the role of the news media in the opinion formation process.

# Framing Effects vs. Media Effects

<!-- look at rune's comments regarding this chapter - keep focusing on framing effects literature -->

Research on framing has shown for decades that citizens' attitudes are highly reactive to minor changes in question wording and emphasis of specific considerations. However, it remains unclear how well these experimental findings translate into the real world, where citizens self-select into media content, receive cues from political actors, and are usually more concerned with their private lifes than politics. Scholarly effort has therefor been devoted to test the conditions under which framing effects materialize, designing experiments which emulate different aspects of real-world environments. For example,it has been shown that exposure to conflicting frames can serve to strengthen the effect of frames one was earlier exposed to, dependent on individual preconditions [@Bechtel2015; @Chong2013; @Druckman2012]. Others have assessed what influence the sender of a frame has and shown that the effects of framing are more pronounced when the sponsor of the frame is from one's own party [@Druckman2001; @Slothuus2010b; @Slothuus2010]. Lastly, concerns about the duration of framing effects have been addressed by some experimental research showing that those effects can last at least several weeks [@Lecheler2011]. (missing here: Lau et al)

While these findings enable a better understanding about individuals’ susceptibility to framing effects in real-world environments, the literature almost exclusively provides us with experimental evidence. Experiments can only incorporate few characteristics at a time and are limited to emulate a realistic environment for the study of news framing. As Donald Kinder puts it: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception. [...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157]. In order to test the external validity of framing effect studies, it is necessary to study observational data.

This call for an assessment of framing effects beyond experimental studies has been echoed by various scholars over time [@Busby2019; @Leeper2020], yet rarely been answered. Existing research is often riddled with endogeneity concerns, co-treatment or concerned with media effects broadly, instead of assessing framing effects specifically. For example, @Jerit2008 investigates the effects of framing on public opinion compared to addressing the opponents issue. She finds that reframing is less effective than engagement with the opposite parties' frames, a finding that suggests that framing is not very effective. However, this study does not try to identify causal effects, but restricts itself to the assessment of correlational evidence. Others show with similar correlational designs that only specific frames seem to drive issue importance [@Mclaren2018], but do not assess effects on attitudes.

Other work has put more emphasis on causal identification of media effects using quasi-experimental designs, but paid less attention to the precise definition of the independent variable. This literature has
usually exploited changes in news media markets such as boycotts of certain
outlets [@Foos2022], entries of new outlets [@DellaVigna2007; @Grossman2022], changing TV channel positions [@Martin2017], or partisan takeovers of news outlets [@Durante2012; @Levendusky2022; @Spirig2020] to estimate the effects of changing news exposure on political behavior. Interestingly, the results diﬀer across studies. While some studies find substantial effects of exposure to slanted media on political attitudes and voting behavior even in the long run [@Foos2020; @Grossman2022], others find that consumers switch outlets when the slant of currently consumed news changes [@Durante2012; @Spirig2020].

Another approach is to assess consumer reactions to news content through ﬁeld
experiments. In this setup, consumers are randomly assigned to speciﬁc news
outlets and the development of their political attitudes is assessed. @Guess2021, for example, randomly assigned individuals to receive content from a left-leaning or a right-leaning news outlet in their online news feeds. Similar studies have assessed the ffects of cross-partisan content on TV [@Broockman2022] and social media [@Bail2018]. This literature provided
contradicting results as well: while some found liberalizing effects of liberal
content [@Broockman2022], others found no effects [@Guess2021], or even partisan backlash (i.e. individuals becoming even more conservative in response to liberal content; @Bail2018).

I argue this lack of consensus regarding the effects of media content is at least partly related to a lack of precision in the definition of the independent variable. The vast majority of studies in this literature observes or manipulates the consumed *outlet* , rather than the *content*. This is problematic for three main reasons. First, by assuming a stable 'slant' of specific news outlets, it remains unclear which content consumers actually react to (or not). While it is certainly true that news outlets have a certain political leaning, there is variation in how political and how persuasive specific news content is. Second, citizens are often aware of outlets' political leaning. @Baum2008a showed that consumers place the same news content more left- or right-leaning, dependent on wether it was presented as Fox news or CNN content. This implies that citizens should be able to discount political bias of outlets (muting potential effects of biased content) or might show motivated responses to content they perceive as motivated by political motives (e.g. backlash to opposing news sources). Third, by focusing on the effects of the consumption of different outlets, the literature studies a process unlikely to be observed in the real world - after all, changes in the makeup of media markets are extremely rare and switches from one partisan outlet to an opposing partisan outlet even more so. The main influence of news editors on public opinion should be exercised by editing the everyday content of news, rather than changing the consumer base of their outlets.

To my knowledge, there are only two observational studies assessing the causal effect of exposure to specific content on political attitudes. @Slothuus2010b takes advantage of a sudden shift in a political parties' framing of retirement benefits, and shows that this changed framing has substantial impact on party supporters' attitudes about the issue. However, it is unclear how these findings translate to news framing effects, as it is impossible to distinguish the effect of partisan cue-taking from the persuasive effect of the frame itself. The only study which assesses the precise impact of changing news content on political attitudes comes from @Djourelova2020. She exploits a ban of the term "illegal migrant" in the *Associated Press* and shows that this language has modest effects migration attitudes. While the study itself reveals impressively how language can shape political attitudes, it constitutes a highly specific case and a rather minor change in the framing of migration. While news stories might lack the term "illegal migrant", they might still extensively cover crimes committed by migrants and thus associate migration with crime.

Summarized, we lack an understanding of how framing affects political opinions in the real world. While experimental evidence suggests rather strong effects, it is unclear how these findings travel outside the lab. Observational evidence on media effects is abundant but has not studied precisely what the impact of framing is. The present study therefor exploits a naturally occurring change in the news framing of a particular issue *within* a specific outlet to isolate the effects of news framing on political opinions.

# Emphasis Framing and the Value-Expectancy Model

”Framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy” [@Nelson1997Rally]. A ”frame” is then the operating unit of this process, defining the issue at hand in a specific way. Different forms of frames have been conceptualised. When I talk about ’frames’ here, I refer to *emphasis frames*. These frames emphasise certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame [@Leeper2020, 152]. For example, issues of increasing welfare contributions might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes. Individuals’ support of a statement will differ dependent on the frame presented [@sniderman2004structure].

Work using the emphasis framing concept of framing - as opposed to other definitions like equivalence frames [@Kahneman1979prospect], episodic frames [@Iyengar2005], or generic frames [@DeVreese2005] - mostly builds on the expectancy-value model developed by @Ajzen2000. This model suggests that an attitude on a given issue is a function of two things: considerations relating to that object and their respective weights. The evaluation of the issue is subdivided into a number of considerations, which will carry clear evaluations. For example, to form an opinion about whether immigration to one's country should be restricted, a person might consider the humanitarian conditions in the countries of origin (negative consideration regarding restrictive migration policy), as well as the risk of increased crime (positive consideration; note that the model does not differentiate whether a consideration is grounded in objective reality). Individuals weigh each of these considerations to form an overall opinion on the subject.

Figure \ref{fig:cogStor} visualizes this logic. A given issue is associated with an attitude $y$. The issue is related to a number of different considerations, each of which carries an associated evaluation $x_i$, e.g. that crime is bad. Each of these considerations is more or less associated with the issue. Based on the strength of this association $w_i$, a given consideration's evaluation is more or less reflected in the issue evaluation $y$, which is equal to the weighted sum of considerations.

```{=tex}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{vis/CognitiveStorage.png}
    \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}
    \label{fig:cogStor}
\end{figure}
```

According to this model, framing changes opinions by changing the association of a single consideration with the issue at hand. As a result, a specific consideration factors more prominently in an individuals' attitude formation process: "media frames influence opinions by stressing specific values, facts, or other considerations, endowing them with greater apparent relevance to the issue than they might appear to have under an alternative frame" [@Nelson1997Rally, 569].

Applying this to the issue of migration policy and the consideration of criminal migrants, one can imagine a news consumer confronted with an increased volume of news about crimes committed by migrants. The value-expectancy model predicts that the consumer forms a cognitive definition of migration that is increasingly associated with the issue of crime, meaning this consideration features more prominently when forming an opinion about the appropriate level of immigration policy. As a result, their opinion about migration policies should become more restrictive.

***Association hypothesis*****: When an individual is exposed to a specific consideration about an issue, their association of the issue with this consideration should be strengthened.**

***Evaluation hypothesis*****: When an individual is exposed to a specific negative consideration about an issue, their attitude about the overall issue should become more negative.**

However, not all those exposed to a frame should respond similarly. As theories of motivated reasoning suggest, individuals should differ in their evaluation of an argument based on the attitudinal congruence of the statement with one's pre-existing attitudes. Those exposed to counter-attitudinal information will evaluate it as less convincing, spend more time counter-arguing it and be less likely to expose themselves to it in the first place [@Kunda1990; @Taber2006]. Hence, those who already hold attitudes congruent with the idea that migration promotes crime - namely that migration should be restricted - should be most likely to react to increased exposure to migration coverage emphasising crime, whereas those with the most liberal migration attitudes should either not react to information they avoid and find unconvincing, or react by developing *more liberal* migration attitudes. Consistent with this hypothesis, existing media effects studies find ideological inertia and even backlash when individuals are exposed to content from opposing political outlets [@Bail2018; @Broockman2022; @Guess2021].

***Motivated reasoning hypothesis*****: The effect of exposure to a specific frame should be stronger for individuals with congruent attitudes.**

# Research Design

## A Rare Shift in Migration Framing

In order to test whether changing news content - rather than a shift in the consumed news outlet - affected political attitudes, I exploit an editorial change in the largest German tabloid newspaper, *Bild*. As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts. Additionally, the fielding of a large-scale panel survey in the same period allow to assess the impact of news content on migration attitudes and how predispositions condition this effect. I will briefly discuss the context of the case in this section.

In the summer of 2015, Germany became sanctuary for around 800,000 refugees who had fled war, violence, and famine in Syria and elsewhere. The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win representation in the national parliament. Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* promoted an open stance towards the newly arriving in this period. This was often connected to chief editor Kai Diekmann, who hosted a refugee family in his home [@BR2015Diekmann].

In December 2016, Axel Springer, the company owning Bild, announces that Diekmann will leave the company. Less than a week after, it becomes public that prosecutors investigate Diekmann for sexual harassment. While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time also suggested Diekmann's departure might have been sped up as a result of the investigation.} [@Spiegel2017Diekmann].  The migration coverage in *Bild* severely changed when Diekmann left the newspaper in February 2017 and Julian Reichelt took over the position as editor-in-chief. The paper increasingly started painting a picture of refugees as criminals on the tabloid's front page [@Niggemeyer2018Bild; @DLF2018Reichelt]. Headlines like "I killed 40 people and want asylum" increasingly dominated the migration coverage of the newspaper. In a speech months before he took over the position as chief editor, Reichelt outlined his motivation for such a shift in migration coverage: "I can assure you: nothing has hurt [*Bild*] economically as much as our clear, humane, empathetic stance in the refugee crisis" \footnote{Reichelt in a speech at Deutschlandfunk's conference "Formate des Politischen 2016": \url{https://vimeo.com/190347766}}. He also argued that the German media shows too little tolerance towards anti-immigration attitudes and therefor excludes those holding such views from the political discourse.

This presents a unique case to study the effects of media content on public opinion. As outlined above, past observational studies have usually explored the effect of consuming a new/different news outlet, without assessing the precise shift in content. In this case, the shift in content took place *within* the outlet and can be clearly identified. The change of editor itself was not salient, which means any opinion changes among readers are most likely the result of the content [@Spirig2020]. Additionally, the timing of the editorial change is potentially exogenous, given the pressure from allegations against Diekmann. In summary, *this case is as close as possible to a field experiment in which a specific consideration of migration coverage is amplified in the coverage of one newspaper, but not others*.

I estimate the effect of this communicative shift in the tabloid's migration coverage with a difference-in-differences design to answer the question how much influence the news media has to shape public opinion. Compared to the experimental setting, this can tell us with high external validity how news content affects political attitudes in contemporary news environments, in the medium term, in the real world.

## Measuring Crime Frames in Migration Coverage

To measure media attention to immigration, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets \textit{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt} and the major German tabloid \textit{Bild} for the period 2013-2019. Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration. Second, I identify content about crime *within* migration coverage by applying a similar supervised classifier. This approach closely resembles the value-expectancy model, as I first identify coverage about the *issue*, before identifying the considerations emphasized in the discussion of this issue.

Table 1 in the appendix shows the number of print copies sold and online page impressions for each newspaper per day. It becomes clear that German newspapers have a rather important position in the German news market. The tabloid \textit{Bild} has by far the largest reach, with over 1.7 Million sold newspaper daily and around 550 million web visits per month. For reference: the German Wikipedia site had less than twice as many visits (975 million) in the same time frame  \footnote{Wikipedia Siteviews Analyisis: https://pageviews.wmcloud.org/siteviews/}. *Bild* is closely followed by the weekly published \textit{Spiegel}. The daily broadsheets sell less, and interestingly the online presence seems to be dominated by the right, given the weak presence of centre-left \textit{SZ} and left-wing \textit{taz}.

To identify whether an article is about migration, a research assistant annotated 1800 articles. As migration content is rare, and training data needs to be somewhat balanced, articles cannot be selected randomly. Instead, I first construct a dictionary of terms related to migration. I use dictionary extension based on German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles. Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with most migration terms and 100 from the remainder in between) for each newspaper for a total of 1,800 papers. Then, a coder hand-coded these articles, assessing whether their main topic is related to migration.

Using this sample, a BERT transformer model\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a subset of 1,400 annotated articles. After fine-tuning, the model correctly classifies 95.5% of the test set (F1: 0.94, recall: 0.93, precision: 0.95). This classifier is then used to annotate all 2.5 million newspaper articles. For the period from 2013 to 2019, around 90,000 (3.6%) are identified to treat the issue of migration.

```{r salience, fig.cap="Share of migration content out of all content in six different newspapers."}

MigSaliencePlot()

```

Figure \@ref(fig:salience) shows the share of migration articles in each newspaper. Clear peaks in attention are visible surrounding the refugee movements of summer 2015, following the large-scale sexual assaults on new years eve in Cologne 2016, and the conflict over asylum policy between the conservative sister parties CDU and CSU in 2018. Newspapers seem to be event-driven and follow largely parallel trends, albeit at different levels, with the centre-left \textit{SZ} discussing migration most and the tabloid \textit{Bild} least. Attention decreases in mid-2016, but remains high compared to pre-2015 levels. Surrounding the fielding period of the survey waves (gray vertical lines), most newspapers show similar levels of attention to the issue between 2.5% and 6% of all articles, with the exception of \textit{SZ}, which moves between 5% and 12.5%.

To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest. Using a training sample of 1400 articles and a test sample of 400 articles, the classifier reaches a very good performance with an F1 score of 85.7%. I then apply this classifier to classify the approximately 90,000 articles about migration identified by the first classifier. About 7% of all migration coverage consists of articles about some form of crime\footnote{See appendix 1.2 for more information about the classifier, training process and data.}. The share of migration content devoted to news about crime within a given time frame allows me to assess how prominent the consideration of crime as a result of migration was at a specific point in time.

```{r treatment, fig.cap="Estimated change in attention to crime content in migration coverage, Bild vs. other newspapers. Black ticks in left panel indicate survey waves."}

TreatmentTrendPlot() + TreatmentDiDPlot()

```

The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line). As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased briefly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change. The trends run largely parallel to each other preceding the treatment, with the major exception being the few months following the events at new year's eve in Cologne 2015/16. The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in Bild. One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, while other newspapers maintained their levels of attention. Note that estimates using a structural topic model to identify migration framing yield similar results (see appendix 2.1).

## Measuring Immigration Attitudes and News Exposure

In order to assess the impact of this change in framing on migration attitudes, it is necessary to use data on consumers' immigration attitudes, as well as their news consumption. The 2017 Election Panel by the German Longitudinal election study luckily contains this data. This study consists of a total of 15 waves from 2016-2020, with 10,000 - 20,000 respondents per wave [@GLES2017Panel]. Six of these waves contain questions on immigration attitudes, asking respondents whether immigration of foreigners should be restricted or made easier. Responses where recorded on a seven-point Likert scale. This variable was centered on zero ($-3$ - easier, $3$ - restricted).

The panel also contains a question on newspaper consumption, which was asked in seven waves. The question provides respondents with a list of the six major daily newspapers plus an option "another daily newspaper", and asks whether they had consumed the paper in print or read articles from their website, and if so, how many days in the past week.

## Estimation

I will present evidence from two different estimation strategies to capture the effect of crime framing in migration coverage on immigration attitudes. The first will exploit the case outlined above and a *difference-in-differences* (DiD) estimator to show the effect of the editorial change - and the related content shift - on migration attitudes:

$$
y_{it} = \alpha + \beta_1*Post_t + \beta_2 * BildReader_i + \beta_3 * Post_t * BildReader_i + \epsilon_{it} 
$$

The dependent variable $y_{it}$ indicates a respondent's migration attitude in a given survey wave, measured on the Likert scale described above. The conditioning variable $BildReader_i$ is a simple binary variable indicating whether respondents read *Bild* in the past week and is measured in the pre-treatment wave. $Post_t$ indicates whether an interview took place preceding or following the editorial change. The estimator of interest is $\beta_3$, which indicates the change in migration attitudes of *Bild* readers following the editorial change, controlling for pre-treatment differences ($BildReader_i$), as well as general pre-post shifts in migration attitudes ($Post_t$).

In order to assess the conditioning effect of prior opinions, I also estimate a model interacting the difference-in-difference term with the initial migration opinion, $y_{i1}$, including all constitutive terms. The metric of interest is again the coefficient of the interaction $Post_t * BildReader_i$, as well as it's variation across different initial migration attitudes, captured by the coefficient for $Post_t * BildReader_i * y_{i,t=1}$.

The second strategy combines the media content analysis with the survey data directly to generate a measure of individual exposure to migration content. Based on the responses to the question which newspapers an individual consumed for how many days in the past week, I generate a weighted estimate of migration content in the week preceding that survey date. I do that by first estimating the daily attention in the specific outlet in the week preceding the interview date. Then, I weight it by the days the person read it and divide the sum of the two by the overall number of days a person read any newspaper. This provides me with an individual estimate of migration content in a respondent's news diet, dependent on interview date and the frequency of newspaper consumption. So if individual $i$ read paper $A$ (devoting 10% of their migration coverage in the past week to consideration $c$) for 3 days last week and paper $B$ (devoting 20% to $c$) 7 days, then the estimated relative exposure to consideration $c$ would be $\frac{3*0.1 + 7*0.2}{3+7} = \frac{1.7}{10} = 0.17$.

This estimate can then be used to assess whether the individual migration opinion has been affected by changing news coverage using a *two-way fixed-effect model* (TWFE). This means that general time trends ($\phi$) and individual differences ($\rho$) are controlled for in order to estimate within-individual changes beyond general trends in migration attitudes. Note however that this model - other than the difference-in-difference model - does *not* estimate a causal effect, but a correlation of crime framing in consumed migration content. A correlation could also be explained by individuals changing their opinion and afterwards selecting their news content accordingly. The model however allows to generalize the findings from the DiD estimate to all newspapers and a broader time period.

$$y_{it} = \alpha + \beta_1*FrameExposure_{it} + \rho_i + \phi_t + \epsilon_{it}$$

The TWFE model creates a rather high hurdle to detect a correlation of independent and dependent variable, not only because I have to rely on daily estimates of newspaper content - which can only be a proxy for actual exposure, but also because the data in this model comes from two different sources, mitigating potential common source error. Both issues should increase attenuation bias, thereby decreasing the size of the estimate of the true underlying correlation.

Again, an interaction model will be estimated for this model, by interacting frame exposure with the initial migration attitude. As the fixed effects already capture any time-constant individual characteristics and thereby already allow the intercept to vary [@Brambor2006a], I will not include both fixed effects and initial migration opinion at the same time, but estimate individual models with either control.

# Results

## Framing Effects on Migration Attitudes

Did increased exposure to crime frames about immigration affect individuals' attitudes? My results, displayed in \@ref(tab:DiDResults) seem to suggest that this was not the case. The dependent variable is a seven-point Likert-scale capturing immigration preferences from -3 (liberalize immigration) to 3 (restrict immigration).  Model 1 shows the simple DiD estimate, comparing changes among Bild-readers to those who never read Bild, even post-treatment. The estimate for the average treatment effect is a moderate 0.131 on the seven-point scale (about 2% of the scale), which is significant at the .05-level. This changes once we include individual fixed effects in model 2: The effect shrinks to a negligible 0.048 and is not significant at any common levels. The average treatment effect of exposure to more crime news at the individual seems negligible. However, do readers react differently, dependent on their prior attitudes?

```{r DiDResults, results='asis', fig.cap="Difference-in-Differences Models"}

DiDModels(dv_name = "1130_clean",
          cond_name = "\n Initial Attitude")

```

Recall that I hypothesized that readers are motivated reasoners, who will evaluate new evidence in line with their pre-existing attitudes. Those with liberal immigration attitudes should reject news about migrant crime, therefor show inertia or even backlash, while those with more conservative attitudes should be more inclined to accept the message. Model 3 and 4 suggest, contrary to my hypothesis, that more liberal readers show the strongest shift towards more conservative migration attitudes. This effect is substantial: for a neutral reader reporting $0$ on the $[-3; 3]$ scale, the model predicts a 0.346 point change, controlling for individual fixed effects. This effect *doubles* to $0.709$ ($.346 + (-.121)*(-3)$), a full 10% of the scale, among the most liberal readers, and decreases to essentially $0$ ($0.017$) among the most conservative readers. It seems that liberal readers are *more* motivated to incorporate the crime framing into their worldview.

```{r DiDPlot, fig.height=6, fig.width=10, fig.cap="Mean Immigration Attitude across Survey Waves, by Readership and Initial Immigration Attitude"}

DiDPlot(legend_position = "None") +
  DiDPlot(placebo = T)

```

The left panel of figure \@ref(fig:DiDPlot) shows this descriptively by initial migration attitude. As one can see, all groups diverge from each other after treatment, however this process is most pronounced (and substantial in size) among those with liberal initial migration attitudes, smaller for those who reported a neutral attitude towards migration, and smallest for those reporting conservative attitudes. Whereas all groups seem to regress to a common mean, it seems that - especially among initially neutral respondents - Bild readers move substantially towards the conservative pole, while non-readers show more stability in their attitudes.

This might be a true effect of the change in newspaper content, however given that treatment assignment is not random, it might also constitute the outcome of a selection bias: Bild readers, differing from those who never read Bild, might converge to a different mean than the general population. This "gravitational pull" towards a common mean should be more pronounced among the most liberal Bild readers, as Bild readers generally hold more conservative immigration attitudes ($\hat{x}_{Bild} = 1.44; \hat{x}_{!Bild} = 1.00$; see appendix 3.1). To assess this possibility, the right-hand panel of figure \@ref(fig:DiDPlot) shows the average migration attitude using a placebo treatment, namely defining Bild readership in the post-election wave of the panel (the last wave containing a question on news consumption), well after the emphasis on crime in Bild increased. Despite the lack of changing content, we can observe similar regression to the mean following the placebo date, despite the shorter post-treatment period. Those with the most liberal immigration attitudes show the strongest divergence from their control group counterparts, whereas the difference is less pronounced in the conservative group. Theoretically, this might be driven by long-term changes among those who were treated in W1. However, as appendix 3.2.1.5 shows, even if we exclude those reading Bild in the original survey wave (i.e. the original treatment group), similar differences arise.

Summarised, these estimates reject two of the three hypotheses outlined above. Neither is there evidence for a direct effect (evaluation hypothesis), nor are there moderated effects beyond what we would expect given selection bias (motivated reasoning hypothesis). The next section will therefor assess the last hypothesis, association, before I discuss the generalizability of these estimates.

## Tracing the Mechanism: the Association of Crime and Migration Attitudes

As outlined above, framing theory suggests that increased exposure to a specific consideration about an issue leads to stronger association of an issue with this consideration. In the present case, this should mean that the correlation of attitudes on immigration with attitudes about crime should increase. The GLES Panel data contains a variable asking respondents whether "the state's capabilities to fight crime should be extended, even if that would entail more surveillance", asked in three waves overlapping with the migration attitude question. Figure \@ref(fig:corplot) shows the correlation of crime- and migration attitudes in treatment and control group, pre- and post-treatment. I added a counterfactual, applying the change in the control group to the treatment group, for easier interpretation. As we can see, the treatment group actually saw a *smaller* increase in the correlation of crime and migration attitudes than the control group, *despite weaker pre-treatment association*. Following [@Nelson1996], table \@ref(tab:cortable) regresses immigration attitudes on attitudes towards crime and investigates whether this association is generally different between the two groups\footnote{These differences are however in the opposite direction as the (substantial) differences in the descriptive correlations outlined in the plot. I am currently not sure how to interpret this.}, changes post-treatment, and whether it changes more in the treatment group using interaction terms. I find minor differences between the groups, but no significant difference when interacted with the DiD-term - respondents do not seem to associate crime more strongly with migration following the change in migration coverage in *Bild*.

```{r corplot, fig.width=8, fig.height=4, fig.cap = "Correlation of crime and migration attitudes in treatment and control group, pre- (wave 1) and post-treatment (waves 3 \\& 13)."}

MigCrimeCorPlot()

```

```{r cortable}

MigCrimeCorTable()

```

## Generalization

Is this null effect specific to Bild readers or does exposure to crime framing affect readers of all newspapers similarly? In order to generalize these findings, I estimate the average exposure of each respondent to crime frames in migration coverage in the week preceding an interview. Immigration attitudes are then regressed on this measure, it's interaction with prior attitudes, as well as fixed effects for individual and wave. This way, it is possible to assess the correlation of changes in migration attitudes with changing exposure to crime framing beyond general time-trends.

Surprisingly, results suggest a significant correlation of individual crime exposure and changes in respondents' immigration attitude. This association is not significant once controlling for the salience of migration content in a respondents diet (i.e. the share of articles concerned with migration out of all articles), which is surprisingly negatively related to migration attitudes, meaning the more salient migration content in a respondents' news content, the less conservative that person's attitude towards migration.

```{r TWFEResults, results='asis', fig.cap="Two-way fixed-effect Models of Direct Exposure", out.width = "50%"}

TWFEModels(dv_name = "1130_clean",
          cond_name = "\n Initial Attitude")

```

Similarly, I do find an interaction effect, which is robust to controlling for exposure to general migration content. The correlation of exposure to crime frames and migration attitudes is strongest among respondents with most liberal initial migration attitudes, and negligible among the most conservative respondents. The finding again contradicts our initial hypothesis that conservative readers should be *most* inclined to react to the exposure. A change in migration framing from 0% to 100% about crime corresponds to a 0.9 point change on the seven-point scale for the most liberal individuals. Note that since there is no biased definition of a treatment group here, this cannot be explained by regression to the mean, but might be related to ceiling effects (which would suggest an even larger true effect).

These findings are rather puzzling. The DiD estimates show absolutely no effect of a substantial increase in crime framing on migration attitudes, nor an increase in the association of migration and crime attitudes. The TWFE model, however, shows a significant correlation of migration attitudes and migration coverage about crime, as well as a stronger reaction of more liberal-minded respondents to such news. As the model presents mere correlations of immigration attitudes and crime content in the news, controlling for time trends, it cannot address endogeneity concerns. Hence, the effects in the TWFE model likely capture selection effects, as individuals developing a more liberal/conservative attitude towards migration choose more liberal/conservative news outlets.

In order to explore this alternative explanation, I estimate a TWFE Model regressing newspaper readership on respondents' migration attitude. The results indicate that changing migration attitudes are only weakly linked to newspaper consumption. A significant effect can only be observed for the left-leaning *SZ* and *taz*, in the expected direction: as individuals develop more conservative (liberal) attitudes, they report reading these two newspapers less (more). The association is however tiny: as respondents move one point towards the conservative pole of the seven point migration attitude scale, their likelihood to report reading SZ (taz) drops by 6 (8) percentage points.

```{r TWFEReadership, results='asis', fig.cap="Two-way fixed-effect Models of Newspaper Readership"}

TWFEReadership()

```

# Conclusion: Framing Effects in the Real World

This study estimated the causal effect of news framing on migration attitudes, exploiting a rare case of changing migration framing. Results indicate that this shift in news framing did not result in any change in migration attitudes. These findings add to a body of theoretical work and recent empirical findings questioning the media's influence on political attitudes [@Guess2021; @Lau2021a]. Taken together, this research suggests that the influence of the news media on opinion formation in contemporary news environments with high levels of consumer choice and diverse exposure is severely limited. Even a major change in migration framing did not change respondents' attitudes in the present study. This does not necessarily entail that classic news media has no influence at all over opinion formation, but it might at the very least be restricted to specific "windows of opportunity". The present case described an established issue that had been in the center of public debate for 1.5 years. It might well be that news framing plays a more critical role for the evaluation of emerging issues. Further research should explore this possibility, assessing the impact of similar cases of changing news framing in the real world. It remains crucial, however, to focus on precise changes in *content*, in order to improve our conceptual understanding of the effects of media exposure.

<!-- The setting more generally represents a least-likely case for the observation of media effects. The migration issue had been salient for one and a half years preceding the takeover, and opinions are likely chrystalized. The polarized nature of the topic should make it less likely that citizens will incorporate new information [@Taber2006; @Zaller1992]. Additionally, Germany had a large debate about refugees and crime after the new year's eve 2015/16 in Cologne. According to a report of the ministry of interior in Northrhine-Westphalia, hundreds of women were sexually assaulted and robbed by men they perceived to be of "north-african/arabic" descent \footnote{see report of the ministry of interior in Northrhine-Westphalia: \url{https://web.archive.org/web/20160116104020/http://m.mik.nrw.de/fileadmin/user_upload/Redakteure/Dokumente/Themen_und_Aufgaben/Schutz_und_Sicherheit/160111ssia/160111berppkoeln.pdf}}. This debate could serve as 'pre-treatment' and as such prevent further attitudinal change [@Druckman2012]. Lastly, the political parties in Germany had taken clear and visible positions on migration, providing citizens with strong party cues from which they could infer positions in case they didn't hold strong attitudes themselves [@Slothuus2021]. -->

<!-- might add: election campaign might expose people to more debate, plus general shift towards more restrictive attitudes ("Zeitgeist") -->

# Resources

### 2022-06-28 paper/main.tex
Update abstract
Revert "Delete paper directory"
This reverts commit b3ea5c81fc5d1df3344229a23a919c1f6b27542d.

@@
 
-\title{The Effect of News Framing on Issue Attitudes and Voting Behaviour}
+\title{The Causal Effect of News Framing on Opinion Formation}
 \author{Nicolai Berk\footnote{Doctoral Candidate, Dynamics Doctoral Program, Humboldt-Universität zu Berlin, \href{mailto:nicolai.berk@hu-berlin.de}{nicolai.berk@hu-berlin.de}}}
@@
     A large body of literature debates the extent to which media consumption affects consumers' issue attitudes and voting behaviour in contemporary media environments.
-Studies supporting the minimal effects hypothesis have often used designs estimating the effects of novel, previously unconsumed content on participants' attitudes.
+Studies arguing that the media has minimal influence on opinion formation in today's media environment  have often used designs estimating the effects of novel, previously unconsumed content on participants' attitudes.
 However, experimental evidence suggests that media consumers discount the bias of different outlets.
 Additionally, most studies assume rather than measure the extent of newspaper bias.
-Combining panel data with state-of-the-art methods of text analysis and exploiting an editorial change, I address both shortcomings with observational data.
+I address both shortcomings with observational evidence exploiting a change in migration framing following an editorial shift in Germany's largest tabloid, \textit{Bild}.
+The study combines panel data with state-of-the-art methods of text analysis and assesses the effect of changing migration frames in respondents' media diet on their attitudes towards migration.
 Results across different specifications indicate that even when assessing within-newspaper changes in issue framing, no effect on attitudes or voting behaviour can be found.
-These findings add further evidence that media effects in the post-broadcast era are limited.
+These findings add further evidence that short-term media effects in the viewers choice era are limited.
 \end{abstract}
@@
 
-How does news media content affect citizens' issue attitudes?
+How does news media content affect citizens' political attitudes and behaviour?
 Research on political behaviour has discussed this question for nearly a century.
@@
 As a result, "most media users will rarely find themselves in the path of attitude-discrepant information".
-Even if consumers had to face such discrepant information, this should reinforce their existing views rather than persuade as they are used to a partisan media diet (\cite[724f]{Bennett2008}).
+Even if consumers had to face such discrepant information, this should reinforce existing views rather than persuade as consumers are used to a partisan media diet (\cite[724f]{Bennett2008}).
 Similarly, agenda setting effects are unlikely as a result of selective exposure (\cite{Lau2021}).
@@
 For example, when a left-wing newspaper endorses a left-wing candidate, this should have no effect on citizens' assessment of the candidate, as the endorsement was to be expected (\cite{Chiang2011a}, see also \cite{Spirig2020}).
-Additionally, citizens might take cues from their preferred publication because they developed trust in its coverage over time.
+Additionally, citizens might have developed trust in the position of their preferred outlet and follow changing issue stances of the medium.
 
@@
 
-\subsection{Case description}
-
-To test this hypothesis, I analyse media and opinion data on the migration issue from the German national election in 2017.
-Following a period of increased refugee arrivals in Europe in the summer of 2015, the election was dominated by the migration topic and the related upcoming of the radical-right populist challenger party \textit{AfD}.
-The major two parties dominating German post-war politics, \textit{SPD} and \textit{CDU/CSU}, had to face severe losses following their 'grand coalition' (\cite{Bieber2021, Wessels2021}).
-
-This strong (although still variant, see figure \ref{fig:salience}) salience of the migration issue both in the media as well as in citizens subjective evaluations presents an ideal case to study the effects of shifting media framing on issue attitudes, as continuous coverage on and public debate of the issue are a given.
-
 \subsection{Public opinion data}
@@
 To measure the dependent variable (issue attitudes) and differentiate the treatment groups (newspaper readers), I employ panel data from the German Longitudinal Election Study (\cite{GLES2019LongTermTracking}).
-The panel consists of 15 waves, of which 6 (4) contain variables on newspaper consumption and immigration (integration) attitudes.
+Following a period of increased refugee arrivals in Europe in the summer of 2015, the 2017 election was dominated by the migration topic and the related upcoming of the radical-right populist challenger party \textit{AfD}.
+The major two parties dominating German post-war politics, \textit{SPD} and \textit{CDU/CSU}, had to face severe losses following their 'grand coalition' (\cite{Bieber2021, Wessels2021}).
+This strong (although still variant, see figure \ref{fig:salience}) salience of the migration issue both in the media as well as in citizens subjective evaluations presents an ideal case to study the effects of shifting media framing on issue attitudes, as continuous coverage on and public debate of the issue are a given.
+
+The panel consists of 15 waves, of which 6 (4) contain variables on newspaper consumption, intended voting decision and immigration (integration) attitudes.
 In each wave 9,000-15,000 respondents were interviewed, which allows the precise estimation of effects of media consumption.
-
 Figure \ref{fig:issues} shows the two main dependent variables for each group of readers.
@@
 
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=\textwidth]{paper/vis/salience_papers_focus.png}
-    \caption{Share of migration articles out of all articles across time for different newspapers.}
-    \label{fig:salience}
-\end{figure}
+To measure media attention to immigration, I collected 2.5 million newspaper articles from the most important German broadsheets \textit{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt} and the major German tabloid \textit{Bild} for the period 2013-2019.
+Table \ref{tab:paper_sales} shows the number of print copies sold and online page impressions for each newspaper per day.
+The tabloid \textit{Bild} has by far the largest reach, closely followed by the weekly published \textit{Spiegel}.
+The daily broadsheets sell less, and interestingly the online presence seems to be dominated by the right, given the weak presence of centre-left \textit{SZ} and \textit{taz}.
 
-To measure media attention to immigration, I collected 2.5 million newspaper articles from the most important German broadsheets \textit{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt} and the major German tabloid \textit{Bild} for the period 2013-2019.
+\begin{table}[!htbp] \centering 
+    \begin{tabular}{@{\extracolsep{5pt}} lcc} 
+    \\[-1.8ex]\hline 
+    \hline \\[-1.8ex] 
+    Paper & Print Sales & Web Impressions \\ 
+     & (thousands) & (millions) \\
+    \hline \\[-1.8ex] 
+    Bild & 1756 & 555 \\ 
+    Spiegel & 758 & 388 \\ 
+    FAZ & 242 & 123 \\ 
+    SZ & 358 & 13 \\ 
+    taz & 51 & 7 \\ 
+    Welt & 521 & 135 \\ 
+    \hline \\[-1.8ex] 
+    \end{tabular} 
+  \caption{Average daily sales and online impressions of different newspapers in 2017. Source: \cite{IVW}. Table generated with stargazer (\cite{stargazer}).} 
+  \label{tab:paper_sales} 
+\end{table}
+
 To identify whether an article is about migration, I train a BERT deep-learning classifier.
-
 As migration content is rare, and my training data needs to be somewhat balanced, I first construct a dictionary of terms related to migration.
@@
 This classifier is then used to annotate all 2.5 million newspaper articles.
-For the time frame of relevance for this study (the entire year of 2017), out of the total of 388,617 articles, 13,589 (3.5\%) are identified to treat the issue of migration\footnote{Note that the classifier, as well as the following topic model, was trained on a corpus of documents spanning 2013-2019.
-This was largely a decision to maximise possible applications for the resulting dataset, but also enables to compare issue attention and frames across time for validity checks.}.
+For the time frame from 2013 to 2019, around 90,000 (3.6\%) are identified to treat the issue of migration.
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/salience_papers.png}
+    \caption{Share of migration articles out of all articles across time for different newspapers.}
+    \label{fig:salience}
+\end{figure}
 
 Figure \ref{fig:salience} shows the share of migration articles in each newspaper.
-While the first few months of 2017 show rather high salience of the issue, attention decreases until May, before the share of articles covering this issue increases again in all newspapers except \textit{Bild}, which shows a stark decrease in July and maintains this level afterward.
-Most newspapers show similar levels of attention to the issue between 2.5\% and 6\% of all articles, with the exception of \textit{SZ}, which moves between 5\% and 12.5\%.
+Clear peaks in attention are visible surrounding the refugee movements of summer 2015, following the new years eve in Cologne 2016, and the conflict over asylum policy between CDU and CSU in 2018.
+Newspapers seem to be event-driven and follow largely parallel trends, albeit at different levels, with the  centre-left \textit{SZ} discussing migration most and the tabloid \textit{Bild} least.
+Attention decreases in mid-2016, but remains high compared to pre-2015 levels.
+Surrounding the fielding period of the survey waves (gray vertical lines), most newspapers show similar levels of attention to the issue between 2.5\% and 6\% of all articles, with the exception of \textit{SZ}, which moves between 5\% and 12.5\%.
 
@@
 The labour market frame should show mixed results, given that labour market integration might be perceived as threatening or addressing needs in the German economy.
-Figure \ref{fig:frames} shows the prevalence of all frames across time for each newspaper.
+Figure \ref{fig:frames} shows the prevalence of these frames across time for each newspaper.
 It can be seen that substantial variation exists in the relative emphasis of migration frames both within and across newspapers.
 Interestingly, some issues seem to vary according to newspaper slant.
-For example, more right-leaning outlets \textit{Bild, FAZ}, and \textit{Welt} seem to largely ignore the humanitarian crisis in the Mediterranean sea, while they emphasise petty crime more.
+For example, more right-leaning outlets \textit{Bild, FAZ}, and \textit{Welt} seem to largely emphasise crime and deportations, compared to their centrist and left-wing competitors.
 This lends some first credibility to the expected effects for these frames, although the differences are not clearly visible for the other frames.
@@
     \centering
-    \includegraphics[width=\textwidth]{paper/vis/frames_papers_focus.png}
-    \caption{Prevalence of different migration frames across newspapers. Gray vertical lines indicate survey field dates.}
+    \includegraphics[width=\textwidth]{paper/vis/frames_papers.png}
+    \caption{Prevalence of different migration frames across newspapers and time.}
     \label{fig:frames}
 \end{figure}
+
+\subsection{Local data on news exposure and voting behaviour}
+
+I am in the process of collecting data on the distribution of different newspapers in German electoral districts, as well as data on voting behaviour within these districts.
+This allows to assess whether higher readership of \textit{Bild} (and thus more exposure to its migration framing) results in changes in voting behavior following the change in migration framing after the editor-in-chiefs departure (see below) and the subsequent change in migration framing.
+
+\section{Case description and treatment}
+
+During the summer of 2015, the German tabloid Bild responded to the emerging migration issue unexpectedly progressive, calling for support for the newly arriving immigrants and attacking those promoting hate against refugees online (Bild stellt Hetzer an den Pranger 2015; Alvarez 2015), before starting the campaign ’We help - \#refugeeswelcome’ (Grosse Bild-Aktion: Wir helfen - \#refugeeswelcome n.d.).
+With this move, the paper heavily diverged from its right-wing tradition.
+The major change in tone was largely ascribed to then editor-in-chief Kai Diekmann, who had also invited a refugee family to live in his house (Reichart 2015).
+Diekmann left the company in January 2017.
+Then sole Bild editor-in-chief Julian Reichelt increasingly painted a picture of refugees as criminals and terrorists on the tabloid's front page (Niggemeyer 2018; Zudeick 2018).
+I aim to exploit this communicative shift in the tabloid’s migration framing to assess the effects of media framing on readers’ issue deﬁnitions, attitudes, and voting behaviour.
+As figure \ref{fig:frames_diekmann} shows, the migration framing presented in Bild changed following Diekmann's departure.
+Specifically, immigration was increasingly framed in terms of crime, while other newspapers maintained their levels of attention (see also figure \ref{app:diekmann_all_frames} in the appendix).
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{paper/frames_bild_diekmann_pres.png}
+    \caption{Monthly attention to different immigration frames following departure of Diekmann from Bild, for Bild and Welt.
+While attention to other frames follows the Welt's coverage of immigration (or any other newspaper, see appendix \ref{app:diekmann_all_frames}), an increase in Bild attention to general crime news when reporting about immigration is visible following the departure of Diekmann.}
+    \label{fig:frames_diekmann}
+\end{figure}
+
+Both studies in this paper build on this shift in attention.
+Study 1 will present estimates from two models assessing whether changing attention to any frame will affect issue attitudes or voting behaviour, using media and opinion data on the migration issue from the German national election in 2017.
+This is followed by a Difference-in-Difference estimate based on the change in attention to the crime frame presented above.
+Study 2 will turn to behavioral data and assess whether voting behaviour in voting districts with more circulation of \textit{Bild} have experienced changes in voting behaviour.
 
@@
 
-I estimate the same DiDs to measure shifts in migration framing in a certain newspaper, controlling for shifts in all other newspapers.
+I estimate the same DiDs to measure shifts in migration framing in a given newspaper, controlling for shifts in all other newspapers.
 To do that, I first sum the attention given to a certain frame in a given newspaper in the past day, week, month, or half year, up to the last survey wave.
@@
 Second, I fit two-way fixed-effect models with individual news framing estimates for each survey interview.
-I measure exposure to each frame by summing up the frame attention of the past week (relative to the interview) in each newspaper the respondent claimed to have read in the past week and dividing it by the total number of newspapers read.
+Since waves are sometimes fielded for several weeks, it might be a strong assumption to treat all interview dates within a given survey wave as identical.
+I measure exposure to each frame by summing up the frame attention of the past week (relative to the individual interview) in each newspaper the respondent claimed to have read in the past week and dividing it by the total number of newspapers read.
 This way, I estimate frame exposure for each individual respondent's interview date and news diet, which allows to estimate the correlation of changes in immigration opinion with the migration framing in recently consumed outlets.
 
-While the DiD's are causally better identified, controlling for shifts in other newspapers and reader groups, they suffer from the fact that surveys are conducted for several days, often up to two weeks, which makes the precise matching of newspaper content impossible.
+While the DiD's are better identified, controlling for shifts in other newspapers and reader groups, they suffer from the fact that surveys are conducted for several days, often up to two weeks, which makes the precise matching of newspaper content impossible.
 The fixed-effect models control for wave effects and (time-constant) individual characteristics, therefor restricting the explainable variance to everything beyond general trends and individual characteristics, but might include more noise.
@@
 
+\subsubsection{Local changes in voting behaviour}
+
 \section{Results}
 
-\subsection{DiD-assumption: Parallel trends}
+\subsection{Study 1}
+
+\subsubsection{Correlation of opinion changes among readers with changing frame attention in consumed newspapers}
+
+As figure \ref{fig:issues} shows, and as discussed in appendix \ref{sec:did_ass} and \ref{sec:did_sig}, the dependent variables show highly parallel trends but also display considerable variation beyond statistical noise\footnote{Recent, additional analyses have shown that the opinion shifts vary beyond statistical noise only when considering the broadly defined treatment (all readers of a newspaper).
+If however consulting only changes among those consuming a single newspaper, significance levels of these shifts approach what would be expected through random sampling error (see figure \ref{fig:did_by_treat}).
+At this point, it is unclear whether this is an outcome of severely decreased sample size or lack of opinion change among exclusive readers.}
+.
+Can these opinion shifts be explained by shifts in news content?
+Figure \ref{fig:did_corr} shows the core analysis to estimate the effect of migration framing on reader opinion.
+The displayed estimates are obtained by regressing the DiD-estimates for issue attitudes on the DiD-estimates for media attention, as described in section \ref{sec:models}.
+If opinion shifts among newspapers' readers - relative to other readers - can be explained by shifts in newspapers' issue framing, these two variables should be highly correlated.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames_did.png}
+    \caption{Regression coefficients from DiD-models with different specifications.}
+    \label{fig:did_corr}
+\end{figure}
+
+This is however not the case.
+Each panel in figure \ref{fig:did_corr} shows the effect of one frame on an attitude variable and the intention to vote for the radical right \textit{AfD} (controlling for all other frames mentioned in section \ref{sec:frame_selection}), across different lags and treatment definitions.
+Each dot in this graph represents the coefficient of a model explaining standardised\footnote{Meaning that independent and dependent variables were mean-corrected and re-scaled to standard deviations before regression.
+A coefficient of one means that a one-standard-deviation shift in the independent variable corresponds to a one-standard deviation shift in the dependent variable.} aggregate opinion shifts with standardised shifts in media attention to specific frames.
+For example, in the upper left panel 'crime', we can see three different panes ('afd-support', 'immigration' and 'integration') for each dependent variable.
+The vertical rows distinguish four different lags indicating the frame prevalence of the past day, week, month, half year, or the entire period up to the last survey date.
+Additionally, the color of the points indicates whether the model was estimated only for readers of a single newspaper (lower N, but no treatment diffusion) or all readers of a newspaper (who might read another newspaper, say SZ readers who also read FAZ).
+
+Only very few estimates are significant and no trends emerge across specifications for any variable.
+All estimates are clustering around zero, indicating no effect.
+Estimates of all relationships indicate both positive and negative relationships across specifications.
+While the 'exclusive reader' estimates show more variation, they also indicate far broader confidence intervals.
+There is no considerable difference across lags, and the variables only differ by the broader confidence intervals of the integration variable, owing to the fewer waves including this question.
+Generally, this analysis indicates no effect of media framing of migration on migration attitudes or voting behaviour.
+
+\subsubsection{Fixed-effect model}
+
+To corroborate these results, I estimate another model directly regressing individual migration opinions on individual estimates of consumed migration frames with fixed effects for survey wave and respondent (see section \ref{sec:models}).
+The results for migration and integration attitudes can be seen in figure \ref{fig:model_fe}.
+
+Again, most estimates are not significant, differ in direction across specifications, and cluster around zero.
+While some estimates are unidirectional (crime and labour market on the immigration issue; crime, capital crime, labour market and camps on \textit{AfD}-support), they show tiny effects (a standard deviation increase in attention to the labour market makes immigration attitudes between 0.005 and 0.015 standard deviations more conservative) and are usually not significant.
+Most importantly, both models do not correspond to expectations.
+This is probably most visible for the capital and sex crime frame ('capcrime'), which should show strongly positive effects (leading to more restrictive attitudes), but also for the illegal immigration and petty crime frame ('crime'), which consistently shows insignificant negative (i.e.
+liberalising) effects, contradicting the more sensible increase in \textit{AfD}-support when exposed to this frame.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames_fe_abs.png}
+    \caption{Regression coefficients from fixed-effects models with different specifications.}
+    \label{fig:model_fe}
+\end{figure}
+
+\subsubsection{Difference-in-Difference estimate}
+
+I initially hoped to match former and current readers of Bild or at least readers of Bild and other outlets to assess whether this shift in framing of a single newspaper affected attitudes and voting behaviour.
+Regrettably, only one survey wave preceded the departure of Diekmann, precluding a test of the parallel trends assumption.
+However, even under this strong assumption the estimate might be of interest.
+At this point, however, I can not present such an estimate yet.
+
+\subsection{Study 2}
+
+Results for local differences in electoral behaviour will be added once the data on local news circulation is available.
+
+\section{Discussion}
+
+This paper assesses the responsiveness of newspaper consumers' migration attitudes to the migration framing of their respective newspaper.
+Aggregate difference-in-differences models and individual estimates show that consumers' opinions on immigration and integration were not reacting to changes in the newspaper framing of the respective issue.
+These findings add to an increasing body of evidence showing the absence of short-term media effects in contemporary media environments (\cite{Arceneaux2013, Durante2012, Gentzkow2010, Guess2021, Lau2021}).
+
+Future research will have to establish whether media consumers react to attitude-discrepant information by changing the outlet instead.
+Several studies found that, instead of reacting with opinion shifts, readers might change their political preferences or mobilise to vote (\cite{Stetka2020}).
+Similarly, several studies indicate that changes in a media outlet's slant will result in a change in the composition of the consumers (ie those with conflicting attitudes stop reading the newspaper) rather than a change in a fixed readership's attitudes (\cite{Arceneaux2013, Durante2012, Spirig2020}).
+Whether similar effects can be observed when explicitly measuring newspaper framing are likely next steps for analysis.
+
+If short term changes in framing have no effect on attitudes in the short run, decreases in readership might lead to long-term changes in political opinions due to generational replacement into a changing media environment.
+This could also make findings from some studies in the field convincingly showing effects (\cite{Foos2020}) consistent with this study and other literature showing weak or absent effects.
+
+Another way forward might be to test theories of \textit{issue evolution} (\cite{Carmines1986}).
+For example, if a process of 'issue-sorting' took place on the migration issue in 2015, when the topic became very salient, citizens might have chosen a side and stuck to their opinion afterward.
+Future studies could hence try to identify such windows of opportunity where media effects might still be relevant.
+
+\printbibliography
+
+\section{Appendix}
+
+\subsection{Change in Bild framing of migration issue}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/did_papers_frames_1617_scatter.png}
+    \label{app:diekmann_all_frames}
+\end{figure}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/did_papers_frames_all_scatter.png}
+\end{figure}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/did_papers_allframes_1617_hist.png}
+\end{figure}
+
+\newpage
+
+\subsection{DiD-assumption: Parallel trends}\label{sec:did_ass}
+
+DiD-designs rest on the assumption that treated and untreated units would follow the same trend, were it not for the treatment.
+This means that, generally, treated and untreated units should show similar trends.
+Returning to figure \ref{fig:issues}, we can safely state that the parallel trends assumption is met in this case.
+All reader groups move in a highly similar fashion on both variables, albeit at different levels, which reflect the ideological leaning of their newspaper.
+
+\subsection{Distribution of DiD-effect significance}\label{sec:did_sig}
 
@@
 
-DiD-designs rest on the assumption that treated and untreated units would follow the same trend, were it not for the treatment.
-This means that, generally, treated and untreated units should show similar trends.
-Returning to figure \ref{fig:issues}, we can safely state that the parallel trends assumption is met in this case.
-All reader groups move in a highly similar fashion on both variables, albeit at different levels, which reflect the ideological leaning of their newspaper.
-
-\subsection{Distribution of DiD-effect significance}
-
 These highly parallel trends might raise another problem, however.
@@
 This means, more often than random (12\% vs 5\%), the opinions of consumers of certain news deviate from the opinions of other citizens.
-This is even more severe for the 192 wave-paper combinations concerning the immigration or integration item used in the remainder of this study, where 18\% of all estimated DiDs fall under the 5\%-threshold\footnote{See plot in appendix \ref{app:p-val_imm}}.
+This is even more severe for the 192 wave-paper combinations concerning the immigration or integration item used in the remainder of this study, where 18\% of all estimated DiDs fall under the 5\%-threshold\footnote{See plot \ref{fig:p-val_imm}}.
 This strongly indicates that news consumption matters for opinion formation and that the data shows variation which can be explained, despite highly parallel trends.
 
-\subsection{Correlation of DiD with frame prevalence}
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps_immint.png}
+    \caption{Empirical and theoretical p-values of 192 DiD-models corresponding to the immigration and integration questions of the GLES.}
+    \label{fig:p-val_imm}
+\end{figure}
 
-There seems to be interesting variation in the dependent variable.
-Can these opinion shifts be explained by shifts in news content?
-Figure \ref{fig:did_corr} shows the core analysis to estimate the effect of migration framing on reader opinion.
-The displayed estimates are obtained by regressing the DiD-estimates for issue attitudes on the DiD-estimates for media attention, as described in section \ref{sec:models}.
-If opinion shifts among newspapers' readers - relative to other readers - can be explained by shifts in newspapers' issue framing, these two variables should be highly correlated.
+\subsection{Opinion change among all and exclusive newspaper consumers}
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{paper/vis/effectplot_frames_did.png}
-    \caption{Regression coefficients from DiD-models with different specifications.}
-    \label{fig:did_corr}
+    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps_immint_bytreat.png}
+    \caption{Empirical p-values of 192 DiD-models showing opinion change for different treatment definitions.}
+    \label{fig:did_by_treat}
 \end{figure}
 
-This is however not the case.
-Each panel in figure \ref{fig:did_corr} shows the effect of one frame on an attitude variable (controlling for all other frames mentioned in section \ref{sec:frame_selection}), across different lags and treatment definitions.
-Each dot in this graph represents the coefficient of a model explaining standardised\footnote{Meaning that independent and dependent variables were mean-corrected and re-scaled to standard deviations before regression.
-A coefficient of one means that a one-standard-deviation shift in the independent variable corresponds to a one-standard deviation shift in the dependent variable.} aggregate opinion shifts with standardised shifts in media attention to specific frames.
-For example, in the upper left panel 'crime', we can see two different panes ('immigration' and 'integration') for each dependent variable.
-The vertical rows distinguish four different lags indicating the frame prevalence of the past day, week, month, half year, or the entire period up to the last survey date.
-Additionally, the color of the points indicates whether the model was estimated only for readers of a single newspaper (lower N, but no treatment diffusion) or all readers of a newspaper (who might read another newspaper, say SZ readers who also read FAZ).
-
-Only very few estimates are significant and no trends emerge across specifications for any variable.
-All estimates are clearly clustering around zero, indicating no effect.
-Estimates of all relationships indicate both positive and negative relationships across specifications.
-While the 'exclusive reader' estimates show more variation, they also indicate far broader confidence intervals.
-There is no considerable difference across lags, and the variables only differ by the broader confidence intervals of the integration variable, owing to the fewer waves including this question.
-Generally, this analysis indicates no effect of media framing of migration on migration attitudes.
-
-To corroborate these results, I estimate another model directly regressing individual migration opinions on individual estimates of consumed migration frames with fixed effects for survey wave and respondent (see section \ref{sec:models}).
-The results for migration and integration attitudes can be seen in figure \ref{fig:model_fe}.
-
-Again, most estimates are not significant, differ in direction across specifications, and cluster around 0.
-While some estimates are unidirectional (crime and labour market in the immigration issue), they show tiny effects (a standard deviation increase in attention to the labour market makes issue attitudes between 0.005 and 0.015 standard deviations more conservative) and are usually not significant.
-Most importantly, both models do not correspond to expectations.
-This is probably most visible for the capital and sex crime frame ('capcrime'), which should show strongly positive effects (leading to more restrictive attitudes), but also for the illegal immigration and petty crime frame ('crime'), which consistently shows insignificant negative (i.e.
-liberalising) effects.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames_fe_abs.png}
-    \caption{Regression coefficients from fixed-effects models with different specifications.}
-    \label{fig:model_fe}
-\end{figure}
-
-\section{Discussion}
-
-This paper assessed the responsiveness of newspaper consumers' migration attitudes to the migration framing of their respective newspaper.
-Aggregate difference-in-differences models and individual estimates show that consumers' opinions on immigration and integration were not reacting to changes in the newspaper framing of the respective issue.
-However, several alternative explanations are possible.
-
-Some other studies found that, instead of reacting with opinion shifts, readers might change their political preferences or mobilise to vote (\cite{Stetka2020}).
-Similarly, several studies indicate that changes in a media outlet's slant will result in a change in the composition of the consumers (ie those with conflicting attitudes stop reading the newspaper) rather than a change in a fixed readership's attitudes (\cite{Arceneaux2013, Durante2012, Spirig2020}).
-Whether similar effects can be observed when explicitly measuring newspaper framing are likely next steps for analysis.
-
-Another theoretical alternative might be the idea of \textit{issue evolution} (\cite{Carmines1986}).
-If a process of 'issue-sorting' took place in 2015, when the migration issue became very salient for the first time in a long time, citizens might have chosen a side and stuck to their opinion afterward.
-Hence, a second further avenue for analysis might look into opinion stability across a longer time horizon or a different case.
-
-On the empirical side, I cannot ensure that respondents actually received treatment when they say they read the newspaper.
-Some might only read the sports section, some might only read specific sub-issues (e.g.
-only the crime news about immigration, but not the news on migrants drowning in the Mediterranean).
-It also might be that survey responses regarding newspaper consumption are generally more statements of which paper respondents like rather than consume.
-It is therefor in no way clear whether the treatment actually reaches respondents, although similar studies connecting survey- and media data (\cite{Eberl2015}) have found effects of media content on attitudes and even voting behaviour.
-
-More could be done to measure emphasis frames as well.
-Recent innovations exploiting word embeddings are particularly noteworthy here, either extracting topics from the embedding space (\cite{Angelov2020, Urman2021}) or measuring conceptual associations across time with diachronic word embeddings (\cite{Rodman2019}).
-
-Beyond the improvement of the analysis, I could try to add a different case and/or exploit a natural experiment.
-The Bild had an editorial shift in 2017 which seems to have coincided with more emphasis of crime topics - in line with anecdotal evidence of the results of this change among journalists.
-Returning to an earlier framing of the paper, this case could be presented as additional evidence of null effects.
-It might also be possible to exploit the increasing attention to the climate issue in 2019 and again in 2020 to assess an opinion formation process from the beginning, although this would necessitate to leave the paper alone for a while, until the survey data is available.
-
-Lastly, if there were in fact no effect of news framing on respondents' attitudes towards migration, there is still a major open question: what does explain the variation that can be observed?
-
-\newpage
-
-\section{Appendix}
+\end{document}
 
@@
 \newpage
-
-\subsection{P-values immigration and integration issue}\label{app:p-val_imm}
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps_immint.png}
-    \caption{Empirical and theoretical p-values of 192 DiD-models corresponding to the immigration and integration questions of the GLES.}
-    \label{fig:p-val_imm}
-\end{figure}
-
-\end{document}

### 2022-06-28 paper/Manuscript_Framing.Rmd
Add word count, update abstract and acknowledgements, drop H3

@@
 However, the study of the effects of framing has almost exclusively taken an experimental approach, with limited external validity.
-Existing observational work has so far mostly studied correlational data or assessed 'media effects' broadly.
-I contribute to these bodies of research by exploiting a unique case from Germany, where an editorial change in Germany's largest tabloid - *Bild* - led to a substantial shift in the paper's migration framing.
+I provide the first real-world study of framing effects by exploiting a unique case from Germany, where an editorial change in Germany's largest tabloid - *Bild* - led to a substantial shift in the paper's migration framing.
 Combining panel data from over 15,000 individuals with content analysis of 2.5 million newspaper articles using transformer models and a difference-in-differences design, I show that a substantial increase in the emphasis of crime in migration coverage did not affect immigration attitudes, nor did it increase the association of migration attitudes with attitudes about crime.
-These findings question the generalizability of framing effects research and add to a recent body of empirical studies questioning the role of the news media for opinion formation in the twentyfirst century."
+These findings fundamentally challenge the generalizability of framing effects research and add to a recent body of empirical studies questioning the role of the news media for opinion formation in the twentyfirst century."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
@@
 
-*I am thankful for extensive feedback on earlier stages of this draft from Christian Arnold, Daniel Bischof, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Felix Hagemann, Julian Heid, Christina Gahn, Matthew Levendusky, Heike Klüver, Thomas M.
-Meyer, Rune Slothuus, Antonio Valentim as well as participants in the EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI, CompText Conference 2022, and the Political Behaviour Section at Aarhus University.*
+\center{WORD COUNT: 6,596}
+
+*I am thankful for extensive feedback on earlier stages of this draft from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Felix Hagemann, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
+Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim as well as participants in the EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI, CompText Conference 2022, and the Political Behaviour Section at Aarhus University.
+I also thank the two RAs, Robin Groß and Nathalie Aerts, for annotating the news articles.
+All remaining confusions are my own.*
 
@@
 ***Evaluation hypothesis*****: When an individual is exposed to a specific negative consideration about an issue, their attitude about the overall issue should become more negative.**
-
-However, not all those exposed to a frame should respond similarly.
-As theories of motivated reasoning suggest, individuals should differ in their evaluation of an argument based on the attitudinal congruence of the statement with one's pre-existing attitudes.
-Those exposed to counter-attitudinal information will evaluate it as less convincing, spend more time counter-arguing it and be less likely to expose themselves to it in the first place [@Kunda1990; @Taber2006].
-Hence, those who already hold attitudes congruent with the idea that migration promotes crime - namely that migration should be restricted - should be most likely to react to increased exposure to migration coverage emphasising crime, whereas those with the most liberal migration attitudes should either not react to information they avoid and find unconvincing, or react by developing *more liberal* migration attitudes.
-Consistent with this hypothesis, existing media effects studies find ideological inertia and even backlash when individuals are exposed to content from opposing political outlets [@Bail2018; @Broockman2022; @Guess2021].
-
-***Motivated reasoning hypothesis*****: The effect of exposure to a specific frame should be stronger for individuals with congruent attitudes.**
 

### 2022-07-08 paper/Manuscript_Framing.Rmd
add renv

@@
 However, the study of the effects of framing has almost exclusively taken an experimental approach, with limited external validity.
-I provide the first real-world study of framing effects by exploiting a unique case from Germany, where an editorial change in Germany's largest tabloid - *Bild* - led to a substantial shift in the paper's migration framing.
+I provide the first observational estimate of framing effects by exploiting a unique case from Germany, where an editorial change in Germany's largest tabloid - *Bild* - led to a substantial shift in the paper's migration framing.
 Combining panel data from over 15,000 individuals with content analysis of 2.5 million newspaper articles using transformer models and a difference-in-differences design, I show that a substantial increase in the emphasis of crime in migration coverage did not affect immigration attitudes, nor did it increase the association of migration attitudes with attitudes about crime.
-These findings fundamentally challenge the generalizability of framing effects research and add to a recent body of empirical studies questioning the role of the news media for opinion formation in the twentyfirst century."
+These findings fundamentally challenge the generalizability of framing effects research and question worries about the news media|s power to shape public opinion."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
@@
 One of the largest fields within this literature is concerned with framing effects.
-A huge body of experimental evidence suggests that citizens substantially alter their issue attitudes when presented with different frames [@Busby2019; @Chong2007b; @Leeper2020; @Nelson1997Rally; @sniderman2004structure; @Slothuus2008a].
+A huge body of experimental evidence suggests that citizens substantially alter their issue attitudes when presented with different frames [@Busby2019; @Chong2007b; @Leeper2020; @Nelson1996; @Nelson1997Rally; @sniderman2004structure; @Slothuus2008a].
 However, there is little research investigating whether these findings translate into a messy reality [@Barabas2010], where frames are communicated by specific actors, and citizens self-select into media outlets, potentially shielding them from some frames and exposing them to others.

### 2022-07-08 pres/Presentation.Rmd
allow caching to keep plot folder

@@
   warning = F, 
-  cache = F, 
+  cache = T, 
   out.width="90%", 

### 2022-07-11 paper/Manuscript_Framing.Rmd
Estimation: drop TWFE and interaction

@@
 
-In order to assess the conditioning effect of prior opinions, I also estimate a model interacting the difference-in-difference term with the initial migration opinion, $y_{i1}$, including all constitutive terms.
-The metric of interest is again the coefficient of the interaction $Post_t * BildReader_i$, as well as it's variation across different initial migration attitudes, captured by the coefficient for $Post_t * BildReader_i * y_{i,t=1}$.
-
-The second strategy combines the media content analysis with the survey data directly to generate a measure of individual exposure to migration content.
-Based on the responses to the question which newspapers an individual consumed for how many days in the past week, I generate a weighted estimate of migration content in the week preceding that survey date.
-I do that by first estimating the daily attention in the specific outlet in the week preceding the interview date.
-Then, I weight it by the days the person read it and divide the sum of the two by the overall number of days a person read any newspaper.
-This provides me with an individual estimate of migration content in a respondent's news diet, dependent on interview date and the frequency of newspaper consumption.
-So if individual $i$ read paper $A$ (devoting 10% of their migration coverage in the past week to consideration $c$) for 3 days last week and paper $B$ (devoting 20% to $c$) 7 days, then the estimated relative exposure to consideration $c$ would be $\frac{3*0.1 + 7*0.2}{3+7} = \frac{1.7}{10} = 0.17$.
-
-This estimate can then be used to assess whether the individual migration opinion has been affected by changing news coverage using a *two-way fixed-effect model* (TWFE).
-This means that general time trends ($\phi$) and individual differences ($\rho$) are controlled for in order to estimate within-individual changes beyond general trends in migration attitudes.
-Note however that this model - other than the difference-in-difference model - does *not* estimate a causal effect, but a correlation of crime framing in consumed migration content.
-A correlation could also be explained by individuals changing their opinion and afterwards selecting their news content accordingly.
-The model however allows to generalize the findings from the DiD estimate to all newspapers and a broader time period.
-
-$$y_{it} = \alpha + \beta_1*FrameExposure_{it} + \rho_i + \phi_t + \epsilon_{it}$$
-
-The TWFE model creates a rather high hurdle to detect a correlation of independent and dependent variable, not only because I have to rely on daily estimates of newspaper content - which can only be a proxy for actual exposure, but also because the data in this model comes from two different sources, mitigating potential common source error.
-Both issues should increase attenuation bias, thereby decreasing the size of the estimate of the true underlying correlation.
-
-Again, an interaction model will be estimated for this model, by interacting frame exposure with the initial migration attitude.
-As the fixed effects already capture any time-constant individual characteristics and thereby already allow the intercept to vary [@Brambor2006a], I will not include both fixed effects and initial migration opinion at the same time, but estimate individual models with either control.
-
 # Results

### 2022-07-11 paper/Manuscript_Framing.Rmd
Results: drop main effect discussion

@@
 
-Recall that I hypothesized that readers are motivated reasoners, who will evaluate new evidence in line with their pre-existing attitudes.
-Those with liberal immigration attitudes should reject news about migrant crime, therefor show inertia or even backlash, while those with more conservative attitudes should be more inclined to accept the message.
-Model 3 and 4 suggest, contrary to my hypothesis, that more liberal readers show the strongest shift towards more conservative migration attitudes.
-This effect is substantial: for a neutral reader reporting $0$ on the $[-3; 3]$ scale, the model predicts a 0.346 point change, controlling for individual fixed effects.
-This effect *doubles* to $0.709$ ($.346 + (-.121)*(-3)$), a full 10% of the scale, among the most liberal readers, and decreases to essentially $0$ ($0.017$) among the most conservative readers.
-It seems that liberal readers are *more* motivated to incorporate the crime framing into their worldview.
-
-```{r DiDPlot, fig.height=6, fig.width=10, fig.cap="Mean Immigration Attitude across Survey Waves, by Readership and Initial Immigration Attitude"}
-
-DiDPlot(legend_position = "None") +
-  DiDPlot(placebo = T)
-
-```
-
-The left panel of figure \@ref(fig:DiDPlot) shows this descriptively by initial migration attitude.
-As one can see, all groups diverge from each other after treatment, however this process is most pronounced (and substantial in size) among those with liberal initial migration attitudes, smaller for those who reported a neutral attitude towards migration, and smallest for those reporting conservative attitudes.
-Whereas all groups seem to regress to a common mean, it seems that - especially among initially neutral respondents - Bild readers move substantially towards the conservative pole, while non-readers show more stability in their attitudes.
-
-This might be a true effect of the change in newspaper content, however given that treatment assignment is not random, it might also constitute the outcome of a selection bias: Bild readers, differing from those who never read Bild, might converge to a different mean than the general population.
-This "gravitational pull" towards a common mean should be more pronounced among the most liberal Bild readers, as Bild readers generally hold more conservative immigration attitudes ($\hat{x}_{Bild} = 1.44; \hat{x}_{!Bild} = 1.00$; see appendix 3.1).
-To assess this possibility, the right-hand panel of figure \@ref(fig:DiDPlot) shows the average migration attitude using a placebo treatment, namely defining Bild readership in the post-election wave of the panel (the last wave containing a question on news consumption), well after the emphasis on crime in Bild increased.
-Despite the lack of changing content, we can observe similar regression to the mean following the placebo date, despite the shorter post-treatment period.
-Those with the most liberal immigration attitudes show the strongest divergence from their control group counterparts, whereas the difference is less pronounced in the conservative group.
-Theoretically, this might be driven by long-term changes among those who were treated in W1.
-However, as appendix 3.2.1.5 shows, even if we exclude those reading Bild in the original survey wave (i.e.
-the original treatment group), similar differences arise.
-
-Summarised, these estimates reject two of the three hypotheses outlined above.
-Neither is there evidence for a direct effect (evaluation hypothesis), nor are there moderated effects beyond what we would expect given selection bias (motivated reasoning hypothesis).
-The next section will therefor assess the last hypothesis, association, before I discuss the generalizability of these estimates.
-
 ## Tracing the Mechanism: the Association of Crime and Migration Attitudes

### 2022-07-11 paper/Manuscript_Framing.Rmd
results: drop twfe

@@
 
-Did increased exposure to crime frames about immigration affect individuals' attitudes?
-My results, displayed in \@ref(tab:DiDResults) seem to suggest that this was not the case.
-The dependent variable is a seven-point Likert-scale capturing immigration preferences from -3 (liberalize immigration) to 3 (restrict immigration).
-Model 1 shows the simple DiD estimate, comparing changes among Bild-readers to those who never read Bild, even post-treatment.
-The estimate for the average treatment effect is a moderate 0.131 on the seven-point scale (about 2% of the scale), which is significant at the .05-level.
-This changes once we include individual fixed effects in model 2: The effect shrinks to a negligible 0.048 and is not significant at any common levels.
-The average treatment effect of exposure to more crime news at the individual seems negligible.
-However, do readers react differently, dependent on their prior attitudes?
-
-```{r DiDResults, results='asis', fig.cap="Difference-in-Differences Models"}
-
-DiDModels(dv_name = "1130_clean",
-          cond_name = "\n Initial Attitude")
-
-```
-
 ## Tracing the Mechanism: the Association of Crime and Migration Attitudes
@@
 MigCrimeCorTable()
-
-```
-
-## Generalization
-
-Is this null effect specific to Bild readers or does exposure to crime framing affect readers of all newspapers similarly?
-In order to generalize these findings, I estimate the average exposure of each respondent to crime frames in migration coverage in the week preceding an interview.
-Immigration attitudes are then regressed on this measure, it's interaction with prior attitudes, as well as fixed effects for individual and wave.
-This way, it is possible to assess the correlation of changes in migration attitudes with changing exposure to crime framing beyond general time-trends.
-
-Surprisingly, results suggest a significant correlation of individual crime exposure and changes in respondents' immigration attitude.
-This association is not significant once controlling for the salience of migration content in a respondents diet (i.e.
-the share of articles concerned with migration out of all articles), which is surprisingly negatively related to migration attitudes, meaning the more salient migration content in a respondents' news content, the less conservative that person's attitude towards migration.
-
-```{r TWFEResults, results='asis', fig.cap="Two-way fixed-effect Models of Direct Exposure", out.width = "50%"}
-
-TWFEModels(dv_name = "1130_clean",
-          cond_name = "\n Initial Attitude")
-
-```
-
-Similarly, I do find an interaction effect, which is robust to controlling for exposure to general migration content.
-The correlation of exposure to crime frames and migration attitudes is strongest among respondents with most liberal initial migration attitudes, and negligible among the most conservative respondents.
-The finding again contradicts our initial hypothesis that conservative readers should be *most* inclined to react to the exposure.
-A change in migration framing from 0% to 100% about crime corresponds to a 0.9 point change on the seven-point scale for the most liberal individuals.
-Note that since there is no biased definition of a treatment group here, this cannot be explained by regression to the mean, but might be related to ceiling effects (which would suggest an even larger true effect).
-
-These findings are rather puzzling.
-The DiD estimates show absolutely no effect of a substantial increase in crime framing on migration attitudes, nor an increase in the association of migration and crime attitudes.
-The TWFE model, however, shows a significant correlation of migration attitudes and migration coverage about crime, as well as a stronger reaction of more liberal-minded respondents to such news.
-As the model presents mere correlations of immigration attitudes and crime content in the news, controlling for time trends, it cannot address endogeneity concerns.
-Hence, the effects in the TWFE model likely capture selection effects, as individuals developing a more liberal/conservative attitude towards migration choose more liberal/conservative news outlets.
-
-In order to explore this alternative explanation, I estimate a TWFE Model regressing newspaper readership on respondents' migration attitude.
-The results indicate that changing migration attitudes are only weakly linked to newspaper consumption.
-A significant effect can only be observed for the left-leaning *SZ* and *taz*, in the expected direction: as individuals develop more conservative (liberal) attitudes, they report reading these two newspapers less (more).
-The association is however tiny: as respondents move one point towards the conservative pole of the seven point migration attitude scale, their likelihood to report reading SZ (taz) drops by 6 (8) percentage points.
-
-```{r TWFEReadership, results='asis', fig.cap="Two-way fixed-effect Models of Newspaper Readership"}
-
-TWFEReadership()
 

### 2022-07-11 paper/Manuscript_Framing.Rmd
Add nulleffectplots

@@
 
+```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}
+
+EffectPlot(multi = T, scaled = T, boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599
+
+```
+
+```{r migwaves, fig.cap="Effect of Change in Framing on Immigration Attitudes across Waves"}
+
+EffectByWavePlot(boundary_share = 1) 
+# would add 2 (or 3) lines here: 
+#   minimal relevant effect (5%/0.3 on 7-point scale); 
+#   conservative experimental effect (10%/0.6)
+#   large (not maximum) experimental effect (30%/2.4)
+
+```
+
 ## Tracing the Mechanism: the Association of Crime and Migration Attitudes

### 2022-07-11 code/functions/visualisation.R
Add most crime mig coverage in bild

@@ -19,7 +19,8 @@ library(data.table)
 
 MigSaliencePlot <- function(aggregation = "months"){
   
-  mig_salience_plot <- fread(here("data/processed/bert_crime_daily.csv")) %>% 
+  mig_salience_plot <- 
+    fread(here("data/processed/bert_crime_daily.csv")) %>% 
     select(date_clean, paper, mig_share) %>% 
     mutate(date_new = floor_date(date_clean, aggregation)) %>% 
     group_by(date_new, paper) %>% 
@@ -35,13 +36,23 @@ MigSaliencePlot <- function(aggregation = "months"){
   return(mig_salience_plot)
 }
 
+TenMostCrime <- function(){
+  fread(here('data/processed/bert_crime_clean.csv'), encoding = "UTF-8") %>% 
+    filter(crime_label > 0, paper == "Bild") %>% 
+    arrange(crime_prob) %>% 
+    select(title) %>% tail(5) %>% 
+    knitr::kable(col.names = "Five headlines with highest crime score") %>% 
+    return()
+}
 
 # Treatment: shift in attention to crime
 
 TreatmentTrendPlot <- function(size = 1, 
                                cntrl_col = "black",
                                treat_col = "red",
-                               maxdate = as.Date("2020-01-01")) {
+                               maxdate = as.Date("2020-01-01"),
+                               mindate = as.Date("2016-01-01"),
+                               aggregation = "quarter") {
   
   ## load BERT data
   bert_ests_raw <- 
@@ -49,16 +60,16 @@ TreatmentTrendPlot <- function(size = 1,
     
     bert_ests <- 
       bert_ests_raw %>% 
-      mutate(month = lubridate::floor_date(date_clean, "quarter")) %>% 
+      mutate(month = lubridate::floor_date(date_clean, aggregation)) %>% 
       group_by(paper, month) %>% 
       summarise(
-        crime_share = mean(crime_label)
+        crime = mean(crime_label)
       ) %>% 
       mutate(paper = ifelse(paper %in% c("bild", "Bild"), "Bild", "Other")) %>%
       group_by(month, paper) %>%
-      select(crime_share) %>% 
+      select(crime) %>% 
       summarise(
-        crime_share = mean(crime_share)
+        crime = mean(crime)
       )
     
     survey_dates <- 
@@ -68,14 +79,15 @@ TreatmentTrendPlot <- function(size = 1,
     ## visualise
     trendplot <- 
       bert_ests %>% 
[…]

### 2022-07-12 code/functions/visualisation.R
Revert "get rid of crime model"
This reverts commit fe0ba7197bf2dc195c9ce649ad512a5eb84653b9.

@@ -270,6 +270,23 @@ EffectPlot <- function(multi = F,
       stop("scaled = 'raw' not supported for multi = T.")
     }else if(scaled){
       # standardised dv
+      gles_p_long["dv"] <- scale(gles_p_long["2880h_clean"])
+      
+    }else if (!scaled){
+      
+      # else percentage of scale
+      gles_p_long$dv <- scales::rescale(gles_p_long$`2880h_clean`, to = c(0,1))
+      
+    }
+    
+    crime_att_model <- 
+      fixest::feglm(dv ~ post*treat | lfdn, 
+                    data = gles_p_long)
+    
+    if(scaled == "raw"){
+      stop("scaled = 'raw' not supported for multi = T.")
+    }else if(scaled){
+      # standardised dv
       gles_p_long["dv"] <- scale(gles_p_long["1210_clean"])
       
     }else if (!scaled){
@@ -318,7 +335,8 @@ EffectPlot <- function(multi = F,
                     data = gles_p_long)
     
     modelsummary::modelplot(
-      list("AfD thermometer" = afd_model,
+      list("Crime Attitude" = crime_att_model, 
+           "AfD thermometer" = afd_model,
            "MIP: Migration" = mip_model,
            "Integration Attitude" = int_att_model,
            "Migration Attitude" = mig_att_model),

### 2022-07-12 code/preprocessing/dependent/02_cleaning.R

@@ -614,6 +614,7 @@ gles_p_long$post <- gles_p_long$date_clean>= as.Date("2017-02-01")
 # define post-treatment date - placebo
 gles_p_long$post_placebo <- gles_p_long$date_clean>= as.Date("2018-01-01")
 
+
 ## save
 gles_p_long %>% 
   fwrite(., here('data/raw/gles/Panel/long_cleaned.csv'))

### 2022-07-12 paper/Manuscript_Framing.Rmd
Add most crime mig coverage in bild
Revert "get rid of crime model"
This reverts commit fe0ba7197bf2dc195c9ce649ad512a5eb84653b9.
Revert "Revert "get rid of crime model""
This reverts commit 4505cbdc2c051ab3d0103f544f5c23341090ca28.

@@
 
-\center{WORD COUNT: 6,596}
+WORD COUNT: 6,596
 
@@
 
-While these findings enable a better understanding about individuals’ susceptibility to framing effects in real-world environments, the literature almost exclusively provides us with experimental evidence.
+While these findings enable a better understanding about individuals' susceptibility to framing effects in real-world environments, the literature almost exclusively provides us with experimental evidence.
 Experiments can only incorporate few characteristics at a time and are limited to emulate a realistic environment for the study of news framing.
@@
 Other work has put more emphasis on causal identification of media effects using quasi-experimental designs, but paid less attention to the precise definition of the independent variable.
-This literature has
-usually exploited changes in news media markets such as boycotts of certain
-outlets [@Foos2022], entries of new outlets [@DellaVigna2007; @Grossman2022], changing TV channel positions [@Martin2017], or partisan takeovers of news outlets [@Durante2012; @Levendusky2022; @Spirig2020] to estimate the effects of changing news exposure on political behavior.
+This literature has usually exploited changes in news media markets such as boycotts of certain outlets [@Foos2022], entries of new outlets [@DellaVigna2007; @Grossman2022], changing TV channel positions [@Martin2017], or partisan takeovers of news outlets [@Durante2012; @Levendusky2022; @Spirig2020] to estimate the effects of changing news exposure on political behavior.
 Interestingly, the results diﬀer across studies.
@@
 
-Another approach is to assess consumer reactions to news content through ﬁeld
-experiments. In this setup, consumers are randomly assigned to speciﬁc news
-outlets and the development of their political attitudes is assessed.
+Another approach is to assess consumer reactions to news content through ﬁeld experiments.
+In this setup, consumers are randomly assigned to speciﬁc news outlets and the development of their political attitudes is assessed.
 @Guess2021, for example, randomly assigned individuals to receive content from a left-leaning or a right-leaning news outlet in their online news feeds.
 Similar studies have assessed the ffects of cross-partisan content on TV [@Broockman2022] and social media [@Bail2018].
-This literature provided
-contradicting results as well: while some found liberalizing effects of liberal
-content [@Broockman2022], others found no effects [@Guess2021], or even partisan backlash (i.e. individuals becoming even more conservative in response to liberal content; @Bail2018).
+This literature provided contradicting results as well: while some found liberalizing effects of liberal content [@Broockman2022], others found no effects [@Guess2021], or even partisan backlash (i.e.
+individuals becoming even more conservative in response to liberal content; @Bail2018).
 
@@
 
-”Framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy” [@Nelson1997Rally].
-A ”frame” is then the operating unit of this process, defining the issue at hand in a specific way.
+"Framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy" [@Nelson1997Rally].
+A "frame" is then the operating unit of this process, defining the issue at hand in a specific way.
 Different forms of frames have been conceptualised.
-When I talk about ’frames’ here, I refer to *emphasis frames*.
+When I talk about 'frames' here, I refer to *emphasis frames*.
 These frames emphasise certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame [@Leeper2020, 152].
 For example, issues of increasing welfare contributions might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes.
-Individuals’ support of a statement will differ dependent on the frame presented [@sniderman2004structure].
+Individuals' support of a statement will differ dependent on the frame presented [@sniderman2004structure].
 
@@
 ```
-
 According to this model, framing changes opinions by changing the association of a single consideration with the issue at hand.
@@
 
+```{r exampleArticles, results='markup'}
+
+TenMostCrime()
+
+```
+
 ## Measuring Immigration Attitudes and News Exposure
@@
 
+Figure \@ref(fig:multidv) visualizes the standardized effect of the change in framing on relevant dependent variables.
+As suggested by @Laken2017 [see also @Peyton2020], I added equivalence bounds of 0.2 standard deviations, representing a minimal effect size
+
 ```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}
 
-EffectPlot(multi = T, scaled = T, boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599
+EffectPlot(multi = T, scaled = "raw", boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599
 
 ```
+
+## Alternative Dependent Variables
+
+```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}
+
+EffectPlot(multi = T, scaled = "raw", boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599
+
+```
+
+## Stability of Estimates
 

### 2022-07-12 code/functions/visualisation.R

@@ -270,23 +270,6 @@ EffectPlot <- function(multi = F,
       stop("scaled = 'raw' not supported for multi = T.")
     }else if(scaled){
       # standardised dv
-      gles_p_long["dv"] <- scale(gles_p_long["2880h_clean"])
-      
-    }else if (!scaled){
-      
-      # else percentage of scale
-      gles_p_long$dv <- scales::rescale(gles_p_long$`2880h_clean`, to = c(0,1))
-      
-    }
-    
-    crime_att_model <- 
-      fixest::feglm(dv ~ post*treat | lfdn, 
-                    data = gles_p_long)
-    
-    if(scaled == "raw"){
-      stop("scaled = 'raw' not supported for multi = T.")
-    }else if(scaled){
-      # standardised dv
       gles_p_long["dv"] <- scale(gles_p_long["1210_clean"])
       
     }else if (!scaled){
@@ -335,8 +318,7 @@ EffectPlot <- function(multi = F,
                     data = gles_p_long)
     
     modelsummary::modelplot(
-      list("Crime Attitude" = crime_att_model, 
-           "AfD thermometer" = afd_model,
+      list("AfD thermometer" = afd_model,
            "MIP: Migration" = mip_model,
            "Integration Attitude" = int_att_model,
            "Migration Attitude" = mig_att_model),

### 2022-07-12 code/preprocessing/dependent/02_cleaning.R

@@ -614,7 +614,6 @@ gles_p_long$post <- gles_p_long$date_clean>= as.Date("2017-02-01")
 # define post-treatment date - placebo
 gles_p_long$post_placebo <- gles_p_long$date_clean>= as.Date("2018-01-01")
 
-
 ## save
 gles_p_long %>% 
   fwrite(., here('data/raw/gles/Panel/long_cleaned.csv'))

### 2022-07-12 paper/Manuscript_Framing.Rmd
Add discussion of expected & smallest effect

@@
 
+## Expected Effect Size
+
+Despite the abundance of framing effects studies, no common standard of the magnitude of framing effects exists.
+Even the correct measurement of the magnitude is a contested question, as different control groups can be compared [see @Chong2007a, 109f for a discussion].
+Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009a], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996].
+Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results seem to lie in between 10% and 25% of the scale when comparing pro and con arguments [@Lecheler2009a; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010], as most studies lack a neutral control group.
+As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [SOURCE], reported effects likely display a selection bias towards strong treatments.
+The treatment can be considered rather strong here, as the crime consideration is associated with strongly negative evaluations and the relative increase in the prevalence of this content is large.
+Additionally, given that readers already consumed that newspapers, the qualities of the sender should rather increase the effect size, while the high salience of the issue should decrease it.
+Given these considerations, I expect an effect of around 10% of the scale, or 0.6 on the seven-point scale[^1], which represents a conservative estimate.
+
+[^1]: As the scale runs from one to seven, it spans six points wide.
+
+As suggested by @Laken2017, I also estimate equivalence bounds indicating the smallest effect size of interest (SESOI, indicated by dotted orange line in the graph), as well as a conservative estimate of the experimentally expected effect.
+I define the SESOI at a 2.5% change, or 0.15 on the seven-point scale, which represents a fraction of the conservative experimental estimate and sets a fairly low bar given the strong treatment.
+This SESOI can be used to define equivalence bounds.
+Any effect estimated to lie within these bounds with statistical significance (i.e.
+a 90%-confidence interval in-between the positive and negative effect of this size) is too small to constitute a meaningful effect, as the hypothesis that the effect is *not* equivalent to zero can be rejected [see also @Peyton2020].
+
 # Results
 
-## Framing Effects on Migration Attitudes
+```{r singlemodel}
 
-Figure \@ref(fig:multidv) visualizes the standardized effect of the change in framing on relevant dependent variables.
-As suggested by @Laken2017 [see also @Peyton2020], I added equivalence bounds of 0.2 standard deviations, representing a minimal effect size
+gles_p_long <- 
+  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
+  as_tibble()
+
+postdate <- as.Date("2017-02-01")
+title <- "Mean migration attitude post-Reichelt takeover"
+
+gles_p_long["dv"] <- gles_p_long["1130_clean"]
+
+single_model <- 
+  fixest::feglm(dv ~ post*treat | lfdn + wave_ctrl, 
+                data = 
+                  # add control for different post-waves
+                  gles_p_long %>% 
+                  filter(!is.na(dv)) %>% 
+                  mutate(
+                    wave_ctrl = 
+                      ifelse(
+                        wave %in% unique(.$wave[c(1,2)]),
+                        "reference",
+                        wave
+                      ) 
+                  ) %>% 
+                  select(dv, post, treat, lfdn, wave_ctrl))
+
+ATT <- single_model$coefficients[["postTRUE:treatTRUE"]]
+t_ATT <- single_model$coeftable["postTRUE:treatTRUE", "t value"]
+p_ATT <- single_model$coeftable["postTRUE:treatTRUE", "Pr(>|t|)"]
+
+```
+
+Figure \@ref(fig:singledv) visualizes the effect of the change in framing on immigration attitudes.
+Green, dashed vertical lines indicate the expected effect from the experimental literature.
+The orange dotted lines indicate the equivalence boundaries.
+If the 90% interval is contained within these boundaries, the hypothesis that the estimate is larger than the SESOI can be rejected.
+The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment (\$t = \$ `r round(t_ATT, 2)`, \$p = \$ `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.6)`% of the expected effect of 0.6.
+The 95% confidence intervals also contains values far smaller than the SESOI of 0.15 but clearly include the vertical red line indicating no change.
+Clearly, the model suggests a null effect.
+
+```{r singleplot, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables", fig.height=2}
+
+# add 0.9 confidence bar
+
+EffectPlot(multi = F, scaled = "raw", theoretical_effect_size = 0.6, boundary_share = 0.25)
+
+```
 
@@
 
-EffectPlot(multi = T, scaled = "raw", boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599
+# add 0.9 confidence bar
+
+EffectPlot(multi = T, scaled = T, theoretical_effect_size = 0.2) # 0.2 SD suggested by Peyton 2020, 599
 
@@
 
-## Alternative Dependent Variables
+Figure \@ref(fig:multidv) shows standardized effects of the change in newspaper framing on immigration attitudes and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD.
+Dotted lines indicate a 20% standard deviation change, which has been defined as the standardized equivalence boundary in existing research [@Peyton2020, 599].
+All estimated effects are smaller in size than 0.05 standard deviations and associated 95%-confidence intervals contain zero.
+This means we can reject the hypothesis of meaningful effect size, but cannot reject that the estimate is statistically different from zero.
+All estimates suggest a clear null effect.
 
-```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}
-
-EffectPlot(multi = T, scaled = "raw", boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599
-
-```
-
-## Stability of Estimates
+To address potential long-term effects of this change in migration framing, figure \@ref(fig:migwaves) assesses the effect in each post-wave compared to the pre-treatment wave.
 
@@
 
-EffectByWavePlot(boundary_share = 1) 
+# add 0.9 confidence bar
+
+EffectByWavePlot(theoretical_effect_size = 0.6, boundary_share = 0.25)
 # would add 2 (or 3) lines here: 

### 2022-07-21 paper/Manuscript_Framing.Rmd
Update abstract

@@
 ---
-title: "Framing Effects in the Wild: How the News Media Shapes Public Opinion by Defining Political Issues"
+title: "Framing Effects in the Wild"
 author: "Nicolai Berk"
@@
       in_header: preamble.tex
-subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
+# subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
 fontsize: 12pt
 geometry: margin=1.5in
-abstract: "A vast body of research is devoted to the persuasive effects of news framing.
-However, the study of the effects of framing has almost exclusively taken an experimental approach, with limited external validity.
-I provide the first observational estimate of framing effects by exploiting a unique case from Germany, where an editorial change in Germany's largest tabloid - *Bild* - led to a substantial shift in the paper's migration framing.
-Combining panel data from over 15,000 individuals with content analysis of 2.5 million newspaper articles using transformer models and a difference-in-differences design, I show that a substantial increase in the emphasis of crime in migration coverage did not affect immigration attitudes, nor did it increase the association of migration attitudes with attitudes about crime.
-These findings fundamentally challenge the generalizability of framing effects research and question worries about the news media|s power to shape public opinion."
+abstract: "A large body of evidence from experimental work suggests that individual attitudes can easily be altered by emphasizing different aspect of an the issue at stake.
+However, such experimental studies of *emphasis framing* are limited in their emulation of the real world, where consumers are treated by multiple sources, select their news content, and pay more or less attention compared to the experimental setting.
+I exploit a rare change in news framing in the major German tabloid paper - *Bild* - to study whether experimental estimates of framing effects translate to the real world.
+In a first step, I apply supervised transformer models to a novel dataset of 2.5M news articles and provide evidence of a substantial shift in *Bild*'s migration framing following an editorial change.
+Second, I use a difference-in-differences design on a panel datset of over 16,000 individuals in ten waves to assess the precise impact on migration attitudes.
+The estimated effect is thirty times smaller than similar estimates from experimental studies, statisticially indistinguishable from zero, and significantly smaller than even minimal relevant effect magnitudes.
+Further analyses show that no change can be observed on other, related dependent variables either, and suggest that the change did not result in outward or inward selection into the newspaper.
+Taken together, these findings fundamentally challenge the external validity of framing effects research and suggests more limited influence of the news media on public opinion than previously thought."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
@@
 
-WORD COUNT: 6,596
+WORD COUNT:
 
-*I am thankful for extensive feedback on earlier stages of this draft from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Felix Hagemann, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
+*I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Felix Hagemann, Violetta Haas, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
 Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim as well as participants in the EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI, CompText Conference 2022, and the Political Behaviour Section at Aarhus University.
@@
 
-# Framing Effects vs. Media Effects
+# Limits of Framing Experiments
 
@@
 
-TreatmentTrendPlot() + TreatmentDiDPlot()
+TreatmentTrendPlot() + 
+  TreatmentDiDPlot()
 
@@
 
+## Difference of Treated and Untreated Units [or matching]
+
 ## Expected Effect Size
@@
 
+## Effect on Migration Attitude
+
 ```{r singlemodel}
@@
                 data = 
-                  # add control for different post-waves
                   gles_p_long %>% 
@@
 Figure \@ref(fig:singledv) visualizes the effect of the change in framing on immigration attitudes.
-Green, dashed vertical lines indicate the expected effect from the experimental literature.
-The orange dotted lines indicate the equivalence boundaries.
+Dashed vertical lines indicate the expected effect from the experimental literature.
+The dotted lines indicate the equivalence boundaries.
 If the 90% interval is contained within these boundaries, the hypothesis that the estimate is larger than the SESOI can be rejected.
@@
 
-```{r singleplot, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables", fig.height=2}
+```{r singleplot, fig.cap="Effect of change in framing on migration attitudes; difference-in-differences estimate.", fig.height=2}
 
-# add 0.9 confidence bar
-
-EffectPlot(multi = F, scaled = "raw", theoretical_effect_size = 0.6, boundary_share = 0.25)
-
-```
-
-```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}
-
-# add 0.9 confidence bar
-
-EffectPlot(multi = T, scaled = T, theoretical_effect_size = 0.2) # 0.2 SD suggested by Peyton 2020, 599
+DiDPlot(multi = F, scaled = "raw", theoretical_effect_size = 0.6, boundary_share = 0.25)
 
@@
 
-EffectByWavePlot(theoretical_effect_size = 0.6, boundary_share = 0.25)
-# would add 2 (or 3) lines here: 
-#   minimal relevant effect (5%/0.3 on 7-point scale); 
-#   conservative experimental effect (10%/0.6)
-#   large (not maximum) experimental effect (30%/2.4)
+DiDByWavePlot(theoretical_effect_size = 0.6, boundary_share = 0.25)
+
+```
+
+## Effect on other dependent variables
+
+```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}
+
+# add 0.9 confidence bar
+
+DiDPlot(multi = T, scaled = T, theoretical_effect_size = 0.2) # 0.2 SD suggested by Peyton 2020, 599
 
@@
 
+## Outward Selection
+
 # Conclusion: Framing Effects in the Real World

### 2022-07-21 paper/Manuscript_Framing.Rmd
Add discussion of limits of experiments

@@
 geometry: margin=1.5in
-abstract: "A large body of evidence from experimental work suggests that individual attitudes can easily be altered by emphasizing different aspect of an the issue at stake.
+abstract: "A large body of experimental work suggests that individual attitudes can easily be altered by emphasizing different aspects of the issue at stake.
 However, such experimental studies of *emphasis framing* are limited in their emulation of the real world, where consumers are treated by multiple sources, select their news content, and pay more or less attention compared to the experimental setting.
-I exploit a rare change in news framing in the major German tabloid paper - *Bild* - to study whether experimental estimates of framing effects translate to the real world.
-In a first step, I apply supervised transformer models to a novel dataset of 2.5M news articles and provide evidence of a substantial shift in *Bild*'s migration framing following an editorial change.
+I exploit a rare change of news framing in the major German tabloid newspaper *Bild* to study whether experimental estimates of framing effects translate into the real world.
+In a first step, I apply supervised transformer models to a novel dataset of 2.5M news articles and provide evidence of a substantial shift in the paper's migration framing following an editorial change.
 Second, I use a difference-in-differences design on a panel datset of over 16,000 individuals in ten waves to assess the precise impact on migration attitudes.
 The estimated effect is thirty times smaller than similar estimates from experimental studies, statisticially indistinguishable from zero, and significantly smaller than even minimal relevant effect magnitudes.
-Further analyses show that no change can be observed on other, related dependent variables either, and suggest that the change did not result in outward or inward selection into the newspaper.
+Further analyses show that no change can be observed on other, related dependent variables either and show no evidence for outward or inward selection into the newspaper.
 Taken together, these findings fundamentally challenge the external validity of framing effects research and suggests more limited influence of the news media on public opinion than previously thought."
@@
 
-knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = F, fig.height=6, fig.width=10, fig.align='center', eval = T)
+knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T)
 
@@
 library(here)
-library(censReg)
 
@@
 
-*I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Felix Hagemann, Violetta Haas, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
+*I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
 Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim as well as participants in the EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI, CompText Conference 2022, and the Political Behaviour Section at Aarhus University.
@@
 # Introduction: Does Framing Matter?
+
+<!--# Limits of observational framing studies, field experiments unethical & expensive, natural experiments rare, summary of study  -->
 
@@
 
+<!--# Need to explain emphasis framing in the introduction or move chapter from below up here, as well as open up distinction of frames in though and frames in communcation -->
+
 # Limits of Framing Experiments
 
-<!-- look at rune's comments regarding this chapter - keep focusing on framing effects literature -->
+<!--# add example of typical emphasis framing experiment -->
+
+Experiments offer strong internal validity at the cost of weaker external validity, compared to observational research.
+Framing effect studies offers strong evidence that the association of issues with different considerations in political communication can change reported attitudes about these issues, however it is unclear whether changing news content in the real world affects consumers' attitudes similarly.
+Figure \@ref(fig:causalPath) shows the main causal steps between frames in news content and reported individual attitudes.
+First (step 1), a frame in communication in news content needs to be presented to a respondent.
+While framing studies usually simply present a news article or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience.
+Additionally, changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news outlets containing such frames (and vice versa seek out attitudinally congruent information).
+This idea of 'selective exposure/avoidance' [@Bennett2008], or a a 'confirmation bias' [@Taber2006] or is one of the main arguments against the use of correlational evidence to study the effect of news content.
+
+Once the consumer receives the content, e.g.
+buys a newspaper, visits its website, or is exposed otherwise, it is not clear whether the content is actually engaged with (step 2).
+E.g., a consumer might well buy a newspaper but skip an article after reading the headline because the topic is not of interest or the frame is at odds with their existing attitude [@Lau2021a].
+Exposure is different from consumption mainly in that consumers actively decide to willfully engage with content rather than passively being exposed to it.
+As most framing studies do not offer choice of content to respondents, this steps remains an assumption in experimental studies.
+The assumptions of exposure and consumption in classic framing studies represent a high hurdle for the translation of experimental effects into the real world.
+
+Step 3 connects the newspaper content [i.e.
+the frame in communication; @Kinder1990] with the cognition of the exposed.
+While the preceding steps concerned the content reaching the respondent, this step is concerned with whether the consumer of the frame actually understands the frame being communicated correctly.
+Step 4 makes the leap from understanding the frame to increasingly associating the issue with the raised consideration - the major mechanism by which emphasis framing is assumed to change attitudes.
+Step 5 then translates these changing associations into (private) attitudes, while step 6 translates them into reported attitudes.
+Steps 3-6 are part of any framing experiment.
+However, this does not mean that they might not differ in the real world.
+Consumption might result in better or worse comprehension in the real world (step 3) because respondents might pay more or less attention to real news content compared to experimental treatments [@Barabas2010].
+Even after understanding the frame, there might be differences in how easily this translate into changing cognitive associations, given that those exposed might take real-world content more seriously.
+The core step of emphasis framing (5) is the change in attitudes following an increased association of an issue with the consideration raised by a presented frame.
+This step is likely unchanged given the mechanic translation of weighted considerations into attitudes assumed in emphasis framing theory [@Ajzen2000; @Nelson1997Rally].
+Lastly, attitudes have to translate into reported attitudes.
+While this is heavily context dependent [see e.g.
+@DinasSocialNorms] and differs based on the survey mode [SOURCE], it is unlikely to differ heavily in this study where attitudes are measured in a survey.
+
+To summarize, the main challenges in the translation of experimental framing effect studies into the real world stem from 1) exposure and 2) consumption, whereas the always limited realism of treatments in experiments might limit 3) comprehension of frames in communication, as well as 4) their translation into a strengthened association of issue and consideration.
+
+```{r causalPath, fig.align='center', fig.cap="Causal pathway of framing effect.", out.height="45%"}
+
+graph <- "digraph boxes_and_circles {
+
+            rankdir = 'LR'
+            bgcolor = 'white'
+
+            # a 'graph' statement
+            graph [overlap = false]
+
+            # several 'node' statements
+            node [shape = plaintext,
+                  fontname = Verdana,
+                  fontcolor = black,
+                  fontsize = 15]
+            A [label = '         News Content         ']
+            B [label = 'Exposure']
+            C [label = 'Consumption']
+            D [label = '  Cognitive Comprehension  ']
+            E [label = 'Cognitive Association']
+            F [label = 'Attitude']
+            G [label = 'Reported Attitude']
+
+            # several 'edge' statements
+            edge [fontname = Verdana,
+                  fontsize = 15,
+                  minlen = 0.3]
+            A->B[label='  1', color = red, fontcolor = red, arrowhead = dot]
+            B->C[label='  2', color = red, fontcolor = red, arrowhead = dot]
+            C->D[label='  3', color = red, fontcolor = red, arrowhead = dot]
+            D->E[label='  4', color = red, fontcolor = red, arrowhead = dot]
+            E->F[label='  5']
+            F->G[label='  6']
+          }
+          "
+
+DiagrammeR::grViz(graph) %>% 
+  DiagrammeRsvg::export_svg() %>% 
+  charToRaw() %>% 
+  rsvg::rsvg_pdf(here("paper/vis/CausalPath.pdf"))
+
+knitr::include_graphics(here("paper/vis/CausalPath.pdf"))
+
+```
+
+<!--# look at rune's comments regarding this chapter - keep focusing on framing effects literature, rework part below -->
 
@@
 <!-- might add: election campaign might expose people to more debate, plus general shift towards more restrictive attitudes ("Zeitgeist") -->
-
-# Resources

### 2022-08-03 paper/appendix.Rmd
Add DPA, Inselection, and Parallel Trends

@@
 ## Market Coverage of Different Newspapers
+
+Table 1 shows the number of print copies sold and online page impressions for each newspaper per day.
+It becomes clear that German newspapers have a rather important position in the German news market.
+The tabloid \textit{Bild} has by far the largest reach, with over 1.7 Million sold newspaper daily and around 550 million web visits per month.
+For reference: the German Wikipedia site had less than twice as many visits (975 million) in the same time frame \footnote{Wikipedia Siteviews Analyisis: https://pageviews.wmcloud.org/siteviews/}.
+Bild is closely followed by the weekly published \textit{Spiegel}.
+The daily broadsheets sell less, and interestingly the online presence seems to be dominated by the right, given the weak presence of centre-left \textit{SZ} and left-wing \textit{taz}.
 
@@
 
-# Structural Topic Model
+### Correcting for change in DPA-sourced content
+
+Among the changes after Reichelt's takeover as chief editor of *Bild* was a severe drop in the overall number of articles published online.
+Figure \@ref(fig:dpaShare) shows the monthly number of articles *Bild* published in their online archive across time.
+Recall that Reichelt took over in February 2017, and briefly after - in June 2017 - the overall number of articles published decreases by over 60%.
+The graph also suggests an explanation for this sudden shift: the share of articles sourced from DPA, a major German press agency alike the Associated Press, sharply decreases at the same time as the major decrease in the number of articles takes place (see top blue bars).
+While the decision to discontinue buying content from DPA must have been made by Reichelt himself (and is thus an outcome of the treatment), it might nevertheless affect the measurement of migration framing in *Bild*.
+DPA is a press agency supplying many German news outlets, which means it must have a rather unbiased or at least centrist coverage, potentially decreasing the estimate of crime frames within Bild's migration content.
+This would not be a problem, as long as this content is equally likely to make it to the front page.
+However, *Bild* likely gives more weight to its own content compared to pre-written content from DPA.
+It is therefore necessary to assess whether the change in framing persists when excluding DPA content.
+
+```{r dpaShare, fig.cap="Monthly number of articles by source."}
+
+data.table::fread(here("data/raw/newspapers/_bild_articles.csv"), 
+                  encoding = "UTF-8") %>% 
+  mutate(
+    dpa = str_detect(text, "(dpa)")
+  ) %>% 
+  mutate(month = lubridate::floor_date(date, "month")) %>% 
+  mutate(
+    dpa = ifelse(dpa, "DPA", "Original")
+  ) %>%
+  ggplot(aes(x = month, fill = dpa)) +
+  geom_bar() +
+  theme_minimal() +
+  ggtitle("Monthly number of articles, Bild online", "By origin, 2013-2019") + 
+  xlab("") + ylab("N") +
+  scale_fill_manual(name = "Source",
+                    values = MetBrewer::met.brewer("Archambault", 2))
+
+```
+
+The left panel of figure \@ref(fig:treatmentDPAcorr) displays the quarterly share of migration articles discussing crime for *Bild* compared to all other newspapers.
+The depression visible in the original plot in 2016-2017 is not visible anymore, as is the sharp increase in June 2017.
+Instead, the share of crime content in Bild's migration coverage increases directly after the takeover by Reichelt.
+The gap between Bild and all other newspapers increases, and this increased difference persists.
+This change becomes even more visible in the right-hand panel, which shows a difference-in-differences estimate of the change of the share of crime news in a newspapers migration content, this time controlling for whether the content is DPA-sourced or not.
+The general picture is quite similar to the original estimate in the paper, as migration coverage only increases in Bild, while all other outlets remain rather stable on this metric.
+The only difference is that in this estimate, the share of migration coverage devoted to crime 'only' increases by 5 percentage points, which still constitutes a very substantial increase.
+
+```{r treatmentDPAcorr, fig.cap="Change in share of crime content in newspaper coverage, excluding DPA-sourced news content.
+Left panel: quarterly share across time, Bild compared to other newspapers' average.
+Right panel: difference-in-differences estimates of change in newspaper coverage compared to other newspapers, controlling for source of content."}
+
+TreatmentTrendPlot(dpa_corrected = T) + 
+  TreatmentDiDPlot(dpa_corrected = T)
+
+```
+
+## Structural Topic Model
 
@@
 
-## Treatment
+### Treatment
 
-## Modeling Exposure with STM in TWFE Model
+# Readership models
+
+## Inward selection
+
+```{r inselection fig.cap = "Coefficients of OLS regression of readership on migration attitude across waves.
+Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change."}
+
+InSelection()
+
+```
 
@@
 
-Treated Group: Bild Readers in first (and only pre-treatment) wave.
-Control Group: Never-Readers of Bild.
-Post Date: $>=$ 01.02.2017
+Treated Group: Bild Readers in first (and only pre-treatment) wave. Control Group: Never-Readers of Bild. Post Date: $>=$ 01.02.2017
 
@@
 
+## DiD assumptions
+
+### Parallel Trends
+
+Figure \@ref(fig:parallelTrends) shows the development of migration attitudes among a panel of Bild readers\footnote{Readership was measured in a single wave in late 2015.} and non-readers across time, recorded in the German Longitudinal Election Study's Longterm Panel [@SOURCE].
+This is a far smaller sample with a limited time frame and hence less useful for the precise estimation of the effects of changing migration framing.
+The plot shows that both groups move along a similar long-term trend, slowly becoming more conservative, while moving into similar directions along the way.
+The only difference between the two groups is that Bild readers seem to be more conservative in late 2015 (note that only the last three interviews were conducted in January 2016).
+However this deviation lies well within the 95% confidence interval and those not reading Bild move in a similar direction, albeit less strongly.
+The parallel trends assumption seems to be generally met.
+
+```{r parallelTrends, fig.cap = "Migration Attitude among Bild-readers compared to non-readers across Time"}
+
+ParallelTrendsPlot()
+
+```
+
 ## Variable: Immigration Attitudes
@@
 (1) 1 Zuzug von Ausländern erleichtern
-(2) 2  
-(3) 3  
-(4) 4  
-(5) 5  
-(6) 6  
+(2) 2\
+(3) 3\
+(4) 4\
+(5) 5\
+(6) 6\
 (7) 7 Zuzug von Ausländern einschränken
@@
 ```
+
 #### Treatment groups across time, by prior attitude
@@
 ```
+
 #### Regression to the mean among Bild readers
@@
 
-### Outcome: Voting Nonresponse (190b = -99 | -98)
+### Outcome: Voting Nonresponse (190b = -99 \| -98)
 
@@
 ```
+
 No effect, but also very low N.
@@
 <!-- fread(here("data/processed/merged_stm.csv")) %>%  -->
+
 <!--   ggplot(aes(crime_label_share)) +  -->
+
 <!--   geom_histogram(bins = 50, col = "white") + -->
+
 <!--   theme_minimal() -->
@@
 <!-- (1) 1 Zuzug von Ausländern erleichtern  -->
+
 <!-- (2) 2   -->
+
 <!-- (3) 3   -->
+
 <!-- (4) 4   -->
+
 <!-- (5) 5   -->
+
 <!-- (6) 6   -->
+
 <!-- (7) 7 Zuzug von Ausländern einschränken -->
@@
 <!-- (1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen  -->
+
 <!-- (2)   -->
+
 <!-- (3)   -->
+
 <!-- (4)   -->
+
 <!-- (5)   -->
+
 <!-- (6)   -->
+
 <!-- (7) Ausländer sollten möglichst nach eigener Kultur leben können  -->
@@
 <!-- TWFEModels("1130_clean",  -->
+
 <!--            cond = "crime_label_share_lag",  -->
+
 <!--            cond_name = "\nLagged Exposure", -->
+
 <!--            dataset = "stm") -->

### 2022-08-22 code/functions/visualisation.R
Add LTP DiD and Change plot

@@ -1086,8 +1086,8 @@ ParallelTrendsPlot <- function(){
                        values = color_palette) +
     scale_fill_manual(values = color_palette) +
     guides(lty = "none", fill = "none") +
-    ggtitle("Migration Attitude by Bild Readership", "GLES Longterm Panel") +
-    ylab("Share") + xlab("") +
+    ggtitle("Immigration Attitude by Bild Readership", "GLES Longterm Panel") +
+    ylab("< More liberal | more restrictive >") + xlab("") +
     hist + 
     guide_area() +
     plot_layout(guides = "collect",
@@ -1099,5 +1099,217 @@ ParallelTrendsPlot <- function(){
   
   
 }
+
+
+
+# Change in Migration Attitudes ####
+
+MigChangePlot <- function(return_table = F) {
+  
+  color_palette = MetBrewer::met.brewer("Archambault", 2)
+  
+  ## load GLES LTP data, wide to long
+  gles_ltp <- 
+    haven::read_dta(here("data/raw/gles/LongTermPanel/ZA5770_v1-0-0.dta")) %>% 
+    pivot_longer(
+      cols = jdatum:nwkrnr3,
+      names_to = c("Erhebung", ".value"),
+      names_pattern = "(.)(.*)"
+    )
+  
+  ## clean migration and readership variable
+  gles_ltp <- 
+    gles_ltp %>% 
+    mutate(
+      `285a_clean` = ifelse(`285a` < 0, NA, `285a` - 1),
+      `174b_clean` = ifelse(`174b` < 0, NA, `174b` - 6),
+      date_clean = 
+        as.Date(
+          case_when(
+            Erhebung == "j" ~ "2013-12-23",
+            Erhebung == "k" ~ "2014-12-11",
+            Erhebung == "l" ~ "2016-01-07",
+            Erhebung == "m" ~ "2016-12-15",
+            Erhebung == "n" ~ "2017-12-08",
+          ),
+          format = "%Y-%m-%d"
+        )
+    )
+  
+  
+  ## estimate attitude change since last wave
+  gles_ltp <- 
+    gles_ltp %>% 
+    select(lfdn, date_clean, Erhebung, `174b_clean`) %>% 
+    pivot_wider(lfdn, names_from = Erhebung, values_from = `174b_clean`, names_prefix = "mig_") %>% 
+    mutate(
+      change_l = abs(mig_l - mig_j),
+      change_n = abs(mig_n - mig_l)
[…]

### 2022-08-22 paper/Manuscript_Framing.Rmd
Update abstract, add change across time

--- 2022-07-21 paper/Manuscript_Framing.Rmd
@@
 geometry: margin=1.5in
-abstract: "A large body of evidence from experimental work suggests that individual attitudes can easily be altered by emphasizing different aspect of an the issue at stake.
-However, such experimental studies of *emphasis framing* are limited in their emulation of the real world, where consumers are treated by multiple sources, select their news content, and pay more or less attention compared to the experimental setting.
-I exploit a rare change in news framing in the major German tabloid paper - *Bild* - to study whether experimental estimates of framing effects translate to the real world.
-In a first step, I apply supervised transformer models to a novel dataset of 2.5M news articles and provide evidence of a substantial shift in *Bild*'s migration framing following an editorial change.
-Second, I use a difference-in-differences design on a panel datset of over 16,000 individuals in ten waves to assess the precise impact on migration attitudes.
-The estimated effect is thirty times smaller than similar estimates from experimental studies, statisticially indistinguishable from zero, and significantly smaller than even minimal relevant effect magnitudes.
-Further analyses show that no change can be observed on other, related dependent variables either, and suggest that the change did not result in outward or inward selection into the newspaper.
-Taken together, these findings fundamentally challenge the external validity of framing effects research and suggests more limited influence of the news media on public opinion than previously thought."
+abstract: "Does news framing affect public opinion?
+While a large body of experimental work suggests that individual attitudes can be easily altered by emphasizing different aspects of an issue, little is known about how these studies translate into the real world.
+I exploit a rare natural change of news framing in the major German tabloid newspaper *Bild* to study whether experimental estimates of framing effects translate into the real world.
+In a first step, I apply supervised transformer models to a novel dataset of 2.5M news articles and provide evidence of a substantial shift in the paper's migration framing following an editorial change.
+Second, I employ a difference-in-differences design using panel data from over 16,000 individuals in ten waves to assess the precise impact on migration attitudes.
+The findings show that, despite a major change in migration framing, immigration attitudes and related variables remain unaffected.
+News framing only seems to be effective within limited opportunity windows during the emergence of political issues."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
@@
 
-WORD COUNT:
+WORD COUNT: `r wordcountaddin::word_count(here("paper/Manuscript_Framing.Rmd"))`
 
-*I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Felix Hagemann, Violetta Haas, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
+*I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
 Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim as well as participants in the EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI, CompText Conference 2022, and the Political Behaviour Section at Aarhus University.
-I also thank the two RAs, Robin Groß and Nathalie Aerts, for annotating the news articles.
 All remaining confusions are my own.*
+
+<!--# I also thank the two RAs, Robin Groß and Nathalie Aerts, for annotating the news articles.  -->
 
@@
 
-The persuasiveness of the news media has been a fixation of research on political communication and public opinion for at least the past 100 years.
-One of the largest fields within this literature is concerned with framing effects.
-A huge body of experimental evidence suggests that citizens substantially alter their issue attitudes when presented with different frames [@Busby2019; @Chong2007b; @Leeper2020; @Nelson1996; @Nelson1997Rally; @sniderman2004structure; @Slothuus2008a].
-However, there is little research investigating whether these findings translate into a messy reality [@Barabas2010], where frames are communicated by specific actors, and citizens self-select into media outlets, potentially shielding them from some frames and exposing them to others.
+Does news framing affect public opinion?
+While a large body of experimental evidence suggests that the emphasis of a certain consideration can substantially alter issue attitudes, we know little about how these findings translate into real-world environments.
+Prior work has shown that the external validity of such experiments might be seriously complicated by environments of diverse frames [@Chong2013] and actors [@Slothuus2010], as well as the seeking and avoidance of specific content [@Lau2021a; @Taber2006].
+Contemporary news environments provide consumers with especially diverse content and maximize their abilities to choose specific outlets and avoid others [@Bennett2008], thereby increasing the gap between the real-world environment and experimental studies.
+Additionally, the very nature of experiments is prone to over-estimate effects in the real world [@Barabas2010].
 
-In fact, many researchers argue that the effects of media content on attitudes are minimal.
-Observational research on media effects is abundant [@Broockman2022; @Durante2012; @Foos2022; @Grossman2022; @Guess2021; @Levendusky2022; @Martin2017; @Spirig2020], but has rarely paid attention to the precise content affecting issue attitudes [see @Djourelova2020 for an exception].
-To the authors knowledge, no existing observational study assesses the causal effect of changing news framing on issue attitudes.
+Following similar considerations, Donald Kinder called for framing research to extend its toolkit: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception.
+[...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157; see also @Busby2019; @Leeper2020].
+To the author's knowledge, no study has yet answered this call to provide an estimate of framing effects in the real world.
 
-I address this gap in the literature by presenting evidence from an editorial change in the largest German tabloid *Bild*, resulting in an increasing emphasis of crime in the paper's migration coverage.
-The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet changed it's framing while other papers maintained theirs.
+I address this gap in the literature by exploiting a rare and naturally occuring shift in the migration framing of Germany's largest tabloid newspaper, *Bild*.
+The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet substantially changed it's framing while other papers maintained theirs.
 By employing BERT models for the measurement of crime frames in a corpus of 2.5 million newspaper articles, I am able to clearly identify the treatment - something that is usually left to experimental studies.
-Coupling this data with a large-scale panel survey of over 15,000 individuals allows the precise estimation of this framing effect with a difference-in-differences design.
+The fielding of the German Longitudinal Election Study in the same period provides the rare opportunity to precisely assess the effect of this changing framing on readers' migration attitudes in a *difference-in-differences (DiD) design*.
 
-The results show that emphasis framing does not affect citizens' political attitudes in the real world.
-The influence of the news media on opinion formation in contemporary news environments with high levels of consumer choice and diverse exposure seems to be rather limited.
-Similarly, the study contributes to the media effects literature by investigating the effects of changing news *content* on public opinion, independent of the effects of the changing availability of news *outlets*.
-More generally, this research has important implications for our understanding of contemporary democracies, questioning the role of the media in public opinion formation.
+The results indicate that even this strong change in news framing did not affect consumers' immigration attitudes.
+The estimated effect is statisticially indistinguishable from zero, and significantly smaller than even minimal relevant effect magnitudes.
+Other variables, such as related issue attitudes, issue importance, and voting intentions are similarly unaffected.
+Additional evidence suggests that readers do also not react by turning away from the newspaper.
+Overall, these results fundamentally challenge the external validity of framing effects research and suggest that the influence of individual news outlets on public opinion is rather limited.
+Even strong changes in news framing do not affect political attitudes or news consumption.
 
-The paper will proceed as follows: in the next section I will briefly discuss the existing literature on framing and media effects, before describing the theoretical framework and research design, including case, measurement, and estimation strategy.
-The results section will then showcase findings from difference-in-differences and fixed-effect models assessing the impact of increased emphasis of crime in news coverage about migration, both on the association of attitudes about crime with attitudes about migration, as well as migration attitudes themselves.
-Lastly, I discuss the wider implications of the findings for the study of framing effects and the role of the news media in the opinion formation process.
+The paper will proceed as follows: in the next section I will briefly introduce the theoretical framework of emphasis framing and derive hypotheses about the impact of news framing on political attitudes.
+I will then discuss the limited external validity of framing effects studies, before I turn to the research design, including case, measurement, and estimation strategy.
+The results section will then showcase evidence from difference-in-differences models assessing the impact of changing migration framing on migration attitudes.
+Lastly, I discuss the wider implications of the findings for the study of framing effects and our understanding of the role of news media in the opinion formation process.
 
-# Limits of Framing Experiments
-
-<!-- look at rune's comments regarding this chapter - keep focusing on framing effects literature -->
-
-Research on framing has shown for decades that citizens' attitudes are highly reactive to minor changes in question wording and emphasis of specific considerations.
-However, it remains unclear how well these experimental findings translate into the real world, where citizens self-select into media content, receive cues from political actors, and are usually more concerned with their private lifes than politics.
-Scholarly effort has therefor been devoted to test the conditions under which framing effects materialize, designing experiments which emulate different aspects of real-world environments.
-For example,it has been shown that exposure to conflicting frames can serve to strengthen the effect of frames one was earlier exposed to, dependent on individual preconditions [@Bechtel2015; @Chong2013; @Druckman2012].
-Others have assessed what influence the sender of a frame has and shown that the effects of framing are more pronounced when the sponsor of the frame is from one's own party [@Druckman2001; @Slothuus2010b; @Slothuus2010].
-Lastly, concerns about the duration of framing effects have been addressed by some experimental research showing that those effects can last at least several weeks [@Lecheler2011].
-(missing here: Lau et al)
-
-While these findings enable a better understanding about individuals' susceptibility to framing effects in real-world environments, the literature almost exclusively provides us with experimental evidence.
-Experiments can only incorporate few characteristics at a time and are limited to emulate a realistic environment for the study of news framing.
-As Donald Kinder puts it: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception.
-[...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157].
-In order to test the external validity of framing effect studies, it is necessary to study observational data.
-
-This call for an assessment of framing effects beyond experimental studies has been echoed by various scholars over time [@Busby2019; @Leeper2020], yet rarely been answered.
-Existing research is often riddled with endogeneity concerns, co-treatment or concerned with media effects broadly, instead of assessing framing effects specifically.
-For example, @Jerit2008 investigates the effects of framing on public opinion compared to addressing the opponents issue.
-She finds that reframing is less effective than engagement with the opposite parties' frames, a finding that suggests that framing is not very effective.
-However, this study does not try to identify causal effects, but restricts itself to the assessment of correlational evidence.
-Others show with similar correlational designs that only specific frames seem to drive issue importance [@Mclaren2018], but do not assess effects on attitudes.
-
-Other work has put more emphasis on causal identification of media effects using quasi-experimental designs, but paid less attention to the precise definition of the independent variable.
-This literature has usually exploited changes in news media markets such as boycotts of certain outlets [@Foos2022], entries of new outlets [@DellaVigna2007; @Grossman2022], changing TV channel positions [@Martin2017], or partisan takeovers of news outlets [@Durante2012; @Levendusky2022; @Spirig2020] to estimate the effects of changing news exposure on political behavior.
-Interestingly, the results diﬀer across studies.
-While some studies find substantial effects of exposure to slanted media on political attitudes and voting behavior even in the long run [@Foos2020; @Grossman2022], others find that consumers switch outlets when the slant of currently consumed news changes [@Durante2012; @Spirig2020].
-
-Another approach is to assess consumer reactions to news content through ﬁeld experiments.
-In this setup, consumers are randomly assigned to speciﬁc news outlets and the development of their political attitudes is assessed.
-@Guess2021, for example, randomly assigned individuals to receive content from a left-leaning or a right-leaning news outlet in their online news feeds.
-Similar studies have assessed the ffects of cross-partisan content on TV [@Broockman2022] and social media [@Bail2018].
-This literature provided contradicting results as well: while some found liberalizing effects of liberal content [@Broockman2022], others found no effects [@Guess2021], or even partisan backlash (i.e.
-individuals becoming even more conservative in response to liberal content; @Bail2018).
-
-I argue this lack of consensus regarding the effects of media content is at least partly related to a lack of precision in the definition of the independent variable.
-The vast majority of studies in this literature observes or manipulates the consumed *outlet* , rather than the *content*.
-This is problematic for three main reasons.
-First, by assuming a stable 'slant' of specific news outlets, it remains unclear which content consumers actually react to (or not).
-While it is certainly true that news outlets have a certain political leaning, there is variation in how political and how persuasive specific news content is.
-Second, citizens are often aware of outlets' political leaning.
-@Baum2008a showed that consumers place the same news content more left- or right-leaning, dependent on wether it was presented as Fox news or CNN content.
-This implies that citizens should be able to discount political bias of outlets (muting potential effects of biased content) or might show motivated responses to content they perceive as motivated by political motives (e.g.
-backlash to opposing news sources).
-Third, by focusing on the effects of the consumption of different outlets, the literature studies a process unlikely to be observed in the real world - after all, changes in the makeup of media markets are extremely rare and switches from one partisan outlet to an opposing partisan outlet even more so.
-The main influence of news editors on public opinion should be exercised by editing the everyday content of news, rather than changing the consumer base of their outlets.
-
-To my knowledge, there are only two observational studies assessing the causal effect of exposure to specific content on political attitudes.
-@Slothuus2010b takes advantage of a sudden shift in a political parties' framing of retirement benefits, and shows that this changed framing has substantial impact on party supporters' attitudes about the issue.
-However, it is unclear how these findings translate to news framing effects, as it is impossible to distinguish the effect of partisan cue-taking from the persuasive effect of the frame itself.
-The only study which assesses the precise impact of changing news content on political attitudes comes from @Djourelova2020.
-She exploits a ban of the term "illegal migrant" in the *Associated Press* and shows that this language has modest effects migration attitudes.
-While the study itself reveals impressively how language can shape political attitudes, it constitutes a highly specific case and a rather minor change in the framing of migration.
-While news stories might lack the term "illegal migrant", they might still extensively cover crimes committed by migrants and thus associate migration with crime.
-
-Summarized, we lack an understanding of how framing affects political opinions in the real world.
-While experimental evidence suggests rather strong effects, it is unclear how these findings travel outside the lab.
-Observational evidence on media effects is abundant but has not studied precisely what the impact of framing is.
-The present study therefor exploits a naturally occurring change in the news framing of a particular issue *within* a specific outlet to isolate the effects of news framing on political opinions.
-
-# Emphasis Framing and the Value-Expectancy Model
+# Emphasis Framing
 
@@
 This model suggests that an attitude on a given issue is a function of two things: considerations relating to that object and their respective weights.
-The evaluation of the issue is subdivided into a number of considerations, which will carry clear evaluations.
+The evaluation of the issue is subdivided into a number of considerations [a so-called "frame in thought"; @Chong2007a, 105; @Kinder1996], which will carry clear evaluations.
 For example, to form an opinion about whether immigration to one's country should be restricted, a person might consider the humanitarian conditions in the countries of origin (negative consideration regarding restrictive migration policy), as well as the risk of increased crime (positive consideration; note that the model does not differentiate whether a consideration is grounded in objective reality).
@@
 ```
-According to this model, framing changes opinions by changing the association of a single consideration with the issue at hand.
-As a result, a specific consideration factors more prominently in an individuals' attitude formation process: "media frames influence opinions by stressing specific values, facts, or other considerations, endowing them with greater apparent relevance to the issue than they might appear to have under an alternative frame" [@Nelson1997Rally, 569].
+How does this model incorporate news content and other forms of political communication?
+News content can emphasize different considerations of an issue [so called "frames in communication" @Kinder1996].
+This strengthens the cognitive association of the issue at hand with the raised consideration.
+As a result, this specific consideration factors more prominently in an individuals' attitude formation process: "media frames influence opinions by stressing specific values, facts, or other considerations, endowing them with greater apparent relevance to the issue than they might appear to have under an alternative frame" [@Nelson1997Rally, 569].
 
@@
 
-***Evaluation hypothesis*****: When an individual is exposed to a specific negative consideration about an issue, their attitude about the overall issue should become more negative.**
+***Evaluation hypothesis*****: When an individual is exposed to a specific positive/negative consideration about an issue, their attitude about the overall issue should become more positive/negative.**
+
+# Limits of Framing Experiments
+
+Research on framing has shown for decades that citizens' attitudes and their issue associations are highly reactive to minor changes in the emphasis of specific considerations.
+However, it remains unclear how well these experimental findings translate into the real world.
+Especially when it comes to the exposure to frames in communication, translating framing effects from experimental studies is only possible under strong assumptions: While framing studies usually simply present a news article or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience.
+Additionally, changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news outlets containing such frames (and vice versa seek out attitudinally congruent information).
+This idea of 'selective exposure/avoidance' [@Bennett2008], or a a 'confirmation bias' [@Taber2006] brings with it a major endogeneity problem making purely correlational evidence of framing effects rather uninformative.
+
+Even if we assume that the consumer receives the content, e.g.
+buys a newspaper, visits its website, or is exposed otherwise, it is not clear whether the content is actually consumed.
+E.g., a reader might well buy a newspaper but skip an article after reading the headline because the topic is not of interest or the frame is at odds with their existing attitude [@Lau2021a].
+As most framing studies do not offer choice of content to respondents, engagement remains an assumption in experimental studies.
+Additionally, even when consuming the content, motivated reasoners presented with a plethora of news content about an issue will spend less time and cognitive energy on counter-attitudinal arguments than those supporting their viewpoint, lending more importance to considerations raised by amenable content [@Taber2006].
+Experimental studies presenting only one frame per issue cannot take this bias into account.
+
+These assumptions of exposure, consumption, and equal engagement in classic framing studies already represent a high hurdle for the translation of experimental estimates of framing effects into the real world.
+However the differences do not end there.
+Consumption might result in better or worse comprehension in the real world because respondents might pay more or less attention to real news content compared to experimental treatments [@Barabas2010].
+Even after understanding the frame, there might be differences in how easily this translates into changing cognitive associations, given that those exposed might take real-world content more seriously.
+
+To summarize, framing might have very different consequences in real-world environments than their experimental emulations.
+When we take the experimental evidence as an approximation of the effectiveness of framing in the real world, we make strong assumptions about citizens' exposure to, consumption of, and engagement with the frames in news content.
+Experiments can only incorporate few characteristics of the real world at a time.
+In order to test the external validity of framing effect studies, it is necessary to study observational data.
+
+## Existing Observational Studies of Framing Effects
+
+Several scholars have arrived at this conclusion and called for the assessment of framing effects beyond experimental studies [@Busby2019; @Kinder2007; @Leeper2020], yet the call has rarely been answered.
+While a large body of media effects research exists, it has not paid specific interest to framing, instead assessing the impact of changing news exposure broadly in observational designs [see e.g.
+@Foos2022; @Grossman2022 @Levendusky2022; @Spirig2020] and field experiments [@Bail2018; @Broockman2022; @Guess2021].
+
+The precious small body of existing research on framing effects is often riddled with endogeneity concerns or compound treatments.
+For example, @Jerit2008 investigates the effects of framing on public opinion compared to addressing the opponent's issue.
+She finds that reframing is less effective than engagement with the opposite parties' frames, a finding that suggests that framing is not very effective.
+However, this study does not provide an estimate of a causal effect, instead restricting itself to the assessment of correlational evidence.
+This is especially problematic regarding framing effects, as news content can affect consumers' inclination to consume news (see preceding section), and political actors might react to public opinion.
+Others show with similar correlational designs that only specific frames seem to drive issue importance [@Mclaren2018], but do not assess effects on attitudes.
+
+To my knowledge, there are only two observational studies assessing the causal effect of exposure to specific content on political attitudes.
+@Slothuus2010b takes advantage of a sudden shift in a political parties' framing of retirement benefits, and shows that this changed framing has substantial impact on party supporters' attitudes about the issue.
+However, it is unclear how these findings translate to news framing effects, as it is impossible to distinguish the effect of partisan cue-taking from the persuasive effect of the frame itself.
+The only study which assesses the precise impact of changing news content on political attitudes comes from @Djourelova2020.
+She exploits a ban of the term "illegal migrant" in the *Associated Press* and shows that this language has modest effects on migration attitudes.
+While the study itself reveals impressively how language can shape political attitudes, it constitutes a highly specific case and a rather minor change in the framing of migration.
+While news stories might lack the term "illegal migrant", they might still extensively cover crimes committed by migrants and thus associate migration with crime.
+
+Summarized, we lack an understanding of how framing affects political opinions in the real world.
+While experimental evidence suggests rather strong effects, it is unclear how these findings translate to the outside world.
+Observational evidence on media effects is abundant but has not studied precisely what the impact of framing is.
+The present study therefor exploits a naturally occurring change in the news framing of a particular issue *within* a specific outlet to isolate the effects of news framing on political opinions.
 
@@
 
-In order to test whether changing news content - rather than a shift in the consumed news outlet - affected political attitudes, I exploit an editorial change in the largest German tabloid newspaper, *Bild*.
+In order to test whether changing news content - rather than a shift in the consumed news outlet - affected political attitudes, I exploit an editorial change in the largest German newspaper, *Bild*.
 As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts.
-Additionally, the fielding of a large-scale panel survey in the same period allow to assess the impact of news content on migration attitudes and how predispositions condition this effect.
-I will briefly discuss the context of the case in this section.
+The fielding of a large-scale panel survey in the same period allow to assess the impact of news content on migration attitudes.
 
@@
 Less than a week after, it becomes public that prosecutors investigate Diekmann for sexual harassment.
-While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time also suggested Diekmann's departure might have been sped up as a result of the investigation.} [@Spiegel2017Diekmann].
+While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time support this interpretation of events.} [@Spiegel2017Diekmann].
 The migration coverage in *Bild* severely changed when Diekmann left the newspaper in February 2017 and Julian Reichelt took over the position as editor-in-chief.
@@
 This presents a unique case to study the effects of media content on public opinion.
-As outlined above, past observational studies have usually explored the effect of consuming a new/different news outlet, without assessing the precise shift in content.
-In this case, the shift in content took place *within* the outlet and can be clearly identified.
-The change of editor itself was not salient, which means any opinion changes among readers are most likely the result of the content [@Spirig2020].
+The shift in content can be clearly identified.
+The change of editor itself was not discussed in the media, which means any opinion changes among readers are the result of the changing content [@Spirig2020].
 Additionally, the timing of the editorial change is potentially exogenous, given the pressure from allegations against Diekmann.
@@
 
-I estimate the effect of this communicative shift in the tabloid's migration coverage with a difference-in-differences design to answer the question how much influence the news media has to shape public opinion.
-Compared to the experimental setting, this can tell us with high external validity how news content affects political attitudes in contemporary news environments, in the medium term, in the real world.
+## Measuring Frames in Communication
 
-## Measuring Crime Frames in Migration Coverage
-
-To measure media attention to immigration, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets \textit{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt} and the major German tabloid \textit{Bild} for the period 2013-2019.
+To measure immigration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets \textit{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt} and the major German tabloid \textit{Bild} for the period 2013-2019 (for the market reach of each outlet, see table 1).
 Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration.
@@
 
-Table 1 in the appendix shows the number of print copies sold and online page impressions for each newspaper per day.
-It becomes clear that German newspapers have a rather important position in the German news market.
-The tabloid \textit{Bild} has by far the largest reach, with over 1.7 Million sold newspaper daily and around 550 million web visits per month.
-For reference: the German Wikipedia site had less than twice as many visits (975 million) in the same time frame \footnote{Wikipedia Siteviews Analyisis: https://pageviews.wmcloud.org/siteviews/}.
-*Bild* is closely followed by the weekly published \textit{Spiegel}.
-The daily broadsheets sell less, and interestingly the online presence seems to be dominated by the right, given the weak presence of centre-left \textit{SZ} and left-wing \textit{taz}.
-
-To identify whether an article is about migration, a research assistant annotated 1800 articles.
-As migration content is rare, and training data needs to be somewhat balanced, articles cannot be selected randomly.
+To identify whether an article is about migration, i employ supervised machine learning.
+As migration content is rare, and training data needs to be somewhat balanced, articles cannot be selected randomly for annotation[^1].
 Instead, I first construct a dictionary of terms related to migration.
@@
 
-Using this sample, a BERT transformer model\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a subset of 1,400 annotated articles.
-After fine-tuning, the model correctly classifies 95.5% of the test set (F1: 0.94, recall: 0.93, precision: 0.95).
+[^1]: If migration content made up about 3% of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall, as the best guess in highly imbalanced data is simply the most common outcome.
+
+Using this sample, a BERT transformer model\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a random subset of 1,400 annotated articles (training set) with a validation set of 200 articles.
+After fine-tuning, the model correctly classifies 95.5% of a test set of 200 articles (F1: 0.94, recall: 0.93, precision: 0.95).
 This classifier is then used to annotate all 2.5 million newspaper articles.
@@
 Figure \@ref(fig:salience) shows the share of migration articles in each newspaper.
-Clear peaks in attention are visible surrounding the refugee movements of summer 2015, following the large-scale sexual assaults on new years eve in Cologne 2016, and the conflict over asylum policy between the conservative sister parties CDU and CSU in 2018.
+Clear peaks in attention are visible surrounding the refugee movements of summer 2015, as well as following the large-scale sexual assaults on new years eve in Cologne 2016[^2], and a conflict over asylum policy between the conservative sister parties CDU and CSU, which almost lead to the breakdown of the governing coalition in 2018.
 Newspapers seem to be event-driven and follow largely parallel trends, albeit at different levels, with the centre-left \textit{SZ} discussing migration most and the tabloid \textit{Bild} least.
@@
 
+[^2]: Germany had a large debate about refugees and crime after the new year's eve 2015/16 in Cologne.
+According to a report of the ministry of interior in Northrhine-Westphalia, hundreds of women were sexually assaulted and robbed by men they perceived to be of "north-african/arabic" descent (see report of the ministry of interior in Northrhine-Westphalia: \\url{[https://web.archive.org/web/20160116104020/http://m.mik.nrw.de/fileadmin/user_upload/Redakteure/Dokumente/Themen_und_Aufgaben/Schutz_und_Sicherheit/160111ssia/160111berppkoeln.pdf}](https://web.archive.org/web/20160116104020/http://m.mik.nrw.de/fileadmin/user_upload/Redakteure/Dokumente/Themen_und_Aufgaben/Schutz_und_Sicherheit/160111ssia/160111berppkoeln.pdf%7D%7D))
+
 To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest.
-Using a training sample of 1400 articles and a test sample of 400 articles, the classifier reaches a very good performance with an F1 score of 85.7%.
+Using a training set of 1400 articles, a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%.
 I then apply this classifier to classify the approximately 90,000 articles about migration identified by the first classifier.
@@
 The share of migration content devoted to news about crime within a given time frame allows me to assess how prominent the consideration of crime as a result of migration was at a specific point in time.
+In order to give an example of the content, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* most likely discussing crime according to the classifier.
+All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about new years eve in cologne.
+
+```{=tex}
+\begin{table}
+\centering
+\begin{tabular}{|p{12cm}|}
+\hline
+Final new years eve report of Cologne police: male groups identified \\ \hline
+Police searching for Northern-african offender: asylum-raid in Dortmund! \\ \hline
+Search in refugee home - mega-raid addressing asylum fraud \\ \hline
+Two groups attacking each other - again bloody conflict in refugee shelter \\ \hline
+Cabin fever! Violence! Mass brawls! This is behind the increase in refugee clashes \\ \hline
+\end{tabular}
+\caption{Headlines of five migration articles most likely to concern crime, according to BERT crime classifier. Translation by author.}
+\label{tab:exampleArticles}
+\end{table}
+```
+The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line).
+As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased briefly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change.
+The trends run largely parallel to each other preceding the treatment, with the major exception being the few months following the events at new year's eve in Cologne 2015/16[^3].
+The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in Bild.
+One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, while other newspapers maintained their levels of attention.
+
+[^3]: Note that the low levels of attention to crime in Bild's migration coverage in 2016 are partially the result of changing arrangements with a German news agency *dpa*, which provides services to quickly distribute news content similar to the Associated Press.
+Estimates excluding content from *dpa* indicate a change in attention to crime of similar size, as can be seen in appendix XX.
 
@@
 
-The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line).
-As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased briefly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change.
-The trends run largely parallel to each other preceding the treatment, with the major exception being the few months following the events at new year's eve in Cologne 2015/16.
-The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in Bild.
-One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, while other newspapers maintained their levels of attention.
-Note that estimates using a structural topic model to identify migration framing yield similar results (see appendix 2.1).
-
-```{r exampleArticles, results='markup'}
-
-TenMostCrime()
-
-```
-
-## Measuring Immigration Attitudes and News Exposure
+## Measuring Frames in Mind
 
@@
 This study consists of a total of 15 waves from 2016-2020, with 10,000 - 20,000 respondents per wave [@GLES2017Panel].
-Six of these waves contain questions on immigration attitudes, asking respondents whether immigration of foreigners should be restricted or made easier.
-Responses where recorded on a seven-point Likert scale.
+Thirteen of these waves contain questions on immigration attitudes, asking respondents whether immigration of foreigners should be restricted or made easier.
+Responses were recorded on a seven-point Likert scale.
 This variable was centered on zero ($-3$ - easier, $3$ - restricted).
@@
 
-I will present evidence from two different estimation strategies to capture the effect of crime framing in migration coverage on immigration attitudes.
-The first will exploit the case outlined above and a *difference-in-differences* (DiD) estimator to show the effect of the editorial change - and the related content shift - on migration attitudes:
+I will present evidence from a *difference-in-differences* (DiD) estimator to show the effect of the editorial change - and the related content shift - on migration attitudes:
 
 $$
-y_{it} = \alpha + \beta_1*Post_t + \beta_2 * BildReader_i + \beta_3 * Post_t * BildReader_i + \epsilon_{it} 
+y_{iw} = \alpha + \beta_1*Post_w + \beta_2 * BildReader_i + \beta_3 * Post_w * BildReader_i + \phi_w + \rho_i + \epsilon_{it} 
 $$
 
-The dependent variable $y_{it}$ indicates a respondent's migration attitude in a given survey wave, measured on the Likert scale described above.
+The dependent variable $y_{iw}$ indicates a respondent's migration attitude in a given survey wave, measured on the Likert scale described above.
 The conditioning variable $BildReader_i$ is a simple binary variable indicating whether respondents read *Bild* in the past week and is measured in the pre-treatment wave.
-$Post_t$ indicates whether an interview took place preceding or following the editorial change.
-The estimator of interest is $\beta_3$, which indicates the change in migration attitudes of *Bild* readers following the editorial change, controlling for pre-treatment differences ($BildReader_i$), as well as general pre-post shifts in migration attitudes ($Post_t$).
-
-## Difference of Treated and Untreated Units [or matching]
+$Post_w$ indicates whether an interview took place preceding or following the editorial change.
+The estimator of interest is $\beta_3$, which indicates the change in migration attitudes of *Bild* readers following the editorial change, controlling for pre-treatment differences ($BildReader_i$), as well as general pre-post shifts in migration attitudes ($Post_w$).
 
@@
 
-Despite the abundance of framing effects studies, no common standard of the magnitude of framing effects exists.
+Despite the abundance of framing effects studies, no common standard to assess the magnitude of framing effects exists.
 Even the correct measurement of the magnitude is a contested question, as different control groups can be compared [see @Chong2007a, 109f for a discussion].
 Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009a], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996].
-Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results seem to lie in between 10% and 25% of the scale when comparing pro and con arguments [@Lecheler2009a; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010], as most studies lack a neutral control group.
-As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [SOURCE], reported effects likely display a selection bias towards strong treatments.
-The treatment can be considered rather strong here, as the crime consideration is associated with strongly negative evaluations and the relative increase in the prevalence of this content is large.
-Additionally, given that readers already consumed that newspapers, the qualities of the sender should rather increase the effect size, while the high salience of the issue should decrease it.
-Given these considerations, I expect an effect of around 10% of the scale, or 0.6 on the seven-point scale[^1], which represents a conservative estimate.
+Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing pro and con arguments[^4] [@Lecheler2009a; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
+As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [see e.g.
+the recent debate regarding nudging effects: \@Maier2022], reported effects likely display a selection bias towards strong treatments.
+The treatment can be considered rather strong here, as the crime consideration is associated with strongly negative evaluations and the relative increase in the prevalence of this content is large \\footnote{6 percentage point increase compared to pre-treatment share of 8.36% in Bild (over 70% increase) and 6.75% in other newspapers (88.9% increase)}.
+Additionally, given that readers already consumed the newspaper, the qualities of the sender should rather increase the effect size, while the high salience of the issue should decrease it.
+Given these considerations, I expect an effect of around 10% of the scale, or 0.7 on the seven-point scale[^5], which represents a conservative estimate compared to reported experimental effects.
 
-[^1]: As the scale runs from one to seven, it spans six points wide.
+[^4]: As many studies do not include a control group, this is the most comparable metric.
 
-As suggested by @Laken2017, I also estimate equivalence bounds indicating the smallest effect size of interest (SESOI, indicated by dotted orange line in the graph), as well as a conservative estimate of the experimentally expected effect.
+[^5]: As the scale runs from one to seven, it spans six points wide.
+
+As suggested by @Laken2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI, indicated by dotted orange line in the graph), as well as a conservative estimate of the experimentally expected effect.
 I define the SESOI at a 2.5% change, or 0.15 on the seven-point scale, which represents a fraction of the conservative experimental estimate and sets a fairly low bar given the strong treatment.
@@
 Any effect estimated to lie within these bounds with statistical significance (i.e.
-a 90%-confidence interval in-between the positive and negative effect of this size) is too small to constitute a meaningful effect, as the hypothesis that the effect is *not* equivalent to zero can be rejected [see also @Peyton2020].
+a 95%-confidence interval in-between the positive and negative effect of this size) is too small to constitute a meaningful effect, as the hypothesis that the effect reaches any size of interest can be rejected [see also @Peyton2020].
 
@@
 
-## Effect on Migration Attitude
+## Effect on Migration Attitudes
 
@@
                   ) %>% 
-                  select(dv, post, treat, lfdn, wave_ctrl))
+                  select(dv, post, treat, lfdn, wave_ctrl),
+                cluster = c("lfdn", "wave_ctrl"))
 
@@
 t_ATT <- single_model$coeftable["postTRUE:treatTRUE", "t value"]
-p_ATT <- single_model$coeftable["postTRUE:treatTRUE", "Pr(>|t|)"]
+p_ATT <- single_model$coeftable["postTRUE:treatTRUE", "Pr(>|t|))"]
 
@@
 The dotted lines indicate the equivalence boundaries.
-If the 90% interval is contained within these boundaries, the hypothesis that the estimate is larger than the SESOI can be rejected.
-The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment (\$t = \$ `r round(t_ATT, 2)`, \$p = \$ `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.6)`% of the expected effect of 0.6.
-The 95% confidence intervals also contains values far smaller than the SESOI of 0.15 but clearly include the vertical red line indicating no change.
-Clearly, the model suggests a null effect.
+If the 95% interval is contained within these boundaries, the hypothesis that the estimate is larger than the SESOI can be rejected.
+The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment (\$t = \$ `r round(t_ATT, 2)`, \$p = \$ `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.7)`% of the expected effect of 0.7.
+The 95% confidence interval also contains values far smaller than the SESOI of 0.15 but clearly include the vertical solid red line indicating no change.
+Surprisingly, the model suggests a clear null effect.
 
@@
 
-DiDPlot(multi = F, scaled = "raw", theoretical_effect_size = 0.6, boundary_share = 0.25)
+DiDPlot(multi = F, scaled = "raw", 
+        theoretical_effect_size = 0.7, boundary_share = 0.25)
 
@@
 
-Figure \@ref(fig:multidv) shows standardized effects of the change in newspaper framing on immigration attitudes and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD.
-Dotted lines indicate a 20% standard deviation change, which has been defined as the standardized equivalence boundary in existing research [@Peyton2020, 599].
-All estimated effects are smaller in size than 0.05 standard deviations and associated 95%-confidence intervals contain zero.
-This means we can reject the hypothesis of meaningful effect size, but cannot reject that the estimate is statistically different from zero.
-All estimates suggest a clear null effect.
+## Effect on The Association of Crime and Migration Attitudes
 
-To address potential long-term effects of this change in migration framing, figure \@ref(fig:migwaves) assesses the effect in each post-wave compared to the pre-treatment wave.
-
-```{r migwaves, fig.cap="Effect of Change in Framing on Immigration Attitudes across Waves"}
-
-# add 0.9 confidence bar
-
-DiDByWavePlot(theoretical_effect_size = 0.6, boundary_share = 0.25)
-
-```
-
-## Effect on other dependent variables
-
-```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}
-
-# add 0.9 confidence bar
-
-DiDPlot(multi = T, scaled = T, theoretical_effect_size = 0.2) # 0.2 SD suggested by Peyton 2020, 599
-
-```
-
-## Tracing the Mechanism: the Association of Crime and Migration Attitudes
-
-As outlined above, framing theory suggests that increased exposure to a specific consideration about an issue leads to stronger association of an issue with this consideration.
+As outlined above, framing theory suggests that increased exposure to a specific consideration about an issue leads to stronger association of the issue with this consideration.
 In the present case, this should mean that the correlation of attitudes on immigration with attitudes about crime should increase.
@@
 
-## Outward Selection
+## Robustness
 
-# Conclusion: Framing Effects in the Real World
+### Effect across time
 
-This study estimated the causal effect of news framing on migration attitudes, exploiting a rare case of changing migration framing.
-Results indicate that this shift in news framing did not result in any change in migration attitudes.
-These findings add to a body of theoretical work and recent empirical findings questioning the media's influence on political attitudes [@Guess2021; @Lau2021a].
-Taken together, this research suggests that the influence of the news media on opinion formation in contemporary news environments with high levels of consumer choice and diverse exposure is severely limited.
-Even a major change in migration framing did not change respondents' attitudes in the present study.
-This does not necessarily entail that classic news media has no influence at all over opinion formation, but it might at the very least be restricted to specific "windows of opportunity".
-The present case described an established issue that had been in the center of public debate for 1.5 years.
-It might well be that news framing plays a more critical role for the evaluation of emerging issues.
-Further research should explore this possibility, assessing the impact of similar cases of changing news framing in the real world.
-It remains crucial, however, to focus on precise changes in *content*, in order to improve our conceptual understanding of the effects of media exposure.
+One reason for this null effect could be that a slowly unfolding long term effect is masked by initial absence of change.
+To assess whether an effect develops over time, figure \@ref(fig:migwaves) assesses the effect within split-samples for each post-wave compared to the pre-treatment wave.
+This allows the assessment of heterogeneous treatment effects across time.
+The black dots with associated confidence intervals indicate the estimated effect for each wave.
+The horizontal dashed line indicates the expected effect based on experimental evidence (0.7), whereas the dotted horizontal line indicates the SESOI of 0.15.
+The vertical (red) dashed line indicates the timing of the editorial change, whereas the dotted (orange) vertical line indicates the timing of the strong increase in crime framing in June 2017, several months after the takeover by Reichelt (see figure \@ref(fig:treatment)).
+It s visible that, over the course of the entire year 2017, the effect is clearly smaller than the SESOI, and includes zero.
+However, estimates for waves 7 and 8 in late 2018 and mid-2019 - more than one and a half years after the editorial change - showcase effects statistically different from zero, and including the SESOI boundary.
+Note however that the effect is still tiny, with a point estimate smaller than a 0.1 on the seven-point Likert scale, as well as an upper boundary just above the SESOI at ??.
+The waves in late 2019 and early 2020 have point estimates at similar lower levels (??, ??), but include zero again.
+Overall, this suggests an effect that remains below an effect size of minimal relevance.
 
-<!-- The setting more generally represents a least-likely case for the observation of media effects.
-The migration issue had been salient for one and a half years preceding the takeover, and opinions are likely chrystalized.
-The polarized nature of the topic should make it less likely that citizens will incorporate new information [@Taber2006; @Zaller1992].
-Additionally, Germany had a large debate about refugees and crime after the new year's eve 2015/16 in Cologne.
-According to a report of the ministry of interior in Northrhine-Westphalia, hundreds of women were sexually assaulted and robbed by men they perceived to be of "north-african/arabic" descent \footnote{see report of the ministry of interior in Northrhine-Westphalia: \url{https://web.archive.org/web/20160116104020/http://m.mik.nrw.de/fileadmin/user_upload/Redakteure/Dokumente/Themen_und_Aufgaben/Schutz_und_Sicherheit/160111ssia/160111berppkoeln.pdf}}.
-This debate could serve as 'pre-treatment' and as such prevent further attitudinal change [@Druckman2012].
-Lastly, the political parties in Germany had taken clear and visible positions on migration, providing citizens with strong party cues from which they could infer positions in case they didn't hold strong attitudes themselves [@Slothuus2021].
--->
+```{r migwaves, fig.cap="Effect of Change in Framing on Immigration Attitudes across Waves"}
 
-<!-- might add: election campaign might expose people to more debate, plus general shift towards more restrictive attitudes ("Zeitgeist") -->
+# add 0.9 confidence bar
+
+DiDByWavePlot(theoretical_effect_size = 0.7, boundary_share = 0.25)
+
+```
+
+### Effect on other alternative dependent variables
+
+While immigration attitudes remain unaffected, it might well be that an increased exposure to crime framing increases individual perceptions of the importance of migration, despite not changing attitudes, or that it raises concerns about the integration rather than the immigration of migrants.
+Similarly, support for the radical-right *AfD* as owner of the migration issue might increased as a result of increased exposure to crime frames.
+Figure \@ref(fig:multidv) displays standardized effects of the change in newspaper framing on immigration attitudes (as reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see Appendix ??
+for precise variable descriptions).
+Dotted lines indicate a 0.2 standard deviation change, which has been defined as the standardized equivalence boundary in existing research [@Peyton2020, 599].
+All estimated effects are smaller in size than 0.05 standard deviations and associated 95%-confidence intervals contain zero.
+This means we can reject the hypothesis of meaningful effect size, but cannot reject that the estimate is statistically different from zero.
+All estimates suggest a clear null effect.
+
+```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}
+
+# add 0.9 confidence bar
+
+DiDPlot(multi = T, scaled = T, 
+        theoretical_effect_size = 0.2) # 0.2 SD suggested by Peyton 2020, 599
+
+```
+# Mechanism
+
+## Effect on News Consumption
+
+```{r selectionModel}
+
+m_sel <- SelectionModel()
+
+```
+
+As the migration framing in Bild becomes more conservative, this could also lead readers with more liberal migration attitudes to stop reading the newspaper, as they avoid information challenging their views.
+Figure \@ref(fig:selection) shows the share of initial readers that report reading Bild at later stages.
+The three different lines describe three different groups, based on their initial migration attitude.
+If readers reacted by selective exposure, one would expect that liberal readers' share would drop more significantly than conservative reader's share, as they actively select out of the newspaper.
+As one can see, that is not the case.
+Liberals' and conservatives' share of readers track each other closely, with those reporting liberal migration attitudes in the first wave even reporting to read Bild at *higher* shares than conservatives in later waves.
+What is interesting is that those reporting neutral migration attitudes seem to be more inclined to leave the newspaper: Neutral readership declines to a level of 57%, around 5 percentage points below the share reported by liberals (62%) and 3pp below the level of conservatives (60%).
+Regressing individual choice to read *Bild* in later waves on initial reported migration attitudes within the subsample of initial *Bild* readers shows a `r round(m_sel$coefficients[["init_mig_groupsNeutral"]], 2)*-100`% lower chance to report Bild readership among initial neutral readers, compared to liberal readers ($p =$ `r round(summary(m_sel)$coefficients["init_mig_groupsNeutral", "Pr(>|t|)"], 3)`), whereas there is no significant or substantial difference for conservative readers.
+Surprisingly, *Bild* readers reporting centrist immigration attitudes select out of the newspaper at higher rates than both conservative or liberal readers, whereas there is no meaningful difference between the latter two.
+
+```{r selectionPlot, fig.cap="Share of initial Bild readers reporting readership in later waves by initial migration attitude. Dashed (red) vertical line indicates editorial change."}
+
+OutSelection()
+
+```
+
+## Openness to Change
+
+```{r MigChange, fig.cap="Change in individual immigration attitudes 2016-2018, compared to 2014-2016. Data taken from the GLES Longterm Panel (SOURCE)."}
+
+MigChangePlot()
+
+MigChangeTable <- MigChangePlot(return_table = T)
+
+```
+
+As readers did not react by selecting out of the newspaper, the question emerges *why* readers did not react to the change in coverage.
+A possible explanation is that individuals informed themselves about the issue and formed an attitude once the issue emerged, in this case in 2015 during the large migratory movements in Europe.
+If that were the case, opinions should change more from 2014 to 2016 compared to the 2016-2018 period.
+Figure \@ref(fig:MigChange) shows this statistic using GLES Longterm Panel data [SOURCE].
+The top panel shows the absolute change in migration attitudes from 2014-2016.
+That is, if a respondent held an attitude of 3 (leaning conservative) on the ten-point scale in 2014 and moved to 2 in 2016, their migration attitude would change by 1.
+Immigration attitudes in the GLES sample shifted on average by `r round(MigChangeTable["2014-2016",][["change_mean"]], 2)` from 2014 to 2016 (lower 95% confidence interval `r round(MigChangeTable["2014-2016",][["change_lower"]], 2)`, upper `r round(MigChangeTable["2014-2016",][["change_upper"]], 2)`), while they shifted significantly less in the period 206-2018 (`r round(MigChangeTable["2016-2018",][["change_mean"]], 2)`; [`r round(MigChangeTable["2016-2018",][["change_lower"]], 2)`, `r round(MigChangeTable["2016-2018",][["change_upper"]], 2)`]).
+
+It becomes apparent that individual migration attitudes stabilised after 2015.
+This evidence is in line with the idea that migration attitudes were only responsive in 2015, when the newspaper did not follow other tabloids in their aggressively negative portrayal of refugees and their impact on society at large.
+When the newspaper changes its migration coverage one and a half years later, the critical window of opportunity seems to have closed, as migration attitudes had crystallized.
+
+# Conclusion: Windows of Opportunity for News Framing Effects
+
+The presented results are robust evidence that, despite an over 70% increase of the emphasis of crime in migration content of Germany's largest newspaper, its readers migration attitudes remained surprisingly unaffected.
+Effect estimates remain below minimal thresholds across time.
+Related dependent variables such as integration attitudes, reporting migration as the most important problem, and support for the radical-right AfD do not deviate from those of other readers.
+Migration attitudes are not increasingly associated with crime attitudes in this group, nor are liberal Bild readers more likely to stop reading the newspaper, nor conservative non-readers more likely to report reading it.
+
+These findings substantially question the external validity of experimental framing studies.
+While it is well-established that exposure to single frames can substantially affect political attitudes in survey- and laboratory experiments, this does not seem to easily translate into real world contexts.
+
+Several potential explanations for this difference come to mind.
+The most likely is certainly selective exposure.
+Although no evidence for selective exposure on the outlet level could be found, readers might still select content *within* the outlet - that is, they skip articles contradicting their worldview or simply do not engage with the content on a cognitive level.
+Alternatively, the diversity of contemporary media environments might expose individuals with so many different frames that political attitudes are ultimately stabilized.
+The framing of individual outlets is crowded out by the many outlets which are consumed.
+
+While these findings are worrisome for framing scholars, they are generally good news for democracy: even when outlets try, they cannot simply manipulate their audience's political attitudes with a snap of their finger.
+Worries about the undermining of democracy trough the takeover of partisan news outlets might be overstated, as consumers either seem to hold a critical distance to their news outlets or consume content from so many outlets that a single one has not much influence.
+Descriptive data about American news diets supports this interpretation [@Guess2021a].
+
+This study suffers from several limitations regarding the generalizabilty of the case at hand.
+First, the immigration issue was already highly salient for one and a half years when Reichelt took over *Bild*.
+This means that attitudes have possibly crystallized as the result of personal reasoning, exposure to information, or cues from one's preferred party.
+Second, while tabloids are often seen as manipulators of public opinion [@Foos2022], they also contain less political content and might be taken less seriously when they write about politics.
+Readers from other outlets might react differently.
+Lastly, Bild readers differ from other readers in many ways, among others they are more conservative and less knowledgeable about politics (see Appendix ??).
+Readers of other outlets might react differently to increased exposure to crime frames.
+
+This study offers several takeaways for future research.
+First, and most importantly, the study suggests caution in the generalization of experimental results to the real world.
+More observational research of framing effects would help in the mapping out of scope conditions for framing effects.
+The present study presented one approach how this can be done.
+On the other hand, experimental research could try to explore external validity issues further, assessing the existence of 'crowding out' effects, as well as conditions for and types of selective exposure.
 

### 2022-08-24 paper/appendix.Rmd
Add LTP DiD and Change plot
Improve plot and variable description migration attitudes

@@
 
+# Change in Migration Attitudes across time
+
+```{r}
+
+MigChangePlot()
+
+```
+
+[Add description of variable and explanation]
+
 # Difference-in-Differences Estimates
@@
 
+## Effect in Longterm-Panel
+
+### Reichelt
+
+```{r LTPDiD, fig.height=2}
+
+LTPDiD()
+
+```
+
+```{r LTPDiD_table}
+
+LTPDiD(return_table = T)
+
+```
+
 ## Variable: Immigration Attitudes
@@
 
-(1) 1 Zuzug von Ausländern erleichtern
-(2) 2\
-(3) 3\
-(4) 4\
-(5) 5\
-(6) 6\
-(7) 7 Zuzug von Ausländern einschränken
+(1) Zuzug von Ausländern erleichtern
+(2)
+(3)
+(4)
+(5)
+(6)
+(7) Zuzug von Ausländern einschränken
 
@@
 fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
-  filter(init_mig_groups != "", !is.na(`1130_clean`), !is.na(treat)) %>% 
+  filter(!is.na(`1130_clean`), !is.na(treat)) %>% 
   group_by(treat, wave) %>% 
@@
     date_clean = min(date_clean, na.rm = T),
-    `1130_clean` = mean(`1130_clean`, na.rm = T)
+    mig_mean = mean(`1130_clean`, na.rm = T),
+    mig_sd = sd(`1130_clean`, na.rm = T),
+    N = n()
   ) %>% 
-  ggplot(aes(x = date_clean, y = `1130_clean`, lty = !treat, col = !treat)) +
+  mutate(
+    mig_lower = mig_mean + qt(0.025, df = N-1) * (mig_sd/sqrt(N)),
+    mig_upper = mig_mean + qt(0.975, df = N-1) * (mig_sd/sqrt(N))
+  ) %>% 
+  ggplot(aes(x = date_clean, y = mig_mean,
+             ymin = mig_lower, ymax = mig_upper,
+             lty = !treat, col = !treat)) +
   geom_line() +
+  geom_pointrange() +
   geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
-  # facet_wrap(~init_mig_groups, ncol = 1) + 
-  theme_minimal()
+  theme_minimal() +
+  labs( x = "", y = "", col = "Readership", lty = "Readership") +
+  scale_color_manual(labels = c("Bild", "Never Bild"),
+                     values = MetBrewer::met.brewer("Archambault", 2)) +
+  scale_linetype_manual(labels = c("Bild", "Never Bild"),
+                     values = c(1,2))
 

### 2022-08-24 paper/Manuscript_Framing.Rmd
Incorporate TM comments (1)

@@
 The findings show that, despite a major change in migration framing, immigration attitudes and related variables remain unaffected.
-News framing only seems to be effective within limited opportunity windows during the emergence of political issues."
+News framing seems to affect attitudes only within limited windows of opportunity early in the politicization of political issues."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
+nocite: |
+  @CologneReport2016
 ---
@@
 Does news framing affect public opinion?
-While a large body of experimental evidence suggests that the emphasis of a certain consideration can substantially alter issue attitudes, we know little about how these findings translate into real-world environments.
+While a large body of experimental evidence suggests that the emphasis of a certain consideration can substantially alter issue attitudes, we know little about the translation of these findings into real-world environments.
 Prior work has shown that the external validity of such experiments might be seriously complicated by environments of diverse frames [@Chong2013] and actors [@Slothuus2010], as well as the seeking and avoidance of specific content [@Lau2021a; @Taber2006].
+Especially on contested issues, citizens might be more inclined to resist persuasion [@Arceneaux2009].
 Contemporary news environments provide consumers with especially diverse content and maximize their abilities to choose specific outlets and avoid others [@Bennett2008], thereby increasing the gap between the real-world environment and experimental studies.
 Additionally, the very nature of experiments is prone to over-estimate effects in the real world [@Barabas2010].
+This is the reason why, fifteen years ago, Donald Kinder called for framing research to extend its toolkit: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception.
+[...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157; see also @Busby2019; @Leeper2020].
 
-Following similar considerations, Donald Kinder called for framing research to extend its toolkit: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception.
-[...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157; see also @Busby2019; @Leeper2020].
-To the author's knowledge, no study has yet answered this call to provide an estimate of framing effects in the real world.
-
-I address this gap in the literature by exploiting a rare and naturally occuring shift in the migration framing of Germany's largest tabloid newspaper, *Bild*.
-The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet substantially changed it's framing while other papers maintained theirs.
+I provide the - to my knowledge - first observational estimate of framing effects by exploiting a rare shift in the migration framing of Germany's largest tabloid newspaper, *Bild*.
+The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet substantially changed its framing while other papers maintained theirs.
 By employing BERT models for the measurement of crime frames in a corpus of 2.5 million newspaper articles, I am able to clearly identify the treatment - something that is usually left to experimental studies.
@@
 
-The results indicate that even this strong change in news framing did not affect consumers' immigration attitudes.
-The estimated effect is statisticially indistinguishable from zero, and significantly smaller than even minimal relevant effect magnitudes.
-Other variables, such as related issue attitudes, issue importance, and voting intentions are similarly unaffected.
-Additional evidence suggests that readers do also not react by turning away from the newspaper.
-Overall, these results fundamentally challenge the external validity of framing effects research and suggest that the influence of individual news outlets on public opinion is rather limited.
-Even strong changes in news framing do not affect political attitudes or news consumption.
+[might want to mention frames in mind and frames in communication distinction here and how it informs research design (follow Rune & Martin Bisgaard)]
 
-The paper will proceed as follows: in the next section I will briefly introduce the theoretical framework of emphasis framing and derive hypotheses about the impact of news framing on political attitudes.
-I will then discuss the limited external validity of framing effects studies, before I turn to the research design, including case, measurement, and estimation strategy.
-The results section will then showcase evidence from difference-in-differences models assessing the impact of changing migration framing on migration attitudes.
-Lastly, I discuss the wider implications of the findings for the study of framing effects and our understanding of the role of news media in the opinion formation process.
+The results indicate that even a strong increase in the use of crime frames did not affect consumers' immigration attitudes.
+The estimated effect is statistically indistinguishable from zero and significantly smaller than even minimal effect magnitudes.
+Related issue attitudes, voting behaviour, and issue importance are similarly unaffected, as is the association of immigration attitudes with the frame provided.
+Additional evidence implies that immigration attitudes had crystallized at the time of the shift, such that individuals were immune to changing framing.
 
-# Emphasis Framing
+Overall, these results fundamentally challenge the external validity of framing effects research and suggest that the influence of individual news outlets on public opinion is more limited than previously thought.
+Even a strong change in news framing did not affect political attitudes.
+Instead, it seems that timing is a crucial factor in the effectiveness of news frames.
+
+# Framing Effects on Public Opinion
 
 "Framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy" [@Nelson1997Rally].
-A "frame" is then the operating unit of this process, defining the issue at hand in a specific way.
-Different forms of frames have been conceptualised.
+Different forms of frames have been conceptualized.
 When I talk about 'frames' here, I refer to *emphasis frames*.
-These frames emphasise certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame [@Leeper2020, 152].
+These frames emphasize certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame [@Leeper2020, 152].
 For example, issues of increasing welfare contributions might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes.
 Individuals' support of a statement will differ dependent on the frame presented [@sniderman2004structure].
+Many other forms of framing exist, such as equivalence frames [@Kahneman1979prospect], episodic frames [@Iyengar2005], or generic frames [@DeVreese2005].
+The focus on emphasis frames in this study is owed to the large body of literature and generalized theory regarding their effect on attitudes about any issue (as opposed to generic and episodic frames), as well as their prevalence in the news media (which is not the case for equivalence frames).
 
-Work using the emphasis framing concept of framing - as opposed to other definitions like equivalence frames [@Kahneman1979prospect], episodic frames [@Iyengar2005], or generic frames [@DeVreese2005] - mostly builds on the expectancy-value model developed by @Ajzen2000.
-This model suggests that an attitude on a given issue is a function of two things: considerations relating to that object and their respective weights.
-The evaluation of the issue is subdivided into a number of considerations [a so-called "frame in thought"; @Chong2007a, 105; @Kinder1996], which will carry clear evaluations.
+Work using the emphasis framing concept of framing mostly builds on the expectancy-value model developed by @Ajzen2000.
+This model suggests that an attitude on a given issue is a function of two things: the value of considerations relating to that issue and the strength of their association with the issue.
+The evaluation of the issue is subdivided into a number of considerations [a "frame in mind"; @Chong2007a, 105; @Nelson1996], which will carry clear evaluations.
 For example, to form an opinion about whether immigration to one's country should be restricted, a person might consider the humanitarian conditions in the countries of origin (negative consideration regarding restrictive migration policy), as well as the risk of increased crime (positive consideration; note that the model does not differentiate whether a consideration is grounded in objective reality).
@@
 Figure \ref{fig:cogStor} visualizes this logic.
-A given issue is associated with an attitude $y$.
-The issue is related to a number of different considerations, each of which carries an associated evaluation $x_i$, e.g.
-that crime is bad.
-Each of these considerations is more or less associated with the issue.
-Based on the strength of this association $w_i$, a given consideration's evaluation is more or less reflected in the issue evaluation $y$, which is equal to the weighted sum of considerations.
+A given issue (bottom square) carries an attitude $y$.
+The issue is associated with a number of different considerations (top circles), each of which carries an evaluation $x_i$, e.g.
+crime is viewed very negatively.
+Based on the strength of the association $w_i$ of a given consideration with the issue, a given consideration's evaluation is more or less reflected in the issue evaluation $y$, which is equal to the weighted sum of considerations.
+For example, if a given individual associates immigration strongly with an increase in criminal activity, welfare fraud, but only very weakly with humanitarian considerations, cultural enrichment, liberty, or economic growth, they will form a rather negative attitude about the issue, as the former factor more prominently in their reasoning about migration.
 
@@
 ```
+
 How does this model incorporate news content and other forms of political communication?
-News content can emphasize different considerations of an issue [so called "frames in communication" @Kinder1996].
-This strengthens the cognitive association of the issue at hand with the raised consideration.
-As a result, this specific consideration factors more prominently in an individuals' attitude formation process: "media frames influence opinions by stressing specific values, facts, or other considerations, endowing them with greater apparent relevance to the issue than they might appear to have under an alternative frame" [@Nelson1997Rally, 569].
+News content can emphasize different considerations of an issue [so called "frames in communication" @Nelson1996].
+By being exposed to the consideration, an individual's cognitive association of the issue at hand with the raised consideration strengthens (or in more technical terms: the weight of the consideration $w_i$ increases).
+As a result, this specific consideration factors more prominently in the formulation of an overall attitude: "media frames influence opinions by stressing specific values, facts, or other considerations, endowing them with greater apparent relevance to the issue than they might appear to have under an alternative frame" [@Nelson1997Rally, 569].
 
 Applying this to the issue of migration policy and the consideration of criminal migrants, one can imagine a news consumer confronted with an increased volume of news about crimes committed by migrants.
-The value-expectancy model predicts that the consumer forms a cognitive definition of migration that is increasingly associated with the issue of crime, meaning this consideration features more prominently when forming an opinion about the appropriate level of immigration policy.
-As a result, their opinion about migration policies should become more restrictive.
+The value-expectancy model predicts that 1) the consumer forms a cognitive definition of migration that is increasingly associated with the issue of crime, meaning this consideration features more prominently when forming an opinion about the appropriate level of immigration; 2) as a result, their opinion about migration policies should become more restrictive, as the negative consideration of crime is weighted more heavily in the evaluation of the migration issue.
 
-***Association hypothesis*****: When an individual is exposed to a specific consideration about an issue, their association of the issue with this consideration should be strengthened.**
+***Association hypothesis*****: When an individual is exposed more to a specific consideration about an issue, their association of the issue with this consideration should be strengthened.**
 
-***Evaluation hypothesis*****: When an individual is exposed to a specific positive/negative consideration about an issue, their attitude about the overall issue should become more positive/negative.**
+***Evaluation hypothesis*****: When an individual is exposed more to a specific positive/negative consideration about an issue, their attitude about the overall issue should become more positive/negative.**
 
@@
 
-Research on framing has shown for decades that citizens' attitudes and their issue associations are highly reactive to minor changes in the emphasis of specific considerations.
+Research on framing has shown for decades that citizens' attitudes and their issue associations are highly reactive to minor changes in the emphasis of specific considerations [@Chong2007; @Chong2010; @Druckman2012Bias; @Kinder1990; @Nelson1996; @Nelson1997; @sniderman2004structure; for reviews see @Busby2019; @Druckman2001; @Leeper2020].
 However, it remains unclear how well these experimental findings translate into the real world.
-Especially when it comes to the exposure to frames in communication, translating framing effects from experimental studies is only possible under strong assumptions: While framing studies usually simply present a news article or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience.
-Additionally, changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news outlets containing such frames (and vice versa seek out attitudinally congruent information).
-This idea of 'selective exposure/avoidance' [@Bennett2008], or a a 'confirmation bias' [@Taber2006] brings with it a major endogeneity problem making purely correlational evidence of framing effects rather uninformative.
+First, taking experimental effects as estimates of the real-world impact of framing means making strong assumptions about citizens' exposure to frames: while framing studies usually simply present a news article or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience.
+Changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news outlets containing such frames (and vice versa seek out attitudinally congruent information).
+This idea of 'selective exposure/avoidance' [@Bennett2008], or a 'confirmation bias' [@Taber2006] brings with it a major endogeneity problem making purely correlational evidence of framing effects rather uninformative.
 
-Even if we assume that the consumer receives the content, e.g.
-buys a newspaper, visits its website, or is exposed otherwise, it is not clear whether the content is actually consumed.
-E.g., a reader might well buy a newspaper but skip an article after reading the headline because the topic is not of interest or the frame is at odds with their existing attitude [@Lau2021a].
-As most framing studies do not offer choice of content to respondents, engagement remains an assumption in experimental studies.
-Additionally, even when consuming the content, motivated reasoners presented with a plethora of news content about an issue will spend less time and cognitive energy on counter-attitudinal arguments than those supporting their viewpoint, lending more importance to considerations raised by amenable content [@Taber2006].
+Second, even if one assumes that the consumers receive the content, (e.g.
+buy a newspaper, visit a website, ...), it is not clear whether the content is actually consumed.
+For example, a reader might well buy a newspaper but skip an article after reading the headline because the topic is not of interest or the frame is at odds with their existing attitude [@Lau2021a].
+As most framing studies do not offer choice of content to respondents, engagement remains an assumption when taking experimental studies as evidence of framing effects in the real world (for an exception see @Druckman2012Bias).
+Additionally, information from different sources, such as TV, social media, blogs, newspapers, ..., might 'crowd out' the framing of a single outlet: By consuming content from many sources, individuals might give less attention to a single outlet, thereby severely limiting the overall impact of that outlet's coverage.
+
+Third, even when consuming the content, cognitive engagement with it might strongly differ in the real world compared to experimental contexts.
+Motivated reasoners presented with a plethora of news content about an issue will spend less time and cognitive energy on counter-attitudinal arguments than those supporting their viewpoint, lending more importance to considerations raised by amenable content [@Taber2006].
 Experimental studies presenting only one frame per issue cannot take this bias into account.
+Consumption might also result in better or worse comprehension in the real world because respondents might pay more or less attention to real news content compared to experimental treatments [@Barabas2010].
+Furthermore, there might be differences in how easily this translates into changing cognitive associations, given that those exposed might take real-world content more seriously.
+Additionally, the relative timing at which a frame is received, relative to other frames and the salience of the issue, affects the way in which individuals react to framing.
+Those citizens who received a different frame earlier might already have formed a crystallized opinion about the issue and thus reject subsequent attempts of persuasion [@Bechtel2015; @Druckman2012Bias; @Lecheler2009b].
 
-These assumptions of exposure, consumption, and equal engagement in classic framing studies already represent a high hurdle for the translation of experimental estimates of framing effects into the real world.
-However the differences do not end there.
-Consumption might result in better or worse comprehension in the real world because respondents might pay more or less attention to real news content compared to experimental treatments [@Barabas2010].
-Even after understanding the frame, there might be differences in how easily this translates into changing cognitive associations, given that those exposed might take real-world content more seriously.
-
-To summarize, framing might have very different consequences in real-world environments than their experimental emulations.
-When we take the experimental evidence as an approximation of the effectiveness of framing in the real world, we make strong assumptions about citizens' exposure to, consumption of, and engagement with the frames in news content.
+To summarize, there are many reasons to assume that framing might have very different consequences in real-world environments than in their experimental emulations, and the above list is by no means comprehensive.
+When we take the experimental evidence as an approximation of the effectiveness of framing in the real world, we make many strong assumptions about citizens' exposure to, consumption of, and engagement with the frames in news content.
 Experiments can only incorporate few characteristics of the real world at a time.
@@
 
-Several scholars have arrived at this conclusion and called for the assessment of framing effects beyond experimental studies [@Busby2019; @Kinder2007; @Leeper2020], yet the call has rarely been answered.
-While a large body of media effects research exists, it has not paid specific interest to framing, instead assessing the impact of changing news exposure broadly in observational designs [see e.g.
-@Foos2022; @Grossman2022 @Levendusky2022; @Spirig2020] and field experiments [@Bail2018; @Broockman2022; @Guess2021].
+Despite repeated calls for the assessment of framing effects beyond experimental studies [@Busby2019; @Kinder2007; @Leeper2020], there is little research addressing this concern.
+While a large body of observational media effects research exists, it has not paid specific interest to framing, instead assessing the impact of changing news exposure broadly [@Bail2018; @Broockman2022; @Foos2022; @Grossman2022; @Guess2021; @Levendusky2022; @Spirig2020].
 
-The precious small body of existing research on framing effects is often riddled with endogeneity concerns or compound treatments.
-For example, @Jerit2008 investigates the effects of framing on public opinion compared to addressing the opponent's issue.
-She finds that reframing is less effective than engagement with the opposite parties' frames, a finding that suggests that framing is not very effective.
-However, this study does not provide an estimate of a causal effect, instead restricting itself to the assessment of correlational evidence.
-This is especially problematic regarding framing effects, as news content can affect consumers' inclination to consume news (see preceding section), and political actors might react to public opinion.
-Others show with similar correlational designs that only specific frames seem to drive issue importance [@Mclaren2018], but do not assess effects on attitudes.
+The precious small body of existing observational research on framing effects is often riddled with endogeneity issues.
+For example, @Jerit2008 investigates the effects of news framing on public opinion.
+She finds that framing is less effective in changing public opinion than engagement with opposing considerations, a finding that suggests that framing is rather ineffective.
+However, her study restricts itself to the assessment of correlational evidence.
+This is especially problematic regarding framing effects, as news content can affect consumers' inclination to consume news (see preceding section), and political actors might react to public opinion, thereby creating endogeneity issues.
+Others show with similar designs that only specific frames seem to drive issue importance [@Mclaren2018], but do not assess effects on attitudes.
 
@@
 @Slothuus2010b takes advantage of a sudden shift in a political parties' framing of retirement benefits, and shows that this changed framing has substantial impact on party supporters' attitudes about the issue.
-However, it is unclear how these findings translate to news framing effects, as it is impossible to distinguish the effect of partisan cue-taking from the persuasive effect of the frame itself.
+However, it is unclear how these findings translate to news framing effects.
+Given that - in this case - a positional change coincided with the changing framing of the issue and parties' special role in citizens' information process, it is impossible to distinguish the effect of partisan cue-taking from the persuasive effect of the frame itself.
+
 The only study which assesses the precise impact of changing news content on political attitudes comes from @Djourelova2020.
@@
 While the study itself reveals impressively how language can shape political attitudes, it constitutes a highly specific case and a rather minor change in the framing of migration.
-While news stories might lack the term "illegal migrant", they might still extensively cover crimes committed by migrants and thus associate migration with crime.
+To gain a deeper understanding of how specifically framing affects immigration attitudes, it is necessary to assess broader changes in the representation of the immigration issue.
 
-Summarized, we lack an understanding of how framing affects political opinions in the real world.
+In sum, we lack an understanding of how framing affects political opinions in the real world.
 While experimental evidence suggests rather strong effects, it is unclear how these findings translate to the outside world.
-Observational evidence on media effects is abundant but has not studied precisely what the impact of framing is.
+Observational evidence on media effects is abundant but has not precisely studied the impact of framing.
 The present study therefor exploits a naturally occurring change in the news framing of a particular issue *within* a specific outlet to isolate the effects of news framing on political opinions.
@@
 
-In order to test whether changing news content - rather than a shift in the consumed news outlet - affected political attitudes, I exploit an editorial change in the largest German newspaper, *Bild*.
+In order to test whether changing news content affected political attitudes, I exploit an editorial change in the largest German newspaper, *Bild*.
 As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts.
@@
 
-In December 2016, Axel Springer, the company owning Bild, announces that Diekmann will leave the company.
-Less than a week after, it becomes public that prosecutors investigate Diekmann for sexual harassment.
+In December 2016, Axel Springer, the company owning Bild, announced that Diekmann will leave the company.
+Less than a week after, it became public that prosecutors investigate Diekmann for sexual harassment.
 While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time support this interpretation of events.} [@Spiegel2017Diekmann].
@@
 In a speech months before he took over the position as chief editor, Reichelt outlined his motivation for such a shift in migration coverage: "I can assure you: nothing has hurt [*Bild*] economically as much as our clear, humane, empathetic stance in the refugee crisis" \footnote{Reichelt in a speech at Deutschlandfunk's conference "Formate des Politischen 2016": \url{https://vimeo.com/190347766}}.
-He also argued that the German media shows too little tolerance towards anti-immigration attitudes and therefor excludes those holding such views from the political discourse.
+While he expressed his support for the decision to take this stance at the time, he argued that the German media shows too little tolerance towards anti-immigration attitudes and therefore excludes those holding such views from political discourse.
 
-This presents a unique case to study the effects of media content on public opinion.
-The shift in content can be clearly identified.
+This case presents a unique case to study the effects of media content on public opinion.
+As will be shown below, a shift in migration coverage can be clearly identified.
 The change of editor itself was not discussed in the media, which means any opinion changes among readers are the result of the changing content [@Spirig2020].
@@
 In summary, *this case is as close as possible to a field experiment in which a specific consideration of migration coverage is amplified in the coverage of one newspaper, but not others*.
+
+[Outline research design, measurement of frames in communication and thought, following RUne and Martin Bisgaard]
 
@@
 
-To identify whether an article is about migration, i employ supervised machine learning.
+To identify whether an article is about migration, I employ supervised machine learning.
 As migration content is rare, and training data needs to be somewhat balanced, articles cannot be selected randomly for annotation[^1].
@@
 Figure \@ref(fig:salience) shows the share of migration articles in each newspaper.
-Clear peaks in attention are visible surrounding the refugee movements of summer 2015, as well as following the large-scale sexual assaults on new years eve in Cologne 2016[^2], and a conflict over asylum policy between the conservative sister parties CDU and CSU, which almost lead to the breakdown of the governing coalition in 2018.
+Clear peaks in attention are visible surrounding the refugee movements of summer 2015, as well as following the large-scale sexual assaults on new years eve in Cologne 2016\footnote{Germany had a large debate about refugees and crime after the new year's eve 2015/16 in Cologne.
+According to a report of the ministry of interior in Northrhine-Westphalia, hundreds of women were sexually assaulted and robbed by men they perceived to be of "north-african/arabic" descent (Ministerium für Inneres und Kommunales des Landes Nordrhein-Westfalen 2016).}, and a conflict over asylum policy between the conservative sister parties CDU and CSU, which almost led to the breakdown of the governing coalition in 2018.
 Newspapers seem to be event-driven and follow largely parallel trends, albeit at different levels, with the centre-left \textit{SZ} discussing migration most and the tabloid \textit{Bild} least.
@@
 
-[^2]: Germany had a large debate about refugees and crime after the new year's eve 2015/16 in Cologne.
-According to a report of the ministry of interior in Northrhine-Westphalia, hundreds of women were sexually assaulted and robbed by men they perceived to be of "north-african/arabic" descent (see report of the ministry of interior in Northrhine-Westphalia: \\url{[https://web.archive.org/web/20160116104020/http://m.mik.nrw.de/fileadmin/user_upload/Redakteure/Dokumente/Themen_und_Aufgaben/Schutz_und_Sicherheit/160111ssia/160111berppkoeln.pdf}](https://web.archive.org/web/20160116104020/http://m.mik.nrw.de/fileadmin/user_upload/Redakteure/Dokumente/Themen_und_Aufgaben/Schutz_und_Sicherheit/160111ssia/160111berppkoeln.pdf%7D%7D))
-
 To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest.
 Using a training set of 1400 articles, a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%.
-I then apply this classifier to classify the approximately 90,000 articles about migration identified by the first classifier.
+I then apply this classifer to identify the approximately 90,000 articles about migration identified by the first classifier.
 About 7% of all migration coverage consists of articles about some form of crime\footnote{See appendix 1.2 for more information about the classifier, training process and data.}.
-The share of migration content devoted to news about crime within a given time frame allows me to assess how prominent the consideration of crime as a result of migration was at a specific point in time.
-In order to give an example of the content, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* most likely discussing crime according to the classifier.
+The share of migration content devoted to news about crime allows me to assess the prominence of the consideration of crime within migration coverage.
+As an example of the content, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood.
 All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about new years eve in cologne.
@@
 ```
+
 The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line).
 As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased briefly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change.
-The trends run largely parallel to each other preceding the treatment, with the major exception being the few months following the events at new year's eve in Cologne 2015/16[^3].
+The trends run largely parallel to each other preceding the treatment, with the major exception being the few months following the events at new year's eve in Cologne 2015/16\footnote{Note that the delayed increase in crime coverage and the low levels of attention to crime in *Bild*'s migration coverage in 2016 are partially the result of a changing number of articles being published.
+This can be traced back to a changing share of content from the German news agency *dpa*, which provides services to quickly distribute news content similar to the Associated Press.
+Estimates excluding content from *dpa* indicate a change in attention to crime of similar size, as can be seen in appendix 1.}.
 The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in Bild.
 One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, while other newspapers maintained their levels of attention.
-
-[^3]: Note that the low levels of attention to crime in Bild's migration coverage in 2016 are partially the result of changing arrangements with a German news agency *dpa*, which provides services to quickly distribute news content similar to the Associated Press.
-Estimates excluding content from *dpa* indicate a change in attention to crime of similar size, as can be seen in appendix XX.
 
@@
 
-## Measuring Frames in Mind
+## Measuring Frames in Thought
 
-In order to assess the impact of this change in framing on migration attitudes, it is necessary to use data on consumers' immigration attitudes, as well as their news consumption.
+In order to assess the impact of this change in framing on public opinion, it is necessary to use data on consumers' immigration attitudes, as well as their news consumption.
 The 2017 Election Panel by the German Longitudinal election study luckily contains this data.
@@
 Responses were recorded on a seven-point Likert scale.
-This variable was centered on zero ($-3$ - easier, $3$ - restricted).
+This variable was centered on zero ($-3$ - easier, $3$ - restricted; the precise wording in the survey can be found in appendix 3.2).
 
@@
 
-The dependent variable $y_{iw}$ indicates a respondent's migration attitude in a given survey wave, measured on the Likert scale described above.
+The dependent variable $y_{iw}$ indicates respondent $i$'s migration attitude in a given survey wave $w$, measured on the Likert scale described above.
 The conditioning variable $BildReader_i$ is a simple binary variable indicating whether respondents read *Bild* in the past week and is measured in the pre-treatment wave.
@@
 
-Despite the abundance of framing effects studies, no common standard to assess the magnitude of framing effects exists.
-Even the correct measurement of the magnitude is a contested question, as different control groups can be compared [see @Chong2007a, 109f for a discussion].
+To provide a baseline expectation regarding the effects, it is useful to consider the expected effect size at this point.
+Despite the abundance of framing effects studies, there is no common standard to assess the magnitude of framing effects.
+Even the correct measurement of the magnitude is a contested question, as different control groups (untreated, opposing frame, ...) can be compared [@Druckman2001; @Chong2007a, 109f for a discussion].
 Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009a], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996].
-Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing pro and con arguments[^4] [@Lecheler2009a; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
+Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing pro and con arguments\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009a; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
 As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [see e.g.
-the recent debate regarding nudging effects: \@Maier2022], reported effects likely display a selection bias towards strong treatments.
-The treatment can be considered rather strong here, as the crime consideration is associated with strongly negative evaluations and the relative increase in the prevalence of this content is large \\footnote{6 percentage point increase compared to pre-treatment share of 8.36% in Bild (over 70% increase) and 6.75% in other newspapers (88.9% increase)}.
+the recent debate regarding nudging effects: @Maier2022], reported effects likely display a selection bias towards strong treatments.
+The treatment can be considered rather strong here, as the crime consideration is associated with strongly negative evaluations and the relative increase in the prevalence of this content is large \footnote{6 percentage point increase compared to pre-treatment share of 8.36% in Bild, an over 70% increase.}.
 Additionally, given that readers already consumed the newspaper, the qualities of the sender should rather increase the effect size, while the high salience of the issue should decrease it.
-Given these considerations, I expect an effect of around 10% of the scale, or 0.7 on the seven-point scale[^5], which represents a conservative estimate compared to reported experimental effects.
+Given these considerations, I expect an effect of around 10% of the scale, or 0.6 on the seven-point scale\footnote{As the scale runs from one to seven, it spans six points wide.}, which represents a conservative estimate compared to reported experimental effects.
 
-[^4]: As many studies do not include a control group, this is the most comparable metric.
-
-[^5]: As the scale runs from one to seven, it spans six points wide.
-
-As suggested by @Laken2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI, indicated by dotted orange line in the graph), as well as a conservative estimate of the experimentally expected effect.
+As suggested by @Lakens2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI, indicated by dotted lines in the figures below), as well as a conservative estimate of the experimentally expected effect.
 I define the SESOI at a 2.5% change, or 0.15 on the seven-point scale, which represents a fraction of the conservative experimental estimate and sets a fairly low bar given the strong treatment.
@@
 
-Figure \@ref(fig:singledv) visualizes the effect of the change in framing on immigration attitudes.
+Figure \@ref(fig:singleplot) visualizes the effect of the change in framing on immigration attitudes.
 Dashed vertical lines indicate the expected effect from the experimental literature.
@@
 If the 95% interval is contained within these boundaries, the hypothesis that the estimate is larger than the SESOI can be rejected.
-The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment (\$t = \$ `r round(t_ATT, 2)`, \$p = \$ `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.7)`% of the expected effect of 0.7.
+The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment ($t = $ `r round(t_ATT, 2)`, $p = $ `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.6)`% of the expected effect of 0.6.
 The 95% confidence interval also contains values far smaller than the SESOI of 0.15 but clearly include the vertical solid red line indicating no change.
@@
 
-```{r singleplot, fig.cap="Effect of change in framing on migration attitudes; difference-in-differences estimate.", fig.height=2}
+```{r singleplot, fig.cap="Effect of change in framing on migration attitudes; difference-in-differences estimate.
+Dashed vertical lines indicate conservative experimental effect (0.6, baseline expectation), dotted vertical lines indicate minimal relevant effect (0.15).
+Full model visible in Appendix XX", fig.height=2}
 
 DiDPlot(multi = F, scaled = "raw", 
-        theoretical_effect_size = 0.7, boundary_share = 0.25)
+        theoretical_effect_size = 0.6, boundary_share = 0.25)
 
@@
 The black dots with associated confidence intervals indicate the estimated effect for each wave.
-The horizontal dashed line indicates the expected effect based on experimental evidence (0.7), whereas the dotted horizontal line indicates the SESOI of 0.15.
+The horizontal dashed line indicates the expected effect based on experimental evidence (0.6), whereas the dotted horizontal line indicates the SESOI of 0.15.
 The vertical (red) dashed line indicates the timing of the editorial change, whereas the dotted (orange) vertical line indicates the timing of the strong increase in crime framing in June 2017, several months after the takeover by Reichelt (see figure \@ref(fig:treatment)).
@@
 
-DiDByWavePlot(theoretical_effect_size = 0.7, boundary_share = 0.25)
+DiDByWavePlot(theoretical_effect_size = 0.6, boundary_share = 0.25)
 
@@
 ```
+
 # Mechanism
@@
 
+cite Lecheler et al, Druckman2012; Druckman2012Bias; X & Arceneaux here showing that individuals are resistant to persuasion on high-importance issues and that timing/pretreatment matters
+
 It becomes apparent that individual migration attitudes stabilised after 2015.

### 2022-08-24 paper/appendix.Rmd
Drop unnecessary parts

@@
 
-```{r inselection fig.cap = "Coefficients of OLS regression of readership on migration attitude across waves.
+```{r inselection, fig.cap="Coefficients of OLS regression of readership on migration attitude across waves.
 Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change."}
@@
 
-*Transformed to [-3, 3].*
+*Recoded to [-3, 3].*
 
@@
 
-#### Treatment groups across time, by prior attitude
-
-```{r did_imm_att_plot_groups}
-
-fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
-  filter(init_mig_groups != "", !is.na(`1130_clean`), !is.na(treat)) %>% 
-  group_by(init_mig_groups, treat, wave) %>% 
-  summarise(
-    date_clean = min(date_clean, na.rm = T),
-    `1130_clean` = mean(`1130_clean`, na.rm = T)
-  ) %>% 
-  ggplot(aes(x = date_clean, y = `1130_clean`, lty = !treat, col = init_mig_groups)) +
-  geom_line() +
-  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
-  # facet_wrap(~init_mig_groups, ncol = 1) + 
-  theme_minimal()
-
-```
-
-#### Effect by prior opinion
-
-```{r linearEffect}
-
-InterLinear() + 
-  InterLinear(placebo = T)
-
-```
-
-#### Regression to the mean among Bild readers
-
--   Placebo-treatment post Bundestagswahl (3-6 months after treatment)
--   Exclusing Bild readers actually treated
-
-```{r}
-DiDPlot(placebo = T, exclude_pretreated = T, legend_position = "None") + InterLinear(placebo = T, exclude_pretreated = T)
-```
-
 #### Effect of Reichelt takeover
@@
 
-DiDModels(dv_name = "1130_clean", 
-          ctrl_var  = "cond",
-          ctrl_name = "Initial Migration Att.")
-
-```
-
-#### Number of respondents in each group
-
-```{r treat_initmig_n, fig.cap="Number of respondents in treatment and control group by pre-existing attitude."}
-
-gles_p_long <- 
-  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
-  filter(wave == "1")
-
-table(gles_p_long$init_mig, gles_p_long$treat) %>% 
-  knitr::kable()
-
-rm(gles_p_long)
-
-```
-
-#### Number of observations
-
-```{r treat_initmig_obs, fig.cap="Number of observations in treatment and control group by pre-existing attitude."}
-
-gles_p_long <- 
-  fread(here('data/raw/gles/Panel/long_cleaned.csv'))
-
-table(gles_p_long$init_mig, gles_p_long$treat) %>% 
-  knitr::kable()
-
-rm(gles_p_long)
-
-```
-
-#### Conservative Outlets only
-
-```{r did_imm_att_cons}
-
-DiDModels("1130_clean", restrict_sample = "conservative_outlets")
-
-```
-
-```{r did_imm_att_cons_vis}
-
-fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
-  filter(init_mig_groups != "", !is.na(`1130_clean`), !is.na(treat)) %>% 
-  filter(bild_init | faz_init | welt_init) %>% 
-  group_by(init_mig_groups, treat, wave) %>% 
-  summarise(
-    date_clean = min(date_clean, na.rm = T),
-    `1130_clean` = mean(`1130_clean`, na.rm = T)
-  ) %>% 
-  ggplot(aes(x = date_clean, y = `1130_clean`, lty = !treat, col = init_mig_groups)) +
-  geom_line() +
-  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
-  ggtitle("Immigration attitudes among Bild readers across time", "Compared to FAZ & Welt readers") + 
-  theme_minimal()
-
-```
-
-### Outcome: Immigration Attitude Nonresponse (1130 = -99)
-
-```{r did_imm_dodge}
-
-DiDModels("1130_dodge")
+SingleDVModel('1130_clean')
 
@@
 
-DiDModels("1210_clean")
-
-```
-
-### Outcome: Integration Attitude Nonresponse (1210 = -99)
-
-## General Nonresponse/Attrition (1130 = -95)
-
-```{r did_part}
-
-DiDModels("participation")
+SingleDVModel("1210_clean")
 
@@
 
-### Outcome: Voting AfD (190b)
+### Outcome: Scalometer AfD (430i)
 
-Bei der Bundestagswahl können Sie ja zwei Stimmen vergeben. Die Erststimme für einen Kandidaten aus Ihrem Wahlkreis und die Zweitstimme für eine Partei. Was werden Sie auf Ihrem Stimmzettel ankreuzen?
+#### QUESTION TEXT MISSING
 
-```{r afd_vote}
+#### DiD Estimate
 
-DiDModels("afd_vote")
+```{r afd_scale}
+
+SingleDVModel("430i_clean")
 
@@
 
-### Outcome: Voting Nonresponse (190b = -99 \| -98)
+## Variable: Issue Importance
 
-```{r vote_mis}
+### Outcome: MIP Migration (840s)
 
-DiDModels("vote_miss")
+#### QUESTION TEXT MISSING
+
+#### DiD Estimate
+
+```{r did_mip_mig}
+
+SingleDVModel("mip_mig")
 
@@
 
-**Sizable effect, most likely among liberals.**
+## Variable: Crime Considerations
 
-### Outcome: Scalometer AfD (430i)
+### Attitudes towards fighting crime (2880h)
 
-```{r afd_scale}
-
-DiDModels("430i_clean")
-
-```
-
-**Decrease, if anything. Most sizable among liberals, but disappers when controlling for individual FEs.**
-
-## Variable: Issue Considerations
-
-### Outcome: MIP Migrant Crime (840s)
-
-```{r did_mip_mig_crime}
-
-DiDModels("mip_mig_crime")
-
-```
-
-No effect, but also very low N.
-
-### Outcome: MIP Migration (840s)
-
-```{r did_mip_mig}
-
-DiDModels("mip_mig")
-
-```
-
-**NO effect on general problem perception of migration.**.
-
-### Outcome: Crime Attitude (2880h)
-
-```{r did_crime_att}
-
-DiDModels("2880h_clean")
-
-```
-
-*Nothing.*
-
-### Outcome: Correlation of Crime Attitude (2880h) & Immigration Attitude (1130)
-
-#### Question
+#### Question Text
 
@@
 (5) stimme voll und ganz zu
+
+#### Direct Effect
+
+```{r did_crime_att}
+
+SingleDVModel("2880h_clean")
+
+```
 
@@
 ```
-
-(cannot show this by subgroup bc would condition on pre-treatment opinion, which restricts variation on migration attitudes to 0, hence no correlation)
 
@@
 ```
-
-## Variable: Accuracy Motivation
-
-**This variable is only measured post-treatment**
-
-### Mean accuracy motivation by initial immigration attitude
-
-```{r acc_mot_means}
-
-gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
-
-gles_p_long %>% 
-  filter(!is.na(init_mig)) %>% 
-  group_by(init_mig) %>% 
-  summarise(acc_mot = mean(`1555d_clean`, na.rm = T)) %>% 
-  ggplot(aes( x = init_mig, y = acc_mot)) +
-  geom_bar(stat = "identity", fill = "lightblue") +
-  xlab("Initial Immigration Opinion") +
-  ylab("Accuracy motivation") +
-  theme_minimal()
-
-```
-
-### DiD by post-treatment accuracy motivation
-
-```{r did_acc_mot}
-
-DiDModels("1130_clean",
-          cond_var = "acc_goal",
-          cond_name = "Accuracy Motivation")
-
-```
-
-# TWFE: BERT Estimates
-
-## Distribution of Independent Variable
-
-```{r bert_dist}
-
-fread(here("data/processed/merged_bert.csv")) %>% 
-  ggplot(aes(crime_label_share)) + 
-  geom_histogram(bins = 50, col = "white") +
-  theme_minimal()
-
-```
-
-## Variable: Immigration Attitudes
-
-### Outcome: Reduce Immigration (1130)
-
-Jetzt geht es um Zuzugsmöglichkeiten für Ausländer. Sollten die Zuzugsmöglichkeiten für Ausländer erleichtert oder eingeschränkt werden?
-
-(1) 1 Zuzug von Ausländern erleichtern
-(2) 2\
-(3) 3\
-(4) 4\
-(5) 5\
-(6) 6\
-(7) 7 Zuzug von Ausländern einschränken
-
-```{r ind_imm_att}
-
-TWFEModels("1130_clean")
-
-```
-
-### Outcome: Immigration Attitude Nonresponse (1130 = -99)
-
-```{r ind_imm_dodge}
-
-TWFEModels("1130_dodge")
-
-```
-
-### Outcome: Integration Attitude (1210)
-
-Es gibt unterschiedliche Auffassungen darüber, wie sehr sich Ausländer in Deutschland anpassen sollten.
-Manche denken, dass sich Ausländer vollständig an die deutsche Kultur anpassen sollten.
-Andere denken, Ausländer sollten auch hier möglichst nach der eigenen Kultur leben können.
-
-(1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen
-(2) 
-(3) 
-(4) 
-(5) 
-(6) 
-(7) Ausländer sollten möglichst nach eigener Kultur leben können
-
-```{r ind_int_att}
-
-TWFEModels("1210_clean")
-
-```
-
-### Outcome: Integration Attitude Nonresponse (1210 = -99)
-
-```{r ind_int_dodge}
-
-TWFEModels("1210_dodge")
-
-```
-
-## Conditioning on Prior Exposure
-
-### DV: Immigration Attitude
-
-```{r ind_cond_exp_lag}
-
-TWFEModels("1130_clean", 
-           cond = "crime_label_share_lag", 
-           cond_name = "\nLagged Exposure")
-
-```
-
-Exposure has no conditioning effect - maybe conditional effect IS ceiling effect? (but still holds compared to conservative news consumers?)
-
-## Variable: Voting Behaviour
-
-### Outcome: Voting AfD (190b)
-
-Bei der Bundestagswahl können Sie ja zwei Stimmen vergeben. Die Erststimme für einen Kandidaten aus Ihrem Wahlkreis und die Zweitstimme für eine Partei. Was werden Sie auf Ihrem Stimmzettel ankreuzen?
-
-### Outcome: Voting Nonresponse (190b = -99 \| -98)
-
-```{r ind_afd_dodge}
-
-TWFEModels("vote_miss")
-
-```
-
-### Outcome: Scalometer AfD (430i)
-
-```{r ind_afd_vote}
-
-TWFEModels("430i_clean")
-
-```
-
-## Variable: Issue Considerations
-
-### Outcome: MIP Migrant Crime (840s)
-
-```{r ind_mip_mig_crime}
-
-TWFEModels("mip_mig_crime")
-
-```
-
-### Outcome: MIP Migration (840s)
-
-```{r ind_mip_mig}
-
-TWFEModels("mip_mig")
-
-```
-
-## TWFE Conditional on Paper Consumed (driven by Bild-readers?)
-
-```{r}
-
-TWFEModels("1130_clean", cond_var = "bild_init", cond_name = "Paper: Bild")
-
-```
-
-Effect **lower** among Bild readers!
-
-<!-- # TWFE: STM Estimates -->
-
-<!-- **STM estimates currently NOT reliable - fix 04a_merge_stm.R** -->
-
-<!-- ## Distribution of Independent Variable -->
-
-<!-- ```{r stm_dist} -->
-
-<!-- fread(here("data/processed/merged_stm.csv")) %>%  -->
-
-<!--   ggplot(aes(crime_label_share)) +  -->
-
-<!--   geom_histogram(bins = 50, col = "white") + -->
-
-<!--   theme_minimal() -->
-
-<!-- ``` -->
-
-<!-- ## Variable: Immigration Attitudes -->
-
-<!-- ### Outcome: Reduce Immigration (1130) -->
-
-<!-- Jetzt geht es um Zuzugsmöglichkeiten für Ausländer. Sollten die Zuzugsmöglichkeiten für Ausländer erleichtert oder eingeschränkt werden? -->
-
-<!-- (1) 1 Zuzug von Ausländern erleichtern  -->
-
-<!-- (2) 2   -->
-
-<!-- (3) 3   -->
-
-<!-- (4) 4   -->
-
-<!-- (5) 5   -->
-
-<!-- (6) 6   -->
-
-<!-- (7) 7 Zuzug von Ausländern einschränken -->
-
-<!-- ```{r ind_imm_att_stm} -->
-
-<!-- TWFEModels("1130_clean", dataset = "stm") -->
-
-<!-- ``` -->
-
-<!-- ### Outcome: Immigration Attitude Nonresponse (1130 = -99) -->
-
-<!-- ```{r ind_imm_dodge_stm} -->
-
-<!-- TWFEModels("1130_dodge", dataset = "stm") -->
-
-<!-- ``` -->
-
-<!-- ### Outcome: Integration Attitude (1210) -->
-
-<!-- Es gibt unterschiedliche Auffassungen darüber, wie sehr sich Ausländer in Deutschland anpassen sollten.
-Manche denken, dass sich Ausländer vollständig an die deutsche Kultur anpassen sollten.
-Andere denken, Ausländer sollten auch hier möglichst nach der eigenen Kultur leben können.
--->
-
-<!-- (1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen  -->
-
-<!-- (2)   -->
-
-<!-- (3)   -->
-
-<!-- (4)   -->
-
-<!-- (5)   -->
-
-<!-- (6)   -->
-
-<!-- (7) Ausländer sollten möglichst nach eigener Kultur leben können  -->
-
-<!-- ```{r ind_int_att_stm} -->
-
-<!-- TWFEModels("1210_clean", dataset = "stm") -->
-
-<!-- ``` -->
-
-<!-- ### Outcome: Integration Attitude Nonresponse (1210 = -99) -->
-
-<!-- ```{r ind_int_dodge_stm} -->
-
-<!-- TWFEModels("1210_dodge", dataset = "stm") -->
-
-<!-- ``` -->
-
-<!-- ## Conditioning on Prior Exposure -->
-
-<!-- ### DV: Immigration Attitude -->
-
-<!-- ```{r ind_cpond_explag_stm} -->
-
-<!-- TWFEModels("1130_clean",  -->
-
-<!--            cond = "crime_label_share_lag",  -->
-
-<!--            cond_name = "\nLagged Exposure", -->
-
-<!--            dataset = "stm") -->
-
-<!-- ``` -->
-
-<!-- Exposure has no conditioning effect - maybe conditional effect IS ceiling effect? (but still holds compared to conservative news consumers?) -->
-
-<!-- ## Variable: Voting Behaviour -->
-
-<!-- ### Outcome: Voting AfD (190b) -->
-
-<!-- Bei der Bundestagswahl können Sie ja zwei Stimmen vergeben.
-Die Erststimme für einen Kandidaten aus Ihrem Wahlkreis und die Zweitstimme für eine Partei.
-Was werden Sie auf Ihrem Stimmzettel ankreuzen?
--->
-
-<!-- ### Outcome: Voting Nonresponse (190b = -99 | -98) -->
-
-<!-- ```{r ind_afd_dodge_stm} -->
-
-<!-- TWFEModels("vote_miss", dataset = "stm") -->
-
-<!-- ``` -->
-
-<!-- ### Outcome: Scalometer AfD (430i) -->
-
-<!-- ```{r ind_afd_scale} -->
-
-<!-- TWFEModels("430i_clean", dataset = "stm") -->
-
-<!-- ``` -->
-
-<!-- ## Variable: Issue Considerations -->
-
-<!-- ### Outcome: MIP Migrant Crime (840s) -->
-
-<!-- ```{r ind_mip_mig_crime_stm} -->
-
-<!-- TWFEModels("mip_mig_crime", dataset = "stm") -->
-
-<!-- ``` -->
-
-<!-- ### Outcome: MIP Migration (840s) -->
-
-<!-- ```{r ind_mip_mig_stm} -->
-
-<!-- TWFEModels("mip_mig", dataset = "stm") -->
-
-<!-- ``` -->
-
-<!-- # TWFE Conditional on Paper Consumed (driven by Bild-readers?) -->
-
-<!-- ```{r ind_cond_paper_stm} -->
-
-<!-- TWFEModels("1130_clean", cond_var = "bild_init", cond_name = "Paper: Bild", dataset = "stm") -->
-
-<!-- ``` -->

### 2022-08-25 paper/Manuscript_Framing.Rmd
Incorporate TM feedback (2/2)

@@
 
-Research on framing has shown for decades that citizens' attitudes and their issue associations are highly reactive to minor changes in the emphasis of specific considerations [@Chong2007; @Chong2010; @Druckman2012Bias; @Kinder1990; @Nelson1996; @Nelson1997; @sniderman2004structure; for reviews see @Busby2019; @Druckman2001; @Leeper2020].
+Research on framing has shown for decades that citizens' attitudes and their issue associations are highly reactive to minor changes in the emphasis of specific considerations [@Chong2007b; @Chong2010; @Druckman2012Bias; @Kinder1990; @Nelson1996; @Nelson1997Rally; @sniderman2004structure; for reviews see @Busby2019; @Druckman2001; @Leeper2020].
 However, it remains unclear how well these experimental findings translate into the real world.
@@
 Even the correct measurement of the magnitude is a contested question, as different control groups (untreated, opposing frame, ...) can be compared [@Druckman2001; @Chong2007a, 109f for a discussion].
-Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009a], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996].
-Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing pro and con arguments\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009a; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
+Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009b], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996].
+Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing pro and con arguments\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009b; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
 As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [see e.g.
@@
 Dashed vertical lines indicate conservative experimental effect (0.6, baseline expectation), dotted vertical lines indicate minimal relevant effect (0.15).
-Full model visible in Appendix XX", fig.height=2}
+Full model visible in Appendix XX.", fig.height=2}
 
@@
 The GLES Panel data contains a variable asking respondents whether "the state's capabilities to fight crime should be extended, even if that would entail more surveillance", asked in three waves overlapping with the migration attitude question.
-Figure \@ref(fig:corplot) shows the correlation of crime- and migration attitudes in treatment and control group, pre- and post-treatment.
+
+Figure \@ref(fig:corplot) shows the correlation of crime- and migration attitudes in treatment (Bild-readers in pre-wave) and control group (never Bild-readers), pre- and post-treatment.
 I added a counterfactual, applying the change in the control group to the treatment group, for easier interpretation.
@@
 
+[explain why this is done, and why constituent terms are not interesting - only the change in association of crime attitude and dependent variable is of interest, we are not trying to explain variation in the dependent variable!
+(which is also why R2 doesn't matter here)]
+
 ## Robustness
@@
 
-One reason for this null effect could be that a slowly unfolding long term effect is masked by initial absence of change.
+If readers only perceive the change in content across longer time periods, the effect should slowly unfold across time.
+If that is the case, initial absence of change might bias the estimates downward and thereby mask an effect.
 To assess whether an effect develops over time, figure \@ref(fig:migwaves) assesses the effect within split-samples for each post-wave compared to the pre-treatment wave.
@@
 The vertical (red) dashed line indicates the timing of the editorial change, whereas the dotted (orange) vertical line indicates the timing of the strong increase in crime framing in June 2017, several months after the takeover by Reichelt (see figure \@ref(fig:treatment)).
-It s visible that, over the course of the entire year 2017, the effect is clearly smaller than the SESOI, and includes zero.
+Over the course of the entire year 2017, the effect is clearly smaller than the SESOI, and includes zero.
 However, estimates for waves 7 and 8 in late 2018 and mid-2019 - more than one and a half years after the editorial change - showcase effects statistically different from zero, and including the SESOI boundary.
@@
 
-```{r migwaves, fig.cap="Effect of Change in Framing on Immigration Attitudes across Waves"}
+```{r migwaves, fig.cap="Effect of Change in Framing on Immigration Attitudes across Waves.
+Dashed (black) horizontal lines indicate conservative experimental effect (0.6, baseline expectation), dotted horizontal lines indicate minimal relevant effect (0.15).
+Dashed (red) vertical line indicates effect of Reichelt takeover, dotted (orange) line timing of change in coverage.
+Full models visible in Appendix XX."}
 
@@
 
-While immigration attitudes remain unaffected, it might well be that an increased exposure to crime framing increases individual perceptions of the importance of migration, despite not changing attitudes, or that it raises concerns about the integration rather than the immigration of migrants.
-Similarly, support for the radical-right *AfD* as owner of the migration issue might increased as a result of increased exposure to crime frames.
+While immigration attitudes remain unaffected, it might well be that an increased exposure to crime framing affects other variables.
+For example, increased attention to crime within migration coverage might increase individual perceptions of the importance of migration, despite not changing attitudes, or raise concerns about the integration rather than the immigration of migrants.
+Similarly, support for the radical-right *AfD* as owner of the migration issue could increase as a result of increased exposure to crime frames.
+All variable descriptions and models can be found in the appendix.
+
 Figure \@ref(fig:multidv) displays standardized effects of the change in newspaper framing on immigration attitudes (as reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see Appendix ??
@@
 
-```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}
+```{r multidv, fig.cap="Standardised effect of change in framing on alternative dependent variables.
+Dotted vertical lines indicate minimal relevant effect (0.2 SD).
+Full models available in Appendix XX."}
 
@@
 
-The presented results are robust evidence that, despite an over 70% increase of the emphasis of crime in migration content of Germany's largest newspaper, its readers migration attitudes remained surprisingly unaffected.
+The presented results are robust evidence that, despite an over 70% increase of the emphasis of crime in migration content of Germany's largest newspaper, its readers' migration attitudes remained surprisingly unaffected.
 Effect estimates remain below minimal thresholds across time.
@@
 
-While these findings are worrisome for framing scholars, they are generally good news for democracy: even when outlets try, they cannot simply manipulate their audience's political attitudes with a snap of their finger.
-Worries about the undermining of democracy trough the takeover of partisan news outlets might be overstated, as consumers either seem to hold a critical distance to their news outlets or consume content from so many outlets that a single one has not much influence.
+While these findings substantially question evidence from experimental framing studies, they are generally good news for democracy: even when outlets try, they cannot simply manipulate their audience's political attitudes with a snap of their finger.
+Worries about the undermining of democracy through the takeover of partisan news outlets might be overstated, as consumers either seem to hold a critical distance to their news outlets or consume content from so many outlets that a single one has not much influence.
 Descriptive data about American news diets supports this interpretation [@Guess2021a].
 
-This study suffers from several limitations regarding the generalizabilty of the case at hand.
+Despite the unique case and the extensive efforts to isolate the effect of the documented change inframing, this study suffers from several limitations regarding the generalizabilty of the case at hand.
 First, the immigration issue was already highly salient for one and a half years when Reichelt took over *Bild*.
@@
 
+[add: no randomisation of treatment!! plus adapt to new evidence regarding attitude stability]
+
 This study offers several takeaways for future research.
@@
 
+\pagebreak
+
 # Resources

### 2022-08-31 paper/appendix.Rmd
Present DPA-correction in paper

@@
 
-# Independent Variable
+# Frames in Communication
 
@@
 
-### Correcting for change in DPA-sourced content
+## Salience of Migration
+
+## Correcting for change in DPA-sourced content
 
@@
 The graph also suggests an explanation for this sudden shift: the share of articles sourced from DPA, a major German press agency alike the Associated Press, sharply decreases at the same time as the major decrease in the number of articles takes place (see top blue bars).
-While the decision to discontinue buying content from DPA must have been made by Reichelt himself (and is thus an outcome of the treatment), it might nevertheless affect the measurement of migration framing in *Bild*.
 DPA is a press agency supplying many German news outlets, which means it must have a rather unbiased or at least centrist coverage, potentially decreasing the estimate of crime frames within Bild's migration content.
@@
 However, *Bild* likely gives more weight to its own content compared to pre-written content from DPA.
-It is therefore necessary to assess whether the change in framing persists when excluding DPA content.
+For this reason, the paper presented data excluding DPA content.
+On the other hand, the decision to discontinue buying content from DPA must have been made by Reichelt himself and is thus an outcome of the treatment.
+Hence, it is fruitful to assess the change including DPA-sourced content.
 
@@
 The left panel of figure \@ref(fig:treatmentDPAcorr) displays the quarterly share of migration articles discussing crime for *Bild* compared to all other newspapers.
-The depression visible in the original plot in 2016-2017 is not visible anymore, as is the sharp increase in June 2017.
-Instead, the share of crime content in Bild's migration coverage increases directly after the takeover by Reichelt.
-The gap between Bild and all other newspapers increases, and this increased difference persists.
+A depression is visible in 2016-2017 which was not visible in the corrected data.
+The share of crime content in *Bild*'s migration coverage strongly increases a few months following the treatment, when the share of DPA-sourced content severely drop.
+The gap between *Bild* and all other newspapers increases, and this increased difference persists.
 This change becomes even more visible in the right-hand panel, which shows a difference-in-differences estimate of the change of the share of crime news in a newspapers migration content, this time controlling for whether the content is DPA-sourced or not.
-The general picture is quite similar to the original estimate in the paper, as migration coverage only increases in Bild, while all other outlets remain rather stable on this metric.
-The only difference is that in this estimate, the share of migration coverage devoted to crime 'only' increases by 5 percentage points, which still constitutes a very substantial increase.
+The general picture is quite similar to the original estimate in the paper, as migration coverage only increases in *Bild*, while all other outlets remain rather stable on this metric.
+In the estimate including DPA content, the share of migration coverage devoted to crime increases by an even stronger 6 percentage points, which still constitutes a very substantial increase.
+Both ways of handling the data suggest a strong increase in the emphasis of crime in migration coverage.
 
@@
 
-TreatmentTrendPlot(dpa_corrected = T) + 
-  TreatmentDiDPlot(dpa_corrected = T)
+TreatmentTrendPlot(dpa_corrected = F) + 
+  TreatmentDiDPlot(dpa_corrected = F)
 

### 2022-08-31 paper/appendix.Rmd
Drop STM, stability of migration attitudes

@@
 
-## Structural Topic Model
-
-To identify different considerations about migration in news coverage, I estimate a structural topic model with 60 topics for the nearly 90,000 migration articles in the full period (2013-2019)\footnote{The topics' prevalence along with the most important words can be assessed in the appendix.}.
-The number of topics was chosen to strike a balance between the computational and human resources necessary to estimate and annotate the topics and finding appropriate topics for the large corpus of nearly 90,000 migration articles\footnote{Currently, I work to identify crime content using supervised models (similar to the identification of migration content) to provide a specific estimate of the attention to the consideration of interest.
-I will also analyse the data with embedding regression, assessing how the meaning of migration related terms like 'migrant', 'asylum' or 'syrian' changed in Bild compared to other newspapers}.
-Topic prevalence is estimated as a function of the release date of the article, as well as the newspaper it has been published in.
-The 60 topics' most predictive words and ten most representative articles were assessed to identify and label the content of each topic, and all topics related to crime (two in total) are selected and their prevalence added together for a daily measure of attention to crime in each newspaper.
-
-### Treatment
-
 # Readership models
@@
 ```
-
-# Change in Migration Attitudes across time
-
-```{r}
-
-MigChangePlot()
-
-```
-
-[Add description of variable and explanation]
 

### 2022-08-31 paper/Manuscript_Framing.Rmd
Revise Text
- Add Discussion of Assumptions in the Translation of Experiments
- Move DPA-corrected estimates into main paper
- move raw treatment estimates into appendix
- Move Salience plot in Appendix
- Fix estimation section (drop reader effect)
- Improve Abstract
- Improve Intro
- Add section labels
- Improve Theory
- Add Figure Labels
- Improve Review of Existing Work
- Clarify Case Description

@@
 While a large body of experimental work suggests that individual attitudes can be easily altered by emphasizing different aspects of an issue, little is known about how these studies translate into the real world.
-I exploit a rare natural change of news framing in the major German tabloid newspaper *Bild* to study whether experimental estimates of framing effects translate into the real world.
-In a first step, I apply supervised transformer models to a novel dataset of 2.5M news articles and provide evidence of a substantial shift in the paper's migration framing following an editorial change.
-Second, I employ a difference-in-differences design using panel data from over 16,000 individuals in ten waves to assess the precise impact on migration attitudes.
-The findings show that, despite a major change in migration framing, immigration attitudes and related variables remain unaffected.
-News framing seems to affect attitudes only within limited windows of opportunity early in the politicization of political issues."
+I exploit a rare change in the migration framing of the major German tabloid *Bild* to study whether experimental estimates of framing effects translate into the real world.
+In a first step, I develop a framework for the measurement of emphasis frames in political communication using supervised machine learning.
+Using this framework, I show that the emphasis of crime in *Bild*'s migration coverage severely increased.
+Second, I employ a difference-in-differences design using panel data from over 16,000 individuals in ten waves to assess the precise impact of this shift on migration attitudes.
+The findings show that, despite a major change in migration framing, a clear null effect on immigration attitudes and related variables can be observed.
+Tracing three key assumptions underlying the translation of experimental effect estimates suggests that news framing affects attitudes only within limited windows of opportunity early in the politicization of political issues."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
@@
 *I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
-Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim as well as participants in the EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI, CompText Conference 2022, and the Political Behaviour Section at Aarhus University.
+Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim as well as participants of CompText 2022, EPSA 2022, ICA 2022, EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI,  and the Political Behaviour Section at Aarhus University.
+I also thank the two RAs, Robin Groß and Nathalie Aerts, for annotating the news articles.
 All remaining confusions are my own.*
-
-<!--# I also thank the two RAs, Robin Groß and Nathalie Aerts, for annotating the news articles.  -->
 
@@
 While a large body of experimental evidence suggests that the emphasis of a certain consideration can substantially alter issue attitudes, we know little about the translation of these findings into real-world environments.
-Prior work has shown that the external validity of such experiments might be seriously complicated by environments of diverse frames [@Chong2013] and actors [@Slothuus2010], as well as the seeking and avoidance of specific content [@Lau2021a; @Taber2006].
-Especially on contested issues, citizens might be more inclined to resist persuasion [@Arceneaux2009].
+Prior work has shown that the external validity of such experiments might be seriously complicated by the current salience and politicisation of the issue of interest [@Arceneaux2009; @Bechtel2015; @Lecheler2009a], the availability of different frames [@Chong2007; @Chong2013; @Druckman2003; @Druckman2012] and communicating actors [@Slothuus2010], as well as the seeking and avoidance of specific content [@Lau2021a; @Taber2006].
 Contemporary news environments provide consumers with especially diverse content and maximize their abilities to choose specific outlets and avoid others [@Bennett2008], thereby increasing the gap between the real-world environment and experimental studies.
@@
 This is the reason why, fifteen years ago, Donald Kinder called for framing research to extend its toolkit: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception.
-[...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157; see also @Busby2019; @Leeper2020].
+[...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157].
 
-I provide the - to my knowledge - first observational estimate of framing effects by exploiting a rare shift in the migration framing of Germany's largest tabloid newspaper, *Bild*.
+In this article, I provide the - to my knowledge - first observational estimate of framing effects by exploiting a rare shift in the framing of a highly politicized issue - migration - in Germany's largest tabloid newspaper, *Bild*.
 The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet substantially changed its framing while other papers maintained theirs.
-By employing BERT models for the measurement of crime frames in a corpus of 2.5 million newspaper articles, I am able to clearly identify the treatment - something that is usually left to experimental studies.
-The fielding of the German Longitudinal Election Study in the same period provides the rare opportunity to precisely assess the effect of this changing framing on readers' migration attitudes in a *difference-in-differences (DiD) design*.
-
-[might want to mention frames in mind and frames in communication distinction here and how it informs research design (follow Rune & Martin Bisgaard)]
+Providing a novel framework for the measurement of emphasis frames using BERT models, I study migration framing in a corpus of 2.5 million newspaper articles.
+I show that the newspaper's migration coverage saw a strong increase in the use of crime frames after the editor in chief was replaced.
+The fielding of the German Longitudinal Election Study in the same period provides the rare opportunity to precisely assess the effect of framing on political attitudes using a *difference-in-differences (DiD) design*.
 
 The results indicate that even a strong increase in the use of crime frames did not affect consumers' immigration attitudes.
-The estimated effect is statistically indistinguishable from zero and significantly smaller than even minimal effect magnitudes.
-Related issue attitudes, voting behaviour, and issue importance are similarly unaffected, as is the association of immigration attitudes with the frame provided.
-Additional evidence implies that immigration attitudes had crystallized at the time of the shift, such that individuals were immune to changing framing.
+The estimated effect is statistically indistinguishable from zero and significantly smaller than even minimally relevant effect magnitudes.
+Related issue attitudes, voting behavior, and issue importance are similarly unaffected, as is the association of immigration attitudes with the frame provided.
+Tracing different assumptions underlying the translation of experimental estimates of framing effects into the real world implies that this lack in responsiveness is not an outcome of readers abandonment of the newspaper, nor the "crowding out" of information through other sources, but rather the crystallization of immigration attitudes prior to the change in framing.
 
-Overall, these results fundamentally challenge the external validity of framing effects research and suggest that the influence of individual news outlets on public opinion is more limited than previously thought.
+Overall, these findings fundamentally challenge the external validity of a large body of framing effects research and suggest that the influence of individual news outlets on public opinion is more limited than previously thought.
 Even a strong change in news framing did not affect political attitudes.
-Instead, it seems that timing is a crucial factor in the effectiveness of news frames.
+Instead, it seems that the news media faces limited windows of opportunity to shape public opinion during the politicization of novel political issues.
 
-# Framing Effects on Public Opinion
+# Framing Effects on Public Opinion {#framing-effects}
 
@@
 These frames emphasize certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame [@Leeper2020, 152].
-For example, issues of increasing welfare contributions might be discussed with reference to inequality and providing chances to the poor, or by mentioning that higher welfare benefits might result in higher taxes.
-Individuals' support of a statement will differ dependent on the frame presented [@sniderman2004structure].
 Many other forms of framing exist, such as equivalence frames [@Kahneman1979prospect], episodic frames [@Iyengar2005], or generic frames [@DeVreese2005].
-The focus on emphasis frames in this study is owed to the large body of literature and generalized theory regarding their effect on attitudes about any issue (as opposed to generic and episodic frames), as well as their prevalence in the news media (which is not the case for equivalence frames).
+The focus on emphasis frames in this study is owed to the generalized theory regarding their effect on attitudes about any issue (as opposed to generic and episodic frames), as well as their common use in news content (which is not the case for equivalence frames).
 
@@
 This model suggests that an attitude on a given issue is a function of two things: the value of considerations relating to that issue and the strength of their association with the issue.
-The evaluation of the issue is subdivided into a number of considerations [a "frame in mind"; @Chong2007a, 105; @Nelson1996], which will carry clear evaluations.
+The evaluation of the issue is subdivided into a number of considerations, which will carry clear evaluations.
 For example, to form an opinion about whether immigration to one's country should be restricted, a person might consider the humanitarian conditions in the countries of origin (negative consideration regarding restrictive migration policy), as well as the risk of increased crime (positive consideration; note that the model does not differentiate whether a consideration is grounded in objective reality).
-Individuals weigh each of these considerations to form an overall opinion on the subject.
+Individuals weigh each of these considerations (so-called "frames in thought"; @Druckman2001) to form an overall opinion on the subject.
 
@@
 crime is viewed very negatively.
-Based on the strength of the association $w_i$ of a given consideration with the issue, a given consideration's evaluation is more or less reflected in the issue evaluation $y$, which is equal to the weighted sum of considerations.
+Based on the strength of the association $w_i$ of a given consideration with the issue, a given consideration's evaluation is more or less reflected in the overall attitude $y$, which is equal to the weighted sum of considerations.
 For example, if a given individual associates immigration strongly with an increase in criminal activity, welfare fraud, but only very weakly with humanitarian considerations, cultural enrichment, liberty, or economic growth, they will form a rather negative attitude about the issue, as the former factor more prominently in their reasoning about migration.
@@
 How does this model incorporate news content and other forms of political communication?
-News content can emphasize different considerations of an issue [so called "frames in communication" @Nelson1996].
+News content can emphasize different considerations of an issue (so-called "frames in communication").
 By being exposed to the consideration, an individual's cognitive association of the issue at hand with the raised consideration strengthens (or in more technical terms: the weight of the consideration $w_i$ increases).
@@
 
-# Limits of Framing Experiments
+# Limits of Framing Experiments {#framing-limits}
 
@@
 However, it remains unclear how well these experimental findings translate into the real world.
-First, taking experimental effects as estimates of the real-world impact of framing means making strong assumptions about citizens' exposure to frames: while framing studies usually simply present a news article or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience.
-Changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news outlets containing such frames (and vice versa seek out attitudinally congruent information).
+Below, I outline three key assumptions in the translation of experimental estimates.
+
+First, taking experimental effects as estimates of the real-world impact of framing means making strong assumptions about citizens' exposure to frames: while framing studies usually simply present news articles or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience.
+Changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news content containing such frames (and vice versa seek out attitudinally congruent information).
 This idea of 'selective exposure/avoidance' [@Bennett2008], or a 'confirmation bias' [@Taber2006] brings with it a major endogeneity problem making purely correlational evidence of framing effects rather uninformative.
+As most framing studies do not offer choice of content to respondents, engagement remains an assumption when taking experimental studies as evidence of framing effects in the real world [for an exception see @Druckman2012Bias].
 
-Second, even if one assumes that the consumers receive the content, (e.g.
-buy a newspaper, visit a website, ...), it is not clear whether the content is actually consumed.
-For example, a reader might well buy a newspaper but skip an article after reading the headline because the topic is not of interest or the frame is at odds with their existing attitude [@Lau2021a].
-As most framing studies do not offer choice of content to respondents, engagement remains an assumption when taking experimental studies as evidence of framing effects in the real world (for an exception see @Druckman2012Bias).
-Additionally, information from different sources, such as TV, social media, blogs, newspapers, ..., might 'crowd out' the framing of a single outlet: By consuming content from many sources, individuals might give less attention to a single outlet, thereby severely limiting the overall impact of that outlet's coverage.
+Second, even if consumers receive the content, it is not clear how much an individual relies on this source when forming an opinion on the subject.
+Information from different sources - such as TV, newspapers, social media, or alternative online media - might 'crowd out' the framing of a single outlet: by consuming content from many sources, individuals might give less attention to a given source, thereby severely limiting the overall impact of that outlet's coverage.
+Experimental evidence suggests that, when an individual receives competing frames, these cancel each other out, although the precise impact is dependent on the relative timing of exposure, the quality of the frame, as well as individual characteristics [@Chong2007b; @Chong2010; @Chong2013].
 
-Third, even when consuming the content, cognitive engagement with it might strongly differ in the real world compared to experimental contexts.
-Motivated reasoners presented with a plethora of news content about an issue will spend less time and cognitive energy on counter-attitudinal arguments than those supporting their viewpoint, lending more importance to considerations raised by amenable content [@Taber2006].
-Experimental studies presenting only one frame per issue cannot take this bias into account.
-Consumption might also result in better or worse comprehension in the real world because respondents might pay more or less attention to real news content compared to experimental treatments [@Barabas2010].
-Furthermore, there might be differences in how easily this translates into changing cognitive associations, given that those exposed might take real-world content more seriously.
-Additionally, the relative timing at which a frame is received, relative to other frames and the salience of the issue, affects the way in which individuals react to framing.
-Those citizens who received a different frame earlier might already have formed a crystallized opinion about the issue and thus reject subsequent attempts of persuasion [@Bechtel2015; @Druckman2012Bias; @Lecheler2009b].
+Third, cognitive engagement with frames might strongly differ in the real world compared to experimental contexts.
+Once individuals formed political attitudes, they might resist framing: Motivated reasoners presented with a plethora of news content about an issue will spend less time and cognitive energy on counter-attitudinal arguments than those supporting their viewpoint, lending more importance to considerations raised by amenable content [@Taber2006].
+Experimental evidence suggests similar dynamics specifically for framing: when individuals are free to choose content, initial frames dominate the opinion-formation process, while novel frames are rejected [@Druckman2012Bias] and even serve to strengthen pre-existing attitudes [@Bechtel2015].
+This also explains why citizens are less reactive to framing attempts on salient and politicized issues [@Lecheler2009b].
 
-To summarize, there are many reasons to assume that framing might have very different consequences in real-world environments than in their experimental emulations, and the above list is by no means comprehensive.
-When we take the experimental evidence as an approximation of the effectiveness of framing in the real world, we make many strong assumptions about citizens' exposure to, consumption of, and engagement with the frames in news content.
+In sum, there are many reasons to assume that framing might have very different consequences in real-world environments than in their experimental emulations.
+If one takes experimental evidence as an approximation of the effectiveness of framing in the real world, they make many strong assumptions about citizens' exposure to, reliance on, and cognitive engagement with the frames in news content.
 Experiments can only incorporate few characteristics of the real world at a time.
@@
 
-## Existing Observational Studies of Framing Effects
+# Existing Observational Studies of Framing Effects
 
 Despite repeated calls for the assessment of framing effects beyond experimental studies [@Busby2019; @Kinder2007; @Leeper2020], there is little research addressing this concern.
-While a large body of observational media effects research exists, it has not paid specific interest to framing, instead assessing the impact of changing news exposure broadly [@Bail2018; @Broockman2022; @Foos2022; @Grossman2022; @Guess2021; @Levendusky2022; @Spirig2020].
+While a large body of observational media effects research exists, it has not paid specific interest to framing, instead assessing the impact of changing news exposure on issue attitudes and voting behavior more broadly.
+Most of these studies are concerned with exposure to a different outlet [@Bail2018; @Broockman2022; @Foos2022; @Grossman2022; @Guess2021].
+This is problematic, as citizens are often aware of outlets' political slant and engage with the coverage differently [@Baum2008; see also @Spirig2020 for a discussion of this issue].
+The existing studies focusing on within-outlet changes in coverage do not identify changing framing directly and assess effects on a broad set of dependent variables, rather than specific issue attitudes [@Levendusky2022; @Spirig2020].
 
-The precious small body of existing observational research on framing effects is often riddled with endogeneity issues.
+The precious small body of existing observational research specifically about framing is often riddled with endogeneity issues.
 For example, @Jerit2008 investigates the effects of news framing on public opinion.
-She finds that framing is less effective in changing public opinion than engagement with opposing considerations, a finding that suggests that framing is rather ineffective.
-However, her study restricts itself to the assessment of correlational evidence.
-This is especially problematic regarding framing effects, as news content can affect consumers' inclination to consume news (see preceding section), and political actors might react to public opinion, thereby creating endogeneity issues.
+She finds that framing is less effective in affecting public opinion compared to engagement with opposing considerations, a finding that suggests that framing is rather ineffective.
 Others show with similar designs that only specific frames seem to drive issue importance [@Mclaren2018], but do not assess effects on attitudes.
+However, these studies restrict themselves to the assessment of correlational evidence.
+This is especially problematic regarding framing effects, as news content can affect consumers' inclination to consume news (see preceding section), and political actors might react to public opinion.
+As both variables affect each other at the same time (endogeneity), it is impossible to assess which direction causality runs.
 
@@
 @Slothuus2010b takes advantage of a sudden shift in a political parties' framing of retirement benefits, and shows that this changed framing has substantial impact on party supporters' attitudes about the issue.
-However, it is unclear how these findings translate to news framing effects.
-Given that - in this case - a positional change coincided with the changing framing of the issue and parties' special role in citizens' information process, it is impossible to distinguish the effect of partisan cue-taking from the persuasive effect of the frame itself.
+However, given that a positional change coincided with the changing framing of the issue and parties' special role in citizens' information process, one cannot distinguish the effect of partisan cue-taking from the persuasive effect of the frame itself.
+Additionally, it is unclear how these findings translate from parties' communication to news framing effects.
 
-The only study which assesses the precise impact of changing news content on political attitudes comes from @Djourelova2020.
+The only study which - to my knowledge - assesses the precise impact of changing news content on political attitudes comes from @Djourelova2020.
 She exploits a ban of the term "illegal migrant" in the *Associated Press* and shows that this language has modest effects on migration attitudes.
 While the study itself reveals impressively how language can shape political attitudes, it constitutes a highly specific case and a rather minor change in the framing of migration.
-To gain a deeper understanding of how specifically framing affects immigration attitudes, it is necessary to assess broader changes in the representation of the immigration issue.
+To gain a deeper understanding of how specifically *framing* affects immigration attitudes, it is necessary to assess broader changes in the representation of the immigration issue.
 
-In sum, we lack an understanding of how framing affects political opinions in the real world.
-While experimental evidence suggests rather strong effects, it is unclear how these findings translate to the outside world.
-Observational evidence on media effects is abundant but has not precisely studied the impact of framing.
-The present study therefor exploits a naturally occurring change in the news framing of a particular issue *within* a specific outlet to isolate the effects of news framing on political opinions.
+It becomes obvious that the discipline lacks an understanding of how news framing affects political attitudes in the real world.
+While experimental studies find strong effects, several assumptions have to be made to translate them beyond the lab or survey context.
+Observational evidence on media effects has not precisely studied the impact of framing.
+To do so, it is necessary to assess within-outlet changes in news framing and their effect on specific issue attitudes using a design able to identify causal effects.
+The following section therefore presents a research design building on a rare change in the migration framing in Germany's largest tabloid, *Bild*.
+It then develops a framework to measure emphasis framing in political communication, and presents a panel dataset tracking migration attitudes in the time-frame of interest, as well as a *difference-in-difference* design to estimate the causal effect of the changing framing.
+The final section discusses the expected effect size from experimental studies, in order to provide a baseline for comparison.
 
@@
 
-## A Rare Shift in Migration Framing
-
 In order to test whether changing news content affected political attitudes, I exploit an editorial change in the largest German newspaper, *Bild*.
 As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts.
-The fielding of a large-scale panel survey in the same period allow to assess the impact of news content on migration attitudes.
+The fielding of a large-scale panel survey in the same period allows to assess the precise impact of this change in news content on consumers' migration attitudes.
+
+## A Rare Shift in Migration Framing
 
@@
 The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win representation in the national parliament.
-Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* promoted an open stance towards the newly arriving in this period.
+Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* initially maintained a somewhat balanced coverage of the newly arriving, which - although portraying migrants more negatively than other outlets - even started a campaign called "#RefugeesWelcome" to gather support for the newly arriving [@Maurer2019; see @BildRefugeesWelcome].
 This was often connected to chief editor Kai Diekmann, who hosted a refugee family in his home [@BR2015Diekmann].
@@
 In a speech months before he took over the position as chief editor, Reichelt outlined his motivation for such a shift in migration coverage: "I can assure you: nothing has hurt [*Bild*] economically as much as our clear, humane, empathetic stance in the refugee crisis" \footnote{Reichelt in a speech at Deutschlandfunk's conference "Formate des Politischen 2016": \url{https://vimeo.com/190347766}}.
-While he expressed his support for the decision to take this stance at the time, he argued that the German media shows too little tolerance towards anti-immigration attitudes and therefore excludes those holding such views from political discourse.
+While he expressed his support for the decision to take this stance at the time, he argued that the German media is self-censoring and generally shows too little tolerance towards anti-immigration attitudes, thereby excluding those holding such views from political discourse.
 
 This case presents a unique case to study the effects of media content on public opinion.
-As will be shown below, a shift in migration coverage can be clearly identified.
-The change of editor itself was not discussed in the media, which means any opinion changes among readers are the result of the changing content [@Spirig2020].
+As I will show below, the emphasis of crime strongly increased in *Bild*'s migration coverage following Reichelt's takeover.
+The change of editor itself was not discussed in the media, which means any opinion changes among readers can only be the result of the changing content [see @Spirig2020].
 Additionally, the timing of the editorial change is potentially exogenous, given the pressure from allegations against Diekmann.
@@
 
-[Outline research design, measurement of frames in communication and thought, following RUne and Martin Bisgaard]
+In the following sections, I will outline a framework for the measurement of emphasis frames in communication and showcase the increasing emphasis of crime in *Bild*'s migration coverage (the treatment).
+Subsequent sections will describe the panel data and variables to measure frames in thought (namely migration attitudes and their correlation with attitudes about crime) and define the difference-in-difference estimator.
+I will close with a discussion of the expected experimental effect size and minimal effects of interest to provide baselines for comparison of the estimator.
 
@@
 
-To measure immigration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets \textit{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt} and the major German tabloid \textit{Bild} for the period 2013-2019 (for the market reach of each outlet, see table 1).
+To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets **Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt* and the major German tabloid *Bild* for the period 2013-2019 (for the market reach of each outlet, see table 1 in the appendix).
 Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration.
-Second, I identify content about crime *within* migration coverage by applying a similar supervised classifier.
-This approach closely resembles the value-expectancy model, as I first identify coverage about the *issue*, before identifying the considerations emphasized in the discussion of this issue.
+Second, I identify content about crime *within* migration coverage by applying another supervised classifier.
+This approach closely resembles the value-expectancy model outlined in section \@ref(framing-effects), as I first identify coverage about the *issue*, before identifying the considerations emphasized in the discussion of this issue.
 
 To identify whether an article is about migration, I employ supervised machine learning.
-As migration content is rare, and training data needs to be somewhat balanced, articles cannot be selected randomly for annotation[^1].
+As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3% of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}.
 Instead, I first construct a dictionary of terms related to migration.
 I use dictionary extension based on German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles.
-Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with most migration terms and 100 from the remainder in between) for each newspaper for a total of 1,800 papers.
-Then, a coder hand-coded these articles, assessing whether their main topic is related to migration.
-
-[^1]: If migration content made up about 3% of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall, as the best guess in highly imbalanced data is simply the most common outcome.
+Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with the highest share of migration terms and 100 from the remaining articles with relative frequencies of migration-related terms in between these two groups) for each newspaper for a total of 1,800 papers.
+Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 1.2.}.
 
@@
 
-```{r salience, fig.cap="Share of migration content out of all content in six different newspapers."}
-
-MigSaliencePlot()
-
-```
-
-Figure \@ref(fig:salience) shows the share of migration articles in each newspaper.
-Clear peaks in attention are visible surrounding the refugee movements of summer 2015, as well as following the large-scale sexual assaults on new years eve in Cologne 2016\footnote{Germany had a large debate about refugees and crime after the new year's eve 2015/16 in Cologne.
-According to a report of the ministry of interior in Northrhine-Westphalia, hundreds of women were sexually assaulted and robbed by men they perceived to be of "north-african/arabic" descent (Ministerium für Inneres und Kommunales des Landes Nordrhein-Westfalen 2016).}, and a conflict over asylum policy between the conservative sister parties CDU and CSU, which almost led to the breakdown of the governing coalition in 2018.
-Newspapers seem to be event-driven and follow largely parallel trends, albeit at different levels, with the centre-left \textit{SZ} discussing migration most and the tabloid \textit{Bild} least.
-Attention decreases in mid-2016, but remains high compared to pre-2015 levels.
-Surrounding the fielding period of the survey waves (gray vertical lines), most newspapers show similar levels of attention to the issue between 2.5% and 6% of all articles, with the exception of \textit{SZ}, which moves between 5% and 12.5%.
-
 To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest.
@@
 The share of migration content devoted to news about crime allows me to assess the prominence of the consideration of crime within migration coverage.
-As an example of the content, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood.
-All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about new years eve in cologne.
+Exemplifying the narture of the treatment, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood.
+All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about the sexual assaults surrounding new years eve in cologne.
 
@@
 The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line).
-As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased briefly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change.
-The trends run largely parallel to each other preceding the treatment, with the major exception being the few months following the events at new year's eve in Cologne 2015/16\footnote{Note that the delayed increase in crime coverage and the low levels of attention to crime in *Bild*'s migration coverage in 2016 are partially the result of a changing number of articles being published.
-This can be traced back to a changing share of content from the German news agency *dpa*, which provides services to quickly distribute news content similar to the Associated Press.
-Estimates excluding content from *dpa* indicate a change in attention to crime of similar size, as can be seen in appendix 1.}.
-The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in Bild.
-One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, while other newspapers maintained their levels of attention.
+As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased directly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change\footnote{Note that this data is corrected for large changes in the overall number of articles being published by Bild.
+These chacnges can be traced back to a changing share of content from the German news agency dpa, which provides services to quickly distribute breaking news similar to the Associated Press.
+Estimates including content from dpa indicate a change in attention to crime of even larger size (6 percentage points), as can be seen in appendix 1.4.}.
+The trends run parallel to each other preceding the treatment.
+The lower attention to crime in 2015 and the increase in 2016 is in line with prior research [@Maurer2019].
+The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in *Bild*.
+One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, increasing the share of articles devoted to crime by around 5 percentage points, while other newspapers maintained their levels of attention.
 
@@
 
-TreatmentTrendPlot() + 
-  TreatmentDiDPlot()
+TreatmentTrendPlot(dpa_corrected = T) + 
+  TreatmentDiDPlot(dpa_corrected = T)
 
@@
 
-In order to assess the impact of this change in framing on public opinion, it is necessary to use data on consumers' immigration attitudes, as well as their news consumption.
-The 2017 Election Panel by the German Longitudinal election study luckily contains this data.
-This study consists of a total of 15 waves from 2016-2020, with 10,000 - 20,000 respondents per wave [@GLES2017Panel].
-Thirteen of these waves contain questions on immigration attitudes, asking respondents whether immigration of foreigners should be restricted or made easier.
+In order to assess the impact of this change in framing on public opinion, it is necessary to use data on citizens' immigration attitudes, as well as their news consumption.
+The 2017 Election Panel by the German Longitudinal election study contains this data.
+It consists of a total of 15 waves from 2016-2020, with 10,000 - 20,000 respondents per wave [@GLES2017Panel].
+Thirteen of these waves contain questions on immigration attitudes, asking respondents whether immigration of foreigners should be liberalized or  restricted.
 Responses were recorded on a seven-point Likert scale.
-This variable was centered on zero ($-3$ - easier, $3$ - restricted; the precise wording in the survey can be found in appendix 3.2).
+This variable was centered on zero ($-3$ - liberalize, $3$ - restrict; the precise wording in the survey can be found in appendix 3.2).
 
@@
 
-I will present evidence from a *difference-in-differences* (DiD) estimator to show the effect of the editorial change - and the related content shift - on migration attitudes:
+To assess the precise impact of increased attention to crime in migration coverage, I will present evidence from a *difference-in-differences* (DiD) estimator to show the effect of the editorial change - and the related content shift - on migration attitudes:
 
 $$
-y_{iw} = \alpha + \beta_1*Post_w + \beta_2 * BildReader_i + \beta_3 * Post_w * BildReader_i + \phi_w + \rho_i + \epsilon_{it} 
+y_{iw} = \alpha + \beta_1*Post_w + \beta_2 * Post_w * BildReader_i + \phi_w + \rho_i + \epsilon_{it} 
 $$
@@
 $Post_w$ indicates whether an interview took place preceding or following the editorial change.
-The estimator of interest is $\beta_3$, which indicates the change in migration attitudes of *Bild* readers following the editorial change, controlling for pre-treatment differences ($BildReader_i$), as well as general pre-post shifts in migration attitudes ($Post_w$).
+The estimator of interest is $\beta_2$, which indicates the change in migration attitudes of *Bild* readers following the editorial change, controlling for time-constant ($\rho_i$) and wave-specific ($\phi_w$) factors with fixed effects, as well as general pre-post shifts in migration attitudes ($Post_w$).
+Note that the pre-treatment differences of treatment and control group are corrected for in the individual fixed effects, as the groups are constant over time (reaedrship is only assessed pre-treatment).
 
@@
 
-To provide a baseline expectation regarding the effects, it is useful to consider the expected effect size at this point.
+To provide a baseline expectation regarding the effect from experimental work, it is useful to consider the expected effect size at this point.
 Despite the abundance of framing effects studies, there is no common standard to assess the magnitude of framing effects.
-Even the correct measurement of the magnitude is a contested question, as different control groups (untreated, opposing frame, ...) can be compared [@Druckman2001; @Chong2007a, 109f for a discussion].
+Even the correct measurement of the magnitude is a contested question, as different control groups can be compared [@Druckman2001; @Chong2007a, 109f for a discussion].
 Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009b], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996].
-Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing pro and con arguments\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009b; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
+Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing opposing frames pushing respondents in opposite directions\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009b; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
 As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [see e.g.
 the recent debate regarding nudging effects: @Maier2022], reported effects likely display a selection bias towards strong treatments.
-The treatment can be considered rather strong here, as the crime consideration is associated with strongly negative evaluations and the relative increase in the prevalence of this content is large \footnote{6 percentage point increase compared to pre-treatment share of 8.36% in Bild, an over 70% increase.}.
-Additionally, given that readers already consumed the newspaper, the qualities of the sender should rather increase the effect size, while the high salience of the issue should decrease it.
+The treatment can be considered rather strong here, as the crime consideration is associated with a strongly negative evaluation and the relative increase in the prevalence of this content is large \footnote{5 percentage point increase compared to pre-treatment share of 8.36 percent in Bild, a 60 percent increase.}.
 Given these considerations, I expect an effect of around 10% of the scale, or 0.6 on the seven-point scale\footnote{As the scale runs from one to seven, it spans six points wide.}, which represents a conservative estimate compared to reported experimental effects.
 
-As suggested by @Lakens2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI, indicated by dotted lines in the figures below), as well as a conservative estimate of the experimentally expected effect.
+As suggested by @Lakens2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI, indicated by dotted lines in the figures below) in order to detect possible null effects.
 I define the SESOI at a 2.5% change, or 0.15 on the seven-point scale, which represents a fraction of the conservative experimental estimate and sets a fairly low bar given the strong treatment.
@@
 # Results
+
+The following section discusses the results.
+I will first present the above-discussed estimate of the effect on immigration attitudes and the association of immigration with crime attitudes.
+Then, I will assess the impact across time and on related variables to assess the robustness of the estimation.
+The last section will trace the key assumptions in the translation of experimental estimates discussed in section \@ref(framing-limits).
 
@@
 If the 95% interval is contained within these boundaries, the hypothesis that the estimate is larger than the SESOI can be rejected.
-The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment ($t = $ `r round(t_ATT, 2)`, $p = $ `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.6)`% of the expected effect of 0.6.
+The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment (*t =* `r round(t_ATT, 2)`, *p =* `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.6)`% of the expected effect of 0.6.
 The 95% confidence interval also contains values far smaller than the SESOI of 0.15 but clearly include the vertical solid red line indicating no change.
@@
 
-# Mechanism
+## Assumptions in the Translation of Experimental Estimates
 
-## Effect on News Consumption
+### Selective Exposure
 
@@
 
-## Openness to Change
+### Attitude Crystallisation
 
@@
 When the newspaper changes its migration coverage one and a half years later, the critical window of opportunity seems to have closed, as migration attitudes had crystallized.
+
+### Crowding Out
 

### 2022-09-02 pres/Presentation.Rmd
Update presentation

@@
 TreatmentTrendPlot(size = 2, 
-                   cntrl_col = "#004A95", 
-                   treat_col = "#cc0000") +
+                   dpa_corrected = T) +
   theme_xaringan()
@@
 
-EffectPlot(multi = F, scaled = "raw", size = 2) +
+DiDPlot(multi = F, scaled = "raw", size = 2) +
   theme_xaringan()
@@
 
-EffectPlot(multi = T, scaled = T, size = 2) +
+DiDPlot(multi = T, scaled = T, size = 2) +
   theme_xaringan()
@@
 
-EffectByWavePlot(size = 2) +
+DiDByWavePlot(size = 2) +
   theme_xaringan()
@@
 
-EffectByWavePlot("2880h_clean", size = 2) +
+DiDByWavePlot("2880h_clean", size = 2) +
   theme_xaringan()
@@
 
-EffectByWavePlot(dv = "1210_clean", size = 2) +
+DiDByWavePlot(dv = "1210_clean", size = 2) +
   theme_xaringan()
@@
 
-EffectByWavePlot(dv = "430i_clean", size = 2) +
+DiDByWavePlot(dv = "430i_clean", size = 2) +
   theme_xaringan()
@@
 
-EffectByWavePlot(dv = "mip_mig", size = 2) +
+DiDByWavePlot(dv = "mip_mig", size = 2) +
   theme_xaringan()

### 2022-09-07 paper/appendix.Rmd
Add section on crowding out

@@
 InSelection()
+
+```
+## Crowding out
+
+```{r crowdout}
+
+gles_long <- 
+  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
+  select(lfdn, date_clean, wave, 
+         `1661a_clean`:`1661g_clean`, `1600_clean`, `1681f_clean`,
+         `1130_clean`, post, treat)
+
+gles_long <- 
+  gles_long %>% 
+  mutate(
+    other_print = 
+      `1661b_clean` +
+      `1661c_clean` +
+      `1661d_clean` +
+      `1661e_clean` +
+      `1661f_clean` +
+      `1661g_clean`,
+    dv = `1130_clean`,
+    tv_use = `1681f_clean`,
+    in_use = `1600_clean`,
+    treat = as.factor(treat),
+    post = as.factor(post)
+  ) %>% 
+  mutate(other_print = 
+           case_when(
+             other_print == 0 ~ "0",
+             other_print > 0  & 
+               other_print <= 3 ~ "1-3",
+             other_print > 3  & 
+               other_print <= 9 ~ "4-9",
+             other_print > 9  & 
+               other_print <= 15 ~ "10-15",
+             other_print > 15 ~ ">15"
+           )
+        ) %>% 
+  filter(!wave %in% c("a1", "a2"))
+
+ests <- 
+  data.frame(
+    CATE = NULL,
+    CATE_lower = NULL,
+    CATE_upper = NULL,
+    value = NULL,
+    moderator = NULL
+  )
+
+for (mod in c("tv_use", "in_use", "other_print")){
+
+  values <- 
+    gles_long %>%
+    filter(!is.na(get(mod))) %>% 
+    select(mod) %>% 
+    unique() %>% 
+    .[[1]]
+
+  for (value in values){
+
+    temp <- 
+      gles_long %>% 
+      filter(get(mod) == value)
+
+    m <- 
+      fixest::feglm(dv ~ post*treat | ID + Wave, 
+                  data = 
+                    temp %>% 
+                    filter(!is.na(dv)) %>% 
+                    mutate(
+                      Wave = 
+                        ifelse(
+                          wave %in% sort(unique(.$wave))[c(1, 2)],
+                          "reference",
+                          wave
+                        ),
+                      ID = lfdn
+                    ) %>% 
+                    select(dv, post, treat, ID, Wave),
+                  cluster = c("ID", "Wave"))
+
+    ests <- 
+      rbind(
+        ests,
+        data.frame(
+          CATE = m$coefficients["postTRUE:treatTRUE"],
+          CATE_lower = confint(m)["postTRUE:treatTRUE", "2.5 %"],
+          CATE_upper = confint(m)["postTRUE:treatTRUE", "97.5 %"],
+          value = value,
+          moderator = mod
+        )
+      )
+
+  }
+
+}
+
+ests <- 
+  ests %>% 
+  mutate(
+    effect_label = 
+      ifelse(
+        value == "0",
+        as.character(round(CATE, 3)),
+        ""
+      ),
+
+  )
+
+varnames <- 
+  list(
+    "in_use" = "Internet use", 
+    "other_print" = "Days other print consumed", 
+    "tv_use" = "TV use")
+
+labeller <- function(variable,value){
+  return(varnames[value])
+}
+
+ests %>%
+  ggplot(aes(x = factor(value,
+                        levels = as.character(c(0, 1, "1-3", 2, 3, 4, "4-9", 
+                                              5, 6, 7, 8, 9, 10, "10-15",
+                                              ">15"))), 
+             y = CATE, ymin = CATE_lower, ymax = CATE_upper,
+             col = value != "0")) +
+  geom_hline(yintercept = 0) +
+  geom_hline(yintercept = c(0.15, -0.15), lty = 3) +
+  geom_hline(yintercept = c(0.6, -0.6), lty = 2) +
+  geom_pointrange() +
+  geom_text(aes(x = "0", 
+                y = CATE, 
+                label = effect_label,
+                hjust = -.3)
+            ) +
+  facet_wrap(~moderator, scales = "free_x",
+             labeller = labeller) +
+  theme_minimal() +
+  xlab("") +
+  theme(legend.position = "None")
 

### 2022-09-07 paper/Manuscript_Framing.Rmd
update
FIx figure placement,
improve case description, empirical strategy, results

@@
   @CologneReport2016
+indent: true
 ---
@@
 
-knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T)
+knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T, fig.pos = "!h", out.extra = "")
 
@@
 
-***Association hypothesis*****: When an individual is exposed more to a specific consideration about an issue, their association of the issue with this consideration should be strengthened.**
+\medskip
 
-***Evaluation hypothesis*****: When an individual is exposed more to a specific positive/negative consideration about an issue, their attitude about the overall issue should become more positive/negative.**
+\noindent \textit{\textbf{Association hypothesis}: When an individual is exposed more to a specific consideration about an issue, their association of the issue with this consideration should be strengthened.}
+
+\noindent \textit{\textbf{Evaluation hypothesis}: When an individual is exposed more to a specific positive/negative consideration about an issue, their attitude about the overall issue should become more positive/negative.}
 
@@
 As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts.
-The fielding of a large-scale panel survey in the same period allows to assess the precise impact of this change in news content on consumers' migration attitudes.
+The fielding of a large-scale panel survey in the same period allows to assess the precise impact of this change in news content on consumers' migration attitudes and related variables.
 
@@
 The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win representation in the national parliament.
-Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* initially maintained a somewhat balanced coverage of the newly arriving, which - although portraying migrants more negatively than other outlets - even started a campaign called "#RefugeesWelcome" to gather support for the newly arriving [@Maurer2019; see @BildRefugeesWelcome].
+Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* initially maintained a somewhat balanced coverage of refugees, which - although still portraying migrants more negatively than other outlets [@Maurer2019] - even started a campaign called "#RefugeesWelcome" to gather support for the newly arriving\footnote{See \url{https://web.archive.org/web/20160114154402/https://www.bild.de/news/topics/fluechtlingshilfe/wir-helfen-buehne-42385428.bild.html}.}.
 This was often connected to chief editor Kai Diekmann, who hosted a refugee family in his home [@BR2015Diekmann].
 
-In December 2016, Axel Springer, the company owning Bild, announced that Diekmann will leave the company.
+About one and a half years later, in December 2016, Axel Springer, the company owning *Bild*, announced that Diekmann will leave the company.
 Less than a week after, it became public that prosecutors investigate Diekmann for sexual harassment.
@@
 
-This case presents a unique case to study the effects of media content on public opinion.
+This case presents a unique opportunity to study the effects of media content on public opinion.
 As I will show below, the emphasis of crime strongly increased in *Bild*'s migration coverage following Reichelt's takeover.
@@
 
-To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets **Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt* and the major German tabloid *Bild* for the period 2013-2019 (for the market reach of each outlet, see table 1 in the appendix).
+To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets *Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt* and the major German tabloid *Bild* for the period 2013-2019.
+These outlets reach a substantial share of the German public, with *Bild* distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 1.1 in the appendix for more information).
 Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration.
 Second, I identify content about crime *within* migration coverage by applying another supervised classifier.
-This approach closely resembles the value-expectancy model outlined in section \@ref(framing-effects), as I first identify coverage about the *issue*, before identifying the considerations emphasized in the discussion of this issue.
+This approach closely resembles the value-expectancy model outlined in section \@ref(framing-effects), as I first identify coverage about the *issue*, before identifying the consideration emphasized in the discussion of this issue.
 
 To identify whether an article is about migration, I employ supervised machine learning.
-As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3% of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}.
+As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3 percent of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}.
 Instead, I first construct a dictionary of terms related to migration.
-I use dictionary extension based on German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles.
+After constructing a seed dictionary of migration-related terms, I apply dictionary extension using German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles\footnote{The dictionary can be found in appendix XX.}.
 Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with the highest share of migration terms and 100 from the remaining articles with relative frequencies of migration-related terms in between these two groups) for each newspaper for a total of 1,800 papers.
-Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 1.2.}.
+Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{The coder was instructed to annotate articles referring to migration or integration, which includes discussions of refugee numbers, immigrants' and naturalization rights, and general reports of migration.}.
 
@@
 This classifier is then used to annotate all 2.5 million newspaper articles.
-For the period from 2013 to 2019, around 90,000 (3.6%) are identified to treat the issue of migration.
+For the period from 2013 to 2019, around 90,000 (3.6%) are identified to treat the issue of migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 1.2.}.
 
@@
 Using a training set of 1400 articles, a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%.
-I then apply this classifer to identify the approximately 90,000 articles about migration identified by the first classifier.
-About 7% of all migration coverage consists of articles about some form of crime\footnote{See appendix 1.2 for more information about the classifier, training process and data.}.
-The share of migration content devoted to news about crime allows me to assess the prominence of the consideration of crime within migration coverage.
-Exemplifying the narture of the treatment, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood.
+I then apply this classifier to identify the approximately 90,000 articles about migration identified by the first classifier.
+About 7% of all migration coverage consists of articles about some form of crime.
+Exemplifying the nature of the coverage, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood.
 All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about the sexual assaults surrounding new years eve in cologne.
@@
 The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line).
-As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased directly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change\footnote{Note that this data is corrected for large changes in the overall number of articles being published by Bild.
-These chacnges can be traced back to a changing share of content from the German news agency dpa, which provides services to quickly distribute breaking news similar to the Associated Press.
-Estimates including content from dpa indicate a change in attention to crime of even larger size (6 percentage points), as can be seen in appendix 1.4.}.
+As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased directly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change\footnote{Note that this data consists exclusively of original Bild content.
+Treatment estimates including third-party authored content are similar in size.
+For a more extensive discussion see appendix XX.}.
 The trends run parallel to each other preceding the treatment.
@@
 
-The panel also contains a question on newspaper consumption, which was asked in seven waves.
+To measure exposure to *Bild* news I use a question on newspaper consumption, which was asked in seven waves.
 The question provides respondents with a list of the six major daily newspapers plus an option "another daily newspaper", and asks whether they had consumed the paper in print or read articles from their website, and if so, how many days in the past week.
+Readers are defined as *treated* if they indicate to read *Bild* in the pre-treatment wave and as *untreated* if they indicate not to read the tabloid in the pre-treatment wave, nor any subsequent wave\footnote{See appendix XX for descriptives of all mentioned variables.}.
+
+In order to assess the effect on the association of immigration and crime, I also measure attitudes about crime using an item asking whether the governments' capabilities to fight crime should be extended\footnote{Precise question wording: "State powers to fight crime should be expanded, even if this means more surveillance of citizens."} on a 5-point Likert-scale.
+I also use additional dependent variables assessing attitudes about the need for immigrants to integrate into German culture (7-point scale), mentioning immigration as the most important problem (binary indicator), and a thermometer score for the radical-right *AfD* (10 point scale).
 
@@
 Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing opposing frames pushing respondents in opposite directions\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009b; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
+[add reference to GSS running welfare panel with welfare vs assistance to the poor form \url{https://www.youtube.com/watch?v=a_CmfRjZ_oY}.
+Problem with this: much better data to show your argument, kinda opposite result - look into this though, maybe after finishing the paper!]
+
 As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [see e.g.
@@
 
-Figure \@ref(fig:singleplot) visualizes the effect of the change in framing on immigration attitudes.
+[simplify all of these sections, follow economist papers from course]
+
+According to the expectancy-value model (see section \@ref{framing-effects}), the most direct implication of increased exposure to crime frames in migration coverage should be a more conservative assessment of immigration.
+Figure \@ref(fig:singleplot) visualizes the effect of the change in framing on immigration attitudes, with higher values indicating that *Bild* readers change their attitudes in a more restrictive direction, compared to the control group.
 Dashed vertical lines indicate the expected effect from the experimental literature.
 The dotted lines indicate the equivalence boundaries.
-If the 95% interval is contained within these boundaries, the hypothesis that the estimate is larger than the SESOI can be rejected.
-The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment (*t =* `r round(t_ATT, 2)`, *p =* `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.6)`% of the expected effect of 0.6.
-The 95% confidence interval also contains values far smaller than the SESOI of 0.15 but clearly include the vertical solid red line indicating no change.
 Surprisingly, the model suggests a clear null effect.
+This effect is not significantly different from zero, but significantly smaller than the above-defined minimal effect of 0.15 on the seven-point Likert scale.
+The point estimate indicates a `r round(ATT, 3)`-point change among *Bild* readers following treatment (*t =* `r round(t_ATT, 2)`, *p =* `r round(p_ATT, 2)`).
+This represents only a fraction (`r round(ATT/0.6, 3)*100`%) of the already conservative experimental estimate of 0.6.
 
@@
 
-As outlined above, framing theory suggests that increased exposure to a specific consideration about an issue leads to stronger association of the issue with this consideration.
+Framing theory suggests that increased exposure to a specific consideration about an issue also leads to stronger association of the issue with this consideration.
 In the present case, this should mean that the correlation of attitudes on immigration with attitudes about crime should increase.
@@
 
-Figure \@ref(fig:corplot) shows the correlation of crime- and migration attitudes in treatment (Bild-readers in pre-wave) and control group (never Bild-readers), pre- and post-treatment.
-I added a counterfactual, applying the change in the control group to the treatment group, for easier interpretation.
-As we can see, the treatment group actually saw a *smaller* increase in the correlation of crime and migration attitudes than the control group, *despite weaker pre-treatment association*.
-Following [@Nelson1996], table \@ref(tab:cortable) regresses immigration attitudes on attitudes towards crime and investigates whether this association is generally different between the two groups\footnote{These differences are however in the opposite direction as the (substantial) differences in the descriptive correlations outlined in the plot.
-I am currently not sure how to interpret this.}, changes post-treatment, and whether it changes more in the treatment group using interaction terms.
-I find minor differences between the groups, but no significant difference when interacted with the DiD-term - respondents do not seem to associate crime more strongly with migration following the change in migration coverage in *Bild*.
+```{r corests}
+
+bs <- MigCrimeCorPlotBS(return_ests = T)
+
+deltas_3 <- 
+  (bs[["mig_crime_cor"]][bs$treat & bs$wave == 3] - 
+    bs[["mig_crime_cor"]][bs$treat & bs$wave == 1]) -
+  (bs[["mig_crime_cor"]][!bs$treat & bs$wave == 3] - 
+    bs[["mig_crime_cor"]][!bs$treat & bs$wave == 1])
+
+deltas_13 <- 
+  (bs[["mig_crime_cor"]][bs$treat & bs$wave == 13] - 
+    bs[["mig_crime_cor"]][bs$treat & bs$wave == 1]) -
+  (bs[["mig_crime_cor"]][!bs$treat & bs$wave == 13] - 
+    bs[["mig_crime_cor"]][!bs$treat & bs$wave == 1])
+
+```
+
+Figure \@ref(fig:corplot) shows the bootstrapped correlations of crime- and migration attitudes in treatment (Bild-readers in pre-wave) and control group (never Bild-readers), pre- and post-treatment.
+The lines indicate the mean estimate, while the whiskers indicate the upper and lower 95%-confidence interval, as defined by the 2.5% and 97.5% percentiles of the distribution of estimates of the correlation.
+I added a counterfactual, applying the changes in the control group to the treatment group, for easier interpretation.
+Surprisingly, the association of crime and immigration attitudes is initially weaker among *Bild* readers.
+Nevertheless, the treatment group actually saw a *smaller* increase in the correlation of crime and migration attitudes in the first post-treatment wave than the control group.
+The difference-in-differences in correlations of `r round(mean(deltas_3), 3)` is substantively rather small (`r abs(mean(deltas_3)/mean(bs[["mig_crime_cor"]][!bs$treat & bs$wave == 1])) %>% round(3)` of the average pre-treatment control group correlation) and not significantly different from zero with a bootstrapped 95% confidence interval of [`r quantile(deltas_3, 0.025)[[1]] %>% round(3)`, `r quantile(deltas_3, 0.975)[[1]] %>% round(3)`].
+In the last wave, the association decreases less than in the control group but the difference-in-differences does not reach conventional levels of significance compared to the pre-treatment wave (`r round(mean(deltas_13), 3)`, [`r quantile(deltas_13, 0.025)[[1]] %>% round(3)`, `r quantile(deltas_13, 0.975)[[1]] %>% round(3)`]).
 
@@
 
-MigCrimeCorPlot()
+MigCrimeCorPlotBS()
 
 ```
+
+Following [@Nelson1996], table \@ref(tab:cortable) also regresses immigration attitudes on attitudes towards crime and investigates whether this association changes as a result of the change in coverage (note that all constituent terms are included but only those regarding the association of crime and immigration attitudes reported).
+Similar to the differences between the groups, I find a weaker association among readers of the tabloid, but no significant or substantively large difference post-treatment or when interacted with the DiD-term.
+Respondents do not seem to associate crime more strongly with migration following the change in migration coverage in *Bild*.
 
@@
 ```
-
-[explain why this is done, and why constituent terms are not interesting - only the change in association of crime attitude and dependent variable is of interest, we are not trying to explain variation in the dependent variable!
-(which is also why R2 doesn't matter here)]
 

### 2022-09-09 paper/Manuscript_Framing.Rmd
Update working paper

@@
     fig_caption: yes
-    includes:
-      in_header: preamble.tex
+    # includes:
+    #   in_header: preamble.tex
 # subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
@@
 abstract: "Does news framing affect public opinion?
-While a large body of experimental work suggests that individual attitudes can be easily altered by emphasizing different aspects of an issue, little is known about how these studies translate into the real world.
-I exploit a rare change in the migration framing of the major German tabloid *Bild* to study whether experimental estimates of framing effects translate into the real world.
+While a large body of experimental work suggests that individual attitudes can be easily altered by emphasizing different aspects of an issue, little is known about how these studies generalize to real world environments.
+I exploit a rare change in the migration framing of the major German tabloid *Bild* to bridge this gap.
 In a first step, I develop a framework for the measurement of emphasis frames in political communication using supervised machine learning.
-Using this framework, I show that the emphasis of crime in *Bild*'s migration coverage severely increased.
-Second, I employ a difference-in-differences design using panel data from over 16,000 individuals in ten waves to assess the precise impact of this shift on migration attitudes.
-The findings show that, despite a major change in migration framing, a clear null effect on immigration attitudes and related variables can be observed.
-Tracing three key assumptions underlying the translation of experimental effect estimates suggests that news framing affects attitudes only within limited windows of opportunity early in the politicization of political issues."
+Using this framework, I show that the emphasis of crime in *Bild*'s migration coverage severely increased following an exogenously timed change of editor.
+Second, I employ a difference-in-differences design using panel data from over 16,000 individuals in thirteen waves to assess the precise impact of this shift on migration attitudes.
+Despite a major change in migration framing, a robust null effect on immigration attitudes and a number of related variables can be observed.
+These findings caution against the generalization of experimental framing studies to real-world environments and open a broader research agenda to study the precise impact of political communication beyond the experimental setting."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
@@
 
-knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T, fig.pos = "!h", out.extra = "")
+knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T, fig.pos = "!ht", out.extra = "")
 
@@
 
+\medskip
+
 *I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
 Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim as well as participants of CompText 2022, EPSA 2022, ICA 2022, EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI,  and the Political Behaviour Section at Aarhus University.
-I also thank the two RAs, Robin Groß and Nathalie Aerts, for annotating the news articles.
+I also thank the two research assistants, Robin Groß and Nathalie Aerts, for annotating the news articles.
 All remaining confusions are my own.*
@@
 Does news framing affect public opinion?
-While a large body of experimental evidence suggests that the emphasis of a certain consideration can substantially alter issue attitudes, we know little about the translation of these findings into real-world environments.
-Prior work has shown that the external validity of such experiments might be seriously complicated by the current salience and politicisation of the issue of interest [@Arceneaux2009; @Bechtel2015; @Lecheler2009a], the availability of different frames [@Chong2007; @Chong2013; @Druckman2003; @Druckman2012] and communicating actors [@Slothuus2010], as well as the seeking and avoidance of specific content [@Lau2021a; @Taber2006].
+Despite the profound importance for the understanding of elite influence in modern democracies, we know little about the persuasive effects of news framing in real-world environments.
+A large body of experimental evidence suggests that the emphasis of specific considerations can substantially alter issue attitudes, However observational data suggests little variation in individual attitudes [@Kustov2021] and prior work has shown that the external validity of such experiments might be seriously complicated by the current salience and politicization of the issue of interest [@Arceneaux2009; @Bechtel2015; @Lecheler2009b], the availability of different frames [@Chong2007a; @Chong2013; @Druckman2003; @Druckman2012] and communicating actors [@Slothuus2010], as well as the seeking and avoidance of specific content [@Arceneaux2009; @Lau2021a; @Taber2006].
 Contemporary news environments provide consumers with especially diverse content and maximize their abilities to choose specific outlets and avoid others [@Bennett2008], thereby increasing the gap between the real-world environment and experimental studies.
@@
 In this article, I provide the - to my knowledge - first observational estimate of framing effects by exploiting a rare shift in the framing of a highly politicized issue - migration - in Germany's largest tabloid newspaper, *Bild*.
-The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet substantially changed its framing while other papers maintained theirs.
+The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet severely changed its coverage, while other papers did not.
 Providing a novel framework for the measurement of emphasis frames using BERT models, I study migration framing in a corpus of 2.5 million newspaper articles.
-I show that the newspaper's migration coverage saw a strong increase in the use of crime frames after the editor in chief was replaced.
-The fielding of the German Longitudinal Election Study in the same period provides the rare opportunity to precisely assess the effect of framing on political attitudes using a *difference-in-differences (DiD) design*.
+I show that the newspaper's migration coverage saw a strong increase in the use of crime frames after the editor in chief was abruptly replaced.
+The fielding of the German Longitudinal Election Study Panel [@GLES2017Panel] in the same period provides the rare opportunity to precisely assess the effect of framing on political attitudes using a *difference-in-differences (DiD) design*.
 
-The results indicate that even a strong increase in the use of crime frames did not affect consumers' immigration attitudes.
+The results indicate that even this strong increase in the use of crime frames did not affect consumers' immigration attitudes.
 The estimated effect is statistically indistinguishable from zero and significantly smaller than even minimally relevant effect magnitudes.
 Related issue attitudes, voting behavior, and issue importance are similarly unaffected, as is the association of immigration attitudes with the frame provided.
-Tracing different assumptions underlying the translation of experimental estimates of framing effects into the real world implies that this lack in responsiveness is not an outcome of readers abandonment of the newspaper, nor the "crowding out" of information through other sources, but rather the crystallization of immigration attitudes prior to the change in framing.
+Tracing different assumptions underlying the generalization of experimental estimates of framing effects into the real world implies that this lack in responsiveness is not an outcome of readers abandonment of the newspaper, nor the "crowding out" of information through other sources, but rather the crystallization of immigration attitudes prior to the change in framing.
 
-Overall, these findings fundamentally challenge the external validity of a large body of framing effects research and suggest that the influence of individual news outlets on public opinion is more limited than previously thought.
+Overall, these findings fundamentally challenge the external validity of a large body of framing effects research and suggest that the influence of media elites on public opinion is more limited than previously thought.
 Even a strong change in news framing did not affect political attitudes.
 Instead, it seems that the news media faces limited windows of opportunity to shape public opinion during the politicization of novel political issues.
+Additionally, the study contributes to a large body of media effects research in economics and political science by opening a research agenda to study the effects of political communication in the real world.
 
@@
 Many other forms of framing exist, such as equivalence frames [@Kahneman1979prospect], episodic frames [@Iyengar2005], or generic frames [@DeVreese2005].
-The focus on emphasis frames in this study is owed to the generalized theory regarding their effect on attitudes about any issue (as opposed to generic and episodic frames), as well as their common use in news content (which is not the case for equivalence frames).
+The focus on emphasis frames in this study is owed to the nature of the case, as well as the generalized theory regarding the effect of emphasis frames on attitudes about any issue (as opposed to generic and episodic frames) and their common use in news content (which is not the case for equivalence frames).
 
@@
 For example, to form an opinion about whether immigration to one's country should be restricted, a person might consider the humanitarian conditions in the countries of origin (negative consideration regarding restrictive migration policy), as well as the risk of increased crime (positive consideration; note that the model does not differentiate whether a consideration is grounded in objective reality).
-Individuals weigh each of these considerations (so-called "frames in thought"; @Druckman2001) to form an overall opinion on the subject.
+Individuals weigh each of these considerations [so-called "frames in thought", @Druckman2001] to form an overall opinion on the subject.
 
 Figure \ref{fig:cogStor} visualizes this logic.
-A given issue (bottom square) carries an attitude $y$.
+An individual holds an attitude $y$ about a given issue (bottom square).
 The issue is associated with a number of different considerations (top circles), each of which carries an evaluation $x_i$, e.g.
-crime is viewed very negatively.
-Based on the strength of the association $w_i$ of a given consideration with the issue, a given consideration's evaluation is more or less reflected in the overall attitude $y$, which is equal to the weighted sum of considerations.
-For example, if a given individual associates immigration strongly with an increase in criminal activity, welfare fraud, but only very weakly with humanitarian considerations, cultural enrichment, liberty, or economic growth, they will form a rather negative attitude about the issue, as the former factor more prominently in their reasoning about migration.
+a potential surge in crime is considered a negative outcome.
+Based on the strength of the association $w_i$ of a given consideration with the issue, a given consideration's evaluation is more or less reflected in the overall attitude $y$, which is equal to the weighted sum of evaluations.
+For example, if a given individual associates immigration strongly with an increase in criminal activity and welfare fraud, but only very weakly with humanitarian considerations, cultural enrichment, liberty, or economic growth, they will form a rather negative attitude about the issue, as the former factor more prominently in their reasoning about migration.
 
@@
 How does this model incorporate news content and other forms of political communication?
-News content can emphasize different considerations of an issue (so-called "frames in communication").
+News content can emphasize different considerations of an issue ("frames in communication").
 By being exposed to the consideration, an individual's cognitive association of the issue at hand with the raised consideration strengthens (or in more technical terms: the weight of the consideration $w_i$ increases).
@@
 Applying this to the issue of migration policy and the consideration of criminal migrants, one can imagine a news consumer confronted with an increased volume of news about crimes committed by migrants.
-The value-expectancy model predicts that 1) the consumer forms a cognitive definition of migration that is increasingly associated with the issue of crime, meaning this consideration features more prominently when forming an opinion about the appropriate level of immigration; 2) as a result, their opinion about migration policies should become more restrictive, as the negative consideration of crime is weighted more heavily in the evaluation of the migration issue.
+The value-expectancy model predicts that i) the consumer forms a cognitive definition of migration that is increasingly associated with the issue of crime, meaning this consideration features more prominently when forming an opinion about the appropriate level of immigration; ii) as a result, their opinion about migration policies should become more restrictive, as the negative consideration of crime is weighted more heavily in the evaluation of the migration issue.
 
@@
 However, it remains unclear how well these experimental findings translate into the real world.
-Below, I outline three key assumptions in the translation of experimental estimates.
+Below, I outline three key assumptions in the generalization of experimental estimates.
 
 First, taking experimental effects as estimates of the real-world impact of framing means making strong assumptions about citizens' exposure to frames: while framing studies usually simply present news articles or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience.
-Changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news content containing such frames (and vice versa seek out attitudinally congruent information).
-This idea of 'selective exposure/avoidance' [@Bennett2008], or a 'confirmation bias' [@Taber2006] brings with it a major endogeneity problem making purely correlational evidence of framing effects rather uninformative.
+Changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news content containing such frames [and vice versa seek out attitudinally congruent information, @Arceneaux2010; @Druckman2012Bias].
+This process of 'selective exposure/avoidance' [@Bennett2008], or a 'confirmation bias' [@Taber2006] brings with it a major endogeneity problem making purely correlational evidence rather uninformative.
 As most framing studies do not offer choice of content to respondents, engagement remains an assumption when taking experimental studies as evidence of framing effects in the real world [for an exception see @Druckman2012Bias].
@@
 Second, even if consumers receive the content, it is not clear how much an individual relies on this source when forming an opinion on the subject.
-Information from different sources - such as TV, newspapers, social media, or alternative online media - might 'crowd out' the framing of a single outlet: by consuming content from many sources, individuals might give less attention to a given source, thereby severely limiting the overall impact of that outlet's coverage.
+Information from different sources might 'crowd out' the framing of a single outlet: by consuming content from many sources, individuals give less attention to a given source, thereby severely limiting the overall impact of that outlet's coverage.
 Experimental evidence suggests that, when an individual receives competing frames, these cancel each other out, although the precise impact is dependent on the relative timing of exposure, the quality of the frame, as well as individual characteristics [@Chong2007b; @Chong2010; @Chong2013].
@@
 Most of these studies are concerned with exposure to a different outlet [@Bail2018; @Broockman2022; @Foos2022; @Grossman2022; @Guess2021].
-This is problematic, as citizens are often aware of outlets' political slant and engage with the coverage differently [@Baum2008; see also @Spirig2020 for a discussion of this issue].
-The existing studies focusing on within-outlet changes in coverage do not identify changing framing directly and assess effects on a broad set of dependent variables, rather than specific issue attitudes [@Levendusky2022; @Spirig2020].
+This is problematic, as citizens are often aware of outlets' political slant and engage with the coverage differently [@Baum2008a; see also @Spirig2020 for a discussion of this issue].
+Those studies focusing on within-outlet changes in coverage do not identify changing framing directly and assess effects on a broad set of dependent variables, rather than specific issue attitudes [@Levendusky2022; @Spirig2020].
 
@@
 This is especially problematic regarding framing effects, as news content can affect consumers' inclination to consume news (see preceding section), and political actors might react to public opinion.
-As both variables affect each other at the same time (endogeneity), it is impossible to assess which direction causality runs.
+As both variables affect each other at the same time, it is impossible to assess which direction causality runs.
 
@@
 
-It becomes obvious that the discipline lacks an understanding of how news framing affects political attitudes in the real world.
+Overall, it becomes obvious that we lacks an understanding of how news framing affects political attitudes in the real world.
 While experimental studies find strong effects, several assumptions have to be made to translate them beyond the lab or survey context.
-Observational evidence on media effects has not precisely studied the impact of framing.
-To do so, it is necessary to assess within-outlet changes in news framing and their effect on specific issue attitudes using a design able to identify causal effects.
+Observational evidence on media effects is only informative about broadly defined 'media effects' in specific cases, mostly without a more detailed focus on which content affects political attitudes.
+In order to identify the precise effects of changing news content, it is necessary to assess within-outlet changes in news coverage and their effect on specific issue attitudes using a design able to identify both the precise nature of the changes in content and their causal effects on attitudes.
 The following section therefore presents a research design building on a rare change in the migration framing in Germany's largest tabloid, *Bild*.
@@
 
-In order to test whether changing news content affected political attitudes, I exploit an editorial change in the largest German newspaper, *Bild*.
+In order to test whether changing news content affected political attitudes, I exploit an exogenously timed editorial change in the largest German newspaper, *Bild*.
 As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts.
@@
 About one and a half years later, in December 2016, Axel Springer, the company owning *Bild*, announced that Diekmann will leave the company.
-Less than a week after, it became public that prosecutors investigate Diekmann for sexual harassment.
+Less than a week after the announcement, it became public that prosecutors investigate Diekmann for sexual harassment.
 While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time support this interpretation of events.} [@Spiegel2017Diekmann].
@@
 In a speech months before he took over the position as chief editor, Reichelt outlined his motivation for such a shift in migration coverage: "I can assure you: nothing has hurt [*Bild*] economically as much as our clear, humane, empathetic stance in the refugee crisis" \footnote{Reichelt in a speech at Deutschlandfunk's conference "Formate des Politischen 2016": \url{https://vimeo.com/190347766}}.
-While he expressed his support for the decision to take this stance at the time, he argued that the German media is self-censoring and generally shows too little tolerance towards anti-immigration attitudes, thereby excluding those holding such views from political discourse.
+While he expressed his support for the decision to take this stance at the time, he argued that the German media shows too little tolerance towards anti-immigration attitudes, thereby excluding those holding such views from political discourse.
 
@@
 
-In the following sections, I will outline a framework for the measurement of emphasis frames in communication and showcase the increasing emphasis of crime in *Bild*'s migration coverage (the treatment).
+In the following sections, I will outline a framework for the measurement of emphasis frames in communication and showcase the increasing emphasis of crime in *Bild*'s migration coverage (treatment).
 Subsequent sections will describe the panel data and variables to measure frames in thought (namely migration attitudes and their correlation with attitudes about crime) and define the difference-in-difference estimator.
-I will close with a discussion of the expected experimental effect size and minimal effects of interest to provide baselines for comparison of the estimator.
+I will close with a discussion of the expected experimental effect size and the minimal effect size of interest to provide baselines for comparison of the estimator.
 
@@
 
-To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets *Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt* and the major German tabloid *Bild* for the period 2013-2019.
-These outlets reach a substantial share of the German public, with *Bild* distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 1.1 in the appendix for more information).
+To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets *Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt*, as well as *Bild* for the period 2013-2019.
+These outlets reach a substantial share of the German public, with *Bild* distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 1.1 in the appendix for more information\footnote{Online appendix available at \url{https://github.com/nicolaiberk/bild/raw/main/paper/appendix.pdf}.}).
 Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration.
-Second, I identify content about crime *within* migration coverage by applying another supervised classifier.
+Second, I identify content about crime *within* migration coverage by training and applying another supervised classifier.
 This approach closely resembles the value-expectancy model outlined in section \@ref(framing-effects), as I first identify coverage about the *issue*, before identifying the consideration emphasized in the discussion of this issue.
@@
 As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3 percent of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}.
-Instead, I first construct a dictionary of terms related to migration.
-After constructing a seed dictionary of migration-related terms, I apply dictionary extension using German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles\footnote{The dictionary can be found in appendix XX.}.
+Instead, I take a more informed approach by oversampling articles which are likely about migration: after constructing a seed dictionary of migration-related terms, I apply dictionary extension using German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles\footnote{The dictionary can be found in appendix XX.}.
 Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with the highest share of migration terms and 100 from the remaining articles with relative frequencies of migration-related terms in between these two groups) for each newspaper for a total of 1,800 papers.
@@
 This classifier is then used to annotate all 2.5 million newspaper articles.
-For the period from 2013 to 2019, around 90,000 (3.6%) are identified to treat the issue of migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 1.2.}.
+For the period from 2013 to 2019, around 90,000 articles (3.6%) are identified to treat the issue of migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 1.2.}.
 
 To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest.
-Using a training set of 1400 articles, a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%.
-I then apply this classifier to identify the approximately 90,000 articles about migration identified by the first classifier.
+Using a training set of 1400 articles (sleected using the identlical process as above), a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%.
+I then apply this classifier to the approximately 90,000 articles about migration identified by the first classifier.
 About 7% of all migration coverage consists of articles about some form of crime.
-Exemplifying the nature of the coverage, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood.
+Exemplifying the nature of the treatment, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood.
 All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about the sexual assaults surrounding new years eve in cologne.
 
-```{=tex}
-\begin{table}
-\centering
-\begin{tabular}{|p{12cm}|}
-\hline
-Final new years eve report of Cologne police: male groups identified \\ \hline
-Police searching for Northern-african offender: asylum-raid in Dortmund! \\ \hline
-Search in refugee home - mega-raid addressing asylum fraud \\ \hline
-Two groups attacking each other - again bloody conflict in refugee shelter \\ \hline
-Cabin fever! Violence! Mass brawls! This is behind the increase in refugee clashes \\ \hline
-\end{tabular}
-\caption{Headlines of five migration articles most likely to concern crime, according to BERT crime classifier. Translation by author.}
-\label{tab:exampleArticles}
-\end{table}
-```
-
-The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line).
+The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, black line), once for Bild and once for all other newspapers (dashed, gray line).
 As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased directly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change\footnote{Note that this data consists exclusively of original Bild content.
@@
 
-TreatmentTrendPlot(dpa_corrected = T) + 
-  TreatmentDiDPlot(dpa_corrected = T)
+TreatmentTrendPlot(dpa_corrected = T, palette = c("black", "gray")) + 
+  TreatmentDiDPlot(dpa_corrected = T, palette = c("black", "gray"))
 
@@
 
-In order to assess the impact of this change in framing on public opinion, it is necessary to use data on citizens' immigration attitudes, as well as their news consumption.
+In order to assess the impact of this change in framing on public opinion, I need data on citizens' immigration attitudes, as well as their news consumption.
 The 2017 Election Panel by the German Longitudinal election study contains this data.
@@
 
+<!-- missing: variables relating to generalisation -->
+
 ## Estimation
@@
 The estimator of interest is $\beta_2$, which indicates the change in migration attitudes of *Bild* readers following the editorial change, controlling for time-constant ($\rho_i$) and wave-specific ($\phi_w$) factors with fixed effects, as well as general pre-post shifts in migration attitudes ($Post_w$).
-Note that the pre-treatment differences of treatment and control group are corrected for in the individual fixed effects, as the groups are constant over time (reaedrship is only assessed pre-treatment).
+Note that the pre-treatment differences of treatment and control group are corrected for in the individual fixed effects, as the groups are constant over time (readership is only assessed pre-treatment).
+As the panel data contains only one pre-treatment wave, the parallel trends assumption cannot be tested with this data directly, but assessing the trends using the GLES Longterm Panel [@GLES2018LangfristPanel] shows that *Bild* and non-*Bild* readers' immigration attitudes move in parallel preceding the treatment (see appendix XX).
 
@@
 
-To provide a baseline expectation regarding the effect from experimental work, it is useful to consider the expected effect size at this point.
+To provide a baseline expectation regarding the effect size in experimental work, it is useful to consider the expected effect size at this point.
 Despite the abundance of framing effects studies, there is no common standard to assess the magnitude of framing effects.
@@
 Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009b], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996].
-Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing opposing frames pushing respondents in opposite directions\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009b; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
-[add reference to GSS running welfare panel with welfare vs assistance to the poor form \url{https://www.youtube.com/watch?v=a_CmfRjZ_oY}.
-Problem with this: much better data to show your argument, kinda opposite result - look into this though, maybe after finishing the paper!]
+Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing opposing frames pushing respondents in opposite directions\footnote{As many studies do not include a control group receiving no frame, this is the most comparable metric.} [@Lecheler2009b; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010].
 
@@
 the recent debate regarding nudging effects: @Maier2022], reported effects likely display a selection bias towards strong treatments.
-The treatment can be considered rather strong here, as the crime consideration is associated with a strongly negative evaluation and the relative increase in the prevalence of this content is large \footnote{5 percentage point increase compared to pre-treatment share of 8.36 percent in Bild, a 60 percent increase.}.
+The treatment in the present study can be considered rather strong, as the crime consideration is associated with a strongly negative evaluation and the relative increase in the prevalence of this content is large \footnote{5 percentage point increase compared to pre-treatment share of 11.8 percent in Bild, an over 40 percent increase.}.
 Given these considerations, I expect an effect of around 10% of the scale, or 0.6 on the seven-point scale\footnote{As the scale runs from one to seven, it spans six points wide.}, which represents a conservative estimate compared to reported experimental effects.
 
-As suggested by @Lakens2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI, indicated by dotted lines in the figures below) in order to detect possible null effects.
+As suggested by @Lakens2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI) in order to detect possible null effects.
 I define the SESOI at a 2.5% change, or 0.15 on the seven-point scale, which represents a fraction of the conservative experimental estimate and sets a fairly low bar given the strong treatment.
@@
 
-The following section discusses the results.
-I will first present the above-discussed estimate of the effect on immigration attitudes and the association of immigration with crime attitudes.
-Then, I will assess the impact across time and on related variables to assess the robustness of the estimation.
-The last section will trace the key assumptions in the translation of experimental estimates discussed in section \@ref(framing-limits).
+I will first present evidence describing the effect on immigration attitudes and the association of immigration with crime attitudes.
+Then, I will assess the impact across time and on related variables to inspect the robustness of the estimation.
+The last section will trace the key assumptions in the generalization of experimental estimates discussed in section \@ref(framing-limits).
 
@@
 
-[simplify all of these sections, follow economist papers from course]
-
-According to the expectancy-value model (see section \@ref{framing-effects}), the most direct implication of increased exposure to crime frames in migration coverage should be a more conservative assessment of immigration.
+According to the expectancy-value model (see section \@ref(framing-effects)), the most direct implication of increased exposure to crime frames in migration coverage should be a more restrictive attitude concerning immigration.
 Figure \@ref(fig:singleplot) visualizes the effect of the change in framing on immigration attitudes, with higher values indicating that *Bild* readers change their attitudes in a more restrictive direction, compared to the control group.
 Dashed vertical lines indicate the expected effect from the experimental literature.
-The dotted lines indicate the equivalence boundaries.
+The dotted lines indicate the equivalence boundaries/SESOI.
 Surprisingly, the model suggests a clear null effect.
-This effect is not significantly different from zero, but significantly smaller than the above-defined minimal effect of 0.15 on the seven-point Likert scale.
+This effect is not significantly different from zero, but significantly smaller than the above-defined SESOI of 0.15 on the seven-point Likert scale.
 The point estimate indicates a `r round(ATT, 3)`-point change among *Bild* readers following treatment (*t =* `r round(t_ATT, 2)`, *p =* `r round(p_ATT, 2)`).
 This represents only a fraction (`r round(ATT/0.6, 3)*100`%) of the already conservative experimental estimate of 0.6.
+The finding is robust to different model specifications, as well as using data from the GLES Longterm Panel (see appendix XX).
 
@@
 
-Figure \@ref(fig:corplot) shows the bootstrapped correlations of crime- and migration attitudes in treatment (Bild-readers in pre-wave) and control group (never Bild-readers), pre- and post-treatment.
-The lines indicate the mean estimate, while the whiskers indicate the upper and lower 95%-confidence interval, as defined by the 2.5% and 97.5% percentiles of the distribution of estimates of the correlation.
-I added a counterfactual, applying the changes in the control group to the treatment group, for easier interpretation.
+Figure \@ref(fig:corplot) shows the bootstrapped correlations of crime- and migration attitudes in treatment (*Bild*-readers in pre-wave) and control group (never *Bild*-readers), for each wave.
+The lines indicate the mean estimate, while the whiskers indicate the upper and lower 95%-confidence interval, as defined by the 2.5% and 97.5% percentiles of the distribution of bootstrapped estimates.
+The dotted line indicates the counterfactual development, assuming that *Bild*-readers behaved similar to the general population not reading *Bild* in the absence of a change in migration framing.
 Surprisingly, the association of crime and immigration attitudes is initially weaker among *Bild* readers.
@@
 
-Following [@Nelson1996], table \@ref(tab:cortable) also regresses immigration attitudes on attitudes towards crime and investigates whether this association changes as a result of the change in coverage (note that all constituent terms are included but only those regarding the association of crime and immigration attitudes reported).
-Similar to the differences between the groups, I find a weaker association among readers of the tabloid, but no significant or substantively large difference post-treatment or when interacted with the DiD-term.
-Respondents do not seem to associate crime more strongly with migration following the change in migration coverage in *Bild*.
+Following [@Nelson1996], I also regress immigration attitudes on attitudes towards crime and investigate whether this association changes as a result of the change in coverage.
+Similar to the differences between the groups, I find a weaker association among readers of the tabloid, but no significant or substantively large difference post-treatment or when interacted with the DiD-term (see table XX in appendix XX).
+Respondents do not associate crime more strongly with migration following the change in migration coverage in *Bild*.
 
-```{r cortable}
-
-MigCrimeCorTable()
-
-```
+<!-- description of findings needs to be simplified in entire section  -->
 
@@
 
-If readers only perceive the change in content across longer time periods, the effect should slowly unfold across time.
-If that is the case, initial absence of change might bias the estimates downward and thereby mask an effect.
+```{r didWaveEsts}
+
+ests <- DiDByWavePlot(return_ests = T)
+
+```
+
+If readers only perceive the change in content across longer time periods, the effect should slowly unfold over time.
+Then, initial absence of change might bias the estimates downward and thereby mask an effect.
 To assess whether an effect develops over time, figure \@ref(fig:migwaves) assesses the effect within split-samples for each post-wave compared to the pre-treatment wave.
@@
 The horizontal dashed line indicates the expected effect based on experimental evidence (0.6), whereas the dotted horizontal line indicates the SESOI of 0.15.
-The vertical (red) dashed line indicates the timing of the editorial change, whereas the dotted (orange) vertical line indicates the timing of the strong increase in crime framing in June 2017, several months after the takeover by Reichelt (see figure \@ref(fig:treatment)).
+The vertical (red) dashed line indicates the timing of the editorial change.
 Over the course of the entire year 2017, the effect is clearly smaller than the SESOI, and includes zero.
-However, estimates for waves 7 and 8 in late 2018 and mid-2019 - more than one and a half years after the editorial change - showcase effects statistically different from zero, and including the SESOI boundary.
-Note however that the effect is still tiny, with a point estimate smaller than a 0.1 on the seven-point Likert scale, as well as an upper boundary just above the SESOI at ??.
-The waves in late 2019 and early 2020 have point estimates at similar lower levels (??, ??), but include zero again.
-Overall, this suggests an effect that remains below an effect size of minimal relevance.
+However, estimates for waves 10 and 11 in late 2018 and mid-2019 - more than one and a half years after the editorial change - showcase effects statistically different from zero, and including the SESOI boundary.
+Note however that the effect is still tiny, with a point estimate of `r round(ests[["point"]][ests$wave == "10"], 3)` on the seven-point Likert scale, as well as an upper boundary just above the SESOI at `r round(ests[["upper"]][ests$wave == "10"], 3)`.
+The waves in late 2019 and early 2020 return to point estimates at lower levels (`r round(ests[["point"]][ests$wave == "12"], 3)`, `r round(ests[["point"]][ests$wave == "13"], 3)`), with confidence intervals including zero.
+Overall, no considerable change in attitudes can be observed at any time.
 
 ```{r migwaves, fig.cap="Effect of Change in Framing on Immigration Attitudes across Waves.
-Dashed (black) horizontal lines indicate conservative experimental effect (0.6, baseline expectation), dotted horizontal lines indicate minimal relevant effect (0.15).
-Dashed (red) vertical line indicates effect of Reichelt takeover, dotted (orange) line timing of change in coverage.
+Dashed horizontal lines indicate conservative experimental effect (0.6, baseline expectation), dotted horizontal lines indicate minimal relevant effect (0.15).
+Dashed vertical line indicates timing of Reichelt takeover.
 Full models visible in Appendix XX."}
@@
 
-### Effect on other alternative dependent variables
+### Effect on alternative dependent variables
 
-While immigration attitudes remain unaffected, it might well be that an increased exposure to crime framing affects other variables.
-For example, increased attention to crime within migration coverage might increase individual perceptions of the importance of migration, despite not changing attitudes, or raise concerns about the integration rather than the immigration of migrants.
+While opinions about immigration and their association with attitudes about crime remain unaffected, it might well be that an increased exposure to crime framing affects other variables.
+For example, increased attention to crime within migration coverage might increase individual perceptions of the importance of migration, or raise concerns about the integration rather than the immigration of migrants.
 Similarly, support for the radical-right *AfD* as owner of the migration issue could increase as a result of increased exposure to crime frames.
-All variable descriptions and models can be found in the appendix.
 
-Figure \@ref(fig:multidv) displays standardized effects of the change in newspaper framing on immigration attitudes (as reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see Appendix ??
-for precise variable descriptions).
-Dotted lines indicate a 0.2 standard deviation change, which has been defined as the standardized equivalence boundary in existing research [@Peyton2020, 599].
-All estimated effects are smaller in size than 0.05 standard deviations and associated 95%-confidence intervals contain zero.
+Figure \@ref(fig:multidv) displays standardized effects of the change in newspaper framing on immigration attitudes (for reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see Appendix XX for precise variable descriptions).
+To provide reference values again, I rescale the expected experimental effect of 0.6 and SESOI of 0.15 for immigration attitudes to standard deviations.
+This results in baselines of 0.34 and 0.08 standard deviations, which can be considered fairly small.
+All estimated effects are significantly smaller than the SESOI and all associated 95%-confidence intervals contain zero.
 This means we can reject the hypothesis of meaningful effect size, but cannot reject that the estimate is statistically different from zero.
@@
 DiDPlot(multi = T, scaled = T, 
-        theoretical_effect_size = 0.2) # 0.2 SD suggested by Peyton 2020, 599
+        theoretical_effect_size = 0.6, 
+        boundary_share = 0.25)
 
@@
 
-## Assumptions in the Translation of Experimental Estimates
+## Assumptions in the Generalization from Experimental Estimates
+
+Although mounting experimental evidence suggests large effects of framing in the experimental context, I find robust evidence that a substantial increase in the emphasis of crime in migration coverage did not affect immigration attitudes, their association with crime, or any related variables.
+As outlined above, there are several key assumptions in the generalization of framing effects from experimental contexts.
+First, those witnessing a changing news framing might select out of the treatment instead of changing their attitudes.
+Second, if citizens consume many sources of political news at the same time, they might not react to a change in a single news outlet.
+Third, issue attitudes might only be responsive to news framing during critical periods of politicization.
+The following section presents evidence about each of these assumptions.
 
@@
 
-As the migration framing in Bild becomes more conservative, this could also lead readers with more liberal migration attitudes to stop reading the newspaper, as they avoid information challenging their views.
-Figure \@ref(fig:selection) shows the share of initial readers that report reading Bild at later stages.
-The three different lines describe three different groups, based on their initial migration attitude.
-If readers reacted by selective exposure, one would expect that liberal readers' share would drop more significantly than conservative reader's share, as they actively select out of the newspaper.
-As one can see, that is not the case.
-Liberals' and conservatives' share of readers track each other closely, with those reporting liberal migration attitudes in the first wave even reporting to read Bild at *higher* shares than conservatives in later waves.
+As the migration framing in *Bild* becomes more conservative, this could also lead readers with more liberal migration attitudes to stop reading the newspaper, as they avoid information challenging their views.
+If readers selectively exposed themselves, I expect that the share of those holding liberal views about immigration reading *Bild* would drop more significantly than other reader's share, as they actively select out of the newspaper.
+That is not the case: Liberals' and conservatives' share of readers track each other closely, with those reporting liberal migration attitudes in the first wave even reporting to read Bild at *higher* shares than conservatives in later waves (see figure \@ref(fig:selectionPlot)).
 What is interesting is that those reporting neutral migration attitudes seem to be more inclined to leave the newspaper: Neutral readership declines to a level of 57%, around 5 percentage points below the share reported by liberals (62%) and 3pp below the level of conservatives (60%).
-Regressing individual choice to read *Bild* in later waves on initial reported migration attitudes within the subsample of initial *Bild* readers shows a `r round(m_sel$coefficients[["init_mig_groupsNeutral"]], 2)*-100`% lower chance to report Bild readership among initial neutral readers, compared to liberal readers ($p =$ `r round(summary(m_sel)$coefficients["init_mig_groupsNeutral", "Pr(>|t|)"], 3)`), whereas there is no significant or substantial difference for conservative readers.
-Surprisingly, *Bild* readers reporting centrist immigration attitudes select out of the newspaper at higher rates than both conservative or liberal readers, whereas there is no meaningful difference between the latter two.
+Regressing individual choice to read *Bild* in later waves on initial reported migration attitudes within the subsample of initial *Bild* readers shows a `r round(m_sel$coefficients[["init_mig_groupsNeutral"]], 2)*-100`% lower chance to report Bild readership among initial neutral readers, compared to liberal readers ($p =$ `r round(summary(m_sel)$coefficients["init_mig_groupsNeutral", "Pr(>|t|)"], 3)`, see table XX in appendix XX), whereas there is no significant or substantial difference for conservative readers.
+Surprisingly, *Bild* readers reporting centrist immigration attitudes select out of the newspaper at higher rates than both conservative or liberal readers, whereas there is no significant difference between the latter two.
+I also tested whether conservative readers were more likely to start reading the newspaper.
+As appendix XX shows, there is no evidence of this process either.
 
@@
 
+### Crowding Out
+
+```{r}
+
+ests <- CrowdOutEstimates(vis = F)
+
+tv_ests <- 
+  ests %>% 
+  filter(moderator == "tv_use", value == 0) %>% 
+  select(contains("CATE"))
+
+int_ests <- 
+  ests %>% 
+  filter(moderator == "in_use", value == 0) %>% 
+  select(contains("CATE"))
+
+print_ests <- 
+  ests %>% 
+  filter(moderator == "other_print", value == 0) %>% 
+  select(contains("CATE"))
+
+```
+
+If readers did not avoid persuasive content by selecting out of the outlet, how can the absence of a framing effect be explained?
+A second possibility is that readers are exposed to so many other sources of political information that the change in the framing of a single outlet does not severely affect their attitudes.
+If that were the case, consumers with a less diverse news diet would still receive a larger relative share of their information from a single outlet and hence respond to changes in the framing of this outlet.
+In other words, I expect a heterogeneous treatment effect: those with very limited news diets should experience an attitudinal change, whereas this effect should decrease with increasing exposure to other outlets.
+The panel data used in this study contains a number of variables that allow me to measure the diversity of a respondent's news diet.
+Respondents could indicate on how many days they consumed newspapers other than *Bild* in the preceding week.
+Summing these responses allows to generate a variable indicating how many newspapers other than *Bild* have been consumed, weighted by the intensity of their readership (see appendix XX for a detailed description).
+
+Results suggest a precise null effect of `r print_ests[["CATE"]] %>% round(3)` [`r print_ests[["CATE_lower"]] %>% round(3)`; `r print_ests[["CATE_upper"]] %>% round(3)`] within the group of those consuming no other newspaper, which is about `r round(print_ests[[1]]/0.6, 3)*100`% of the expected experimental baseline and much smaller than the SESOI of 0.15.
+The estimate is virtually identical for respondents indicating to consume other newspapers 1-3 times per week.
+Point estimates for other groups (consuming other newspapers 4-9, 10-15 or more than 15 days\footnote{A 'day' refers here to the additive days for every mentioned newspaper, that means if an individual reads newspaper A for seven days and another for six days, the total number of days will add up to thirteen.} in the preceding week) are well below the SESOI and statistically not different from zero, although estimation is less precise with higher values\footnote{See appendix XX for a visualization of all effects described in this section.}.
+
+I also exploit available data on consumption of political news from TV news providers (binary indicator) and on how many days respondents informed themselves about politics on the internet.
+Effects in the group of those indicating to have not consumed TV news (or their online counterparts) show a similarly precise null effect (`r tv_ests[["CATE"]] %>% round(3)` [`r tv_ests[["CATE_lower"]] %>% round(3)`; `r tv_ests[["CATE_upper"]] %>% round(3)`]).
+The estimate among those not informing themselves about politics on the internet is less precise, neither being significantly different from the SESOI nor zero, however the magnitude of the point estimate of `r int_ests[["CATE"]] %>% round(3)` is about half of the minimal effect size of interest.
+No clear pattern emerges with increasing internet exposure, in fact the only significant (but tiny) positive effect of `r ests[["CATE"]][ests$value == "1" & ests$moderator == "in_use"] %>% round(3)` ([`r ests[["CATE_lower"]][ests$value == "1" & ests$moderator == "in_use"] %>% round(3)`; `r ests[["CATE_upper"]][ests$value == "1" & ests$moderator == "in_use"] %>% round(3)`]) is observed in the group consuming political news on the internet on one out of seven days in the past week.
+
+Crowding out does not explain the absence of an effect of news framing on political attitudes.
+Those respondents consuming no other political information from newspapers, TV news, or online sources are no more reactive to a change in migration framing than those with a more diverse news diet.
+
 ### Attitude Crystallisation
 
-```{r MigChange, fig.cap="Change in individual immigration attitudes 2016-2018, compared to 2014-2016. Data taken from the GLES Longterm Panel (SOURCE)."}
+```{r MigChange, fig.cap="Change in individual immigration attitudes 2014-2018. Data taken from the GLES Longterm Panel (Roßteutscher et al. 2018)."}
 
-MigChangePlot()
+MigChangePlot(line_plot = T)
 
@@
 
-As readers did not react by selecting out of the newspaper, the question emerges *why* readers did not react to the change in coverage.
-A possible explanation is that individuals informed themselves about the issue and formed an attitude once the issue emerged, in this case in 2015 during the large migratory movements in Europe.
-If that were the case, opinions should change more from 2014 to 2016 compared to the 2016-2018 period.
-Figure \@ref(fig:MigChange) shows this statistic using GLES Longterm Panel data [SOURCE].
-The top panel shows the absolute change in migration attitudes from 2014-2016.
-That is, if a respondent held an attitude of 3 (leaning conservative) on the ten-point scale in 2014 and moved to 2 in 2016, their migration attitude would change by 1.
-Immigration attitudes in the GLES sample shifted on average by `r round(MigChangeTable["2014-2016",][["change_mean"]], 2)` from 2014 to 2016 (lower 95% confidence interval `r round(MigChangeTable["2014-2016",][["change_lower"]], 2)`, upper `r round(MigChangeTable["2014-2016",][["change_upper"]], 2)`), while they shifted significantly less in the period 206-2018 (`r round(MigChangeTable["2016-2018",][["change_mean"]], 2)`; [`r round(MigChangeTable["2016-2018",][["change_lower"]], 2)`, `r round(MigChangeTable["2016-2018",][["change_upper"]], 2)`]).
+Readers did not react by selecting out of the newspaper, nor was the change in framing crowded out by other sources of information.
+Another possible explanation is that individuals informed themselves about the issue and formed an attitude once the issue emerged, in this case in 2015 during the large migratory movements in Europe.
+If that were the case, opinions should change less in the 2015 period than the period before or after.
+Figure \@ref(fig:MigChange) shows this statistic using GLES Longterm Panel data [@GLES2018LangfristPanel].
+Unfortunately, I lack data for the period preceding 2014 and 2015, forcing me to make one-off comparisons rather than providing a longitudinal picture.
+The left panel compares the absolute change in individual immigration attitudes from 2014-2016 and 2016-2018, always measured in January.
+That is, if a respondent held an attitude of 3 (leaning conservative) on the ten-point scale in 2014 and moved to 2 in 2016, the absolute change would be equal to 1.
+Immigration attitudes in the GLES sample shifted on average by a substantial `r round(MigChangeTable["2014-2016",][["change_mean"]], 2)` from 2014 to 2016 (lower 95% confidence interval `r round(MigChangeTable["2014-2016",][["change_lower"]], 2)`, upper `r round(MigChangeTable["2014-2016",][["change_upper"]], 2)`), while they shifted significantly less in the period 2016-2018 (`r round(MigChangeTable["2016-2018",][["change_mean"]], 2)`; [`r round(MigChangeTable["2016-2018",][["change_lower"]], 2)` `r round(MigChangeTable["2016-2018",][["change_upper"]], 2)`]).
+The right-hand panel shows the change across one year, comparing 2016-2017 to 2017-2018 (to be comparable, the periods have to be of equal size).
+Across the course of 2016, when the debate surrounding the integration of refugees following their immigration in autumn 2015 and the events of new years eve 2016 in Cologne, individuals still show higher rates of attitudinal changes (`r round(MigChangeTable["2016-2017",][["change_mean"]], 2)`; [`r round(MigChangeTable["2016-2017",][["change_lower"]], 2)` `r round(MigChangeTable["2016-2017",][["change_upper"]], 2)`]) than 2017-2018 (`r round(MigChangeTable["2017-2018",][["change_mean"]], 2)`; [`r round(MigChangeTable["2017-2018",][["change_lower"]], 2)` `r round(MigChangeTable["2017-2018",][["change_upper"]], 2)`]).
 
-cite Lecheler et al, Druckman2012; Druckman2012Bias; X & Arceneaux here showing that individuals are resistant to persuasion on high-importance issues and that timing/pretreatment matters
+Although we lack evidence about the changes in migration attitudes pre-2015, these substantial and significant differences (technically differences-in-differences) suggest that, during the politicization of the issue in 2015, citizens updated their attitudes about the immigration issue, which, after the debate cooled down, crystallized into stable attitudinal positions, resistant to additional information.
 
-It becomes apparent that individual migration attitudes stabilised after 2015.
-This evidence is in line with the idea that migration attitudes were only responsive in 2015, when the newspaper did not follow other tabloids in their aggressively negative portrayal of refugees and their impact on society at large.
-When the newspaper changes its migration coverage one and a half years later, the critical window of opportunity seems to have closed, as migration attitudes had crystallized.
+This finding relates to a broader experimental literature on the persuasiveness of information under different degrees of societal salience and politicization.
+@Arceneaux2009 find that campaign messages can affect political attitudes, but only on issues which are not politicized.
+They conclude: "[p]eople’s attitudes on these types of issues are likely to be crystallized and firm, limiting the effect of persuasive communication" [@Arceneaux2009, 245].
+@Lecheler2009b study this question regarding framing effects, comparing high- and low-importance issues, and show that only the latter are responsive to framing.
+This finding has been reproduced in realistic settings involving opposing party cues [@Bechtel2015] and research about the impact of pre-treatment and exposure to conflicting frames point in similar directions [@Druckman2012; @Druckman2012Bias].
 
-### Crowding Out
+# Conclusion: The Power of News Framing in the Real World
 
-# Conclusion: Windows of Opportunity for News Framing Effects
+Does news framing affect public opinion?
+While the answer to this question has profound implications about the extent of elite influence in contemporary democracies, our current evidence comes almost exclusively from experiments.
+The present study addresses this gap by estimating the impact of an abrupt increase in the emphasis of crime in the migration coverage of Germany's largest tabloid, *Bild*.
 
-The presented results are robust evidence that, despite an over 70% increase of the emphasis of crime in migration content of Germany's largest newspaper, its readers' migration attitudes remained surprisingly unaffected.
-Effect estimates remain below minimal thresholds across time.
+The presented results are robust evidence that readers' migration attitudes remained surprisingly unaffected.
+Estimates of attitudinal change are indistinguishable from zero and remain below minimal effect sizes in a number of specifications and within different subgroups.
+Migration attitudes are also not increasingly associated with crime attitudes.
 Related dependent variables such as integration attitudes, reporting migration as the most important problem, and support for the radical-right AfD do not deviate from those of other readers.
-Migration attitudes are not increasingly associated with crime attitudes in this group, nor are liberal Bild readers more likely to stop reading the newspaper, nor conservative non-readers more likely to report reading it.
+In other words, readers did not react to a substantial increase in the emphasis of crime in migration coverage.
 
-These findings substantially question the external validity of experimental framing studies.
-While it is well-established that exposure to single frames can substantially affect political attitudes in survey- and laboratory experiments, this does not seem to easily translate into real world contexts.
+The paper assessed several potential violated assumptions in the generalization from experimental estimates of framing effects into the real world.
+The differences could not be explained by selective exposure: readers with liberal immigration attitudes did not opt out of the newspaper at higher rates than readers with more conservative migration attitudes.
+Similarly, the exposure to information from other outlets did not condition the effect on readers' immigration attitudes.
+Even readers who consumed no other newspaper, TV news, or online news are unresponsive to the change in coverage.
 
-Several potential explanations for this difference come to mind.
-The most likely is certainly selective exposure.
-Although no evidence for selective exposure on the outlet level could be found, readers might still select content *within* the outlet - that is, they skip articles contradicting their worldview or simply do not engage with the content on a cognitive level.
-Alternatively, the diversity of contemporary media environments might expose individuals with so many different frames that political attitudes are ultimately stabilized.
-The framing of individual outlets is crowded out by the many outlets which are consumed.
+I found some support for the explanation that attitudes have become unresponsive after 2015: following this period, the average change in individual immigration attitudes decreased substantively and significantly.
+This suggests that - if there was opportunity at all - the newspaper might have missed a critical window to influence readers' migration attitudes.
 
-While these findings substantially question evidence from experimental framing studies, they are generally good news for democracy: even when outlets try, they cannot simply manipulate their audience's political attitudes with a snap of their finger.
-Worries about the undermining of democracy through the takeover of partisan news outlets might be overstated, as consumers either seem to hold a critical distance to their news outlets or consume content from so many outlets that a single one has not much influence.
-Descriptive data about American news diets supports this interpretation [@Guess2021a].
+The main takeaway from the present study is that experimental estimates of framing effects do *not* simply generalize into the real world.
+While it is well-established that exposure to single frames can substantially affect political attitudes in survey- and laboratory experiments, real world environments are more complicated.
+My findings parallel evidence from panel surveys suggesting that attitudinal change of migration attitudes is rather rare [@Kustov2021].
+This incongruence of experimental and observational evidence suggests that the power of the news media to shape public opinion is more limited than previously thought.
+Even when elites try, they might not always be able to manipulate their audience's political attitudes.
+While work on media effects has shown that public opinion *can* be affected by changing news exposure [@DellaVigna2007; @Foos2022; @Grossman2022; @Levendusky2022], future work should investigate the relevant scope conditions conditioning this process and the precise treatments inducing opinion change in the real world.
 
-Despite the unique case and the extensive efforts to isolate the effect of the documented change inframing, this study suffers from several limitations regarding the generalizabilty of the case at hand.
-First, the immigration issue was already highly salient for one and a half years when Reichelt took over *Bild*.
-This means that attitudes have possibly crystallized as the result of personal reasoning, exposure to information, or cues from one's preferred party.
-Second, while tabloids are often seen as manipulators of public opinion [@Foos2022], they also contain less political content and might be taken less seriously when they write about politics.
-Readers from other outlets might react differently.
-Lastly, Bild readers differ from other readers in many ways, among others they are more conservative and less knowledgeable about politics (see Appendix ??).
-Readers of other outlets might react differently to increased exposure to crime frames.
+The present study has made a first step, outlining a simple framework for the measurement of emphasis frames in political communication, as well as their combination with the causal estimation of their impact.
+Subsequent studies should go further, seeking out quasi-experiments or conduct field experiments with different scope-conditions and assessing the impact of different forms of political communication.
+I want to emphasize the importance of a precise measurement of the independent variable here: unless we are able to compare treatments of different quality, the debate surrounding media effects will be stuck in a constant back-and-forth about the general size of broadly defined "media effects", rather than assessing which treatments affect public opinion under which conditions.
 
-[add: no randomisation of treatment!! plus adapt to new evidence regarding attitude stability]
+The experimental literature on framing, on the other hand, would profit from trying to reconcile the strong evidence of opinion stability in the real world with the strong framing effects observed under experimental conditions.
+After all, we conduct experiments in order to generalize to broader contexts.
+This paper has shown that the findings from a large body of framing research do not easily generalize, and offered a possible explanation.
+Further research into the determinants of attitude stability, as well as the generalizability of the assumptions underlying framing experiments will help to explain the disconnect between the observational and experimental evidence.
 
-This study offers several takeaways for future research.
-First, and most importantly, the study suggests caution in the generalization of experimental results to the real world.
-More observational research of framing effects would help in the mapping out of scope conditions for framing effects.
-The present study presented one approach how this can be done.
-On the other hand, experimental research could try to explore external validity issues further, assessing the existence of 'crowding out' effects, as well as conditions for and types of selective exposure.
+Despite the unique case and the extensive efforts to isolate the effect of the documented change in framing, this study suffers from several limitations.
+Tabloid readers differ from other readers in many ways, among others they are more opposed to immigration and less knowledgeable about politics (see Appendix XX).
+As the treatment in this study is not randomized, other groups might react differently to increased exposure to crime frames.
+Additionally, it is unclear how this finding translates into different contexts with more partisan media outlets, polarized electorates, or less educated citizens.
+However my main argument is precisely that we cannot simply assume that political communication has similar effects in different contexts.
+To identify which scope conditions are relevant, further work is necessary.
 

### 2022-09-19 paper/Manuscript_Framing.Rmd
Acknowledge Anselm

@@
 
-*I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
-Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim as well as participants of CompText 2022, EPSA 2022, ICA 2022, EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI,  and the Political Behaviour Section at Aarhus University.
+*I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Anselm Hager, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
+Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim, as well as participants of CompText 2022, EPSA 2022, ICA 2022, EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI,  and the Political Behaviour Section at Aarhus University.
 I also thank the two research assistants, Robin Groß and Nathalie Aerts, for annotating the news articles.

### 2022-09-19 paper/appendix.Rmd
Bulk changes
- add table with example headlines
- replace code w functions

--- 2022-08-31 paper/appendix.Rmd
@@
 
+```{=tex}
+\begin{table}
+\centering
+\begin{tabular}{|p{12cm}|}
+\hline
+Final new years eve report of Cologne police: male groups identified \\ \hline
+Police searching for Northern-african offender: asylum-raid in Dortmund! \\ \hline
+Search in refugee home - mega-raid addressing asylum fraud \\ \hline
+Two groups attacking each other - again bloody conflict in refugee shelter \\ \hline
+Cabin fever! Violence! Mass brawls! This is behind the increase in refugee clashes \\ \hline
+\end{tabular}
+\caption{Headlines of five migration articles most likely to concern crime, according to BERT crime classifier. Translation by author.}
+\label{tab:exampleArticles}
+\end{table}
+```
+
 ## Salience of Migration
@@
 ```
+## Crowding out
+
+```{r crowdout}
+
+CrowdOutEstimates(vis = T)
+
+```
 
@@
 
-### Reichelt
-
 ```{r LTPDiD, fig.height=2}
@@
 
-LTPDiD(return_table = T)
+modelsummary::modelsummary(LTPDiD(return_table = T), output = "markdown", stars = T)
 
@@
 
-(Association of Crime with migration attitude should be sigificantly higher in post-treatment-group)
-
 ```{r did_cond_crime}
 
-gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
-
-# define dv and conditioning variable
-gles_p_long[["dv"]] <- gles_p_long[["1130_clean"]]
-gles_p_long[["crime_att"]] <- gles_p_long[["2880h_clean"]]
-gles_p_long$Individual <- gles_p_long$lfdn
-
-inter <- 
-  feglm(dv ~ post * treat * crime_att, 
-        cluster = c("Individual"), 
-        data = gles_p_long %>% 
-          filter(!is.na(dv), !is.na(treat), !is.na(post), !is.na(crime_att)))
-
-inter_cond <- 
-  feglm(dv ~ post * treat * init_mig * crime_att , 
-        cluster = c("Individual"), 
-        data = gles_p_long %>% 
-          filter(!is.na(dv), !is.na(treat), !is.na(post), 
-                 !is.na(crime_att), !is.na(init_mig)))
-
-inter_fe_cond <- 
-  feglm(dv ~ post * treat * init_mig * crime_att | Individual, 
-        cluster = c("Individual"), 
-        data = gles_p_long %>% 
-          filter(!is.na(dv), !is.na(treat), !is.na(post), 
-                 !is.na(crime_att), !is.na(init_mig)))
-
-inter_fe <- 
-  feglm(dv ~ post * treat * crime_att | Individual, 
-        cluster = c("Individual"), 
-        data = gles_p_long %>% 
-          filter(!is.na(dv), !is.na(treat), !is.na(post), !is.na(crime_att)))
-
-modelsummary(
-  list(
-    inter, inter_fe, inter_cond, inter_fe_cond
-  ),
-  stars = T,
-  # coef_map =
-  #   c("postTRUE:treatTRUE" = "ATE",
-  #     "postTRUE:treatTRUE:crime_att" = "ATE X Crime Attitude",
-  #     "postTRUE:treatTRUE:init_mig:crime_att" = "ATE X Crime Attitude X \nInitial Migration Attitude"),
-  gof_omit = "^(?!R2.Pseudo|Num|Std|FE)", 
-  output = "markdown"
-)
-
-rm(gles_p_long, inter, inter_fe, inter_cond, inter_fe_cond)
+MigCrimeCorTable()
 

### 2022-09-19 paper/appendix.Rmd
Rewrite structure

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center')
+```{r setup, include=FALSE, cache=FALSE}
+knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', fig.pos = "!ht", out.extra = "")
 
@@
 
-# Frames in Communication
+# Variables & Decriptives
+
+## Dependent Variables
+
+### Overview
+
+Table, treated vs. untreated
+
+### Immigration Attitudes (1130 in GLES)
+
+#### Question Text
+
+*Translated:*
+
+Now it's about immigration opportunities for foreigners. Should immigration opportunities for foreigners be made easier or restricted?
+
+(1) Make it easier for foreigners to move here
+(2)
+(3)
+(4)
+(5)
+(6)
+(7) Restrict immigration of foreigners
+
+*Recoded to [-3, 3].*
+
+---
+
+*Original/DE:*
+
+Jetzt geht es um Zuzugsmöglichkeiten für Ausländer. Sollten die Zuzugsmöglichkeiten für Ausländer erleichtert oder eingeschränkt werden?
+
+(1) Zuzug von Ausländern erleichtern
+(2)
+(3)
+(4)
+(5)
+(6)
+(7) Zuzug von Ausländern einschränken
+
+#### Distribution
+
+```{r}
+
+GroupedDistPlot()
+
+```
+
+### Integration Attitudes (1210 in GLES)
+
+*Translated:*
+
+There are different opinions about how much foreigners in Germany should adapt.
+Some think that foreigners should fully assimilate to German culture.
+Others think that foreigners should be able to live according to their own culture if possible.
+
+(1) Foreigners should fully assimilate to German culture
+(2)
+(3)
+(4)
+(5)
+(6)
+(7) Foreigners should, if possible, be able to live according to their own culture
+
+*Recoded to [-3, 3].*
+
+---
+
+*Original/DE:*
+
+Es gibt unterschiedliche Auffassungen darüber, wie sehr sich Ausländer in Deutschland anpassen sollten.
+Manche denken, dass sich Ausländer vollständig an die deutsche Kultur anpassen sollten.
+Andere denken, Ausländer sollten auch hier möglichst nach der eigenen Kultur leben können.
+
+(1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen
+(2) 
+(3) 
+(4) 
+(5) 
+(6) 
+(7) Ausländer sollten möglichst nach eigener Kultur leben können
+
+### MIP: Immigration (840 in GLES)
+
+*Translated:*
+
+In your opinion, what is the most important political problem in Germany at the moment?
+Please name only one *single* problem.
+
+*0/1 indicator assessing mention of any migration related code (3411-3413 or 3750-3759; find coding scheme on GLES website).*
+
+---
+
+*Original/DE:*
+
+Was ist Ihrer Meinung nach gegenwärtig das wichtigste politische Problem in Deutschland? 
+Hinweistext: Nennen Sie bitte nur ein *einziges* Problem.
+
+### AfD Scalometer
+
+*Translated:*
+
+What do you think of the individual political parties in general? AfD (Alternative for Germany)
+
+(1) -5 don't think much of the party at all
+(2) -4
+(3) -3
+(4) -2
+(5) -1
+(6) 0
+(7) +1
+(8) +2
+(9) +3
+(10) +4
+(11) +5 think very highly of the party
+
+(-71) I don't know [labeled as "not known" in the data set]
+
+*Recoded to [-5, 5].*
+
+---
+
+*Original/DE:*
+
+Was halten Sie so ganz allgemein von den einzelnen politischen Parteien? AfD (Alternative für Deutschland)
+
+(1) -5 halte überhaupt nichts von der Partei 
+(2) -4 
+(3) -3 
+(4) -2 
+(5) -1 
+(6) 0 
+(7) +1 
+(8) +2 
+(9) +3 
+(10) +4 
+(11) +5 halte sehr viel von der Partei
+
+(-71) kenne ich nicht [im Datensatz gelabelt als „nicht bekannt“]
+
+### Attitude towards fighting crime (2880h)
+
+#### Question Text
+
+*Translated:*
+
+State powers to fight crime should be expanded, even if this means more surveillance of citizens.
+
+(1) totally disagree
+(2) rather disagree
+(3) partly/partly
+(4) tend to agree
+(5) I totally agree
+
+*Recoded to [-2, 2].*
+
+---
+
+*Original/DE:*
+
+Die staatlichen Befugnisse in der Kriminalitätsbekämpfung sollten ausgeweitet werden, auch wenn das zu einer stärkeren Überwachung der Bürger führt.
+
+(1) stimme überhaupt nicht zu
+(2) stimme eher nicht zu
+(3) teils/teils
+(4) stimme eher zu
+(5) stimme voll und ganz zu
+
+## Bild Readership
+
+## Media Exposure Variables
+
+### Other Newspapers
+
+### TV News
+
+### Internet News Consumption
+
+# Treatment
 
@@
 
-### Migration
+### Dictionaries
 
-### Crime
+### Handcoding
+
+### Preprocessing
+
+### Training
 
@@
 
-## Salience of Migration
-
-## Correcting for change in DPA-sourced content
+### Correcting for change in DPA-sourced content
 
@@
 
+### Raw Crime Estimates
+
 ```{r treatmentDPAcorr, fig.cap="Change in share of crime content in newspaper coverage, excluding DPA-sourced news content.
@@
 
-# Readership models
+### Migration Attention over Time
 
-## Inward selection
+## Salience of Migration
 
-```{r inselection, fig.cap="Coefficients of OLS regression of readership on migration attitude across waves.
-Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change."}
+# Results
 
-InSelection()
-
-```
-## Crowding out
-
-```{r crowdout}
-
-CrowdOutEstimates(vis = T)
-
-```
-
-# Difference-in-Differences Estimates
+## Treatment Groups
 
 Treated Group: Bild Readers in first (and only pre-treatment) wave. Control Group: Never-Readers of Bild. Post Date: $>=$ 01.02.2017
-
-## Descriptives
-
-Show Demographics for Treatment and Control Groups.
 
@@
 
-## DiD assumptions
-
-### Parallel Trends
+## Parallel Trends
 
@@
 ```
+
+## Robustness of Main Effect
+
+```{r did_imm_att, results='asis'}
+
+SingleDVModel('1130_clean')
+
+```
+
+## Multiple DV Table
+
+## Longterm-Panel Model
 
@@
 
-## Variable: Immigration Attitudes
-
-### Outcome: Reduce Immigration (1130)
-
-#### Question Text
-
-Jetzt geht es um Zuzugsmöglichkeiten für Ausländer. Sollten die Zuzugsmöglichkeiten für Ausländer erleichtert oder eingeschränkt werden?
-
-(1) Zuzug von Ausländern erleichtern
-(2)
-(3)
-(4)
-(5)
-(6)
-(7) Zuzug von Ausländern einschränken
-
-*Recoded to [-3, 3].*
-
-#### Treatment groups across time
-
-(add counterfactual if time)
-
-```{r did_imm_att_plot}
-
-fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
-  filter(!is.na(`1130_clean`), !is.na(treat)) %>% 
-  group_by(treat, wave) %>% 
-  summarise(
-    date_clean = min(date_clean, na.rm = T),
-    mig_mean = mean(`1130_clean`, na.rm = T),
-    mig_sd = sd(`1130_clean`, na.rm = T),
-    N = n()
-  ) %>% 
-  mutate(
-    mig_lower = mig_mean + qt(0.025, df = N-1) * (mig_sd/sqrt(N)),
-    mig_upper = mig_mean + qt(0.975, df = N-1) * (mig_sd/sqrt(N))
-  ) %>% 
-  ggplot(aes(x = date_clean, y = mig_mean,
-             ymin = mig_lower, ymax = mig_upper,
-             lty = !treat, col = !treat)) +
-  geom_line() +
-  geom_pointrange() +
-  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
-  theme_minimal() +
-  labs( x = "", y = "", col = "Readership", lty = "Readership") +
-  scale_color_manual(labels = c("Bild", "Never Bild"),
-                     values = MetBrewer::met.brewer("Archambault", 2)) +
-  scale_linetype_manual(labels = c("Bild", "Never Bild"),
-                     values = c(1,2))
-
-```
-
-#### Effect of Reichelt takeover
-
-```{r did_imm_att}
-
-SingleDVModel('1130_clean')
-
-```
-
-### Outcome: Integration Attitude (1210)
-
-#### Question Text
-
-Es gibt unterschiedliche Auffassungen darüber, wie sehr sich Ausländer in Deutschland anpassen sollten.
-Manche denken, dass sich Ausländer vollständig an die deutsche Kultur anpassen sollten.
-Andere denken, Ausländer sollten auch hier möglichst nach der eigenen Kultur leben können.
-
-(1) Ausländer sollten sich vollständig an die deutsche Kultur anpassen
-(2) 
-(3) 
-(4) 
-(5) 
-(6) 
-(7) Ausländer sollten möglichst nach eigener Kultur leben können
-
-*Recoded to [-3, 3].*
-
-#### Effect of Reichelt takover
-
-```{r did_int_att}
-
-SingleDVModel("1210_clean")
-
-```
-
-## Variable: Voting Behaviour
-
-### Outcome: Scalometer AfD (430i)
-
-#### QUESTION TEXT MISSING
-
-#### DiD Estimate
-
-```{r afd_scale}
-
-SingleDVModel("430i_clean")
-
-```
-
-## Variable: Issue Importance
-
-### Outcome: MIP Migration (840s)
-
-#### QUESTION TEXT MISSING
-
-#### DiD Estimate
-
-```{r did_mip_mig}
-
-SingleDVModel("mip_mig")
-
-```
-
-## Variable: Crime Considerations
-
-### Attitudes towards fighting crime (2880h)
-
-#### Question Text
-
-Die staatlichen Befugnisse in der Kriminalitätsbekämpfung sollten ausgeweitet werden, auch wenn das zu einer stärkeren Überwachung der Bürger führt.
-
-(1) stimme überhaupt nicht zu
-(2) stimme eher nicht zu
-(3) teils/teils
-(4) stimme eher zu
-(5) stimme voll und ganz zu
-
-#### Direct Effect
-
-```{r did_crime_att}
-
-SingleDVModel("2880h_clean")
-
-```
-
-#### Bootstrap of correlations
-
-```{r crime_mig_cor}
-
-cors <- 
-  fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
-  filter(!is.na(`1130_clean`), !is.na(`2880h_clean`), !is.na(treat)) %>% 
-  group_by(treat, post) %>% 
-  summarise(mig_crime_cor = cor(`1130_clean`, `2880h_clean`, use = "complete.obs")) %>% 
-  mutate(universe = "factual")
-
-cors <- 
-  cors %>% 
-  rbind(
-    data.frame(
-      treat = c(TRUE, TRUE),
-      post = c(FALSE, TRUE),
-      mig_crime_cor = c(cors[cors$treat & !cors$post, "mig_crime_cor"][[1]], 
-                        cors[cors$treat & !cors$post, "mig_crime_cor"][[1]] +  
-                          sqrt((cors[cors$treat & cors$post, "mig_crime_cor"][[1]] -
-                          cors[!cors$treat & cors$post, "mig_crime_cor"][[1]])^2)),
-      universe = "counterfactual"
-    ), 
-  ) %>% 
-  mutate(universe = factor(universe, levels = c("factual", "counterfactual")))
-
-cors %>% 
-  mutate(treat_universe = paste(treat, universe, sep = "_")) %>% 
-  ggplot(aes(x = post, y = mig_crime_cor, col = treat, lty = universe, group = treat_universe)) +
-  geom_point() +
-  geom_line() +
-  theme_minimal()
-
-```
-
-#### Interaction of DiD with Crime Attitude (following Nelson & Kinder 1996)
+## Association Model
 
@@
 ```
+
+## Readership models
+
+### Inward selection
+
+```{r inselection}
+
+InSelection()
+
+```
+
+Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change.
+
+### Crowding out
+
+```{r crowdout}
+
+CrowdOutEstimates(vis = T)
+
+```

### 2022-09-19 paper/appendix.Rmd
Add descriptives DVs

@@
 
-GroupedDistPlot()
+GroupedDistPlot("1130_clean",
+                header = "Distribution of Immigration Attitudes")
 
@@
 ### Integration Attitudes (1210 in GLES)
+
+#### Question Text
 
@@
 
+#### Distribution
+
+```{r}
+
+GroupedDistPlot("1210_clean",
+                header = "Distribution of Integration Attitudes")
+
+```
+
 ### MIP: Immigration (840 in GLES)
+
+#### Question Text
 
@@
 
-### AfD Scalometer
+#### Distribution
+
+```{r}
+
+GroupedDistPlot("mip_mig",
+                header = "Mention of Migration as Most Important Problem")
+
+```
+
+### AfD Scalometer (430i in GLES)
+
+#### Question Text
 
@@
 
+#### Distribution
+
+```{r}
+
+GroupedDistPlot("430i_clean",
+                header = "Distribution of Attitude Towards AfD")
+
+```
+
 ### Attitude towards fighting crime (2880h)
@@
 
-## Bild Readership
+#### Distribution
+
+```{r}
+
+GroupedDistPlot("2880h_clean",
+                header = "Distribution of Attitude towards Fighting Crime")
+
+```
 

### 2022-09-19 code/functions/visualisation.R

@@ -1391,13 +1391,13 @@ GroupedDistPlot <- function(variable = NULL,
   
   p_upper <- 
     gles_p_long %>% 
-    filter(treat) %>% 
+    filter(treat, !is.na(dv)) %>% 
     ggplot(aes(dv)) +
     geom_bar(aes(y = (..count..)/sum(..count..)),
              fill = MetBrewer::met.brewer("Archambault")[4]) +
     geom_vline(xintercept = 
                  gles_p_long %>% 
-                 filter(treat) %>% 
+                 filter(treat, !is.na(dv)) %>% 
                  summarise(dv = mean(dv, na.rm = T)) %>% 
                  .[1,]) +
     theme_minimal() +
@@ -1406,13 +1406,13 @@ GroupedDistPlot <- function(variable = NULL,
   
   p_lower <- 
     gles_p_long %>% 
-    filter(!treat) %>% 
+    filter(!treat, !is.na(dv)) %>% 
     ggplot(aes(dv)) +
     geom_bar(aes(y = (..count..)/sum(..count..)),
              fill = MetBrewer::met.brewer("Archambault")[1]) +
     geom_vline(xintercept = 
                  gles_p_long %>% 
-                 filter(!treat) %>% 
+                 filter(!treat, !is.na(dv)) %>% 
                  summarise(dv = mean(dv, na.rm = T)) %>% 
                  .[1,]) +
     theme_minimal() +

### 2022-09-21 paper/appendix.Rmd
Add descriptives, explain sampling

@@
 ```{r setup, include=FALSE, cache=FALSE}
-knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', fig.pos = "!ht", out.extra = "")
+knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, 
+                      fig.width=10, fig.align='center', fig.pos = "!ht", out.extra = "")
 
@@
 
-### Other Newspapers
+### Reading Bild (1661a in GLES)
 
-### TV News
+#### Question Text
 
-### Internet News Consumption
+*Translated:*
+
+On how many days in the past week did you read political reports in the following newspapers or on their websites? [Bild]
+
+(1) 0 Days
+(2) 1 Day
+(3) 2 Days
+(4) 3 Days
+(5) 4 Days
+(6) 5 Days
+(7) 6 Days
+(8) 7 Days
+
+*Recoded to [0,7]*
+
+---
+
+*Original/DE:*
+
+An wie vielen Tagen haben Sie in der vergangenen Woche politische Berichte in den folgenden Zeitungen oder auf deren Internetseiten gelesen? [Bild]
+
+(1) 0 Tage 
+(2) 1 Tag 
+(3) 2 Tage 
+(4) 3 Tage 
+(5) 4 Tage 
+(6) 5 Tage 
+(7) 6 Tage 
+(8) 7 Tage
+
+#### Distribution
+
+```{r}
+
+gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
+
+gles_p_long %>% 
+  ggplot(aes(`1661a_clean`)) +
+  geom_bar(aes(y = (..count..)/sum(..count..))) +
+  geom_vline(xintercept = 
+               gles_p_long %>% 
+               summarise(dv = mean(`1661a_clean`, na.rm = T)) %>% 
+               .[1,]) +
+  theme_minimal() +
+  xlab("") + ylab("Share") +
+  ggtitle("How many days last week did you read... Bild?")
+
+```
+
+### Treatment Indicator (Reading Bild recoded)
+
+The treatment definition is based on the "reading Bild" variable described above, but refined.
+The treatment is binarized, such that it is zero for those not reading Bild for any day last week and one for those indicating that they read it at least one day.
+Respondents indicating not to read Bild in the first wave, but reading it in later waves are dropped in order to maintain an untreated control group.
+
+```{r}
+
+gles_p_long %>%
+  filter(!is.na(treat)) %>% 
+  mutate(treat = ifelse(treat, "Treatment", "Control")) %>% 
+  ggplot(aes(treat, fill = treat)) +
+  geom_bar(aes(y = (..count..)/sum(..count..))) +
+  theme_minimal() +
+  xlab("") + ylab("Share") +
+  ggtitle("Respondents by treatment group")
+
+```
+
+### Other Newspapers (1661 in GLES)
+
+Items identical to the one asking respondents about their consumption of *Bild* news in the past week have been asked regarding the consumption of other newspapers, namely *Frankfurter Rundschau*, *Frankfurter Allgemeine Zeitung (FAZ)*, *Süddeutsche Zeitung (SZ)*, *die tageszeitung (taz)*, and *die Welt*.
+Additionally, respondents could indicate if they had consumed any other daily newspaper, and how many days last week.
+Based on these responses, I constructed an additive index of exposure to content from newspapers other than *Bild* in the first (pre-treatment) wave.
+This variable measures exposure in newspaper-days, meaning that for each newspaper, the number of days it was read in the week preceding the interview was summed.
+
+```{r}
+
+gles_p_long <- 
+    gles_p_long %>% 
+    filter(wave == "1") %>% 
+    mutate(
+      other_print = 
+        `1661b_clean` +
+        `1661c_clean` +
+        `1661d_clean` +
+        `1661e_clean` +
+        `1661f_clean` +
+        `1661g_clean`,
+      tv_use = ifelse(`1681f_clean`, "False", "True"),
+      in_use = `1600_clean`
+    ) %>% 
+    select(lfdn, in_use, tv_use, other_print) %>% 
+    right_join(gles_p_long, by = c("lfdn"))
+
+gles_p_long %>% 
+  filter(!is.na(other_print)) %>% 
+  ggplot(aes(other_print)) +
+  geom_bar(aes(y = (..count..)/sum(..count..))) +
+  geom_vline(xintercept = 
+               gles_p_long %>% 
+               summarise(dv = mean(other_print, na.rm = T)) %>% 
+               .[1,]) +
+  theme_minimal() +
+  xlab("") + ylab("Share") +
+  ggtitle("Additive index of exposure to newspapers other than Bild")
+
+```
+
+### TV News (1681f in GLES)
+
+#### Question Text
+
+*Translated:*
+
+I haven't watched TV news or read political reports on their websites.
+
+(1) mentioned
+(2) not mentioned
+
+*Recoded to (False = 1 (have not viewed); True = 2 (have viewed))*
+
+---
+
+*Original/DE:*
+
+Ich habe keine Fernsehnachrichten gesehen oder politische Berichte auf deren Internetseiten gelesen.
+
+(1) genannt 
+(2) nicht genannt
+
+#### Distribution
+
+```{r}
+
+gles_p_long %>% 
+  filter(!is.na(tv_use)) %>% 
+  ggplot(aes(tv_use)) +
+  geom_bar(aes(y = (..count..)/sum(..count..))) +
+  theme_minimal() +
+  xlab("") + ylab("Share") +
+  ggtitle("Exposure to TV news")
+
+```
+
+### Internet News Consumption (1600)
+
+#### Question Text
+
+*Translated:*
+
+An wie vielen Tagen haben Sie sich in der vergangenen Woche im Internet über Politik informiert?
+
+(1) 0 Days
+(2) 1 Days
+(3) 2 Days
+(4) 3 Days
+(5) 4 Days
+(6) 5 Days
+(7) 6 Days
+(8) 7 Days
+
+*Recoded to [0,7]*
+
+---
+
+*Original/DE:*
+
+An wie vielen Tagen haben Sie sich in der vergangenen Woche im Internet über Politik informiert?
+
+(1) 0 Tage 
+(2) 1 Tag 
+(3) 2 Tage 
+(4) 3 Tage 
+(5) 4 Tage 
+(6) 5 Tage 
+(7) 6 Tage 
+(8) 7 Tage
+
+#### Distribution
+
+```{r}
+
+gles_p_long %>% 
+  filter(!is.na(in_use)) %>% 
+  ggplot(aes(in_use)) +
+  geom_bar(aes(y = (..count..)/sum(..count..))) +
+  theme_minimal() +
+  xlab("") + ylab("Share") +
+  ggtitle("Exposure to TV news")
+
+```
 
@@
 
+```{r}
+
+seed_dict_mig <- 
+  c("asyl", "asylant", "asylanten", "asylantinnen", 
+     "asylbewerber", "asylbewerberin", "asylbewerberinnen", 
+     "auslander","auslanderinnen", 
+     "einwanderer", "einwandererin", "einwandererinnen", "einwandernde", "einwanderung",  
+     "fluchtling", "fluchtende", "fluchtlinge",
+     "migration", "immigration", 
+     "schutzsuchende", "schutzbedurftige",
+     "visa", "visum", 
+     "zuwanderung", "zuwanderer",  "zuwandernde",
+     "ausländer", "ausländerinnen", 
+     "flüchtling", "flüchtende", "flüchtlinge", 
+     "schutzbedürftige")
+
+ext_dict_mig <- 
+  read.csv("https://raw.githubusercontent.com/nicolaiberk/bild/main/code/content_analysis/bert/mig/dict/_dicts/german_glove.csv") %>% 
+  .[[2]]
+
+seed_dict_crime <- 
+  c("täter", "täterin", "polizei", "verbrechen", "überfall", "mord",
+    "attacke", "raub", "straftat", "ermittelt", "gericht", "prozess",
+    "staatsanwaltschaft", "staatsanwalt", "staatsanwältin", "gefährder", 
+    "haft", "festnahme", "betrug", "betrüger", "erstochen", "opfer", 
+    "anwalt", "drogen", "dealer", "getötet", "verletzung", "delikt",
+    "vergewaltigung")
+
+ext_dict_crime <- 
+  read.csv("https://raw.githubusercontent.com/nicolaiberk/bild/main/code/content_analysis/bert/crime/dict/_dicts/crime_glove.csv") %>% 
+  .[[2]]
+
+```
+
+In order to generate informative samples for the annotation, crime and migration content had to be oversampled from the raw data.
+To identify which articles likely contain relevant content, it is useful to construct dictionaries identifying the concept of interest and then use these dictionaries to assess what share of words in a given article is concerned with this content.
+In a first step, a seed dictionary is constructed to identify the concept of interest.
+To avoid missing any relevant words, word embeddings trained on large german language corpora can be used to identify terms with similar meaning.
+Using embeddings from a pre-trained model\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}, I select the 100 most similar term for each term in the seed dictionary.
+Those terms associated with at least four terms in the seed dictionary (i.e.
+being among the 100 most similar words for at least four words) are included in the extended dictionary.
+You can see the seed and extended dictionaries below.
+
+#### Migration
+
+**Raw Dictionary**:
+
+`r seed_dict_mig`
+
+**Dictionary after Extension using Embeddings**:
+
+`r ext_dict_mig`
+
+#### Crime
+
+**Raw Dictionary**:
+
+`r seed_dict_crime`
+
+**Dictionary after Extension using Embeddings**:
+
+`r ext_dict_crime`
+
+### Sampling
+
+Using the dictionaries, relevant words in each article are counted, and the share of relevant words out of all words is calculated.
+I then draw a stratified sample of migration articles, pulling 100 articles with no mention of migration-related terms, 100 with a moderate share of migration-related terms (25th to 75th percentile), and 100 with a high share of migration related words (above 75th percentile), for each newspaper in the sample.
+I repeat this process with the crime dictionary, however here I choose a higher cutoff (95th percentile) given the lower incidence of crime coverage compared to migration coverage in my sample.
+
 ### Handcoding
+
+Using this sampling procedure, I generate two samples of 1000 articles for annotation by research assistants.
+These samples oversample from articles likely to contain coverage of interest in order to provide a relatively balanced sample for training of the classifiers.
+Coders were sent a shiny app designed for annotations, together with the following instructions:
+
+> The task is to identify crime content in news articles.
+This should always be the main topic, i.e.
+articles discussing a specific incident/crime, court cases, or crime statistics.
+Please familiarise yourself with the examples and send me an email if you feel you need more specific instructions about the precise definition of what constitutes crime content or are unsure about a specific case (a brief definition is given in the app).
+
+Along with these instructions, coders were sent example articles which were considered to be especially difficult, annotated by me.
+
+Annotation took place in a shiny app (see screenshot below). This allowed faster annotation and minimized errors
+
+```{r, fig.cap="Screenshot of Annotation App"}
+
+knitr::include_graphics("vis/HandCodingScreenshot.png")
+
+```
 
@@
 
-```{r, bild_descriptives}
+```{r bild_descriptives, results = "asis"}
 
@@
 
-```{r LTPDiD_table}
+```{r LTPDiD_table, results='asis'}
 
-modelsummary::modelsummary(LTPDiD(return_table = T), output = "markdown", stars = T)
+modelsummary::modelsummary(LTPDiD(return_table = T), output = "latex", stars = T)
 
@@
 
-```{r did_cond_crime}
+```{r did_cond_crime, results='asis'}
 

### 2022-09-21 paper/appendix.Rmd
Add intercoder reliability

@@
 
-Annotation took place in a shiny app (see screenshot below). This allowed faster annotation and minimized errors
+Annotation took place in a shiny app (see screenshot below).
+Coders were shown the title and text of a random news article in the sample.
+Then they were asked whether the article refers to the topics of crime, law and order, or public safety.
+Coders could see a more specific definition by clicking a button.
+After selecting whether the article referred to crime or not, they could either click a button to get to the next article or safe their progress to return later.
+Coders could also return to the preceding article in case they had selected the wrong option.
+The app allowed for faster annotation and minimized errors in the coding (compared to noting the annotations in an excel sheet).
 
@@
 
-### Preprocessing
+```{r}
 
-### Training
+library(irr)
+
+crime_coding_nat <- 
+  fread(here("code/content_analysis/bert/crime/handcoding/crime/nathalie/handcoding_nathalie.csv"), encoding = "UTF-8")
+
+crime_coding_rob <- 
+  fread(here("code/content_analysis/bert/crime/handcoding/crime/robin/handcoding_robin.csv"), encoding = "UTF-8")
+
+## correlation of codings
+common_nat <- 
+  crime_coding_nat %>% 
+  filter(url %in% crime_coding_rob$url) %>% 
+  arrange(url)
+
+common_rob <- 
+  crime_coding_rob %>% 
+  filter(url %in% crime_coding_nat$url) %>% 
+  arrange(url)
+
+# correlation table - not so great
+table(common_nat$crime, common_rob$crime)
+
+# merge for agreement metrics
+common <- 
+  common_nat %>% 
+  mutate(
+    coder = "nathalie"
+  ) %>% 
+  select(url, coder, crime) %>% 
+  rbind(common_rob %>% 
+              mutate(
+                  coder = "robin"
+                ) %>% 
+              select(url, coder, crime)
+               )
+
+common <- 
+  common %>% 
+  mutate(
+    crime = ifelse(crime == "Ja", 1, 0)
+  ) %>% 
+  pivot_wider(id_cols = url, names_from = coder, values_from = crime) %>% 
+  select(-url)
+
+agreement <- agree(common)$value
+k_alpha <- kripp.alpha(t(common), method = "ordinal")$value
+
+```
+
+The migration annotation has been conducted by only one coder (1800 articles), while the crime articles have been annotated by two different coders separately (1000 each with 200 identical articles in each coder's sample).
+Annotation was very reliable with an agreement for `r agreement`% of annotated articles and a Krippendorff's alpha of `r round(k_alpha, 2)`.
+Conflicts were resolved by the author after inspection of the conflicting codings.
+
+### Classifier Training
 

### 2022-09-29 paper/Manuscript_Framing.Rmd
Update: Limits of Media Effects

@@
 ---
-title: "Framing Effects in the Wild"
+title: "Limits of Media Effects"
+subtitle: "How Politicisation Shapes the Pace of Attitudinal Change"
 author: "Nicolai Berk"
@@
     fig_caption: yes
-    # includes:
-    #   in_header: preamble.tex
+    number_sections: false
+    includes:
+      in_header: preamble.tex
 # subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
@@
 geometry: margin=1.5in
-abstract: "Does news framing affect public opinion?
-While a large body of experimental work suggests that individual attitudes can be easily altered by emphasizing different aspects of an issue, little is known about how these studies generalize to real world environments.
-I exploit a rare change in the migration framing of the major German tabloid *Bild* to bridge this gap.
-In a first step, I develop a framework for the measurement of emphasis frames in political communication using supervised machine learning.
-Using this framework, I show that the emphasis of crime in *Bild*'s migration coverage severely increased following an exogenously timed change of editor.
-Second, I employ a difference-in-differences design using panel data from over 16,000 individuals in thirteen waves to assess the precise impact of this shift on migration attitudes.
-Despite a major change in migration framing, a robust null effect on immigration attitudes and a number of related variables can be observed.
-These findings caution against the generalization of experimental framing studies to real-world environments and open a broader research agenda to study the precise impact of political communication beyond the experimental setting."
+abstract: "What are the limits of the news media's ability to shape public opinion?
+I argue that politicization conditions the responsiveness of individual attitudes to changes in the information environment.
+Exploiting a rare change in the migration framing of the biggest German tabloid *Bild*, I estimate the precise impact of this shift on immigration attitudes using large-scale panel data.
+Despite a 42 percent increase of the emphasis of crime in migration coverage, I find a robust null effect on immigration attitudes and a number of related variables.
+Further analyses suggest that media outlets' ability to manipulate public opinion in the short term seems to be limited to brief opportunity windows during the politicisation of a given issue."
+keywords: "Public Opinion, Media Effects, News Framing, Opinion Formation, Emphasis Framing, Conditions of Media Effects."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
@@
 
-```{r setup, include = F}
+```{r setup, include = F, cache=F}
 
-knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T, fig.pos = "!ht", out.extra = "")
+knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = F, fig.height=5, fig.width=8, fig.align='center', eval = T, fig.pos = "!ht", out.extra = "")
 
@@
 library(here)
+library(extrafont)
+
+loadfonts(device = "win")
 
@@
 
+\medskip
+
 WORD COUNT: `r wordcountaddin::word_count(here("paper/Manuscript_Framing.Rmd"))`
 
-\medskip
+\pagebreak
 
-*I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Anselm Hager, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
-Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim, as well as participants of CompText 2022, EPSA 2022, ICA 2022, EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI,  and the Political Behaviour Section at Aarhus University.
-I also thank the two research assistants, Robin Groß and Nathalie Aerts, for annotating the news articles.
-All remaining confusions are my own.*
+\doublespacing
 
-# Introduction: Does Framing Matter?
+# Introduction
 
-Does news framing affect public opinion?
-Despite the profound importance for the understanding of elite influence in modern democracies, we know little about the persuasive effects of news framing in real-world environments.
-A large body of experimental evidence suggests that the emphasis of specific considerations can substantially alter issue attitudes, However observational data suggests little variation in individual attitudes [@Kustov2021] and prior work has shown that the external validity of such experiments might be seriously complicated by the current salience and politicization of the issue of interest [@Arceneaux2009; @Bechtel2015; @Lecheler2009b], the availability of different frames [@Chong2007a; @Chong2013; @Druckman2003; @Druckman2012] and communicating actors [@Slothuus2010], as well as the seeking and avoidance of specific content [@Arceneaux2009; @Lau2021a; @Taber2006].
-Contemporary news environments provide consumers with especially diverse content and maximize their abilities to choose specific outlets and avoid others [@Bennett2008], thereby increasing the gap between the real-world environment and experimental studies.
-Additionally, the very nature of experiments is prone to over-estimate effects in the real world [@Barabas2010].
-This is the reason why, fifteen years ago, Donald Kinder called for framing research to extend its toolkit: "[E]xperimental results can always be questioned on their generalizability, and framing effects are no exception.
+A long tradition of research on public opinion suggests that political attitudes are a direct reflection of the information environment shaping the 'pictures in our heads' [@Lippmann1922].
+This view is supported by an extensive body of experimental evidence showing that framing is highly effective in the manipulation of issue attitudes.
+However, prior work has shown that the extrapolation of experimental results to real-world environments is often difficult [@Barabas2010], and that the effects of framing are highly dependent on the political context [@Chong2013].
+Media effects research has established that real-world changes in the media environment *can* affect issue attitudes [@Foos2022; @Grossman2022; @Djourelova2020], but not always [@Chiang2011a; @Spirig2020].
+We currently know little about the real-world conditions under which news framing affects public opinion.
+
+This study attempts to address this research gap presenting evidence from Germany, 2017-2020.
+This period - following a spike in asylum applications in 2015 - was marked by a focus on immigration in political discourse, as well as the first parliamentary entrance of a radical-right party since the post-war years.
+Many observers connected this sudden change in Germany's political landscape to a changing immigration discourse and the normalization of far-right ideas in public debate [@NYT2017BTW].
+Germany's largest tabloid newspaper, *Bild*, was seen as a strong driver of this development: it was claimed that by framing asylum seekers as criminals, the paper fueled anti-immigration sentiment and support for the radical-right *AfD* [@Niggemeyer2018Bild].
+
+In the remainder of this paper, I will argue that *Bild* missed a critical window of opportunity to shape public opinion.
+As readers' immigration attitudes had crystallized following the politicization of immigration in 2015, their immigration attitudes remained resistant to a change in the tabloid's migration framing.
+I support my argument with evidence presented in three steps: first, I show that *Bild* indeed increasingly emphasized crime-related news in its migration coverage, following an exogenously timed change of the editor-in-chief.
+I then exploit this natural experiment to provide evidence that this change did little to affect readers' immigration attitudes or related variables.
+In a last step, I trace different explanations for the absence of this effect, suggesting that the pace of attitudinal change severely decreased following the politicization of the issue in 2015.
+
+To assess whether the migration framing in *Bild* really changed, I develop an approach to measure framing in political texts.
+I apply this framework to a dataset of 2.5 million articles from the major German daily newspapers.
+Using supervised classifiers, I first select migration-related coverage, to then estimate the prevalence of crime content within this coverage.
+This analysis suggests that following the change of the editor-in-chief, the emphasis of crime in migration content increased by over 40 percent.
+
+To estimate the effect of this changing framing on immigration attitudes, I employ panel data from the German Longitudinal Election Study, fielded in the period of interest [@GLES2017Panel].
+I use a *difference-in-differences* (DiD) design to estimate the impact of the increased emphasis of crime in the coverage of migration and refugees.
+Results show that the changing framing did not result in more restrictive attitudes towards immigration, nor did it affect the association of crime with migration, views on integration, or the perceived importance of the immigration issue.
+
+Lastly, I explore different explanations why this shift in migration framing did not bring about attitudinal changes.
+First, I assess whether readers with initially liberal migration attitudes selected out of the newspaper in response to the changing portrayal of migrants.
+Reported readership of respondents with liberal migration attitudes remains at similar levels as that of readers with restrictive migration attitudes.
+Second, I investigate whether readers with many different sources of information are less reactive to the changing coverage and mask the effect.
+I find no effect heterogeneity across the reported consumption of newspaper, TV and online news, ruling out the possibility that readers with more diverse information hide an effect among exclusive *Bild* readers.
+Third, I test whether attitudes change after longer-term exposure.
+I find small effects after more than one and a half years, suggesting a very slow pace of attiudinal change.
+Lastly, I assess whether attitudes crystallized after the politicization of immigration in 2015.
+Using data from a long-term online panel [@GLES2018LangfristPanel], I show that the average individual change in immigration attitudes was substantially lower in the period 2016-2018 compared to the period 2014-2016.
+
+This evidence suggests a general model of opinion change that contributes to distinct literatures on media effects, attitude formation, and framing.
+Students of the effects of news content on political attitudes have started to explore the scope conditions of media effects [@Chiang2011a; @Spirig2020].
+This paper contributes to this literature by showing that changes in media coverage are ineffective when they are not addressing currently politicised issues.
+As a result, elite influence on public opinion is limited outside specific windows of opportunity.
+
+The analyses in this paper also speak to recent evidence of overall attitude stability [@Kustov2021]: citizens' immigration attitudes *are* rather stable most of the time.
+However, my findings suggest that the pace of attitudinal change increases dramatically when an issue becomes salient in public debate.
+The emerging picture is an ebb and flow of attitudinal stability and change, dependent on the salience of the issue at stake.
+
+Lastly, the evidence speaks to the study of framing effects.
+Fifteen years ago, Donald Kinder called for observational research on framing effects: "Experimental results can always be questioned on their generalizability, and framing effects are no exception.
 [...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157].
+By precisely identifying the nature of the change in news coverage, this study answered this call.
+The null effects found suggest that framing effects do not easily generalize from the experimental context.
 
-In this article, I provide the - to my knowledge - first observational estimate of framing effects by exploiting a rare shift in the framing of a highly politicized issue - migration - in Germany's largest tabloid newspaper, *Bild*.
-The case is ideal to assess the everyday influence of issue frames on public opinion, as one outlet severely changed its coverage, while other papers did not.
-Providing a novel framework for the measurement of emphasis frames using BERT models, I study migration framing in a corpus of 2.5 million newspaper articles.
-I show that the newspaper's migration coverage saw a strong increase in the use of crime frames after the editor in chief was abruptly replaced.
-The fielding of the German Longitudinal Election Study Panel [@GLES2017Panel] in the same period provides the rare opportunity to precisely assess the effect of framing on political attitudes using a *difference-in-differences (DiD) design*.
+The paper proceeds as follows: I provide a brief review of the expectancy-value model of attitude formation, which informs my hypotheses and content analysis, before discussing potential limits of framing effects in real-world environments.
+I then present the research design, content analysis, and a discussion of expected and minimal effect size of interest, before turning to the estimation of the effect of changing immigration framing on immigration attitudes and trace different explanations for the observed resistance.
+In the conclusion, I outline the implications of this model for framing, media, and public opinion research, as well as the limitations of this study.
 
-The results indicate that even this strong increase in the use of crime frames did not affect consumers' immigration attitudes.
-The estimated effect is statistically indistinguishable from zero and significantly smaller than even minimally relevant effect magnitudes.
-Related issue attitudes, voting behavior, and issue importance are similarly unaffected, as is the association of immigration attitudes with the frame provided.
-Tracing different assumptions underlying the generalization of experimental estimates of framing effects into the real world implies that this lack in responsiveness is not an outcome of readers abandonment of the newspaper, nor the "crowding out" of information through other sources, but rather the crystallization of immigration attitudes prior to the change in framing.
-
-Overall, these findings fundamentally challenge the external validity of a large body of framing effects research and suggest that the influence of media elites on public opinion is more limited than previously thought.
-Even a strong change in news framing did not affect political attitudes.
-Instead, it seems that the news media faces limited windows of opportunity to shape public opinion during the politicization of novel political issues.
-Additionally, the study contributes to a large body of media effects research in economics and political science by opening a research agenda to study the effects of political communication in the real world.
-
-# Framing Effects on Public Opinion {#framing-effects}
+# The Expectancy-Value Model {#framing-effects}
 
@@
 Work using the emphasis framing concept of framing mostly builds on the expectancy-value model developed by @Ajzen2000.
-This model suggests that an attitude on a given issue is a function of two things: the value of considerations relating to that issue and the strength of their association with the issue.
+This model suggests that an attitude on a given issue is a function of two factors: the value of considerations relating to that issue and the strength of their association with the issue.
 The evaluation of the issue is subdivided into a number of considerations, which will carry clear evaluations.
@@
 a potential surge in crime is considered a negative outcome.
-Based on the strength of the association $w_i$ of a given consideration with the issue, a given consideration's evaluation is more or less reflected in the overall attitude $y$, which is equal to the weighted sum of evaluations.
+Based on the strength of the association $w_i$ of a given consideration with the issue, that consideration's evaluation is more or less reflected in the overall attitude $y$, which is equal to the weighted sum of evaluations.
 For example, if a given individual associates immigration strongly with an increase in criminal activity and welfare fraud, but only very weakly with humanitarian considerations, cultural enrichment, liberty, or economic growth, they will form a rather negative attitude about the issue, as the former factor more prominently in their reasoning about migration.
@@
 
-# Limits of Framing Experiments {#framing-limits}
+# Limits of Framing Effects {#framing-limits}
 
@@
 Second, even if consumers receive the content, it is not clear how much an individual relies on this source when forming an opinion on the subject.
-Information from different sources might 'crowd out' the framing of a single outlet: by consuming content from many sources, individuals give less attention to a given source, thereby severely limiting the overall impact of that outlet's coverage.
+Information from different sources might 'crowd out' the framing of one specific outlet: by consuming content from many sources, individuals give less attention to a given source, thereby severely limiting the overall impact of that outlet's coverage.
 Experimental evidence suggests that, when an individual receives competing frames, these cancel each other out, although the precise impact is dependent on the relative timing of exposure, the quality of the frame, as well as individual characteristics [@Chong2007b; @Chong2010; @Chong2013].
+Additionally, individuals might update their perceptions slowly, as the increased emphasis of a consideration is not necessarily evident from the first few articles, instead arising from repeated exposure over time.
+Especially given that this study is concerned with a change in the *relative* emphasis of a consideration, it might take some time for citizens' perceptions to catch up to the changing issue representation.
 
 Third, cognitive engagement with frames might strongly differ in the real world compared to experimental contexts.
-Once individuals formed political attitudes, they might resist framing: Motivated reasoners presented with a plethora of news content about an issue will spend less time and cognitive energy on counter-attitudinal arguments than those supporting their viewpoint, lending more importance to considerations raised by amenable content [@Taber2006].
+Once individuals formed political attitudes, they might resist framing: Citizens presented with a plethora of news content about an issue will spend less time and cognitive energy on counter-attitudinal arguments than those supporting their viewpoint, lending more importance to considerations raised by amenable content [@Taber2006].
 Experimental evidence suggests similar dynamics specifically for framing: when individuals are free to choose content, initial frames dominate the opinion-formation process, while novel frames are rejected [@Druckman2012Bias] and even serve to strengthen pre-existing attitudes [@Bechtel2015].
-This also explains why citizens are less reactive to framing attempts on salient and politicized issues [@Lecheler2009b].
 
@@
 In order to test the external validity of framing effect studies, it is necessary to study observational data.
-
-# Existing Observational Studies of Framing Effects
-
-Despite repeated calls for the assessment of framing effects beyond experimental studies [@Busby2019; @Kinder2007; @Leeper2020], there is little research addressing this concern.
-While a large body of observational media effects research exists, it has not paid specific interest to framing, instead assessing the impact of changing news exposure on issue attitudes and voting behavior more broadly.
-Most of these studies are concerned with exposure to a different outlet [@Bail2018; @Broockman2022; @Foos2022; @Grossman2022; @Guess2021].
-This is problematic, as citizens are often aware of outlets' political slant and engage with the coverage differently [@Baum2008a; see also @Spirig2020 for a discussion of this issue].
-Those studies focusing on within-outlet changes in coverage do not identify changing framing directly and assess effects on a broad set of dependent variables, rather than specific issue attitudes [@Levendusky2022; @Spirig2020].
-
-The precious small body of existing observational research specifically about framing is often riddled with endogeneity issues.
-For example, @Jerit2008 investigates the effects of news framing on public opinion.
-She finds that framing is less effective in affecting public opinion compared to engagement with opposing considerations, a finding that suggests that framing is rather ineffective.
-Others show with similar designs that only specific frames seem to drive issue importance [@Mclaren2018], but do not assess effects on attitudes.
-However, these studies restrict themselves to the assessment of correlational evidence.
-This is especially problematic regarding framing effects, as news content can affect consumers' inclination to consume news (see preceding section), and political actors might react to public opinion.
-As both variables affect each other at the same time, it is impossible to assess which direction causality runs.
-
-To my knowledge, there are only two observational studies assessing the causal effect of exposure to specific content on political attitudes.
-@Slothuus2010b takes advantage of a sudden shift in a political parties' framing of retirement benefits, and shows that this changed framing has substantial impact on party supporters' attitudes about the issue.
-However, given that a positional change coincided with the changing framing of the issue and parties' special role in citizens' information process, one cannot distinguish the effect of partisan cue-taking from the persuasive effect of the frame itself.
-Additionally, it is unclear how these findings translate from parties' communication to news framing effects.
-
-The only study which - to my knowledge - assesses the precise impact of changing news content on political attitudes comes from @Djourelova2020.
-She exploits a ban of the term "illegal migrant" in the *Associated Press* and shows that this language has modest effects on migration attitudes.
-While the study itself reveals impressively how language can shape political attitudes, it constitutes a highly specific case and a rather minor change in the framing of migration.
-To gain a deeper understanding of how specifically *framing* affects immigration attitudes, it is necessary to assess broader changes in the representation of the immigration issue.
-
-Overall, it becomes obvious that we lacks an understanding of how news framing affects political attitudes in the real world.
-While experimental studies find strong effects, several assumptions have to be made to translate them beyond the lab or survey context.
-Observational evidence on media effects is only informative about broadly defined 'media effects' in specific cases, mostly without a more detailed focus on which content affects political attitudes.
-In order to identify the precise effects of changing news content, it is necessary to assess within-outlet changes in news coverage and their effect on specific issue attitudes using a design able to identify both the precise nature of the changes in content and their causal effects on attitudes.
-The following section therefore presents a research design building on a rare change in the migration framing in Germany's largest tabloid, *Bild*.
-It then develops a framework to measure emphasis framing in political communication, and presents a panel dataset tracking migration attitudes in the time-frame of interest, as well as a *difference-in-difference* design to estimate the causal effect of the changing framing.
-The final section discusses the expected effect size from experimental studies, in order to provide a baseline for comparison.
 
@@
 The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win representation in the national parliament.
-Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* initially maintained a somewhat balanced coverage of refugees, which - although still portraying migrants more negatively than other outlets [@Maurer2019] - even started a campaign called "#RefugeesWelcome" to gather support for the newly arriving\footnote{See \url{https://web.archive.org/web/20160114154402/https://www.bild.de/news/topics/fluechtlingshilfe/wir-helfen-buehne-42385428.bild.html}.}.
+Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* initially maintained a somewhat balanced coverage of refugees, which – although still portraying migrants more negatively than other outlets [@Maurer2019] – even started a campaign called "#RefugeesWelcome" to gather support for the newly arriving\footnote{See \url{https://web.archive.org/web/20160114154402/https://www.bild.de/news/topics/fluechtlingshilfe/wir-helfen-buehne-42385428.bild.html}.}.
 This was often connected to chief editor Kai Diekmann, who hosted a refugee family in his home [@BR2015Diekmann].
 
-About one and a half years later, in December 2016, Axel Springer, the company owning *Bild*, announced that Diekmann will leave the company.
-Less than a week after the announcement, it became public that prosecutors investigate Diekmann for sexual harassment.
+About one and a half years later, in December 2016, Axel Springer, the company owning *Bild*, announced that Diekmann would leave the company.
+Less than a week after the announcement, it became public that prosecutors investigated Diekmann for sexual harassment.
 While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time support this interpretation of events.} [@Spiegel2017Diekmann].
@@
 The change of editor itself was not discussed in the media, which means any opinion changes among readers can only be the result of the changing content [see @Spirig2020].
-Additionally, the timing of the editorial change is potentially exogenous, given the pressure from allegations against Diekmann.
+Additionally, the timing of the editorial change is likely exogenous, given the pressure from allegations against Diekmann.
 In summary, *this case is as close as possible to a field experiment in which a specific consideration of migration coverage is amplified in the coverage of one newspaper, but not others*.
 
-In the following sections, I will outline a framework for the measurement of emphasis frames in communication and showcase the increasing emphasis of crime in *Bild*'s migration coverage (treatment).
-Subsequent sections will describe the panel data and variables to measure frames in thought (namely migration attitudes and their correlation with attitudes about crime) and define the difference-in-difference estimator.
+In the following sections, I will outline a framework for the measurement of emphasis frames in communication and showcase the increasing emphasis of crime in *Bild*'s migration coverage.
+Subsequent sections will describe the panel data and variables to measure frames in thought (namely migration attitudes and their association with attitudes about crime) and define the difference-in-difference estimator.
 I will close with a discussion of the expected experimental effect size and the minimal effect size of interest to provide baselines for comparison of the estimator.
@@
 To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets *Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt*, as well as *Bild* for the period 2013-2019.
-These outlets reach a substantial share of the German public, with *Bild* distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 1.1 in the appendix for more information\footnote{Online appendix available at \url{https://github.com/nicolaiberk/bild/raw/main/paper/appendix.pdf}.}).
+These outlets reach a substantial share of the German public, with *Bild* distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 2.1 in the appendix for more information\footnote{Online appendix available at \url{https://github.com/nicolaiberk/bild/raw/main/paper/appendix.pdf}.}).
 Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration.
 Second, I identify content about crime *within* migration coverage by training and applying another supervised classifier.
-This approach closely resembles the value-expectancy model outlined in section \@ref(framing-effects), as I first identify coverage about the *issue*, before identifying the consideration emphasized in the discussion of this issue.
+This approach closely resembles the value-expectancy model outlined [above](#framing-effects), as I first identify coverage about the *issue*, before identifying the consideration emphasized in the discussion of this issue.
 
@@
 As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3 percent of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}.
-Instead, I take a more informed approach by oversampling articles which are likely about migration: after constructing a seed dictionary of migration-related terms, I apply dictionary extension using German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles\footnote{The dictionary can be found in appendix XX.}.
+Instead, I take a more informed approach by oversampling articles which are likely about migration: after constructing a seed dictionary of migration-related terms, I apply dictionary extension using German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles\footnote{The dictionary can be found in appendix 2.2.1.}.
 Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with the highest share of migration terms and 100 from the remaining articles with relative frequencies of migration-related terms in between these two groups) for each newspaper for a total of 1,800 papers.
-Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{The coder was instructed to annotate articles referring to migration or integration, which includes discussions of refugee numbers, immigrants' and naturalization rights, and general reports of migration.}.
+Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{The coder was instructed to annotate articles referring to migration or integration, which includes discussions of refugee numbers, immigrants' and naturalization rights, and general reports of migration.
+More information can be found in Appendix 2.2.3.}.
 
-Using this sample, a BERT transformer model\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a random subset of 1,400 annotated articles (training set) with a validation set of 200 articles.
+Using this sample, a BERT transformer model\footnote{\url{https://huggingface.co/bert-base-german-cased}}, pre-trained on a large German corpus of Wikipedia articles, News, and legal documents, is fine-tuned on a random subset of 1,400 annotated articles (training set) with a validation set of 200 articles.
 After fine-tuning, the model correctly classifies 95.5% of a test set of 200 articles (F1: 0.94, recall: 0.93, precision: 0.95).
 This classifier is then used to annotate all 2.5 million newspaper articles.
-For the period from 2013 to 2019, around 90,000 articles (3.6%) are identified to treat the issue of migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 1.2.}.
+For the period from 2013 to 2019, around 90,000 articles (3.6%) are identified to treat the issue of migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 2.2.}.
 
 To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest.
-Using a training set of 1400 articles (sleected using the identlical process as above), a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%.
+Using a training set of 1400 articles (selected using the identical process as above), a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%.
 I then apply this classifier to the approximately 90,000 articles about migration identified by the first classifier.
-About 7% of all migration coverage consists of articles about some form of crime.
-Exemplifying the nature of the treatment, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood.
-All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about the sexual assaults surrounding new years eve in cologne.
+About 7% of all migration coverage consists of articles about some form of crime\footnote{See appendix 2.2.7 for more information.}.
 
-The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, black line), once for Bild and once for all other newspapers (dashed, gray line).
+The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news, once for *Bild* (solid, black line) and once for all other newspapers (dashed, gray line).
 As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased directly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change\footnote{Note that this data consists exclusively of original Bild content.
 Treatment estimates including third-party authored content are similar in size.
-For a more extensive discussion see appendix XX.}.
+For a more extensive discussion see appendix 2.2.5.}.
 The trends run parallel to each other preceding the treatment.
@@
 The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in *Bild*.
-One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, increasing the share of articles devoted to crime by around 5 percentage points, while other newspapers maintained their levels of attention.
+One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, increasing the share of articles devoted to crime by around 5 percentage points (over 40 percent percent of the pre-treatment average), while other newspapers maintained their levels of attention.
 
@@
 The 2017 Election Panel by the German Longitudinal election study contains this data.
-It consists of a total of 15 waves from 2016-2020, with 10,000 - 20,000 respondents per wave [@GLES2017Panel].
+It consists of a total of 15 waves from 2016-2020, with 10,000 – 20,000 respondents per wave [@GLES2017Panel].
 Thirteen of these waves contain questions on immigration attitudes, asking respondents whether immigration of foreigners should be liberalized or  restricted.
 Responses were recorded on a seven-point Likert scale.
-This variable was centered on zero ($-3$ - liberalize, $3$ - restrict; the precise wording in the survey can be found in appendix 3.2).
+This variable was centered on zero ($-3$ – liberalize, $3$ – restrict; the precise wording in the survey can be found in appendix 1.1.2).
 
-To measure exposure to *Bild* news I use a question on newspaper consumption, which was asked in seven waves.
-The question provides respondents with a list of the six major daily newspapers plus an option "another daily newspaper", and asks whether they had consumed the paper in print or read articles from their website, and if so, how many days in the past week.
-Readers are defined as *treated* if they indicate to read *Bild* in the pre-treatment wave and as *untreated* if they indicate not to read the tabloid in the pre-treatment wave, nor any subsequent wave\footnote{See appendix XX for descriptives of all mentioned variables.}.
+To measure exposure to *Bild* news, I use a question on newspaper consumption.
+The question provides respondents with a list of the six major daily newspapers plus an option "another daily newspaper" and asks whether they had consumed the paper in print or read articles from their website, and if so, how many days in the past week.
+Readers are defined as *treated* if they indicate to read *Bild* in the pre-treatment wave and as *untreated* if they indicate not to read the tabloid in the pre-treatment wave, nor any subsequent wave\footnote{See appendix 1 for descriptives of all mentioned variables.}.
 
@@
 
-<!-- missing: variables relating to generalisation -->
-
 ## Estimation
 
-To assess the precise impact of increased attention to crime in migration coverage, I will present evidence from a *difference-in-differences* (DiD) estimator to show the effect of the editorial change - and the related content shift - on migration attitudes:
+To assess the precise impact of increased attention to crime in migration coverage, I will present evidence from a *difference-in-differences* (DiD) estimator to show the effect of the editorial change – and the related content shift – on migration attitudes:
 
@@
 Note that the pre-treatment differences of treatment and control group are corrected for in the individual fixed effects, as the groups are constant over time (readership is only assessed pre-treatment).
-As the panel data contains only one pre-treatment wave, the parallel trends assumption cannot be tested with this data directly, but assessing the trends using the GLES Longterm Panel [@GLES2018LangfristPanel] shows that *Bild* and non-*Bild* readers' immigration attitudes move in parallel preceding the treatment (see appendix XX).
+As the panel data contains only one pre-treatment wave, the parallel trends assumption cannot be tested with this data directly, but assessing the trends using the GLES Longterm Panel [@GLES2018LangfristPanel] shows that *Bild* and non-*Bild* readers' immigration attitudes move in parallel preceding the treatment (see appendix 3.1).
 
@@
 
-To provide a baseline expectation regarding the effect size in experimental work, it is useful to consider the expected effect size at this point.
+To provide a baseline expectation regarding the effect size in experimental work, it is useful to consider an expected effect size at this point.
 Despite the abundance of framing effects studies, there is no common standard to assess the magnitude of framing effects.
@@
 Given these considerations, I expect an effect of around 10% of the scale, or 0.6 on the seven-point scale\footnote{As the scale runs from one to seven, it spans six points wide.}, which represents a conservative estimate compared to reported experimental effects.
+At this point, it should be mentioned that it is rather difficult to compare these experimental effects with a real world treatment.
+Experiments expose participants to one of two potential considerations, whereas in the real world, newspapers can only increase the relative prevalence of a given consideration.
 
-As suggested by @Lakens2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI) in order to detect possible null effects.
+As suggested by @Lakens2017, I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI) in order to provide a baseline for a meaningful effect size.
 I define the SESOI at a 2.5% change, or 0.15 on the seven-point scale, which represents a fraction of the conservative experimental estimate and sets a fairly low bar given the strong treatment.
@@
 Then, I will assess the impact across time and on related variables to inspect the robustness of the estimation.
-The last section will trace the key assumptions in the generalization of experimental estimates discussed in section \@ref(framing-limits).
+The last section will trace the key assumptions in the generalization of experimental estimates discussed in the [section on the limits of framing effects](#framing-limits).
 
@@
 
-According to the expectancy-value model (see section \@ref(framing-effects)), the most direct implication of increased exposure to crime frames in migration coverage should be a more restrictive attitude concerning immigration.
-Figure \@ref(fig:singleplot) visualizes the effect of the change in framing on immigration attitudes, with higher values indicating that *Bild* readers change their attitudes in a more restrictive direction, compared to the control group.
+According to the expectancy-value model, the most direct implication of increased exposure to crime frames in migration coverage should be a more restrictive attitude concerning immigration.
+The upper panel of figure \@ref(fig:singleplot) plots the average immigration attitude among *Bild*-readers compared to those never reading *Bild*.
+The dashed vertical line indicates the timing of the change of the editor-in-chief at *Bild*.
+Higher values indicate more restrictive migration attitudes.
+We can see that *Bild* readers generally hold more restrictive immigration attitudes with a difference of about 0.4 on the seven-point scale.
+Both trends move largely parallel and seem to react to shocks similarly.
+
+The lower panel of figure \@ref(fig:singleplot) visualizes the average treatment effect, based on the model described in the [estimation section](#estimation).
 Dashed vertical lines indicate the expected effect from the experimental literature.
 The dotted lines indicate the equivalence boundaries/SESOI.
-Surprisingly, the model suggests a clear null effect.
+The model suggests a clear null effect.
 This effect is not significantly different from zero, but significantly smaller than the above-defined SESOI of 0.15 on the seven-point Likert scale.
@@
 This represents only a fraction (`r round(ATT/0.6, 3)*100`%) of the already conservative experimental estimate of 0.6.
-The finding is robust to different model specifications, as well as using data from the GLES Longterm Panel (see appendix XX).
+The finding is robust to different model specifications, as well as using data from the GLES Longterm Panel (see appendix 3.2 and 3.4).
 
-```{r singleplot, fig.cap="Effect of change in framing on migration attitudes; difference-in-differences estimate.
-Dashed vertical lines indicate conservative experimental effect (0.6, baseline expectation), dotted vertical lines indicate minimal relevant effect (0.15).
-Full model visible in Appendix XX.", fig.height=2}
+```{r singleplot, fig.cap="Top Panel: Development of Migration Attitudes across Time, by Bild-Readership. Bottom Panel: Average Treatment Effect."}
 
-DiDPlot(multi = F, scaled = "raw", 
-        theoretical_effect_size = 0.6, boundary_share = 0.25)
+DescPlot(legend_position = "bottom") + 
+  DiDPlot(size = 0.5) + 
+  plot_layout(design = 
+              "
+              AAAAAA
+              AAAAAA
+              BBBBBB
+              ")
 
@@
 Figure \@ref(fig:corplot) shows the bootstrapped correlations of crime- and migration attitudes in treatment (*Bild*-readers in pre-wave) and control group (never *Bild*-readers), for each wave.
-The lines indicate the mean estimate, while the whiskers indicate the upper and lower 95%-confidence interval, as defined by the 2.5% and 97.5% percentiles of the distribution of bootstrapped estimates.
+The lines indicate the mean estimate, while the whiskers indicate the upper and lower 95%-confidence interval, as defined by the 2.5 and 97.5 percentiles of the distribution of bootstrapped estimates.
 The dotted line indicates the counterfactual development, assuming that *Bild*-readers behaved similar to the general population not reading *Bild* in the absence of a change in migration framing.
@@
 Nevertheless, the treatment group actually saw a *smaller* increase in the correlation of crime and migration attitudes in the first post-treatment wave than the control group.
-The difference-in-differences in correlations of `r round(mean(deltas_3), 3)` is substantively rather small (`r abs(mean(deltas_3)/mean(bs[["mig_crime_cor"]][!bs$treat & bs$wave == 1])) %>% round(3)` of the average pre-treatment control group correlation) and not significantly different from zero with a bootstrapped 95% confidence interval of [`r quantile(deltas_3, 0.025)[[1]] %>% round(3)`, `r quantile(deltas_3, 0.975)[[1]] %>% round(3)`].
+The difference-in-differences in correlations of `r round(mean(deltas_3), 3)` is substantively rather small (`r (abs(mean(deltas_3)/mean(bs[["mig_crime_cor"]][!bs$treat & bs$wave == 1])) %>% round(3))*100` percent of the average pre-treatment control group correlation) and not significantly different from zero with a bootstrapped 95% confidence interval of [`r quantile(deltas_3, 0.025)[[1]] %>% round(3)`, `r quantile(deltas_3, 0.975)[[1]] %>% round(3)`].
 In the last wave, the association decreases less than in the control group but the difference-in-differences does not reach conventional levels of significance compared to the pre-treatment wave (`r round(mean(deltas_13), 3)`, [`r quantile(deltas_13, 0.025)[[1]] %>% round(3)`, `r quantile(deltas_13, 0.975)[[1]] %>% round(3)`]).
+The association of crime and immigration attitudes did not increase among *Bild* readers, relative to the control group.
 
@@
 Following [@Nelson1996], I also regress immigration attitudes on attitudes towards crime and investigate whether this association changes as a result of the change in coverage.
-Similar to the differences between the groups, I find a weaker association among readers of the tabloid, but no significant or substantively large difference post-treatment or when interacted with the DiD-term (see table XX in appendix XX).
+Similar to the differences between the groups, I find a weaker association among readers of the tabloid, but no significant or substantively large difference post-treatment or when interacted with the DiD-term (see table in appendix 3.5).
 Respondents do not associate crime more strongly with migration following the change in migration coverage in *Bild*.
 
-<!-- description of findings needs to be simplified in entire section  -->
-
-## Robustness
-
-### Effect across time
-
-```{r didWaveEsts}
-
-ests <- DiDByWavePlot(return_ests = T)
-
-```
-
-If readers only perceive the change in content across longer time periods, the effect should slowly unfold over time.
-Then, initial absence of change might bias the estimates downward and thereby mask an effect.
-To assess whether an effect develops over time, figure \@ref(fig:migwaves) assesses the effect within split-samples for each post-wave compared to the pre-treatment wave.
-This allows the assessment of heterogeneous treatment effects across time.
-The black dots with associated confidence intervals indicate the estimated effect for each wave.
-The horizontal dashed line indicates the expected effect based on experimental evidence (0.6), whereas the dotted horizontal line indicates the SESOI of 0.15.
-The vertical (red) dashed line indicates the timing of the editorial change.
-Over the course of the entire year 2017, the effect is clearly smaller than the SESOI, and includes zero.
-However, estimates for waves 10 and 11 in late 2018 and mid-2019 - more than one and a half years after the editorial change - showcase effects statistically different from zero, and including the SESOI boundary.
-Note however that the effect is still tiny, with a point estimate of `r round(ests[["point"]][ests$wave == "10"], 3)` on the seven-point Likert scale, as well as an upper boundary just above the SESOI at `r round(ests[["upper"]][ests$wave == "10"], 3)`.
-The waves in late 2019 and early 2020 return to point estimates at lower levels (`r round(ests[["point"]][ests$wave == "12"], 3)`, `r round(ests[["point"]][ests$wave == "13"], 3)`), with confidence intervals including zero.
-Overall, no considerable change in attitudes can be observed at any time.
-
-```{r migwaves, fig.cap="Effect of Change in Framing on Immigration Attitudes across Waves.
-Dashed horizontal lines indicate conservative experimental effect (0.6, baseline expectation), dotted horizontal lines indicate minimal relevant effect (0.15).
-Dashed vertical line indicates timing of Reichelt takeover.
-Full models visible in Appendix XX."}
-
-# add 0.9 confidence bar
-
-DiDByWavePlot(theoretical_effect_size = 0.6, boundary_share = 0.25)
-
-```
-
-### Effect on alternative dependent variables
+## Effect on alternative dependent variables
 
@@
 For example, increased attention to crime within migration coverage might increase individual perceptions of the importance of migration, or raise concerns about the integration rather than the immigration of migrants.
-Similarly, support for the radical-right *AfD* as owner of the migration issue could increase as a result of increased exposure to crime frames.
+Similarly, support for the radical-right *AfD* as owner of the migration issue could increase as a result of increased exposure to this type of migration coverage.
 
-Figure \@ref(fig:multidv) displays standardized effects of the change in newspaper framing on immigration attitudes (for reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see Appendix XX for precise variable descriptions).
+Figure \@ref(fig:multidv) displays standardized effects of the change in newspaper framing on immigration attitudes (for reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see Appendix 1 for precise variable descriptions).
 To provide reference values again, I rescale the expected experimental effect of 0.6 and SESOI of 0.15 for immigration attitudes to standard deviations.
@@
 Dotted vertical lines indicate minimal relevant effect (0.2 SD).
-Full models available in Appendix XX."}
-
-# add 0.9 confidence bar
+Full models available in Appendix 3.3."}
 
@@
 
-## Assumptions in the Generalization from Experimental Estimates
+## Explanations for Resistance to Framing
 
@@
 Second, if citizens consume many sources of political news at the same time, they might not react to a change in a single news outlet.
-Third, issue attitudes might only be responsive to news framing during critical periods of politicization.
+Third, repeated exposure over time might produce effects which are not perceptable in earlier waves.
+Fourth, issue attitudes might only be responsive to news framing during critical periods of politicization.
 The following section presents evidence about each of these assumptions.
@@
 What is interesting is that those reporting neutral migration attitudes seem to be more inclined to leave the newspaper: Neutral readership declines to a level of 57%, around 5 percentage points below the share reported by liberals (62%) and 3pp below the level of conservatives (60%).
-Regressing individual choice to read *Bild* in later waves on initial reported migration attitudes within the subsample of initial *Bild* readers shows a `r round(m_sel$coefficients[["init_mig_groupsNeutral"]], 2)*-100`% lower chance to report Bild readership among initial neutral readers, compared to liberal readers ($p =$ `r round(summary(m_sel)$coefficients["init_mig_groupsNeutral", "Pr(>|t|)"], 3)`, see table XX in appendix XX), whereas there is no significant or substantial difference for conservative readers.
+Regressing individual choice to read *Bild* in later waves on initial reported migration attitudes within the subsample of initial *Bild* readers shows a `r round(m_sel$coefficients[["init_mig_groupsNeutral"]], 2)*-100`% lower chance to report Bild readership among initial neutral readers, compared to liberal readers ($p =$ `r round(summary(m_sel)$coefficients["init_mig_groupsNeutral", "Pr(>|t|)"], 3)`), whereas there is no significant or substantial difference for conservative readers.
 Surprisingly, *Bild* readers reporting centrist immigration attitudes select out of the newspaper at higher rates than both conservative or liberal readers, whereas there is no significant difference between the latter two.
-I also tested whether conservative readers were more likely to start reading the newspaper.
-As appendix XX shows, there is no evidence of this process either.
+I also tested whether the association of reading the newspaper and conservative immigration attitudes was streangthened over time.
+As appendix 3.6.1 shows, there is no evidence of this process either.
 
-```{r selectionPlot, fig.cap="Share of initial Bild readers reporting readership in later waves by initial migration attitude. Dashed (red) vertical line indicates editorial change."}
+```{r selectionPlot, fig.cap="Share of initial Bild readers reporting readership in later waves by initial migration attitude. Dashed vertical line indicates editorial change."}
 
-OutSelection()
+OutSelection(color_palette = scales::grey_pal()(3))
 
@@
 Respondents could indicate on how many days they consumed newspapers other than *Bild* in the preceding week.
-Summing these responses allows to generate a variable indicating how many newspapers other than *Bild* have been consumed, weighted by the intensity of their readership (see appendix XX for a detailed description).
+Summing these responses allows to generate a variable indicating how many newspapers other than *Bild* have been consumed, weighted by the intensity of their readership (see appendix 1.2.3 for a detailed description).
 
@@
 The estimate is virtually identical for respondents indicating to consume other newspapers 1-3 times per week.
-Point estimates for other groups (consuming other newspapers 4-9, 10-15 or more than 15 days\footnote{A 'day' refers here to the additive days for every mentioned newspaper, that means if an individual reads newspaper A for seven days and another for six days, the total number of days will add up to thirteen.} in the preceding week) are well below the SESOI and statistically not different from zero, although estimation is less precise with higher values\footnote{See appendix XX for a visualization of all effects described in this section.}.
+Point estimates for other groups (consuming other newspapers 4-9, 10-15 or more than 15 days\footnote{A 'day' refers here to the additive days for every mentioned newspaper, that means if an individual reads newspaper A for seven days and another for six days, the total number of days will add up to thirteen.} in the preceding week) are well below the SESOI and statistically not different from zero, although estimation is less precise with higher values\footnote{See appendix 3.6.2 for a visualization of all effects described in this section.}.
 
@@
 
+```{r crowdout, fig.cap="Heterogenous treatment effects by level of exposure to different news sources."}
+
+CrowdOutEstimates(vis = T)
+
+```
+
 Crowding out does not explain the absence of an effect of news framing on political attitudes.
 Those respondents consuming no other political information from newspapers, TV news, or online sources are no more reactive to a change in migration framing than those with a more diverse news diet.
+
+### Slow Updating
+
+```{r didWaveEsts}
+
+ests <- DiDByWavePlot(return_ests = T)
+
+```
+
+If readers only perceive the change in content across longer time periods, the effect should slowly unfold over time.
+Then, initial absence of change might bias the estimates downward and thereby mask an effect.
+To assess whether an effect develops over time, figure \@ref(fig:migwaves) assesses the effect within split-samples for each post-wave compared to the pre-treatment wave.
+This allows the assessment of heterogeneous treatment effects across time.
+The black dots with associated confidence intervals indicate the estimated effect for each wave.
+The horizontal dashed line indicates the expected effect based on experimental evidence (0.6), whereas the dotted horizontal line indicates the SESOI of 0.15.
+The vertical dashed line indicates the timing of the editorial change.
+Over the course of the entire year 2017, the effect is clearly smaller than the SESOI, and includes zero.
+However, estimates for waves 10 and 11 in late 2018 and mid-2019 – more than one and a half years after the editorial change – showcase effects statistically different from zero, and including the SESOI boundary.
+The effects are rather small, with a point estimate of `r round(ests[["point"]][ests$wave == "10"], 3)` on the seven-point Likert scale, as well as an upper boundary just above the SESOI at `r round(ests[["upper"]][ests$wave == "10"], 3)`.
+The waves in late 2019 and early 2020 return to point estimates at slightly lower levels (`r round(ests[["point"]][ests$wave == "12"], 3)`, `r round(ests[["point"]][ests$wave == "13"], 3)`), with confidence intervals including zero.
+While there is evidence of persuasion in the long term, the effect size is overall very small.
+
+```{r migwaves, fig.cap="Effect on migration attitudes, by survey wave."}
+
+DiDByWavePlot()
+
+```
 
@@
 Readers did not react by selecting out of the newspaper, nor was the change in framing crowded out by other sources of information.
-Another possible explanation is that individuals informed themselves about the issue and formed an attitude once the issue emerged, in this case in 2015 during the large migratory movements in Europe.
-If that were the case, opinions should change less in the 2015 period than the period before or after.
+Even long-term exposure produced rather minor effects.
+Another possible explanation for this resilience to framing is that individuals informed themselves about the issue and formed an attitude once the issue emerged, in this case in 2015 during the large migratory movements in Europe.
+If that were the case, opinions should change more in 2015 than the following period.
 Figure \@ref(fig:MigChange) shows this statistic using GLES Longterm Panel data [@GLES2018LangfristPanel].
-Unfortunately, I lack data for the period preceding 2014 and 2015, forcing me to make one-off comparisons rather than providing a longitudinal picture.
+Unfortunately, I lack data for the period preceding 2014 and the year 2015, forcing me to make one-off comparisons rather than providing a longitudinal picture.
 The left panel compares the absolute change in individual immigration attitudes from 2014-2016 and 2016-2018, always measured in January.
@@
 The right-hand panel shows the change across one year, comparing 2016-2017 to 2017-2018 (to be comparable, the periods have to be of equal size).
-Across the course of 2016, when the debate surrounding the integration of refugees following their immigration in autumn 2015 and the events of new years eve 2016 in Cologne, individuals still show higher rates of attitudinal changes (`r round(MigChangeTable["2016-2017",][["change_mean"]], 2)`; [`r round(MigChangeTable["2016-2017",][["change_lower"]], 2)` `r round(MigChangeTable["2016-2017",][["change_upper"]], 2)`]) than 2017-2018 (`r round(MigChangeTable["2017-2018",][["change_mean"]], 2)`; [`r round(MigChangeTable["2017-2018",][["change_lower"]], 2)` `r round(MigChangeTable["2017-2018",][["change_upper"]], 2)`]).
+Across the course of 2016, when the German public debated the integration of refugees and the events of new years eve 2016 in Cologne, individuals still display higher levels of attitudinal change (`r round(MigChangeTable["2016-2017",][["change_mean"]], 2)`; [`r round(MigChangeTable["2016-2017",][["change_lower"]], 2)` `r round(MigChangeTable["2016-2017",][["change_upper"]], 2)`]) than 2017-2018 (`r round(MigChangeTable["2017-2018",][["change_mean"]], 2)`; [`r round(MigChangeTable["2017-2018",][["change_lower"]], 2)` `r round(MigChangeTable["2017-2018",][["change_upper"]], 2)`]).
 
 Although we lack evidence about the changes in migration attitudes pre-2015, these substantial and significant differences (technically differences-in-differences) suggest that, during the politicization of the issue in 2015, citizens updated their attitudes about the immigration issue, which, after the debate cooled down, crystallized into stable attitudinal positions, resistant to additional information.
+
+# Conclusion: The Ebb and Flow of Attitudinal Change
+
+What are the limits of media power?
+While the answer to this question has profound implications about the extent of elite influence in contemporary democracies, we currently lack evidence about the scope conditions of media effects.
+This study addresses this gap by presenting evidence from a rare shift in the migration coverage of Germany's largest tabloid, *Bild*.
+The presented results are robust evidence that readers' immigration attitudes remained surprisingly unaffected.
+Estimates of attitudinal change are indistinguishable from zero and remain below minimal effect sizes in a number of specifications, dependent variables, and subgroups.
+
+The paper presents a clear explanation for this resilience.
+After ruling out that readers selected out of the newspaper or that exposure to other sources conditions the effect, I find support for the explanation that attitudes became unresponsive after 2015: following this period, the average change in individual immigration attitudes decreased substantively and significantly.
+This suggests that the newspaper has missed a critical window to influence readers' immigration attitudes.
 
@@
 
-# Conclusion: The Power of News Framing in the Real World
+While this evidence might seem like a contradiction to the idea that attitudes change *most* during the politicization of an issue, it is useful to take a longitudinal perspective.
+The model I propose views political issues as defined in public discourse.
+Once an issue emerges in public debate (usually because of an external event), problem definitions, causal explanations, and potential solutions are collectively debated.
+Political actors struggle to get their frames considered.
+Only a small subset of these frames will get to dominate public debate, shaping citizens' understanding of the issue.
+This collective definition will be resistant to attempts of framing and thus stabilize attitudes.
+Attitudinal change hence accelerates during the politicization of an issue, as citizens update their perceptions.
+Once a stable collective issue definition emerges, individuals become resistant to further information about the issue.
 
-Does news framing affect public opinion?
-While the answer to this question has profound implications about the extent of elite influence in contemporary democracies, our current evidence comes almost exclusively from experiments.
-The present study addresses this gap by estimating the impact of an abrupt increase in the emphasis of crime in the migration coverage of Germany's largest tabloid, *Bild*.
+This model also speaks to a large body of media effects research.
+It suggests that the power of the news media to shape public opinion is more limited than previously thought.
+Even when elites try, they might not always be able to manipulate their audience's political attitudes.
+While studies on media effects has shown that public opinion *can* be affected by changing news exposure [@DellaVigna2007; @Foos2022; @Grossman2022; @Levendusky2022], this study took a first step to investigate under which conditions this process takes place.
 
-The presented results are robust evidence that readers' migration attitudes remained surprisingly unaffected.
-Estimates of attitudinal change are indistinguishable from zero and remain below minimal effect sizes in a number of specifications and within different subgroups.
-Migration attitudes are also not increasingly associated with crime attitudes.
-Related dependent variables such as integration attitudes, reporting migration as the most important problem, and support for the radical-right AfD do not deviate from those of other readers.
-In other words, readers did not react to a substantial increase in the emphasis of crime in migration coverage.
-
-The paper assessed several potential violated assumptions in the generalization from experimental estimates of framing effects into the real world.
-The differences could not be explained by selective exposure: readers with liberal immigration attitudes did not opt out of the newspaper at higher rates than readers with more conservative migration attitudes.
-Similarly, the exposure to information from other outlets did not condition the effect on readers' immigration attitudes.
-Even readers who consumed no other newspaper, TV news, or online news are unresponsive to the change in coverage.
-
-I found some support for the explanation that attitudes have become unresponsive after 2015: following this period, the average change in individual immigration attitudes decreased substantively and significantly.
-This suggests that - if there was opportunity at all - the newspaper might have missed a critical window to influence readers' migration attitudes.
-
-The main takeaway from the present study is that experimental estimates of framing effects do *not* simply generalize into the real world.
-While it is well-established that exposure to single frames can substantially affect political attitudes in survey- and laboratory experiments, real world environments are more complicated.
-My findings parallel evidence from panel surveys suggesting that attitudinal change of migration attitudes is rather rare [@Kustov2021].
-This incongruence of experimental and observational evidence suggests that the power of the news media to shape public opinion is more limited than previously thought.
-Even when elites try, they might not always be able to manipulate their audience's political attitudes.
-While work on media effects has shown that public opinion *can* be affected by changing news exposure [@DellaVigna2007; @Foos2022; @Grossman2022; @Levendusky2022], future work should investigate the relevant scope conditions conditioning this process and the precise treatments inducing opinion change in the real world.
-
-The present study has made a first step, outlining a simple framework for the measurement of emphasis frames in political communication, as well as their combination with the causal estimation of their impact.
-Subsequent studies should go further, seeking out quasi-experiments or conduct field experiments with different scope-conditions and assessing the impact of different forms of political communication.
-I want to emphasize the importance of a precise measurement of the independent variable here: unless we are able to compare treatments of different quality, the debate surrounding media effects will be stuck in a constant back-and-forth about the general size of broadly defined "media effects", rather than assessing which treatments affect public opinion under which conditions.
-
-The experimental literature on framing, on the other hand, would profit from trying to reconcile the strong evidence of opinion stability in the real world with the strong framing effects observed under experimental conditions.
-After all, we conduct experiments in order to generalize to broader contexts.
-This paper has shown that the findings from a large body of framing research do not easily generalize, and offered a possible explanation.
-Further research into the determinants of attitude stability, as well as the generalizability of the assumptions underlying framing experiments will help to explain the disconnect between the observational and experimental evidence.
-
-Despite the unique case and the extensive efforts to isolate the effect of the documented change in framing, this study suffers from several limitations.
-Tabloid readers differ from other readers in many ways, among others they are more opposed to immigration and less knowledgeable about politics (see Appendix XX).
-As the treatment in this study is not randomized, other groups might react differently to increased exposure to crime frames.
-Additionally, it is unclear how this finding translates into different contexts with more partisan media outlets, polarized electorates, or less educated citizens.
-However my main argument is precisely that we cannot simply assume that political communication has similar effects in different contexts.
-To identify which scope conditions are relevant, further work is necessary.
+This study has several limitations, which should be addressed by future research.
+The argument in this paper applies to liberal democracies in general, but I present evidence from Germany, which is a Western European democracy with a relatively high-quality press, large public broadcasters, and a moderately involved electorate.
+While the experimental evidence from the US, Switzerland, and Denmark discussed above supports the idea that this might be a more general phenomenon, future observational studies should assess longitudinal panel data in other contexts.
+Similarly, migration might be a 'special' issue, meaning that citizens form different attitudes differently on this issue [@Kustov2021].
+Lastly, my analysis of the 'crystallization' of attitudes is limited by the available data.
+To observe the ac- and deceleration of attitudinal change relative to issue's politicization, future research could exploit panel data from different contexts and on different issues, but ultimately more longer-term panel data tracking issue attitudes will be necessary.
+This is especially challenging, as attitudinal measures are usually added to survey questionnaires only *after* the politicization of these issues.
+However, to get a full picture of the process of attitude formation, it is necessary to track the same issues irrespective of their current relevance in day-to-day politics.
+Otherwise, researchers will only observe issue attitudes after the relevant processes of attitude formation have taken place.
 
@@
 
+# Acknowledgment
+
+\textit{I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Anselm Hager, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
+Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim, as well as participants of CompText 2022, EPSA 2022, ICA 2022, EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI,  and the Political Behaviour Section at Aarhus University.
+I also thank the two research assistants, Robin Groß and Nathalie Aerts, for annotating the news articles.
+This research was generously funded by Funded  by  the  Deutsche  Forschungsgemeinschaft  (DFG,  German  Research  Foundation) – 390285477/ GRK 2458 and the Deutscher Akademischer Austauschdienst (DAAD, German Academic Exchange Service)  – 57595508.}
+
 # Resources

### 2022-09-29 paper/appendix.Rmd
Adjust plot placement

@@
 output: 
-  pdf_document:
+  bookdown::pdf_document2:
     number_sections: TRUE
 toc: TRUE
+bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
 ---
@@
 knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, 
-                      fig.width=10, fig.align='center', fig.pos = "!ht", out.extra = "")
+                      fig.width=10, fig.align='center', fig.pos = "!htp", out.extra = "")
 
@@
 ### Overview
+
+Treated Group: Bild Readers in first (and only pre-treatment) wave. Control Group: Never-Readers of Bild. Post Date: $>=$ 01.02.2017
+
+```{r bild_descriptives, results = "asis"}
+
+gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
+
+desc <- 
+  gles_p_long %>% 
+  filter(wave == "1", !is.na(treat)) %>% 
+  group_by(treat) %>% 
+  select(gender_clean, ybirth_clean, `010_clean`, 
+         `1130_clean`, `1500_clean`, `afd_vote`, `430i_clean`) %>%
+  mutate(gender_clean = gender_clean-1) %>% 
+  mutate(across(.fns = as.integer)) %>% 
+  summarise(across(.fns = mean, na.rm = T)) %>% 
+  select(-treat) %>% 
+  t() %>% round(2)
+
+colnames(desc) <- c("Control", "Treatment")
+row.names(desc) <- c("Gender (0 = m, 1 = f)", "Birthyear", 
+                     "Political interest (1, 5)", "Immigration Attitude (-3, 3)",
+                     "General left-right (0-10)", "Share of AfD supporters", "AfD attitude (-5, 5)")
+
+knitr::kable(desc, align = c("c", "c"))
+
+rm(gles_p_long, desc)
+
+```
+
+Note that the variable "Birthyear" is left-censored in the data. All respondents born before 1955 were assigned 1955 as birth year.
 
@@
 
-GroupedDistPlot("mip_mig",
-                header = "Mention of Migration as Most Important Problem")
+gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
+
+gles_p_long[["dv"]] <- gles_p_long[["mip_mig"]]
+
+p_upper <- 
+  gles_p_long %>% 
+  filter(treat, !is.na(dv)) %>% 
+  ggplot(aes(dv)) +
+  geom_bar(aes(y = (..count..)/sum(..count..)),
+           fill = MetBrewer::met.brewer("Archambault")[4]) +
+  theme_minimal() +
+  xlab("") + ylab("Share") +
+  ggtitle("Mention of Migration as Most Important Problem", "Bild Readers")
+
+p_lower <- 
+  gles_p_long %>% 
+  filter(!treat, !is.na(dv)) %>% 
+  ggplot(aes(dv)) +
+  geom_bar(aes(y = (..count..)/sum(..count..)),
+           fill = MetBrewer::met.brewer("Archambault")[1]) +
+  theme_minimal() +
+  xlab("") + ylab("Share") +
+  ggtitle("", "Never Bild Readers")
+
+p_upper / p_lower
+
+rm(gles_p_long)
 
@@
 
+rm(gles_p_long)
+
 ```
+
+\pagebreak
 
@@
 ```
+
+\pagebreak
 
@@
 
+\pagebreak
+
 ### Handcoding
@@
 
-Annotation took place in a shiny app (see screenshot below).
+```{r, fig.cap="Screenshot of Annotation App", out.width = "\\textwidth"}
+
+knitr::include_graphics("vis/HandCodingScreenshot.png")
+
+```
+
+Annotation took place in a shiny app (see screenshot above).
 Coders were shown the title and text of a random news article in the sample.
@@
 Coders could also return to the preceding article in case they had selected the wrong option.
-The app allowed for faster annotation and minimized errors in the coding (compared to noting the annotations in an excel sheet).
-
-```{r, fig.cap="Screenshot of Annotation App"}
-
-knitr::include_graphics("vis/HandCodingScreenshot.png")
-
-```
+The app allowed for faster annotation and minimized errors in the coding (compared to e.g.
+noting the annotations in an excel sheet).
 
@@
   arrange(url)
-
-# correlation table - not so great
-table(common_nat$crime, common_rob$crime)
 
@@
 The migration annotation has been conducted by only one coder (1800 articles), while the crime articles have been annotated by two different coders separately (1000 each with 200 identical articles in each coder's sample).
-Annotation was very reliable with an agreement for `r agreement`% of annotated articles and a Krippendorff's alpha of `r round(k_alpha, 2)`.
-Conflicts were resolved by the author after inspection of the conflicting codings.
+Annotation was very congruent across coders with an agreement for `r agreement`% of annotated articles and a Krippendorff's alpha of `r round(k_alpha, 2)`.
+Conflicts were resolved by the author after inspection of the conflicting annotations.
 
-### Classifier Training
+\pagebreak
+
+### Classifier Fine-tuning
+
+```{r}
+
+bert_ests_raw <- 
+    fread(here('data/processed/bert_crime_clean.csv'))
+
+```
+
+Using the annotated samples, I fine-tune BERT classifiers from Huggingface's 'transformers' library for python (bert-base-german-cased), pre-trained on german Wikipedia articles, legal documents, and news articles.
+For each topic (crime/migration), 1400 articles served as training set, 200 each as validation and test set.
+Articles longer than 512 tokens (the maximum length of input for the BERT model) were truncated.
+I fine-tune for 10 epochs.
+Performance on the test set is outstanding for the migration classifier (F1 = 0.94, accuracy = 0.96, precision = 0.95, recall = 0.93) and very good for the crime classifier (F1 = 0.86, accuracy = 0.93, precision = 0.8, recall = 0.92).
+Both classifiers were subjected to sanity checks, before classifying first all articles according to their migration content, which returns `r nrow(bert_ests_raw)` articles (3.6% of all articles).
+For this subset, crime content is identified in `r sum(bert_ests_raw$crime_label)` articles (`r round(sum(bert_ests_raw$crime_label)/nrow(bert_ests_raw), 3)*100`).
 
 ```{=tex}
-\begin{table}
+\begin{table}[!h]
 \centering
@@
 
+As a sanity check, and in order to exemplify the nature of the treatment, table \@ref(tab:exampleArticles) shows the five *Bild* articles classified as crime with the highest likelihood, out of all migration-related articles.
+All articles relate to both migration and crime: one mentions a police report on the mass sexual assaults on new years eve 2015 in Cologne, two discuss police raids in refugee homes, and two discuss violence in refugee shelters.
+
+\pagebreak
+
 ### Correcting for change in DPA-sourced content
-
-Among the changes after Reichelt's takeover as chief editor of *Bild* was a severe drop in the overall number of articles published online.
-Figure \@ref(fig:dpaShare) shows the monthly number of articles *Bild* published in their online archive across time.
-Recall that Reichelt took over in February 2017, and briefly after - in June 2017 - the overall number of articles published decreases by over 60%.
-The graph also suggests an explanation for this sudden shift: the share of articles sourced from DPA, a major German press agency alike the Associated Press, sharply decreases at the same time as the major decrease in the number of articles takes place (see top blue bars).
-DPA is a press agency supplying many German news outlets, which means it must have a rather unbiased or at least centrist coverage, potentially decreasing the estimate of crime frames within Bild's migration content.
-This would not be a problem, as long as this content is equally likely to make it to the front page.
-However, *Bild* likely gives more weight to its own content compared to pre-written content from DPA.
-For this reason, the paper presented data excluding DPA content.
-On the other hand, the decision to discontinue buying content from DPA must have been made by Reichelt himself and is thus an outcome of the treatment.
-Hence, it is fruitful to assess the change including DPA-sourced content.
 
@@
 
-The left panel of figure \@ref(fig:treatmentDPAcorr) displays the quarterly share of migration articles discussing crime for *Bild* compared to all other newspapers.
-A depression is visible in 2016-2017 which was not visible in the corrected data.
-The share of crime content in *Bild*'s migration coverage strongly increases a few months following the treatment, when the share of DPA-sourced content severely drop.
-The gap between *Bild* and all other newspapers increases, and this increased difference persists.
-This change becomes even more visible in the right-hand panel, which shows a difference-in-differences estimate of the change of the share of crime news in a newspapers migration content, this time controlling for whether the content is DPA-sourced or not.
-The general picture is quite similar to the original estimate in the paper, as migration coverage only increases in *Bild*, while all other outlets remain rather stable on this metric.
-In the estimate including DPA content, the share of migration coverage devoted to crime increases by an even stronger 6 percentage points, which still constitutes a very substantial increase.
-Both ways of handling the data suggest a strong increase in the emphasis of crime in migration coverage.
+Among the changes after Reichelt's takeover as chief editor of *Bild* was a severe drop in the overall number of articles published online.
+Figure \@ref(fig:dpaShare) shows the monthly number of articles *Bild* published in their online archive across time.
+Recall that Reichelt took over in February 2017, and briefly after - in June 2017 - the overall number of articles published decreases by over 60%.
+The graph also suggests an explanation for this sudden shift: the share of articles sourced from DPA, a major German press agency alike the Associated Press, sharply decreases at the same time as the major decrease in the number of articles takes place (see top blue bars).
+DPA is a press agency supplying many German news outlets, which means it must have a rather unbiased or at least centrist coverage, potentially decreasing the estimate of crime frames within Bild's migration content.
+This would not be a problem, as long as this content is equally likely to make it to the front page.
+However, *Bild* likely gives more weight to its own content compared to pre-written content from DPA.
+For this reason, the paper presented data excluding DPA content.
+On the other hand, the decision to discontinue buying content from DPA must have been made by Reichelt himself and is thus an outcome of the treatment.
+Hence, it is fruitful to assess the change including DPA-sourced content.
+
+\pagebreak
 
@@
 
+The left panel of figure \@ref(fig:treatmentDPAcorr) displays the quarterly share of migration articles discussing crime for *Bild* compared to all other newspapers.
+A depression is visible in 2016-2017 which was not visible in the corrected data.
+The share of crime content in *Bild*'s migration coverage strongly increases a few months following the treatment, when the share of DPA-sourced content severely drop.
+The gap between *Bild* and all other newspapers increases, and this increased difference persists.
+This change becomes even more visible in the right-hand panel, which shows a difference-in-differences estimate of the change of the share of crime news in a newspapers migration content, this time controlling for whether the content is DPA-sourced or not.
+The general picture is quite similar to the original estimate in the paper, as migration coverage only increases in *Bild*, while all other outlets remain rather stable on this metric.
+In the estimate including DPA content, the share of migration coverage devoted to crime increases by an even stronger 6 percentage points, which still constitutes a very substantial increase.
+Both ways of handling the data suggest a strong increase in the emphasis of crime in migration coverage.
+
+\pagebreak
+
 ### Migration Attention over Time
 
-## Salience of Migration
+```{r migSalience, fig.cap="Attention to Migration in Different News Outlets"}
+
+MigSaliencePlot()
+
+```
+
+Figure \@ref(fig:migSalience) shows that the prevalence of migration content as classified by the first Bert model generally follows expectations.
+Three distinct peaks can be observed: first during the migratory movements to Germany in 2015, then after the sexual assaults on new years eve in 2016, and during the conflict regarding migration policy within the conservative party alliance CDU/CSU in 2018.
+Prevalence differs strongly across newspapers, with *Bild* having the lowest prevalence of migration content.
+This is likely due to their tabloid format, which emphasizes entertainment over news and politics content.
+The left-leaning SZ shows the highest attention to migration (during the peak in September 2015, nearly every second article is concerned with migration).
+This is likely the result of a website highly focused on politics.
+
+\pagebreak
 
@@
 
-## Treatment Groups
+## Parallel Trends
 
-Treated Group: Bild Readers in first (and only pre-treatment) wave. Control Group: Never-Readers of Bild. Post Date: $>=$ 01.02.2017
+```{r parallelTrends, fig.cap="Migration Attitude among Bild-readers compared to non-readers across Time"}
 
-```{r bild_descriptives, results = "asis"}
-
-gles_p_long <- fread(here('data/raw/gles/Panel/long_cleaned.csv'))
-
-desc <- 
-  gles_p_long %>% 
-  filter(wave == "1", !is.na(treat)) %>% 
-  group_by(treat) %>% 
-  select(gender_clean, ybirth_clean, `010_clean`, 
-         `1130_clean`, `1500_clean`, `afd_vote`, `430i_clean`) %>%
-  mutate(gender_clean = gender_clean-1) %>% 
-  mutate(across(.fns = as.integer)) %>% 
-  summarise(across(.fns = mean, na.rm = T)) %>% 
-  select(-treat) %>% 
-  t() %>% round(2)
-
-colnames(desc) <- c("Control", "Treatment")
-row.names(desc) <- c("Gender (0 = m, 1 = f)", "Birthyear", 
-                     "Political interest (1, 5)", "Immigration Attitude (-3, 3)",
-                     "General left-right (0-10)", "Share of AfD supporters", "AfD attitude (-5, 5)")
-
-knitr::kable(desc, align = c("c", "c"))
-
-rm(gles_p_long, desc)
+ParallelTrendsPlot()
 
@@
 
-Note that the variable "Birthyear" is left-censored in the data. All respondents born before 1955 were assigned 1955 as birth year.
-
-## Parallel Trends
-
-Figure \@ref(fig:parallelTrends) shows the development of migration attitudes among a panel of Bild readers\footnote{Readership was measured in a single wave in late 2015.} and non-readers across time, recorded in the German Longitudinal Election Study's Longterm Panel [@SOURCE].
+Figure \@ref(fig:parallelTrends) shows the development of migration attitudes among a panel of Bild readers\footnote{Readership was measured in a single wave in late 2015.} and non-readers across time, recorded in the German Longitudinal Election Study's Longterm Panel [@GLES2018LangfristPanel].
 This is a far smaller sample with a limited time frame and hence less useful for the precise estimation of the effects of changing migration framing.
@@
 
-```{r parallelTrends, fig.cap = "Migration Attitude among Bild-readers compared to non-readers across Time"}
-
-ParallelTrendsPlot()
-
-```
+\pagebreak
 
@@
 
-```{r did_imm_att, results='asis'}
+```{r did_imm_att}
 
@@
 
+\pagebreak
+
 ## Multiple DV Table
 
-## Longterm-Panel Model
+```{r}
+
+DiDPlot(return_table = T, multi = T)
+
+```
+
+\pagebreak
 
@@
 
-```{r LTPDiD, fig.height=2}
+It is also possible to estimate the effect of the change in editorship from the smaller and less frequent long-term panel, with a smaller sample size (between 1,700 and 5,000).
+The only post-treatment wave has been conducted from September to December 2017.
+The question wording of the variable measuring immigration attitudes is identical to the Panel study used in the main paper, however responses have been recorded on a 11-point scale.
+Treatment was defined similar to the main paper, with respondents who indicated to read *Bild* in the pre-treatment wave in the treatment group, and respondents indicating never to read *Bild* in the control group.
 
-LTPDiD()
+```{r LTPDiD_table, fig.cap="Effect of Reichelt Takeover on Immigration Attitudes among Bild-reader"}
+
+rawmodel <- LTPDiD(return_table = T)
+
+delta_pt <- rawmodel$coefficients[["postTRUE:treatTRUE"]]
+delta_lower <- confint(rawmodel)["postTRUE:treatTRUE", 1]
+delta_upper <- confint(rawmodel)["postTRUE:treatTRUE", 2]
+
+modelsummary::modelsummary(LTPDiD(return_table = T), output = "markdown", stars = T)
 
@@
 
-```{r LTPDiD_table, results='asis'}
+The model suggests a liberalizing effect of `r round(delta_pt, 2)` (`r abs(round(delta_pt, 3))/10*100`% of the scale range), which is not significant (lower CI `r round(delta_lower, 2)`; upper CI `r round(delta_upper, 2)`), suggesting a null effect, similar to the main model.
 
-modelsummary::modelsummary(LTPDiD(return_table = T), output = "latex", stars = T)
-
-```
+\pagebreak
 
@@
 
-```{r did_cond_crime, results='asis'}
+```{r did_cond_crime}
 
@@
 
+\pagebreak
+
 ## Readership models
@@
 
-```{r inselection}
+```{r inselection, fig.cap="Coefficients of OLS regression of readership on migration attitude across waves.
+Vertical lines indicate 95 percent confidence intervals, dashed (red) vertical line indicates editorial change."}
 
@@
 
-Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change.
-
-### Crowding out
-
-```{r crowdout}
-
-CrowdOutEstimates(vis = T)
-
-```
+# Resources

### 2022-09-29 paper/Manuscript_Framing.Rmd
Drop name

@@
 subtitle: "How Politicisation Shapes the Pace of Attitudinal Change"
-author: "Nicolai Berk"
 date: "`r Sys.Date()`"
@@
   bookdown::pdf_document2:
+    keep_tex: true
     toc: false
@@
 To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets *Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt*, as well as *Bild* for the period 2013-2019.
-These outlets reach a substantial share of the German public, with *Bild* distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 2.1 in the appendix for more information\footnote{Online appendix available at \url{https://github.com/nicolaiberk/bild/raw/main/paper/appendix.pdf}.}).
+These outlets reach a substantial share of the German public, with *Bild* distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 2.1 in the online appendix for more information).
 Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration.
@@
 As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3 percent of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}.
-Instead, I take a more informed approach by oversampling articles which are likely about migration: after constructing a seed dictionary of migration-related terms, I apply dictionary extension using German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles\footnote{The dictionary can be found in appendix 2.2.1.}.
+Instead, I take a more informed approach by oversampling articles which are likely about migration: after constructing a seed dictionary of migration-related terms, I apply dictionary extension using German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles\footnote{The dictionary can be found in online appendix 2.2.1.}.
 Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with the highest share of migration terms and 100 from the remaining articles with relative frequencies of migration-related terms in between these two groups) for each newspaper for a total of 1,800 papers.
 Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{The coder was instructed to annotate articles referring to migration or integration, which includes discussions of refugee numbers, immigrants' and naturalization rights, and general reports of migration.
-More information can be found in Appendix 2.2.3.}.
+More information can be found in online appendix 2.2.3.}.
 
@@
 This classifier is then used to annotate all 2.5 million newspaper articles.
-For the period from 2013 to 2019, around 90,000 articles (3.6%) are identified to treat the issue of migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 2.2.}.
+For the period from 2013 to 2019, around 90,000 articles (3.6%) are identified to treat the issue of migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in online appendix 2.2.}.
 
@@
 I then apply this classifier to the approximately 90,000 articles about migration identified by the first classifier.
-About 7% of all migration coverage consists of articles about some form of crime\footnote{See appendix 2.2.7 for more information.}.
+About 7% of all migration coverage consists of articles about some form of crime\footnote{See online appendix 2.2.7 for more information.}.
 
@@
 Treatment estimates including third-party authored content are similar in size.
-For a more extensive discussion see appendix 2.2.5.}.
+For a more extensive discussion see online appendix 2.2.5.}.
 The trends run parallel to each other preceding the treatment.
@@
 Responses were recorded on a seven-point Likert scale.
-This variable was centered on zero ($-3$ – liberalize, $3$ – restrict; the precise wording in the survey can be found in appendix 1.1.2).
+This variable was centered on zero ($-3$ – liberalize, $3$ – restrict; the precise wording in the survey can be found in online appendix 1.1.2).
 
@@
 The question provides respondents with a list of the six major daily newspapers plus an option "another daily newspaper" and asks whether they had consumed the paper in print or read articles from their website, and if so, how many days in the past week.
-Readers are defined as *treated* if they indicate to read *Bild* in the pre-treatment wave and as *untreated* if they indicate not to read the tabloid in the pre-treatment wave, nor any subsequent wave\footnote{See appendix 1 for descriptives of all mentioned variables.}.
+Readers are defined as *treated* if they indicate to read *Bild* in the pre-treatment wave and as *untreated* if they indicate not to read the tabloid in the pre-treatment wave, nor any subsequent wave\footnote{See online appendix 1 for descriptives of all mentioned variables.}.
 
@@
 Note that the pre-treatment differences of treatment and control group are corrected for in the individual fixed effects, as the groups are constant over time (readership is only assessed pre-treatment).
-As the panel data contains only one pre-treatment wave, the parallel trends assumption cannot be tested with this data directly, but assessing the trends using the GLES Longterm Panel [@GLES2018LangfristPanel] shows that *Bild* and non-*Bild* readers' immigration attitudes move in parallel preceding the treatment (see appendix 3.1).
+As the panel data contains only one pre-treatment wave, the parallel trends assumption cannot be tested with this data directly, but assessing the trends using the GLES Longterm Panel [@GLES2018LangfristPanel] shows that *Bild* and non-*Bild* readers' immigration attitudes move in parallel preceding the treatment (see online appendix 3.1).
 
@@
 t_ATT <- single_model$coeftable["postTRUE:treatTRUE", "t value"]
-p_ATT <- single_model$coeftable["postTRUE:treatTRUE", "Pr(>|t|))"]
+p_ATT <- single_model$coeftable["postTRUE:treatTRUE", "Pr(>|t|)"]
 
@@
 This represents only a fraction (`r round(ATT/0.6, 3)*100`%) of the already conservative experimental estimate of 0.6.
-The finding is robust to different model specifications, as well as using data from the GLES Longterm Panel (see appendix 3.2 and 3.4).
+The finding is robust to different model specifications, as well as using data from the GLES Longterm Panel (see online appendix 3.2 and 3.4).
 
@@
 Following [@Nelson1996], I also regress immigration attitudes on attitudes towards crime and investigate whether this association changes as a result of the change in coverage.
-Similar to the differences between the groups, I find a weaker association among readers of the tabloid, but no significant or substantively large difference post-treatment or when interacted with the DiD-term (see table in appendix 3.5).
+Similar to the differences between the groups, I find a weaker association among readers of the tabloid, but no significant or substantively large difference post-treatment or when interacted with the DiD-term (see table in online appendix 3.5).
 Respondents do not associate crime more strongly with migration following the change in migration coverage in *Bild*.
@@
 
-Figure \@ref(fig:multidv) displays standardized effects of the change in newspaper framing on immigration attitudes (for reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see Appendix 1 for precise variable descriptions).
+Figure \@ref(fig:multidv) displays standardized effects of the change in newspaper framing on immigration attitudes (for reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see online appendix 1 for precise variable descriptions).
 To provide reference values again, I rescale the expected experimental effect of 0.6 and SESOI of 0.15 for immigration attitudes to standard deviations.
@@
 Dotted vertical lines indicate minimal relevant effect (0.2 SD).
-Full models available in Appendix 3.3."}
+Full models available in online appendix 3.3."}
 
@@
 I also tested whether the association of reading the newspaper and conservative immigration attitudes was streangthened over time.
-As appendix 3.6.1 shows, there is no evidence of this process either.
+As online appendix 3.6.1 shows, there is no evidence of this process either.
 
@@
 Respondents could indicate on how many days they consumed newspapers other than *Bild* in the preceding week.
-Summing these responses allows to generate a variable indicating how many newspapers other than *Bild* have been consumed, weighted by the intensity of their readership (see appendix 1.2.3 for a detailed description).
+Summing these responses allows to generate a variable indicating how many newspapers other than *Bild* have been consumed, weighted by the intensity of their readership (see online appendix 1.2.3 for a detailed description).
 
@@
 The estimate is virtually identical for respondents indicating to consume other newspapers 1-3 times per week.
-Point estimates for other groups (consuming other newspapers 4-9, 10-15 or more than 15 days\footnote{A 'day' refers here to the additive days for every mentioned newspaper, that means if an individual reads newspaper A for seven days and another for six days, the total number of days will add up to thirteen.} in the preceding week) are well below the SESOI and statistically not different from zero, although estimation is less precise with higher values\footnote{See appendix 3.6.2 for a visualization of all effects described in this section.}.
+Point estimates for other groups (consuming other newspapers 4-9, 10-15 or more than 15 days\footnote{A 'day' refers here to the additive days for every mentioned newspaper, that means if an individual reads newspaper A for seven days and another for six days, the total number of days will add up to thirteen.} in the preceding week) are well below the SESOI and statistically not different from zero, although estimation is less precise with higher values\footnote{See online appendix 3.6.2 for a visualization of all effects described in this section.}.
 
@@
 
-# Acknowledgment
-
-\textit{I am thankful for extensive feedback and other support on this manuscript from Christian Arnold, Daniel Bischof, Philipp Broniecki, Jóhanna Ýr Bjarnadóttir, Elias Dinas, Florian Foos, Violetta Haas, Felix Hagemann, Anselm Hager, Julian Heid, Christina Gahn, Heike Klüver, Martin Vinæs Larsen, Matthew Levendusky, Will Lowe, Thomas M.
-Meyer, Rune Slothuus, Judith Spirig, Antonio Valentim, as well as participants of CompText 2022, EPSA 2022, ICA 2022, EPSIP Colloquium at HU Berlin, CIVICA EGN Workshop at the EUI,  and the Political Behaviour Section at Aarhus University.
-I also thank the two research assistants, Robin Groß and Nathalie Aerts, for annotating the news articles.
-This research was generously funded by Funded  by  the  Deutsche  Forschungsgemeinschaft  (DFG,  German  Research  Foundation) – 390285477/ GRK 2458 and the Deutscher Akademischer Austauschdienst (DAAD, German Academic Exchange Service)  – 57595508.}
-
 # Resources

### 2022-09-29 paper/appendix.Rmd
Drop name

@@
 title: "Appendix for 'Framing Effects in the Wild'"
-author: "Nicolai Berk"
 date: "15 5 2022"

### 2022-09-29 paper/Manuscript_Framing.Rmd
keep tex, final proofread

@@
       in_header: preamble.tex
-# subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
 fontsize: 12pt
@@
 Despite a 42 percent increase of the emphasis of crime in migration coverage, I find a robust null effect on immigration attitudes and a number of related variables.
-Further analyses suggest that media outlets' ability to manipulate public opinion in the short term seems to be limited to brief opportunity windows during the politicisation of a given issue."
+Further analyses suggest that media outlets' ability to manipulate public opinion seems to be limited to brief opportunity windows during the politicisation of a given issue."
 keywords: "Public Opinion, Media Effects, News Framing, Opinion Formation, Emphasis Framing, Conditions of Media Effects."
@@
 
-In the remainder of this paper, I will argue that *Bild* missed a critical window of opportunity to shape public opinion.
+I argue that *Bild* missed a critical window of opportunity to shape public opinion.
 As readers' immigration attitudes had crystallized following the politicization of immigration in 2015, their immigration attitudes remained resistant to a change in the tabloid's migration framing.
-I support my argument with evidence presented in three steps: first, I show that *Bild* indeed increasingly emphasized crime-related news in its migration coverage, following an exogenously timed change of the editor-in-chief.
-I then exploit this natural experiment to provide evidence that this change did little to affect readers' immigration attitudes or related variables.
+I support my argument with evidence presented in three steps: first, I show that *Bild* increasingly emphasized crime-related news in its migration coverage, following an exogenously timed change of the editor-in-chief.
+I then exploit this quasi-experiment to provide evidence that this change did little to affect readers' immigration attitudes or related variables.
 In a last step, I trace different explanations for the absence of this effect, suggesting that the pace of attitudinal change severely decreased following the politicization of the issue in 2015.
@@
 I apply this framework to a dataset of 2.5 million articles from the major German daily newspapers.
-Using supervised classifiers, I first select migration-related coverage, to then estimate the prevalence of crime content within this coverage.
+Using supervised classifiers, I first identify migration-related coverage, to then estimate the prevalence of crime content within this coverage.
 This analysis suggests that following the change of the editor-in-chief, the emphasis of crime in migration content increased by over 40 percent.
@@
 I use a *difference-in-differences* (DiD) design to estimate the impact of the increased emphasis of crime in the coverage of migration and refugees.
-Results show that the changing framing did not result in more restrictive attitudes towards immigration, nor did it affect the association of crime with migration, views on integration, or the perceived importance of the immigration issue.
+Results show that the changing framing did not result in more restrictive attitudes towards immigration, nor did it affect the association of crime with immigration, views on integration, the perceived importance of the immigration issue, or support for the radical right.
 
@@
 Third, I test whether attitudes change after longer-term exposure.
-I find small effects after more than one and a half years, suggesting a very slow pace of attiudinal change.
+I find small effects after more than one and a half years, suggesting a very slow pace of attitudinal change.
 Lastly, I assess whether attitudes crystallized after the politicization of immigration in 2015.
@@
 [...] A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside" [-@Kinder2007, 157].
-By precisely identifying the nature of the change in news coverage, this study answered this call.
+By precisely identifying framing in news coverage, as well as its effects on public opinion, this study answered his call.
 The null effects found suggest that framing effects do not easily generalize from the experimental context.
@@
 The paper proceeds as follows: I provide a brief review of the expectancy-value model of attitude formation, which informs my hypotheses and content analysis, before discussing potential limits of framing effects in real-world environments.
-I then present the research design, content analysis, and a discussion of expected and minimal effect size of interest, before turning to the estimation of the effect of changing immigration framing on immigration attitudes and trace different explanations for the observed resistance.
-In the conclusion, I outline the implications of this model for framing, media, and public opinion research, as well as the limitations of this study.
+I then present the research design, content analysis, and a discussion of expected and minimal effect size of interest, before turning to the estimation of the effect of interest.
+The last empirical part traces different explanations for the observed resistance.
+In the conclusion, I outline the implications of my model, the limitations of the study, as well as avenues for future research.
 
@@
 Many other forms of framing exist, such as equivalence frames [@Kahneman1979prospect], episodic frames [@Iyengar2005], or generic frames [@DeVreese2005].
-The focus on emphasis frames in this study is owed to the nature of the case, as well as the generalized theory regarding the effect of emphasis frames on attitudes about any issue (as opposed to generic and episodic frames) and their common use in news content (which is not the case for equivalence frames).
+The focus on emphasis frames in this study is owed to the generalized theory regarding the effect of emphasis frames on attitudes about any issue (as opposed to generic and episodic frames) and their common use in news content (which is not the case for equivalence frames).
 
@@
 Research on framing has shown for decades that citizens' attitudes and their issue associations are highly reactive to minor changes in the emphasis of specific considerations [@Chong2007b; @Chong2010; @Druckman2012Bias; @Kinder1990; @Nelson1996; @Nelson1997Rally; @sniderman2004structure; for reviews see @Busby2019; @Druckman2001; @Leeper2020].
-However, it remains unclear how well these experimental findings translate into the real world.
+However, it remains unclear how well these experimental findings translate into citizens' everyday realities.
 Below, I outline three key assumptions in the generalization of experimental estimates.
@@
 First, taking experimental effects as estimates of the real-world impact of framing means making strong assumptions about citizens' exposure to frames: while framing studies usually simply present news articles or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience.
-Changes in news framing itself might affect how likely readers are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news content containing such frames [and vice versa seek out attitudinally congruent information, @Arceneaux2010; @Druckman2012Bias].
+Changes in news framing itself might affect how likely citizens are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news content containing such frames [and vice versa seek out attitudinally congruent information, @Arceneaux2010; @Druckman2012Bias].
 This process of 'selective exposure/avoidance' [@Bennett2008], or a 'confirmation bias' [@Taber2006] brings with it a major endogeneity problem making purely correlational evidence rather uninformative.
@@
 In the summer of 2015, Germany became sanctuary for around 800,000 refugees who had fled war, violence, and famine in Syria and elsewhere.
-The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win representation in the national parliament.
+The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win seats in the national parliament.
 Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* initially maintained a somewhat balanced coverage of refugees, which – although still portraying migrants more negatively than other outlets [@Maurer2019] – even started a campaign called "#RefugeesWelcome" to gather support for the newly arriving\footnote{See \url{https://web.archive.org/web/20160114154402/https://www.bild.de/news/topics/fluechtlingshilfe/wir-helfen-buehne-42385428.bild.html}.}.
@@
 These outlets reach a substantial share of the German public, with *Bild* distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 2.1 in the online appendix for more information).
-Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration.
-Second, I identify content about crime *within* migration coverage by training and applying another supervised classifier.
-This approach closely resembles the value-expectancy model outlined [above](#framing-effects), as I first identify coverage about the *issue*, before identifying the consideration emphasized in the discussion of this issue.
+Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I identify content about migration.
+Second, I identify content about crime *within* migration coverage.
+This approach closely resembles the value-expectancy model outlined [above](#framing-effects), as I first identify coverage about the *issue*, before identifying the *consideration* emphasized in the discussion of this issue.
 
@@
 
-# Conclusion: The Ebb and Flow of Attitudinal Change
+# Conclusion
 
 What are the limits of media power?
-While the answer to this question has profound implications about the extent of elite influence in contemporary democracies, we currently lack evidence about the scope conditions of media effects.
+While the answer to this question has profound implications for our understanding of elite influence in contemporary democracies, we currently lack evidence about the scope conditions of media effects.
 This study addresses this gap by presenting evidence from a rare shift in the migration coverage of Germany's largest tabloid, *Bild*.
@@
 This collective definition will be resistant to attempts of framing and thus stabilize attitudes.
-Attitudinal change hence accelerates during the politicization of an issue, as citizens update their perceptions.
+Attitudinal change accelerates during the politicization of an issue, as citizens update their perceptions.
 Once a stable collective issue definition emerges, individuals become resistant to further information about the issue.
@@
 Even when elites try, they might not always be able to manipulate their audience's political attitudes.
-While studies on media effects has shown that public opinion *can* be affected by changing news exposure [@DellaVigna2007; @Foos2022; @Grossman2022; @Levendusky2022], this study took a first step to investigate under which conditions this process takes place.
+While studies on media effects have shown that public opinion *can* be affected by changing news exposure [@DellaVigna2007; @Foos2022; @Grossman2022; @Levendusky2022], this study took a first step to investigate under which conditions this process takes place.
 
@@
 While the experimental evidence from the US, Switzerland, and Denmark discussed above supports the idea that this might be a more general phenomenon, future observational studies should assess longitudinal panel data in other contexts.
-Similarly, migration might be a 'special' issue, meaning that citizens form different attitudes differently on this issue [@Kustov2021].
+Similarly, migration might be a 'special' issue, meaning that citizens form attitudes differently on this issue [@Kustov2021].
 Lastly, my analysis of the 'crystallization' of attitudes is limited by the available data.
-To observe the ac- and deceleration of attitudinal change relative to issue's politicization, future research could exploit panel data from different contexts and on different issues, but ultimately more longer-term panel data tracking issue attitudes will be necessary.
+To observe the ac- and deceleration of attitudinal change relative to issue's politicization, future research should exploit panel data from different contexts and on different issues, but ultimately more longer-term panel data tracking issue attitudes will be necessary.
 This is especially challenging, as attitudinal measures are usually added to survey questionnaires only *after* the politicization of these issues.

### 2022-09-29 paper/Manuscript_Framing.tex
keep tex, final proofread

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Limits of Media Effects},
  pdfkeywords={Public Opinion, Media Effects, News Framing, Opinion Formation, Emphasis Framing, Conditions of Media Effects.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{The Limits of Media Effects}
\lhead{}
\usepackage{setspace}\singlespacing
\renewcommand{\footnotesize}{\normalsize \doublespacing}
\setlength{\headheight}{14.49998pt}
\cfoot{\thepage}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Limits of Media Effects}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{How Politicisation Shapes the Pace of Attitudinal Change}
\author{}
\date{\vspace{-2.5em}2022-09-29}

\begin{document}
\maketitle
\begin{abstract}
What are the limits of the news media's ability to shape public opinion? I argue that politicization conditions the responsiveness of individual attitudes to changes in the information environment. Exploiting a rare change in the migration framing of the biggest German tabloid \emph{Bild}, I estimate the precise impact of this shift on immigration attitudes using large-scale panel data. Despite a 42 percent increase of the emphasis of crime in migration coverage, I find a robust null effect on immigration attitudes and a number of related variables. Further analyses suggest that media outlets' ability to manipulate public opinion seems to be limited to brief opportunity windows during the politicisation of a given issue.
\end{abstract}

\medskip

WORD COUNT: 8101

\pagebreak

\doublespacing

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

A long tradition of research on public opinion suggests that political attitudes are a direct reflection of the information environment shaping the `pictures in our heads' (Lippmann 1922). This view is supported by an extensive body of experimental evidence showing that framing is highly effective in the manipulation of issue attitudes. However, prior work has shown that the extrapolation of experimental results to real-world environments is often difficult (Barabas and Jerit 2010), and that the effects of framing are highly dependent on the political context (Chong and Druckman 2013). Media effects research has established that real-world changes in the media environment \emph{can} affect issue attitudes (Foos and Bischof 2022; Grossman, Margalit, and Mitts 2022; Djourelova 2020), but not always (Chiang and Knight 2011; Spirig 2020). We currently know little about the real-world conditions under which news framing affects public opinion.

This study attempts to address this research gap presenting evidence from Germany, 2017-2020. This period - following a spike in asylum applications in 2015 - was marked by a focus on immigration in political discourse, as well as the first parliamentary entrance of a radical-right party since the post-war years. Many observers connected this sudden change in Germany's political landscape to a changing immigration discourse and the normalization of far-right ideas in public debate (Hermsmeier 2017). Germany's largest tabloid newspaper, \emph{Bild}, was seen as a strong driver of this development: it was claimed that by framing asylum seekers as criminals, the paper fueled anti-immigration sentiment and support for the radical-right \emph{AfD} (Niggemeyer 2018).

I argue that \emph{Bild} missed a critical window of opportunity to shape public opinion. As readers' immigration attitudes had crystallized following the politicization of immigration in 2015, their immigration attitudes remained resistant to a change in the tabloid's migration framing. I support my argument with evidence presented in three steps: first, I show that \emph{Bild} increasingly emphasized crime-related news in its migration coverage, following an exogenously timed change of the editor-in-chief. I then exploit this quasi-experiment to provide evidence that this change did little to affect readers' immigration attitudes or related variables. In a last step, I trace different explanations for the absence of this effect, suggesting that the pace of attitudinal change severely decreased following the politicization of the issue in 2015.

To assess whether the migration framing in \emph{Bild} really changed, I develop an approach to measure framing in political texts. I apply this framework to a dataset of 2.5 million articles from the major German daily newspapers. Using supervised classifiers, I first identify migration-related coverage, to then estimate the prevalence of crime content within this coverage. This analysis suggests that following the change of the editor-in-chief, the emphasis of crime in migration content increased by over 40 percent.

To estimate the effect of this changing framing on immigration attitudes, I employ panel data from the German Longitudinal Election Study, fielded in the period of interest (Debus, Faas, and Roßteutscher 2017). I use a \emph{difference-in-differences} (DiD) design to estimate the impact of the increased emphasis of crime in the coverage of migration and refugees. Results show that the changing framing did not result in more restrictive attitudes towards immigration, nor did it affect the association of crime with immigration, views on integration, the perceived importance of the immigration issue, or support for the radical right.

Lastly, I explore different explanations why this shift in migration framing did not bring about attitudinal changes. First, I assess whether readers with initially liberal migration attitudes selected out of the newspaper in response to the changing portrayal of migrants. Reported readership of respondents with liberal migration attitudes remains at similar levels as that of readers with restrictive migration attitudes. Second, I investigate whether readers with many different sources of information are less reactive to the changing coverage and mask the effect. I find no effect heterogeneity across the reported consumption of newspaper, TV and online news, ruling out the possibility that readers with more diverse information hide an effect among exclusive \emph{Bild} readers. Third, I test whether attitudes change after longer-term exposure. I find small effects after more than one and a half years, suggesting a very slow pace of attitudinal change. Lastly, I assess whether attitudes crystallized after the politicization of immigration in 2015. Using data from a long-term online panel (Roßteutscher et al. 2018), I show that the average individual change in immigration attitudes was substantially lower in the period 2016-2018 compared to the period 2014-2016.

This evidence suggests a general model of opinion change that contributes to distinct literatures on media effects, attitude formation, and framing. Students of the effects of news content on political attitudes have started to explore the scope conditions of media effects (Chiang and Knight 2011; Spirig 2020). This paper contributes to this literature by showing that changes in media coverage are ineffective when they are not addressing currently politicised issues. As a result, elite influence on public opinion is limited outside specific windows of opportunity.

The analyses in this paper also speak to recent evidence of overall attitude stability (Kustov, Laaker, and Reller 2021): citizens' immigration attitudes \emph{are} rather stable most of the time. However, my findings suggest that the pace of attitudinal change increases dramatically when an issue becomes salient in public debate. The emerging picture is an ebb and flow of attitudinal stability and change, dependent on the salience of the issue at stake.

Lastly, the evidence speaks to the study of framing effects. Fifteen years ago, Donald Kinder called for observational research on framing effects: ``Experimental results can always be questioned on their generalizability, and framing effects are no exception. {[}\ldots{]} A more balanced reading of frame effects requires methodological diversification, experiments and studies oriented to the world outside'' (2007, 157). By precisely identifying framing in news coverage, as well as its effects on public opinion, this study answered his call. The null effects found suggest that framing effects do not easily generalize from the experimental context.

The paper proceeds as follows: I provide a brief review of the expectancy-value model of attitude formation, which informs my hypotheses and content analysis, before discussing potential limits of framing effects in real-world environments. I then present the research design, content analysis, and a discussion of expected and minimal effect size of interest, before turning to the estimation of the effect of interest. The last empirical part traces different explanations for the observed resistance. In the conclusion, I outline the implications of my model, the limitations of the study, as well as avenues for future research.

\hypertarget{framing-effects}{%
\section{The Expectancy-Value Model}\label{framing-effects}}

``Framing is the process by which a communication source, such as a news organisation, defines and constructs a political issue or public controversy'' (Nelson, Clawson, and Oxley 1997). Different forms of frames have been conceptualized. When I talk about `frames' here, I refer to \emph{emphasis frames}. These frames emphasize certain topics in relation to an issue, guiding the recipient to think about the issue with those considerations in mind that are promoted by the frame (Leeper and Slothuus 2020, 152). Many other forms of framing exist, such as equivalence frames (Kahneman and Tversky 1979), episodic frames (Iyengar 2005), or generic frames (De Vreese 2005). The focus on emphasis frames in this study is owed to the generalized theory regarding the effect of emphasis frames on attitudes about any issue (as opposed to generic and episodic frames) and their common use in news content (which is not the case for equivalence frames).

Work using the emphasis framing concept of framing mostly builds on the expectancy-value model developed by Ajzen and Fishbein (2000). This model suggests that an attitude on a given issue is a function of two factors: the value of considerations relating to that issue and the strength of their association with the issue. The evaluation of the issue is subdivided into a number of considerations, which will carry clear evaluations. For example, to form an opinion about whether immigration to one's country should be restricted, a person might consider the humanitarian conditions in the countries of origin (negative consideration regarding restrictive migration policy), as well as the risk of increased crime (positive consideration; note that the model does not differentiate whether a consideration is grounded in objective reality). Individuals weigh each of these considerations (so-called ``frames in thought,'' Druckman 2001) to form an overall opinion on the subject.

Figure \ref{fig:cogStor} visualizes this logic. An individual holds an attitude \(y\) about a given issue (bottom square). The issue is associated with a number of different considerations (top circles), each of which carries an evaluation \(x_i\), e.g.~a potential surge in crime is considered a negative outcome. Based on the strength of the association \(w_i\) of a given consideration with the issue, that consideration's evaluation is more or less reflected in the overall attitude \(y\), which is equal to the weighted sum of evaluations. For example, if a given individual associates immigration strongly with an increase in criminal activity and welfare fraud, but only very weakly with humanitarian considerations, cultural enrichment, liberty, or economic growth, they will form a rather negative attitude about the issue, as the former factor more prominently in their reasoning about migration.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{vis/CognitiveStorage.png}
    \caption{The cognitive evaluation of an issue $y$ is determined by the strength of association $w_i$ with other concepts with existing evaluations $x_i$.}
    \label{fig:cogStor}
\end{figure}

How does this model incorporate news content and other forms of political communication? News content can emphasize different considerations of an issue (``frames in communication''). By being exposed to the consideration, an individual's cognitive association of the issue at hand with the raised consideration strengthens (or in more technical terms: the weight of the consideration \(w_i\) increases). As a result, this specific consideration factors more prominently in the formulation of an overall attitude: ``media frames influence opinions by stressing specific values, facts, or other considerations, endowing them with greater apparent relevance to the issue than they might appear to have under an alternative frame'' (Nelson, Clawson, and Oxley 1997, 569).

Applying this to the issue of migration policy and the consideration of criminal migrants, one can imagine a news consumer confronted with an increased volume of news about crimes committed by migrants. The value-expectancy model predicts that i) the consumer forms a cognitive definition of migration that is increasingly associated with the issue of crime, meaning this consideration features more prominently when forming an opinion about the appropriate level of immigration; ii) as a result, their opinion about migration policies should become more restrictive, as the negative consideration of crime is weighted more heavily in the evaluation of the migration issue.

\medskip

\noindent \textit{\textbf{Association hypothesis}: When an individual is exposed more to a specific consideration about an issue, their association of the issue with this consideration should be strengthened.}

\noindent \textit{\textbf{Evaluation hypothesis}: When an individual is exposed more to a specific positive/negative consideration about an issue, their attitude about the overall issue should become more positive/negative.}

\hypertarget{framing-limits}{%
\section{Limits of Framing Effects}\label{framing-limits}}

Research on framing has shown for decades that citizens' attitudes and their issue associations are highly reactive to minor changes in the emphasis of specific considerations (Chong and Druckman 2007b, 2010; Druckman, Fein, and Leeper 2012; Kinder and Sanders 1990; Nelson and Kinder 1996; Nelson, Clawson, and Oxley 1997; Sniderman and Theriault 2004; for reviews see Busby, Flynn, and Druckman 2019; Druckman 2001; Leeper and Slothuus 2020). However, it remains unclear how well these experimental findings translate into citizens' everyday realities. Below, I outline three key assumptions in the generalization of experimental estimates.

First, taking experimental effects as estimates of the real-world impact of framing means making strong assumptions about citizens' exposure to frames: while framing studies usually simply present news articles or other forms of political content to respondents, news content in the real world competes with other news and entertainment content to reach its audience. Changes in news framing itself might affect how likely citizens are to consume news content: readers might be less likely to consume frames challenging their existing attitudes and reject news content containing such frames (and vice versa seek out attitudinally congruent information, Arceneaux and Johnson 2010; Druckman, Fein, and Leeper 2012). This process of `selective exposure/avoidance' (Bennett and Iyengar 2008), or a `confirmation bias' (Taber and Lodge 2006) brings with it a major endogeneity problem making purely correlational evidence rather uninformative. As most framing studies do not offer choice of content to respondents, engagement remains an assumption when taking experimental studies as evidence of framing effects in the real world (for an exception see Druckman, Fein, and Leeper 2012).

Second, even if consumers receive the content, it is not clear how much an individual relies on this source when forming an opinion on the subject. Information from different sources might `crowd out' the framing of one specific outlet: by consuming content from many sources, individuals give less attention to a given source, thereby severely limiting the overall impact of that outlet's coverage. Experimental evidence suggests that, when an individual receives competing frames, these cancel each other out, although the precise impact is dependent on the relative timing of exposure, the quality of the frame, as well as individual characteristics (Chong and Druckman 2007b, 2010, 2013). Additionally, individuals might update their perceptions slowly, as the increased emphasis of a consideration is not necessarily evident from the first few articles, instead arising from repeated exposure over time. Especially given that this study is concerned with a change in the \emph{relative} emphasis of a consideration, it might take some time for citizens' perceptions to catch up to the changing issue representation.

Third, cognitive engagement with frames might strongly differ in the real world compared to experimental contexts. Once individuals formed political attitudes, they might resist framing: Citizens presented with a plethora of news content about an issue will spend less time and cognitive energy on counter-attitudinal arguments than those supporting their viewpoint, lending more importance to considerations raised by amenable content (Taber and Lodge 2006). Experimental evidence suggests similar dynamics specifically for framing: when individuals are free to choose content, initial frames dominate the opinion-formation process, while novel frames are rejected (Druckman, Fein, and Leeper 2012) and even serve to strengthen pre-existing attitudes (Bechtel et al. 2015).

In sum, there are many reasons to assume that framing might have very different consequences in real-world environments than in their experimental emulations. If one takes experimental evidence as an approximation of the effectiveness of framing in the real world, they make many strong assumptions about citizens' exposure to, reliance on, and cognitive engagement with the frames in news content. Experiments can only incorporate few characteristics of the real world at a time. In order to test the external validity of framing effect studies, it is necessary to study observational data.

\hypertarget{research-design}{%
\section{Research Design}\label{research-design}}

In order to test whether changing news content affected political attitudes, I exploit an exogenously timed editorial change in the largest German newspaper, \emph{Bild}. As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts. The fielding of a large-scale panel survey in the same period allows to assess the precise impact of this change in news content on consumers' migration attitudes and related variables.

\hypertarget{a-rare-shift-in-migration-framing}{%
\subsection{A Rare Shift in Migration Framing}\label{a-rare-shift-in-migration-framing}}

In the summer of 2015, Germany became sanctuary for around 800,000 refugees who had fled war, violence, and famine in Syria and elsewhere. The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win seats in the national parliament. Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper \emph{Bild} initially maintained a somewhat balanced coverage of refugees, which -- although still portraying migrants more negatively than other outlets (Maurer et al. 2019) -- even started a campaign called ``\#RefugeesWelcome'' to gather support for the newly arriving\footnote{See \url{https://web.archive.org/web/20160114154402/https://www.bild.de/news/topics/fluechtlingshilfe/wir-helfen-buehne-42385428.bild.html}.}. This was often connected to chief editor Kai Diekmann, who hosted a refugee family in his home (Reichart 2015).

About one and a half years later, in December 2016, Axel Springer, the company owning \emph{Bild}, announced that Diekmann would leave the company. Less than a week after the announcement, it became public that prosecutors investigated Diekmann for sexual harassment. While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time support this interpretation of events.} ({``{Springer-Mitarbeiterin wirft Diekmann Bel{ä}stigung vor}''} 2017). The migration coverage in \emph{Bild} severely changed when Diekmann left the newspaper in February 2017 and Julian Reichelt took over the position as editor-in-chief. The paper increasingly started painting a picture of refugees as criminals on the tabloid's front page (Niggemeyer 2018; Zudeick 2018). Headlines like ``I killed 40 people and want asylum'' increasingly dominated the migration coverage of the newspaper. In a speech months before he took over the position as chief editor, Reichelt outlined his motivation for such a shift in migration coverage: ``I can assure you: nothing has hurt {[}\emph{Bild}{]} economically as much as our clear, humane, empathetic stance in the refugee crisis'' \footnote{Reichelt in a speech at Deutschlandfunk's conference "Formate des Politischen 2016": \url{https://vimeo.com/190347766}}. While he expressed his support for the decision to take this stance at the time, he argued that the German media shows too little tolerance towards anti-immigration attitudes, thereby excluding those holding such views from political discourse.

This case presents a unique opportunity to study the effects of media content on public opinion. As I will show below, the emphasis of crime strongly increased in \emph{Bild}'s migration coverage following Reichelt's takeover. The change of editor itself was not discussed in the media, which means any opinion changes among readers can only be the result of the changing content (see Spirig 2020). Additionally, the timing of the editorial change is likely exogenous, given the pressure from allegations against Diekmann. In summary, \emph{this case is as close as possible to a field experiment in which a specific consideration of migration coverage is amplified in the coverage of one newspaper, but not others}.

In the following sections, I will outline a framework for the measurement of emphasis frames in communication and showcase the increasing emphasis of crime in \emph{Bild}'s migration coverage. Subsequent sections will describe the panel data and variables to measure frames in thought (namely migration attitudes and their association with attitudes about crime) and define the difference-in-difference estimator. I will close with a discussion of the expected experimental effect size and the minimal effect size of interest to provide baselines for comparison of the estimator.

\hypertarget{measuring-frames-in-communication}{%
\subsection{Measuring Frames in Communication}\label{measuring-frames-in-communication}}

To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets \emph{Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt}, as well as \emph{Bild} for the period 2013-2019. These outlets reach a substantial share of the German public, with \emph{Bild} distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 2.1 in the online appendix for more information). Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I identify content about migration. Second, I identify content about crime \emph{within} migration coverage. This approach closely resembles the value-expectancy model outlined \protect\hyperlink{framing-effects}{above}, as I first identify coverage about the \emph{issue}, before identifying the \emph{consideration} emphasized in the discussion of this issue.

To identify whether an article is about migration, I employ supervised machine learning. As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3 percent of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}. Instead, I take a more informed approach by oversampling articles which are likely about migration: after constructing a seed dictionary of migration-related terms, I apply dictionary extension using German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles\footnote{The dictionary can be found in online appendix 2.2.1.}. Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with the highest share of migration terms and 100 from the remaining articles with relative frequencies of migration-related terms in between these two groups) for each newspaper for a total of 1,800 papers. Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{The coder was instructed to annotate articles referring to migration or integration, which includes discussions of refugee numbers, immigrants' and naturalization rights, and general reports of migration. More information can be found in online appendix 2.2.3.}.

Using this sample, a BERT transformer model\footnote{\url{https://huggingface.co/bert-base-german-cased}}, pre-trained on a large German corpus of Wikipedia articles, News, and legal documents, is fine-tuned on a random subset of 1,400 annotated articles (training set) with a validation set of 200 articles. After fine-tuning, the model correctly classifies 95.5\% of a test set of 200 articles (F1: 0.94, recall: 0.93, precision: 0.95). This classifier is then used to annotate all 2.5 million newspaper articles. For the period from 2013 to 2019, around 90,000 articles (3.6\%) are identified to treat the issue of migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in online appendix 2.2.}.

To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest. Using a training set of 1400 articles (selected using the identical process as above), a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7\%. I then apply this classifier to the approximately 90,000 articles about migration identified by the first classifier. About 7\% of all migration coverage consists of articles about some form of crime\footnote{See online appendix 2.2.7 for more information.}.

The left panel of figure \ref{fig:treatment} shows the share of migration coverage devoted to crime news, once for \emph{Bild} (solid, black line) and once for all other newspapers (dashed, gray line). As we can see, \emph{Bild}'s attention to crime news in its migration coverage substantially increased directly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change\footnote{Note that this data consists exclusively of original Bild content. Treatment estimates including third-party authored content are similar in size. For a more extensive discussion see online appendix 2.2.5.}. The trends run parallel to each other preceding the treatment. The lower attention to crime in 2015 and the increase in 2016 is in line with prior research (Maurer et al. 2019). The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in \emph{Bild}. One can see that \emph{Bild} was the only newspaper which substantially changed its emphasis of the frame, increasing the share of articles devoted to crime by around 5 percentage points (over 40 percent percent of the pre-treatment average), while other newspapers maintained their levels of attention.

\begin{figure}[!ht]

{\centering \includegraphics{Manuscript_Framing_files/figure-latex/treatment-1}

}

\caption{Estimated change in attention to crime content in migration coverage, Bild vs. other newspapers. Black ticks in left panel indicate survey waves.}\label{fig:treatment}
\end{figure}

\hypertarget{measuring-frames-in-thought}{%
\subsection{Measuring Frames in Thought}\label{measuring-frames-in-thought}}

In order to assess the impact of this change in framing on public opinion, I need data on citizens' immigration attitudes, as well as their news consumption. The 2017 Election Panel by the German Longitudinal election study contains this data. It consists of a total of 15 waves from 2016-2020, with 10,000 -- 20,000 respondents per wave (Debus, Faas, and Roßteutscher 2017). Thirteen of these waves contain questions on immigration attitudes, asking respondents whether immigration of foreigners should be liberalized or restricted. Responses were recorded on a seven-point Likert scale. This variable was centered on zero (\(-3\) -- liberalize, \(3\) -- restrict; the precise wording in the survey can be found in online appendix 1.1.2).

To measure exposure to \emph{Bild} news, I use a question on newspaper consumption. The question provides respondents with a list of the six major daily newspapers plus an option ``another daily newspaper'' and asks whether they had consumed the paper in print or read articles from their website, and if so, how many days in the past week. Readers are defined as \emph{treated} if they indicate to read \emph{Bild} in the pre-treatment wave and as \emph{untreated} if they indicate not to read the tabloid in the pre-treatment wave, nor any subsequent wave\footnote{See online appendix 1 for descriptives of all mentioned variables.}.

In order to assess the effect on the association of immigration and crime, I also measure attitudes about crime using an item asking whether the governments' capabilities to fight crime should be extended\footnote{Precise question wording: "State powers to fight crime should be expanded, even if this means more surveillance of citizens."} on a 5-point Likert-scale. I also use additional dependent variables assessing attitudes about the need for immigrants to integrate into German culture (7-point scale), mentioning immigration as the most important problem (binary indicator), and a thermometer score for the radical-right \emph{AfD} (10 point scale).

\hypertarget{estimation}{%
\subsection{Estimation}\label{estimation}}

To assess the precise impact of increased attention to crime in migration coverage, I will present evidence from a \emph{difference-in-differences} (DiD) estimator to show the effect of the editorial change -- and the related content shift -- on migration attitudes:

\[
y_{iw} = \alpha + \beta_1*Post_w + \beta_2 * Post_w * BildReader_i + \phi_w + \rho_i + \epsilon_{it} 
\]

The dependent variable \(y_{iw}\) indicates respondent \(i\)'s migration attitude in a given survey wave \(w\), measured on the Likert scale described above. The conditioning variable \(BildReader_i\) is a simple binary variable indicating whether respondents read \emph{Bild} in the past week and is measured in the pre-treatment wave. \(Post_w\) indicates whether an interview took place preceding or following the editorial change. The estimator of interest is \(\beta_2\), which indicates the change in migration attitudes of \emph{Bild} readers following the editorial change, controlling for time-constant (\(\rho_i\)) and wave-specific (\(\phi_w\)) factors with fixed effects, as well as general pre-post shifts in migration attitudes (\(Post_w\)). Note that the pre-treatment differences of treatment and control group are corrected for in the individual fixed effects, as the groups are constant over time (readership is only assessed pre-treatment). As the panel data contains only one pre-treatment wave, the parallel trends assumption cannot be tested with this data directly, but assessing the trends using the GLES Longterm Panel (Roßteutscher et al. 2018) shows that \emph{Bild} and non-\emph{Bild} readers' immigration attitudes move in parallel preceding the treatment (see online appendix 3.1).

\hypertarget{expected-effect-size}{%
\subsection{Expected Effect Size}\label{expected-effect-size}}

To provide a baseline expectation regarding the effect size in experimental work, it is useful to consider an expected effect size at this point. Despite the abundance of framing effects studies, there is no common standard to assess the magnitude of framing effects. Even the correct measurement of the magnitude is a contested question, as different control groups can be compared (Druckman 2001; Chong and Druckman 2007c, 109f for a discussion). Additionally, framing effects differ based on the polarization and salience of the issue (Lecheler, De Vreese, and Slothuus 2009), repeated exposure (Chong and Druckman 2007a), the sender (Slothuus and De Vreese 2010), political knowledge (Chong and Druckman 2007b), as well as the reference of certain groups (Nelson and Kinder 1996). Generally, reported effect size around 30\% of the scale are not uncommon (Slothuus and De Vreese 2010), sometimes even over 40\% (Chong and Druckman 2007c, 104), but most results lie in between 10\% and 25\% of the scale when comparing opposing frames pushing respondents in opposite directions\footnote{As many studies do not include a control group receiving no frame, this is the most comparable metric.} (Lecheler, De Vreese, and Slothuus 2009; Nelson, Oxley, and Clawson 1997; Nelson, Clawson, and Oxley 1997; Slothuus 2008; Slothuus and De Vreese 2010).

As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge (see e.g.~the recent debate regarding nudging effects: Maier et al. 2022), reported effects likely display a selection bias towards strong treatments. The treatment in the present study can be considered rather strong, as the crime consideration is associated with a strongly negative evaluation and the relative increase in the prevalence of this content is large \footnote{5 percentage point increase compared to pre-treatment share of 11.8 percent in Bild, an over 40 percent increase.}. Given these considerations, I expect an effect of around 10\% of the scale, or 0.6 on the seven-point scale\footnote{As the scale runs from one to seven, it spans six points wide.}, which represents a conservative estimate compared to reported experimental effects. At this point, it should be mentioned that it is rather difficult to compare these experimental effects with a real world treatment. Experiments expose participants to one of two potential considerations, whereas in the real world, newspapers can only increase the relative prevalence of a given consideration.

As suggested by Lakens (2017), I also compare the estimated effect to equivalence bounds indicating the smallest effect size of interest (SESOI) in order to provide a baseline for a meaningful effect size. I define the SESOI at a 2.5\% change, or 0.15 on the seven-point scale, which represents a fraction of the conservative experimental estimate and sets a fairly low bar given the strong treatment. This SESOI can be used to define equivalence bounds. Any effect estimated to lie within these bounds with statistical significance (i.e.~a 95\%-confidence interval in-between the positive and negative effect of this size) is too small to constitute a meaningful effect, as the hypothesis that the effect reaches any size of interest can be rejected (see also Peyton 2020).

\hypertarget{results}{%
\section{Results}\label{results}}

I will first present evidence describing the effect on immigration attitudes and the association of immigration with crime attitudes. Then, I will assess the impact across time and on related variables to inspect the robustness of the estimation. The last section will trace the key assumptions in the generalization of experimental estimates discussed in the \protect\hyperlink{framing-limits}{section on the limits of framing effects}.

\hypertarget{effect-on-migration-attitudes}{%
\subsection{Effect on Migration Attitudes}\label{effect-on-migration-attitudes}}

According to the expectancy-value model, the most direct implication of increased exposure to crime frames in migration coverage should be a more restrictive attitude concerning immigration. The upper panel of figure \ref{fig:singleplot} plots the average immigration attitude among \emph{Bild}-readers compared to those never reading \emph{Bild}. The dashed vertical line indicates the timing of the change of the editor-in-chief at \emph{Bild}. Higher values indicate more restrictive migration attitudes. We can see that \emph{Bild} readers generally hold more restrictive immigration attitudes with a difference of about 0.4 on the seven-point scale. Both trends move largely parallel and seem to react to shocks similarly.

The lower panel of figure \ref{fig:singleplot} visualizes the average treatment effect, based on the model described in the \protect\hyperlink{estimation}{estimation section}. Dashed vertical lines indicate the expected effect from the experimental literature. The dotted lines indicate the equivalence boundaries/SESOI. The model suggests a clear null effect. This effect is not significantly different from zero, but significantly smaller than the above-defined SESOI of 0.15 on the seven-point Likert scale. The point estimate indicates a 0.019-point change among \emph{Bild} readers following treatment (\emph{t =} 1.33, \emph{p =} 0.22). This represents only a fraction (3.1\%) of the already conservative experimental estimate of 0.6. The finding is robust to different model specifications, as well as using data from the GLES Longterm Panel (see online appendix 3.2 and 3.4).

\begin{figure}[!ht]

{\centering \includegraphics{Manuscript_Framing_files/figure-latex/singleplot-1}

}

\caption{Top Panel: Development of Migration Attitudes across Time, by Bild-Readership. Bottom Panel: Average Treatment Effect.}\label{fig:singleplot}
\end{figure}

\hypertarget{effect-on-the-association-of-crime-and-migration-attitudes}{%
\subsection{Effect on The Association of Crime and Migration Attitudes}\label{effect-on-the-association-of-crime-and-migration-attitudes}}

Framing theory suggests that increased exposure to a specific consideration about an issue also leads to stronger association of the issue with this consideration. In the present case, this should mean that the correlation of attitudes on immigration with attitudes about crime should increase. The GLES Panel data contains a variable asking respondents whether ``the state's capabilities to fight crime should be extended, even if that would entail more surveillance'', asked in three waves overlapping with the migration attitude question.

Figure \ref{fig:corplot} shows the bootstrapped correlations of crime- and migration attitudes in treatment (\emph{Bild}-readers in pre-wave) and control group (never \emph{Bild}-readers), for each wave. The lines indicate the mean estimate, while the whiskers indicate the upper and lower 95\%-confidence interval, as defined by the 2.5 and 97.5 percentiles of the distribution of bootstrapped estimates. The dotted line indicates the counterfactual development, assuming that \emph{Bild}-readers behaved similar to the general population not reading \emph{Bild} in the absence of a change in migration framing. Surprisingly, the association of crime and immigration attitudes is initially weaker among \emph{Bild} readers. Nevertheless, the treatment group actually saw a \emph{smaller} increase in the correlation of crime and migration attitudes in the first post-treatment wave than the control group. The difference-in-differences in correlations of -0.028 is substantively rather small (9.3 percent of the average pre-treatment control group correlation) and not significantly different from zero with a bootstrapped 95\% confidence interval of {[}-0.079, 0.022{]}. In the last wave, the association decreases less than in the control group but the difference-in-differences does not reach conventional levels of significance compared to the pre-treatment wave (0.035, {[}-0.029, 0.094{]}). The association of crime and immigration attitudes did not increase among \emph{Bild} readers, relative to the control group.

\begin{figure}[!ht]

{\centering \includegraphics{Manuscript_Framing_files/figure-latex/corplot-1}

}

\caption{Correlation of crime and migration attitudes in treatment and control group, pre- (wave 1) and post-treatment (waves 3 \& 13).}\label{fig:corplot}
\end{figure}

Following (Nelson and Kinder 1996), I also regress immigration attitudes on attitudes towards crime and investigate whether this association changes as a result of the change in coverage. Similar to the differences between the groups, I find a weaker association among readers of the tabloid, but no significant or substantively large difference post-treatment or when interacted with the DiD-term (see table in online appendix 3.5). Respondents do not associate crime more strongly with migration following the change in migration coverage in \emph{Bild}.

\hypertarget{effect-on-alternative-dependent-variables}{%
\subsection{Effect on alternative dependent variables}\label{effect-on-alternative-dependent-variables}}

While opinions about immigration and their association with attitudes about crime remain unaffected, it might well be that an increased exposure to crime framing affects other variables. For example, increased attention to crime within migration coverage might increase individual perceptions of the importance of migration, or raise concerns about the integration rather than the immigration of migrants. Similarly, support for the radical-right \emph{AfD} as owner of the migration issue could increase as a result of increased exposure to this type of migration coverage.

Figure \ref{fig:multidv} displays standardized effects of the change in newspaper framing on immigration attitudes (for reference) and three related dependent variables, namely integration attitudes, the likelihood to report migration as the most important problem facing the country, as well as thermometer scores for the radical-right AfD (see online appendix 1 for precise variable descriptions). To provide reference values again, I rescale the expected experimental effect of 0.6 and SESOI of 0.15 for immigration attitudes to standard deviations. This results in baselines of 0.34 and 0.08 standard deviations, which can be considered fairly small. All estimated effects are significantly smaller than the SESOI and all associated 95\%-confidence intervals contain zero. This means we can reject the hypothesis of meaningful effect size, but cannot reject that the estimate is statistically different from zero. All estimates suggest a clear null effect.

\begin{figure}[!ht]

{\centering \includegraphics{Manuscript_Framing_files/figure-latex/multidv-1}

}

\caption{Standardised effect of change in framing on alternative dependent variables. Dotted vertical lines indicate minimal relevant effect (0.2 SD). Full models available in online appendix 3.3.}\label{fig:multidv}
\end{figure}

\hypertarget{explanations-for-resistance-to-framing}{%
\subsection{Explanations for Resistance to Framing}\label{explanations-for-resistance-to-framing}}

Although mounting experimental evidence suggests large effects of framing in the experimental context, I find robust evidence that a substantial increase in the emphasis of crime in migration coverage did not affect immigration attitudes, their association with crime, or any related variables. As outlined above, there are several key assumptions in the generalization of framing effects from experimental contexts. First, those witnessing a changing news framing might select out of the treatment instead of changing their attitudes. Second, if citizens consume many sources of political news at the same time, they might not react to a change in a single news outlet. Third, repeated exposure over time might produce effects which are not perceptable in earlier waves. Fourth, issue attitudes might only be responsive to news framing during critical periods of politicization. The following section presents evidence about each of these assumptions.

\hypertarget{selective-exposure}{%
\subsubsection{Selective Exposure}\label{selective-exposure}}

As the migration framing in \emph{Bild} becomes more conservative, this could also lead readers with more liberal migration attitudes to stop reading the newspaper, as they avoid information challenging their views. If readers selectively exposed themselves, I expect that the share of those holding liberal views about immigration reading \emph{Bild} would drop more significantly than other reader's share, as they actively select out of the newspaper. That is not the case: Liberals' and conservatives' share of readers track each other closely, with those reporting liberal migration attitudes in the first wave even reporting to read Bild at \emph{higher} shares than conservatives in later waves (see figure \ref{fig:selectionPlot}). What is interesting is that those reporting neutral migration attitudes seem to be more inclined to leave the newspaper: Neutral readership declines to a level of 57\%, around 5 percentage points below the share reported by liberals (62\%) and 3pp below the level of conservatives (60\%). Regressing individual choice to read \emph{Bild} in later waves on initial reported migration attitudes within the subsample of initial \emph{Bild} readers shows a 5\% lower chance to report Bild readership among initial neutral readers, compared to liberal readers (\(p =\) 0.003), whereas there is no significant or substantial difference for conservative readers. Surprisingly, \emph{Bild} readers reporting centrist immigration attitudes select out of the newspaper at higher rates than both conservative or liberal readers, whereas there is no significant difference between the latter two. I also tested whether the association of reading the newspaper and conservative immigration attitudes was streangthened over time. As online appendix 3.6.1 shows, there is no evidence of this process either.

\begin{figure}[!ht]

{\centering \includegraphics{Manuscript_Framing_files/figure-latex/selectionPlot-1}

}

\caption{Share of initial Bild readers reporting readership in later waves by initial migration attitude. Dashed vertical line indicates editorial change.}\label{fig:selectionPlot}
\end{figure}

\hypertarget{crowding-out}{%
\subsubsection{Crowding Out}\label{crowding-out}}

If readers did not avoid persuasive content by selecting out of the outlet, how can the absence of a framing effect be explained? A second possibility is that readers are exposed to so many other sources of political information that the change in the framing of a single outlet does not severely affect their attitudes. If that were the case, consumers with a less diverse news diet would still receive a larger relative share of their information from a single outlet and hence respond to changes in the framing of this outlet. In other words, I expect a heterogeneous treatment effect: those with very limited news diets should experience an attitudinal change, whereas this effect should decrease with increasing exposure to other outlets. The panel data used in this study contains a number of variables that allow me to measure the diversity of a respondent's news diet. Respondents could indicate on how many days they consumed newspapers other than \emph{Bild} in the preceding week. Summing these responses allows to generate a variable indicating how many newspapers other than \emph{Bild} have been consumed, weighted by the intensity of their readership (see online appendix 1.2.3 for a detailed description).

Results suggest a precise null effect of 0.006 {[}-0.05; 0.062{]} within the group of those consuming no other newspaper, which is about 1\% of the expected experimental baseline and much smaller than the SESOI of 0.15. The estimate is virtually identical for respondents indicating to consume other newspapers 1-3 times per week. Point estimates for other groups (consuming other newspapers 4-9, 10-15 or more than 15 days\footnote{A 'day' refers here to the additive days for every mentioned newspaper, that means if an individual reads newspaper A for seven days and another for six days, the total number of days will add up to thirteen.} in the preceding week) are well below the SESOI and statistically not different from zero, although estimation is less precise with higher values\footnote{See online appendix 3.6.2 for a visualization of all effects described in this section.}.

I also exploit available data on consumption of political news from TV news providers (binary indicator) and on how many days respondents informed themselves about politics on the internet. Effects in the group of those indicating to have not consumed TV news (or their online counterparts) show a similarly precise null effect (-0.073 {[}-0.167; 0.021{]}). The estimate among those not informing themselves about politics on the internet is less precise, neither being significantly different from the SESOI nor zero, however the magnitude of the point estimate of 0.079 is about half of the minimal effect size of interest. No clear pattern emerges with increasing internet exposure, in fact the only significant (but tiny) positive effect of 0.164 ({[}0.054; 0.273{]}) is observed in the group consuming political news on the internet on one out of seven days in the past week.

\begin{figure}[!ht]

{\centering \includegraphics{Manuscript_Framing_files/figure-latex/crowdout-1}

}

\caption{Heterogenous treatment effects by level of exposure to different news sources.}\label{fig:crowdout}
\end{figure}

Crowding out does not explain the absence of an effect of news framing on political attitudes. Those respondents consuming no other political information from newspapers, TV news, or online sources are no more reactive to a change in migration framing than those with a more diverse news diet.

\hypertarget{slow-updating}{%
\subsubsection{Slow Updating}\label{slow-updating}}

If readers only perceive the change in content across longer time periods, the effect should slowly unfold over time. Then, initial absence of change might bias the estimates downward and thereby mask an effect. To assess whether an effect develops over time, figure \ref{fig:migwaves} assesses the effect within split-samples for each post-wave compared to the pre-treatment wave. This allows the assessment of heterogeneous treatment effects across time. The black dots with associated confidence intervals indicate the estimated effect for each wave. The horizontal dashed line indicates the expected effect based on experimental evidence (0.6), whereas the dotted horizontal line indicates the SESOI of 0.15. The vertical dashed line indicates the timing of the editorial change. Over the course of the entire year 2017, the effect is clearly smaller than the SESOI, and includes zero. However, estimates for waves 10 and 11 in late 2018 and mid-2019 -- more than one and a half years after the editorial change -- showcase effects statistically different from zero, and including the SESOI boundary. The effects are rather small, with a point estimate of 0.09 on the seven-point Likert scale, as well as an upper boundary just above the SESOI at 0.162. The waves in late 2019 and early 2020 return to point estimates at slightly lower levels (0.067, 0.074), with confidence intervals including zero. While there is evidence of persuasion in the long term, the effect size is overall very small.

\begin{figure}[!ht]

{\centering \includegraphics{Manuscript_Framing_files/figure-latex/migwaves-1}

}

\caption{Effect on migration attitudes, by survey wave.}\label{fig:migwaves}
\end{figure}

\hypertarget{attitude-crystallisation}{%
\subsubsection{Attitude Crystallisation}\label{attitude-crystallisation}}

\begin{figure}[!ht]

{\centering \includegraphics{Manuscript_Framing_files/figure-latex/MigChange-1}

}

\caption{Change in individual immigration attitudes 2014-2018. Data taken from the GLES Longterm Panel (Roßteutscher et al. 2018).}\label{fig:MigChange}
\end{figure}

Readers did not react by selecting out of the newspaper, nor was the change in framing crowded out by other sources of information. Even long-term exposure produced rather minor effects. Another possible explanation for this resilience to framing is that individuals informed themselves about the issue and formed an attitude once the issue emerged, in this case in 2015 during the large migratory movements in Europe. If that were the case, opinions should change more in 2015 than the following period. Figure \ref{fig:MigChange} shows this statistic using GLES Longterm Panel data (Roßteutscher et al. 2018). Unfortunately, I lack data for the period preceding 2014 and the year 2015, forcing me to make one-off comparisons rather than providing a longitudinal picture. The left panel compares the absolute change in individual immigration attitudes from 2014-2016 and 2016-2018, always measured in January. That is, if a respondent held an attitude of 3 (leaning conservative) on the ten-point scale in 2014 and moved to 2 in 2016, the absolute change would be equal to 1. Immigration attitudes in the GLES sample shifted on average by a substantial 2.25 from 2014 to 2016 (lower 95\% confidence interval 2.19, upper 2.3), while they shifted significantly less in the period 2016-2018 (1.73; {[}1.69 1.78{]}). The right-hand panel shows the change across one year, comparing 2016-2017 to 2017-2018 (to be comparable, the periods have to be of equal size). Across the course of 2016, when the German public debated the integration of refugees and the events of new years eve 2016 in Cologne, individuals still display higher levels of attitudinal change (1.74; {[}1.69 1.79{]}) than 2017-2018 (1.54; {[}1.5 1.59{]}).

Although we lack evidence about the changes in migration attitudes pre-2015, these substantial and significant differences (technically differences-in-differences) suggest that, during the politicization of the issue in 2015, citizens updated their attitudes about the immigration issue, which, after the debate cooled down, crystallized into stable attitudinal positions, resistant to additional information.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

What are the limits of media power? While the answer to this question has profound implications for our understanding of elite influence in contemporary democracies, we currently lack evidence about the scope conditions of media effects. This study addresses this gap by presenting evidence from a rare shift in the migration coverage of Germany's largest tabloid, \emph{Bild}. The presented results are robust evidence that readers' immigration attitudes remained surprisingly unaffected. Estimates of attitudinal change are indistinguishable from zero and remain below minimal effect sizes in a number of specifications, dependent variables, and subgroups.

The paper presents a clear explanation for this resilience. After ruling out that readers selected out of the newspaper or that exposure to other sources conditions the effect, I find support for the explanation that attitudes became unresponsive after 2015: following this period, the average change in individual immigration attitudes decreased substantively and significantly. This suggests that the newspaper has missed a critical window to influence readers' immigration attitudes.

This finding relates to a broader experimental literature on the persuasiveness of information under different degrees of societal salience and politicization. Arceneaux and Kolodny (2009) find that campaign messages can affect political attitudes, but only on issues which are not politicized. They conclude: ``{[}p{]}eople's attitudes on these types of issues are likely to be crystallized and firm, limiting the effect of persuasive communication'' (Arceneaux and Kolodny 2009, 245). Lecheler, De Vreese, and Slothuus (2009) study this question regarding framing effects, comparing high- and low-importance issues, and show that only the latter are responsive to framing. This finding has been reproduced in realistic settings involving opposing party cues (Bechtel et al. 2015) and research about the impact of pre-treatment and exposure to conflicting frames point in similar directions (Druckman and Leeper 2012; Druckman, Fein, and Leeper 2012).

While this evidence might seem like a contradiction to the idea that attitudes change \emph{most} during the politicization of an issue, it is useful to take a longitudinal perspective. The model I propose views political issues as defined in public discourse. Once an issue emerges in public debate (usually because of an external event), problem definitions, causal explanations, and potential solutions are collectively debated. Political actors struggle to get their frames considered. Only a small subset of these frames will get to dominate public debate, shaping citizens' understanding of the issue. This collective definition will be resistant to attempts of framing and thus stabilize attitudes. Attitudinal change accelerates during the politicization of an issue, as citizens update their perceptions. Once a stable collective issue definition emerges, individuals become resistant to further information about the issue.

This model also speaks to a large body of media effects research. It suggests that the power of the news media to shape public opinion is more limited than previously thought. Even when elites try, they might not always be able to manipulate their audience's political attitudes. While studies on media effects have shown that public opinion \emph{can} be affected by changing news exposure (DellaVigna and Kaplan 2007; Foos and Bischof 2022; Grossman, Margalit, and Mitts 2022; Levendusky 2022), this study took a first step to investigate under which conditions this process takes place.

This study has several limitations, which should be addressed by future research. The argument in this paper applies to liberal democracies in general, but I present evidence from Germany, which is a Western European democracy with a relatively high-quality press, large public broadcasters, and a moderately involved electorate. While the experimental evidence from the US, Switzerland, and Denmark discussed above supports the idea that this might be a more general phenomenon, future observational studies should assess longitudinal panel data in other contexts. Similarly, migration might be a `special' issue, meaning that citizens form attitudes differently on this issue (Kustov, Laaker, and Reller 2021). Lastly, my analysis of the `crystallization' of attitudes is limited by the available data. To observe the ac- and deceleration of attitudinal change relative to issue's politicization, future research should exploit panel data from different contexts and on different issues, but ultimately more longer-term panel data tracking issue attitudes will be necessary. This is especially challenging, as attitudinal measures are usually added to survey questionnaires only \emph{after} the politicization of these issues. However, to get a full picture of the process of attitude formation, it is necessary to track the same issues irrespective of their current relevance in day-to-day politics. Otherwise, researchers will only observe issue attitudes after the relevant processes of attitude formation have taken place.

\pagebreak

\hypertarget{resources}{%
\section*{Resources}\label{resources}}
\addcontentsline{toc}{section}{Resources}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Ajzen2000}{}}%
Ajzen, Icek, and Martin Fishbein. 2000. {``{Attitudes and the Attitude-Behavior Relation: Reasoned and Automatic Processes}.''} \emph{European Review of Social Psychology} 11 (1): 1--33. \url{https://doi.org/10.1080/14792779943000116}.

\leavevmode\vadjust pre{\hypertarget{ref-Arceneaux2010}{}}%
Arceneaux, Kevin, and Martin Johnson. 2010. {``{Does Media Fragmentation Produce Mass Polarization? Selective Exposure and a New Era of Minimal Effects},''} APSA 2010 Annual Meeting Paper.

\leavevmode\vadjust pre{\hypertarget{ref-Arceneaux2009}{}}%
Arceneaux, Kevin, and Robin Kolodny. 2009. {``{The Effect of Grassroots Campaigning on Issue Preferences and Issue Salience}.''} \emph{Journal of Elections, Public Opinion and Parties} 19 (3): 235--49. \url{https://doi.org/10.1080/17457280903072916}.

\leavevmode\vadjust pre{\hypertarget{ref-Barabas2010}{}}%
Barabas, Jason, and Jennifer Jerit. 2010. {``{Are survey experiments externally valid?}''} \emph{American Political Science Review} 104 (2): 226--42. \url{https://doi.org/10.1017/S0003055410000092}.

\leavevmode\vadjust pre{\hypertarget{ref-Bechtel2015}{}}%
Bechtel, Michael M., Jens Hainmueller, Dominik Hangartner, and Marc Helbling. 2015. {``{Reality Bites: The Limits of Framing Effects for Salient and Contested Policy Issues}.''} \emph{Political Science Research and Methods} 3 (3): 683--95. \url{https://doi.org/10.1017/psrm.2014.39}.

\leavevmode\vadjust pre{\hypertarget{ref-Bennett2008}{}}%
Bennett, W. Lance, and Shanto Iyengar. 2008. {``{A new era of minimal effects? The changing foundations of political communication}.''} \emph{Journal of Communication} 58 (4): 707--31. \url{https://doi.org/10.1111/j.1460-2466.2008.00410.x}.

\leavevmode\vadjust pre{\hypertarget{ref-Busby2019}{}}%
Busby, Ethan C., D. J. Flynn, and James N. Druckman. 2019. {``{Studying Framing Effects on Political Preferences}.''} \emph{Doing News Framing Analysis II}, 27--50. \url{https://doi.org/10.4324/9781315642239-2}.

\leavevmode\vadjust pre{\hypertarget{ref-Chiang2011a}{}}%
Chiang, Chun Fang, and Brian Knight. 2011. {``{Media bias and influence: Evidence from newspaper endorsements}.''} \emph{Review of Economic Studies} 78 (3): 795--820. \url{https://doi.org/10.1093/restud/rdq037}.

\leavevmode\vadjust pre{\hypertarget{ref-Chong2007competitiveFraming}{}}%
Chong, Dennis, and James N. Druckman. 2007a. {``{A theory of framing and opinion formation in competitive elite environments}.''} \emph{Journal of Communication} 57 (1): 99--118. \url{https://doi.org/10.1111/j.1460-2466.2006.00331.x}.

\leavevmode\vadjust pre{\hypertarget{ref-Chong2007b}{}}%
---------. 2007b. {``{Framing public opinion in competitive democracies}.''} \emph{American Political Science Review} 101 (4): 636--55. \url{https://doi.org/10.1017/S0003055407070554}.

\leavevmode\vadjust pre{\hypertarget{ref-Chong2007a}{}}%
---------. 2007c. {``{Framing theory}.''} \emph{Annual Review of Political Science} 10: 103--26. \url{https://doi.org/10.1146/annurev.polisci.10.072805.103054}.

\leavevmode\vadjust pre{\hypertarget{ref-Chong2010}{}}%
---------. 2010. {``{Dynamic public opinion: Communication effects over time}.''} \emph{American Political Science Review} 104 (4): 663--80. \url{https://doi.org/10.1017/S0003055410000493}.

\leavevmode\vadjust pre{\hypertarget{ref-Chong2013}{}}%
---------. 2013. {``{Counterframing effects}.''} \emph{Journal of Politics} 75 (1): 1--16. \url{https://doi.org/10.1017/S0022381612000837}.

\leavevmode\vadjust pre{\hypertarget{ref-DeVreese2005}{}}%
De Vreese, Claes H. 2005. {``{Claes H . de Vreese News framing : Theory and typology}.''} \emph{Information Design Journal + Document Design} 12 (1): 51--62.

\leavevmode\vadjust pre{\hypertarget{ref-GLES2017Panel}{}}%
Debus, Marc, Thorsten Faas, and Sigrid Roßteutscher. 2017. {``{GLES Panel 2016-2021, Wellen 1-15}.''} K{ö}ln: GESIS Datenarchiv. \url{https://doi.org/10.4232/1.13783}.

\leavevmode\vadjust pre{\hypertarget{ref-DellaVigna2007}{}}%
DellaVigna, Stefano, and Ethan Kaplan. 2007. {``{The fox news effect: Media bias and voting}.''} \emph{Quarterly Journal of Economics} 122 (3): 1187--1234. \url{https://doi.org/10.1162/qjec.122.3.1187}.

\leavevmode\vadjust pre{\hypertarget{ref-Djourelova2020}{}}%
Djourelova, Milena. 2020. {``{Media Persuasion through Slanted Language: Evidence from the Coverage of Immigration}.''} \emph{Working Paper}, no. May.

\leavevmode\vadjust pre{\hypertarget{ref-Druckman2001}{}}%
Druckman, James N. 2001. {``{The Implications of Framing Effects for Citizen Competence}.''} \emph{Political Behavior} 23 (3): 225--56. \url{http://www.ingentaconnect.com/content/klu/pobe/2001/00000023/00000003/00369814}.

\leavevmode\vadjust pre{\hypertarget{ref-Druckman2012Bias}{}}%
Druckman, James N., Jordan Fein, and Thomas J. Leeper. 2012. {``{A source of bias in public opinion stability}.''} \emph{American Political Science Review} 106 (2): 430--54. \url{https://doi.org/10.1017/S0003055412000123}.

\leavevmode\vadjust pre{\hypertarget{ref-Druckman2012}{}}%
Druckman, James N., and Thomas J. Leeper. 2012. {``{Learning More from Political Communication Experiments: Pretreatment and Its Effects}.''} \emph{American Journal of Political Science} 56 (4): 875--96. \url{https://doi.org/10.1111/j.1540-5907.2012.00582.x}.

\leavevmode\vadjust pre{\hypertarget{ref-Foos2022}{}}%
Foos, Florian, and Daniel Bischof. 2022. {``{Tabloid Media Campaigns and Public Opinion: Quasi-Experimental Evidence on Euroscepticism in England}.''} \emph{American Political Science Review} 116 (1): 19--37. \url{https://doi.org/10.1017/S000305542100085X}.

\leavevmode\vadjust pre{\hypertarget{ref-Grossman2022}{}}%
Grossman, Guy, Yotam Margalit, and Tamar Mitts. 2022. {``{How the Ultra-Rich Use Media Ownership as a Political Investment}.''} \emph{The Journal of Politics}. \url{https://doi.org/10.1086/719415}.

\leavevmode\vadjust pre{\hypertarget{ref-NYT2017BTW}{}}%
Hermsmeier, Lukas. 2017. {``{Germany's `Boring' Election Is a Victory for the Right}.''} \href{https://www.nytimes.com/2017/09/20/opinion/germany-election-\%20merkel.html\%7B/\%\%7D0AOP-ED}{https://www.nytimes.com/2017/09/20/opinion/germany-election- merkel.html\{\textbackslash\%\}0AOP-ED}.

\leavevmode\vadjust pre{\hypertarget{ref-Iyengar2005}{}}%
Iyengar, Shanto. 2005. {``{Speaking of values: The framing of American politics}.''} \emph{Forum} 3 (3). \url{https://doi.org/10.2202/1540-8884.1093}.

\leavevmode\vadjust pre{\hypertarget{ref-Kahneman1979prospect}{}}%
Kahneman, Daniel, and Amos Tversky. 1979. {``{Prospect Theory: An Analysis of Decision under Risk}.''} \emph{Econometrica} 47 (2): 263--91.

\leavevmode\vadjust pre{\hypertarget{ref-Kinder2007}{}}%
Kinder, Donald R. 2007. {``{Curmudgeonly advice}.''} \emph{Journal of Communication} 57 (1): 155--62. \url{https://doi.org/10.1111/j.1460-2466.2006.00335.x}.

\leavevmode\vadjust pre{\hypertarget{ref-Kinder1990}{}}%
Kinder, Donald R., and Lynn M. Sanders. 1990. {``{Mimicking Political Debate with Survey Questions: The Case of White Opinion on Affirmative Action for Blacks}.''} \emph{Social Cognition} 8 (1): 73--103. \url{https://doi.org/10.1521/soco.1990.8.1.73}.

\leavevmode\vadjust pre{\hypertarget{ref-Kustov2021}{}}%
Kustov, Alexander, Dillon Laaker, and Cassidy Reller. 2021. {``{The stability of immigration attitudes: Evidence and implications}.''} \emph{Journal of Politics} 83 (4): 1478--94. \url{https://doi.org/10.1086/715061}.

\leavevmode\vadjust pre{\hypertarget{ref-Lakens2017}{}}%
Lakens, Daniël. 2017. {``{Equivalence Tests: A Practical Primer for t Tests, Correlations, and Meta-Analyses}.''} \emph{Social Psychological and Personality Science} 8 (4): 355--62. \url{https://doi.org/10.1177/1948550617697177}.

\leavevmode\vadjust pre{\hypertarget{ref-Lecheler2009b}{}}%
Lecheler, Sophie, Claes De Vreese, and Rune Slothuus. 2009. {``{Issue importance as a moderator of framing effects}.''} \emph{Communication Research} 36 (3): 400--425. \url{https://doi.org/10.1177/0093650209333028}.

\leavevmode\vadjust pre{\hypertarget{ref-Leeper2020}{}}%
Leeper, Thomas J., and Rune Slothuus. 2020. {``{How the News Media Persuades}.''} \emph{The Oxford Handbook of Electoral Persuasion}, 150--68. \url{https://doi.org/10.1093/oxfordhb/9780190860806.013.4}.

\leavevmode\vadjust pre{\hypertarget{ref-Levendusky2022}{}}%
Levendusky, Matthew S. 2022. {``{How Does Local TV News Change Viewers' Attitudes?The Case of Sinclair Broadcasting}.''} \emph{Political Communication} 39 (1): 23--38. \url{https://doi.org/10.1080/10584609.2021.1901807}.

\leavevmode\vadjust pre{\hypertarget{ref-Lippmann1922}{}}%
Lippmann, Walter. 1922. \emph{{Public Opinion}}. Toronto: Collier-MacMillan.

\leavevmode\vadjust pre{\hypertarget{ref-Maier2022}{}}%
Maier, Maximilian, Frantisek Bartos, T. D. Stanley, David R. Shanks, Adam J. L. Harris, and Eric-Jan Wagenmakers. 2022. {``{No Evidence for Construal Level Theory After Accounting for Publication Bias Maximilian}.''} \emph{Proceedings of the National Academy of Sciences of the United States of America} 119 (31): 10--11.

\leavevmode\vadjust pre{\hypertarget{ref-Maurer2019}{}}%
Maurer, Marcus, Pablo Jost, Jörg Haßler, and Simon Kruschinski. 2019. {``{Auf den Spuren der L{ü}genpresse}.''} \emph{Publizistik} 64 (1): 15--35. \url{https://doi.org/10.1007/s11616-018-00466-y}.

\leavevmode\vadjust pre{\hypertarget{ref-CologneReport2016}{}}%
Ministerium für Inneres und Kommunales des Landes Nordrhein-Westfalen. 2016. {``{Bericht {ü}ber die {Ü}bergriffe am Hauptbahnhof K{ö}ln zum Jahreswechsel}.''} \url{https://web.archive.org/web/20160116104020/http://m.mik.nrw.de/fileadmin/user\%7B/_\%7Dupload/Redakteure/Dokumente/Themen\%7B/_\%7Dund\%7B/_\%7DAufgaben/Schutz\%7B/_\%7Dund\%7B/_\%7DSicherheit/160111ssia/160111berppkoeln.pdf}.

\leavevmode\vadjust pre{\hypertarget{ref-Nelson1997Rally}{}}%
Nelson, Thomas E., Rosalee A Clawson, and Zoe Oxley. 1997. {``{Media Framing of a Civil Liberties Conflict and Its Effect on Tolerance}.''} \emph{American Political Science Review} 91 (3): 567--83.

\leavevmode\vadjust pre{\hypertarget{ref-Nelson1996}{}}%
Nelson, Thomas E., and Donald R. Kinder. 1996. {``{Issue frames and group-centrism in American public opinion}.''} \emph{Journal of Politics} 58 (4): 1055--78. \url{https://doi.org/10.2307/2960149}.

\leavevmode\vadjust pre{\hypertarget{ref-Nelson1997Psychology}{}}%
Nelson, Thomas E., Zoe M. Oxley, and Rosalee A. Clawson. 1997. {``{Toward a psychology of framing effects}.''} \emph{Political Behavior} 19 (3): 221--46. \url{https://doi.org/10.1023/A:1024834831093}.

\leavevmode\vadjust pre{\hypertarget{ref-Niggemeyer2018Bild}{}}%
Niggemeyer, Stefan. 2018. {``{"Asyl" nicht mehr ohne "Irrsinn" denken}.''} \url{https://uebermedien.de/30565/asyl-nicht-mehr-ohne-irrsinn-denken/}.

\leavevmode\vadjust pre{\hypertarget{ref-Peyton2020}{}}%
Peyton, Kyle. 2020. {``{Does Trust in Government Increase Support for Redistribution? Evidence from Randomized Survey Experiments}.''} \emph{American Political Science Review} 114 (2): 596--602. \url{https://doi.org/10.1017/S0003055420000076}.

\leavevmode\vadjust pre{\hypertarget{ref-BR2015Diekmann}{}}%
Reichart, Laury. 2015. {``{Mann, ist der Diekmann}.''} \url{https://www.br.de/puls/themen/welt/kommentar-bild-kampagne-wir-helfen-100.html}.

\leavevmode\vadjust pre{\hypertarget{ref-GLES2018LangfristPanel}{}}%
Roßteutscher, Sigrid, Rüdiger Schmitt-Beck, Harald Schoen, Bernhard Weßels, Christof Wolf, Maria Preißinger, Agatha Kratz, and Alexander Wuttke. 2018. {``{Langfrist-Panel 2013-2017 (GLES)}.''} K{ö}ln: GESIS Datenarchiv. \url{https://doi.org/10.4232/1.13018}.

\leavevmode\vadjust pre{\hypertarget{ref-Slothuus2008}{}}%
Slothuus, Rune. 2008. {``{More than weighting cognitive importance: A dual-process model of issue framing effects}.''} \emph{Political Psychology} 29 (1): 1--28. \url{https://doi.org/10.1111/j.1467-9221.2007.00610.x}.

\leavevmode\vadjust pre{\hypertarget{ref-Slothuus2010}{}}%
Slothuus, Rune, and Claes H. De Vreese. 2010. {``{Political parties, motivated reasoning, and issue framing effects}.''} \emph{Journal of Politics} 72 (3): 630--45. \url{https://doi.org/10.1017/S002238161000006X}.

\leavevmode\vadjust pre{\hypertarget{ref-sniderman2004structure}{}}%
Sniderman, Paul M., and Sean M. Theriault. 2004. {``{The Structure of Political Argument and the Logic of Issue Framing}.''} In \emph{Studies in Public Opinion}, 133--65. Princeton, NJ: Princeton University Press. \url{https://doi.org/10.2307/j.ctv346px8.9}.

\leavevmode\vadjust pre{\hypertarget{ref-Spirig2020}{}}%
Spirig, Judith. 2020. {``{Media Take-Over and Voting Behavior : Can Politician-Owned Newspapers Sway Voters ?}''}

\leavevmode\vadjust pre{\hypertarget{ref-Spiegel2017Diekmann}{}}%
{``{Springer-Mitarbeiterin wirft Diekmann Bel{ä}stigung vor}.''} 2017. \url{https://www.spiegel.de/panorama/justiz/kai-diekmann-springer-mitarbeiterin-wirft-diekmann-belaestigung-vor-a-1128822.html}.

\leavevmode\vadjust pre{\hypertarget{ref-Taber2006}{}}%
Taber, Charles S., and Milton Lodge. 2006. {``{Motivated Skepticism in the Evaluation of Political Beliefs}.''} \emph{American Journal of Political Science} 50 (3): 755--69.

\leavevmode\vadjust pre{\hypertarget{ref-DLF2018Reichelt}{}}%
Zudeick, Peter. 2018. {``{Der Krawallmodus wird ihr nicht helfen}.''} \url{https://www.deutschlandfunkkultur.de/kommentar-zur-bild-zeitung-der-krawallmodus-wird-ihr-nicht.1005.de.html?dram:article\%7B/_\%7Did=422831}.

\end{CSLReferences}

\end{document}

### 2022-09-29 paper/appendix.Rmd
keep tex, final proofread

@@
     number_sections: TRUE
+    keep_tex: true
 toc: TRUE

### 2022-09-29 paper/appendix.tex
keep tex, final proofread

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Appendix for `Framing Effects in the Wild'},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Appendix for `Framing Effects in the Wild'}
\author{}
\date{\vspace{-2.5em}15 5 2022}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{variables-decriptives}{%
\section{Variables \& Decriptives}\label{variables-decriptives}}

\hypertarget{dependent-variables}{%
\subsection{Dependent Variables}\label{dependent-variables}}

\hypertarget{overview}{%
\subsubsection{Overview}\label{overview}}

Treated Group: Bild Readers in first (and only pre-treatment) wave. Control Group: Never-Readers of Bild. Post Date: \(>=\) 01.02.2017

\begin{tabular}{l|c|c}
\hline
  & Control & Treatment\\
\hline
Gender (0 = m, 1 = f) & 0.57 & 0.44\\
\hline
Birthyear & 1971.18 & 1972.24\\
\hline
Political interest (1, 5) & 3.24 & 3.54\\
\hline
Immigration Attitude (-3, 3) & 1.00 & 1.43\\
\hline
General left-right (0-10) & 4.30 & 4.96\\
\hline
Share of AfD supporters & 0.16 & 0.22\\
\hline
AfD attitude (-5, 5) & -3.05 & -1.94\\
\hline
\end{tabular}

Note that the variable ``Birthyear'' is left-censored in the data. All respondents born before 1955 were assigned 1955 as birth year.

Table, treated vs.~untreated

\hypertarget{immigration-attitudes-1130-in-gles}{%
\subsubsection{Immigration Attitudes (1130 in GLES)}\label{immigration-attitudes-1130-in-gles}}

\hypertarget{question-text}{%
\paragraph{Question Text}\label{question-text}}

\emph{Translated:}

Now it's about immigration opportunities for foreigners. Should immigration opportunities for foreigners be made easier or restricted?

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Make it easier for foreigners to move here
\item
\item
\item
\item
\item
\item
  Restrict immigration of foreigners
\end{enumerate}

\emph{Recoded to {[}-3, 3{]}.}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Original/DE:}

Jetzt geht es um Zuzugsmöglichkeiten für Ausländer. Sollten die Zuzugsmöglichkeiten für Ausländer erleichtert oder eingeschränkt werden?

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Zuzug von Ausländern erleichtern
\item
\item
\item
\item
\item
\item
  Zuzug von Ausländern einschränken
\end{enumerate}

\hypertarget{distribution}{%
\paragraph{Distribution}\label{distribution}}

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-1-1} \end{center}

\hypertarget{integration-attitudes-1210-in-gles}{%
\subsubsection{Integration Attitudes (1210 in GLES)}\label{integration-attitudes-1210-in-gles}}

\hypertarget{question-text-1}{%
\paragraph{Question Text}\label{question-text-1}}

\emph{Translated:}

There are different opinions about how much foreigners in Germany should adapt. Some think that foreigners should fully assimilate to German culture. Others think that foreigners should be able to live according to their own culture if possible.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Foreigners should fully assimilate to German culture
\item
\item
\item
\item
\item
\item
  Foreigners should, if possible, be able to live according to their own culture
\end{enumerate}

\emph{Recoded to {[}-3, 3{]}.}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Original/DE:}

Es gibt unterschiedliche Auffassungen darüber, wie sehr sich Ausländer in Deutschland anpassen sollten. Manche denken, dass sich Ausländer vollständig an die deutsche Kultur anpassen sollten. Andere denken, Ausländer sollten auch hier möglichst nach der eigenen Kultur leben können.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Ausländer sollten sich vollständig an die deutsche Kultur anpassen
\item
\item
\item
\item
\item
\item
  Ausländer sollten möglichst nach eigener Kultur leben können
\end{enumerate}

\hypertarget{distribution-1}{%
\paragraph{Distribution}\label{distribution-1}}

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-2-1} \end{center}

\hypertarget{mip-immigration-840-in-gles}{%
\subsubsection{MIP: Immigration (840 in GLES)}\label{mip-immigration-840-in-gles}}

\hypertarget{question-text-2}{%
\paragraph{Question Text}\label{question-text-2}}

\emph{Translated:}

In your opinion, what is the most important political problem in Germany at the moment?
Please name only one \emph{single} problem.

\emph{0/1 indicator assessing mention of any migration related code (3411-3413 or 3750-3759; find coding scheme on GLES website).}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Original/DE:}

Was ist Ihrer Meinung nach gegenwärtig das wichtigste politische Problem in Deutschland?
Hinweistext: Nennen Sie bitte nur ein \emph{einziges} Problem.

\hypertarget{distribution-2}{%
\paragraph{Distribution}\label{distribution-2}}

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-3-1} \end{center}

\hypertarget{afd-scalometer-430i-in-gles}{%
\subsubsection{AfD Scalometer (430i in GLES)}\label{afd-scalometer-430i-in-gles}}

\hypertarget{question-text-3}{%
\paragraph{Question Text}\label{question-text-3}}

\emph{Translated:}

What do you think of the individual political parties in general? AfD (Alternative for Germany)

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  -5 don't think much of the party at all
\item
  -4
\item
  -3
\item
  -2
\item
  -1
\item
  0
\item
  +1
\item
  +2
\item
  +3
\item
  +4
\item
  +5 think very highly of the party
\end{enumerate}

(-71) I don't know {[}labeled as ``not known'' in the data set{]}

\emph{Recoded to {[}-5, 5{]}.}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Original/DE:}

Was halten Sie so ganz allgemein von den einzelnen politischen Parteien? AfD (Alternative für Deutschland)

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  -5 halte überhaupt nichts von der Partei
\item
  -4
\item
  -3
\item
  -2
\item
  -1
\item
  0
\item
  +1
\item
  +2
\item
  +3
\item
  +4
\item
  +5 halte sehr viel von der Partei
\end{enumerate}

(-71) kenne ich nicht {[}im Datensatz gelabelt als „nicht bekannt``{]}

\hypertarget{distribution-3}{%
\paragraph{Distribution}\label{distribution-3}}

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-4-1} \end{center}

\hypertarget{attitude-towards-fighting-crime-2880h}{%
\subsubsection{Attitude towards fighting crime (2880h)}\label{attitude-towards-fighting-crime-2880h}}

\hypertarget{question-text-4}{%
\paragraph{Question Text}\label{question-text-4}}

\emph{Translated:}

State powers to fight crime should be expanded, even if this means more surveillance of citizens.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  totally disagree
\item
  rather disagree
\item
  partly/partly
\item
  tend to agree
\item
  I totally agree
\end{enumerate}

\emph{Recoded to {[}-2, 2{]}.}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Original/DE:}

Die staatlichen Befugnisse in der Kriminalitätsbekämpfung sollten ausgeweitet werden, auch wenn das zu einer stärkeren Überwachung der Bürger führt.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  stimme überhaupt nicht zu
\item
  stimme eher nicht zu
\item
  teils/teils
\item
  stimme eher zu
\item
  stimme voll und ganz zu
\end{enumerate}

\hypertarget{distribution-4}{%
\paragraph{Distribution}\label{distribution-4}}

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-5-1} \end{center}

\hypertarget{media-exposure-variables}{%
\subsection{Media Exposure Variables}\label{media-exposure-variables}}

\hypertarget{reading-bild-1661a-in-gles}{%
\subsubsection{Reading Bild (1661a in GLES)}\label{reading-bild-1661a-in-gles}}

\hypertarget{question-text-5}{%
\paragraph{Question Text}\label{question-text-5}}

\emph{Translated:}

On how many days in the past week did you read political reports in the following newspapers or on their websites? {[}Bild{]}

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  0 Days
\item
  1 Day
\item
  2 Days
\item
  3 Days
\item
  4 Days
\item
  5 Days
\item
  6 Days
\item
  7 Days
\end{enumerate}

\emph{Recoded to {[}0,7{]}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Original/DE:}

An wie vielen Tagen haben Sie in der vergangenen Woche politische Berichte in den folgenden Zeitungen oder auf deren Internetseiten gelesen? {[}Bild{]}

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  0 Tage
\item
  1 Tag
\item
  2 Tage
\item
  3 Tage
\item
  4 Tage
\item
  5 Tage
\item
  6 Tage
\item
  7 Tage
\end{enumerate}

\hypertarget{distribution-5}{%
\paragraph{Distribution}\label{distribution-5}}

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-6-1} \end{center}

\hypertarget{treatment-indicator-reading-bild-recoded}{%
\subsubsection{Treatment Indicator (Reading Bild recoded)}\label{treatment-indicator-reading-bild-recoded}}

The treatment definition is based on the ``reading Bild'' variable described above, but refined. The treatment is binarized, such that it is zero for those not reading Bild for any day last week and one for those indicating that they read it at least one day. Respondents indicating not to read Bild in the first wave, but reading it in later waves are dropped in order to maintain an untreated control group.

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-7-1} \end{center}

\hypertarget{other-newspapers-1661-in-gles}{%
\subsubsection{Other Newspapers (1661 in GLES)}\label{other-newspapers-1661-in-gles}}

Items identical to the one asking respondents about their consumption of \emph{Bild} news in the past week have been asked regarding the consumption of other newspapers, namely \emph{Frankfurter Rundschau}, \emph{Frankfurter Allgemeine Zeitung (FAZ)}, \emph{Süddeutsche Zeitung (SZ)}, \emph{die tageszeitung (taz)}, and \emph{die Welt}. Additionally, respondents could indicate if they had consumed any other daily newspaper, and how many days last week. Based on these responses, I constructed an additive index of exposure to content from newspapers other than \emph{Bild} in the first (pre-treatment) wave. This variable measures exposure in newspaper-days, meaning that for each newspaper, the number of days it was read in the week preceding the interview was summed.

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-8-1} \end{center}

\hypertarget{tv-news-1681f-in-gles}{%
\subsubsection{TV News (1681f in GLES)}\label{tv-news-1681f-in-gles}}

\hypertarget{question-text-6}{%
\paragraph{Question Text}\label{question-text-6}}

\emph{Translated:}

I haven't watched TV news or read political reports on their websites.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  mentioned
\item
  not mentioned
\end{enumerate}

\emph{Recoded to (False = 1 (have not viewed); True = 2 (have viewed))}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Original/DE:}

Ich habe keine Fernsehnachrichten gesehen oder politische Berichte auf deren Internetseiten gelesen.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  genannt
\item
  nicht genannt
\end{enumerate}

\hypertarget{distribution-6}{%
\paragraph{Distribution}\label{distribution-6}}

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-9-1} \end{center}

\hypertarget{internet-news-consumption-1600}{%
\subsubsection{Internet News Consumption (1600)}\label{internet-news-consumption-1600}}

\hypertarget{question-text-7}{%
\paragraph{Question Text}\label{question-text-7}}

\emph{Translated:}

An wie vielen Tagen haben Sie sich in der vergangenen Woche im Internet über Politik informiert?

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  0 Days
\item
  1 Days
\item
  2 Days
\item
  3 Days
\item
  4 Days
\item
  5 Days
\item
  6 Days
\item
  7 Days
\end{enumerate}

\emph{Recoded to {[}0,7{]}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Original/DE:}

An wie vielen Tagen haben Sie sich in der vergangenen Woche im Internet über Politik informiert?

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  0 Tage
\item
  1 Tag
\item
  2 Tage
\item
  3 Tage
\item
  4 Tage
\item
  5 Tage
\item
  6 Tage
\item
  7 Tage
\end{enumerate}

\hypertarget{distribution-7}{%
\paragraph{Distribution}\label{distribution-7}}

\begin{center}\includegraphics{appendix_files/figure-latex/unnamed-chunk-10-1} \end{center}

\pagebreak

\hypertarget{treatment}{%
\section{Treatment}\label{treatment}}

\hypertarget{market-coverage-of-different-newspapers}{%
\subsection{Market Coverage of Different Newspapers}\label{market-coverage-of-different-newspapers}}

Table 1 shows the number of print copies sold and online page impressions for each newspaper per day. It becomes clear that German newspapers have a rather important position in the German news market. The tabloid \textit{Bild} has by far the largest reach, with over 1.7 Million sold newspaper daily and around 550 million web visits per month. For reference: the German Wikipedia site had less than twice as many visits (975 million) in the same time frame \footnote{Wikipedia Siteviews Analyisis: https://pageviews.wmcloud.org/siteviews/}. Bild is closely followed by the weekly published \textit{Spiegel}. The daily broadsheets sell less, and interestingly the online presence seems to be dominated by the right, given the weak presence of centre-left \textit{SZ} and left-wing \textit{taz}.

\begin{table}[!htbp] \centering
    \begin{tabular}{@{\extracolsep{5pt}} lcc}
    \\[-1.8ex]\hline
    \hline \\[-1.8ex]
    Paper & Print Sales & Web Impressions \\
     & (thousands) & (millions) \\
    \hline \\[-1.8ex]
    Bild & 1756 & 555 \\
    Spiegel & 758 & 388 \\
    FAZ & 242 & 123 \\
    SZ & 358 & 13 \\
    taz & 51 & 7 \\
    Welt & 521 & 135 \\
    \hline \\[-1.8ex]
    \end{tabular}
  \caption{Average daily sales and monthly online impressions of different newspapers in 2017. Source: Informationsgemeinschaft zur Feststellung der Verbreitung von Werbeträgern e. V. (2021). Quartalsauflagen. https://ivw.de/aw/print/qa. Table generated with stargazer.}
  \label{tab:paper_sales}
\end{table}

\pagebreak

\hypertarget{bert-classifiers}{%
\subsection{BERT Classifiers}\label{bert-classifiers}}

\hypertarget{dictionaries}{%
\subsubsection{Dictionaries}\label{dictionaries}}

In order to generate informative samples for the annotation, crime and migration content had to be oversampled from the raw data. To identify which articles likely contain relevant content, it is useful to construct dictionaries identifying the concept of interest and then use these dictionaries to assess what share of words in a given article is concerned with this content. In a first step, a seed dictionary is constructed to identify the concept of interest. To avoid missing any relevant words, word embeddings trained on large german language corpora can be used to identify terms with similar meaning. Using embeddings from a pre-trained model\textbackslash footnote\{Downloadable from \url{https://deepset.ai/german-word-embeddings}, I select the 100 most similar term for each term in the seed dictionary. Those terms associated with at least four terms in the seed dictionary (i.e.~being among the 100 most similar words for at least four words) are included in the extended dictionary. You can see the seed and extended dictionaries below.

\hypertarget{migration}{%
\paragraph{Migration}\label{migration}}

\textbf{Raw Dictionary}:

asyl, asylant, asylanten, asylantinnen, asylbewerber, asylbewerberin, asylbewerberinnen, auslander, auslanderinnen, einwanderer, einwandererin, einwandererinnen, einwandernde, einwanderung, fluchtling, fluchtende, fluchtlinge, migration, immigration, schutzsuchende, schutzbedurftige, visa, visum, zuwanderung, zuwanderer, zuwandernde, ausländer, ausländerinnen, flüchtling, flüchtende, flüchtlinge, schutzbedürftige

\textbf{Dictionary after Extension using Embeddings}:

asyl, asylant, asylanten, asylbewerber, asylbewerberin, auslander, einwanderer, einwandernde, einwanderung, migration, immigration, schutzsuchende, visa, visum, zuwanderung, zuwanderer, zuwandernde, ausländer, ausländerinnen, flüchtling, flüchtende, flüchtlinge, flüchtlingen, migranten, vertriebene, asylantinnen, asylbewerberinnen, auslanderinnen, einwandererin, einwandererinnen, fluchtling, fluchtende, fluchtlinge, schutzbedurftige, schutzbedürftige

\hypertarget{crime}{%
\paragraph{Crime}\label{crime}}

\textbf{Raw Dictionary}:

täter, täterin, polizei, verbrechen, überfall, mord, attacke, raub, straftat, ermittelt, gericht, prozess, staatsanwaltschaft, staatsanwalt, staatsanwältin, gefährder, haft, festnahme, betrug, betrüger, erstochen, opfer, anwalt, drogen, dealer, getötet, verletzung, delikt, vergewaltigung

\textbf{Dictionary after Extension using Embeddings}:

täter, täterin, polizei, verbrechen, überfall, mord, attacke, raub, straftat, ermittelt, gericht, prozess, staatsanwalt, staatsanwältin, gefährder, haft, festnahme, betrug, betrüger, erstochen, opfer, anwalt, drogen, dealer, getötet, verletzung, delikt, vergewaltigung, begangen, angeklagt, sexuelle, vorwurf, sexuellen, entführung, folter, mordes, missbrauch, morde, tötung, vergehen, beschuldigt, diebstahl, sexueller, übergriffe, brandstiftung, untreue, erpressung, bezichtigt, missbrauchs, misshandlung, ehebruch, totschlag, belästigung, nötigung, inzest, todesfolge, versuchter, staatsanwaltschaft

\hypertarget{sampling}{%
\subsubsection{Sampling}\label{sampling}}

Using the dictionaries, relevant words in each article are counted, and the share of relevant words out of all words is calculated. I then draw a stratified sample of migration articles, pulling 100 articles with no mention of migration-related terms, 100 with a moderate share of migration-related terms (25th to 75th percentile), and 100 with a high share of migration related words (above 75th percentile), for each newspaper in the sample. I repeat this process with the crime dictionary, however here I choose a higher cutoff (95th percentile) given the lower incidence of crime coverage compared to migration coverage in my sample.

\pagebreak

\hypertarget{handcoding}{%
\subsubsection{Handcoding}\label{handcoding}}

Using this sampling procedure, I generate two samples of 1000 articles for annotation by research assistants. These samples oversample from articles likely to contain coverage of interest in order to provide a relatively balanced sample for training of the classifiers. Coders were sent a shiny app designed for annotations, together with the following instructions:

\begin{quote}
The task is to identify crime content in news articles. This should always be the main topic, i.e.~articles discussing a specific incident/crime, court cases, or crime statistics. Please familiarise yourself with the examples and send me an email if you feel you need more specific instructions about the precise definition of what constitutes crime content or are unsure about a specific case (a brief definition is given in the app).
\end{quote}

Along with these instructions, coders were sent example articles which were considered to be especially difficult, annotated by me.

\begin{figure}[!htp]

{\centering \includegraphics[width=\textwidth,]{vis/HandCodingScreenshot}

}

\caption{Screenshot of Annotation App}\label{fig:unnamed-chunk-12}
\end{figure}

Annotation took place in a shiny app (see screenshot above). Coders were shown the title and text of a random news article in the sample. Then they were asked whether the article refers to the topics of crime, law and order, or public safety. Coders could see a more specific definition by clicking a button. After selecting whether the article referred to crime or not, they could either click a button to get to the next article or safe their progress to return later. Coders could also return to the preceding article in case they had selected the wrong option. The app allowed for faster annotation and minimized errors in the coding (compared to e.g.~noting the annotations in an excel sheet).

The migration annotation has been conducted by only one coder (1800 articles), while the crime articles have been annotated by two different coders separately (1000 each with 200 identical articles in each coder's sample). Annotation was very congruent across coders with an agreement for 91.5\% of annotated articles and a Krippendorff's alpha of 0.79. Conflicts were resolved by the author after inspection of the conflicting annotations.

\pagebreak

\hypertarget{classifier-fine-tuning}{%
\subsubsection{Classifier Fine-tuning}\label{classifier-fine-tuning}}

Using the annotated samples, I fine-tune BERT classifiers from Huggingface's `transformers' library for python (bert-base-german-cased), pre-trained on german Wikipedia articles, legal documents, and news articles. For each topic (crime/migration), 1400 articles served as training set, 200 each as validation and test set. Articles longer than 512 tokens (the maximum length of input for the BERT model) were truncated. I fine-tune for 10 epochs. Performance on the test set is outstanding for the migration classifier (F1 = 0.94, accuracy = 0.96, precision = 0.95, recall = 0.93) and very good for the crime classifier (F1 = 0.86, accuracy = 0.93, precision = 0.8, recall = 0.92). Both classifiers were subjected to sanity checks, before classifying first all articles according to their migration content, which returns 85691 articles (3.6\% of all articles). For this subset, crime content is identified in 6045 articles (7.1).

\begin{table}[!h]
\centering
\begin{tabular}{|p{12cm}|}
\hline
Final new years eve report of Cologne police: male groups identified \\ \hline
Police searching for Northern-african offender: asylum-raid in Dortmund! \\ \hline
Search in refugee home - mega-raid addressing asylum fraud \\ \hline
Two groups attacking each other - again bloody conflict in refugee shelter \\ \hline
Cabin fever! Violence! Mass brawls! This is behind the increase in refugee clashes \\ \hline
\end{tabular}
\caption{Headlines of five migration articles most likely to concern crime, according to BERT crime classifier. Translation by author.}
\label{tab:exampleArticles}
\end{table}

As a sanity check, and in order to exemplify the nature of the treatment, table \ref{tab:exampleArticles} shows the five \emph{Bild} articles classified as crime with the highest likelihood, out of all migration-related articles. All articles relate to both migration and crime: one mentions a police report on the mass sexual assaults on new years eve 2015 in Cologne, two discuss police raids in refugee homes, and two discuss violence in refugee shelters.

\pagebreak

\hypertarget{correcting-for-change-in-dpa-sourced-content}{%
\subsubsection{Correcting for change in DPA-sourced content}\label{correcting-for-change-in-dpa-sourced-content}}

\begin{figure}[!htp]

{\centering \includegraphics{appendix_files/figure-latex/dpaShare-1}

}

\caption{Monthly number of articles by source.}\label{fig:dpaShare}
\end{figure}

Among the changes after Reichelt's takeover as chief editor of \emph{Bild} was a severe drop in the overall number of articles published online. Figure \ref{fig:dpaShare} shows the monthly number of articles \emph{Bild} published in their online archive across time. Recall that Reichelt took over in February 2017, and briefly after - in June 2017 - the overall number of articles published decreases by over 60\%. The graph also suggests an explanation for this sudden shift: the share of articles sourced from DPA, a major German press agency alike the Associated Press, sharply decreases at the same time as the major decrease in the number of articles takes place (see top blue bars). DPA is a press agency supplying many German news outlets, which means it must have a rather unbiased or at least centrist coverage, potentially decreasing the estimate of crime frames within Bild's migration content. This would not be a problem, as long as this content is equally likely to make it to the front page. However, \emph{Bild} likely gives more weight to its own content compared to pre-written content from DPA. For this reason, the paper presented data excluding DPA content. On the other hand, the decision to discontinue buying content from DPA must have been made by Reichelt himself and is thus an outcome of the treatment. Hence, it is fruitful to assess the change including DPA-sourced content.

\pagebreak

\hypertarget{raw-crime-estimates}{%
\subsubsection{Raw Crime Estimates}\label{raw-crime-estimates}}

\begin{figure}[!htp]

{\centering \includegraphics{appendix_files/figure-latex/treatmentDPAcorr-1}

}

\caption{Change in share of crime content in newspaper coverage, excluding DPA-sourced news content. Left panel: quarterly share across time, Bild compared to other newspapers' average. Right panel: difference-in-differences estimates of change in newspaper coverage compared to other newspapers, controlling for source of content.}\label{fig:treatmentDPAcorr}
\end{figure}

The left panel of figure \ref{fig:treatmentDPAcorr} displays the quarterly share of migration articles discussing crime for \emph{Bild} compared to all other newspapers. A depression is visible in 2016-2017 which was not visible in the corrected data. The share of crime content in \emph{Bild}'s migration coverage strongly increases a few months following the treatment, when the share of DPA-sourced content severely drop. The gap between \emph{Bild} and all other newspapers increases, and this increased difference persists. This change becomes even more visible in the right-hand panel, which shows a difference-in-differences estimate of the change of the share of crime news in a newspapers migration content, this time controlling for whether the content is DPA-sourced or not. The general picture is quite similar to the original estimate in the paper, as migration coverage only increases in \emph{Bild}, while all other outlets remain rather stable on this metric. In the estimate including DPA content, the share of migration coverage devoted to crime increases by an even stronger 6 percentage points, which still constitutes a very substantial increase. Both ways of handling the data suggest a strong increase in the emphasis of crime in migration coverage.

\pagebreak

\hypertarget{migration-attention-over-time}{%
\subsubsection{Migration Attention over Time}\label{migration-attention-over-time}}

\begin{figure}[!htp]

{\centering \includegraphics{appendix_files/figure-latex/migSalience-1}

}

\caption{Attention to Migration in Different News Outlets}\label{fig:migSalience}
\end{figure}

Figure \ref{fig:migSalience} shows that the prevalence of migration content as classified by the first Bert model generally follows expectations. Three distinct peaks can be observed: first during the migratory movements to Germany in 2015, then after the sexual assaults on new years eve in 2016, and during the conflict regarding migration policy within the conservative party alliance CDU/CSU in 2018. Prevalence differs strongly across newspapers, with \emph{Bild} having the lowest prevalence of migration content. This is likely due to their tabloid format, which emphasizes entertainment over news and politics content. The left-leaning SZ shows the highest attention to migration (during the peak in September 2015, nearly every second article is concerned with migration). This is likely the result of a website highly focused on politics.

\pagebreak

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{parallel-trends}{%
\subsection{Parallel Trends}\label{parallel-trends}}

\begin{figure}[!htp]

{\centering \includegraphics{appendix_files/figure-latex/parallelTrends-1}

}

\caption{Migration Attitude among Bild-readers compared to non-readers across Time}\label{fig:parallelTrends}
\end{figure}

Figure \ref{fig:parallelTrends} shows the development of migration attitudes among a panel of Bild readers\footnote{Readership was measured in a single wave in late 2015.} and non-readers across time, recorded in the German Longitudinal Election Study's Longterm Panel (Roßteutscher et al. 2018). This is a far smaller sample with a limited time frame and hence less useful for the precise estimation of the effects of changing migration framing. The plot shows that both groups move along a similar long-term trend, slowly becoming more conservative, while moving into similar directions along the way. The only difference between the two groups is that Bild readers seem to be more conservative in late 2015 (note that only the last three interviews were conducted in January 2016). However this deviation lies well within the 95\% confidence interval and those not reading Bild move in a similar direction, albeit less strongly. The parallel trends assumption seems to be generally met.

\pagebreak

\hypertarget{robustness-of-main-effect}{%
\subsection{Robustness of Main Effect}\label{robustness-of-main-effect}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2386}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1477}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1477}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1477}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1477}}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1705}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Model 1
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Model 2
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Model 3
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Model 4
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Model 5
\end{minipage} \\
\midrule
\endhead
(Intercept) & 0.999*** & & & & \\
& (0.016) & & & & \\
postTRUE & -0.061*** & -0.027* & -0.027* & -0.103*** & -0.103*** \\
& (0.017) & (0.011) & (0.011) & (0.012) & (0.004) \\
treatTRUE & 0.434*** & & & & \\
& (0.032) & & & & \\
postTRUE × treatTRUE & 0.067+ & 0.018 & 0.018 & 0.019 & 0.019 \\
& (0.035) & (0.023) & (0.023) & (0.023) & (0.014) \\
Num.Obs. & 102373 & 102373 & 102373 & 102373 & 102373 \\
R2 & & & & & \\
R2 Adj. & & & & & \\
R2 Within & & & & & \\
R2 Pseudo & 0.003 & 0.404 & 0.404 & 0.407 & 0.407 \\
AIC & 405382.7 & 275755.8 & 275755.8 & 274534.5 & 274534.5 \\
BIC & 405420.9 & 434431.6 & 434431.6 & 433296.1 & 433296.1 \\
Log.Lik. & -202687.360 & -121238.885 & -121238.885 & -120619.252 & -120619.252 \\
Std.Errors & Standard & by: ID & by: ID & by: ID & by: ID \& Wave \\
FE: ID & & X & X & X & X \\
FE: Wave & & & & X & X \\
\bottomrule
\end{longtable}

\textbf{Note:}
\^{}\^{} + p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001

\pagebreak

\hypertarget{multiple-dv-table}{%
\subsection{Multiple DV Table}\label{multiple-dv-table}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2018}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2018}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2018}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2018}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AfD thermometer
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
MIP: Migration
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Integration Attitude
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Migration Attitude
\end{minipage} \\
\midrule
\endhead
postTRUE & -0.028*** & -0.090*** & 0.059*** & -0.058*** \\
& (0.002) & (0.003) & (0.003) & (0.002) \\
postTRUE × treatTRUE & -0.021* & -0.007 & -0.008 & 0.011 \\
& (0.007) & (0.010) & (0.011) & (0.008) \\
Num.Obs. & 119245 & 86636 & 76633 & 102373 \\
R2 & & & & \\
R2 Adj. & & & & \\
R2 Within & & & & \\
R2 Pseudo & 0.636 & 0.308 & 0.434 & 0.570 \\
AIC & 155449.1 & 202562.0 & 155613.8 & 158189.8 \\
BIC & 315810.7 & 354356.8 & 309840.9 & 316951.4 \\
Log.Lik. & -61173.562 & -85080.017 & -61127.913 & -62446.895 \\
Std.Errors & by: lfdn \& wave\_ctrl & by: lfdn \& wave\_ctrl & by: lfdn \& wave\_ctrl & by: lfdn \& wave\_ctrl \\
FE: lfdn & X & X & X & X \\
FE: wave\_ctrl & X & X & X & X \\
\bottomrule
\end{longtable}

\textbf{Note:}
\^{}\^{} + p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001

\pagebreak

\hypertarget{effect-in-longterm-panel}{%
\subsection{Effect in Longterm-Panel}\label{effect-in-longterm-panel}}

It is also possible to estimate the effect of the change in editorship from the smaller and less frequent long-term panel, with a smaller sample size (between 1,700 and 5,000). The only post-treatment wave has been conducted from September to December 2017. The question wording of the variable measuring immigration attitudes is identical to the Panel study used in the main paper, however responses have been recorded on a 11-point scale. Treatment was defined similar to the main paper, with respondents who indicated to read \emph{Bild} in the pre-treatment wave in the treatment group, and respondents indicating never to read \emph{Bild} in the control group.

\begin{longtable}[]{@{}lc@{}}
\toprule
& Model 1 \\
\midrule
\endhead
postTRUE & 0.178* \\
& (0.078) \\
postTRUE × treatTRUE & -0.233 \\
& (0.216) \\
Num.Obs. & 3255 \\
R2 & \\
R2 Adj. & \\
R2 Within & \\
R2 Pseudo & 0.264 \\
AIC & 13743.6 \\
BIC & 19271.5 \\
Log.Lik. & -5963.811 \\
Std.Errors & by: lfdn \\
FE: Wave & X \\
FE: ID & X \\
\bottomrule
\end{longtable}

\textbf{Note:}
\^{}\^{} + p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001

The model suggests a liberalizing effect of -0.23 (2.33\% of the scale range), which is not significant (lower CI -0.66; upper CI 0.19), suggesting a null effect, similar to the main model.

\pagebreak

\hypertarget{association-model}{%
\subsection{Association Model}\label{association-model}}

\begin{longtable}[]{@{}lc@{}}
\toprule
& Model 1 \\
\midrule
\endhead
Crime Attitude & 0.478*** \\
& (0.015) \\
Crime Attitude X Post & 0.000 \\
& (0.017) \\
Crime Attitude X Bild Reader & -0.106*** \\
& (0.030) \\
Crime Attitude X Post X Bild & 0.004 \\
& (0.037) \\
Num.Obs. & 33164 \\
Std.Errors & by: ID \\
\bottomrule
\end{longtable}

\textbf{Note:}
\^{}\^{} + p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001

\pagebreak

\hypertarget{readership-models}{%
\subsection{Readership models}\label{readership-models}}

\hypertarget{inward-selection}{%
\subsubsection{Inward selection}\label{inward-selection}}

\begin{figure}[!htp]

{\centering \includegraphics{appendix_files/figure-latex/inselection-1}

}

\caption{Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95 percent confidence intervals, dashed (red) vertical line indicates editorial change.}\label{fig:inselection}
\end{figure}

\hypertarget{resources}{%
\section*{Resources}\label{resources}}
\addcontentsline{toc}{section}{Resources}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-GLES2018LangfristPanel}{}}%
Roßteutscher, Sigrid, Rüdiger Schmitt-Beck, Harald Schoen, Bernhard Weßels, Christof Wolf, Maria Preißinger, Agatha Kratz, and Alexander Wuttke. 2018. {``{Langfrist-Panel 2013-2017 (GLES)}.''} K{ö}ln: GESIS Datenarchiv. \url{https://doi.org/10.4232/1.13018}.

\end{CSLReferences}

\end{document}

### 2022-12-19 paper/Manuscript_Framing.Rmd
fix estimator description

--- 2022-09-29 paper/Manuscript_Framing.Rmd
@@
 
-To assess the precise impact of increased attention to crime in migration coverage, I will present evidence from a *difference-in-differences* (DiD) estimator to show the effect of the editorial change – and the related content shift – on migration attitudes:
+To assess the precise impact of increased attention to crime in migration coverage, I will present evidence from a two-way fixed effects (TWFE) *difference-in-differences* (DiD) estimator to show the effect of the editorial change – and the related content shift – on migration attitudes:
 
 $$
-y_{iw} = \alpha + \beta_1*Post_w + \beta_2 * Post_w * BildReader_i + \phi_w + \rho_i + \epsilon_{it} 
+y_{w,i} = \alpha + \beta * D_{w,i}+ \phi_w + \rho_i + \epsilon_{w,i} 
 $$
 
-The dependent variable $y_{iw}$ indicates respondent $i$'s migration attitude in a given survey wave $w$, measured on the Likert scale described above.
-The conditioning variable $BildReader_i$ is a simple binary variable indicating whether respondents read *Bild* in the past week and is measured in the pre-treatment wave.
-$Post_w$ indicates whether an interview took place preceding or following the editorial change.
-The estimator of interest is $\beta_2$, which indicates the change in migration attitudes of *Bild* readers following the editorial change, controlling for time-constant ($\rho_i$) and wave-specific ($\phi_w$) factors with fixed effects, as well as general pre-post shifts in migration attitudes ($Post_w$).
-Note that the pre-treatment differences of treatment and control group are corrected for in the individual fixed effects, as the groups are constant over time (readership is only assessed pre-treatment).
-As the panel data contains only one pre-treatment wave, the parallel trends assumption cannot be tested with this data directly, but assessing the trends using the GLES Longterm Panel [@GLES2018LangfristPanel] shows that *Bild* and non-*Bild* readers' immigration attitudes move in parallel preceding the treatment (see appendix 3.1).
+The dependent variable $y_{w,i}$ indicates respondent $i$'s migration attitude in a given survey wave $w$, measured on the Likert scale described above.
+The treatment variable $D_{w,i}$ is a simple binary variable indicating whether respondents are treated, specifically it indicates post-treatment whether respondents indicated to read *Bild* preceding the editorial change.
+This variable is identical to the interaction of a variable indicating whether an interview took place post-treatment and whether someone reported *Bild* readership pre-treatment.
+The estimator of interest is $\beta$, which indicates the change in migration attitudes of *Bild* readers following the editorial change, controlling for time-constant ($\rho_i$) and wave-specific ($\phi_w$) factors with fixed effects.
+Note that the pre-treatment differences of treatment and control group are corrected for in the individual fixed effects, as the groups are constant over time (readership is only assessed pre-treatment), while any time trends are corrected for in the wave fixed effects ($\phi_w$).
+As the panel data contains only one pre-treatment wave, the parallel trends assumption cannot be tested with this data directly, but assessing the trends using the GLES Longterm Panel [@GLES2018LangfristPanel] shows that *Bild* and non-*Bild* readers' immigration attitudes move in parallel preceding the treatment (see online appendix 3.1).
 

### 2023-04-13 pres/Pres_ETH.qmd
prepare Job Talk

---
title: "<font size=12>Do Framing Effects Persist Beyond the Lab?</font>"
subtitle: "Job Market Presentation | <font color='#801414'> Public Policy Group & Immigration Policy Lab </font> | ETH Zürich"
author: "Nicolai Berk"
date: "2023-03-14"
date-format: "DD.MM.YYYY"
format: 
  revealjs:
    theme: [simple, custom.scss]
    embed-resources: true
editor: visual
bibliography: "C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib"
---

## News Framing

```{r setup}

knitr::opts_chunk$set(echo = F, cache = T, warning = F, fig.align='center', out.width="100%")

# packages
library(tidyverse)
library(here)
library(patchwork)
library(fontawesome)

# load self-made functions
for (filename in list.files(here("code/functions"))){
  source(here(paste0('code/functions/', filename)))
}

# define theme params

ipl_red <- "#801414"
ipl_gray <- "#5B5B66"
ipl_bg <- '#f0f0f0'

theme_ipl <-
  theme_minimal() +
  theme(panel.background = element_rect(fill = ipl_bg, colour = ipl_bg),
        plot.background = element_rect(fill = ipl_bg, colour = ipl_bg),
        legend.key = element_rect(fill = ipl_bg))

```

![](vis/foxbanner.png){.absolute width="500" top="250" left="0"}

![](vis/cnnborder.png){.absolute width="500" top="250" right="0"}

## Evidence on Framing {#lit}

<br>

::: incremental
<!-- -   Media effects literature mostly concerned with changes in exposure or general "slant".\ -->
<!-- <font size="5"> [@Ash2020covid; @Foos2020; @Gentzkow2010]</font> -->
-   Evidence almost [exclusively from survey experiments]{style="background-color: #801414; color: #f0f0f0;"}.
-   Unclear how these generalize.\
<font size="5"> [@Barabas2010; @Hainmueller2015] </font>
-   Real world is messy:
    -   **selective exposure** <font size="5"> [@Druckman2012] </font>
    -   **weak persistence over time** <font size="5"> [@Lecheler2011] </font>
    -   **crowding out** <font size="5"> [@Chong2013] </font>
    -   **attitude crystallization** <font size="5"> [@Bechtel2015] </font>

:::

---

<br><br><br><br>

### Do Framing Effects Generalize?

---

### Editorial Change at Germany's Largest Tabloid {.smaller}

<br>

::: incremental

-   Feb 2017: *Bild* chief editor leaves over allegations of sexual misconduct.
-   New editor: "we must talk about criminal migrants".
-   Most likely case:
    - Largest German outlet.\
    <font size="6" color="#801414">1.7M print sales and 18.5M web impressions per day.</font>
    - Seen as highly influential on public opinion.
    - Very strong frame (crime) & large change.

:::

# Treatment

## Measuring Crime Framing {#mediadata}

<br>

- Web-scrape 2.5M news articles.
- Train two classifiers (crime/migration):
  + Draw two [stratified samples](#imbalance) of 1800 articles.
  + Annotate 2x1800 articles using [app interface](#app).
  + Fine-tune [BERT](#bert) transformer models.

::: aside
[Examples](#example)
:::

## Performance

<br>

::: columns
::: {.column width="50%"}
::: {.callout-note icon="false"}
## Migration classifier

-   Accuracy: 0.96
-   **F1: 0.94**
-   Recall: 0.93
-   Precision: 0.95

**3.6%** of articles about migration.
:::
:::

::: {.column width="50%"}
::: {.callout-note icon="false"}
## Crime classifier

-   Accuracy: 0.93
-   **F1: 0.86**
-   Recall: 0.92
-   Precision: 0.8

**7%** of migration content about crime.
:::
:::
:::

## Bild's Migration Coverage

<br>

```{r trendplot}

TreatmentTrendPlot(size = 2, dpa_corrected = F, palette = c(ipl_red, ipl_gray), ) +
  theme_ipl

```

# Effect

## Estimation: Difference-in-Differences {#estimation}

::: columns
::: {.column width="30%"}
```{r didtheory}

data.frame(
  X = factor(c("pre", "pre", "post", "post", "pre", "post"),
             levels = c("pre", "post")),
  Y = c(1.1, 1.3, 1.5, 1.9, 1.3, 1.7),
  universe = factor(c(rep("counterfactual", 4), rep("factual", 2)),
                    levels = c("counterfactual", "factual")),
  group = factor(c("untreated", "treated", "untreated", 
                   "treated", "untreated", "untreated"),
                 levels = c("treated", "untreated"))
) %>% 
  ggplot(aes(x = X, y = Y, 
             lty = universe, col = group,
             group = paste0(universe, group))) +
  geom_line(size = 2) + 
  geom_point(size = 6) +
  ylab("") + xlab("") +
  theme(axis.text.y = element_blank(), 
        legend.position = "None") +
  theme_void() +
  theme(panel.background = element_rect(fill = ipl_bg, colour = ipl_bg),
        plot.background = element_rect(fill = ipl_bg, colour = ipl_bg),
        legend.position = "None") +
  scale_color_manual(values = c(ipl_red, ipl_gray))
```
:::

::: {.column width="70%"}
<br>

<font size="6" color="#801414"> $y_{w,i} = \alpha + \beta * D_{w,i}+ \phi_w + \rho_i + \epsilon_{w,i}$ </font>
:::
:::

-   Attitudinal data from [GLES Panel](#gles). \
<font size="6">(ca. 15,000 respondents in 15 waves)</font>
-   Treated: *Bild* readers in pre-treatment wave.
-   Control: *never*-Bild-readers.
-   ATE = $\Delta$ attitude Bild readers - $\Delta$ control group.
-   Parallel Trends: [pre](#sec-trends-pre), [post](#sec-trends-post)

# Results

## Effect on Main Dependent Variables {#mainresults}

<br>

```{r didest, fig.width=8, fig.height=3}

DiDPlot(col = ipl_red, multi = T, scaled = T) +
  theme_ipl

```

::: aside
Dashed lines represent lower bound of experimental estimates, dotted lines indicate Smallest Effect Size of Interest [@Lakens2017].  [More...](#sesoi)
:::

## Null Effect Explanation {#ipl}

<br>

- Sample Size: >100k observations, >15k individuals.
- Measurement:
  + Independent: [LDA](#lda) confirms increase in attention to crime in Bild.
  + Dependent: Multiple outcomes, different survey, same result.
- Spillover: possible, yet attitudes more liberal.

:::aside
See @alrababa2022
:::

## Theoretical Explanations {#why}

<br>

::: {.callout-important icon="false"}
## ❌ [Selective Exposure](#sec-explain1)
:::

::: {.callout-important icon="false"}
## ❌ [Crowding out](#sec-explain3)
:::

::: {.callout-important icon="false"}
## ❌ [Over-time effects](#sec-explain2)
:::

. . .

::: {.callout-warning icon="false"}
## ❓[Attitude Crystallisation](#sec-explain4)

Far less Attitudinal Change 2016-18 than 2014-16

:::

## Contributions

<br>

. . .

::: callout-important
## No Framing Effects in Most-Likely Case

***If*** any Effects, only During Brief **Windows of Opportunity**

:::

<!-- . . . -->

<!-- ::: callout-tip -->
<!-- ## Conditions of Media Effects: Politicization -->
<!-- ::: -->

. . .

::: callout-tip
## Conditions of Media Effects: Politicization <font size="5">[@Spirig2020]</font>

:::

. . .

::: callout-tip
## Migration Attitudes: Stability and Change <font size="5">[@Kustov2021]</font>
:::

. . .

::: callout-tip
## Measurement of Framing with Supervised Machine Learning
:::

# Thank you

## Research Agenda {.smaller visibility="uncounted"}

:::: columns
::: {.column width="75%"}

::: {.callout-ipl icon="false"}
## Media and Migration

- [<font color="black">Does Migration Coverage Always Benefit the Radical Right?</font>](https://raw.githubusercontent.com/nicolaiberk/FrameCompetition/main/pres/Presentation.pdf)
- The Effect of Radical Right Violence on Media Coverage about Migration \
(with W. Krause)
<!-- - [Does Framing Affect Voting Behaviour?](https://nicolai-berk.shinyapps.io/wzb-221214/#/title-slide) -->
<!-- - [<font color="black">How Elite Behaviour affects Individual Vaccination Decisions</font>](https://raw.githubusercontent.com/nicolaiberk/PartyVac/main/pres/Presentation.pdf) -->

:::

::: {.callout icon="false"}
## NLP & ML

- [<font color="black">Measuring Party Accommodation with Supervised Machine Learning</font>](https://raw.githubusercontent.com/nicolaiberk/bild/main/paper/Manuscript_Framing.pdf)
- Bias and Imbalance in Content Classification
<!-- - [Measuring Media Bias with Cross-Domain Deep Learning (with T. Arend)](https://raw.githubusercontent.com/nicolaiberk/nlpdl_project/main/reports/final-report-latex/final-report.pdf) -->

:::

::: {.callout-ipl icon="false"}
## Potential IPL Projects

- Does Media Coverage about Migrants affect Integration Outcomes?
- Efficient Maintenance of Classification Pipelines w. Drift Detection & Active Learning
- Government Communication about Planned Refugee Homes & Local Acceptance?
- Do Local Anti-Immigration Movements Depress Immigration at an Economic Cost?

:::
:::

::: {.column width="25%"}

::: {.right}

<br>
<br>
<br>

#### Contact

[`r fa("laptop")`](nicolaiberk.com) \| [`r fa("envelope")`](mailto:nicolai.berk@gmail) \| [`r fa("github")`](https://github.com/nicolaiberk) \| [`r fa("twitter")`](twitter.com/nicolaiberk)

:::

::: {.absolute bottom=-10 right=-30 width=250}

```{r, fig.height=5, fig.width=5, fig.align="right"}
plot(qrcode::qr_code("nicolaiberk.com"), col = c(ipl_bg, ipl_red))
```

:::
:::
::::

# Resources {visibility="uncounted"}

::: {#refs}
:::

# Appendix {visibility="uncounted"}

## Why [BERT](https://huggingface.co/docs/transformers/model_doc/bert) {#bert visibility="uncounted"}

<br>

- Pre-trained on large language corpus. <font size="5">([Details](https://www.deepset.ai/german-bert))</font> \
<font color='#801414'>➡ less training data, better performance.</font>
- Uses **contextual** embeddings. \
<font color='#801414'>➡ "fish & **chips**" vs "poker **chips**".</font>
- Outperforms humans on [SQuAD](https://rajpurkar.github.io/SQuAD-explorer/).
- SOTA in text classification.

<br>

[BACK](#mediadata)

![](vis/bertarch.png){.absolute width=400 bottom=0 right=0}

## Dealing with Imbalance {#imbalance visibility="uncounted"}

::: columns
::: {.column width="70%"}

::: callout-important
## Imbalance: Little Information in Random Samples
:::

::: callout-tip
## Informed Approach

- Generate dictionary related to outcome class.
- Extend using word embeddings to minimize bias.
- Count occurences in data.
- Draw stratified sample for subsequent training.

**Ensures overweighting of minority class.**

:::
:::

::: {.column width="30%"}

<br>

```{r, fig.height=4, fig.width=3}

counts <- 
  round(rbeta(1000, 0.2, 0.5)* 10, 0) %>%
  as_tibble() %>% 
  mutate(sample_id = cut(value, 
                         c(-Inf, 0.5, 2.5, Inf), 
                         c(1, 2, 3)),
         id = 1:n())

counts$sample_T <- rbinom(nrow(counts), 1, 0.05*(counts$value+1))

counts %>% 
  ggplot(aes(x = value)) +
  geom_histogram(aes(fill = as.character(sample_T)), bins=3) +
  theme_ipl +
  scale_fill_manual(values = c(ipl_gray, ipl_red),
                    labels = c("not sampled", "sampled")) +
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  xlab("# of dict terms in text") + ylab("Observations")

```

:::
:::

[BACK](#mediadata)

## Effective Annotation using App {#app visibility="uncounted"}

```{r, fig.cap="Screenshot of Annotation App", out.width = "\\textwidth"}

knitr::include_graphics("vis/HandCodingScreenshot.png")

```

[BACK](#mediadata)

## Five most Representative Articles {.smaller visibility="uncounted" #example}

<br>

```{r crimeExamples, results="asis"}

TenMostCrime()

```

<br>

[BACK](#mediadata)

## Prevalence DPA {visibility="uncounted"}

```{r dpa}

data.table::fread(here("data/raw/newspapers/_bild_articles.csv"), 
                  encoding = "UTF-8") %>% 
  mutate(
    dpa = str_detect(text, "(dpa)")
  ) %>% 
  mutate(month = lubridate::floor_date(date, "month")) %>% 
  mutate(
    dpa = ifelse(dpa, "DPA", "Original")
  ) %>%
  ggplot(aes(x = month, fill = dpa)) +
  geom_bar() +
  theme_minimal() +
  ggtitle("Monthly number of articles, Bild online", "By origin, 2013-2019") + 
  xlab("") + ylab("N") +
  scale_fill_manual(name = "Source",
                    values = c(ipl_red, ipl_gray)) +
  theme_ipl

```

## Attention to Immigration {.smaller visibility="uncounted"}

::: {.panel-tabset}

## incl. DPA

```{r migSalience}

MigSaliencePlot(papers = c("Bild"), 
                dpa_corrected = F) +
  geom_vline(xintercept = as.Date("2017-02-01"), col = "red", lty = 2) +
  theme_ipl

```

## excl. DPA

```{r migSalienceNODPA}

MigSaliencePlot(papers = c("Bild"), 
                dpa_corrected = T) +
  geom_vline(xintercept = as.Date("2017-02-01"), col = "red", lty = 2) +
  theme_ipl

```

:::

## Treatment excl. DPA content {.smaller visibility="uncounted"}

::: {.panel-tabset}

## incl. DPA

```{r treatment}

TreatmentTrendPlot(dpa_corrected = F, palette = c(ipl_red, ipl_gray)) +
  theme_ipl + 
  TreatmentDiDPlot(dpa_corrected = F, palette = c(ipl_red, ipl_gray)) +
  theme_ipl +
  theme(legend.position = "None")

```

## excl. DPA

```{r treatmentNODPA}

TreatmentTrendPlot(dpa_corrected = T, palette = c(ipl_red, ipl_gray)) +
  theme_ipl + 
  TreatmentDiDPlot(dpa_corrected = T, palette = c(ipl_red, ipl_gray)) +
  theme_ipl +
  theme(legend.position = "None")

```

:::

## Alternative Measurement: LDA {visibility="uncounted" #lda}

![](vis/topicChanges.png)

::: aside
[BACK](#ipl)
:::

## Dependent Variables {#gles visibility="uncounted"}

### German Longitudinal Election Study (GLES) Panel <font size="5"> [@GLES2017Panel]</font>

<!-- ::: columns -->
<!-- ::: {.column width="60%"} -->

-   [Immigration Attitudes](#secdv1)
-   [Integration Attitudes](#secdv1)
-   [Crime Attitudes](#secdv2)
-   [Support for RR](#secdv2)
-   [Most Important Problem](#secdv2)

[BACK](#estimation)

<!-- ::: -->

<!-- ::: {.column width="40%"} -->

![](vis/gles.png){.absolute height=500 bottom=0 right=0}

<!-- ::: -->
<!-- ::: -->

## Dependent Variables: Immigration {#secdv1 visibility="uncounted"}

::: columns
::: {.column width="50%"}
::: {.callout-note icon="false"}
## Immigration Attitudes

-   **Opportunities for immigration** of foreigners should be
    -   extended (-3) or
    -   restricted (3).
-   Asked in **13** waves (1 pre).
:::
:::

::: {.column width="50%"}
::: {.callout-note icon="false"}
## Integration Attitudes

-   Foreigners should...
    -   completely **adapt to German culture** (-3) or
    -   be able to live according to their own culture (3).
-   Asked in **4** waves (1 pre)
:::
:::
:::

[BACK](#gles)

## Dependent Variables: Other {#secdv2 visibility="uncounted"}

::: columns
::: {.column width="50%"}
::: {.callout-note icon="false"}
## Support for radical-right AfD

-   Attitude towards **AfD**
    -   strongly dislike (-5) to
    -   strongly like (5).
-   Asked in **14** waves (1 pre)
:::

::: {.callout-note icon="false"}
## MIP: Migration

-   Binary indicator, 1 if most important problem is migration.
:::
:::

::: {.column width="50%"}
::: {.callout-note icon="false"}
## Attitude towards crime policy

-   "state should get **more competences in fighting crime**, even if this means more surveillance"
    -   strongly disagree (1) to
    -   strongly agree (5).
-   Asked in **4** waves (1 pre)
:::
:::
:::

[BACK](#gles)

## Parallel Trends: Pre {#sec-trends-pre visibility="uncounted"}

```{r pretrend, warning = F}
ParallelTrendsPlot(color_palette = c(ipl_gray, ipl_red), multiplot = F) +
  theme_ipl
```

[BACK](#estimation)

::: aside
Data from GLES Longterm Panel [@GLES2018LangfristPanel]
:::

## Parallel Trends: Post {#sec-trends-post visibility="uncounted"}

```{r posttrend}
DescPlot(legend_position = "bottom", colorful = T, col_palette = c(ipl_red, ipl_gray)) +
  theme_ipl
```

[BACK](#estimation)

## Group Differences {.smaller visibility="uncounted"}

<br>

```{r bildtable}

GroupedTable(color_palette = c(ipl_red, ipl_bg))

```

## Expected Effect Size {#sesoi visibility="uncounted"}

<br>

-   most results in framing literature between 10% and 25% of range, up to \>40%.
-   **expected effect** to meet experimental studies at 10% of range = **0.6** on 7-point Likert or **0.34 SD**.
-   **Smallest Effect Size Of Interest** [SESOI, @Lakens2017] of 2.5% of range = **0.15** or **0.08 SD**.

::: aside
Share of scale reported due to often unreported standard deviations.
:::

[BACK](#mainresults)

## Association of Migration with Crime {#assoc visibility="uncounted"}

<br>

```{r assoc, fig.height=3.5, fig.width=8, fig.cap="Bootstrapped Correlation of Crime and Migration Attitude, per wave."}

MigCrimeCorPlotBS(cols = c(ipl_gray, ipl_red)) +
  theme_ipl

```

## Selective Exposure {#sec-explain1 visibility="uncounted"}

<br>

```{r outselect, fig.height=3.5, fig.width=8, fig.cap="Share of Bild readers indicating to have consumed Bild, by wave."}
OutSelection(color_palette = MetBrewer::met.brewer("NewKingdom", 3)[c(2, 3, 1)]) +
  theme_ipl
```

[BACK](#why)

## Over-time effects {#sec-explain2 visibility="uncounted"}

<br>

```{r overtime, fig.height=3.5, fig.width=8, fig.cap="Treatment Effect, by wave."}
DiDByWavePlot() +
  theme_ipl
```

[BACK](#why)

## Crowding Out {#sec-explain3 visibility="uncounted"}

<br>

```{r crowdout, fig.height=3.5, fig.width=8, fig.cap="Effect Conditional on Consumption of Other News Sources."}
CrowdOutEstimates(vis = T, col_scale = c(ipl_red, ipl_gray)) +
  theme_ipl +
  theme(legend.position = "none")

```

[BACK](#why)

## Attitude Crystallisation {#sec-explain4 visibility="uncounted"}

<br>

```{r migchange, warning=FALSE, fig.height=3, fig.width=6, fig.cap="Average Change in Immigration Attitude, by period"}
MigChangePlot(line_plot = T, 
              color_palette = c(ipl_red, ipl_gray), 
              distances = c(2)) +
  theme_ipl +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    text = element_text(family = "serif"),
    legend.position = "None"
  )
```

[BACK](#why)

### 2023-04-13 pres/Presentation.Rmd
prepare Job Talk

@@
 
-.footnote[(Very liberal after Sniderman and Theriault 2004)]
+.footnote[(Very freely after Sniderman and Theriault 2004)]
 
@@
 ## No observational studies assessing causal effect of framing!
-
----
-
-## What is necessary for the study of framing effects?
-
-<br>
-
-# 1. Precisely identifiable, sharp change of frames in communication.
-# 2. Good measure of frames in mind.
 
@@
 - **Clearly identifiable short-term-change** in migration coverage.
-- Clear expectations regarding impact.
+- Clear expectations regarding impact (more conservative migration attitudes).
 - Change not debated in the media $\rightarrow$__No co-treatment__! <font size="5" color="#004A95"> `r Citep(myBib["Spirig2020"])`</font>.
@@
 
-class: inverse, center, middle
+<!-- class: inverse, center, middle -->
 
-# How does this affect migration attitudes?
+<!-- # How does this affect migration attitudes? -->
 
----
+<!-- --- -->
 
-## Theoretical Expectations
+<!-- ## Theoretical Expectations -->
 
-.pull-left[
+<!-- .pull-left[ -->
 
-![](vis/CognitiveStorage.png)
+<!-- ![](vis/CognitiveStorage.png) -->
 
-]
+<!-- ] -->
 
-.pull-right[
+<!-- .pull-right[ -->
 
-### Increased exposure to crime frames will lead to...
-- H1: **more conservative** attitudes towards migration.
-- H2: **stronger association** of crime and migration attitudes.
+<!-- ### Increased exposure to crime frames will lead to... -->
+<!-- - H1: **more conservative** attitudes towards migration. -->
+<!-- - H2: **stronger association** of crime and migration attitudes. -->
 
-]
+<!-- ] -->
 
----
+<!-- --- -->
 
@@
   2. **Select crime frames**.
-    + Same, but subset of articles about migration content.
+    + Same procedure.
+    + Estimation of crime content **within** migration content.
 
@@
 
-TreatmentTrendPlot(size = 2, 
-                   dpa_corrected = T) +
+TreatmentTrendPlot(size = 2, dpa_corrected = F, palette = c("red", "#004A95")) +
   theme_xaringan()
@@
 
-German Longitudinal Election Study (GLES) Panel <font size="5" color="#004A95"> `r Citep(myBib["GLES2017Panel"])`</font>.
+### German Longitudinal Election Study (GLES) Panel <font size="5" color="#004A95"> `r Citep(myBib["GLES2017Panel"])`</font>.
 
-.pull-left[
+**Questions on:**
 
-### Immigration Attitudes
-- **Opportunities for immigration** of foreigners should be 
-  + extended (-3) or
-  + restricted (3).
-- Asked in **13** waves (1 pre).
-
-]
-
-.pull-right[
-
-### Integration Attitudes
-- Foreigners should...
-  + completely **adapt to German culture** (-3) or
-  + be able to live according to their own culture (3).
-- Asked in **4** waves (1 pre)
-
-]
-
----
-
-## Frames in Mind (continued)
-
-.pull-left[
-
-### Support for radical-right AfD
-- Attitude towards **AfD**
-  + strongly dislike (-5) to
-  + strongly like (5).
-- Asked in **14** waves (1 pre)
-
-### MIP: Migration
-- Binary indicator, 1 if most important problem is migration.
-
-]
-
-.pull-right[
-
-### Attitude towards crime policy
-- "state should get **more competences in fighting crime**, even if this means more surveillance"
-  + strongly disagree (1) to
-  + strongly agree (5).
-- Asked in **4** waves (1 pre)
-
-]
+- [Immigration Attitudes]()
+- [Integration Attitudes]()
+- [Crime Attitudes]()
+- [Support for RR]()
+- [Most Important Problem]()
 
@@
 ]
+
+---
+
+class: inverse, center, middle
+
+# Appendix
+
+---
+
+## Operationalization DV
+
+.pull-left[
+
+### Immigration Attitudes
+- **Opportunities for immigration** of foreigners should be 
+  + extended (-3) or
+  + restricted (3).
+- Asked in **13** waves (1 pre).
+
+]
+
+.pull-right[
+
+### Integration Attitudes
+- Foreigners should...
+  + completely **adapt to German culture** (-3) or
+  + be able to live according to their own culture (3).
+- Asked in **4** waves (1 pre)
+
+]
+
+---
+
+## Operationalization DV (continued)
+
+.pull-left[
+
+### Support for radical-right AfD
+- Attitude towards **AfD**
+  + strongly dislike (-5) to
+  + strongly like (5).
+- Asked in **14** waves (1 pre)
+
+### MIP: Migration
+- Binary indicator, 1 if most important problem is migration.
+
+]
+
+.pull-right[
+
+### Attitude towards crime policy
+- "state should get **more competences in fighting crime**, even if this means more surveillance"
+  + strongly disagree (1) to
+  + strongly agree (5).
+- Asked in **4** waves (1 pre)
+
+]

### 2023-04-13 code/functions/visualisation.R

@@ -14,12 +14,15 @@ library(dplyr)
 library(here)
 library(data.table)
 library(ggrepel)
+library(modelsummary)
+library(gt)
 
 
 # Migration Salience ####
 
 MigSaliencePlot <- function(aggregation = "months",
-                            dpa_corrected = T){
+                            dpa_corrected = T,
+                            papers = c("Bild", "FAZ", "Spiegel", "SZ", "TAZ", "Welt")){
   
   bert_ests <- 
     fread(
@@ -37,11 +40,12 @@ MigSaliencePlot <- function(aggregation = "months",
     mutate(date_new = lubridate::floor_date(date_clean, aggregation)) %>% 
     group_by(date_new, paper) %>% 
     summarise_all(mean) %>% 
-    filter(date_new < as.Date('2019-01-01')) %>%
+    filter(date_new < as.Date('2019-01-01'),
+           (paper %in% papers)) %>%
     ggplot(aes(x = date_new, y = mig_share, col = paper, lty = paper, shape = paper)) +
     geom_line() + geom_point() +
     ggtitle('Migration salience in different newspapers') +
-    xlab('') + ylab('Share of migration articles') +
+    xlab('') + ylab('Share of articles') +
     theme_minimal() +
     theme(text = element_text(family = "serif")) +
     labs(color = "Outlet", lty = "Outlet", shape = "Outlet") %>% 
@@ -105,7 +109,7 @@ TreatmentTrendPlot <- function(size = 1,
       geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "black", size = size) +
       geom_line(size = size) +
       geom_rug(data = survey_dates, aes(x = date), sides = 't', inherit.aes = F) +
-      ggtitle(paste0(aggregation, "ly Share of Migration Content Devoted to Crime Frames"), 
+      ggtitle(paste0(aggregation, "ly Attention to Crime"), 
               paste0("Bild vs. other major daily newspapers, 2016-", lubridate::year(maxdate))) + 
       xlab("Date") + 
       ylab(paste0("Share of Migration Articles", 
@@ -232,7 +236,8 @@ TreatmentDiDPlot <- function(size = 1,
 
 ## Descriptive visualisation - cntrl vs treatment (by group)
 DescPlot <- function(legend_position = "right",
-                     colorful = F){
+                     colorful = F, 
+                     col_palette = MetBrewer::met.brewer("Archambault", 2)){
   
[…]
